### 2018-09-10 Paper/Paper.tex
Started writing a paper

\documentclass[12pt]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor,graphicx}
\usepackage[subfolder,cleanup]{gnuplottex}
\usepackage{tikz}
\usepackage{pgfplots}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}

\newcommand{\diff}[3][]{\frac{d^{#1}#2}{d{#3}^{#1}}}
\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
\newcommand{\Es}{E_{sat}}
\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}

\title{}
\author{Brady Metherall}

\newgeometry{margin=1in}
\setlength\parindent{0pt}

\begin{document}
\maketitle

\section{Model}
Each component of the laser is treated separately and all processes will be composed to represent a single circuit of the laser.

\subsection{Gain}
As the pulse travels through the gain media the change in energy is
\begin{align*}
\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es},
\end{align*}
where $g_0$ is a small signal gain, and $E_{sat}$ is the energy at which the gain starts to saturate \cite{silfvast}. For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly. The energy can be solved analytically by separating and integrating yielding
\begin{align}
\label{eq:energy}
E(z) = \Es W_0 \left( \frac{E_0}{\Es} e^{E_0 / \Es} e^{g_0 z} \right),
\end{align}
where $W_0$ is the Lambert $W$ function. However, only the exiting energy is of interest, thus \eqref{eq:energy} can be written as
\begin{align*}
E' = \Es W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right),
\end{align*}
where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain media. Since the energy can be expressed as
\begin{align*}
E &= \int_{-\infty}^{\infty} |A(T)|^2 dT,
\end{align*}
it can be shown that
\begin{align*}
\frac{E'}{E} &= \left( \frac{A'}{A} \right)^2,
\end{align*}
and so the gain in terms of the amplitude is given by
\begin{align}
\label{eq:gain}
G(A) &= \left[ \frac{\Es}{E} W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right) \right]^{1/2} A.
\end{align}

\subsection{Dispersion}
Expressions for the amplitude as the pulse travels through the grating as well as the fibre can be derived from
\begin{align}
\label{eq:nlse}
i \pdiff{A}{z} - \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \gamma |A|^2 A = 0,
\end{align}
the non-linear Schr\"{o}dinger equation \cite{ferreira}. In the case of the dispersive element $\gamma$ is assumed to be negligible. Thus, \eqref{eq:nlse} reduces to
\begin{align*}
i \pdiff{A}{z} - \frac{1}{2} \beta_2 \pdiff[2]{A}{T} &= 0,
\end{align*}
and after taking the Fourier transform
\begin{align*}
\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
\end{align*}
The Fourier transform of $A$ can be found and evaluated at $z = L_d$ yielding
\begin{align*}
D(A) &= \FTi{e^{\frac{1}{2} i \beta_2 \omega^2 L_D} \FT{A}}
\end{align*}
as the effect of the dispersive element on the pulse.

\subsection{Fibre}
The effect of the fibre can also be found from \eqref{eq:nlse}, by assuming the dispersion of the fibre is negligible when compared to the dispersive element the non-linear Schr\"{o}dinger equation simplifies to
\begin{align*}
\pdiff{A}{z} - i \gamma |A|^2 A = 0,
\end{align*}
or after multiplying by the complex conjugate of $A$,
\begin{align}
\label{eq:fibre}
\pdiff{A}{z}\bar{A} - i \gamma |A|^4 = 0.
\end{align}
Adding \eqref{eq:fibre} to its complex conjugate gives
\begin{align}
\label{eq:fibre2}
\pdiff{|A|^2}{z} &= 0,
\end{align}
this suggests the envelope of the pulse does not change as it travels through the fibre, a solution of the form $A = A_0 e^{i \varphi}$ can be assumed. Substituting this expression into \eqref{eq:fibre2} gives $\varphi = \gamma |A|^2 z$ therefore
\begin{align*}
F(A) &= A e^{i \gamma |A|^2 L_f},
\end{align*}
where $L_f$ is the length of the fibre.

\subsection{Loss}
Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. It will be assumed all loss occurs at a particular point in the circuit, however, the model can easily be modified to account for the optical loss between each component. The loss is then given as
\begin{align*}
L(A) &= C e^{- \alpha L}A,
\end{align*}
where $C$ is the loss due to the output coupler, and $\alpha$ is a characteristic loss per length of the fibre.

\subsection{Modulation}
Pick
\begin{align*}
M(A) &= e^{-T^2 / 2 T_M^2} A
\end{align*}
since its Fourier transform is itself

\section{Non-Dimensionalization}

\begin{align*}
T = T_M \widetilde{T}, \quad E = \Es \widetilde{E}, \quad A = \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}, \quad \omega = \frac{\widetilde{\omega}}{T_M}
\end{align*}

\section{Results}

\begin{align*}
\left( \frac{W(a E e^E)}{E} \right)^{1/2} S(s) h = 1
\end{align*}

\begin{align*}
E = \frac{S(s)^2 h^2}{1 - S(s)^2 h^2} \ln \left( a S(s)^2 h^2 \right)
\end{align*}

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
f(x) = m * x + c
fit [0.03:0.6] f(x) '../sdata.dat' u 1:(log($2)) via m, c
set grid
set ytics 0.1
set xl '$s$'
set yl 'Spread'
plot '../sdata.dat' u 1:2 w p pt 7 ps 0.4 t 'Data', \
exp(f(x)) t '$\exp(-0.513865s + 0.00203874)$'
\end{gnuplot}
\caption{}
\label{fig:}
\end{figure}

\begin{figure}[htbp]
\centering
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
S(x) = exp(-0.5131 * x + 0.00174)
E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
a = 30

set grid

set pm3d map

set isosamples 100, 100
set hidden3d

set contour surface
set cntrparam levels incremental 0, 0.1, 1.5

set palette rgbformulae 22, 13, -31

set ytics 0.1
set xl '$s$'
set yl rotate by 0 '$h$'
set cbl rotate by 0 '$E$'
set xr [0:0.5]
set yr [0.3:0.6]

unset clabel

splot E(x, y) not

\end{gnuplot}
\caption{a=30}
\label{fig:}
\end{figure}

\newpage
\begin{thebibliography}{99}
\bibitem{silfvast}
Laser Fundamentals

\bibitem{ferreira}
Nonlinear Effects in Optical Fibers

\end{thebibliography}
\end{document}

### 2018-09-10 Lasers.py
Generated squish data

@@ -1,6 +1,7 @@
 import numpy as np
 import scipy.special.lambertw as W
 import matplotlib.pyplot as plt
+import time
 
 def Energy(A, dx):
 	return np.real(np.sum(A * np.conj(A)) * dx)
@@ -17,7 +18,9 @@ def Loss(A, h = 0.1):
 	return h * A
 
 def Mod(A, T, nu = 1, mu = 1):
-	return 1.0 / 2.0 * (1 - nu * np.cos(mu * np.pi * np.exp(-T**2))) * A
+	return np.exp(-T**2 / 2) * A
+	#return 1.0 / 2.0 * (1 - nu * np.cos(mu * np.pi * np.exp(-T**2))) * A
+	#return 1.0 / 2.0 * (np.cos(np.pi * T) + 1) * (T < 1) * (T > -1) * A
 
 def Fibre(A, f = 10):
 	return np.exp(1j * f * A * np.conj(A)) * A
@@ -29,15 +32,15 @@ def Disp(A, T, s = 0.1):
 	return np.fft.ifft(F * np.exp(1j * w**2 * s**2))
 
 # 1 round trip
-def Loop(A, T, dx):
-	A = Gain(A, Energy(A, dx))
-	A = Disp(A, T)
+def Loop(A, T, dx, s):
+	#A = Gain(A, Energy(A, dx))
+	#A = Fibre(A, 0)
+	#A = Loss(A, 0.5)
+	A = Disp(A, T, s)
 	A = Mod(A, T)
-	A = Loss(A, 0.25)
-	A = Fibre(A)
 	return A
 
-N = 280 # Number of loops of the circuit
+N = 100 # Number of loops of the circuit
 p = 2**12 # Number of points in the discretization
 width = 4 # Size of window
 E0 = 1 # Initial energy
@@ -45,12 +48,12 @@ E0 = 1 # Initial energy
 # Initialization
 T = np.linspace(-width, width, p, endpoint = False)
 dx = T[1] - T[0]
-A0 = np.exp(1j * np.pi * 1.0 / 4.0) / np.cosh(5 * T)
+A0 = 1 / np.cosh(2 * T) * np.exp(1j * np.pi / 4)
 A0 = np.sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
 E = np.zeros(N)
 data = np.zeros((2 * N, p))
 A = A0
-
+'''
[…]

### 2018-09-11 Paper/Paper.tex
Added bib file

@@
 \usepackage[subfolder,cleanup]{gnuplottex}
-\usepackage{tikz}
-\usepackage{pgfplots}
 %\usepackage{amsthm}
@@
 %\usepackage{hyperref}
+\usepackage{biblatex}
+
+\bibliography{Ref.bib}
 
@@
 
+\begin{align*}
+G(A) &= \left( \frac{W_0 \left( a E e^{E}\right)}{E} \right)^{1/2} A.
+\end{align*}
+
+\begin{align*}
+D(A) &= \FTi{e^{i s^2 \omega^2} \FT{A}}
+\end{align*}
+
+\begin{align*}
+F(A) &= A e^{i b |A|^2},
+\end{align*}
+
+\begin{align*}
+L(A) &= h A,
+\end{align*}
+
+\begin{align*}
+M(A) &= e^{-T^2 / 2} A
+\end{align*}
+
+\begin{align*}
+a = e^{g_0 L_g} \quad s^2 = \frac{\beta_2 L_D}{2 T_M^2}, \quad b = \gamma L_F \frac{\Es}{T_M}, \quad h = C e^{-\alpha L}
+\end{align*}
+
 \section{Results}
@@
 f(x) = m * x + c
-fit [0.03:0.6] f(x) '../sdata.dat' u 1:(log($2)) via m, c
+fit f(x) '../sdata.dat' u 1:(log($2)) via m, c
 set grid
@@
 plot '../sdata.dat' u 1:2 w p pt 7 ps 0.4 t 'Data', \
-exp(f(x)) t '$\exp(-0.513865s + 0.00203874)$'
+exp(f(x)) t '$\exp(-0.521294s + 0.00365752)$'
 \end{gnuplot}
@@
 \newpage
-\begin{thebibliography}{99}
-\bibitem{silfvast}
-Laser Fundamentals
+\appendix
+\section{Numbers}
 
-\bibitem{ferreira}
-Nonlinear Effects in Optical Fibers
+\begin{table}
+\begin{tabular}{|l|l|}
+\hline
+Parameter & Value \\
+\hline
+$\beta_2^g L_D$ & $10$--$2000 \text{ps}^2$ \\
+$g_0$ & $1$--$10 \text{m}^{-1}$ \\
+$\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
+$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \\
+$\Es$ & $10^4 \text{pJ}$ \\
+$L_g$ & $3 \text{m}$ \\
+\hline
+\end{tabular}
+\end{table}
 
-\end{thebibliography}
+\newpage
+\printbibliography
 \end{document}

### 2018-09-13 Paper/Paper.tex
Updated model section

@@
 %\usepackage{subcaption}
-%\usepackage{hyperref}
+\usepackage{hyperref}
 \usepackage{biblatex}
@@
 \section{Model}
-Each component of the laser is treated separately and all processes will be composed to represent a single circuit of the laser.
+The laser cavity is treated as the composition of five independent process---gain, nonlinearity, loss, dispersion, and modulation.
+Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal, ferreira, shtyrina, yarutkina},
+\begin{align}
+\label{eq:nlse}
+\pdiff{A}{z} = - i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
+\end{align}
+where $A$ is the complex amplitude of the pulse, $\beta_2$ and $\beta_3$ are the second and third order dispersion coefficients respectively, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fiber.
 
 \subsection{Gain}
-As the pulse travels through the gain media the change in energy is
+Within the Er-doped gain fiber the other four processes are assumed to be negligible, and so \eqref{eq:nlse} reduces to
+\begin{align}
+\label{eq:gainde}
+\pdiff{A}{z} = \frac{1}{2} g(A) A
+\end{align}
+with
 \begin{align*}
-\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es},
+g(A) &= \frac{g_0}{1 + E / \Es},
 \end{align*}
-where $g_0$ is a small signal gain, and $E_{sat}$ is the energy at which the gain starts to saturate \cite{silfvast}.
+where $g_0$ is a small signal gain, $\Es$ is the energy at which the gain begins to saturate, and \begin{align*}
+E = \int_{-\infty}^\infty |A|^2 \, dT,
+\end{align*}
+is the energy of the pulse \cite{bohun, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
+\begin{align*}
+\pdiff{A}{z} = \frac{1}{2} \cdot \frac{g_0 A}{1 + E / \Es},
+\end{align*}
+multiplying by $\bar{A}$, the complex conjugate of $A$, and then adding the complex conjugate gives
+\begin{align*}
+\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es},
+\end{align*}
+which after integrating becomes
+\begin{align*}
+\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
+\end{align*}
 For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-The energy can be solved analytically by separating and integrating yielding
+A closed form of the energy can be found by separating and integrating yielding
 \begin{align}
@@
 \end{align*}
-where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain media. Since the energy can be expressed as
-\begin{align*}
-E &= \int_{-\infty}^{\infty} |A(T)|^2 dT,
-\end{align*}
-it can be shown that
-\begin{align*}
-\frac{E'}{E} &= \left( \frac{A'}{A} \right)^2,
-\end{align*}
-and so the gain in terms of the amplitude is given by
+where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain fiber. Since $E \sim |A|^2$ the gain in terms of the amplitude is given by
 \begin{align}
@@
 
-\subsection{Dispersion}
-Expressions for the amplitude as the pulse travels through the grating as well as the fibre can be derived from
-\begin{align}
-\label{eq:nlse}
-i \pdiff{A}{z} - \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \gamma |A|^2 A = 0,
-\end{align}
-the non-linear Schr\"{o}dinger equation \cite{ferreira}. In the case of the dispersive element $\gamma$ is assumed to be negligible. Thus, \eqref{eq:nlse} reduces to
-\begin{align*}
-i \pdiff{A}{z} - \frac{1}{2} \beta_2 \pdiff[2]{A}{T} &= 0,
-\end{align*}
-and after taking the Fourier transform
-\begin{align*}
-\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
-\end{align*}
-The Fourier transform of $A$ can be found and evaluated at $z = L_d$ yielding
-\begin{align*}
-D(A) &= \FTi{e^{\frac{1}{2} i \beta_2 \omega^2 L_D} \FT{A}}
-\end{align*}
-as the effect of the dispersive element on the pulse.
-
-\subsection{Fibre}
-The effect of the fibre can also be found from \eqref{eq:nlse}, by assuming the dispersion of the fibre is negligible when compared to the dispersive element the non-linear Schr\"{o}dinger equation simplifies to
+\subsection{Nonlinearity of Fiber}
+The effect of the nonlinearity of the fiber can also be found from \eqref{eq:nlse}:
 \begin{align*}
@@
 \end{align*}
-or after multiplying by the complex conjugate of $A$,
+which similarly to the gain, can be transformed by multiplying by the complex conjugate of $A$, and adding its complex conjugate gives
 \begin{align}
 \label{eq:fibre}
-\pdiff{A}{z}\bar{A} - i \gamma |A|^4 = 0.
+\pdiff{|A|^2}{z} &= 0.
 \end{align}
-Adding \eqref{eq:fibre} to its complex conjugate gives
-\begin{align}
-\label{eq:fibre2}
-\pdiff{|A|^2}{z} &= 0,
-\end{align}
-this suggests the envelope of the pulse does not change as it travels through the fibre, a solution of the form $A = A_0 e^{i \varphi}$ can be assumed.
-Substituting this expression into \eqref{eq:fibre2} gives $\varphi = \gamma |A|^2 z$ therefore
+This suggests the envelope of the pulse does not change as it travels through the fiber---a solution of the form $A = A_0 e^{i \varphi}$ can be assumed.
+Substituting this expression into \eqref{eq:fibre} gives $\varphi = \gamma |A|^2 z$ therefore
 \begin{align*}
@@
 \end{align*}
-where $L_f$ is the length of the fibre.
+where $L_f$ is the length of the fiber.
 
@@
 Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit.
-It will be assumed all loss occurs at a particular point in the circuit, however, the model can easily be modified to account for the optical loss between each component.
+It will be assumed all loss occurs at a particular point in the circuit because of the extremely high reflectivity of the fiber the optical loss is negligible compared to the output coupler loss ***cite.
 The loss is then given as
@@
 \end{align*}
-where $C$ is the loss due to the output coupler, and $\alpha$ is a characteristic loss per length of the fibre.
+where $C$ is the loss due to the output coupler.
+
+\subsection{Dispersion}
+The dominant dispersion is due to the chirped fiber Bragg grating (CFBG)---the dispersion due to the fiber is negligible in comparison \cite{agrawalother}.
+The dispersive pieces of \eqref{eq:nlse} give
+\begin{align}
+\label{eq:disp}
+\pdiff{A}{z} = -i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T},
+\end{align}
+but, the third order effects of dispersion will be neglected ***cite.
+Although, under some circumstances they may need to be considered since the CFBG is highly dispersive \cite{litchinitser}.
+Taking the Fourier transform of \eqref{eq:disp} gives
+\begin{align*}
+\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
+\end{align*}
+The Fourier transform of $A$ can be found by integrating and
+\begin{align*}
+D(A) &= \FTi{e^{i \frac{1}{2} \beta_2 \omega^2 L_D} \FT{A}}
+\end{align*}
+is the effect of the CFBG on the pulse.
 
 \subsection{Modulation}
-Pick
+Pick a function that is bump-like, infinitely differentiable (I don't know how important that is), and has a maximum of $1$. We shall pick
 \begin{align*}
-M(A) &= e^{-T^2 / 2 T_M^2} A
+M(A) &= e^{-T^2 / 2 T_M^2} A,
 \end{align*}
-since its Fourier transform is itself
+where $T_M$ is a characteristic width of the modulation, since its Fourier transform is itself. ***I don't know how to write this.
+
+\subsection{Combining the Pieces}
+
+\begin{align*}
+\mathcal{L}(A) = M(D(L(F(G(A)))))
+\end{align*}
+
+A solution such that $|\mathcal{L}(A)|^2 = |A|^2$ is sought.
 
@@
 
-\newpage
-\appendix
-\section{Numbers}
-
 \begin{table}
@@
 $\Es$ & $10^4 \text{pJ}$ \\
-$L_g$ & $3 \text{m}$ \\
+$L_G$ & $3 \text{m}$ \\
 \hline

### 2018-09-13 Paper/Paper.tex
Added references to derivation of model

@@
 The laser cavity is treated as the composition of five independent process---gain, nonlinearity, loss, dispersion, and modulation.
-Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal, ferreira, shtyrina, yarutkina},
+Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal2013, ferreira, shtyrina, yarutkina},
 \begin{align}
@@
 \end{align*}
-is the energy of the pulse \cite{bohun, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
+is the energy of the pulse \cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
 \begin{align*}
@@
 \subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit.
-It will be assumed all loss occurs at a particular point in the circuit because of the extremely high reflectivity of the fiber the optical loss is negligible compared to the output coupler loss ***cite.
-The loss is then given as
+Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. The loss is then given as
 \begin{align*}
@@
 \subsection{Dispersion}
-The dominant dispersion is due to the chirped fiber Bragg grating (CFBG)---the dispersion due to the fiber is negligible in comparison \cite{agrawalother}.
-The dispersive pieces of \eqref{eq:nlse} give
+The dominant dispersion is due to the chirped fiber Bragg grating (CFBG).
+The dispersion due to the fiber is negligible in comparison---a $10$cm chirped grating can provide as much dispersion as $300$km of fiber \cite{agrawal2002}.
+The dispersive terms of \eqref{eq:nlse} give
 \begin{align}
@@
 \end{align}
-but, the third order effects of dispersion will be neglected ***cite.
-Although, under some circumstances they may need to be considered since the CFBG is highly dispersive \cite{litchinitser}.
+however, the third order effects of dispersion will be neglected \cite{agrawal2013, ferreira}.
+Although, under some circumstances they may need to be considered since the grating is highly dispersive \cite{agrawal2013, litchinitser}.
 Taking the Fourier transform of \eqref{eq:disp} gives
@@
 \end{align*}
-The Fourier transform of $A$ can be found by integrating and
+The Fourier transform of $A$ can be found by integrating and thus,
 \begin{align*}
@@
 \end{align*}
-is the effect of the CFBG on the pulse.
+is the effect of the grating on the pulse.
 

### 2018-09-18 Paper/Paper.tex
Added linear solution

@@
 
+\subsection{Non-Dimensionalization}
+The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
+Specifically, the time shall be scaled by the characteristic modulation time, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
+\begin{align*}
+T = T_M \widetilde{T}, \quad E = \Es \widetilde{E}, \quad A = \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
+\end{align*}
+The new process maps, after dropping the tildes, become
+\begin{align*}
+G(A) &= \left( \frac{W_0 \left( a E e^{E}\right)}{E} \right)^{1/2} A, \\
+F(A) &= A e^{i b |A|^2}, \\
+L(A) &= h A, \\
+D(A) &= \FTi{e^{i s^2 \omega^2} \FT{A}}, \\
+M(A) &= e^{-T^2 / 2} A,
+\end{align*}
+with the dimensionless parameters
+\begin{align*}
+a = e^{g_0 L_g} \sim 30, \quad s = \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.1, \quad b = \gamma L_F \frac{\Es}{T_M} \sim 0.1, \quad h = C e^{-\alpha L} \sim 0.25,
+\end{align*}
+which control the behaviour of the laser.
+
 \subsection{Combining the Pieces}
@@
 
-\section{Non-Dimensionalization}
-
+\section{Results}
+\subsection{Linear Solution}
+Suppose an initial pulse with envelope
 \begin{align*}
-T = T_M \widetilde{T}, \quad E = \Es \widetilde{E}, \quad A = \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}, \quad \omega = \frac{\widetilde{\omega}}{T_M}
+|A_0| = \sqrt{P} e^{-x^2 / 2 \sigma^2},
+\end{align*}
+the after passing through the gain and loss pieces, and neglecting the fibre nonlinearity, the envelope will be
+\begin{align*}
+|A| = \sqrt{P} g(E) h e^{-x^2 / 2 \sigma^2},
+\end{align*}
+where
+\begin{align*}
+g(E) = \left( \frac{W_0(a E e^E)}{E} \right)^{1/2}
+\end{align*}
+is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread. This can be represented as
+\begin{align*}
+|A| = \sqrt{P} g(E) h \zeta(s, b) e^{-x^2 / 2 \tilde{\sigma}^2}
+\end{align*}
+where $\zeta(s, b)$ represents the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. Although, note that the dispersive element conserves energy, thus,
+\begin{align*}
+\int_{-\infty}^{\infty} P g(E)^2 h^2 e^{-x^2 / \sigma^2} \, dx = \int_{-\infty}^{\infty} P g(E)^2 h^2 \zeta^2(s, b) e^{-x^2 / \widetilde{\sigma}^2} \, dx,
+\end{align*}
+or more simply
+\begin{align*}
+\sigma = \zeta^2(s, b) \widetilde{\sigma}.
+\end{align*}
+Therefore, the envelope as the pulse exits the grating is
+\begin{align*}
+|A| = \sqrt{P} g(E) h \zeta(s, b) \exp \left( -\zeta^4(s, b) \frac{x^2}{2 \sigma^2} \right).
+\end{align*}
+Lastly, the pulse is modulated and so
+\begin{align*}
+|A| = \sqrt{P} g(E) h \zeta(s, b) \exp \left( -\zeta^4(s, b) \frac{x^2}{2 \sigma^2} - \frac{x^2}{2} \right).
+\end{align*}
+In equilibrium the envelope of the pulse is unchanged after passing through each element, in other words,
+\begin{align*}
+\sqrt{P} e^{-x^2 / 2 \sigma^2} =  \sqrt{P} g(E) h \zeta(s, b) \exp \left( -\zeta^4(s, b) \frac{x^2}{2 \sigma^2} - \frac{x^2}{2} \right).
+\end{align*}
+For this to be the case 
+\begin{align}
+\label{eq:energycond}
+\left( \frac{W_0(a E e^E)}{E} \right)^{1/2} h \zeta(s, b) = 1,
+\end{align}
+as well as
+\begin{align*}
+-x^2 / 2 \sigma^2 = -\zeta^4(s, b) \frac{x^2}{2 \sigma^2} - \frac{x^2}{2},
+\end{align*}
+which reduces to
+\begin{align*}
+\sigma = \sqrt{1 - \zeta^4(s, b)}.
 \end{align*}
@@
 \begin{align*}
-G(A) &= \left( \frac{W_0 \left( a E e^{E}\right)}{E} \right)^{1/2} A.
+P = \frac{E}{\sqrt{\pi} \sigma}
 \end{align*}
 
+From \eqref{eq:energycond} the equilibrium energy is found to be
 \begin{align*}
-D(A) &= \FTi{e^{i s^2 \omega^2} \FT{A}}
-\end{align*}
-
-\begin{align*}
-F(A) &= A e^{i b |A|^2},
-\end{align*}
-
-\begin{align*}
-L(A) &= h A,
-\end{align*}
-
-\begin{align*}
-M(A) &= e^{-T^2 / 2} A
-\end{align*}
-
-\begin{align*}
-a = e^{g_0 L_g} \quad s^2 = \frac{\beta_2 L_D}{2 T_M^2}, \quad b = \gamma L_F \frac{\Es}{T_M}, \quad h = C e^{-\alpha L}
-\end{align*}
-
-\section{Results}
-
-\begin{align*}
-\left( \frac{W(a E e^E)}{E} \right)^{1/2} S(s) h = 1
-\end{align*}
-
-\begin{align*}
-E = \frac{S(s)^2 h^2}{1 - S(s)^2 h^2} \ln \left( a S(s)^2 h^2 \right)
+E = \frac{\zeta^2(s, b) h^2}{1 - \zeta^2(s, b) h^2} \ln \left( a \zeta^2(s, b) h^2 \right).
 \end{align*}
@@
 set xl '$s$'
-set yl 'Spread'
-plot '../sdata.dat' u 1:2 w p pt 7 ps 0.4 t 'Data', \
-exp(f(x)) t '$\exp(-0.521294s + 0.00365752)$'
+set yl rotate by 0 '$\zeta(s)$'
+plot '../sdata.dat' u 1:2 w p pt 7 ps 0.2 t 'Data', \
+exp(f(x)) dt 4 t '$\exp(-0.521294s + 0.00365752)$'
 \end{gnuplot}
 \caption{}
-\label{fig:}
+\label{fig:zeta}
 \end{figure}
@@
 $\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
-$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \\
+$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
 $\Es$ & $10^4 \text{pJ}$ \\
-$L_G$ & $3 \text{m}$ \\
+$L_G$ & $2$--$3 \text{m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
 \hline
 \end{tabular}
+\caption{yes}
 \end{table}

### 2018-10-09 Paper/Paper.tex
Added Sean's additions

--- 2018-09-13 Paper/Paper.tex
@@
 
-\newcommand{\diff}[3][]{\frac{d^{#1}#2}{d{#3}^{#1}}}
+\providecommand{\df}{\textrm{d}}
+\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
 \newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
-\newcommand{\Es}{E_{sat}}
+\newcommand{\Es}{E_{\textrm{sat}}}
 \newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
@@
 
+\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
+\DeclareMathOperator{\sgn}{sgn}
+
+%Impetutus: Want every student to have at least one experiential learning opportunity by the time they graduate.
+%Stake from province: 780K received to do this
+%
+%Examples of experiential learning:
+%industry or community agency sponsored research projects
+%interactive simulations
+%capstone projects
+%on-campus work/teaching labs
+%performance based learning
+%
+%Checkmark 1: Student is in a workplace or a simulated workplace.
+%This could be a lab or a workstation.  Use of industry standard software.  Case study application.
+%Field trips provided that it meets all of the criteria.
+%
+%Checkmark 2: Student is exposed to authentic demands that improve employability.
+%Initiative, communication, conflict resolution, making them use their own initiative to solve
+%problems that may arise.
+%
+%Checkmark 3: Experience is structured, with purposeful and meaningful activities.
+%Planning, supervision, guidance, check-in.  There is resource from Reyerson that helps break this down
+%This is not just photocopying or filing.
+%
+%Checkmark 4: Student applies program knowledge.
+%Relevance to course learning and encourage students to be flexible.
+%
+%Checkmark 5: Experience includes self-evaluation and assessment of learning outcomes.
+%This is a typical stumbling block and requires that the student is reflective on what was learned and
+%how this applies to future learning.  Assessment of the student's work is tied to to the learning outcomes.
+%Student's need to be introduced to meaningful reflection.
+%
+%Checkmark 6: Experience includes formal recognition.
+%Recognition has to acknowledge the experience meets the previous five criteria.
+%
+% HIGH LEVEL IDEAS:
+%Case studies - partnership with a pharmaceutical firm to develop in-office posters to explain how a 
+%drug works for use by a physician. (Check out RIIPEN website)
+%Field trips - design and incorporate activity, conceptualization, and reflection.  A tour of an R&D facility.
+%Hackathons - Student-led intensive sessions to solve real-world problems.  Interdisciplinary teams
+%to create ideas for a community healthcare initiative.
+%
+%
+%
+%Promoting a tapestry of science.
+
 \title{}
-\author{Brady Metherall}
+\author{Brady Metherall \& C.\ Sean Bohun}
 
 \newgeometry{margin=1in}
-\setlength\parindent{0pt}
+%\setlength\parindent{0pt}
 
@@
 
-\section{Model}
-The laser cavity is treated as the composition of five independent process---gain, nonlinearity, loss, dispersion, and modulation.
-Expressions for each component will be derived from the  generalized nonlinear Schr\"{o}dinger equation \cite{agrawal2013, ferreira, shtyrina, yarutkina},
+\noindent
+To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review 
+of the efforts to describe an `average' model.  The idea is to capture some of the physical the elements 
+in the waveform (dispersion, modulation and gain/loss) described by an effective PDE, the solution of
+which gives the amplitude of the wave packet.
+
+\section{Average Model}
+
+The model for the amplitude in the `average' model is presupposed to have the form
+\begin{equation}
+\label{average}
+	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
+\end{equation}
+where $A=A(T,z)$ is the complex amplitude of the pulse
+with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the
+modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.  Expression~(\ref{average}) is reminiscent of the 
+nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
+Consequently, the ansatz for the amplitude is taken to be a function of the form
+\begin{equation}
+\label{ansatz}
+	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
+	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
+\end{equation}
+so that the modulus, $|A|$, and the phase, $A/|A|$, are given by
+\begin{align*}
+	\left|A\right| &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)^{1/2}
+	\exp\left(-\frac{\delta \Omega^2 T^2}{2(1 + C^2)}\right),&
+	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
+	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
+\end{align*}
+The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where
+$2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$
+is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ 
+since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}}
+f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
+\[
+	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t
+	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
+	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
+\]
+and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$.  The corresponding half-width of the
+pulse duration comes from the expression for $|A|$ and gives
+\begin{equation}
+\label{duration}
+	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
+\end{equation}
+
+Applying the form~(\ref{ansatz}) to expression~(\ref{average}) provides the algebraic condition
+\begin{align*}
+	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
+	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right)-\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
+	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
+	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
+\end{align*}
+Treating this condition as a complex valued quadratic in $T$ gives four conditions.  Assuming that $\psi\in\mathbb{R}$,
+the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
+\begin{align*}
+	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
+	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
+	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
+	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
+\end{align*}
+Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that 
+$\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$. 
+From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, 
+$\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).  
+The result is a two parameter family of solutions
+of the form~(\ref{ansatz}) with
+\begin{align*}
+	C &= \sgn(\beta_2),&
+	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2},&
+	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
+	g &= \left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2}.
+\end{align*}
+Moreover, we also see that the representation~(\ref{ansatz})
+as a classical solution of~(\ref{average}) imposes a subclass of solutions with 
+$g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.  
+A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
+\begin{align*}
+	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.
+\end{align*}
+
+Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.  In practice, 
+at high power levels, the gain drops as the fibre saturates.  One can model this with a gain term that
+takes the form
+\begin{equation}
+\label{newg}
+	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
+\end{equation}
+where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity.
+The power in the fibre depends on the frequency $f$ and modulus of the pulse so that
+\begin{align*}
+	f \int_{-\infty}^\infty |A(s)|^2\, \df s &=
+	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 = \Delta P_0, &
+	\Delta &= \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}=
+	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
+\end{align*}
+where $\Delta$ is the duty cycle of the pulse.  Denoting the saturation power as 
+$P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
+\[
+	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f}  \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/4}
+	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
+\]
+
+Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.  
+The representative hyperbola, $\epsilon|\beta_2| = 2g^2$ correspond to constant gain while
+the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
+Curves of constant power level are also indicated.  One of the main drawbacks of this model is 
+the fixed chirp and its symmetric behaviour with respect to $T$.  One way to alleviate some of these
+restrictions is to construct a discrete model whereby each of the modules in the tuneable laser
+are given by a transfer function that is motivated by the PDE~(\ref{average}).  In particular, the
+dispersion and the modulation would correspond to transfer functions of the form
+\begin{align}
+	\hat{A}_{\textrm{out}}(\omega) &= \hat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
+	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
+\end{align}
+respectively where the dispersion is naturally defined in the frequency domain.  Between the modules, 
+the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent
+with the transfer functions.  Details of this technique and its ability of predict a number of experimental
+effects can be found in~\cite{burgoyne2014}.
+
+\section{A New Model}
+Rather than using a transfer function with a linear PDE, we instead return to generalized nonlinear 
+Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
 \begin{align}
 \label{eq:nlse}
-\pdiff{A}{z} = - i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
+\pdiff{A}{z} = - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} 
++ i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
 \end{align}
-where $A$ is the complex amplitude of the pulse, $\beta_2$ and $\beta_3$ are the second and third order dispersion coefficients respectively, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fiber.
+to represent the waveform.  In this expression, $\beta_3$ is the third order dispersion coefficient, 
+$\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
+Using this expression as a starting point, the laser cavity is assumed to be composed of five independent 
+processes---gain, nonlinearity, loss, dispersion, and modulation. 
+Within each component of the laser cavity the other four process are assumed to be negligible, that is, 
+each process is dominant only within one part of the laser, just as with the discrete model, but embracing
+any nonlinearities.
 
 \subsection{Gain}
-Within the Er-doped gain fiber the other four processes are assumed to be negligible, and so \eqref{eq:nlse} reduces to
+Considering the gain term as dominant as is expected with the 
+the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
 \begin{align}
 \label{eq:gainde}
-\pdiff{A}{z} = \frac{1}{2} g(A) A
+	\pdiff{A}{z} &= \frac{1}{2} g(A) A,& g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
 \end{align}
-with
+where $g_0$ is a small signal gain, $E$ is the energy of the 
+pulse~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina} and $\Es$ is the energy at which the gain 
+begins to saturate.
+%We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
+Multiplying~\eqref{eq:gainde} by $\bar{A}$, the complex conjugate of $A$, yields
 \begin{align*}
-g(A) &= \frac{g_0}{1 + E / \Es},
+	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es}.
 \end{align*}
-where $g_0$ is a small signal gain, $\Es$ is the energy at which the gain begins to saturate, and \begin{align*}
-E = \int_{-\infty}^\infty |A|^2 \, dT,
-\end{align*}
-is the energy of the pulse \cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}. We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. Taking
-\begin{align*}
-\pdiff{A}{z} = \frac{1}{2} \cdot \frac{g_0 A}{1 + E / \Es},
-\end{align*}
-multiplying by $\bar{A}$, the complex conjugate of $A$, and then adding the complex conjugate gives
-\begin{align*}
-\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es},
-\end{align*}
-which after integrating becomes
-\begin{align*}
+Adding this to its complex conjugate and integrating over $T$ gives
+%\begin{align*}
+%	\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
+%\end{align*}
+%After integrating this becomes
+\begin{align}
+\label{diffez}
 	\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
-\end{align*}
+\end{align}
 For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-A closed form of the energy can be found by separating and integrating yielding
+To obtain a closed form, integrate~(\ref{diffez}) over a gain fibre of length $z$ and assume the energy
+increases from $E$ to $E_{\textrm{out}}$ so that
+\[
+	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es}
+\]
+and by exponentiating, rearranging, and applying $W_0$, the positive branch of the Lambert $W$ function,
+\[
+	 W_0\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
+	 W_0\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
+\]
+This results in the closed form expression
 \begin{align}
 \label{eq:energy}
-E(z) = \Es W_0 \left( \frac{E_0}{\Es} e^{E_0 / \Es} e^{g_0 z} \right),
+	E_{\textrm{out}}(z) = \Es W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
 \end{align}
-where $W_0$ is the Lambert $W$ function. However, only the exiting energy is of interest, thus \eqref{eq:energy} can be written as
-\begin{align*}
-E' = \Es W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right),
-\end{align*}
-where $E$ is the energy of the incoming pulse, and $E'$ is the energy after traveling through the length of the gain fiber. Since $E \sim |A|^2$ the gain in terms of the amplitude is given by
+with the desired property that $E_{\textrm{out}}(0)=E$.  Since $E \sim |A|^2$, the gain in terms of 
+the amplitude is given by
 \begin{align}
 \label{eq:gain}
-G(A) &= \left[ \frac{\Es}{E} W_0 \left( \frac{E}{\Es} e^{E / \Es} e^{g_0 L_g} \right) \right]^{1/2} A.
+	G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = 
+	\left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
+	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
+\end{align}
+where $L_g$ is the length of the gain fibre.
+
+\subsection{Fibre Nonlinearity}
+The nonlinearity of the fibre depends on the parameter $\gamma$.  In regions where this effect is dominant 
+expression~\eqref{eq:nlse} gives
+\begin{align}
+\label{eq:fibrediff}
+	\pdiff{A}{z} - i \gamma |A|^2 A = 0,
+\end{align}
+so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
+Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives 
+$\varphi(T,z) = \gamma |A|^2 z$. For a fibre of length $L_f$ the effect of the nonlinearity is therefore
+\begin{align}
+\label{eq:fibre}
+	F(A) &= A e^{i \gamma |A|^2 L_f}.
 \end{align}
 
-\subsection{Nonlinearity of Fiber}
-The effect of the nonlinearity of the fiber can also be found from \eqref{eq:nlse}:
-\begin{align*}
-\pdiff{A}{z} - i \gamma |A|^2 A = 0,
-\end{align*}
-which similarly to the gain, can be transformed by multiplying by the complex conjugate of $A$, and adding its complex conjugate gives
+\subsection{Loss}
+Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss 
+due to absorption and scattering. Combining these two effect gives a loss that takes the form
 \begin{align}
-\label{eq:fibre}
-\pdiff{|A|^2}{z} &= 0.
+\label{eq:fibreloss}
+	L(A) &= C e^{- \alpha L}A,
 \end{align}
-This suggests the envelope of the pulse does not change as it travels through the fiber---a solution of the form $A = A_0 e^{i \varphi}$ can be assumed.
-Substituting this expression into \eqref{eq:fibre} gives $\varphi = \gamma |A|^2 z$ therefore
-\begin{align*}
-F(A) &= A e^{i \gamma |A|^2 L_f},
-\end{align*}
-where $L_f$ is the length of the fiber.
-
-\subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to the circuit. The loss is then given as
-\begin{align*}
-L(A) &= C e^{- \alpha L}A,
-\end{align*}
-where $C$ is the loss due to the output coupler.
+where $C$ is the percentage lost due to the output coupler, and $L$ is the length of the laser circuit.
 
 \subsection{Dispersion}
-The dominant dispersion is due to the chirped fiber Bragg grating (CFBG).
-The dispersion due to the fiber is negligible in comparison---a $10$cm chirped grating can provide as much dispersion as $300$km of fiber \cite{agrawal2002}.
-The dispersive terms of \eqref{eq:nlse} give
+Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).  In comparision,
+the dispersion due to the fibre is negligible.\footnote{A $10$ cm chirped grating can provide as much dispersion 
+as $300$ km of fibre~\cite{agrawal2002}.} The dispersive terms of \eqref{eq:nlse} give
 \begin{align}
 \label{eq:disp}
-\pdiff{A}{z} = -i \frac{1}{2} \beta_2 \pdiff[2]{A}{T} + \frac{1}{6} \beta_3 \pdiff[3]{A}{T},
+	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
 \end{align}
-however, the third order effects of dispersion will be neglected \cite{agrawal2013, ferreira}.
-Although, under some circumstances they may need to be considered since the grating is highly dispersive \cite{agrawal2013, litchinitser}.
-Taking the Fourier transform of \eqref{eq:disp} gives
+and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform 
+of~\eqref{eq:disp}, giving the result that
 \begin{align*}
-\pdiff{\FT{A}}{z} &= \frac{1}{2} i \beta_2 \omega^2 \FT{A}.
+	\pdiff{\FT{A}}{z} &= i\frac{\omega^2}{2}\left(\beta_2 + \frac{\beta_3}{3} \omega\right) \FT{A}.
 \end{align*}
-The Fourier transform of $A$ can be found by integrating and thus,
-\begin{align*}
-D(A) &= \FTi{e^{i \frac{1}{2} \beta_2 \omega^2 L_D} \FT{A}}
-\end{align*}
-is the effect of the grating on the pulse.
+The affect of dispersion is then
+\begin{align}
+\label{eq:dispersion}
+	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 + \beta_3 \omega/3)/2} \FT{A}}.
+\end{align}
+For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
+However, for simplicity in the basic model, the third order effect will be neglected so we set $\beta_3=0$ for 
+the subsequent analysis~\cite{agrawal2013, ferreira}.
 
 \subsection{Modulation}
-Pick a function that is bump-like, infinitely differentiable (I don't know how important that is), and has a maximum of $1$. We shall pick
+In the average model the amount of modulation is characterized by the parameter $\epsilon$ through
+the term $\frac{\epsilon}{2}T^2 A$.  In the new model, the modulation is considered to be applied
+externally through its action on the spectrum and for simplicity the representation is taken as a
+Gaussian pulse  
+\begin{align}
+	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
+\end{align}
+where $T_M$ is a characteristic width of the modulation.\footnote{Taking the Fourier transform, 
+$\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
+
+\subsection{Non-Dimensionalization}
+The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
+Specifically, the time shall be scaled by the characteristic modulation time, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
 \begin{align*}
-M(A) &= e^{-T^2 / 2 T_M^2} A,
+	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
 \end{align*}
-where $T_M$ is a characteristic width of the modulation, since its Fourier transform is itself. ***I don't know how to write this.
+The new process maps, after dropping the tildes, become
+\begin{align*}
+	G(A) &= \left(E^{-1} W_0 \left( a E e^{E}\right) \right)^{1/2} A,&
+	F(A) &= A \textrm{e}^{i b |A|^2},&
+	L(A) &= h A,\\
+	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
+	M(A) &= \textrm{e}^{-T^2 / 2} A,
+\end{align*}
+with four dimensionless parameter groups (see Table~\ref{tab:values})
+\begin{align*}
+	a &= \textrm{e}^{g_0 L_g} \sim 30,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.1,&
+	b &= \gamma L_F \frac{\Es}{T_M} \sim 0.1,& h &= C \textrm{e}^{-\alpha L} \sim 0.25,
+\end{align*}
+which control the behaviour of the laser.
 
 \subsection{Combining the Pieces}
-
+In this model the pulse is iteratively passed through each process, the order of which is now
+important.  In this first realization, the pulse is first
+amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity 
+needs to be considered. The pulse is then tapped off by the output coupler, and then passes 
+through the grating and is modulated. The pulse after one complete circuit of the laser 
+cavity is then passed back in to restart the process. Functionally this can be denoted as
 \begin{align*}
-\mathcal{L}(A) = M(D(L(F(G(A)))))
+	\mathcal{L}(A) = M(D(L(F(G(A))))),
 \end{align*}
-
-A solution such that $|\mathcal{L}(A)|^2 = |A|^2$ is sought.
-
-\section{Non-Dimensionalization}
-
-\begin{align*}
-T = T_M \widetilde{T}, \quad E = \Es \widetilde{E}, \quad A = \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}, \quad \omega = \frac{\widetilde{\omega}}{T_M}
-\end{align*}
-
-\begin{align*}
-G(A) &= \left( \frac{W_0 \left( a E e^{E}\right)}{E} \right)^{1/2} A.
-\end{align*}
-
-\begin{align*}
-D(A) &= \FTi{e^{i s^2 \omega^2} \FT{A}}
-\end{align*}
-
-\begin{align*}
-F(A) &= A e^{i b |A|^2},
-\end{align*}
-
-\begin{align*}
-L(A) &= h A,
-\end{align*}
-
-\begin{align*}
-M(A) &= e^{-T^2 / 2} A
-\end{align*}
-
-\begin{align*}
-a = e^{g_0 L_g} \quad s^2 = \frac{\beta_2 L_D}{2 T_M^2}, \quad b = \gamma L_F \frac{\Es}{T_M}, \quad h = C e^{-\alpha L}
-\end{align*}
+where $\mathcal{L}$ is one loop of the circuit. A solution to this model is one in which the 
+envelope is unchanged after traversing every component in the cavity, that is, such 
+that $|\mathcal{L}(A)| = |A|$.
 
 \section{Results}
+The model described is solved numerically and somewhat surprisingly, its convergence as a function
+of the characteristic parameter groups is highly complex.  To gain some insight into this process
+we consider an linear analysis that ignores the nonlinear fibre effects.
 
+\subsection{Linear Solution}
+Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge 
+to a Gaussian.  Consider an initial pulse with envelope
 \begin{align*}
-\left( \frac{W(a E e^E)}{E} \right)^{1/2} S(s) h = 1
+	|A_0| = \sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2},
 \end{align*}
+after passing through the gain and loss pieces, and neglecting the fibre nonlinearity, the envelope 
+will have the form
+\begin{align*}
+	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
+	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
+\end{align*}
+where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will 
+maintain its Gaussian shape, however, it will have spread. This can be represented as
+\begin{align}
+\label{linear1}
+	|A| = \sqrt{P} g(E) h \zeta(s, 0) \textrm{e}^{-T^2 / 2 \tilde{\sigma}^2}
+\end{align}
+where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. 
+Because the dispersive element conserves energy,
+\begin{align*}
+	\int_{-\infty}^{\infty} P g(E)^2 h^2 \textrm{e}^{-T^2 / \sigma^2} \, \df T = 
+	\int_{-\infty}^{\infty} P g(E)^2 h^2 \zeta^2(s, 0) \textrm{e}^{-T^2 / \widetilde{\sigma}^2} \, \df T,
+\end{align*}
+or more simply $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$.
+Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
+\begin{align*}
+	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} \right).
+\end{align*}
+Finally, the pulse is modulated and so that after one loop the total effect is given by
+\begin{align}
+\label{linear2}
+	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right).
+\end{align}
 
+In equilibrium the envelope of the pulse is unchanged after completing a full circuit, in other words,
 \begin{align*}
-E = \frac{S(s)^2 h^2}{1 - S(s)^2 h^2} \ln \left( a S(s)^2 h^2 \right)
+	\sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2} =  
+	\sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right),
+\end{align*}
+or more simply,
+\begin{align}
+\label{eq:energycond}
+	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta(s, 0) &= 1,&
+	-\frac{T^2}{2 \sigma^2} &= -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2}.
+\end{align}
+The second condition simplifies to
+\begin{align*}
+	\sigma = \sqrt{1 - \zeta^4(s, 0)}
+\end{align*}
+and the peak of the pulse can be found by integration to give
+\begin{align*}
+	P = \frac{E}{\sqrt{\pi} \sigma}.
+\end{align*}
+Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
+\begin{align*}
+	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
 \end{align*}
@@
 \centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-f(x) = m * x + c
-fit f(x) '../sdata.dat' u 1:(log($2)) via m, c
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 2}]
+# Constant power things
+Ps = 1
+f = 1
+g = 1
+a = 0.1
+f(x,y) = Ps / (sqrt(pi) * f) * (y / (2 * x))**(1/4) * (g / (sqrt(x * y / 2) + a) -1)
+
 set grid
-set ytics 0.1
-set xl '$s$'
-set yl 'Spread'
-plot '../sdata.dat' u 1:2 w p pt 7 ps 0.4 t 'Data', \
-exp(f(x)) t '$\exp(-0.521294s + 0.00365752)$'
+set xr [0:10]
+set yr [0:10]
+set xl '$\epsilon$'
+set yl '$|\beta_2|$'
+
+# Put contours in file
+set contour base  
+set cntrparam levels incremental 0, 0.1
+unset surface  
+set table 'curve.dat'
+set isosamples 1000
+splot f(x,y)  
+unset table
+
+# Plot everything
+p 2 / x t 'Constant Gain' lc 1 dt 5, \
+for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
+0 t 'Constant Duration' lc 4 dt 5, \
+for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 4 dt 5, \
+'curve.dat' w l t 'Constant Power' lw 2
+
 \end{gnuplot}
@@
 \begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-S(x) = exp(-0.5131 * x + 0.00174)
+f(x) = m * x + c
+fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
+set grid
+set ytics 0.1
+set xl '$s$'
+set yl '$\zeta(s, 0)$'
+set yr [0.75:1.05]
+plot '../Zeta.dat' u 1:2 w l t 'Data', \
+exp(f(x)) dt 4 t '$\exp(-0.511444s + 0.00174128)$'
+\end{gnuplot}
+\caption{}
+\label{fig:zeta}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+set grid
+set xl '$s$'
+set yl '$b$'
+set cbl 'Error'
+set xr [0:1.5]
+set view map
+
+set palette defined ( 0 '#D73027',\
+    	    	      1 '#F46D43',\
+		      2 '#FDAE61',\
+		      3 '#FEE090',\
+		      4 '#E0F3F8',\
+		      5 '#ABD9E9',\
+		      6 '#74ADD1',\
+7 '#4575B4' )
+
+set cbr [0:0.5]
+sp '../abig.dat' using 1:2:3 w image not
+\end{gnuplot}
+\caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 75) - A(\text{iteration } 74) \|_2}{\|A(\text{iteration } 74) \|_2}$}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+set grid
+set xl '$s$'
+set yl '$b$'
+set cbl 'Energy'
+set xr [0:1.5]
+set view map
+
+set palette defined ( 0 '#D73027',\
+    	    	      1 '#F46D43',\
+		      2 '#FDAE61',\
+		      3 '#FEE090',\
+		      4 '#E0F3F8',\
+		      5 '#ABD9E9',\
+		      6 '#74ADD1',\
+7 '#4575B4' )
+
+set cbr [0:0.25]
+sp '../abig.dat' using 1:2:4 w image not
+\end{gnuplot}
+\caption{}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+S(x) = exp(-0.511444 * x + 0.0017412)
 E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
@@
 set grid
-
 set pm3d map
-
 set isosamples 100, 100
 set hidden3d
-
 set contour surface
 set cntrparam levels incremental 0, 0.1, 1.5
+set palette rgbformulae 22, 13, -31
 
-set palette rgbformulae 22, 13, -31
+set palette defined ( 0 '#D73027',\
+    	    	      1 '#F46D43',\
+		      2 '#FDAE61',\
+		      3 '#FEE090',\
+		      4 '#E0F3F8',\
+		      5 '#ABD9E9',\
+		      6 '#74ADD1',\
+7 '#4575B4' )
 
@@
 set xr [0:0.5]
-set yr [0.3:0.6]
+set yr [0.25:0.6]
+set cbr [0:1.4]
 
@@
 splot E(x, y) not
-
 \end{gnuplot}
-\caption{a=30}
+\caption{Equation \eqref{eq:energycond} for $a = 30$}
 \label{fig:}
@@
 \begin{table}
+\begin{center}
 \begin{tabular}{|l|l|}
@@
 $\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
-$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \\
+$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
 $\Es$ & $10^4 \text{pJ}$ \\
-$L_G$ & $3 \text{m}$ \\
+$L_G$ & $2$--$3 \text{m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
 \hline
 \end{tabular}
+\caption{}
+\label{tab:values}
+\end{center}
 \end{table}

### 2018-10-09 Paper/laser2018.tex
Added Sean's additions

\documentclass[12pt,twoside,letterpaper]{article}

\usepackage{fancyhdr}
\usepackage{graphicx,epsfig,color,pstricks}
\usepackage{amsmath,esint}
\usepackage{latexsym,amssymb}
\usepackage{gensymb}
\usepackage{units}

%\usepackage[latin1]{inputenc}
%\usefonttheme{professionalfonts}
%\usepackage{times}
%\usepackage{tikz}
%\usepackage{amsmath, esint}

% sget page layout parameters (two sides)
\newlength{\defaultheadheight}
\setlength{\defaultheadheight}{\headheight}
\newlength{\defaultheadsep}
\setlength{\defaultheadsep}{\headsep}

% set page layout parameters (two sides)
\textwidth 7.0in
\textheight 9.75in
\hoffset -0.25in 
\voffset -0.75in
\topmargin 0in
\headheight \defaultheadheight
\headsep 0.16in
\footskip=0in
\oddsidemargin 0in 
\evensidemargin 0in %22pt default
%\evensidemargin 0.34in %22pt default
\raggedbottom

\DeclareMathOperator{\prob}{Prob}
\DeclareMathOperator{\pv}{PV}
\DeclareMathOperator{\sech}{sech}
\DeclareMathOperator{\sgn}{sgn}

%differentiation
\makeatletter
\providecommand*{\diff}%
    {\@ifnextchar^{\DIfF}{\DIfF^{}}}
\def\DIfF^#1{%
    \mathop{\mathrm{\mathstrut d}}%
        \nolimits^{#1}\gobblespace}
\def\gobblespace{%
    \futurelet\diffarg\opspace}
\def\opspace{%
    \let\DiffSpace\!%
    \ifx\diffarg(%
        \let\DiffSpace\relax
    \else
        \ifx\diffarg[%
            \let\DiffSpace\relax
    \else
        \ifx\diffarg\{%
            \let\DiffSpace\relax
        \fi\fi\fi\DiffSpace}

\providecommand*{\deriv}[3][]{%                   % \deriv[]{u}{x}
   \frac{\diff^{#1}#2}{\diff #3^{#1}}}
%\providecommand*{\deriv}[3][]{\frac{\diff^{#1}}{\diff #3^{#1}}#2}
\providecommand*{\pd}[3][]{\frac{\partial^{#1}#2}{\partial #3^{#1}}}
\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
\providecommand{\littleO}[1]{\ensuremath{\mathop{}\mathopen{}o\mathopen{}\left(#1\right)}}

% Special code to use the double bracket without loading the whole stmry package
\DeclareSymbolFont{stmry}{U}{stmry}{m}{n}
\SetSymbolFont{stmry}{bold}{U}{stmry}{b}{n}
\DeclareMathDelimiter\llbracket{\mathopen}{stmry}{"4A}{stmry}{"71}
\DeclareMathDelimiter\rrbracket{\mathclose}{stmry}{"4B}{stmry}{"79}

\begin{document}

\newcounter{mychapter}
\setcounter{mychapter}{1}
\renewcommand{\labelenumi}{\textbf{\arabic{mychapter}.\arabic{enumi}}}

\pagenumbering{arabic}
%\setcounter{page}{1}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\headrulewidth}{0.1pt}

\fancyhead[L]{\textbf{Tunable Lasers}: Dr. C. Sean Bohun}
\fancyhead[R]{Brady -- 2018 \ Page \thepage}

The model for the amplitude in the `average' model is given by
\begin{equation}
\label{average}
	\pd{A}{z} = -i\frac{\beta_2}{2}\pd[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
\end{equation}
with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the
modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
The ansatz for the amplitude is a function of the form
\begin{equation}
\label{ansatz}
	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
\end{equation}
so that the modulus $|A|$ and the phase $A/|A|$ are given by
\begin{align*}
	\left|A\right| &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)^{1/2}
	\exp\left(-\frac{\delta \Omega^2 T^2}{2(1 + C^2)}\right),&
	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
\end{align*}
The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where
$2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$
is the accumulated phase, and $\delta\Omega^2$ is the spectral half-width of $|A|^2$ 
since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}}
f(t)\textrm{e}^{i\omega t}\,\diff t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
\[
	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{\infty}^\infty A(t,z) \textrm{e}^{i\omega t}\, \diff t
	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
\]
and $|\hat{A}|^2(\delta\Omega,z) = \textrm{e}^{-1}|\hat{A}|^2(0,z)$.  The corresponding half-width of the
pulse duration comes from the expression for $|A|$ and gives
\begin{equation}
\label{duration}
	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
\end{equation}

In the case of the expression~(\ref{average}), applying~(\ref{ansatz}) gives the condition
\begin{align*}
	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right)-\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
\end{align*}
This gives four conditions by utilizing that $\psi\in\mathbb{R}$.  In detail,
\begin{align*}
	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
\end{align*}
Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that 
$\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$. 
From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, 
$\beta_2 C = |\beta_2|$ and $\epsilon > 0$.  We also see that the representation~(\ref{ansatz})
as a classical solution of~(\ref{average}) imposes a subclass of solutions whereby 
$g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.  One is left with a two parameter family of solutions
to~(\ref{ansatz}) with
\begin{align*}
	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2},&
	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.&
\end{align*}
Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.  In practice however, 
at high power levels the gain drops as the fibre saturates.  One can model this with
\begin{equation}
\label{newg}
	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
\end{equation}
where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity.
The power in the fibre depends on the frequency $f$ and modulus of the pulse so that
\begin{align*}
	f \int_{-\infty}^\infty |A(s)|^2\,\diff s &=
	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 = \Delta P_0, &
	\Delta &= \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}
\end{align*}
where $\Delta$ is the duty cycle of the pulse.  Denoting the saturation power as 
$P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
\[
	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f}  \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
\]

\end{document}

### 2018-10-09 Lasers.py

@@ -4,46 +4,49 @@ import matplotlib.pyplot as plt
 import time
 
 def Energy(A, dx):
-	return np.real(np.sum(A * np.conj(A)) * dx)
+	return np.trapz(np.real(A * np.conj(A)), dx = dx)
+
+def zeta(s):
+	return np.exp(-0.511444 * s + 0.00174128)
+
+def EE(a, s, h):
+	r = zeta(s)**2 * h**2
+	return r / (1 - r) * np.log(a * r)
 
 # Functions for each component
 def Gain(A, E, a = 30):
-	if E < 20:
-		return np.sqrt(W(a * E * np.exp(E)) / E) * A
-	else:
-		# For large E python has overflow problems, but this approximation can be used instead
-		return np.sqrt((E + np.log(a)) / E) * A
+	return np.real(np.sqrt(W(a * E * np.exp(E)) / E)) * A
 
-def Loss(A, h = 0.1):
+def Loss(A, h = 0.4):
 	return h * A
 
-def Mod(A, T, nu = 1, mu = 1):
+def Mod(A, T):
 	return np.exp(-T**2 / 2) * A
-	#return 1.0 / 2.0 * (1 - nu * np.cos(mu * np.pi * np.exp(-T**2))) * A
-	#return 1.0 / 2.0 * (np.cos(np.pi * T) + 1) * (T < 1) * (T > -1) * A
 
-def Fibre(A, f = 10):
-	return np.exp(1j * f * A * np.conj(A)) * A
+def Fibre(A, b = 0.1):
+	return np.exp(1j * b * np.real(np.abs(A)**2)) * A
 
 def Disp(A, T, s = 0.1):
 	F = np.fft.fft(A)
+	F = (np.abs(F) > 10**-4) * F
 	dw = np.pi / T[-1]
 	w = np.fft.fftfreq(len(A)) * len(A) * dw
-	return np.fft.ifft(F * np.exp(1j * w**2 * s**2))
+	return np.fft.ifft(F * np.exp(1j * (w**2 * s**2 - 0 * s**2 * w**3)))
 
 # 1 round trip
-def Loop(A, T, dx, s):
-	#A = Gain(A, Energy(A, dx))
-	#A = Fibre(A, 0)
-	#A = Loss(A, 0.5)
+def Loop(A0, T, dx, s, b):
+	A = A0
+	A = Gain(A0, Energy(A0, dx))
+	A = Fibre(A, b)
+	A = Loss(A, 0.6)
[…]

### 2018-10-10 Paper/Paper.tex
Cleaned up tex file

@@
 %\usepackage{wrapfig}
-%\usepackage{subcaption}
+\usepackage{subcaption}
 \usepackage{hyperref}
@@
 
-%Impetutus: Want every student to have at least one experiential learning opportunity by the time they graduate.
-%Stake from province: 780K received to do this
-%
-%Examples of experiential learning:
-%industry or community agency sponsored research projects
-%interactive simulations
-%capstone projects
-%on-campus work/teaching labs
-%performance based learning
-%
-%Checkmark 1: Student is in a workplace or a simulated workplace.
-%This could be a lab or a workstation.  Use of industry standard software.  Case study application.
-%Field trips provided that it meets all of the criteria.
-%
-%Checkmark 2: Student is exposed to authentic demands that improve employability.
-%Initiative, communication, conflict resolution, making them use their own initiative to solve
-%problems that may arise.
-%
-%Checkmark 3: Experience is structured, with purposeful and meaningful activities.
-%Planning, supervision, guidance, check-in.  There is resource from Reyerson that helps break this down
-%This is not just photocopying or filing.
-%
-%Checkmark 4: Student applies program knowledge.
-%Relevance to course learning and encourage students to be flexible.
-%
-%Checkmark 5: Experience includes self-evaluation and assessment of learning outcomes.
-%This is a typical stumbling block and requires that the student is reflective on what was learned and
-%how this applies to future learning.  Assessment of the student's work is tied to to the learning outcomes.
-%Student's need to be introduced to meaningful reflection.
-%
-%Checkmark 6: Experience includes formal recognition.
-%Recognition has to acknowledge the experience meets the previous five criteria.
-%
-% HIGH LEVEL IDEAS:
-%Case studies - partnership with a pharmaceutical firm to develop in-office posters to explain how a 
-%drug works for use by a physician. (Check out RIIPEN website)
-%Field trips - design and incorporate activity, conceptualization, and reflection.  A tour of an R&D facility.
-%Hackathons - Student-led intensive sessions to solve real-world problems.  Interdisciplinary teams
-%to create ideas for a community healthcare initiative.
-%
-%
-%
-%Promoting a tapestry of science.
-
 \title{}
@@
 \noindent
-To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review 
-of the efforts to describe an `average' model.  The idea is to capture some of the physical the elements 
-in the waveform (dispersion, modulation and gain/loss) described by an effective PDE, the solution of
-which gives the amplitude of the wave packet.
+To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
+The idea is to capture some of the physical the elements in the waveform (dispersion, modulation and gain/loss) described by an effective PDE, the solution of which gives the amplitude of the wave packet.
 
 \section{Average Model}
-
 The model for the amplitude in the `average' model is presupposed to have the form
@@
 \end{equation}
-where $A=A(T,z)$ is the complex amplitude of the pulse
-with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the
-modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.  Expression~(\ref{average}) is reminiscent of the 
-nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
+where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
+Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
 Consequently, the ansatz for the amplitude is taken to be a function of the form
@@
 \end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where
-$2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$
-is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ 
-since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}}
-f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
+The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where $2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
 \[
@@
 \]
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$.  The corresponding half-width of the
-pulse duration comes from the expression for $|A|$ and gives
+and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|$ and gives
 \begin{equation}
@@
 \end{align*}
-Treating this condition as a complex valued quadratic in $T$ gives four conditions.  Assuming that $\psi\in\mathbb{R}$,
-the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
+Treating this condition as a complex valued quadratic in $T$ gives four conditions. Assuming that $\psi\in\mathbb{R}$, the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
 \begin{align*}
@@
 \end{align*}
-Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that 
-$\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$. 
-From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, 
-$\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).  
-The result is a two parameter family of solutions
-of the form~(\ref{ansatz}) with
+Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that $\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$.
+From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, $\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).
+The result is a two parameter family of solutions of the form~(\ref{ansatz}) with
 \begin{align*}
@@
 \end{align*}
-Moreover, we also see that the representation~(\ref{ansatz})
-as a classical solution of~(\ref{average}) imposes a subclass of solutions with 
-$g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.  
+Moreover, we also see that the representation~(\ref{ansatz}) as a classical solution of~(\ref{average}) imposes a subclass of solutions with $g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.
 A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
@@
 
-Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.  In practice, 
-at high power levels, the gain drops as the fibre saturates.  One can model this with a gain term that
-takes the form
+Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
+In practice, at high power levels, the gain drops as the fibre saturates.
+One can model this with a gain term that takes the form
 \begin{equation}
@@
 \end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity.
-The power in the fibre depends on the frequency $f$ and modulus of the pulse so that
+where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency $f$ and modulus of the pulse so that
 \begin{align*}
@@
 \end{align*}
-where $\Delta$ is the duty cycle of the pulse.  Denoting the saturation power as 
-$P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
+where $\Delta$ is the duty cycle of the pulse. Denoting the saturation power as $P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
 \[
@@
 
+\begin{figure}[htbp]
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 2}]
+# Constant power things
+Ps = 1
+f = 1
+g = 1
+a = 0.1
+f(x,y) = Ps / (sqrt(pi) * f) * (y / (2 * x))**(1/4) * (g / (sqrt(x * y / 2) + a) -1)
+
+set grid
+set xr [0:10]
+set yr [0:10]
+set xl '$\epsilon$'
+set yl '$|\beta_2|$'
+
+# Put contours in file
+set contour base 
+set cntrparam levels incremental 0, 0.1
+unset surface 
+set table 'curve.dat'
+set isosamples 1000
+splot f(x,y) 
+unset table
+
+# Plot everything
+p 2 / x t 'Constant Gain' lc 1 dt 5, \
+for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
+0 t 'Constant Duration' lc 4 dt 5, \
+for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 4 dt 5, \
+'curve.dat' w l t 'Constant Power' lw 2
+
+\end{gnuplot}
+\caption{}
+\label{fig:average}
+\end{figure}
+
 Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$ correspond to constant gain while
-the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
-Curves of constant power level are also indicated.  One of the main drawbacks of this model is 
-the fixed chirp and its symmetric behaviour with respect to $T$.  One way to alleviate some of these
-restrictions is to construct a discrete model whereby each of the modules in the tuneable laser
-are given by a transfer function that is motivated by the PDE~(\ref{average}).  In particular, the
-dispersion and the modulation would correspond to transfer functions of the form
+The representative hyperbola, $\epsilon|\beta_2| = 2g^2$ correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
+Curves of constant power level are also indicated.
+One of the main drawbacks of this model is the fixed chirp and its symmetric behaviour with respect to $T$.
+One way to alleviate some of these restrictions is to construct a discrete model whereby each of the modules in the tuneable laser are given by a transfer function that is motivated by the PDE~(\ref{average}).
+In particular, the dispersion and the modulation would correspond to transfer functions of the form
 \begin{align}
@@
 \end{align}
-respectively where the dispersion is naturally defined in the frequency domain.  Between the modules, 
-the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent
-with the transfer functions.  Details of this technique and its ability of predict a number of experimental
-effects can be found in~\cite{burgoyne2014}.
+respectively where the dispersion is naturally defined in the frequency domain.
+Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
+Details of this technique and its ability of predict a number of experimental effects can be found in~\cite{burgoyne2014}.
 
 \section{A New Model}
-Rather than using a transfer function with a linear PDE, we instead return to generalized nonlinear 
-Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
+Rather than using a transfer function with a linear PDE, we instead return to generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
 \begin{align}
@@
 \end{align}
-to represent the waveform.  In this expression, $\beta_3$ is the third order dispersion coefficient, 
-$\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
-Using this expression as a starting point, the laser cavity is assumed to be composed of five independent 
-processes---gain, nonlinearity, loss, dispersion, and modulation. 
-Within each component of the laser cavity the other four process are assumed to be negligible, that is, 
-each process is dominant only within one part of the laser, just as with the discrete model, but embracing
-any nonlinearities.
+to represent the waveform.
+In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
+Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
+Within each component of the laser cavity the other four process are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
 
 \subsection{Gain}
-Considering the gain term as dominant as is expected with the 
-the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
+Considering the gain term as dominant as is expected with the the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
 \begin{align}
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the 
-pulse~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina} and $\Es$ is the energy at which the gain 
-begins to saturate.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina} and $\Es$ is the energy at which the gain begins to saturate.
 %We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
@@
 For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form, integrate~(\ref{diffez}) over a gain fibre of length $z$ and assume the energy
-increases from $E$ to $E_{\textrm{out}}$ so that
+To obtain a closed form, integrate~(\ref{diffez}) over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
 \[
@@
 \end{align}
-with the desired property that $E_{\textrm{out}}(0)=E$.  Since $E \sim |A|^2$, the gain in terms of 
-the amplitude is given by
+with the desired property that $E_{\textrm{out}}(0)=E$. Since $E \sim |A|^2$, the gain in terms of the amplitude is given by
 \begin{align}
@@
 \subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$.  In regions where this effect is dominant 
-expression~\eqref{eq:nlse} gives
+The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this effect is dominant expression~\eqref{eq:nlse} gives
 \begin{align}
@@
 so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives 
-$\varphi(T,z) = \gamma |A|^2 z$. For a fibre of length $L_f$ the effect of the nonlinearity is therefore
+Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives $\varphi(T,z) = \gamma |A|^2 z$.
+For a fibre of length $L_f$ the effect of the nonlinearity is therefore
 \begin{align}
@@
 \subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss 
-due to absorption and scattering. Combining these two effect gives a loss that takes the form
+Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
+Combining these two effect gives a loss that takes the form
 \begin{align}
@@
 \subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).  In comparision,
-the dispersion due to the fibre is negligible.\footnote{A $10$ cm chirped grating can provide as much dispersion 
-as $300$ km of fibre~\cite{agrawal2002}.} The dispersive terms of \eqref{eq:nlse} give
+Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
+In comparison, the dispersion due to the fibre is negligible.\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.} The dispersive terms of \eqref{eq:nlse} give
 \begin{align}
@@
 \end{align}
-and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform 
-of~\eqref{eq:disp}, giving the result that
+and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
 \begin{align*}
@@
 For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model, the third order effect will be neglected so we set $\beta_3=0$ for 
-the subsequent analysis~\cite{agrawal2013, ferreira}.
+However, for simplicity in the basic model, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
 
 \subsection{Modulation}
-In the average model the amount of modulation is characterized by the parameter $\epsilon$ through
-the term $\frac{\epsilon}{2}T^2 A$.  In the new model, the modulation is considered to be applied
-externally through its action on the spectrum and for simplicity the representation is taken as a
-Gaussian pulse  
+In the average model the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
+In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as a Gaussian pulse
 \begin{align}
@@
 \end{align}
-where $T_M$ is a characteristic width of the modulation.\footnote{Taking the Fourier transform, 
-$\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
+where $T_M$ is a characteristic width of the modulation.\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
 
@@
 \subsection{Combining the Pieces}
-In this model the pulse is iteratively passed through each process, the order of which is now
-important.  In this first realization, the pulse is first
-amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity 
-needs to be considered. The pulse is then tapped off by the output coupler, and then passes 
-through the grating and is modulated. The pulse after one complete circuit of the laser 
-cavity is then passed back in to restart the process. Functionally this can be denoted as
+In this model the pulse is iteratively passed through each process, the order of which is now important.
+In this first realization, the pulse is first amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity needs to be considered.
+The pulse is then tapped off by the output coupler, and then passes through the grating and is modulated.
+The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
+Functionally this can be denoted as
 \begin{align*}
@@
 \end{align*}
-where $\mathcal{L}$ is one loop of the circuit. A solution to this model is one in which the 
-envelope is unchanged after traversing every component in the cavity, that is, such 
-that $|\mathcal{L}(A)| = |A|$.
+where $\mathcal{L}$ is one loop of the circuit.
+A solution to this model is one in which the envelope is unchanged after traversing every component in the cavity, that is, such that $|\mathcal{L}(A)| = |A|$.
 
 \section{Results}
-The model described is solved numerically and somewhat surprisingly, its convergence as a function
-of the characteristic parameter groups is highly complex.  To gain some insight into this process
-we consider an linear analysis that ignores the nonlinear fibre effects.
+The model described is solved numerically and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
+To gain some insight into this process we consider an linear analysis that ignores the nonlinear fibre effects.
 
 \subsection{Linear Solution}
-Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge 
-to a Gaussian.  Consider an initial pulse with envelope
+Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge to a Gaussian. Consider an initial pulse with envelope
 \begin{align*}
@@
 \end{align*}
-after passing through the gain and loss pieces, and neglecting the fibre nonlinearity, the envelope 
-will have the form
+after passing through the gain and loss pieces, and neglecting the fibre nonlinearity, the envelope will have the form
 \begin{align*}
@@
 \end{align*}
-where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will 
-maintain its Gaussian shape, however, it will have spread. This can be represented as
+where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread. This can be represented as
 \begin{align}
@@
 \end{align}
-where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. 
-Because the dispersive element conserves energy,
+where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. Because the dispersive element conserves energy,
 \begin{align*}
@@
 \end{align*}
-or more simply $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$.
-Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
+or more simply $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
 \begin{align*}
@@
 \centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 2}]
-# Constant power things
-Ps = 1
-f = 1
-g = 1
-a = 0.1
-f(x,y) = Ps / (sqrt(pi) * f) * (y / (2 * x))**(1/4) * (g / (sqrt(x * y / 2) + a) -1)
-
-set grid
-set xr [0:10]
-set yr [0:10]
-set xl '$\epsilon$'
-set yl '$|\beta_2|$'
-
-# Put contours in file
-set contour base  
-set cntrparam levels incremental 0, 0.1
-unset surface  
-set table 'curve.dat'
-set isosamples 1000
-splot f(x,y)  
-unset table
-
-# Plot everything
-p 2 / x t 'Constant Gain' lc 1 dt 5, \
-for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
-0 t 'Constant Duration' lc 4 dt 5, \
-for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 4 dt 5, \
-'curve.dat' w l t 'Constant Power' lw 2
-
-\end{gnuplot}
-\caption{}
-\label{fig:}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
 \begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
@@
 \centering
+\begin{subfigure}[]{\textwidth}
 \begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
@@
 set cbl 'Error'
-set xr [0:1.5]
+set xr [0:1]
 set view map
 
-set palette defined ( 0 '#D73027',\
-    	    	      1 '#F46D43',\
-		      2 '#FDAE61',\
-		      3 '#FEE090',\
-		      4 '#E0F3F8',\
-		      5 '#ABD9E9',\
-		      6 '#74ADD1',\
-7 '#4575B4' )
+load '/home/brady/Templates/YGB.p'
 
-set cbr [0:0.5]
-sp '../abig.dat' using 1:2:3 w image not
+set cbr [0:0.75]
+sp '../On.dat' using 1:2:3 w image not
 \end{gnuplot}
+\caption{}
+\label{fig:}
+\end{subfigure}
+\begin{subfigure}[]{\textwidth}
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+set grid
+set xl '$s$'
+set yl '$b$'
+set cbl 'Error'
+set xr [0:0.2]
+set view map
+
+load '/home/brady/Templates/YGB.p'
+
+set cbr [0:0.75]
+sp '../Zoom01.dat' using 1:2:3 w image not
+\end{gnuplot}
+\caption{}
+\end{subfigure}
 \caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 75) - A(\text{iteration } 74) \|_2}{\|A(\text{iteration } 74) \|_2}$}
@@
 \begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Energy'
-set xr [0:1.5]
-set view map
-
-set palette defined ( 0 '#D73027',\
-    	    	      1 '#F46D43',\
-		      2 '#FDAE61',\
-		      3 '#FEE090',\
-		      4 '#E0F3F8',\
-		      5 '#ABD9E9',\
-		      6 '#74ADD1',\
-7 '#4575B4' )
-
-set cbr [0:0.25]
-sp '../abig.dat' using 1:2:4 w image not
-\end{gnuplot}
-\caption{}
-\label{fig:}
-\end{figure}
-
-\begin{figure}[htbp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+load '/home/brady/Templates/YGB.p'
 S(x) = exp(-0.511444 * x + 0.0017412)
@@
 set cntrparam levels incremental 0, 0.1, 1.5
-set palette rgbformulae 22, 13, -31
-
-set palette defined ( 0 '#D73027',\
-    	    	      1 '#F46D43',\
-		      2 '#FDAE61',\
-		      3 '#FEE090',\
-		      4 '#E0F3F8',\
-		      5 '#ABD9E9',\
-		      6 '#74ADD1',\
-7 '#4575B4' )
 

### 2018-10-10 Paper/Paper.tex
Fixed typos

@@
 %\usepackage{enumitem}
-%\usepackage{wrapfig}
+\usepackage{wrapfig}
 \usepackage{subcaption}
@@
 Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
-Details of this technique and its ability of predict a number of experimental effects can be found in~\cite{burgoyne2014}.
+Details of this technique and its ability to predict a number of experimental effects can be found in~\cite{burgoyne2014}.
 
 \section{A New Model}
-Rather than using a transfer function with a linear PDE, we instead return to generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
+Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
 \begin{align}
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina} and $\Es$ is the energy at which the gain begins to saturate.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}.
 %We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
@@
 For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form, integrate~(\ref{diffez}) over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
+To obtain a closed form solution, integrate~(\ref{diffez}) over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
 \[
@@
 Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
-In comparison, the dispersion due to the fibre is negligible.\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.} The dispersive terms of \eqref{eq:nlse} give
+In comparison, the dispersion due to the fibre is negligible\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.}.
+The dispersive terms of \eqref{eq:nlse} give
 \begin{align}
@@
 \begin{align*}
-	\pdiff{\FT{A}}{z} &= i\frac{\omega^2}{2}\left(\beta_2 + \frac{\beta_3}{3} \omega\right) \FT{A}.
+	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\left(\beta_2 - \frac{\beta_3}{3} \omega\right) \FT{A}.
 \end{align*}
@@
 \label{eq:dispersion}
-	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 + \beta_3 \omega/3)/2} \FT{A}}.
+	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
 \end{align}
@@
 \subsection{Non-Dimensionalization}
+
+\begin{wraptable}{r}{0.45\textwidth}
+\begin{center}
+\begin{tabular}{|l|l|}
+\hline
+Parameter & Value \\
+\hline
+$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \\
+$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
+$\beta_2^f$ & $20$--$50 \text{ ps}^2/ \text{km}$ \\
+$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
+$\Es$ & $10^4 \text{ pJ}$ \\
+$L_G$ & $2$--$3 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
+\hline
+\end{tabular}
+\caption{Orders of magnitude of various parameters.}
+\label{tab:values}
+\end{center}
+\end{wraptable}
+
 The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
@@
 	G(A) &= \left(E^{-1} W_0 \left( a E e^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2},&
-	L(A) &= h A,\\
+	F(A) &= A \textrm{e}^{i b |A|^2}, \\
+	L(A) &= h A,&
 	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
@@
 The model described is solved numerically and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we consider an linear analysis that ignores the nonlinear fibre effects.
+To gain some insight into this process we consider a linear analysis that ignores the nonlinear fibre effects.
 
 \subsection{Linear Solution}
+\begin{wrapfigure}{r}{0.45\textwidth}
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
+f(x) = m * x + c
+fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
+set grid
+set ytics 0.1
+set xl '$s$'
+set yl '$\zeta(s, 0)$'
+set yr [0.75:1.05]
+plot '../Zeta.dat' u 1:2 w l t 'Data', \
+exp(f(x)) dt 4 t 'Fit'
+\end{gnuplot}
+\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
+\label{fig:zeta}
+\end{wrapfigure}
+
 Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge to a Gaussian. Consider an initial pulse with envelope
@@
 \end{align*}
-after passing through the gain and loss pieces, and neglecting the fibre nonlinearity, the envelope will have the form
+after passing through the gain and loss pieces, and having neglected the fibre nonlinearity, the envelope will have the form
 \begin{align*}
-	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
+	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2}, \\
 	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
@@
 \end{align}
-where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. Because the dispersive element conserves energy,
+where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. However, since dispersion conserves energy
 \begin{align*}
@@
 \end{align*}
-or more simply $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
+which reduces to $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
 \begin{align*}
@@
 \end{align*}
-or more simply,
+or more explicitly,
 \begin{align}
@@
 \end{align*}
-
-\begin{figure}[htbp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-f(x) = m * x + c
-fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
-set grid
-set ytics 0.1
-set xl '$s$'
-set yl '$\zeta(s, 0)$'
-set yr [0.75:1.05]
-plot '../Zeta.dat' u 1:2 w l t 'Data', \
-exp(f(x)) dt 4 t '$\exp(-0.511444s + 0.00174128)$'
-\end{gnuplot}
-\caption{}
-\label{fig:zeta}
-\end{figure}
 
@@
 \end{subfigure}
-\caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 75) - A(\text{iteration } 74) \|_2}{\|A(\text{iteration } 74) \|_2}$}
+\caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 25) - A(\text{iteration } 24) \|_2}{\|A(\text{iteration } 24) \|_2}$}
 \label{fig:}
@@
 
-\begin{figure}[htbp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-load '/home/brady/Templates/YGB.p'
-S(x) = exp(-0.511444 * x + 0.0017412)
-E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
-a = 30
-
-set grid
-set pm3d map
-set isosamples 100, 100
-set hidden3d
-set contour surface
-set cntrparam levels incremental 0, 0.1, 1.5
-
-set ytics 0.1
-set xl '$s$'
-set yl rotate by 0 '$h$'
-set cbl rotate by 0 '$E$'
-set xr [0:0.5]
-set yr [0.25:0.6]
-set cbr [0:1.4]
-
-unset clabel
-
-splot E(x, y) not
-\end{gnuplot}
-\caption{Equation \eqref{eq:energycond} for $a = 30$}
-\label{fig:}
-\end{figure}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\beta_2^g L_D$ & $10$--$2000 \text{ps}^2$ \\
-$g_0$ & $1$--$10 \text{m}^{-1}$ \\
-$\beta_2^f$ & $20$--$50 \text{ps}^2/ \text{km}$ \\
-$\gamma$ & $0.001$--$0.01 \text{W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$\Es$ & $10^4 \text{pJ}$ \\
-$L_G$ & $2$--$3 \text{m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-\hline
-\end{tabular}
-\caption{}
-\label{tab:values}
-\end{center}
-\end{table}
+%\begin{figure}[htbp]
+%\centering
+%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+%load '/home/brady/Templates/YGB.p'
+%S(x) = exp(-0.511444 * x + 0.0017412)
+%E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
+%a = 30
+%
+%set grid
+%set pm3d map
+%set isosamples 100, 100
+%set hidden3d
+%set contour surface
+%set cntrparam levels incremental 0, 0.1, 1.5
+%
+%set ytics 0.1
+%set xl '$s$'
+%set yl rotate by 0 '$h$'
+%set cbl rotate by 0 '$E$'
+%set xr [0:0.5]
+%set yr [0.25:0.6]
+%set cbr [0:1.4]
+%
+%unset clabel
+%
+%splot E(x, y) not
+%\end{gnuplot}
+%\caption{Equation \eqref{eq:energycond} for $a = 30$}
+%\label{fig:}
+%\end{figure}
 

### 2018-10-13 Paper/Envelopes.tex
Finished draft

\begin{figure}[htbp]
\centering
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,3in lw 3}]
set grid
set key above
set xr [-2:2]
set yr [-0.75:0.75]
set xl '$T$'
set xtics 1

unset key
set multiplot layout 1, 2

set size 0.5, 1
p '../Stable/Envelope8.dat' u 1:4 w l t 'Magnitude', \
 '../Stable/Envelope8.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Stable/Envelope8.dat' u 1:3 w l dt 4 t 'Imaginary'

set size 0.5, 1
p '../Stable/Envelope15.dat' u 1:4 w l t 'Magnitude', \
 '../Stable/Envelope15.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Stable/Envelope15.dat' u 1:3 w l dt 4 t 'Imaginary'

set key at 0, 0.8
unset ytics
unset xtics
unset border
unset xl
set size 1, 0.1
set yr [0:0.01]

p 2 t 'Magnitude', \
2 dt 5 lc 7 t 'Real', \
2 dt 4 t 'Imaginary'
\end{gnuplot}
\caption{Wave is stable for $b = 1.5$.}
\label{fig:stable}
\end{subfigure} \\
\vspace{4mm}
\begin{subfigure}[]{\textwidth}
\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,3in lw 3}]
set grid
set key above
set xr [-2:2]
set yr [-0.75:0.75]
set xl '$T$'
set xtics 1

unset key
set multiplot layout 1, 2

set size 0.5, 1
p '../Break/Envelope8.dat' u 1:4 w l t 'Magnitude', \
 '../Break/Envelope8.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Break/Envelope8.dat' u 1:3 w l dt 4 t 'Imaginary'

set size 0.5, 1
p '../Break/Envelope15.dat' u 1:4 w l t 'Magnitude', \
 '../Break/Envelope15.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
'../Break/Envelope15.dat' u 1:3 w l dt 4 t 'Imaginary'

set key at 0, 0.8
unset ytics
unset xtics
unset border
unset xl
set size 1, 0.1
set yr [0:0.01]
p 2 t 'Magnitude', \
2 dt 5 lc 7 t 'Real', \
2 dt 4 t 'Imaginary'

\end{gnuplot}
\caption{Wave breaks for $b = 1.4$.}
\label{fig:break}
\end{subfigure}
\caption{Simulation with $s = 0.11$, $a = 30$, $h = 0.6$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$. \textbf{Left:} Pulse after 8 iterations. \textbf{Right:} Pulse after 15 iterations.}
\label{fig:envelope}
\end{figure}

### 2018-10-13 Paper/Paper.tex
Finished draft

@@
 \DeclareMathOperator{\sgn}{sgn}
+\DeclareMathOperator{\sech}{sech}
 
@@
 To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical the elements in the waveform (dispersion, modulation and gain/loss) described by an effective PDE, the solution of which gives the amplitude of the wave packet.
+The idea is to capture some of the physical elements in the waveform (dispersion, modulation, and gain/loss) described by an effective PDE, the solution of which gives the amplitude of the wave packet.
 
@@
 for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
-0 t 'Constant Duration' lc 4 dt 5, \
-for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 4 dt 5, \
-'curve.dat' w l t 'Constant Power' lw 2
+0 t 'Constant Duration' lc 7 dt 4, \
+for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 7 dt 4, \
+'curve.dat' w l t 'Constant Power' lw 2 lc 3
 
@@
 Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
-Combining these two effect gives a loss that takes the form
+Combining these two effects give a loss that takes the form
 \begin{align}
@@
 \end{align*}
-The affect of dispersion is then
+The effect of dispersion is then
 \begin{align}
@@
 \subsection{Modulation}
-In the average model the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
+In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
 In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as a Gaussian pulse
@@
 	a &= \textrm{e}^{g_0 L_g} \sim 30,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.1,&
-	b &= \gamma L_F \frac{\Es}{T_M} \sim 0.1,& h &= C \textrm{e}^{-\alpha L} \sim 0.25,
+	b &= \gamma L_F \frac{\Es}{T_M} \sim 0.1,& h &= C \textrm{e}^{-\alpha L} \sim 0.6,
 \end{align*}
@@
 \section{Results}
-The model described is solved numerically and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we consider a linear analysis that ignores the nonlinear fibre effects.
-
-\subsection{Linear Solution}
 \begin{wrapfigure}{r}{0.45\textwidth}
@@
 \end{wrapfigure}
+The model described is solved numerically and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
+To gain some insight into this process we consider a linear analysis that ignores the nonlinear fibre effects.
+
+\subsection{Linear Solution}
+
+% gnuplot code for the four waveforms
+\input{Envelopes}
 
@@
 \begin{align*}
-	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2}, \\
+	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
 	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
@@
 
-In equilibrium the envelope of the pulse is unchanged after completing a full circuit, in other words,
+In equilibrium, the envelope of the pulse is unchanged after completing a full circuit, in other words,
 \begin{align*}
@@
 Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
+\begin{align}
+	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
+	\label{eq:equilenergy}
+\end{align}
+
+\subsection{Nonlinear Solution}
+In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
+However, this is not necessarily the case with the inclusion of the nonlinearity.
+The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations because of the Fourier transform which then reinforces the oscillations.
+These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
+\\
+
+Figure \ref{fig:stable} shows that small oscillations in the envelope can become smoothed out leading to a Gaussian-esque waveform.
+Conversely, Figure \ref{fig:break} shows how the waveform evolves for a slightly different $b$ value.
+Notice the oscillations are more pronounced, this effect compounds resulting in the wave breaking.
+\\
+
+The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
+Note that in Figure \ref{fig:envelope} the wave breaks for the smaller of the two $b$ values.
+This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
 \begin{align*}
-	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
+\frac{\|A(\text{iteration } 25) - A(\text{iteration } 24) \|_2}{\|A(\text{iteration } 24) \|_2}.
 \end{align*}
+In the region $0.35 < s < 0.6$ the wave does not break regardless of $b$.
+This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
 
@@
 
-load '/home/brady/Templates/YGB.p'
+load '/home/brady/Templates/Blues.p'
 
 set cbr [0:0.75]
-sp '../On.dat' using 1:2:3 w image not
+sp '../30-06-01-DM.dat' using 1:2:3 w image not
+%'../ProductContours.dat' w l lc 'black' not
+\end{gnuplot}
+\caption{}
+\label{fig:DMZ}
+\end{subfigure}
+\begin{subfigure}[]{\textwidth}
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+set grid
+set xl '$s$'
+set yl '$b$'
+set cbl 'Error'
+set xr [0:0.2]
+set view map
+
+load '/home/brady/Templates/Blues.p'
+
+set cbr [0:0.75]
+
+set cntrlabel start 1
+
+sp '../30-06-01-DM-Z.dat' using 1:2:3 w image not
+#'contours.dat' u ($1 / 2500):($2 / 250):($2 / 250 < 10 * $1 / 2500 + 0.17 ? 1 : 1/0) w l lc 'black' not
+\end{gnuplot}
+\caption{}
+\label{fig:DM}
+\end{subfigure}
+\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 30$, $h = 0.6$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.}
+\label{fig:DMmap}
+\end{figure}
+
+\subsubsection{Ordering}
+Since some of the individual mappings are nonlinear they do not commute---thus changing the order of the components should lead to different results.
+The nonlinearity should still follow the gain component since that is where it is most dominant.
+Furthermore, the loss is a linear mapping and so it will commute with both dispersion and modulation.
+Therefore, the only other unique case to consider is if dispersion follows modulation.
+\\
+
+Figure \ref{fig:switch} shows the effect of switching these two components.
+Overall, the large scale structure is unchanged with the exception of $0.4 < s < 0.7$ and $20 < b$.
+In this region the waveform appears to have reached a period 2 equilibrium, that is, $|\mathcal{L}(\mathcal{L}(A))| = |A|$.
+
+\begin{figure}[htbp]
+\centering
+\begin{subfigure}[]{\textwidth}
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+set grid
+set xl '$s$'
+set yl '$b$'
+set cbl 'Error'
+set xr [0:1]
+set view map
+
+load '/home/brady/Templates/Blues.p'
+
+set cbr [0:0.75]
+sp '../30-06-01-MD.dat' using 1:2:3 w image not
 \end{gnuplot}
@@
 
-load '/home/brady/Templates/YGB.p'
+load '/home/brady/Templates/Blues.p'
 
 set cbr [0:0.75]
-sp '../Zoom01.dat' using 1:2:3 w image not
+sp '../30-06-01-MD-Z.dat' using 1:2:3 w image not
 \end{gnuplot}
@@
 \end{subfigure}
-\caption{Error is calculated by $\displaystyle \frac{\|A(\text{iteration } 25) - A(\text{iteration } 24) \|_2}{\|A(\text{iteration } 24) \|_2}$}
-\label{fig:}
+\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}}
+\label{fig:switch}
 \end{figure}
@@
 
-\newpage
 \printbibliography

### 2018-11-03 Paper/Paper.tex
Added Bryan's corrections

@@
 \end{equation}
-so that the modulus, $|A|$, and the phase, $A/|A|$, are given by
+so that the modulus, $|A|^2$, and the phase factor, $A/|A|$, are given by
 \begin{align*}
-	\left|A\right| &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)^{1/2}
-	\exp\left(-\frac{\delta \Omega^2 T^2}{2(1 + C^2)}\right),&
+	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
+	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right),&
 	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
@@
 \end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\theta$ where $2\theta = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
+The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
 \[
@@
 \]
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|$ and gives
+and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
 \begin{equation}
@@
 Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
-In practice, at high power levels, the gain drops as the fibre saturates.
+In practice, at high power levels, the gain drops as it saturates.
 One can model this with a gain term that takes the form
@@
 \end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency $f$ and modulus of the pulse so that
+where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency of the pulses, $f$, and modulus of the pulse so that
 \begin{align*}
-	f \int_{-\infty}^\infty |A(s)|^2\, \df s &=
+	f \int_{-\infty}^\infty |A(T)|^2\, \df T &=
 	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 = \Delta P_0, &
@@
 set yr [0:10]
-set xl '$\epsilon$'
-set yl '$|\beta_2|$'
+set xl '$\epsilon$ (AU)'
+set yl '$|\beta_2|$ (AU)'
 
@@
 \end{gnuplot}
-\caption{}
+\caption{The parameters are not to scale---this is only intended to show the structure.}
 \label{fig:average}
@@
 Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$ correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
+The representative hyperbola, $\epsilon|\beta_2| = 2g^2$, correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
 Curves of constant power level are also indicated.
@@
 \begin{align}
-	\hat{A}_{\textrm{out}}(\omega) &= \hat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
+	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
 	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
@@
 to represent the waveform.
-In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
+In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity or self-phase modulation, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
 Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
@@
 For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form solution, integrate~(\ref{diffez}) over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
+To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
 \[
@@
 \begin{align}
+	\nonumber G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
 	\label{eq:gain}
-	G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = 
-	\left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
+	&= \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
 	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
@@
 \end{align}
-so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives $\varphi(T,z) = \gamma |A|^2 z$.
+so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \phi(T,z)}$.
+Substituting this representation into~\eqref{eq:fibrediff} and setting $\phi(T,0)=0$ gives $\phi(T,z) = \gamma |A|^2 z$.
 For a fibre of length $L_f$ the effect of the nonlinearity is therefore
@@
 \label{eq:fibreloss}
-	L(A) &= C e^{- \alpha L}A,
+	L(A) &= R e^{- \alpha L}A,
 \end{align}
-where $C$ is the percentage lost due to the output coupler, and $L$ is the length of the laser circuit.
+where $R$ is the reflectivity of the output coupler, and $L$ is the length of the laser circuit.
 
@@
 For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
+However, for simplicity in the basic model and because of the nature of the grating, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
 
@@
 \begin{wraptable}{r}{0.45\textwidth}
+\vspace{-15mm}
 \begin{center}
@@
 \hline
+$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
+$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
+$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
 $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^f$ & $20$--$50 \text{ ps}^2/ \text{km}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$\Es$ & $10^4 \text{ pJ}$ \\
-$L_G$ & $2$--$3 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
+$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \\
+$T_M$ & $15$--$150 \text{ ps}$ \\
+$L$ & $10$--$100 \text{ m}$ \\
+$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
+$L_f$ & $0.15$--$1 \text{ m}$ \\
 \hline
@@
 \end{center}
+%\vspace{15mm}
 \end{wraptable}
@@
 The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
+Specifically, the time shall be scaled by the characteristic modulation time which is proportional to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
 \begin{align*}
@@
 \begin{align*}
-	G(A) &= \left(E^{-1} W_0 \left( a E e^{E}\right) \right)^{1/2} A,&
+	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
 	F(A) &= A \textrm{e}^{i b |A|^2}, \\
@@
 \begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 30,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.1,&
-	b &= \gamma L_F \frac{\Es}{T_M} \sim 0.1,& h &= C \textrm{e}^{-\alpha L} \sim 0.6,
+	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
+	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
 \end{align*}
@@
 \end{align*}
-where $\mathcal{L}$ is one loop of the circuit.
-A solution to this model is one in which the envelope is unchanged after traversing every component in the cavity, that is, such that $|\mathcal{L}(A)| = |A|$.
+where $\mathcal{L}$ is one loop of the laser.
+A solution to this model is one in which the envelope is unchanged after traversing every component in the cavity, that is, such that $|\mathcal{L}(A)|^2 = |A|^2$.
 
@@
 \begin{wrapfigure}{r}{0.45\textwidth}
+\vspace{-11mm}
 \centering
@@
 \end{wrapfigure}
-The model described is solved numerically and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we consider a linear analysis that ignores the nonlinear fibre effects.
+The model described is solved numerically, and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
+To gain some insight into this process we first consider a linear analysis that ignores the nonlinear fibre effects.
 
@@
 \subsection{Nonlinear Solution}
-In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
-However, this is not necessarily the case with the inclusion of the nonlinearity.
-The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations because of the Fourier transform which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
-\\
-
-Figure \ref{fig:stable} shows that small oscillations in the envelope can become smoothed out leading to a Gaussian-esque waveform.
-Conversely, Figure \ref{fig:break} shows how the waveform evolves for a slightly different $b$ value.
-Notice the oscillations are more pronounced, this effect compounds resulting in the wave breaking.
-\\
-
-The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
-Note that in Figure \ref{fig:envelope} the wave breaks for the smaller of the two $b$ values.
-This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
-\begin{align*}
-\frac{\|A(\text{iteration } 25) - A(\text{iteration } 24) \|_2}{\|A(\text{iteration } 24) \|_2}.
-\end{align*}
-In the region $0.35 < s < 0.6$ the wave does not break regardless of $b$.
-This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
 
@@
 set cbr [0:0.75]
-sp '../30-06-01-DM.dat' using 1:2:3 w image not
-%'../ProductContours.dat' w l lc 'black' not
+sp '../8000-04-01-DM.dat' using 1:2:3 w image not, \
+'../TM_Contours.dat' w l lw 0.5 lc 'black' not
 \end{gnuplot}
-\caption{}
+\caption{Along the black lines $T_M$ is the only parameter varying.}
 \label{fig:DMZ}
@@
 set cbl 'Error'
-set xr [0:0.2]
+set xr [0:0.25]
 set view map
@@
 
-sp '../30-06-01-DM-Z.dat' using 1:2:3 w image not
+sp '../8000-04-01-DM-Z.dat' using 1:2:3 w image not
 #'contours.dat' u ($1 / 2500):($2 / 250):($2 / 250 < 10 * $1 / 2500 + 0.17 ? 1 : 1/0) w l lc 'black' not
@@
 \end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 30$, $h = 0.6$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.}
+\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.}
 \label{fig:DMmap}
@@
 
+In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
+However, this is not necessarily the case with the inclusion of the nonlinearity.
+The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
+These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
+\\
+
+Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
+In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function.
+However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
+Furthermore, the chirp is highly erratic.
+\\
+
+The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
+Note that in Figure \ref{fig:pulse} the wave breaks for the smaller of the two $b$ values.
+This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
+\begin{align*}
+\frac{\|A(\text{iteration } 40) - A(\text{iteration } 39) \|_2}{\|A(\text{iteration } 39) \|_2}.
+\end{align*}
+Additionally, Figure \ref{fig:energy} shows the energy of the pulse within the parameter space. \\
+
+One interesting feature is that in the region $0.25 < s < 0.55$ the wave does not break regardless of $b$.
+This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
+
 \subsubsection{Ordering}
-Since some of the individual mappings are nonlinear they do not commute---thus changing the order of the components should lead to different results.
+
+\begin{figure}[!bp]
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+load '/home/brady/Templates/Blues.p'
+set grid
+set xl '$s$'
+set yl '$b$'
+set cbl '$E \, (\times 10^3)$'
+set view map
+set cbr [0:4]
+sp '../8000-04-01-DM-Z.dat' u 1:2:(1000*$4) w image not, \
+'EnergyContours.dat' w l lc 'black' lw 0.5 not
+\end{gnuplot}
+\caption{Energy as a function of $s$ and $b$.
+The energy is constant along the black lines.
+Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
+\label{fig:energy}
+\end{figure}
+
+Since some of the individual mappings are nonlinear they do not commute---changing the order of the components should lead to different results.
 The nonlinearity should still follow the gain component since that is where it is most dominant.
@@
 Figure \ref{fig:switch} shows the effect of switching these two components.
-Overall, the large scale structure is unchanged with the exception of $0.4 < s < 0.7$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $|\mathcal{L}(\mathcal{L}(A))| = |A|$.
+Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
+In this region the waveform appears to have reached a period 2 equilibrium, that is, $|\mathcal{L}(\mathcal{L}(A))|^2 = |A|^2$.
 
@@
 set cbr [0:0.75]
-sp '../30-06-01-MD.dat' using 1:2:3 w image not
+sp '../8000-04-01-MD.dat' using 1:2:3 w image not
 \end{gnuplot}
@@
 set cbr [0:0.75]
-sp '../30-06-01-MD-Z.dat' using 1:2:3 w image not
+sp '../8000-04-01-MD-Z.dat' using 1:2:3 w image not
 \end{gnuplot}

### 2018-12-15 Paper/Envelopes.tex
Updated paper

@@
-\begin{figure}[htbp]
+\begin{figure*}[htbp]
 \centering
 \begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,3in lw 3}]
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,2in lw 3}]
 set grid
-set key above
 set xr [-2:2]
-set yr [-0.75:0.75]
 set xl '$T$'
-set xtics 1
+set xtics 0.5
+set ytics 1
+set yl '$|A|^2$ (AU)'
 
-unset key
-set multiplot layout 1, 2
+p '../Stable/Envelope25.dat' u 1:(10**3*$4**2) w l t 'Stable', \
+'../Break/Envelope25.dat' u 1:(10**3*$4**2) w l dt 5 t 'Broken'
+\end{gnuplot}
+\caption{Envelope}
+\label{fig:envelope}
+\end{subfigure} \\
 
-set size 0.5, 1
-p '../Stable/Envelope8.dat' u 1:4 w l t 'Magnitude', \
- '../Stable/Envelope8.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
-'../Stable/Envelope8.dat' u 1:3 w l dt 4 t 'Imaginary'
+\begin{subfigure}[]{\textwidth}
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,2in lw 3}]
+set grid
+set xl '$\omega$'
+set yl '$|\widehat{A}|$'
+set xr [-40:40]
+set ytics 3
 
-set size 0.5, 1
-p '../Stable/Envelope15.dat' u 1:4 w l t 'Magnitude', \
- '../Stable/Envelope15.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
-'../Stable/Envelope15.dat' u 1:3 w l dt 4 t 'Imaginary'
-
-set key at 0, 0.8
-unset ytics
-unset xtics
-unset border
-unset xl
-set size 1, 0.1
-set yr [0:0.01]
-
-p 2 t 'Magnitude', \
-2 dt 5 lc 7 t 'Real', \
-2 dt 4 t 'Imaginary'
-\end{gnuplot}
-\caption{Wave is stable for $b = 1.5$.}
-\label{fig:stable}
-\end{subfigure} \\
-\vspace{4mm}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,3in lw 3}]
-set grid
-set key above
-set xr [-2:2]
-set yr [-0.75:0.75]
-set xl '$T$'
-set xtics 1
-
-unset key
-set multiplot layout 1, 2
-
-set size 0.5, 1
-p '../Break/Envelope8.dat' u 1:4 w l t 'Magnitude', \
- '../Break/Envelope8.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
-'../Break/Envelope8.dat' u 1:3 w l dt 4 t 'Imaginary'
-
-set size 0.5, 1
-p '../Break/Envelope15.dat' u 1:4 w l t 'Magnitude', \
- '../Break/Envelope15.dat' u 1:2 w l dt 5 lc 7 t 'Real', \
-'../Break/Envelope15.dat' u 1:3 w l dt 4 t 'Imaginary'
-
-set key at 0, 0.8
-unset ytics
-unset xtics
-unset border
-unset xl
-set size 1, 0.1
-set yr [0:0.01]
-p 2 t 'Magnitude', \
-2 dt 5 lc 7 t 'Real', \
-2 dt 4 t 'Imaginary'
+p '../Stable/Envelope25.dat' u 6:($7**2) w l t 'Stable', \
+'../Break/Envelope25.dat' u 6:($7**2) w l dt 5 t 'Broken'
 
 \end{gnuplot}
-\caption{Wave breaks for $b = 1.4$.}
-\label{fig:break}
+\caption{Fourier Transform}
+\label{fig:fourier}
+\end{subfigure} \\
+
+\begin{subfigure}[]{\textwidth}
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6.5in,2in lw 3}]
+#d2(x,y) = ($0 == 0) ? (x1 = x, y1 = y, 1/0) : (x2 = x1, x1 = x, y2 = y1, y1 = y, if (x1 > x2 + pi) (x2 = x2 + 2 * pi), (y1-y2)/(x1-x2))
+
+x0=NaN
+y0=NaN
+
+d(x,y) = (dx=x-x0, x0=x, dy=y-y0, y0=y, (dy > pi) ? (dy = dy-2*pi) : (dy), ((dy < -pi)) ? (dy = dy+2*pi) : (dy), dy/dx)
+
+set grid
+set xr [-2:2]
+set yr [-20:20]
+set xl '$T$'
+set xtics 0.5
+set ytics 10
+set yl '$-\diff{\varphi}{T}$'
+set key bottom right opaque
+
+p '../Stable/Envelope25.dat' u 1:(-d($1,$5)) w l t 'Stable', \
+'../Break/Envelope25.dat' u 1:(-d($1,$5)) w l dt 5 t 'Broken'
+\end{gnuplot}
+\caption{Chirp}
+\label{fig:chirp}
 \end{subfigure}
-\caption{Simulation with $s = 0.11$, $a = 30$, $h = 0.6$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
-\textbf{Left:} Pulse after 8 iterations.
-\textbf{Right:} Pulse after 15 iterations.}
-\label{fig:envelope}
-\end{figure}
+
+\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
+$\Gamma$ is chosen such that $\int_{-\infty}^\infty |A|^2 \, \textrm{d}T = E_0$, and hyperbolic secant is chosen since it is a common soliton.
+In the stable case $b = 1.32$, whereas for the broken case $b = 1.25$.
+The pulse is shown after 25 iterations.}
+\label{fig:pulse}
+\end{figure*}

### 2018-12-15 Paper/Paper.tex
Updated paper

@@
 \section{Results}
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-11mm}
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
-f(x) = m * x + c
-fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
-set grid
-set ytics 0.1
-set xl '$s$'
-set yl '$\zeta(s, 0)$'
-set yr [0.75:1.05]
-plot '../Zeta.dat' u 1:2 w l t 'Data', \
-exp(f(x)) dt 4 t 'Fit'
-\end{gnuplot}
-\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
-\label{fig:zeta}
-\end{wrapfigure}
-The model described is solved numerically, and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we first consider a linear analysis that ignores the nonlinear fibre effects.
+%\begin{wrapfigure}{r}{0.45\textwidth}
+%\vspace{-11mm}
+%\centering
+%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
+%f(x) = m * x + c
+%fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
+%set grid
+%set ytics 0.1
+%set xl '$s$'
+%set yl '$\zeta(s, 0)$'
+%set yr [0.75:1.05]
+%plot '../Zeta.dat' u 1:2 w l t 'Data', \
+%exp(f(x)) dt 4 t 'Fit'
+%\end{gnuplot}
+%\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
+%\label{fig:zeta}
+%\end{wrapfigure}
+The linear version of the model described can be solved analytically , however, the full non-linear version must be solved numerically.
+Somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
+To gain some insight into this process we first consider the linear analysis that ignores the nonlinear fibre effects.
 
@@
 
-Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge to a Gaussian. Consider an initial pulse with envelope
+Since the pulse is modulated by a Gaussian, it is expected that the equilibrium envelope will also be a Gaussian. Consider the initial pulse
 \begin{align*}
-	|A_0| = \sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2},
+	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),
 \end{align*}
-after passing through the gain and loss pieces, and having neglected the fibre nonlinearity, the envelope will have the form
+where $C$ is the chirp. After passing through the gain and loss pieces---and having neglected the fibre nonlinearity---the pulse will have the form
 \begin{align*}
-	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
-	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
+	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),&
+	\text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
 \end{align*}
-where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread. This can be represented as
+is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread \cite{agrawal2013}. This can be written as
 \begin{align}
 \label{linear1}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \textrm{e}^{-T^2 / 2 \tilde{\sigma}^2}
+	A_3 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right),
 \end{align}
-where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. However, since dispersion conserves energy
-\begin{align*}
-	\int_{-\infty}^{\infty} P g(E)^2 h^2 \textrm{e}^{-T^2 / \sigma^2} \, \df T = 
-	\int_{-\infty}^{\infty} P g(E)^2 h^2 \zeta^2(s, 0) \textrm{e}^{-T^2 / \widetilde{\sigma}^2} \, \df T,
-\end{align*}
-which reduces to $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
-\begin{align*}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} \right).
-\end{align*}
-Finally, the pulse is modulated and so that after one loop the total effect is given by
+where $\widetilde{\sigma}^2$ is the resulting variance, and $\widetilde{C}$ is the resulting chirp. Finally, the pulse is modulated---after one loop the total effect is given by
 \begin{align}
 \label{linear2}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right).
+	A_4 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
 \end{align}
 
-In equilibrium, the envelope of the pulse is unchanged after completing a full circuit, in other words,
-\begin{align*}
-	\sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2} = 
-	\sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right),
-\end{align*}
-or more explicitly,
+In equilibrium, the envelope of the pulse as well as the chirp are unchanged after completing a full circuit, it must bet that $A_0 = A_4$.
+%\begin{align*}
+%	\sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) = 
+%	\sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
+%\end{align*}
+More explicitly, this gives three conditions:
 \begin{align}
 \label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta(s, 0) &= 1,&
-	-\frac{T^2}{2 \sigma^2} &= -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2}.
+	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \qquad
+	\frac{1}{\sigma^2} = \frac{1}{\widetilde{\sigma}^2} + 1, \qquad
+	\frac{C}{\sigma^2} = \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
 \end{align}
-The second condition simplifies to
+The out-coming variance and chirp are given by \cite{agrawal2013}
+\begin{align}
+\label{eq:tildes}
+	\widetilde{\sigma}^2 = \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \qquad
+	\widetilde{C} = C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
+\end{align}
+From \eqref{eq:energycond} and \eqref{eq:tildes} we find that the equilibrium variance reduces to the quartic
 \begin{align*}
-	\sigma = \sqrt{1 - \zeta^4(s, 0)}
+\left( \sigma^2 \right)^4 + 4 s^2 \left( \sigma^2 \right)^3 - 20 s^2 \left( \sigma^2 \right)^2 + 32 s^2 \left( \sigma^2 \right) - 16 s^2 = 0,
 \end{align*}
-and the peak of the pulse can be found by integration to give
+which has the solution
 \begin{align*}
-	P = \frac{E}{\sqrt{\pi} \sigma}.
+\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
 \end{align*}
@@
 \begin{align}
-	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
 	\label{eq:equilenergy}
+	E = \frac{h^2 \zeta}{1 - h^2 \zeta} \ln \left( a h^2 \zeta \right),
 \end{align}
+by letting $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.
 
@@
 
-In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
+In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
 However, this is not necessarily the case with the inclusion of the nonlinearity.
@@
 set yl '$b$'
-set cbl '$E \, (\times 10^3)$'
+set cbl '$E \, (\times 10^{-3})$'
 set view map

### 2018-12-15 Lasers.py
Housekeeping

@@ -14,19 +14,19 @@ def EE(a, s, h):
 	return r / (1 - r) * np.log(a * r)
 
 # Functions for each component
-def Gain(A, E, a = 30):
+def Gain(A, E, a = 8000):
 	return np.real(np.sqrt(W(a * E * np.exp(E)) / E)) * A
 
-def Loss(A, h = 0.4):
+def Loss(A, h = 0.04):
 	return h * A
 
 def Mod(A, T):
 	return np.exp(-T**2 / 2) * A
 
-def Fibre(A, b = 0.1):
+def Fibre(A, b = 0.25):
 	return np.exp(1j * b * np.real(np.abs(A)**2)) * A
 
-def Disp(A, T, s = 0.1):
+def Disp(A, T, s = 0.2):
 	F = np.fft.fft(A)
 	F = (np.abs(F) > 10**-4) * F
 	dw = np.pi / T[-1]
@@ -37,21 +37,25 @@ def Disp(A, T, s = 0.1):
 def Loop(A0, T, dx, s, b):
 	A = A0
 	A = Gain(A0, Energy(A0, dx))
-	A = Fibre(A, b)
-	A = Loss(A, 0.6)
+	#A = Fibre(A, b)
+	A = Loss(A)
+	#old = np.gradient(-np.gradient(np.angle(A), dx),dx)[len(A)/2]
 	A = Disp(A, T, s)
+	#new = np.gradient(-np.gradient(np.angle(A), dx),dx)[len(A)/2]
 	A = Mod(A, T)
+	#print old - new
 	return A
 
-N = 100 # Number of loops of the circuit
+N = 50 # Number of loops of the circuit
 p = 2**14 # Number of points in the discretization
-width = 64 # Size of window
-E0 = 0.1 # Initial energy
+width = 128 # Size of window
+E0 = 0.0001 # Initial energy
 
 # Initialization
 T = np.linspace(-width, width, p, endpoint = False)
 dx = T[1] - T[0]
-A0 = 1 / np.cosh(2 * T) * np.exp(1j * np.pi / 4)
+#A0 = 1 / np.cosh(2 * T) * np.exp(1j * np.pi / 4)
+A0 = np.exp(-(1+2.89005*1j)*T**2 / (2*0.938229**2))
 A0 = np.sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
 E = np.zeros(N)
 data = np.zeros((2 * N, p))
[…]

### 2018-12-15 Preprint/ms.tex
Added arXiv preprint

--- 2018-12-15 Paper/Paper.tex
@@
-\documentclass[12pt]{article}
+\pdfoutput=1
+% ****** Start of file aipsamp.tex ******
+%
+%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
+%   Version 4.1 of REVTeX, October 2009
+%
+%   Copyright (c) 2009 American Institute of Physics.
+%
+%   See the AIP README file for restrictions and more information.
+%
+% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
+% as well as the rest of the prerequisites for REVTeX 4.1
+%
+% It also requires running BibTeX. The commands are as follows:
+%
+%  1)  latex  aipsamp
+%  2)  bibtex aipsamp
+%  3)  latex  aipsamp
+%  4)  latex  aipsamp
+%
+% Use this file as a source of example code for your aip document.
+% Use the file aiptemplate.tex as a template for your document.
+\documentclass[%
+ aps,
+ jmp,%
+ amsmath,amssymb,
+%preprint,%
+ reprint,%
+%author-year,%
+%author-numerical,%
+nofootinbib
+]{revtex4-1}
 
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{xcolor,graphicx}
-\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{amsthm}
-%\usepackage{enumitem}
-\usepackage{wrapfig}
+\usepackage{graphicx}% Include figure files
+\usepackage{dcolumn}% Align table columns on decimal point
+\usepackage{bm}% bold math
+%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
+%\linenumbers\relax % Commence numbering lines
+
+%\usepackage[subfolder,cleanup]{gnuplottex}
+%\usepackage{wrapfig}
 \usepackage{subcaption}
 \usepackage{hyperref}
-\usepackage{biblatex}
+\usepackage{epstopdf}
+%\usepackage{biblatex}
 
-\bibliography{Ref.bib}
+%\bibliography{Ref.bib}
 
@@
 
-\title{}
-\author{Brady Metherall \& C.\ Sean Bohun}
-
-\newgeometry{margin=1in}
-%\setlength\parindent{0pt}
+\setlength{\abovecaptionskip}{5pt plus 3pt minus 2pt}
 
 \begin{document}
+
+%\preprint{AIP/123-QED}
+
+\title[]{A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers}% Force line breaks with \\
+%\thanks{Footnote to title of article.}
+
+\author{Brady Metherall}
+ \email{brady.metherall@uoit.ca}
+ \affiliation{University of Ontario Institute of Technology}
+\author{C. Sean Bohun}%
+ \email{sean.bohun@uoit.ca}
+ \affiliation{University of Ontario Institute of Technology}
+
+\date{\today}% It is always \today, today,
+             %  but any date may be explicitly specified
+
+\begin{abstract}
+A new nonlinear model is proposed for tuneable lasers.
+Using the generalized non-linear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
+These transformations are then composed to give the overall effect of one trip around the cavity.
+The linear version of this model is solved analytically, and the nonlinear version numerically.
+A consequence of this model being nonlinear is that it is able to exhibit wave breaking which prior models could not.
+We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
+\end{abstract}
+
+%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
+                             % Classification Scheme.
+%\keywords{Suggested keywords}%Use showkeys class option if keyword
+                              %display desired
 \maketitle
 
-\noindent
+\section{Introduction}
+Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
+Tuneable lasers on the other hand, have the ability to operate within a range of wavelengths \cite{bohun, burgoyne2010, yamashita}.
+As a result, tuneable lasers have applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}.
+This article is concerned with dispersion-tuned actively mode-locked (DTAML) lasers.
+The laser cavity consists of four elements: the dispersive element, the modulator, the gain fibre, and the optical coupler.
+The gain fibre consists of either an Erbium or Ytterbium doped fibre, and dispersion is generated by the highly dispersive chirped fibre Bragg grating (CFBG).
+\\
+
 To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform (dispersion, modulation, and gain/loss) described by an effective PDE, the solution of which gives the amplitude of the wave packet.
+The idea is to capture some of the physical elements in the waveform described by an effective PDE, the solution of which gives the amplitude of the wave packet.
 
@@
 where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
-Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
+Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation, but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
 Consequently, the ansatz for the amplitude is taken to be a function of the form
@@
 	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
-	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right),&
+	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right), \\
 	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
@@
 The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
-\[
-	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t
-	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
+\begin{align*}
+	\hat{A}(\omega,z) &= \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t \\
+	&= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
 	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
-\]
+\end{align*}
 and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
@@
 	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
-	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right)-\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
+	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right) \\
+	& \quad -\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
 	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
@@
 	C &= \sgn(\beta_2),&
-	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2},&
+	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2}, \\
 	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
@@
 \begin{align*}
-	f \int_{-\infty}^\infty |A(T)|^2\, \df T &=
-	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 = \Delta P_0, &
-	\Delta &= \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}=
+	f \int_{-\infty}^\infty |A(T)|^2\, \df T =
+	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 &= \Delta P_0, \\
+	\Delta = \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}&=
 	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 \centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 2}]
-# Constant power things
-Ps = 1
-f = 1
-g = 1
-a = 0.1
-f(x,y) = Ps / (sqrt(pi) * f) * (y / (2 * x))**(1/4) * (g / (sqrt(x * y / 2) + a) -1)
-
-set grid
-set xr [0:10]
-set yr [0:10]
-set xl '$\epsilon$ (AU)'
-set yl '$|\beta_2|$ (AU)'
-
-# Put contours in file
-set contour base 
-set cntrparam levels incremental 0, 0.1
-unset surface 
-set table 'curve.dat'
-set isosamples 1000
-splot f(x,y) 
-unset table
-
-# Plot everything
-p 2 / x t 'Constant Gain' lc 1 dt 5, \
-for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
-0 t 'Constant Duration' lc 7 dt 4, \
-for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 7 dt 4, \
-'curve.dat' w l t 'Constant Power' lw 2 lc 3
-
-\end{gnuplot}
+\input{Param}
 \caption{The parameters are not to scale---this is only intended to show the structure.}
@@
 In particular, the dispersion and the modulation would correspond to transfer functions of the form
-\begin{align}
+\begin{align*}
 	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
 	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
-\end{align}
-respectively where the dispersion is naturally defined in the frequency domain.
+\end{align*}
+respectively, where the dispersion is naturally defined in the frequency domain.
 Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
@@
 \label{eq:nlse}
-\pdiff{A}{z} = - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} 
-+ i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} \\
+\nonumber& \quad + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
 \end{align}
@@
 Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
-Within each component of the laser cavity the other four process are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
+Within each component of the laser cavity the other four processes are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
 
 \subsection{Gain}
-Considering the gain term as dominant as is expected with the the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
+Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
 \begin{align}
 \label{eq:gainde}
-	\pdiff{A}{z} &= \frac{1}{2} g(A) A,& g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
+	\pdiff{A}{z} &= \frac{1}{2} \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
 \end{align}
@@
 \subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this effect is dominant expression~\eqref{eq:nlse} gives
+The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this affect is dominant expression~\eqref{eq:nlse} becomes
 \begin{align}
@@
 \end{align}
-where $R$ is the reflectivity of the output coupler, and $L$ is the length of the laser circuit.
+where $R$ is the reflectivity of the output coupler, and $L$ is the total length of the laser circuit.
 
@@
 In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
-In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as a Gaussian pulse
+In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
 \begin{align}
@@
 \end{align}
-where $T_M$ is a characteristic width of the modulation.\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
+where $T_M$ is a characteristic width of the modulation.%\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
 
@@
 
-\begin{wraptable}{r}{0.45\textwidth}
-\vspace{-15mm}
+\begin{table}
 \begin{center}
@@
 $g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \\
-$T_M$ & $15$--$150 \text{ ps}$ \\
+$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \cite{burgoyne2014, agrawal2013, litchinitser} \\
+$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \cite{burgoyne2014, agrawal2013} \\
+$T_M$ & $15$--$150 \text{ ps}$ \cite{burgoyne2014} \\
 $L$ & $10$--$100 \text{ m}$ \\
@@
 \end{center}
-%\vspace{15mm}
-\end{wraptable}
+\end{table}
+
+\begin{figure}[tbp]
+\centering
+\begin{subfigure}[]{\columnwidth}
+\input{Shape}
+\caption{Envelope}
+\label{fig:envelope}
+\end{subfigure} \\
+\begin{subfigure}[]{\columnwidth}
+\input{Transform}
+\caption{Fourier Transform}
+\label{fig:fourier}
+\end{subfigure} \\
+\begin{subfigure}[]{\columnwidth}
+\input{Chirp}
+\caption{Chirp}
+\end{subfigure}
+\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
+$\Gamma$ is chosen such that $\int_{-\infty}^\infty |A|^2 \, \textrm{d}T = E_0$, and hyperbolic secant is chosen since it is a common soliton.
+In the stable case $b = 1.32$, whereas for the broken case $b = 1.25$.
+The pulses are shown after 25 iterations.}
+\label{fig:pulse}
+\end{figure}
 
@@
 	F(A) &= A \textrm{e}^{i b |A|^2}, \\
-	L(A) &= h A,&
 	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
+	L(A) &= h A, \\
 	M(A) &= \textrm{e}^{-T^2 / 2} A,
@@
 \begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
+	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2, \\
 	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
@@
 
-\subsection{Combining the Pieces}
+\subsection{Combining the Effects}
 In this model the pulse is iteratively passed through each process, the order of which is now important.
@@
 where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope is unchanged after traversing every component in the cavity, that is, such that $|\mathcal{L}(A)|^2 = |A|^2$.
+A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A$---potentially with a constant phase shift.
 
 \section{Results}
-%\begin{wrapfigure}{r}{0.45\textwidth}
-%\vspace{-11mm}
-%\centering
-%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
-%f(x) = m * x + c
-%fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
-%set grid
-%set ytics 0.1
-%set xl '$s$'
-%set yl '$\zeta(s, 0)$'
-%set yr [0.75:1.05]
-%plot '../Zeta.dat' u 1:2 w l t 'Data', \
-%exp(f(x)) dt 4 t 'Fit'
-%\end{gnuplot}
-%\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
-%\label{fig:zeta}
-%\end{wrapfigure}
-The linear version of the model described can be solved analytically , however, the full non-linear version must be solved numerically.
+
+The linear version of the model described can be solved analytically, however, the full nonlinear version must be solved numerically.
 Somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
@@
 
-% gnuplot code for the four waveforms
-\input{Envelopes}
+\begin{figure}[tbp]
+\vspace{-8mm}
+\centering
+\input{Energy}
+\caption{Energy as a function of $s$ and $b$ with $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$.
+The energy is constant along the black lines.
+Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
+\label{fig:energy}
+\end{figure}
 
@@
 \begin{align*}
-	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),
+	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right).
 \end{align*}
-where $C$ is the chirp. After passing through the gain and loss pieces---and having neglected the fibre nonlinearity---the pulse will have the form
+After passing through the gain and loss pieces---and having neglected the fibre nonlinearity---the pulse will have the form
 \begin{align*}
-	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),&
+	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right), \\
 	\text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
@@
 \end{align}
-where $\widetilde{\sigma}^2$ is the resulting variance, and $\widetilde{C}$ is the resulting chirp. Finally, the pulse is modulated---after one loop the total effect is given by
+where $\widetilde{\sigma}^2$ denotes the resulting variance, and $\widetilde{C}$ denotes the resulting chirp. Finally, the pulse is modulated---after one loop the total affect is given by
 \begin{align}
@@
 
-In equilibrium, the envelope of the pulse as well as the chirp are unchanged after completing a full circuit, it must bet that $A_0 = A_4$.
+In equilibrium, it must be that $A_0 = A_4$.
 %\begin{align*}
@@
 \label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \qquad
+	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \\
+\label{eq:varcond}
 	\frac{1}{\sigma^2} = \frac{1}{\widetilde{\sigma}^2} + 1, \qquad
@@
 \begin{align}
-\label{eq:tildes}
-	\widetilde{\sigma}^2 = \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \qquad
-	\widetilde{C} = C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
+\label{eq:variance}
+	\widetilde{\sigma}^2 &= \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \\
+\label{eq:chirp}
+	\widetilde{C} &= C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
 \end{align}
-From \eqref{eq:energycond} and \eqref{eq:tildes} we find that the equilibrium variance reduces to the quartic
+From (\ref{eq:varcond}--\ref{eq:chirp}) we find that the equilibrium variance reduces to the quartic
 \begin{align*}
@@
 \begin{align*}
-\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
+\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} \\
+&\qquad - s^4 - s^2 \sqrt{4 + s^4}.
 \end{align*}
@@
 \end{align}
-by letting $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.
+where $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.
 
@@
 
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:1]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-DM.dat' using 1:2:3 w image not, \
-'../TM_Contours.dat' w l lw 0.5 lc 'black' not
-\end{gnuplot}
-\caption{Along the black lines $T_M$ is the only parameter varying.}
-\label{fig:DMZ}
+\begin{figure*}
+\begin{subfigure}[]{0.5\textwidth}
+\input{Big}
+\end{subfigure}%
+\begin{subfigure}[]{0.5\textwidth}
+\input{Zoom}
 \end{subfigure}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:0.25]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-
-set cntrlabel start 1
-
-sp '../8000-04-01-DM-Z.dat' using 1:2:3 w image not
-#'contours.dat' u ($1 / 2500):($2 / 250):($2 / 250 < 10 * $1 / 2500 + 0.17 ? 1 : 1/0) w l lc 'black' not
-\end{gnuplot}
-\caption{}
-\label{fig:DM}
-\end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.}
+\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
+Along the black lines $T_M$ is the only parameter varying.}
 \label{fig:DMmap}
-\end{figure}
+\end{figure*}
 
@@
 Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
-In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function.
+In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function in close agreement with \cite{chen}.
 However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
@@
 This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
-
-\subsubsection{Ordering}
-
-\begin{figure}[!bp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-load '/home/brady/Templates/Blues.p'
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl '$E \, (\times 10^{-3})$'
-set view map
-set cbr [0:4]
-sp '../8000-04-01-DM-Z.dat' u 1:2:(1000*$4) w image not, \
-'EnergyContours.dat' w l lc 'black' lw 0.5 not
-\end{gnuplot}
-\caption{Energy as a function of $s$ and $b$.
-The energy is constant along the black lines.
-Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
-\label{fig:energy}
-\end{figure}
+\\
 
@@
 Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $|\mathcal{L}(\mathcal{L}(A))|^2 = |A|^2$.
+In this region the waveform appears to have reached a period 2 equilibrium, that is, $\mathcal{L}(\mathcal{L}(A)) = A$.
 
-\begin{figure}[htbp]
+\begin{figure*}
 \centering
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:1]
-set view map
+\begin{subfigure}[]{0.5\textwidth}
+\input{Switch}
+\end{subfigure}%
+\begin{subfigure}[]{0.5\textwidth}
+\input{SwitchZoom}
+\end{subfigure}
+\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}.}
+\label{fig:switch}
+\end{figure*}
 
-load '/home/brady/Templates/Blues.p'
+\section{Conclusion}
 
-set cbr [0:0.75]
-sp '../8000-04-01-MD.dat' using 1:2:3 w image not
-\end{gnuplot}
-\caption{}
-\label{fig:}
-\end{subfigure}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:0.25]
-set view map
+We proposed a new nonlinear model for tuneable lasers derived from the generalized nonlinear Schr\"{o}dinger equation.
+It was demonstrated that this model is able to predict the phenomenon wave breaking due to the inclusion of the nonlinearity.
+We then showed the rich structure of the boundary between a sustainable pulse, and a pulse that breaks.
+This model will hopefully aid in the design of tuneable lasers.
+\newpage
 
-load '/home/brady/Templates/Blues.p'
+%\printbibliography
 
-set cbr [0:0.75]
-sp '../8000-04-01-MD-Z.dat' using 1:2:3 w image not
-\end{gnuplot}
-\caption{}
-\end{subfigure}
-\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}}
-\label{fig:switch}
-\end{figure}
+\bibliography{Ref}
 
-%\begin{figure}[htbp]
-%\centering
-%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-%load '/home/brady/Templates/YGB.p'
-%S(x) = exp(-0.511444 * x + 0.0017412)
-%E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
-%a = 30
-%
-%set grid
-%set pm3d map
-%set isosamples 100, 100
-%set hidden3d
-%set contour surface
-%set cntrparam levels incremental 0, 0.1, 1.5
-%
-%set ytics 0.1
-%set xl '$s$'
-%set yl rotate by 0 '$h$'
-%set cbl rotate by 0 '$E$'
-%set xr [0:0.5]
-%set yr [0.25:0.6]
-%set cbr [0:1.4]
-%
-%unset clabel
-%
-%splot E(x, y) not
-%\end{gnuplot}
-%\caption{Equation \eqref{eq:energycond} for $a = 30$}
-%\label{fig:}
-%\end{figure}
-
-\printbibliography
 \end{document}

### 2018-12-19 Thesis/Figures/CFBG.tex
Started thesis

\begin{tikzpicture}
\draw (4,0) -- (12,0) -- (12,4) -- (4,4) -- cycle;
\foreach \i in {1,...,12}
  \draw (12 - 1/18*\i*\i,0) -- (12 - 1/18*\i*\i,4);
%\foreach \i in {0,...,12}
%  \draw [dashed] (12 - 1/18*\i*\i,4) -- (12 - 1/18*\i*\i,8);
\draw [domain=0:(12-16/18), samples=400, blue, thick] plot (\x, {-0.5*cos(4*pi*(\x-(12-25/18)) r) + 3});
\draw [domain=0:(12-81/18), samples=400, red, thick] plot (\x, {0.5*cos(2*pi*36/38*(\x-(12-100/18)) r) + 1});

\draw [thick, decoration={brace, mirror, raise=0.2cm}, decorate] (7.5,0) -- (100/9,0)
node [pos=0.5,anchor=north,yshift=-0.5cm] {Time Delay};
\draw [thick, decoration={brace, mirror, raise=0.2cm}, decorate] (12,0) -- (12,4)
node [pos=0.5,anchor=west,xshift=0.5cm] {CFBG};

\draw [->] (4,5) -- (12.5,5)
node [pos=0.47,anchor=north,yshift=-0.25cm] {$z$};
\draw [->] (4,5) -- (4,8)
node [pos=0.5,anchor=east,xshift=-0.2cm] {$n(z)$};
\foreach \i in {0,...,12}
  \draw [domain=(12-\i*\i/18):(12-(\i-1)*(\i-1)/18), samples=40, black, thick] plot (\x, {3/4*cos(2*pi*36/(4*\i-2)*(\x-(12-\i*\i/18)) r) + 6.5});
\end{tikzpicture}

### 2018-12-19 Thesis/Intro/Introduction.tex
Started thesis

--- 2018-12-15 Preprint/ms.tex
@@
-\pdfoutput=1
-% ****** Start of file aipsamp.tex ******
-%
-%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
-%   Version 4.1 of REVTeX, October 2009
-%
-%   Copyright (c) 2009 American Institute of Physics.
-%
-%   See the AIP README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex  aipsamp
-%  2)  bibtex aipsamp
-%  3)  latex  aipsamp
-%  4)  latex  aipsamp
-%
-% Use this file as a source of example code for your aip document.
-% Use the file aiptemplate.tex as a template for your document.
-\documentclass[%
- aps,
- jmp,%
- amsmath,amssymb,
-%preprint,%
- reprint,%
-%author-year,%
-%author-numerical,%
-nofootinbib
-]{revtex4-1}
-
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
-
-%\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{epstopdf}
-%\usepackage{biblatex}
-
-%\bibliography{Ref.bib}
-
-\providecommand{\df}{\textrm{d}}
-\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
-\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
-\newcommand{\Es}{E_{\textrm{sat}}}
-\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
-\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
-
-\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\sech}{sech}
-
-\setlength{\abovecaptionskip}{5pt plus 3pt minus 2pt}
-
-\begin{document}
-
-%\preprint{AIP/123-QED}
-
-\title[]{A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers}% Force line breaks with \\
-%\thanks{Footnote to title of article.}
-
-\author{Brady Metherall}
- \email{brady.metherall@uoit.ca}
- \affiliation{University of Ontario Institute of Technology}
-\author{C. Sean Bohun}%
- \email{sean.bohun@uoit.ca}
- \affiliation{University of Ontario Institute of Technology}
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
-
-\begin{abstract}
-A new nonlinear model is proposed for tuneable lasers.
-Using the generalized non-linear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
-These transformations are then composed to give the overall effect of one trip around the cavity.
-The linear version of this model is solved analytically, and the nonlinear version numerically.
-A consequence of this model being nonlinear is that it is able to exhibit wave breaking which prior models could not.
-We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
-\end{abstract}
-
-%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-\maketitle
-
-\section{Introduction}
+\chapter{Introduction}
 Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
@@
 
-\section{Average Model}
-The model for the amplitude in the `average' model is presupposed to have the form
-\begin{equation}
-\label{average}
-	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
-\end{equation}
-where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
-Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation, but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
-Consequently, the ansatz for the amplitude is taken to be a function of the form
-\begin{equation}
-\label{ansatz}
-	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
-	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
-\end{equation}
-so that the modulus, $|A|^2$, and the phase factor, $A/|A|$, are given by
-\begin{align*}
-	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
-	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right), \\
-	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
-	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
-\end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
-\begin{align*}
-	\hat{A}(\omega,z) &= \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t \\
-	&= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
-	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
-\end{align*}
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
-\begin{equation}
-\label{duration}
-	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
-\end{equation}
-
-Applying the form~(\ref{ansatz}) to expression~(\ref{average}) provides the algebraic condition
-\begin{align*}
-	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
-	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right) \\
-	& \quad -\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
-	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
-	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
-\end{align*}
-Treating this condition as a complex valued quadratic in $T$ gives four conditions. Assuming that $\psi\in\mathbb{R}$, the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
-\begin{align*}
-	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
-	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
-	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
-	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
-\end{align*}
-Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that $\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$.
-From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, $\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).
-The result is a two parameter family of solutions of the form~(\ref{ansatz}) with
-\begin{align*}
-	C &= \sgn(\beta_2),&
-	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2}, \\
-	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
-	g &= \left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2}.
-\end{align*}
-Moreover, we also see that the representation~(\ref{ansatz}) as a classical solution of~(\ref{average}) imposes a subclass of solutions with $g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.
-A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
-\begin{align*}
-	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.
-\end{align*}
-
-Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
-In practice, at high power levels, the gain drops as it saturates.
-One can model this with a gain term that takes the form
-\begin{equation}
-\label{newg}
-	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
-\end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency of the pulses, $f$, and modulus of the pulse so that
-\begin{align*}
-	f \int_{-\infty}^\infty |A(T)|^2\, \df T =
-	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 &= \Delta P_0, \\
-	\Delta = \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}&=
-	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
-\end{align*}
-where $\Delta$ is the duty cycle of the pulse. Denoting the saturation power as $P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
-\[
-	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f} \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/4}
-	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
-\]
-
-\begin{figure}[tbp]
+\begin{figure}[htbp]
 \centering
-\input{Param}
-\caption{The parameters are not to scale---this is only intended to show the structure.}
-\label{fig:average}
+\input{./Figures/CFBG}
+\label{fig:cfbg}
+\caption[Chirped Fibre Bragg Grating]{Chirped fibre Bragg grating schematic.}
 \end{figure}
-
-Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$, correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
-Curves of constant power level are also indicated.
-One of the main drawbacks of this model is the fixed chirp and its symmetric behaviour with respect to $T$.
-One way to alleviate some of these restrictions is to construct a discrete model whereby each of the modules in the tuneable laser are given by a transfer function that is motivated by the PDE~(\ref{average}).
-In particular, the dispersion and the modulation would correspond to transfer functions of the form
-\begin{align*}
-	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
-	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
-\end{align*}
-respectively, where the dispersion is naturally defined in the frequency domain.
-Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
-Details of this technique and its ability to predict a number of experimental effects can be found in~\cite{burgoyne2014}.
-
-\section{A New Model}
-Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} \\
-\nonumber& \quad + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align}
-to represent the waveform.
-In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity or self-phase modulation, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
-Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
-Within each component of the laser cavity the other four processes are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
-
-\subsection{Gain}
-Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
-\begin{align}
-\label{eq:gainde}
-	\pdiff{A}{z} &= \frac{1}{2} \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
-\end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}.
-%We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
-Multiplying~\eqref{eq:gainde} by $\bar{A}$, the complex conjugate of $A$, yields
-\begin{align*}
-	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es}.
-\end{align*}
-Adding this to its complex conjugate and integrating over $T$ gives
-%\begin{align*}
-%	\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
-%\end{align*}
-%After integrating this becomes
-\begin{align}
-\label{diffez}
-	\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
-\end{align}
-For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
-\[
-	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es}
-\]
-and by exponentiating, rearranging, and applying $W_0$, the positive branch of the Lambert $W$ function,
-\[
-	 W_0\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
-	 W_0\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
-\]
-This results in the closed form expression
-\begin{align}
-\label{eq:energy}
-	E_{\textrm{out}}(z) = \Es W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
-\end{align}
-with the desired property that $E_{\textrm{out}}(0)=E$. Since $E \sim |A|^2$, the gain in terms of the amplitude is given by
-\begin{align}
-	\nonumber G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
-	\label{eq:gain}
-	&= \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
-	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
-\end{align}
-where $L_g$ is the length of the gain fibre.
-
-\subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this affect is dominant expression~\eqref{eq:nlse} becomes
-\begin{align}
-\label{eq:fibrediff}
-	\pdiff{A}{z} - i \gamma |A|^2 A = 0,
-\end{align}
-so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \phi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\phi(T,0)=0$ gives $\phi(T,z) = \gamma |A|^2 z$.
-For a fibre of length $L_f$ the effect of the nonlinearity is therefore
-\begin{align}
-\label{eq:fibre}
-	F(A) &= A e^{i \gamma |A|^2 L_f}.
-\end{align}
-
-\subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
-Combining these two effects give a loss that takes the form
-\begin{align}
-\label{eq:fibreloss}
-	L(A) &= R e^{- \alpha L}A,
-\end{align}
-where $R$ is the reflectivity of the output coupler, and $L$ is the total length of the laser circuit.
-
-\subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
-In comparison, the dispersion due to the fibre is negligible\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.}.
-The dispersive terms of \eqref{eq:nlse} give
-\begin{align}
-\label{eq:disp}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
-\end{align}
-and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
-\begin{align*}
-	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\left(\beta_2 - \frac{\beta_3}{3} \omega\right) \FT{A}.
-\end{align*}
-The effect of dispersion is then
-\begin{align}
-\label{eq:dispersion}
-	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
-\end{align}
-For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model and because of the nature of the grating, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
-
-\subsection{Modulation}
-In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
-In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
-\begin{align}
-	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
-\end{align}
-where $T_M$ is a characteristic width of the modulation.%\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
-
-\subsection{Non-Dimensionalization}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \cite{burgoyne2014, agrawal2013, litchinitser} \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \cite{burgoyne2014, agrawal2013} \\
-$T_M$ & $15$--$150 \text{ ps}$ \cite{burgoyne2014} \\
-$L$ & $10$--$100 \text{ m}$ \\
-$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-$L_f$ & $0.15$--$1 \text{ m}$ \\
-\hline
-\end{tabular}
-\caption{Orders of magnitude of various parameters.}
-\label{tab:values}
-\end{center}
-\end{table}
-
-\begin{figure}[tbp]
-\centering
-\begin{subfigure}[]{\columnwidth}
-\input{Shape}
-\caption{Envelope}
-\label{fig:envelope}
-\end{subfigure} \\
-\begin{subfigure}[]{\columnwidth}
-\input{Transform}
-\caption{Fourier Transform}
-\label{fig:fourier}
-\end{subfigure} \\
-\begin{subfigure}[]{\columnwidth}
-\input{Chirp}
-\caption{Chirp}
-\end{subfigure}
-\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
-$\Gamma$ is chosen such that $\int_{-\infty}^\infty |A|^2 \, \textrm{d}T = E_0$, and hyperbolic secant is chosen since it is a common soliton.
-In the stable case $b = 1.32$, whereas for the broken case $b = 1.25$.
-The pulses are shown after 25 iterations.}
-\label{fig:pulse}
-\end{figure}
-
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is proportional to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
-\begin{align*}
-	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
-\end{align*}
-The new process maps, after dropping the tildes, become
-\begin{align*}
-	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2}, \\
-	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
-	L(A) &= h A, \\
-	M(A) &= \textrm{e}^{-T^2 / 2} A,
-\end{align*}
-with four dimensionless parameter groups (see Table~\ref{tab:values})
-\begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2, \\
-	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
-\end{align*}
-which control the behaviour of the laser.
-
-\subsection{Combining the Effects}
-In this model the pulse is iteratively passed through each process, the order of which is now important.
-In this first realization, the pulse is first amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity needs to be considered.
-The pulse is then tapped off by the output coupler, and then passes through the grating and is modulated.
-The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
-Functionally this can be denoted as
-\begin{align*}
-	\mathcal{L}(A) = M(D(L(F(G(A))))),
-\end{align*}
-where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A$---potentially with a constant phase shift.
-
-\section{Results}
-
-The linear version of the model described can be solved analytically, however, the full nonlinear version must be solved numerically.
-Somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we first consider the linear analysis that ignores the nonlinear fibre effects.
-
-\subsection{Linear Solution}
-
-\begin{figure}[tbp]
-\vspace{-8mm}
-\centering
-\input{Energy}
-\caption{Energy as a function of $s$ and $b$ with $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$.
-The energy is constant along the black lines.
-Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
-\label{fig:energy}
-\end{figure}
-
-Since the pulse is modulated by a Gaussian, it is expected that the equilibrium envelope will also be a Gaussian. Consider the initial pulse
-\begin{align*}
-	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right).
-\end{align*}
-After passing through the gain and loss pieces---and having neglected the fibre nonlinearity---the pulse will have the form
-\begin{align*}
-	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right), \\
-	\text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
-\end{align*}
-is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread \cite{agrawal2013}. This can be written as
-\begin{align}
-\label{linear1}
-	A_3 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right),
-\end{align}
-where $\widetilde{\sigma}^2$ denotes the resulting variance, and $\widetilde{C}$ denotes the resulting chirp. Finally, the pulse is modulated---after one loop the total affect is given by
-\begin{align}
-\label{linear2}
-	A_4 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
-\end{align}
-
-In equilibrium, it must be that $A_0 = A_4$.
-%\begin{align*}
-%	\sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) = 
-%	\sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
-%\end{align*}
-More explicitly, this gives three conditions:
-\begin{align}
-\label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \\
-\label{eq:varcond}
-	\frac{1}{\sigma^2} = \frac{1}{\widetilde{\sigma}^2} + 1, \qquad
-	\frac{C}{\sigma^2} = \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
-\end{align}
-The out-coming variance and chirp are given by \cite{agrawal2013}
-\begin{align}
-\label{eq:variance}
-	\widetilde{\sigma}^2 &= \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \\
-\label{eq:chirp}
-	\widetilde{C} &= C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
-\end{align}
-From (\ref{eq:varcond}--\ref{eq:chirp}) we find that the equilibrium variance reduces to the quartic
-\begin{align*}
-\left( \sigma^2 \right)^4 + 4 s^2 \left( \sigma^2 \right)^3 - 20 s^2 \left( \sigma^2 \right)^2 + 32 s^2 \left( \sigma^2 \right) - 16 s^2 = 0,
-\end{align*}
-which has the solution
-\begin{align*}
-\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} \\
-&\qquad - s^4 - s^2 \sqrt{4 + s^4}.
-\end{align*}
-Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
-\begin{align}
-	\label{eq:equilenergy}
-	E = \frac{h^2 \zeta}{1 - h^2 \zeta} \ln \left( a h^2 \zeta \right),
-\end{align}
-where $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.
-
-\subsection{Nonlinear Solution}
-
-\begin{figure*}
-\begin{subfigure}[]{0.5\textwidth}
-\input{Big}
-\end{subfigure}%
-\begin{subfigure}[]{0.5\textwidth}
-\input{Zoom}
-\end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
-Along the black lines $T_M$ is the only parameter varying.}
-\label{fig:DMmap}
-\end{figure*}
-
-In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
-However, this is not necessarily the case with the inclusion of the nonlinearity.
-The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
-\\
-
-Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
-In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function in close agreement with \cite{chen}.
-However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
-Furthermore, the chirp is highly erratic.
-\\
-
-The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
-Note that in Figure \ref{fig:pulse} the wave breaks for the smaller of the two $b$ values.
-This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
-\begin{align*}
-\frac{\|A(\text{iteration } 40) - A(\text{iteration } 39) \|_2}{\|A(\text{iteration } 39) \|_2}.
-\end{align*}
-Additionally, Figure \ref{fig:energy} shows the energy of the pulse within the parameter space. \\
-
-One interesting feature is that in the region $0.25 < s < 0.55$ the wave does not break regardless of $b$.
-This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
-\\
-
-Since some of the individual mappings are nonlinear they do not commute---changing the order of the components should lead to different results.
-The nonlinearity should still follow the gain component since that is where it is most dominant.
-Furthermore, the loss is a linear mapping and so it will commute with both dispersion and modulation.
-Therefore, the only other unique case to consider is if dispersion follows modulation.
-\\
-
-Figure \ref{fig:switch} shows the effect of switching these two components.
-Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $\mathcal{L}(\mathcal{L}(A)) = A$.
-
-\begin{figure*}
-\centering
-\begin{subfigure}[]{0.5\textwidth}
-\input{Switch}
-\end{subfigure}%
-\begin{subfigure}[]{0.5\textwidth}
-\input{SwitchZoom}
-\end{subfigure}
-\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}.}
-\label{fig:switch}
-\end{figure*}
-
-\section{Conclusion}
-
-We proposed a new nonlinear model for tuneable lasers derived from the generalized nonlinear Schr\"{o}dinger equation.
-It was demonstrated that this model is able to predict the phenomenon wave breaking due to the inclusion of the nonlinearity.
-We then showed the rich structure of the boundary between a sustainable pulse, and a pulse that breaks.
-This model will hopefully aid in the design of tuneable lasers.
-\newpage
-
-%\printbibliography
-
-\bibliography{Ref}
-
-\end{document}

### 2018-12-19 Thesis/Linear/Linear.tex
Started thesis

--- 2018-12-15 Preprint/ms.tex
@@
-\pdfoutput=1
-% ****** Start of file aipsamp.tex ******
-%
-%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
-%   Version 4.1 of REVTeX, October 2009
-%
-%   Copyright (c) 2009 American Institute of Physics.
-%
-%   See the AIP README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex  aipsamp
-%  2)  bibtex aipsamp
-%  3)  latex  aipsamp
-%  4)  latex  aipsamp
-%
-% Use this file as a source of example code for your aip document.
-% Use the file aiptemplate.tex as a template for your document.
-\documentclass[%
- aps,
- jmp,%
- amsmath,amssymb,
-%preprint,%
- reprint,%
-%author-year,%
-%author-numerical,%
-nofootinbib
-]{revtex4-1}
-
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
-
-%\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{epstopdf}
-%\usepackage{biblatex}
-
-%\bibliography{Ref.bib}
-
-\providecommand{\df}{\textrm{d}}
-\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
-\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
-\newcommand{\Es}{E_{\textrm{sat}}}
-\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
-\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
-
-\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\sech}{sech}
-
-\setlength{\abovecaptionskip}{5pt plus 3pt minus 2pt}
-
-\begin{document}
-
-%\preprint{AIP/123-QED}
-
-\title[]{A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers}% Force line breaks with \\
-%\thanks{Footnote to title of article.}
-
-\author{Brady Metherall}
- \email{brady.metherall@uoit.ca}
- \affiliation{University of Ontario Institute of Technology}
-\author{C. Sean Bohun}%
- \email{sean.bohun@uoit.ca}
- \affiliation{University of Ontario Institute of Technology}
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
-
-\begin{abstract}
-A new nonlinear model is proposed for tuneable lasers.
-Using the generalized non-linear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
-These transformations are then composed to give the overall effect of one trip around the cavity.
-The linear version of this model is solved analytically, and the nonlinear version numerically.
-A consequence of this model being nonlinear is that it is able to exhibit wave breaking which prior models could not.
-We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
-\end{abstract}
-
-%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-\maketitle
-
-\section{Introduction}
-Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
-Tuneable lasers on the other hand, have the ability to operate within a range of wavelengths \cite{bohun, burgoyne2010, yamashita}.
-As a result, tuneable lasers have applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}.
-This article is concerned with dispersion-tuned actively mode-locked (DTAML) lasers.
-The laser cavity consists of four elements: the dispersive element, the modulator, the gain fibre, and the optical coupler.
-The gain fibre consists of either an Erbium or Ytterbium doped fibre, and dispersion is generated by the highly dispersive chirped fibre Bragg grating (CFBG).
-\\
-
-To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform described by an effective PDE, the solution of which gives the amplitude of the wave packet.
-
-\section{Average Model}
-The model for the amplitude in the `average' model is presupposed to have the form
-\begin{equation}
-\label{average}
-	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
-\end{equation}
-where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
-Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation, but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
-Consequently, the ansatz for the amplitude is taken to be a function of the form
-\begin{equation}
-\label{ansatz}
-	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
-	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
-\end{equation}
-so that the modulus, $|A|^2$, and the phase factor, $A/|A|$, are given by
-\begin{align*}
-	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
-	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right), \\
-	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
-	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
-\end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
-\begin{align*}
-	\hat{A}(\omega,z) &= \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t \\
-	&= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
-	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
-\end{align*}
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
-\begin{equation}
-\label{duration}
-	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
-\end{equation}
-
-Applying the form~(\ref{ansatz}) to expression~(\ref{average}) provides the algebraic condition
-\begin{align*}
-	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
-	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right) \\
-	& \quad -\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
-	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
-	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
-\end{align*}
-Treating this condition as a complex valued quadratic in $T$ gives four conditions. Assuming that $\psi\in\mathbb{R}$, the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
-\begin{align*}
-	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
-	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
-	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
-	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
-\end{align*}
-Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that $\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$.
-From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, $\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).
-The result is a two parameter family of solutions of the form~(\ref{ansatz}) with
-\begin{align*}
-	C &= \sgn(\beta_2),&
-	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2}, \\
-	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
-	g &= \left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2}.
-\end{align*}
-Moreover, we also see that the representation~(\ref{ansatz}) as a classical solution of~(\ref{average}) imposes a subclass of solutions with $g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.
-A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
-\begin{align*}
-	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.
-\end{align*}
-
-Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
-In practice, at high power levels, the gain drops as it saturates.
-One can model this with a gain term that takes the form
-\begin{equation}
-\label{newg}
-	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
-\end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency of the pulses, $f$, and modulus of the pulse so that
-\begin{align*}
-	f \int_{-\infty}^\infty |A(T)|^2\, \df T =
-	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 &= \Delta P_0, \\
-	\Delta = \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}&=
-	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
-\end{align*}
-where $\Delta$ is the duty cycle of the pulse. Denoting the saturation power as $P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
-\[
-	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f} \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/4}
-	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
-\]
-
-\begin{figure}[tbp]
-\centering
-\input{Param}
-\caption{The parameters are not to scale---this is only intended to show the structure.}
-\label{fig:average}
-\end{figure}
-
-Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$, correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
-Curves of constant power level are also indicated.
-One of the main drawbacks of this model is the fixed chirp and its symmetric behaviour with respect to $T$.
-One way to alleviate some of these restrictions is to construct a discrete model whereby each of the modules in the tuneable laser are given by a transfer function that is motivated by the PDE~(\ref{average}).
-In particular, the dispersion and the modulation would correspond to transfer functions of the form
-\begin{align*}
-	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
-	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
-\end{align*}
-respectively, where the dispersion is naturally defined in the frequency domain.
-Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
-Details of this technique and its ability to predict a number of experimental effects can be found in~\cite{burgoyne2014}.
-
-\section{A New Model}
-Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} \\
-\nonumber& \quad + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align}
-to represent the waveform.
-In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity or self-phase modulation, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
-Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
-Within each component of the laser cavity the other four processes are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
-
-\subsection{Gain}
-Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
-\begin{align}
-\label{eq:gainde}
-	\pdiff{A}{z} &= \frac{1}{2} \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
-\end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}.
-%We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
-Multiplying~\eqref{eq:gainde} by $\bar{A}$, the complex conjugate of $A$, yields
-\begin{align*}
-	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es}.
-\end{align*}
-Adding this to its complex conjugate and integrating over $T$ gives
-%\begin{align*}
-%	\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
-%\end{align*}
-%After integrating this becomes
-\begin{align}
-\label{diffez}
-	\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
-\end{align}
-For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
-\[
-	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es}
-\]
-and by exponentiating, rearranging, and applying $W_0$, the positive branch of the Lambert $W$ function,
-\[
-	 W_0\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
-	 W_0\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
-\]
-This results in the closed form expression
-\begin{align}
-\label{eq:energy}
-	E_{\textrm{out}}(z) = \Es W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
-\end{align}
-with the desired property that $E_{\textrm{out}}(0)=E$. Since $E \sim |A|^2$, the gain in terms of the amplitude is given by
-\begin{align}
-	\nonumber G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
-	\label{eq:gain}
-	&= \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
-	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
-\end{align}
-where $L_g$ is the length of the gain fibre.
-
-\subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this affect is dominant expression~\eqref{eq:nlse} becomes
-\begin{align}
-\label{eq:fibrediff}
-	\pdiff{A}{z} - i \gamma |A|^2 A = 0,
-\end{align}
-so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \phi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\phi(T,0)=0$ gives $\phi(T,z) = \gamma |A|^2 z$.
-For a fibre of length $L_f$ the effect of the nonlinearity is therefore
-\begin{align}
-\label{eq:fibre}
-	F(A) &= A e^{i \gamma |A|^2 L_f}.
-\end{align}
-
-\subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
-Combining these two effects give a loss that takes the form
-\begin{align}
-\label{eq:fibreloss}
-	L(A) &= R e^{- \alpha L}A,
-\end{align}
-where $R$ is the reflectivity of the output coupler, and $L$ is the total length of the laser circuit.
-
-\subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
-In comparison, the dispersion due to the fibre is negligible\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.}.
-The dispersive terms of \eqref{eq:nlse} give
-\begin{align}
-\label{eq:disp}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
-\end{align}
-and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
-\begin{align*}
-	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\left(\beta_2 - \frac{\beta_3}{3} \omega\right) \FT{A}.
-\end{align*}
-The effect of dispersion is then
-\begin{align}
-\label{eq:dispersion}
-	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
-\end{align}
-For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model and because of the nature of the grating, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
-
-\subsection{Modulation}
-In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
-In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
-\begin{align}
-	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
-\end{align}
-where $T_M$ is a characteristic width of the modulation.%\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
-
-\subsection{Non-Dimensionalization}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \cite{burgoyne2014, agrawal2013, litchinitser} \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \cite{burgoyne2014, agrawal2013} \\
-$T_M$ & $15$--$150 \text{ ps}$ \cite{burgoyne2014} \\
-$L$ & $10$--$100 \text{ m}$ \\
-$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-$L_f$ & $0.15$--$1 \text{ m}$ \\
-\hline
-\end{tabular}
-\caption{Orders of magnitude of various parameters.}
-\label{tab:values}
-\end{center}
-\end{table}
-
-\begin{figure}[tbp]
-\centering
-\begin{subfigure}[]{\columnwidth}
-\input{Shape}
-\caption{Envelope}
-\label{fig:envelope}
-\end{subfigure} \\
-\begin{subfigure}[]{\columnwidth}
-\input{Transform}
-\caption{Fourier Transform}
-\label{fig:fourier}
-\end{subfigure} \\
-\begin{subfigure}[]{\columnwidth}
-\input{Chirp}
-\caption{Chirp}
-\end{subfigure}
-\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
-$\Gamma$ is chosen such that $\int_{-\infty}^\infty |A|^2 \, \textrm{d}T = E_0$, and hyperbolic secant is chosen since it is a common soliton.
-In the stable case $b = 1.32$, whereas for the broken case $b = 1.25$.
-The pulses are shown after 25 iterations.}
-\label{fig:pulse}
-\end{figure}
-
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is proportional to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
-\begin{align*}
-	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
-\end{align*}
-The new process maps, after dropping the tildes, become
-\begin{align*}
-	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2}, \\
-	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
-	L(A) &= h A, \\
-	M(A) &= \textrm{e}^{-T^2 / 2} A,
-\end{align*}
-with four dimensionless parameter groups (see Table~\ref{tab:values})
-\begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2, \\
-	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
-\end{align*}
-which control the behaviour of the laser.
-
-\subsection{Combining the Effects}
-In this model the pulse is iteratively passed through each process, the order of which is now important.
-In this first realization, the pulse is first amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity needs to be considered.
-The pulse is then tapped off by the output coupler, and then passes through the grating and is modulated.
-The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
-Functionally this can be denoted as
-\begin{align*}
-	\mathcal{L}(A) = M(D(L(F(G(A))))),
-\end{align*}
-where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A$---potentially with a constant phase shift.
-
-\section{Results}
-
-The linear version of the model described can be solved analytically, however, the full nonlinear version must be solved numerically.
-Somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we first consider the linear analysis that ignores the nonlinear fibre effects.
-
-\subsection{Linear Solution}
-
-\begin{figure}[tbp]
-\vspace{-8mm}
-\centering
-\input{Energy}
-\caption{Energy as a function of $s$ and $b$ with $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$.
-The energy is constant along the black lines.
-Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
-\label{fig:energy}
-\end{figure}
+\chapter{Linear Solution}
 
@@
 \begin{align*}
-	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right), \\
-	\text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
+	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),& \text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
 \end{align*}
@@
 
-In equilibrium, it must be that $A_0 = A_4$.
-%\begin{align*}
-%	\sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) = 
-%	\sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
-%\end{align*}
-More explicitly, this gives three conditions:
+In equilibrium, it must be that $A_0 = A_4$. More explicitly, this gives three conditions:
 \begin{align}
 \label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \\
-\label{eq:varcond}
-	\frac{1}{\sigma^2} = \frac{1}{\widetilde{\sigma}^2} + 1, \qquad
-	\frac{C}{\sigma^2} = \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
+	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1,& \frac{1}{\sigma^2} &= \frac{1}{\widetilde{\sigma}^2} + 1,& \frac{C}{\sigma^2} &= \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
 \end{align}
@@
 \label{eq:variance}
-	\widetilde{\sigma}^2 &= \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \\
-\label{eq:chirp}
-	\widetilde{C} &= C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
+	\widetilde{\sigma}^2 &= \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2},& \widetilde{C} &= C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
 \end{align}
@@
 \begin{align*}
-\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} \\
-&\qquad - s^4 - s^2 \sqrt{4 + s^4}.
+\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
 \end{align*}
@@
 where $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.
-
-\subsection{Nonlinear Solution}
-
-\begin{figure*}
-\begin{subfigure}[]{0.5\textwidth}
-\input{Big}
-\end{subfigure}%
-\begin{subfigure}[]{0.5\textwidth}
-\input{Zoom}
-\end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
-Along the black lines $T_M$ is the only parameter varying.}
-\label{fig:DMmap}
-\end{figure*}
-
-In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
-However, this is not necessarily the case with the inclusion of the nonlinearity.
-The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
-\\
-
-Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
-In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function in close agreement with \cite{chen}.
-However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
-Furthermore, the chirp is highly erratic.
-\\
-
-The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
-Note that in Figure \ref{fig:pulse} the wave breaks for the smaller of the two $b$ values.
-This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
-\begin{align*}
-\frac{\|A(\text{iteration } 40) - A(\text{iteration } 39) \|_2}{\|A(\text{iteration } 39) \|_2}.
-\end{align*}
-Additionally, Figure \ref{fig:energy} shows the energy of the pulse within the parameter space. \\
-
-One interesting feature is that in the region $0.25 < s < 0.55$ the wave does not break regardless of $b$.
-This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
-\\
-
-Since some of the individual mappings are nonlinear they do not commute---changing the order of the components should lead to different results.
-The nonlinearity should still follow the gain component since that is where it is most dominant.
-Furthermore, the loss is a linear mapping and so it will commute with both dispersion and modulation.
-Therefore, the only other unique case to consider is if dispersion follows modulation.
-\\
-
-Figure \ref{fig:switch} shows the effect of switching these two components.
-Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $\mathcal{L}(\mathcal{L}(A)) = A$.
-
-\begin{figure*}
-\centering
-\begin{subfigure}[]{0.5\textwidth}
-\input{Switch}
-\end{subfigure}%
-\begin{subfigure}[]{0.5\textwidth}
-\input{SwitchZoom}
-\end{subfigure}
-\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}.}
-\label{fig:switch}
-\end{figure*}
-
-\section{Conclusion}
-
-We proposed a new nonlinear model for tuneable lasers derived from the generalized nonlinear Schr\"{o}dinger equation.
-It was demonstrated that this model is able to predict the phenomenon wave breaking due to the inclusion of the nonlinearity.
-We then showed the rich structure of the boundary between a sustainable pulse, and a pulse that breaks.
-This model will hopefully aid in the design of tuneable lasers.
-\newpage
-
-%\printbibliography
-
-\bibliography{Ref}
-
-\end{document}

### 2018-12-19 Thesis/Model/Model.tex
Started thesis

--- 2018-12-15 Preprint/ms.tex
@@
-\pdfoutput=1
-% ****** Start of file aipsamp.tex ******
-%
-%   This file is part of the AIP files in the AIP distribution for REVTeX 4.
-%   Version 4.1 of REVTeX, October 2009
-%
-%   Copyright (c) 2009 American Institute of Physics.
-%
-%   See the AIP README file for restrictions and more information.
-%
-% TeX'ing this file requires that you have AMS-LaTeX 2.0 installed
-% as well as the rest of the prerequisites for REVTeX 4.1
-%
-% It also requires running BibTeX. The commands are as follows:
-%
-%  1)  latex  aipsamp
-%  2)  bibtex aipsamp
-%  3)  latex  aipsamp
-%  4)  latex  aipsamp
-%
-% Use this file as a source of example code for your aip document.
-% Use the file aiptemplate.tex as a template for your document.
-\documentclass[%
- aps,
- jmp,%
- amsmath,amssymb,
-%preprint,%
- reprint,%
-%author-year,%
-%author-numerical,%
-nofootinbib
-]{revtex4-1}
-
-\usepackage{graphicx}% Include figure files
-\usepackage{dcolumn}% Align table columns on decimal point
-\usepackage{bm}% bold math
-%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
-%\linenumbers\relax % Commence numbering lines
-
-%\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{epstopdf}
-%\usepackage{biblatex}
-
-%\bibliography{Ref.bib}
-
-\providecommand{\df}{\textrm{d}}
-\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
-\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
-\newcommand{\Es}{E_{\textrm{sat}}}
-\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
-\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
-
-\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\sech}{sech}
-
-\setlength{\abovecaptionskip}{5pt plus 3pt minus 2pt}
-
-\begin{document}
-
-%\preprint{AIP/123-QED}
-
-\title[]{A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers}% Force line breaks with \\
-%\thanks{Footnote to title of article.}
-
-\author{Brady Metherall}
- \email{brady.metherall@uoit.ca}
- \affiliation{University of Ontario Institute of Technology}
-\author{C. Sean Bohun}%
- \email{sean.bohun@uoit.ca}
- \affiliation{University of Ontario Institute of Technology}
-
-\date{\today}% It is always \today, today,
-             %  but any date may be explicitly specified
-
-\begin{abstract}
-A new nonlinear model is proposed for tuneable lasers.
-Using the generalized non-linear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
-These transformations are then composed to give the overall effect of one trip around the cavity.
-The linear version of this model is solved analytically, and the nonlinear version numerically.
-A consequence of this model being nonlinear is that it is able to exhibit wave breaking which prior models could not.
-We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
-\end{abstract}
-
-%\pacs{Valid PACS appear here}% PACS, the Physics and Astronomy
-                             % Classification Scheme.
-%\keywords{Suggested keywords}%Use showkeys class option if keyword
-                              %display desired
-\maketitle
-
-\section{Introduction}
-Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
-Tuneable lasers on the other hand, have the ability to operate within a range of wavelengths \cite{bohun, burgoyne2010, yamashita}.
-As a result, tuneable lasers have applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}.
-This article is concerned with dispersion-tuned actively mode-locked (DTAML) lasers.
-The laser cavity consists of four elements: the dispersive element, the modulator, the gain fibre, and the optical coupler.
-The gain fibre consists of either an Erbium or Ytterbium doped fibre, and dispersion is generated by the highly dispersive chirped fibre Bragg grating (CFBG).
-\\
-
-To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform described by an effective PDE, the solution of which gives the amplitude of the wave packet.
-
-\section{Average Model}
-The model for the amplitude in the `average' model is presupposed to have the form
-\begin{equation}
-\label{average}
-	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
-\end{equation}
-where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
-Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation, but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
-Consequently, the ansatz for the amplitude is taken to be a function of the form
-\begin{equation}
-\label{ansatz}
-	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
-	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
-\end{equation}
-so that the modulus, $|A|^2$, and the phase factor, $A/|A|$, are given by
-\begin{align*}
-	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
-	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right), \\
-	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
-	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
-\end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
-\begin{align*}
-	\hat{A}(\omega,z) &= \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t \\
-	&= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
-	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
-\end{align*}
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
-\begin{equation}
-\label{duration}
-	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
-\end{equation}
-
-Applying the form~(\ref{ansatz}) to expression~(\ref{average}) provides the algebraic condition
-\begin{align*}
-	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
-	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right) \\
-	& \quad -\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
-	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
-	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
-\end{align*}
-Treating this condition as a complex valued quadratic in $T$ gives four conditions. Assuming that $\psi\in\mathbb{R}$, the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
-\begin{align*}
-	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
-	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
-	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
-	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
-\end{align*}
-Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that $\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$.
-From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, $\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).
-The result is a two parameter family of solutions of the form~(\ref{ansatz}) with
-\begin{align*}
-	C &= \sgn(\beta_2),&
-	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2}, \\
-	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
-	g &= \left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2}.
-\end{align*}
-Moreover, we also see that the representation~(\ref{ansatz}) as a classical solution of~(\ref{average}) imposes a subclass of solutions with $g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.
-A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
-\begin{align*}
-	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.
-\end{align*}
-
-Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
-In practice, at high power levels, the gain drops as it saturates.
-One can model this with a gain term that takes the form
-\begin{equation}
-\label{newg}
-	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
-\end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency of the pulses, $f$, and modulus of the pulse so that
-\begin{align*}
-	f \int_{-\infty}^\infty |A(T)|^2\, \df T =
-	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 &= \Delta P_0, \\
-	\Delta = \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}&=
-	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
-\end{align*}
-where $\Delta$ is the duty cycle of the pulse. Denoting the saturation power as $P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
-\[
-	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f} \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/4}
-	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
-\]
-
-\begin{figure}[tbp]
-\centering
-\input{Param}
-\caption{The parameters are not to scale---this is only intended to show the structure.}
-\label{fig:average}
-\end{figure}
-
-Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$, correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
-Curves of constant power level are also indicated.
-One of the main drawbacks of this model is the fixed chirp and its symmetric behaviour with respect to $T$.
-One way to alleviate some of these restrictions is to construct a discrete model whereby each of the modules in the tuneable laser are given by a transfer function that is motivated by the PDE~(\ref{average}).
-In particular, the dispersion and the modulation would correspond to transfer functions of the form
-\begin{align*}
-	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
-	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
-\end{align*}
-respectively, where the dispersion is naturally defined in the frequency domain.
-Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
-Details of this technique and its ability to predict a number of experimental effects can be found in~\cite{burgoyne2014}.
-
-\section{A New Model}
+\chapter{A New Model}
 Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
@@
 \label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} \\
-\nonumber& \quad + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
 \end{align}
@@
 
-\subsection{Gain}
+\section{Gain}
 Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
@@
 \begin{align}
-	\nonumber G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
 	\label{eq:gain}
-	&= \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
+	G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
 	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
@@
 
-\subsection{Fibre Nonlinearity}
+\section{Fibre Nonlinearity}
 The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this affect is dominant expression~\eqref{eq:nlse} becomes
@@
 
-\subsection{Loss}
+\section{Loss}
 Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
@@
 
-\subsection{Dispersion}
+\section{Dispersion}
 Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
@@
 
-\subsection{Modulation}
+\section{Modulation}
 In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
@@
 
-\subsection{Non-Dimensionalization}
+\section{Non-Dimensionalization}
 
@@
 
-\begin{figure}[tbp]
-\centering
-\begin{subfigure}[]{\columnwidth}
-\input{Shape}
-\caption{Envelope}
-\label{fig:envelope}
-\end{subfigure} \\
-\begin{subfigure}[]{\columnwidth}
-\input{Transform}
-\caption{Fourier Transform}
-\label{fig:fourier}
-\end{subfigure} \\
-\begin{subfigure}[]{\columnwidth}
-\input{Chirp}
-\caption{Chirp}
-\end{subfigure}
-\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
+%\begin{figure}[tbp]
+%\centering
+%\begin{subfigure}[]{\columnwidth}
+%\input{Shape}
+%\caption{Envelope}
+%\label{fig:envelope}
+%\end{subfigure} \\
+%\begin{subfigure}[]{\columnwidth}
+%\input{Transform}
+%\caption{Fourier Transform}
+%\label{fig:fourier}
+%\end{subfigure} \\
+%\begin{subfigure}[]{\columnwidth}
+%\input{Chirp}
+%\caption{Chirp}
+%\end{subfigure}
+%\caption{Simulation with $s = 0.09$, $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
 $\Gamma$ is chosen such that $\int_{-\infty}^\infty |A|^2 \, \textrm{d}T = E_0$, and hyperbolic secant is chosen since it is a common soliton.
@@
 The pulses are shown after 25 iterations.}
-\label{fig:pulse}
-\end{figure}
+%\label{fig:pulse}
+%\end{figure}
 
@@
 	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2}, \\
+	F(A) &= A \textrm{e}^{i b |A|^2},&
+	M(A) &= \textrm{e}^{-T^2 / 2} A, \\
 	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
-	L(A) &= h A, \\
-	M(A) &= \textrm{e}^{-T^2 / 2} A,
+	L(A) &= h A,
 \end{align*}
@@
 \begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2, \\
+	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
 	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
@@
 
-\subsection{Combining the Effects}
+\section{Combining the Effects}
 In this model the pulse is iteratively passed through each process, the order of which is now important.
@@
 A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A$---potentially with a constant phase shift.
-
-\section{Results}
-
-The linear version of the model described can be solved analytically, however, the full nonlinear version must be solved numerically.
-Somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we first consider the linear analysis that ignores the nonlinear fibre effects.
-
-\subsection{Linear Solution}
-
-\begin{figure}[tbp]
-\vspace{-8mm}
-\centering
-\input{Energy}
-\caption{Energy as a function of $s$ and $b$ with $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$.
-The energy is constant along the black lines.
-Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
-\label{fig:energy}
-\end{figure}
-
-Since the pulse is modulated by a Gaussian, it is expected that the equilibrium envelope will also be a Gaussian. Consider the initial pulse
-\begin{align*}
-	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right).
-\end{align*}
-After passing through the gain and loss pieces---and having neglected the fibre nonlinearity---the pulse will have the form
-\begin{align*}
-	A_2 &= \sqrt{P} g(E) h \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right), \\
-	\text{where } g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2}
-\end{align*}
-is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread \cite{agrawal2013}. This can be written as
-\begin{align}
-\label{linear1}
-	A_3 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right),
-\end{align}
-where $\widetilde{\sigma}^2$ denotes the resulting variance, and $\widetilde{C}$ denotes the resulting chirp. Finally, the pulse is modulated---after one loop the total affect is given by
-\begin{align}
-\label{linear2}
-	A_4 = \sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
-\end{align}
-
-In equilibrium, it must be that $A_0 = A_4$.
-%\begin{align*}
-%	\sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) = 
-%	\sqrt{P} g(E) h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
-%\end{align*}
-More explicitly, this gives three conditions:
-\begin{align}
-\label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} &= 1, \\
-\label{eq:varcond}
-	\frac{1}{\sigma^2} = \frac{1}{\widetilde{\sigma}^2} + 1, \qquad
-	\frac{C}{\sigma^2} = \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
-\end{align}
-The out-coming variance and chirp are given by \cite{agrawal2013}
-\begin{align}
-\label{eq:variance}
-	\widetilde{\sigma}^2 &= \frac{\sigma^4 + 4 C s^2 \sigma^2 + 4 C^2 s^4 +4s^4}{\sigma^2}, \\
-\label{eq:chirp}
-	\widetilde{C} &= C + \left( 1 + C^2 \right) \frac{2s^2}{\sigma^2}.
-\end{align}
-From (\ref{eq:varcond}--\ref{eq:chirp}) we find that the equilibrium variance reduces to the quartic
-\begin{align*}
-\left( \sigma^2 \right)^4 + 4 s^2 \left( \sigma^2 \right)^3 - 20 s^2 \left( \sigma^2 \right)^2 + 32 s^2 \left( \sigma^2 \right) - 16 s^2 = 0,
-\end{align*}
-which has the solution
-\begin{align*}
-\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} \\
-&\qquad - s^4 - s^2 \sqrt{4 + s^4}.
-\end{align*}
-Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
-\begin{align}
-	\label{eq:equilenergy}
-	E = \frac{h^2 \zeta}{1 - h^2 \zeta} \ln \left( a h^2 \zeta \right),
-\end{align}
-where $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}}$.
-
-\subsection{Nonlinear Solution}
-
-\begin{figure*}
-\begin{subfigure}[]{0.5\textwidth}
-\input{Big}
-\end{subfigure}%
-\begin{subfigure}[]{0.5\textwidth}
-\input{Zoom}
-\end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.
-Along the black lines $T_M$ is the only parameter varying.}
-\label{fig:DMmap}
-\end{figure*}
-
-In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
-However, this is not necessarily the case with the inclusion of the nonlinearity.
-The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
-\\
-
-Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
-In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function in close agreement with \cite{chen}.
-However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
-Furthermore, the chirp is highly erratic.
-\\
-
-The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
-Note that in Figure \ref{fig:pulse} the wave breaks for the smaller of the two $b$ values.
-This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
-\begin{align*}
-\frac{\|A(\text{iteration } 40) - A(\text{iteration } 39) \|_2}{\|A(\text{iteration } 39) \|_2}.
-\end{align*}
-Additionally, Figure \ref{fig:energy} shows the energy of the pulse within the parameter space. \\
-
-One interesting feature is that in the region $0.25 < s < 0.55$ the wave does not break regardless of $b$.
-This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
-\\
-
-Since some of the individual mappings are nonlinear they do not commute---changing the order of the components should lead to different results.
-The nonlinearity should still follow the gain component since that is where it is most dominant.
-Furthermore, the loss is a linear mapping and so it will commute with both dispersion and modulation.
-Therefore, the only other unique case to consider is if dispersion follows modulation.
-\\
-
-Figure \ref{fig:switch} shows the effect of switching these two components.
-Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $\mathcal{L}(\mathcal{L}(A)) = A$.
-
-\begin{figure*}
-\centering
-\begin{subfigure}[]{0.5\textwidth}
-\input{Switch}
-\end{subfigure}%
-\begin{subfigure}[]{0.5\textwidth}
-\input{SwitchZoom}
-\end{subfigure}
-\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}.}
-\label{fig:switch}
-\end{figure*}
-
-\section{Conclusion}
-
-We proposed a new nonlinear model for tuneable lasers derived from the generalized nonlinear Schr\"{o}dinger equation.
-It was demonstrated that this model is able to predict the phenomenon wave breaking due to the inclusion of the nonlinearity.
-We then showed the rich structure of the boundary between a sustainable pulse, and a pulse that breaks.
-This model will hopefully aid in the design of tuneable lasers.
-\newpage
-
-%\printbibliography
-
-\bibliography{Ref}
-
-\end{document}

### 2018-12-19 Thesis/Nonlinear/Nonlinear.tex
Started thesis

--- 2018-11-03 Paper/Paper.tex
@@
-\documentclass[12pt]{article}
+\chapter{Nonlinear Solution}
 
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{xcolor,graphicx}
-\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{amsthm}
-%\usepackage{enumitem}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{biblatex}
-
-\bibliography{Ref.bib}
-
-\providecommand{\df}{\textrm{d}}
-\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
-\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
-\newcommand{\Es}{E_{\textrm{sat}}}
-\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
-\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
-
-\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
-\DeclareMathOperator{\sgn}{sgn}
-\DeclareMathOperator{\sech}{sech}
-
-\title{}
-\author{Brady Metherall \& C.\ Sean Bohun}
-
-\newgeometry{margin=1in}
-%\setlength\parindent{0pt}
-
-\begin{document}
-\maketitle
-
-\noindent
-To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform (dispersion, modulation, and gain/loss) described by an effective PDE, the solution of which gives the amplitude of the wave packet.
-
-\section{Average Model}
-The model for the amplitude in the `average' model is presupposed to have the form
-\begin{equation}
-\label{average}
-	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
-\end{equation}
-where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
-Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
-Consequently, the ansatz for the amplitude is taken to be a function of the form
-\begin{equation}
-\label{ansatz}
-	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
-	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
-\end{equation}
-so that the modulus, $|A|^2$, and the phase factor, $A/|A|$, are given by
-\begin{align*}
-	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
-	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right),&
-	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
-	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
-\end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
-\[
-	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t
-	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
-	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
-\]
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
-\begin{equation}
-\label{duration}
-	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
-\end{equation}
-
-Applying the form~(\ref{ansatz}) to expression~(\ref{average}) provides the algebraic condition
-\begin{align*}
-	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
-	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right)-\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
-	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
-	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
-\end{align*}
-Treating this condition as a complex valued quadratic in $T$ gives four conditions. Assuming that $\psi\in\mathbb{R}$, the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
-\begin{align*}
-	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
-	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
-	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
-	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
-\end{align*}
-Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that $\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$.
-From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, $\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).
-The result is a two parameter family of solutions of the form~(\ref{ansatz}) with
-\begin{align*}
-	C &= \sgn(\beta_2),&
-	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2},&
-	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
-	g &= \left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2}.
-\end{align*}
-Moreover, we also see that the representation~(\ref{ansatz}) as a classical solution of~(\ref{average}) imposes a subclass of solutions with $g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.
-A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
-\begin{align*}
-	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.
-\end{align*}
-
-Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
-In practice, at high power levels, the gain drops as it saturates.
-One can model this with a gain term that takes the form
-\begin{equation}
-\label{newg}
-	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
-\end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency of the pulses, $f$, and modulus of the pulse so that
-\begin{align*}
-	f \int_{-\infty}^\infty |A(T)|^2\, \df T &=
-	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 = \Delta P_0, &
-	\Delta &= \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}=
-	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
-\end{align*}
-where $\Delta$ is the duty cycle of the pulse. Denoting the saturation power as $P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
-\[
-	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f} \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/4}
-	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
-\]
-
-\begin{figure}[htbp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 2}]
-# Constant power things
-Ps = 1
-f = 1
-g = 1
-a = 0.1
-f(x,y) = Ps / (sqrt(pi) * f) * (y / (2 * x))**(1/4) * (g / (sqrt(x * y / 2) + a) -1)
-
-set grid
-set xr [0:10]
-set yr [0:10]
-set xl '$\epsilon$ (AU)'
-set yl '$|\beta_2|$ (AU)'
-
-# Put contours in file
-set contour base 
-set cntrparam levels incremental 0, 0.1
-unset surface 
-set table 'curve.dat'
-set isosamples 1000
-splot f(x,y) 
-unset table
-
-# Plot everything
-p 2 / x t 'Constant Gain' lc 1 dt 5, \
-for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
-0 t 'Constant Duration' lc 7 dt 4, \
-for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 7 dt 4, \
-'curve.dat' w l t 'Constant Power' lw 2 lc 3
-
-\end{gnuplot}
-\caption{The parameters are not to scale---this is only intended to show the structure.}
-\label{fig:average}
-\end{figure}
-
-Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$, correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
-Curves of constant power level are also indicated.
-One of the main drawbacks of this model is the fixed chirp and its symmetric behaviour with respect to $T$.
-One way to alleviate some of these restrictions is to construct a discrete model whereby each of the modules in the tuneable laser are given by a transfer function that is motivated by the PDE~(\ref{average}).
-In particular, the dispersion and the modulation would correspond to transfer functions of the form
-\begin{align}
-	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
-	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
-\end{align}
-respectively where the dispersion is naturally defined in the frequency domain.
-Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
-Details of this technique and its ability to predict a number of experimental effects can be found in~\cite{burgoyne2014}.
-
-\section{A New Model}
-Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} = - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} 
-+ i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align}
-to represent the waveform.
-In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity or self-phase modulation, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
-Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
-Within each component of the laser cavity the other four process are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
-
-\subsection{Gain}
-Considering the gain term as dominant as is expected with the the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
-\begin{align}
-\label{eq:gainde}
-	\pdiff{A}{z} &= \frac{1}{2} g(A) A,& g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
-\end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}.
-%We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
-Multiplying~\eqref{eq:gainde} by $\bar{A}$, the complex conjugate of $A$, yields
-\begin{align*}
-	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es}.
-\end{align*}
-Adding this to its complex conjugate and integrating over $T$ gives
-%\begin{align*}
-%	\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
-%\end{align*}
-%After integrating this becomes
-\begin{align}
-\label{diffez}
-	\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
-\end{align}
-For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
-\[
-	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es}
-\]
-and by exponentiating, rearranging, and applying $W_0$, the positive branch of the Lambert $W$ function,
-\[
-	 W_0\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
-	 W_0\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
-\]
-This results in the closed form expression
-\begin{align}
-\label{eq:energy}
-	E_{\textrm{out}}(z) = \Es W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
-\end{align}
-with the desired property that $E_{\textrm{out}}(0)=E$. Since $E \sim |A|^2$, the gain in terms of the amplitude is given by
-\begin{align}
-	\nonumber G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
-	\label{eq:gain}
-	&= \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
-	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
-\end{align}
-where $L_g$ is the length of the gain fibre.
-
-\subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this effect is dominant expression~\eqref{eq:nlse} gives
-\begin{align}
-\label{eq:fibrediff}
-	\pdiff{A}{z} - i \gamma |A|^2 A = 0,
-\end{align}
-so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \phi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\phi(T,0)=0$ gives $\phi(T,z) = \gamma |A|^2 z$.
-For a fibre of length $L_f$ the effect of the nonlinearity is therefore
-\begin{align}
-\label{eq:fibre}
-	F(A) &= A e^{i \gamma |A|^2 L_f}.
-\end{align}
-
-\subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
-Combining these two effects give a loss that takes the form
-\begin{align}
-\label{eq:fibreloss}
-	L(A) &= R e^{- \alpha L}A,
-\end{align}
-where $R$ is the reflectivity of the output coupler, and $L$ is the length of the laser circuit.
-
-\subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
-In comparison, the dispersion due to the fibre is negligible\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.}.
-The dispersive terms of \eqref{eq:nlse} give
-\begin{align}
-\label{eq:disp}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
-\end{align}
-and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
-\begin{align*}
-	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\left(\beta_2 - \frac{\beta_3}{3} \omega\right) \FT{A}.
-\end{align*}
-The effect of dispersion is then
-\begin{align}
-\label{eq:dispersion}
-	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
-\end{align}
-For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model and because of the nature of the grating, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
-
-\subsection{Modulation}
-In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
-In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as a Gaussian pulse
-\begin{align}
-	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
-\end{align}
-where $T_M$ is a characteristic width of the modulation.\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
-
-\subsection{Non-Dimensionalization}
-
-\begin{wraptable}{r}{0.45\textwidth}
-\vspace{-15mm}
-\begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \\
-$T_M$ & $15$--$150 \text{ ps}$ \\
-$L$ & $10$--$100 \text{ m}$ \\
-$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-$L_f$ & $0.15$--$1 \text{ m}$ \\
-\hline
-\end{tabular}
-\caption{Orders of magnitude of various parameters.}
-\label{tab:values}
-\end{center}
-%\vspace{15mm}
-\end{wraptable}
-
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is proportional to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
-\begin{align*}
-	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
-\end{align*}
-The new process maps, after dropping the tildes, become
-\begin{align*}
-	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2}, \\
-	L(A) &= h A,&
-	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
-	M(A) &= \textrm{e}^{-T^2 / 2} A,
-\end{align*}
-with four dimensionless parameter groups (see Table~\ref{tab:values})
-\begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
-	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
-\end{align*}
-which control the behaviour of the laser.
-
-\subsection{Combining the Pieces}
-In this model the pulse is iteratively passed through each process, the order of which is now important.
-In this first realization, the pulse is first amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity needs to be considered.
-The pulse is then tapped off by the output coupler, and then passes through the grating and is modulated.
-The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
-Functionally this can be denoted as
-\begin{align*}
-	\mathcal{L}(A) = M(D(L(F(G(A))))),
-\end{align*}
-where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope is unchanged after traversing every component in the cavity, that is, such that $|\mathcal{L}(A)|^2 = |A|^2$.
-
-\section{Results}
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-11mm}
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
-f(x) = m * x + c
-fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
-set grid
-set ytics 0.1
-set xl '$s$'
-set yl '$\zeta(s, 0)$'
-set yr [0.75:1.05]
-plot '../Zeta.dat' u 1:2 w l t 'Data', \
-exp(f(x)) dt 4 t 'Fit'
-\end{gnuplot}
-\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
-\label{fig:zeta}
-\end{wrapfigure}
-The model described is solved numerically, and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we first consider a linear analysis that ignores the nonlinear fibre effects.
-
-\subsection{Linear Solution}
-
-% gnuplot code for the four waveforms
-\input{Envelopes}
-
-Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge to a Gaussian. Consider an initial pulse with envelope
-\begin{align*}
-	|A_0| = \sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2},
-\end{align*}
-after passing through the gain and loss pieces, and having neglected the fibre nonlinearity, the envelope will have the form
-\begin{align*}
-	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
-	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
-\end{align*}
-where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread. This can be represented as
-\begin{align}
-\label{linear1}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \textrm{e}^{-T^2 / 2 \tilde{\sigma}^2}
-\end{align}
-where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. However, since dispersion conserves energy
-\begin{align*}
-	\int_{-\infty}^{\infty} P g(E)^2 h^2 \textrm{e}^{-T^2 / \sigma^2} \, \df T = 
-	\int_{-\infty}^{\infty} P g(E)^2 h^2 \zeta^2(s, 0) \textrm{e}^{-T^2 / \widetilde{\sigma}^2} \, \df T,
-\end{align*}
-which reduces to $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
-\begin{align*}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} \right).
-\end{align*}
-Finally, the pulse is modulated and so that after one loop the total effect is given by
-\begin{align}
-\label{linear2}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right).
-\end{align}
-
-In equilibrium, the envelope of the pulse is unchanged after completing a full circuit, in other words,
-\begin{align*}
-	\sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2} = 
-	\sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right),
-\end{align*}
-or more explicitly,
-\begin{align}
-\label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta(s, 0) &= 1,&
-	-\frac{T^2}{2 \sigma^2} &= -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2}.
-\end{align}
-The second condition simplifies to
-\begin{align*}
-	\sigma = \sqrt{1 - \zeta^4(s, 0)}
-\end{align*}
-and the peak of the pulse can be found by integration to give
-\begin{align*}
-	P = \frac{E}{\sqrt{\pi} \sigma}.
-\end{align*}
-Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
-\begin{align}
-	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
-	\label{eq:equilenergy}
-\end{align}
-
-\subsection{Nonlinear Solution}
-
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:1]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-DM.dat' using 1:2:3 w image not, \
-'../TM_Contours.dat' w l lw 0.5 lc 'black' not
-\end{gnuplot}
-\caption{Along the black lines $T_M$ is the only parameter varying.}
-\label{fig:DMZ}
-\end{subfigure}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:0.25]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-
-set cntrlabel start 1
-
-sp '../8000-04-01-DM-Z.dat' using 1:2:3 w image not
-#'contours.dat' u ($1 / 2500):($2 / 250):($2 / 250 < 10 * $1 / 2500 + 0.17 ? 1 : 1/0) w l lc 'black' not
-\end{gnuplot}
-\caption{}
-\label{fig:DM}
-\end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.}
-\label{fig:DMmap}
-\end{figure}
-
-In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
+In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
 However, this is not necessarily the case with the inclusion of the nonlinearity.
@@
 This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
-
-\subsubsection{Ordering}
-
-\begin{figure}[!bp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-load '/home/brady/Templates/Blues.p'
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl '$E \, (\times 10^3)$'
-set view map
-set cbr [0:4]
-sp '../8000-04-01-DM-Z.dat' u 1:2:(1000*$4) w image not, \
-'EnergyContours.dat' w l lc 'black' lw 0.5 not
-\end{gnuplot}
-\caption{Energy as a function of $s$ and $b$.
-The energy is constant along the black lines.
-Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
-\label{fig:energy}
-\end{figure}
+\\
 
@@
 Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $|\mathcal{L}(\mathcal{L}(A))|^2 = |A|^2$.
-
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:1]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-MD.dat' using 1:2:3 w image not
-\end{gnuplot}
-\caption{}
-\label{fig:}
-\end{subfigure}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:0.25]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-MD-Z.dat' using 1:2:3 w image not
-\end{gnuplot}
-\caption{}
-\end{subfigure}
-\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}}
-\label{fig:switch}
-\end{figure}
-
-%\begin{figure}[htbp]
-%\centering
-%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-%load '/home/brady/Templates/YGB.p'
-%S(x) = exp(-0.511444 * x + 0.0017412)
-%E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
-%a = 30
-%
-%set grid
-%set pm3d map
-%set isosamples 100, 100
-%set hidden3d
-%set contour surface
-%set cntrparam levels incremental 0, 0.1, 1.5
-%
-%set ytics 0.1
-%set xl '$s$'
-%set yl rotate by 0 '$h$'
-%set cbl rotate by 0 '$E$'
-%set xr [0:0.5]
-%set yr [0.25:0.6]
-%set cbr [0:1.4]
-%
-%unset clabel
-%
-%splot E(x, y) not
-%\end{gnuplot}
-%\caption{Equation \eqref{eq:energycond} for $a = 30$}
-%\label{fig:}
-%\end{figure}
-
-\printbibliography
-\end{document}
+In this region the waveform appears to have reached a period 2 equilibrium, that is, $\mathcal{L}(\mathcal{L}(A)) = A$.

### 2018-12-19 Thesis/Thesis.tex
Started thesis

--- 2018-11-03 Paper/Paper.tex
@@
-\documentclass[12pt]{article}
+\documentclass[oneside]{UOIT_Thesis}
 
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{geometry}
-\usepackage{xcolor,graphicx}
-\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{amsthm}
-%\usepackage{enumitem}
-\usepackage{wrapfig}
-\usepackage{subcaption}
-\usepackage{hyperref}
-\usepackage{biblatex}
+\usepackage{tikz}
+\usetikzlibrary{patterns,snakes}
 
-\bibliography{Ref.bib}
+\usetikzlibrary{external}
+\tikzexternalize[prefix=Figures/]
+
+% Code Stuff
+\include{Listing}
 
@@
 
-\title{}
-\author{Brady Metherall \& C.\ Sean Bohun}
-
-\newgeometry{margin=1in}
-%\setlength\parindent{0pt}
+\title{A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers}
+\author{Brady Metherall}
+\degree{Master of Science}
+\faculty{Science}
+\program{Modelling and Computational Science}
 
 \begin{document}
+
+\frontmatter
+\pagenumbering{roman} 
 \maketitle
 
-\noindent
-To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform (dispersion, modulation, and gain/loss) described by an effective PDE, the solution of which gives the amplitude of the wave packet.
+\makeabstract{
+A new nonlinear model is proposed for tuneable lasers.
+Using the generalized non-linear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
+These transformations are then composed to give the overall effect of one trip around the cavity.
+The linear version of this model is solved analytically, and the nonlinear version numerically.
+A consequence of this model being nonlinear is that it is able to exhibit wave breaking which prior models could not.
+We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
+}
 
-\section{Average Model}
-The model for the amplitude in the `average' model is presupposed to have the form
-\begin{equation}
-\label{average}
-	\pdiff{A}{z} = -i\frac{\beta_2}{2}\pdiff[2]{A}{T} - \frac{\epsilon}{2}T^2 A + \frac{g}{2}A
-\end{equation}
-where $A=A(T,z)$ is the complex amplitude of the pulse with $\beta_2 \in \mathbb{R}$ defining the dispersion, $\epsilon \in \mathbb{R}$, $\epsilon > 0$, determining the modulation and $g \in \mathbb{R}$, $g > 0$ giving the gain.
-Expression~(\ref{average}) is reminiscent of the nonlinear Schr\"odinger equation but linear in $A$ so that the solution can take the form of a Gaussian wavepacket.
-Consequently, the ansatz for the amplitude is taken to be a function of the form
-\begin{equation}
-\label{ansatz}
-	A(T,z) = \left(\frac{P_0}{1-i C}\right)^{1/2}\exp
-	\left(-\frac{\delta \Omega^2 T^2}{2(1-i C)}\right)\textrm{e}^{i\psi z}
-\end{equation}
-so that the modulus, $|A|^2$, and the phase factor, $A/|A|$, are given by
-\begin{align*}
-	\left|A\right|^2 &= \left(\frac{P_0}{\sqrt{1 + C^2}}\right)
-	\exp\left(-\frac{\delta \Omega^2 T^2}{(1 + C^2)}\right),&
-	\frac{A}{|A|} &= \left(\frac{1+iC}{\sqrt{1+C^2}}\right)^{1/2}\exp
-	\left(-i\frac{\delta \Omega^2 T^2 C}{2(1+C^2)}\right)\textrm{e}^{i\psi z}.
-\end{align*}
-The quantity $C \in \mathbb{R}$ is known as the chirp and contributes a constant phase of $\varphi$ where $2\varphi = \arctan C$, $P_0$ is the maximum value of $|A|^2$ at $C=0$ (zero chirp), $\psi \in \mathbb{R}$ is the accumulated phase, and $\delta\Omega$ is the spectral half-width of $|A|^2$ since\footnote{If $f(t) = \textrm{e}^{-\alpha t^2}$ then $\hat{f}(\omega) = \frac{1}{2\pi}\int_{\mathbb{R}} f(t)\textrm{e}^{-i\omega t}\, \df t = \frac{1}{2\pi} (\frac{\pi}{\alpha})^{1/2}\textrm{e}^{-\omega^2/4\alpha}$.}
-\[
-	\hat{A}(\omega,z) = \frac{1}{2\pi}\int_{-\infty}^\infty A(t,z) \textrm{e}^{-i\omega t}\, \df t
-	= \left(\frac{P_0}{2\pi\delta \Omega^2}\right)^{1/2}
-	\exp\left(-\frac{(1-i C)\omega^2}{2\delta \Omega^2}\right) \textrm{e}^{i\psi z},
-\]
-and $|\hat{A}(\delta\Omega,z)|^2 = \textrm{e}^{-1}|\hat{A}(0,z)|^2$. The corresponding half-width of the pulse duration comes from the expression for $|A|^2$ and gives
-\begin{equation}
-\label{duration}
-	\delta T = \frac{\sqrt{1+C^2}}{\delta \Omega}.
-\end{equation}
+\makeacknowledgements{
+Thank some people that you like here.
+}
 
-Applying the form~(\ref{ansatz}) to expression~(\ref{average}) provides the algebraic condition
-\begin{align*}
-	i\psi &= -i\frac{\beta_2}{2}\delta\Omega^2(1-iC)^{-1}
-	\left(-1 + \delta\Omega^2(1-iC)^{-1}T^2\right)-\frac{\epsilon}{2}T^2 + \frac{g}{2} \\
-	&= \frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(-C(1+C^2)+2\delta\Omega^2 T^2C) -\frac{\epsilon}{2}T^2 + \frac{g}{2}\\
-	& \quad + i\frac{\beta_2\delta\Omega^2}{2(1+C^2)^2}(1+C^2 + \delta\Omega^2 T^2(C^2-1)).
-\end{align*}
-Treating this condition as a complex valued quadratic in $T$ gives four conditions. Assuming that $\psi\in\mathbb{R}$, the real and imaginary components at $\bigO{1}$ and $\bigO{T^2}$ yield
-\begin{align*}
-	&\bigO{T^2}_{\textrm{Im}}: 0 = C^2 - 1, &
-	&\bigO{1}_{\textrm{Im}}: \psi = \frac{\beta_2\delta\Omega^2}{2(1+C^2)}, \\
-	&\bigO{T^2}_{\textrm{Re}}: \epsilon = \frac{2\beta_2\delta\Omega^4C}{(1+C^2)^2}, &
-	&\bigO{1}_{\textrm{Re}}: g = \frac{\beta_2\delta\Omega^2C}{(1+C^2)}.
-\end{align*}
-Starting with $\bigO{1}_{\textrm{Re}}$ we note that $g > 0$ implies that $\sgn(\beta_2 C) = \sgn(\beta_2)\sgn(C) = 1$.
-From $\bigO{T^2}_{\textrm{Im}}$, $C = \pm 1$ and therefore $C = \sgn(\beta_2)$, $\beta_2 C = |\beta_2|$ and $\epsilon > 0$, consistent with~(\ref{average}).
-The result is a two parameter family of solutions of the form~(\ref{ansatz}) with
-\begin{align*}
-	C &= \sgn(\beta_2),&
-	\delta\Omega^2 &= \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/2},&
-	\psi &= \sgn(\beta_2)\left(\frac{\epsilon|\beta_2|}{8}\right)^{1/2},&
-	g &= \left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2}.
-\end{align*}
-Moreover, we also see that the representation~(\ref{ansatz}) as a classical solution of~(\ref{average}) imposes a subclass of solutions with $g = \left(\epsilon|\beta_2|/2\right)^{1/2}$.
-A useful pulse characterization is the half-width of the pulse duration, $\delta T$, which satisfies
-\begin{align*}
-	\delta T^2 &= \left(\frac{2|\beta_2|}{\epsilon}\right)^{1/2}.
-\end{align*}
+\makedeclaration
 
-Since~(\ref{average}) is linear in $A$, any value of the peak power, $P_0$, is admissible.
-In practice, at high power levels, the gain drops as it saturates.
-One can model this with a gain term that takes the form
-\begin{equation}
-\label{newg}
-	g(P_0) = \frac{g_0}{1+\frac{\textrm{power in fibre}}{\textrm{saturation power}}} - \alpha
-\end{equation}
-where $g_0$ is the low-power gain and $\alpha$ represents the net losses in the laser cavity. The power in the fibre depends on the frequency of the pulses, $f$, and modulus of the pulse so that
-\begin{align*}
-	f \int_{-\infty}^\infty |A(T)|^2\, \df T &=
-	\frac{\sqrt{\pi}f}{\delta\Omega}P_0 = \Delta P_0, &
-	\Delta &= \frac{\sqrt{\pi}f}{\delta\Omega} = \frac{\sqrt{\pi}f\delta T}{\sqrt{1+C^2}}=
-	\sqrt{\pi}f \left(\frac{|\beta_2|}{2\epsilon}\right)^{1/4}
-\end{align*}
-where $\Delta$ is the duty cycle of the pulse. Denoting the saturation power as $P_{\textrm{sat}}$,~(\ref{newg}) can be inverted to give
-\[
-	P_0 = \frac{P_{\textrm{sat}}}{\sqrt{\pi}f} \left(\frac{2\epsilon}{|\beta_2|}\right)^{1/4}
-	\left(g_0\left(\left(\frac{\epsilon|\beta_2|}{2}\right)^{1/2} + \alpha\right)^{-1} - 1\right).
-\]
+\maketableofcontents
 
-\begin{figure}[htbp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 2}]
-# Constant power things
-Ps = 1
-f = 1
-g = 1
-a = 0.1
-f(x,y) = Ps / (sqrt(pi) * f) * (y / (2 * x))**(1/4) * (g / (sqrt(x * y / 2) + a) -1)
+\mainmatter
 
-set grid
-set xr [0:10]
-set yr [0:10]
-set xl '$\epsilon$ (AU)'
-set yl '$|\beta_2|$ (AU)'
+\pagenumbering{arabic}
+\doublespacing
 
-# Put contours in file
-set contour base 
-set cntrparam levels incremental 0, 0.1
-unset surface 
-set table 'curve.dat'
-set isosamples 1000
-splot f(x,y) 
-unset table
+%Red light faster than blue
 
-# Plot everything
-p 2 / x t 'Constant Gain' lc 1 dt 5, \
-for [g=1:5] 2 * g**2 / x not lc 1 dt 5, \
-0 t 'Constant Duration' lc 7 dt 4, \
-for [T=0:20:2] x / 2 * (T/10.0)**4 not lc 7 dt 4, \
-'curve.dat' w l t 'Constant Power' lw 2 lc 3
+\include{./Intro/Introduction}
+\include{./Model/Model}
+\include{./Linear/Linear}
+\include{./Nonlinear/Nonlinear}
 
-\end{gnuplot}
-\caption{The parameters are not to scale---this is only intended to show the structure.}
-\label{fig:average}
-\end{figure}
+\phantomsection 
+\addcontentsline{toc}{chapter}{References} 
+\bibliography{Ref}
 
-Figure~\ref{fig:average} shows a select set of possible waveforms in $(\epsilon,|\beta_2|)$ parameter space.
-The representative hyperbola, $\epsilon|\beta_2| = 2g^2$, correspond to constant gain while the rays through the origin, $|\beta_2|/\epsilon = \delta T^4/4$, correspond to constant width.
-Curves of constant power level are also indicated.
-One of the main drawbacks of this model is the fixed chirp and its symmetric behaviour with respect to $T$.
-One way to alleviate some of these restrictions is to construct a discrete model whereby each of the modules in the tuneable laser are given by a transfer function that is motivated by the PDE~(\ref{average}).
-In particular, the dispersion and the modulation would correspond to transfer functions of the form
-\begin{align}
-	\widehat{A}_{\textrm{out}}(\omega) &= \widehat{A}_{\textrm{in}}(\omega)\textrm{e}^{i\beta_2\omega^2/2},&
-	A_{\textrm{out}}(T) &= A_{\textrm{in}}(T)\textrm{e}^{-\epsilon T^2/2},
-\end{align}
-respectively where the dispersion is naturally defined in the frequency domain.
-Between the modules, the pulse is assumed to propagate according to the representation~(\ref{ansatz}) chosen to be consistent with the transfer functions.
-Details of this technique and its ability to predict a number of experimental effects can be found in~\cite{burgoyne2014}.
+\appendix
 
-\section{A New Model}
-Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} = - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} 
-+ i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align}
-to represent the waveform.
-In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity or self-phase modulation, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
-Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
-Within each component of the laser cavity the other four process are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
+\chapter{Code}
 
-\subsection{Gain}
-Considering the gain term as dominant as is expected with the the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
-\begin{align}
-\label{eq:gainde}
-	\pdiff{A}{z} &= \frac{1}{2} g(A) A,& g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
-\end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}.
-%We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
-Multiplying~\eqref{eq:gainde} by $\bar{A}$, the complex conjugate of $A$, yields
-\begin{align*}
-	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es}.
-\end{align*}
-Adding this to its complex conjugate and integrating over $T$ gives
-%\begin{align*}
-%	\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
-%\end{align*}
-%After integrating this becomes
-\begin{align}
-\label{diffez}
-	\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
-\end{align}
-For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
-\[
-	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es}
-\]
-and by exponentiating, rearranging, and applying $W_0$, the positive branch of the Lambert $W$ function,
-\[
-	 W_0\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
-	 W_0\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
-\]
-This results in the closed form expression
-\begin{align}
-\label{eq:energy}
-	E_{\textrm{out}}(z) = \Es W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
-\end{align}
-with the desired property that $E_{\textrm{out}}(0)=E$. Since $E \sim |A|^2$, the gain in terms of the amplitude is given by
-\begin{align}
-	\nonumber G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
-	\label{eq:gain}
-	&= \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
-	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
-\end{align}
-where $L_g$ is the length of the gain fibre.
+\lstinputlisting[language=Python, lastline=60]{../Lasers.py}
 
-\subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this effect is dominant expression~\eqref{eq:nlse} gives
-\begin{align}
-\label{eq:fibrediff}
-	\pdiff{A}{z} - i \gamma |A|^2 A = 0,
-\end{align}
-so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \phi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\phi(T,0)=0$ gives $\phi(T,z) = \gamma |A|^2 z$.
-For a fibre of length $L_f$ the effect of the nonlinearity is therefore
-\begin{align}
-\label{eq:fibre}
-	F(A) &= A e^{i \gamma |A|^2 L_f}.
-\end{align}
-
-\subsection{Loss}
-Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
-Combining these two effects give a loss that takes the form
-\begin{align}
-\label{eq:fibreloss}
-	L(A) &= R e^{- \alpha L}A,
-\end{align}
-where $R$ is the reflectivity of the output coupler, and $L$ is the length of the laser circuit.
-
-\subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
-In comparison, the dispersion due to the fibre is negligible\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.}.
-The dispersive terms of \eqref{eq:nlse} give
-\begin{align}
-\label{eq:disp}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
-\end{align}
-and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
-\begin{align*}
-	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\left(\beta_2 - \frac{\beta_3}{3} \omega\right) \FT{A}.
-\end{align*}
-The effect of dispersion is then
-\begin{align}
-\label{eq:dispersion}
-	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
-\end{align}
-For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model and because of the nature of the grating, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
-
-\subsection{Modulation}
-In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
-In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as a Gaussian pulse
-\begin{align}
-	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
-\end{align}
-where $T_M$ is a characteristic width of the modulation.\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
-
-\subsection{Non-Dimensionalization}
-
-\begin{wraptable}{r}{0.45\textwidth}
-\vspace{-15mm}
-\begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \\
-$T_M$ & $15$--$150 \text{ ps}$ \\
-$L$ & $10$--$100 \text{ m}$ \\
-$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-$L_f$ & $0.15$--$1 \text{ m}$ \\
-\hline
-\end{tabular}
-\caption{Orders of magnitude of various parameters.}
-\label{tab:values}
-\end{center}
-%\vspace{15mm}
-\end{wraptable}
-
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is proportional to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
-\begin{align*}
-	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
-\end{align*}
-The new process maps, after dropping the tildes, become
-\begin{align*}
-	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2}, \\
-	L(A) &= h A,&
-	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
-	M(A) &= \textrm{e}^{-T^2 / 2} A,
-\end{align*}
-with four dimensionless parameter groups (see Table~\ref{tab:values})
-\begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
-	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
-\end{align*}
-which control the behaviour of the laser.
-
-\subsection{Combining the Pieces}
-In this model the pulse is iteratively passed through each process, the order of which is now important.
-In this first realization, the pulse is first amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity needs to be considered.
-The pulse is then tapped off by the output coupler, and then passes through the grating and is modulated.
-The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
-Functionally this can be denoted as
-\begin{align*}
-	\mathcal{L}(A) = M(D(L(F(G(A))))),
-\end{align*}
-where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope is unchanged after traversing every component in the cavity, that is, such that $|\mathcal{L}(A)|^2 = |A|^2$.
-
-\section{Results}
-\begin{wrapfigure}{r}{0.45\textwidth}
-\vspace{-11mm}
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.85in lw 3}]
-f(x) = m * x + c
-fit f(x) '../Zeta.dat' u 1:(log($2)) via m, c
-set grid
-set ytics 0.1
-set xl '$s$'
-set yl '$\zeta(s, 0)$'
-set yr [0.75:1.05]
-plot '../Zeta.dat' u 1:2 w l t 'Data', \
-exp(f(x)) dt 4 t 'Fit'
-\end{gnuplot}
-\caption{$\zeta(s, 0)$ is found empirically to be $\exp(-0.511444s + 0.00174128)$.}
-\label{fig:zeta}
-\end{wrapfigure}
-The model described is solved numerically, and somewhat surprisingly, its convergence as a function of the characteristic parameter groups is highly complex.
-To gain some insight into this process we first consider a linear analysis that ignores the nonlinear fibre effects.
-
-\subsection{Linear Solution}
-
-% gnuplot code for the four waveforms
-\input{Envelopes}
-
-Since the pulse is modulated by a Gaussian, it is expected that the envelope will also converge to a Gaussian. Consider an initial pulse with envelope
-\begin{align*}
-	|A_0| = \sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2},
-\end{align*}
-after passing through the gain and loss pieces, and having neglected the fibre nonlinearity, the envelope will have the form
-\begin{align*}
-	|A| &= \sqrt{P} g(E) h \textrm{e}^{-T^2 / 2 \sigma^2},&
-	g(E) &= \left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2},
-\end{align*}
-where $g(E)$ is the gain component. After the pulse travels through the grating, the envelope will maintain its Gaussian shape, however, it will have spread. This can be represented as
-\begin{align}
-\label{linear1}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \textrm{e}^{-T^2 / 2 \tilde{\sigma}^2}
-\end{align}
-where $\zeta(s, b)$ is the decrease in the amplitude and $\widetilde{\sigma}^2$ is the new variance. However, since dispersion conserves energy
-\begin{align*}
-	\int_{-\infty}^{\infty} P g(E)^2 h^2 \textrm{e}^{-T^2 / \sigma^2} \, \df T = 
-	\int_{-\infty}^{\infty} P g(E)^2 h^2 \zeta^2(s, 0) \textrm{e}^{-T^2 / \widetilde{\sigma}^2} \, \df T,
-\end{align*}
-which reduces to $\sigma = \zeta^2(s, 0) \widetilde{\sigma}$. Therefore, the envelope as the pulse exits the grating given by~(\ref{linear1}) is
-\begin{align*}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} \right).
-\end{align*}
-Finally, the pulse is modulated and so that after one loop the total effect is given by
-\begin{align}
-\label{linear2}
-	|A| = \sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right).
-\end{align}
-
-In equilibrium, the envelope of the pulse is unchanged after completing a full circuit, in other words,
-\begin{align*}
-	\sqrt{P} \textrm{e}^{-T^2 / 2 \sigma^2} = 
-	\sqrt{P} g(E) h \zeta(s, 0) \exp \left( -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2} \right),
-\end{align*}
-or more explicitly,
-\begin{align}
-\label{eq:energycond}
-	\left( \frac{W_0(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta(s, 0) &= 1,&
-	-\frac{T^2}{2 \sigma^2} &= -\zeta^4(s, 0) \frac{T^2}{2 \sigma^2} - \frac{T^2}{2}.
-\end{align}
-The second condition simplifies to
-\begin{align*}
-	\sigma = \sqrt{1 - \zeta^4(s, 0)}
-\end{align*}
-and the peak of the pulse can be found by integration to give
-\begin{align*}
-	P = \frac{E}{\sqrt{\pi} \sigma}.
-\end{align*}
-Furthermore, from~\eqref{eq:energycond} the equilibrium energy is found to be
-\begin{align}
-	E = \frac{\zeta^2(s, 0) h^2}{1 - \zeta^2(s, 0) h^2} \ln \left( a \zeta^2(s, 0) h^2 \right).
-	\label{eq:equilenergy}
-\end{align}
-
-\subsection{Nonlinear Solution}
-
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:1]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-DM.dat' using 1:2:3 w image not, \
-'../TM_Contours.dat' w l lw 0.5 lc 'black' not
-\end{gnuplot}
-\caption{Along the black lines $T_M$ is the only parameter varying.}
-\label{fig:DMZ}
-\end{subfigure}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:0.25]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-
-set cntrlabel start 1
-
-sp '../8000-04-01-DM-Z.dat' using 1:2:3 w image not
-#'contours.dat' u ($1 / 2500):($2 / 250):($2 / 250 < 10 * $1 / 2500 + 0.17 ? 1 : 1/0) w l lc 'black' not
-\end{gnuplot}
-\caption{}
-\label{fig:DM}
-\end{subfigure}
-\caption{Regions of convergence in the $s$--$b$ parameter space for $a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$ with $A_0 = \Gamma \sech{(2T)} \textrm{e}^{i \pi / 4}$.}
-\label{fig:DMmap}
-\end{figure}
-
-In the linear model, the pulse will converge to a Gaussian as long as $\zeta(s, 0) h > \sqrt a$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
-However, this is not necessarily the case with the inclusion of the nonlinearity.
-The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
-\\
-
-Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
-In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function.
-However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
-Furthermore, the chirp is highly erratic.
-\\
-
-The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
-Note that in Figure \ref{fig:pulse} the wave breaks for the smaller of the two $b$ values.
-This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
-\begin{align*}
-\frac{\|A(\text{iteration } 40) - A(\text{iteration } 39) \|_2}{\|A(\text{iteration } 39) \|_2}.
-\end{align*}
-Additionally, Figure \ref{fig:energy} shows the energy of the pulse within the parameter space. \\
-
-One interesting feature is that in the region $0.25 < s < 0.55$ the wave does not break regardless of $b$.
-This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
-
-\subsubsection{Ordering}
-
-\begin{figure}[!bp]
-\centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-load '/home/brady/Templates/Blues.p'
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl '$E \, (\times 10^3)$'
-set view map
-set cbr [0:4]
-sp '../8000-04-01-DM-Z.dat' u 1:2:(1000*$4) w image not, \
-'EnergyContours.dat' w l lc 'black' lw 0.5 not
-\end{gnuplot}
-\caption{Energy as a function of $s$ and $b$.
-The energy is constant along the black lines.
-Note this is the energy after a complete circuit of the laser cavity \emph{not} the energy outputted by the optical coupler.}
-\label{fig:energy}
-\end{figure}
-
-Since some of the individual mappings are nonlinear they do not commute---changing the order of the components should lead to different results.
-The nonlinearity should still follow the gain component since that is where it is most dominant.
-Furthermore, the loss is a linear mapping and so it will commute with both dispersion and modulation.
-Therefore, the only other unique case to consider is if dispersion follows modulation.
-\\
-
-Figure \ref{fig:switch} shows the effect of switching these two components.
-Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $|\mathcal{L}(\mathcal{L}(A))|^2 = |A|^2$.
-
-\begin{figure}[htbp]
-\centering
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:1]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-MD.dat' using 1:2:3 w image not
-\end{gnuplot}
-\caption{}
-\label{fig:}
-\end{subfigure}
-\begin{subfigure}[]{\textwidth}
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-set grid
-set xl '$s$'
-set yl '$b$'
-set cbl 'Error'
-set xr [0:0.25]
-set view map
-
-load '/home/brady/Templates/Blues.p'
-
-set cbr [0:0.75]
-sp '../8000-04-01-MD-Z.dat' using 1:2:3 w image not
-\end{gnuplot}
-\caption{}
-\end{subfigure}
-\caption{Regions of convergence with modulation preceding dispersion, same parameters as Figure \ref{fig:DMmap}}
-\label{fig:switch}
-\end{figure}
-
-%\begin{figure}[htbp]
-%\centering
-%\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
-%load '/home/brady/Templates/YGB.p'
-%S(x) = exp(-0.511444 * x + 0.0017412)
-%E(x, y) = -y**2 * log(a * y**2 * S(x)**2) * S(x)**2 / (y**2 * S(x)**2 - 1)
-%a = 30
-%
-%set grid
-%set pm3d map
-%set isosamples 100, 100
-%set hidden3d
-%set contour surface
-%set cntrparam levels incremental 0, 0.1, 1.5
-%
-%set ytics 0.1
-%set xl '$s$'
-%set yl rotate by 0 '$h$'
-%set cbl rotate by 0 '$E$'
-%set xr [0:0.5]
-%set yr [0.25:0.6]
-%set cbr [0:1.4]
-%
-%unset clabel
-%
-%splot E(x, y) not
-%\end{gnuplot}
-%\caption{Equation \eqref{eq:energycond} for $a = 30$}
-%\label{fig:}
-%\end{figure}
-
-\printbibliography
 \end{document}

### 2018-12-19 Thesis/Figures/Cavity.tex
Added laser cavity figure

\begin{tikzpicture}
% Two laser loops
\draw [rounded corners=4mm] (0,0) rectangle ++(9,4);
\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4);

% Gain
\draw (0.5,2.25) circle (0.5cm);
\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er Doped \\ Fibre};
\draw (0.5,1.75) circle (0.5cm);

% Modulator and pump
\filldraw[fill=white, draw=black] (3.5,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};

% Coupler and output
\draw[-{Latex[length=2.5mm]}] (4.5,4) -- (4.5,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
\draw[densely dashdotted] (4,3.5) -- (5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};

% Circulator
\filldraw[fill=white, draw=black] (9,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
\draw (9,2.5) arc (0:-90:0.5cm);
\draw (9,1.5) arc (0:90:0.5cm);

% Grating
\draw (8.5,2) -- (6.5,2) node [pos=0.5,anchor=south,yshift=0.25cm,xshift=-0.15cm] {CFBG};
\foreach \i in {0,...,13}
  \draw (6.5 + \i*\i/100,1.75) -- (6.5 + \i*\i/100,2.25);

% Arrows
\draw[-{Latex[length=2.5mm]}] (2.16,0) -- (2.15,0);
\draw[-{Latex[length=2.5mm]}] (2.39,4) -- (2.4,4);
\draw[-{Latex[length=2.5mm]}] (6.76,0) -- (6.75,0);
\draw[-{Latex[length=2.5mm]}] (7.09,4) -- (7.1,4);
\draw[-{Latex[length=2.5mm]}] (-0.649,0) -- (-0.65,0);
\draw[-{Latex[length=2.5mm]}] (-0.351,4) -- (-0.35,4);
\draw[-{Latex[length=2.5mm]}] (8.807,2.11) -- (8.8,2.1);
\draw[-{Latex[length=2.5mm]}] (8.96,1.712) -- (8.97,1.7);
\end{tikzpicture}

### 2018-12-19 Thesis/Figures/CFBG.tex
Updated CFBG figure

@@
 %  \draw [dashed] (12 - 1/18*\i*\i,4) -- (12 - 1/18*\i*\i,8);
-\draw [domain=0:(12-16/18), samples=400, blue, thick] plot (\x, {-0.5*cos(4*pi*(\x-(12-25/18)) r) + 3});
-\draw [domain=0:(12-81/18), samples=400, red, thick] plot (\x, {0.5*cos(2*pi*36/38*(\x-(12-100/18)) r) + 1});
+\draw [domain=0:(12-16/18), samples=1000, blue, thick] plot (\x, {-0.5*cos(4*pi*(\x-(12-25/18)) r) + 3});
+\draw [domain=0:(12-81/18), samples=500, red, thick] plot (\x, {0.5*cos(2*pi*36/38*(\x-(12-100/18)) r) + 1});
 
@@
 \foreach \i in {0,...,12}
-  \draw [domain=(12-\i*\i/18):(12-(\i-1)*(\i-1)/18), samples=40, black, thick] plot (\x, {3/4*cos(2*pi*36/(4*\i-2)*(\x-(12-\i*\i/18)) r) + 6.5});
+  \draw [domain=(12-\i*\i/18):(12-(\i-1)*(\i-1)/18), samples=100, black, thick] plot (\x, {3/4*cos(2*pi*36/(4*\i-2)*(\x-(12-\i*\i/18)) r) + 6.5});
 \end{tikzpicture}

### 2018-12-23 Thesis/Model/Model.tex
Told TeXWorks what the main file was

@@
+% !TeX root = ../Thesis.tex
+
 \chapter{A New Model}
@@
 \begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \cite{burgoyne2014, agrawal2013, litchinitser} \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \cite{burgoyne2014, agrawal2013} \\
-$T_M$ & $15$--$150 \text{ ps}$ \cite{burgoyne2014} \\
-$L$ & $10$--$100 \text{ m}$ \\
-$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-$L_f$ & $0.15$--$1 \text{ m}$ \\
+\begin{tabular}{lclc}
+Parameter & Symbol & Value & Source \\
+\noalign{\global\arrayrulewidth=1.5pt}\hline
+Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail} \\
+Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013} \\
+Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail} \\
+Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{burgoyne2014, agrawal2013, litchinitser} \\
+Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{burgoyne2014, agrawal2013} \\
+Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{burgoyne2014, burgoyneemail} \\
+Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail} \\
+Length of Gain Fibre & $L_g$ & $1$--$4 \text{ m}$ & \cite{burgoyne2014, shtyrina, yarutkina} \\
+Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
 \hline

### 2019-01-21 Thesis/Appendices/Dispersion.tex
Added appendices

% !TeX root = ../Thesis.tex

\chapter{Spread Due to Dispersion}

\cite{integrals}

### 2019-01-21 Thesis/Appendices/Lambert.tex
Added appendices

% !TeX root = ../Thesis.tex

\chapter{The Lambert $W$ Function}
\label{chap:lambertw}
The Lambert $W$ function is defined to be the inverse of the function $f(x) = x \textrm{e}^x$ and its graph is shown in Figure \ref{fig:lambertw}. In other words, if $z = x \textrm{e}^x$ then $x = W(z)$. Notice that by combining these relations we obtain the identities
\begin{align}
\label{eq:lambertw}
z &= W(z) \textrm{e}^{W(z)}, & x &= W(x \textrm{e}^x).
\end{align}
This function is called the Lambert $W$ function because it is the logarithm of a special instance of Lambert's series---the letter $W$ is used because of the work done by E. M. Wright \cite{lambertw}.

Notice that the original function, $f(x) = x \textrm{e}^x$, is \emph{not} injective, and as a consequence, the $W$ function is multi-valued on the interval $[-1/\textrm{e},0)$. To alleviate this, sometimes the branch $W(x) \geq -1$ is denoted $W_0$ and is called the upper or principal branch, whereas the branch $W(x) < -1$ is denoted $W_{-1}$ and is called the lower branch. However, in this work the $W$ function will only take positive real values and so this distinction is not needed.

\begin{figure}[htbp]
\centering
\input{./Figures/LambertPlot}
\caption{The two branches of the Lambert $W$ function.}
\label{fig:lambertw}
\end{figure}

The Lambert $W$ function has applications in various areas of math and physics \cite{lambertw} including:
\begin{itemize}
\item Jet fuel problems
\item Combustion problems
\item Enzyme kinetics problems
\item Linear constant coefficient differential delay equations
\item Volterra equations.
\end{itemize}
Primarily, the $W$ function is used when solving iterated exponentiation, and solving certain algebraic equations. For example, consider the equation $z = x^x$. By taking the logarithm of each side we have
\begin{align*}
\log z &= x \log x, \\
&= \log x \textrm{e}^{\log x},
\end{align*}
which after applying the $W$ function reduces to $W(\log z) = \log x$ by \eqref{eq:lambertw}. Finally, the answer can be written as $x = \exp(W(\log z))$.

### 2019-01-21 Thesis/Intro/Introduction.tex
Updated CFBG figure
Told TeXWorks what the main file was
Updated thesis

@@
+% !TeX root = ../Thesis.tex
+
 \chapter{Introduction}
+
+\section{Tuneable Lasers}
+
+\section{CFBG}
+
+\section{Previous Modelling Efforts}
+
+\section{Chirp}
+
+\section{GNLSE}
+
 Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
@@
 \end{figure}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/Cavity}
+\label{fig:cavity}
+\caption[Laser Cavity]{Laser cavity schematic.}
+\end{figure}

### 2019-01-21 Thesis/Model/Model.tex
Updated thesis

--- 2018-12-19 Thesis/Model/Model.tex
@@
+% !TeX root = ../Thesis.tex
+
 \chapter{A New Model}
-Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina} 
+Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina, burgoyne2007, peng} 
 \begin{align}
@@
 
-\section{Gain}
+\section{Components}
+
+\subsection{Gain}
 Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina}.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina, peng}.
 %We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
@@
 \]
-and by exponentiating, rearranging, and applying $W_0$, the positive branch of the Lambert $W$ function,
+and by exponentiating, rearranging, and applying $W$, the Lambert $W$ function (See Appendix \ref{chap:lambertw}),
 \[
-	 W_0\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
-	 W_0\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
+	 W\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
+	 W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
 \]
@@
 \label{eq:energy}
-	E_{\textrm{out}}(z) = \Es W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
+	E_{\textrm{out}}(z) = \Es W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
 \end{align}
@@
 	\label{eq:gain}
-	G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W_0 \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
+	G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
 	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
@@
 
-\section{Fibre Nonlinearity}
+\subsection{Fibre Nonlinearity}
 The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this affect is dominant expression~\eqref{eq:nlse} becomes
@@
 
-\section{Loss}
+\subsection{Loss}
 Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
@@
 
-\section{Dispersion}
+\subsection{Dispersion}
 Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
@@
 
-\section{Modulation}
+\subsection{Modulation}
 In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
@@
 \begin{center}
-\begin{tabular}{|l|l|}
-\hline
-Parameter & Value \\
-\hline
-$\Es$ & $10^3$--$10^4 \text{ pJ}$ \\
-$\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ \cite{agrawal2013} \\
-$g_0$ & $1$--$10 \text{ m}^{-1}$ \\
-$\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ \cite{burgoyne2014, agrawal2013, litchinitser} \\
-$\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ \cite{burgoyne2014, agrawal2013} \\
-$T_M$ & $15$--$150 \text{ ps}$ \cite{burgoyne2014} \\
-$L$ & $10$--$100 \text{ m}$ \\
-$L_g$ & $1$--$4 \text{ m}$ \cite{burgoyne2014, shtyrina, yarutkina} \\
-$L_f$ & $0.15$--$1 \text{ m}$ \\
+\begin{tabular}{lclc}
+Parameter & Symbol & Value & Sources \\
+\noalign{\global\arrayrulewidth=1.5pt}\hline
+Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, yarutkina} \\
+Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, yarutkina} \\
+Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
+Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{burgoyne2014, agrawal2013, shenping, agrawal2002} \\
+Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{burgoyne2014, agrawal2013, yarutkina, litchinitser, peng} \\
+Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{burgoyne2014, burgoyneemail, bohun} \\
+Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
+Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, shtyrina, yarutkina, peng} \\
+Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
+Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
+Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, yarutkina, shtyrina} \\
 \hline
@@
 \begin{align*}
-	G(A) &= \left(E^{-1} W_0 \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
+	G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
 	F(A) &= A \textrm{e}^{i b |A|^2},&
@@
 	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
-	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= R \textrm{e}^{-\alpha L} \sim 0.04,
+	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04,
 \end{align*}
@@
 In this model the pulse is iteratively passed through each process, the order of which is now important.
-In this first realization, the pulse is first amplified by the gain fibre, then since the pulse's magnitude is greatest the nonlinearity needs to be considered.
-The pulse is then tapped off by the output coupler, and then passes through the grating and is modulated.
+We are most interested in the output of the laser cavity, and so we shall start with the loss component---what enters the optical coupler.
+Next the pulse is passed though the CFBG, as well as the modulator.
+Finally, the pulse travels through the gain fibre to be amplified, and then we consider the effect of the nonlinearity since this is the region where the power is maximized.
 The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
@@
 \begin{align*}
-	\mathcal{L}(A) = M(D(L(F(G(A))))),
+	\mathcal{L}(A) = F(G(M(D(L(A))))),
 \end{align*}
@@
 A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A$---potentially with a constant phase shift.
+
+\section{Solution to the Linear Model}
+Since the pulse is modulated by a Gaussian, it is expected that the equilibrium envelope will also be a Gaussian. Consider the initial pulse
+\begin{align*}
+	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),
+\end{align*}
+where $P$ is the peak power.
+After passing though the optical coupler the pulse will simply decay, $A_1 = h A_0$.
+The pulse then enters the CFBG, where it will maintain its Gaussian shape, however, it will spread \cite{agrawal2013}.
+This can be written as
+\begin{align*}
+A_2 = \sqrt{P} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right),
+\end{align*}
+where $\widetilde{\sigma}^2$ denotes the resulting variance, and $\widetilde{C}$ denotes the resulting chirp. Next, the pulse is modulated:
+\begin{align*}
+A_3 = \sqrt{P} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
+\end{align*}
+Finally, the pulse travels though the gain fibre where it is amplified to
+\begin{align*}
+A_4 = \sqrt{P} \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right),
+\end{align*}
+with $E$ the energy of the pulse as it enters the gain fibre.
+
+In equilibrium, it must be that $A_0 = A_4 \textrm{e}^{i \varphi}$, for some $\varphi$. More explicitly, this gives three conditions:
+\begin{subequations}
+\begin{align}
+\label{eq:energycond}
+1 &= \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}, \\
+\label{eq:varcond}
+\frac{1}{\sigma^2} &= \frac{1}{\widetilde{\sigma}^2} + 1, \\
+\label{eq:chirpcond}
+\frac{C}{\sigma^2} &= \frac{\widetilde{C}}{\widetilde{\sigma}^2}.
+\end{align}
+\end{subequations}
+
+\subsection{Equilibrium Shape}
+After dispersion, the out-going variance $\widetilde{\sigma}$ can be found by computing the effect of dispersion given by ***. In the case of a Gaussian pulse \cite{agrawal2013} we have
+\begin{align*}
+\left( \frac{T_1}{T_0} \right)^2 &= \left( 1 + \frac{C \beta_2 z}{T_0^2} \right)^2 + \left( \frac{ \beta_2 z}{T_0^2} \right)^2,&
+\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2}
+\end{align*}
+where $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, $z = L_D$, and $\beta_2 z T_0^{-2} = 2s^2\sigma^{-2}$ within our non-dimensionalization. Making these substitutions yields the relations
+\begin{subequations}
+\begin{align}
+\label{eq:varout}
+\widetilde{\sigma}^2 \sigma^2 &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4s^4, \\
+\label{eq:chirpout}
+\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2},
+\end{align}
+\end{subequations}
+for the variance and chirp after the dispersive element. Now, the out-going variance and chirp can be eliminated from this system of equations using \eqref{eq:varcond} and \eqref{eq:chirpcond}:
+\begin{align*}
+\widetilde{\sigma}^2 &= \frac{\sigma^2}{1 - \sigma^2}, \\
+\widetilde{C} &= C \frac{1}{1 - \sigma^2}.
+\end{align*}
+Combining this first expression with \eqref{eq:varout} and expanding, we have that
+\begin{align*}
+\frac{\sigma^4}{1 - \sigma^2} = \sigma^4 + 4 C^2 s^4 + 4 C s^2 \sigma^2 + 4s^4,
+\end{align*}
+or written as a polynomial in $\sigma$,
+\begin{align*}
+0 = \sigma^6 + 4 C s^2 \sigma^4 + \left( 4s^4 (C^2 + 1) - 4 C s^2 \right) \sigma^2 - 4s^4 (C^2 + 1).
+\end{align*}
+The chirp can now be eliminated using \eqref{eq:chirpout}, the $1+C^2$ can be reduced in order by noticing that
+\begin{align*}
+C \frac{1}{1 - \sigma^2} &= C + (1 + C^2) \frac{2s^2}{\sigma^2} \\
+1 + C^2 &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} C.
+\end{align*}
+Furthermore, the chirp can be completely eliminated since
+\begin{align}
+\nonumber
+C &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} \pm \sqrt{\frac{\sigma^8}{16s^4(1 - \sigma^2)^2} - 1}, \\
+\label{eq:equilchirp}
+&= \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}}{4s^2(1 - \sigma^2)}.
+\end{align}
+After simplifying algebraically, we arrive at
+\begin{align*}
+0 &= \sigma^6 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}(2 - \sigma^2), \\
+\frac{\sigma^6}{2 - \sigma^2} &= \mp \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}.
+\end{align*}
+Notice that the left hand side of this expression is strictly positive ($\sigma$ is strictly less than $1$ at equilibrium), therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
+After squaring each side of this expression we obtain
+\begin{align*}
+\sigma^{12} = \sigma^8 (2 - \sigma^2)^2 - 16s^4 (1 - \sigma^2)^2 (2 - \sigma^2)^2,
+\end{align*}
+which once fully simplified, yields the biquartic equation
+\begin{align*}
+\left( \sigma^2 \right)^4 + 4 s^4 \left( \sigma^2 \right)^3 - 20 s^4 \left( \sigma^2 \right)^2 + 32 s^4 \left( \sigma^2 \right) - 16 s^4 = 0.
+\end{align*}
+Since this is a quartic in $\sigma^2$ this can be solved analytically; the (positive) solution is
+\begin{align}
+\label{eq:equilvar}
+\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
+\end{align}
+
+\subsection{Equilibrium Energy}
+From~\eqref{eq:energycond} the equilibrium energy can be found, as well as the equilibrium peak power. This relation can be simplified by squaring both sides and rearranging to give
+\begin{align*}
+\frac{1}{h^2 \zeta} E = W \left( a E \textrm{e}^E \right),
+\end{align*}
+where $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}} = \sqrt{1 - \sigma^2}$. Then, by taking the exponential of each side, and multiplying by the original expression, we obtain
+\begin{align*}
+\frac{1}{h^2 \zeta} E \exp \left(\frac{1}{h^2 \zeta} E \right) &= W \left( a E \textrm{e}^E \right) \exp \left( W \left( a E \textrm{e}^E \right) \right) \\
+&= a E \textrm{e}^E,
+\end{align*}
+by \eqref{eq:lambertw}. Now, this can be written as 
+\begin{align*}
+a h^2 \zeta &= \exp \left( \frac{1}{h^2 \zeta}E - E \right), \\
+\log \left( a h^2 \zeta \right) &= E \left( \frac{1}{h^2 \zeta} - 1 \right).
+\end{align*}
+The energy of the pulse entering the gain fibre at equilibrium is thus
+\begin{align*}
+E = \frac{h^2 \zeta}{1 - h^2 \zeta} \log \left( a h^2 \zeta \right).
+\end{align*}
+***the pulse will converge if the argument of the log is greater than 1***
+The energy of the pulses as it enters the optical coupler can now be found, recall from \eqref{eq:gainde} that the energy is defined as
+\begin{align*}
+E = \int_{-\infty}^\infty |A|^2 \, \df T;
+\end{align*}
+the energy entering the optical coupler is then
+\begin{align}
+\nonumber E_* &= \int_{-\infty}^\infty |G(A)|^2 \, \df T, \\
+\nonumber &= \frac{W(a E \textrm{e}^E)}{E} \int_{-\infty}^\infty |A|^2 \, \df T, \\
+&= W(a E \textrm{e}^E).
+\end{align}
+Since we have previously found the equilibrium shape, we can now find the amplitude of the pulse as well. Again, from \eqref{eq:gainde}, it must be that $E_* = P \sigma \sqrt{\pi}$, or,
+\begin{align}
+P = \frac{W(a E \textrm{e}^E)}{\sigma \sqrt{\pi}}.
+\end{align}

### 2019-01-21 Thesis/Nonlinear/Nonlinear.tex
Told TeXWorks what the main file was
Updated thesis

@@
-\chapter{Nonlinear Solution}
+% !TeX root = ../Thesis.tex
 
-In the linear model, the pulse will converge to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
+\chapter{Solution of the Nonlinear Model}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/Variance}
+\caption{Simulation and analytic equilibrium standard deviation as a function of $s$.}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/LinearPlot}
+\caption{Equilibrium energy and peak power of the pulse as a function of $s$.}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/Stability}
+\caption{}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/StabilityZoom}
+\caption{}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/StabilitySwitch}
+\caption{}
+\label{fig:}
+\end{figure}
+
+\begin{figure}[htbp]
+\centering
+\input{./Figures/StabilitySwitchZoom}
+\caption{}
+\label{fig:}
+\end{figure}
+
+In the linear model, the pulse converges to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
 However, this is not necessarily the case with the inclusion of the nonlinearity.
 The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the laser until the envelope of the pulse becomes mangled.
+These oscillations are then intensified with each trip around the cavity until the envelope of the pulse becomes mangled.
 \\

### 2019-01-21 Lasers.py
Cleaned up file quite a bit

@@ -1,17 +1,29 @@
+##################################################
+#			Brady Metherall
+#			MSc Thesis
+##################################################
+'''
+This is the code used for my MSc thesis. This code
+is separated into four parts each described below.
+'''
+
+###############
+#	Part I
+###############
+'''
+Function definitions and initialization
+'''
+
 import numpy as np
 import scipy.special.lambertw as W
 import matplotlib.pyplot as plt
-import time
+from scipy.optimize import curve_fit
 
+def func(x, a, b):
+	return a * np.exp(-x**2 / (2 * b**2))
+ 
 def Energy(A, dx):
 	return np.trapz(np.real(A * np.conj(A)), dx = dx)
-
-def zeta(s):
-	return np.exp(-0.511444 * s + 0.00174128)
-
-def EE(a, s, h):
-	r = zeta(s)**2 * h**2
-	return r / (1 - r) * np.log(a * r)
 
 # Functions for each component
 def Gain(A, E, a = 8000):
@@ -23,119 +35,152 @@ def Loss(A, h = 0.04):
 def Mod(A, T):
 	return np.exp(-T**2 / 2) * A
 
-def Fibre(A, b = 0.25):
-	return np.exp(1j * b * np.real(np.abs(A)**2)) * A
+def Fibre(A, b = 1.0):
+	return np.exp(1j * b * np.abs(A)**2) * A
 
-def Disp(A, T, s = 0.2):
+def Disp(A, T, s = 0.1):
 	F = np.fft.fft(A)
-	F = (np.abs(F) > 10**-4) * F
+	F = F * (np.abs(F) > 10**-4) # Numerical stability
 	dw = np.pi / T[-1]
 	w = np.fft.fftfreq(len(A)) * len(A) * dw
-	return np.fft.ifft(F * np.exp(1j * (w**2 * s**2 - 0 * s**2 * w**3)))
+	return np.fft.ifft(F * np.exp(1j * w**2 * s**2)))
 
 # 1 round trip
-def Loop(A0, T, dx, s, b):
-	A = A0
-	A = Gain(A0, Energy(A0, dx))
-	#A = Fibre(A, b)
+def Loop(A, T, dx, s, b, switch = False):
 	A = Loss(A)
[…]

### 2019-01-23 Thesis/Appendices/Dispersion.tex
Made some edits

@@
 \chapter{Spread Due to Dispersion}
+\label{chap:disp}
 
-\cite{integrals}
+The effect of dispersion can be computed analytically for several input pulses using ***. In the case of a Gaussian pulse, we make use of the transforms \cite{integrals}
+\begin{align*}
+\FT{\textrm{e}^{-\eta T^2}} &= (2 \eta)^{-1/2}\textrm{e}^{-\omega^2/4\eta},& \FTi{\textrm{e}^{-\eta \omega^2}} &= (2 \eta)^{-1/2}\textrm{e}^{-T^2/4\eta}.
+\end{align*}
+From *** we have that
+\begin{align*}
+D \left( \textrm{e}^{-\eta T^2} \right) &=\FTi{\textrm{e}^{i s^2 \omega^2} \FT{\textrm{e}^{-\eta T^2}}}, \\
+&= (2 \eta)^{-1/2} \FTi{\exp \left( -\omega^2 \left( \frac{1}{4\eta} - i s^2 \right) \right)}, \\
+&= (1 - 4 i \eta s^2)^{-1/2} \exp \left( -T^2 \frac{a}{1 - 4 i s^2 \eta} \right).
+\end{align*}
+For us, $\displaystyle \eta = \frac{1}{2} \frac{1 + i C}{\sigma^2}$; making this substitution yields
+\begin{align*}
+D \left( \Gamma \right) &= \left( 1 + \frac{2C s^2}{\sigma^2} - \frac{2s^2}{\sigma^2}i \right)^{-1/2} \exp \left( -T^2 \frac{1 + i C}{2\sigma^2 - 4 i s^2 (1 + i C)} \right),
+\end{align*}
+where $\displaystyle \Gamma = \exp \left( -T^2 \frac{1 + iC}{2 \sigma^2} \right)$. This can be greatly simplified by first rationalizing the denominators to give
+\begin{align*}
+D \left( \Gamma \right) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right),
+\end{align*}
+and then by writing in polar / rectangular coordinates:
+\begin{multline*}
+D \left( \Gamma \right) = \left( \left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{\frac{2s^2}{\sigma^2}}{1 + \frac{2C s^2}{\sigma^2}} \right) \right) \\
+\times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
+\end{multline*}
+Finally, this can be simplified further to
+\begin{multline*}
+D \left( \Gamma \right) = \sigma \left( \left( \sigma^2 + 2C s^2 \right)^2 + 4s^4 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right) \right) \\
+\times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
+\end{multline*}
+From this expression it is clear that at equilibrium
+\begin{align*}
+\widetilde{\sigma}^2 \sigma^2 &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4s^4, \\
+\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2}, \\
+\phi &= \frac{1}{2} \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right), \\
+\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
+\end{align*}
+
+The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, silfvast, ferreira}
+\begin{align*}
+\left( \frac{T_1}{T_0} \right)^2 &= \left( 1 + \frac{C \beta_2 z}{T_0^2} \right)^2 + \left( \frac{ \beta_2 z}{T_0^2} \right)^2,&
+\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2}.
+\end{align*}
+Where, within our non-dimensionalization, $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, $z = L_D$, and $\beta_2 z T_0^{-2} = 2s^2\sigma^{-2}$.
+In addition to this, the expression for $\zeta$ can be validated using conservation of energy.
+Within the CFBG energy is conserved, therefore,
+\begin{align*}
+\int_{-\infty}^\infty |A_1|^2 \, \df T &= \int_{-\infty}^\infty |A_2|^2 \, \df T.
+\end{align*}
+Which, after substituted the expressions from Section \ref{sec:linear}, reduces to
+\begin{align*}
+h^2 P \int_{-\infty}^\infty \textrm{e}^{-T^2/\sigma^2} \, \df T &= h^2 P \zeta \int_{-\infty}^\infty \textrm{e}^{-T^2/\widetilde{\sigma}^2} \, \df T.
+\end{align*}
+These expressions are easily integrated to show that $\sqrt{\pi \sigma^2} = \sqrt{\pi \widetilde{\sigma}^2} \zeta^2$, and finally that
+\begin{align*}
+\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
+\end{align*}

### 2019-01-23 Thesis/Appendices/Lambert.tex
Made some edits

@@
 Notice that the original function, $f(x) = x \textrm{e}^x$, is \emph{not} injective, and as a consequence, the $W$ function is multi-valued on the interval $[-1/\textrm{e},0)$.
-To alleviate this, sometimes the branch $W(x) \geq -1$ is denoted $W_0$ and is called the upper or principal branch, whereas the branch $W(x) < -1$ is denoted $W_{-1}$ and is called the lower branch.
+To alleviate this, occasionally the branch $W(x) \geq -1$ is denoted $W_0$ and is called the principal or upper branch, whereas the branch $W(x) < -1$ is denoted $W_{-1}$ and is called the lower branch.
 However, in this work the $W$ function will only take positive real values and so this distinction is not needed.
@@
 \end{itemize}
-Primarily, the $W$ function is used when solving iterated exponentiation, and solving certain algebraic equations.
-For example, consider the equation $z = x^x$.
-By taking the logarithm of each side we have
+Primarily, the $W$ function arises when solving iterated exponentiation or certain algebraic equations. For example, consider the equation $z = x^x$. By taking the logarithm of each side we have
 \begin{align*}
@@
 \end{align*}
-which after applying the $W$ function reduces to $W(\log z) = \log x$ by \eqref{eq:lambertw}. Finally, the answer can be written as $x = \exp(W(\log z))$.
+which after applying the $W$ function reduces to $W(\log z) = \log x$ by \eqref{eq:lambertw}. Finally, $x$ as a function of $z$ can be written as $x = \exp(W(\log z))$.

### 2019-01-23 Thesis/Model/Model.tex
Made some edits

@@
 Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
+\begin{align*}
+\pdiff{A}{z} &= \frac{1}{2} g(A),
+\end{align*}
+where $g(A)$ takes the form \cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina, peng}
 \begin{align}
 \label{eq:gainde}
-	\pdiff{A}{z} &= \frac{1}{2} \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
+	g(A) &= \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate~\cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina, peng}.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate.
 %We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
@@
 \begin{align*}
-	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es}.
+	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es},
 \end{align*}
-Adding this to its complex conjugate and integrating over $T$ gives
+adding this to its complex conjugate and integrating over $T$ gives
 %\begin{align*}
@@
 \end{align}
-For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the energy grows linearly.
-To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assume the energy increases from $E$ to $E_{\textrm{out}}$ so that
+For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the growth is linear.
+To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assuming the energy increases from $E$ to $E_{\textrm{out}}$, then
 \[
@@
 \]
-and by exponentiating, rearranging, and applying $W$, the Lambert $W$ function (See Appendix \ref{chap:lambertw}),
-\[
-	 W\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) = 
-	 W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es}.
-\]
-This results in the closed form expression
-\begin{align}
-\label{eq:energy}
+and by exponentiating, rearranging, and applying $W$, the Lambert $W$ function\footnote{see Appendix \ref{chap:lambertw}},
+\begin{align*}
+W\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) \\
+&= \frac{E_{\textrm{out}}}{\Es},
+\end{align*}
+by \eqref{eq:lambertw}. This results in the closed form expression
+\begin{align*}
 E_{\textrm{out}}(z) = \Es W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
-\end{align}
-with the desired property that $E_{\textrm{out}}(0)=E$. Since $E \sim |A|^2$, the gain in terms of the amplitude is given by
-\begin{align}
-	\label{eq:gain}
-	G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} 
-	\textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
-\end{align}
+\end{align*}
+with the desired property that $E_{\textrm{out}}(0)=E$. Furthermore, since $E \sim |A|^2$, the gain in terms of the amplitude is given by
+\begin{align*}
+G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
+&= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
+\end{align*}
 where $L_g$ is the length of the gain fibre.
@@
 \subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre depends on the parameter $\gamma$. In regions where this affect is dominant expression~\eqref{eq:nlse} becomes
+The nonlinearity of the fibre arises from the parameter $\gamma$; in regions where this affect is dominant expression~\eqref{eq:nlse} becomes
 \begin{align}
 \label{eq:fibrediff}
-	\pdiff{A}{z} - i \gamma |A|^2 A = 0,
+	\pdiff{A}{z} - i \gamma |A|^2 A = 0.
 \end{align}
-so that $\frac{\partial}{\partial z} |A|^2 = 0$ suggesting that $A(T,z) = A_0(T) e^{i \phi(T,z)}$.
-Substituting this representation into~\eqref{eq:fibrediff} and setting $\phi(T,0)=0$ gives $\phi(T,z) = \gamma |A|^2 z$.
-For a fibre of length $L_f$ the effect of the nonlinearity is therefore
-\begin{align}
-\label{eq:fibre}
+This expression can be manipulated to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
+Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives $\varphi(T,z) = \gamma |A|^2 z$.
+For a fibre of length $L_f$ the effect of the nonlinearity is thus
+\begin{align*}
 F(A) &= A e^{i \gamma |A|^2 L_f}.
-\end{align}
+\end{align*}
 
@@
 Combining these two effects give a loss that takes the form
-\begin{align}
-\label{eq:fibreloss}
-	L(A) &= R e^{- \alpha L}A,
-\end{align}
+\begin{align*}
+L(A) &= (1 - R) e^{- \alpha L}A,
+\end{align*}
 where $R$ is the reflectivity of the output coupler, and $L$ is the total length of the laser circuit.
@@
 \end{align}
-and since dispersion acts in the frequency domain, it is convenient to use the Fourier transform of~\eqref{eq:disp}, giving the result that
+and since dispersion acts in the frequency domain, it is convenient to take the Fourier transform of~\eqref{eq:disp}, giving
 \begin{align*}
@@
 The effect of dispersion is then
-\begin{align}
-\label{eq:dispersion}
+\begin{align*}
 D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
-\end{align}
+\end{align*}
 For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
@@
 In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
-In the new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
-\begin{align}
+In this new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
+\begin{align*}
 M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
-\end{align}
-where $T_M$ is a characteristic width of the modulation.%\footnote{Taking the Fourier transform, $\FT{\textrm{e}^{-T^2/ 2 T_M^2}} = \frac{1}{\sqrt{2\pi}}T_M\textrm{e}^{-\omega^2T_M^2/2}$.}
+\end{align*}
+where $T_M$ is a characteristic width of the modulation.
 
@@
 \noalign{\global\arrayrulewidth=1.5pt}\hline
+Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, yarutkina, shtyrina} \\
+Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{burgoyne2014, agrawal2013, yarutkina, litchinitser, peng} \\
+Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, yarutkina} \\
+Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{burgoyne2014, agrawal2013, shenping, agrawal2002} \\
+Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
+Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
+Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, shtyrina, yarutkina, peng} \\
+Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{burgoyne2014, burgoyneemail, bohun} \\
+Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
 Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, yarutkina} \\
-Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, yarutkina} \\
 Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
-Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{burgoyne2014, agrawal2013, shenping, agrawal2002} \\
-Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{burgoyne2014, agrawal2013, yarutkina, litchinitser, peng} \\
-Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{burgoyne2014, burgoyneemail, bohun} \\
-Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
-Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, shtyrina, yarutkina, peng} \\
-Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
-Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
-Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, yarutkina, shtyrina} \\
 \hline
@@
 The new process maps, after dropping the tildes, become
-\begin{align*}
-	G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A,&
-	F(A) &= A \textrm{e}^{i b |A|^2},&
+\begin{subequations}
+\begin{align}
+G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, \\
+F(A) &= A \textrm{e}^{i b |A|^2}, \\
 M(A) &= \textrm{e}^{-T^2 / 2} A, \\
-	D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}},&
+D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, \\
 L(A) &= h A,
-\end{align*}
+\end{align}
+\end{subequations}
 with four dimensionless parameter groups (see Table~\ref{tab:values})
 \begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,&
+	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2, \\
 	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04,
@@
 In this model the pulse is iteratively passed through each process, the order of which is now important.
-We are most interested in the output of the laser cavity, and so we shall start with the loss component---what enters the optical coupler.
+We are most interested in the output of the laser cavity, and so we shall start with the loss component.
 Next the pulse is passed though the CFBG, as well as the modulator.
@@
 where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A$---potentially with a constant phase shift.
+A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
 
 \section{Solution to the Linear Model}
-Since the pulse is modulated by a Gaussian, it is expected that the equilibrium envelope will also be a Gaussian. Consider the initial pulse
+\label{sec:linear}
+In the case of $b = 0$---which shall be referred to as the linear model---a solution can be found analytically.
+It is expected the solution will take the form of a Gaussian.
+There are a few reasons for this; the solution to the average model is a Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function ***, and since a Gaussian is a fixed point of the Fourier transform \cite{integrals} dispersion will not alter the envelope.
+\\
+
+Consider the initial pulse
 \begin{align*}
-	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right),
+	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \textrm{e}^{i \phi_0},
 \end{align*}
-where $P$ is the peak power.
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
 After passing though the optical coupler the pulse will simply decay, $A_1 = h A_0$.
@@
 \begin{align*}
-A_2 = \sqrt{P} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right),
+A_2 = \sqrt{P} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right) \textrm{e}^{i(\phi_0 + \phi)},
 \end{align*}
-where $\widetilde{\sigma}^2$ denotes the resulting variance, and $\widetilde{C}$ denotes the resulting chirp. Next, the pulse is modulated:
+where $\widetilde{\sigma}^2$ denotes the resulting variance, $\widetilde{C}$ denotes the resulting chirp, and $\zeta$ is the reduction of the amplitude caused by dispersion.
+Next, the pulse is modulated:
 \begin{align*}
-A_3 = \sqrt{P} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right).
+A_3 = \sqrt{P} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right) \textrm{e}^{i(\phi_0 + \phi)}.
 \end{align*}
@@
 \begin{align*}
-A_4 = \sqrt{P} \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2} \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right),
+A_4 = \sqrt{P} \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right) \textrm{e}^{i(\phi_0 + \phi)},
 \end{align*}
@@
 
-In equilibrium, it must be that $A_0 = A_4 \textrm{e}^{i \varphi}$, for some $\varphi$. More explicitly, this gives three conditions:
+In equilibrium it must be that $A_0 = A_4 \textrm{e}^{-i \phi}$. More explicitly, this gives three conditions:
 \begin{subequations}
@@
 \label{eq:energycond}
-1 &= \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}, \\
+1 &= \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta, \\
 \label{eq:varcond}
@@
 \subsection{Equilibrium Shape}
-After dispersion, the out-going variance $\widetilde{\sigma}$ can be found by computing the effect of dispersion given by ***. In the case of a Gaussian pulse \cite{agrawal2013} we have
-\begin{align*}
-\left( \frac{T_1}{T_0} \right)^2 &= \left( 1 + \frac{C \beta_2 z}{T_0^2} \right)^2 + \left( \frac{ \beta_2 z}{T_0^2} \right)^2,&
-\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2}
-\end{align*}
-where $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, $z = L_D$, and $\beta_2 z T_0^{-2} = 2s^2\sigma^{-2}$ within our non-dimensionalization. Making these substitutions yields the relations
+Each of these processes has a relatively straight forward effect, with the exception of dispersion.
+After dispersion, the out-going variance $\widetilde{\sigma}^2$ can be found by computing the effect of dispersion given by ***.
+This yields the relations
 \begin{subequations}
@@
 \label{eq:chirpout}
-\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2},
+\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2}, \\
+\label{eq:phase}
+\phi &= \frac{1}{2} \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right), \\
+\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}
 \end{align}
 \end{subequations}
-for the variance and chirp after the dispersive element. Now, the out-going variance and chirp can be eliminated from this system of equations using \eqref{eq:varcond} and \eqref{eq:chirpcond}:
+for the variance, chirp, and phase shift after the dispersive element, the full details can be found in Appendix \ref{chap:disp}.
+Now, the out-going variance and chirp can be eliminated from this system of equations using \eqref{eq:varcond} and \eqref{eq:chirpcond}:
 \begin{align*}
@@
 \begin{align*}
-C \frac{1}{1 - \sigma^2} &= C + (1 + C^2) \frac{2s^2}{\sigma^2} \\
+C \frac{1}{1 - \sigma^2} &= C + (1 + C^2) \frac{2s^2}{\sigma^2}, \\
 1 + C^2 &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} C.
@@
 \end{align*}
-Notice that the left hand side of this expression is strictly positive ($\sigma$ is strictly less than $1$ at equilibrium), therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
+Notice that the left hand side of this expression is strictly positive ($\sigma$ is strictly less than $1$ at equilibrium ***), therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
 After squaring each side of this expression we obtain
@@
 \end{align*}
-Since this is a quartic in $\sigma^2$ this can be solved analytically; the (positive) solution is
+Since this is a quartic in $\sigma^2$ this can be solved analytically; the (positive, real) solution is
 \begin{align}
@@
 \begin{align*}
-\frac{1}{h^2 \zeta} E = W \left( a E \textrm{e}^E \right),
+\frac{1}{h^2 \zeta^2} E = W \left( a E \textrm{e}^E \right).
 \end{align*}
-where $\displaystyle \zeta \equiv \frac{\sigma}{\widetilde{\sigma}} = \sqrt{1 - \sigma^2}$. Then, by taking the exponential of each side, and multiplying by the original expression, we obtain
+Then, by taking the exponential of each side, and multiplying by the original expression, we obtain
 \begin{align*}
-\frac{1}{h^2 \zeta} E \exp \left(\frac{1}{h^2 \zeta} E \right) &= W \left( a E \textrm{e}^E \right) \exp \left( W \left( a E \textrm{e}^E \right) \right) \\
+\frac{1}{h^2 \zeta^2} E \exp \left(\frac{1}{h^2 \zeta^2} E \right) &= W \left( a E \textrm{e}^E \right) \exp \left( W \left( a E \textrm{e}^E \right) \right) \\
 &= a E \textrm{e}^E,
@@
 \begin{align*}
-a h^2 \zeta &= \exp \left( \frac{1}{h^2 \zeta}E - E \right), \\
-\log \left( a h^2 \zeta \right) &= E \left( \frac{1}{h^2 \zeta} - 1 \right).
+a h^2 \zeta^2 &= \exp \left( \frac{1}{h^2 \zeta^2}E - E \right), \\
+\log \left( a h^2 \zeta^2 \right) &= E \left( \frac{1}{h^2 \zeta^2} - 1 \right).
 \end{align*}
@@
 \begin{align*}
-E = \frac{h^2 \zeta}{1 - h^2 \zeta} \log \left( a h^2 \zeta \right).
+E = \frac{h^2 \zeta^2}{1 - h^2 \zeta^2} \log \left( a h^2 \zeta^2 \right).
 \end{align*}

### 2019-01-23 Thesis/Nonlinear/Nonlinear.tex
Made some edits

@@
 \chapter{Solution of the Nonlinear Model}
+\section{Code}
+With the inclusion of the nonlinearity ($b > 0$) the model becomes too difficult to solve analytically, and we must resort to solving it numerically.
+
+Appendix \ref{chap:code}
+
+\subsection{Validation}
+The code can be validated by comparing to the results of the linear model.
 
@@
 \input{./Figures/Variance}
-\caption{Simulation and analytic equilibrium standard deviation as a function of $s$.}
+\caption{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.}
 \label{fig:}
@@
 \end{figure}
+
+\section{Nonlinear Model}
 

### 2019-02-11 Thesis/Figures/CFBG.tex
Added script for plots
Added/updated figures

@@
 \begin{tikzpicture}
+% CFBG
 \draw (4,0) -- (12,0) -- (12,4) -- (4,4) -- cycle;
@@
 %  \draw [dashed] (12 - 1/18*\i*\i,4) -- (12 - 1/18*\i*\i,8);
+% Waves
 \draw [domain=0:(12-16/18), samples=1000, blue, thick] plot (\x, {-0.5*cos(4*pi*(\x-(12-25/18)) r) + 3});
-\draw [domain=0:(12-81/18), samples=500, red, thick] plot (\x, {0.5*cos(2*pi*36/38*(\x-(12-100/18)) r) + 1});
+\draw [domain=0:(12-81/18), samples=500, red, thick, densely dashed] plot (\x, {0.5*cos(2*pi*36/38*(\x-(12-100/18)) r) + 1});
 
-\draw [thick, decoration={brace, mirror, raise=0.2cm}, decorate] (7.5,0) -- (100/9,0)
+% Labels
+\draw [thick, decorate, decoration={brace, mirror, raise=0.2cm, amplitude=10pt}] (7.5,0) -- (100/9,0)
 node [pos=0.5,anchor=north,yshift=-0.5cm] {Time Delay};
-\draw [thick, decoration={brace, mirror, raise=0.2cm}, decorate] (12,0) -- (12,4)
+\draw [thick, decorate, decoration={brace, mirror, raise=0.2cm, amplitude=10pt}] (12,0) -- (12,4)
 node [pos=0.5,anchor=west,xshift=0.5cm] {CFBG};
 
+% Index of refraction
 \draw [->] (4,5) -- (12.5,5)

### 2019-02-11 Thesis/Figures/Hologram.tex
Added/updated figures

% !TeX root = ../Thesis.tex

\begin{tikzpicture}

\draw[pattern=north east lines, pattern color=blue] (-4,0.5) rectangle (4,1); % Top Insulation
\draw[pattern=north west lines, pattern color=blue] (-4,-0.5) rectangle (4,-1); % Bottom Insulation
\draw[pattern=mydots, pattern color=OliveGreen] (-4,-0.5) rectangle (4,0.5); % Core

\foreach \i in {0,...,3}{
  % Rays
  \draw[->, >=stealth, magenta, thick] (-2.25 + \i,4.5) -- (-1.25 + \i,-1.5);
  \draw[->, >=stealth, magenta, thick] (-0.75 + \i,4.5) -- (-1.75 + \i,-1.5);
}
% Labels
\draw[->, >=stealth, thick] (3,-1.5) -- (2,0) node[pos=-0.2] {Ge Doped Core};
\draw[->, >=stealth, thick] (-3,-1.5) -- (-2,-0.75) node[pos=-0.3] {Cladding};
\draw[->, >=stealth, thick] (-3,2.5) -- (-1.82,2) node[pos=-0.4] {UV Light};
\end{tikzpicture}

### 2019-02-11 Thesis/Appendices/Dispersion.tex
Edited appendices

@@
 
-The effect of dispersion can be computed analytically for several input pulses using ***. In the case of a Gaussian pulse, we make use of the transforms \cite{integrals}
+The effect of dispersion can be computed analytically for several input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{gradshteyn}
 \begin{align*}
@@
 \end{align*}
-From *** we have that
+From \eqref{eq:disp} we have that
 \begin{align*}
@@
 \begin{align*}
-D \left( \Gamma \right) &= \left( 1 + \frac{2C s^2}{\sigma^2} - \frac{2s^2}{\sigma^2}i \right)^{-1/2} \exp \left( -T^2 \frac{1 + i C}{2\sigma^2 - 4 i s^2 (1 + i C)} \right),
+D(A_1) &= \left( 1 + \frac{2C s^2}{\sigma^2} - \frac{2s^2}{\sigma^2}i \right)^{-1/2} \exp \left( -T^2 \frac{1 + i C}{2\sigma^2 - 4 i s^2 (1 + i C)} \right).
 \end{align*}
-where $\displaystyle \Gamma = \exp \left( -T^2 \frac{1 + iC}{2 \sigma^2} \right)$. This can be greatly simplified by first rationalizing the denominators to give
+This can be greatly simplified by first rationalizing the denominators to give
 \begin{align*}
-D \left( \Gamma \right) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right),
+D(A_1) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right),
 \end{align*}
@@
 \begin{multline*}
-D \left( \Gamma \right) = \left( \left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{\frac{2s^2}{\sigma^2}}{1 + \frac{2C s^2}{\sigma^2}} \right) \right) \\
+D(A_1) = \left( \left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{\frac{2s^2}{\sigma^2}}{1 + \frac{2C s^2}{\sigma^2}} \right) \right) \\
 \times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
@@
 \begin{multline*}
-D \left( \Gamma \right) = \sigma \left( \left( \sigma^2 + 2C s^2 \right)^2 + 4s^4 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right) \right) \\
+D(A_1) = \sigma \left( \left( \sigma^2 + 2C s^2 \right)^2 + 4s^4 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right) \right) \\
 \times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
@@
 
-The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, silfvast, ferreira}
+The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, ferreira, silfvast}
 \begin{align*}
@@
 \end{align*}
-Which, after substituted the expressions from Section \ref{sec:linear}, reduces to
+Which, after substituting the expressions from Section \ref{sec:linear}, reduces to
 \begin{align*}

### 2019-02-11 Thesis/Intro/Introduction.tex
Started writing into

@@
 
-\section{Tuneable Lasers}
-
-\section{CFBG}
-
-\section{Previous Modelling Efforts}
-
-\section{Chirp}
-
-\section{GNLSE}
-
-Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
+%Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
 Tuneable lasers on the other hand, have the ability to operate within a range of wavelengths \cite{bohun, burgoyne2010, yamashita}.
@@
 
-To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform described by an effective PDE, the solution of which gives the amplitude of the wave packet.
-
-\begin{figure}[htbp]
-\centering
-\input{./Figures/CFBG}
-\label{fig:cfbg}
-\caption[Chirped Fibre Bragg Grating]{Chirped fibre Bragg grating schematic.}
-\end{figure}
-
+\section{Tuneable Lasers}
 \begin{figure}[htbp]
@@
 \input{./Figures/Cavity}
+\caption[Laser Cavity]{Laser cavity schematic.}
 \label{fig:cavity}
-\caption[Laser Cavity]{Laser cavity schematic.}
 \end{figure}
+
+\subsection{Gain and Pump}
+
+\subsection{Optical Coupler}
+
+\subsection{Modulator}
+
+\subsection{Fibre Bragg Grating}
+A fibre Bragg grating (FBG) is an optical fibre where the refractive index varies periodically along its length \cite{ferreira}.
+To achieve this, typically silica fibres are doped with Germanium, which when exposed to intense ultraviolet (UV) light alter the refractive index of the core \cite{starodoumov}.
+The photosensitivity of the optical fibres can be increased by more than an order of magnitude by the Germanium doping \cite{ferreira}.
+\\
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}{\textwidth}
+\centering
+\input{./Figures/PhaseMask}
+\caption{\textbf{Phase-Mask:} The phase-mask focuses the ultraviolet light onto the centre of the core causing periodic constructive and destructive interference.}
+\label{fig:phasemask}
+\vspace{10mm}
+\end{subfigure}
+\begin{subfigure}{\textwidth}
+\centering
+\input{./Figures/Hologram}
+\caption{\textbf{Holographic Side Exposure:} Two incident ultraviolet waves cause periodic constructive and destructive interference at the centre of the core.}
+\label{fig:holographic}
+\end{subfigure}
+\caption{Depictions of the two methods for manufacturing FBGs.}
+\label{fig:fbgmake}
+\end{figure}
+
+FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
+Both methods cause the periodic nature of the refractive index through interference.
+In the phase-mask method (Figure \ref{fig:phasemask}) a single beam of UV light passes through the phase-mask which acts as a series of lenses focusing the light at the core---this causes a sinusoidal interference pattern.
+Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of UV light are instead used to create the interference pattern.
+\\
+
+The purpose of FBGs is that they act as reflective filters \cite{agrawal2002, alazzawi, ferreira, starodoumov}.
+Due to the periodicity of the refractive index, light with the corresponding wavelength will be reflected, with all others passing through.
+This wavelength is defined by the Bragg condition \cite{agrawal2002, alazzawi, ferreira, silfvast, starodoumov}:
+\begin{align}
+\label{eq:bragg}
+\lambda_B = 2 \Lambda \bar{n},
+\end{align}
+where $\lambda_B$ is the Bragg wavelength, $\Lambda$ is the period of the grating, and $\bar{n}$ is the average index of refraction.
+This reflects wavelengths close to $\lambda_B$, known as the stop-band.
+In this way, FBGs as be used as filters.
+\\
+
+\subsubsection{Chirped Fibre Bragg Grating}
+\begin{figure}[tbp]
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Unchirped}
+\caption{Unchirped Gaussian pulse.}
+\label{fig:unchirped}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Chirped}
+\caption{Linearly chirped Gaussian pulse.}
+\label{fig:chirped}
+\end{subfigure}
+\caption{In a unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.}
+\label{fig:chirp}
+\end{figure}
+
+Chirp is simply the term for a signal that has a non-constant frequency across it.
+Figure \ref{fig:chirp} shows examples of chirped and unchirped Gaussian pulses---the most common type of chirp is linear chirp, where the frequency varies linearly across the pulse.
+By using a chirped phase-mask a chirped fibre Bragg grating (CFBG) can be created.
+Since the period of the refractive index varies across the CFBG, so does when the Bragg condition, \eqref{eq:bragg}, is satisfied.
+This causes most wavelengths to be reflected by a CFBG, but with each wavelength penetrating to a different depth.
+A consequence of this is that a time delay is caused between wavelengths---this is depicted in Figure \ref{fig:cfbg} with the upper portion showing  the refractive index as a function of the depth.
+In this orientation, the red (dashed) wave is unable to penetrate as far as the blue (solid) wave since each wave is reflected where it matches the frequency of the refractive index.
+\\
+
+\begin{figure}[tbp]
+\centering
+\input{./Figures/CFBG}
+\caption[CFBG]{CFBG}
+\label{fig:cfbg}
+\end{figure}
+
+The speed of light in an optical fibre is slightly dependent on the wavelength---this causes light with a longer wavelength to travel faster, and is known as chromatic dispersion.
+This is a large problem in fibre optic communications, the signal can spread and potentially becomes uninterpretable after large distances.
+However, chromatic dispersion can be counteracted using a CFBG \cite{agrawal2002, alazzawi, starodoumov} (in the opposite orientation of Figure \ref{fig:cfbg}).
+By forcing the longer wavelengths to travel farther the dispersion can be reversed, restoring the original signal\footnote{A $10$ cm CFBG can compensate the dispersion of $300$ km of fibre~\cite{agrawal2002}.}.
+However, in our case, we wish to accelerate the dispersion, simulating hundreds of metres of fibre, so the CGBG is used in the orientation shown in Figure \ref{fig:cfbg}.
+\\
+
+\subsection{Optical Circulator}
+\begin{wrapfigure}{O}{0.5\textwidth}
+\centering
+\input{./Figures/Circulator}
+\caption[Optical Circulator]{Symbol for a four port optical circulator.}
+\label{fig:circulator}
+\end{wrapfigure}
+%\begin{figure}[htbp]
+%\centering
+%\input{./Figures/Circulator}
+%\caption[Optical Circulator]{Symbol for a four port optical circulator.}
+%\label{fig:circulator}
+%\end{figure}
+An optical circulator is an optical device that routes signals from port to port in a circular fashion \cite{agrawal2002, alazzawi}, the symbol for a four port optical circulator is shown in Figure \ref{fig:circulator}.
+A signal entering from port 1 will be outputted from port 2; a signal entering from port 2 will exit from port 3; and so forth.
+Typically, optical circulators have three or four ports, with the first port being input only, and the final port being output only \cite{alazzawi}.
+Optical circulators are most commonly used with devices that reflect signals instead of transmit them.
+For example, a signal may enter through port 1, exit through port 2, be reflected by an FBG, re-enter port 2, and finally exit through port 3.
+
+\section{Generalized Nonlinear Sch\"odinger Equation}
+The standard equation for studying nonlinear optics is the generalized nonlinear Schr\"odinger equation (GNLSE) \cite{agrawal2013, burgoyne2007, ferreira, peng, shtyrina, yarutkina},
+\begin{align}
+\label{eq:nlse}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A.
+\end{align}
+Here, $A$ is the complex pulse amplitude, $\beta_2$ and $\beta_3$ are the second-order dispersion or group delay dispersion and third-order dispersion, respectively.
+$\gamma$ is the coefficient of nonlinearity, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption.
+\\
+
+This equation can be derived from the nonlinear wave equation, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
+Within the derivation comoving coordinates are used so that the reference frame propagates with the group velocity.
+This is achieved with the substitution
+\begin{align*}
+T = t - \frac{z}{v_g}.
+\end{align*}
+
+The GNLSE takes the same form as the Schr\"odinger equation with the inclusion of the cubic nonlinear term, hence its name.
+For this reason, it is sometimes referred to as the cubic nonlinear Schr\"odinger equation.
+For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this makes the addition of a quintic term to incorporate nonlinearities associated with such large powers.
+Furthermore, the $\beta$ terms come from a Taylor expansion of the wavenumber, that is,
+\begin{align*}
+k(\omega) &= k_0 + \pdiff{k}{\omega}(\omega - \omega_0) + \frac{1}{2} \pdiff[2]{k}{\omega}(\omega - \omega_0)^2 + \frac{1}{6} \pdiff[3]{k}{\omega}(\omega - \omega_0)^3 + \dots, \\
+&= \phi + \frac{1}{v_g}(\omega - \omega_0) + \frac{1}{2}\beta_2 (\omega - \omega_0)^2 + \frac{1}{6}\beta_3 (\omega - \omega_0)^3 + \dots,
+\end{align*}
+where $\phi$ is the phase shift, and $v_g$ is the group velocity.
+Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth \cite{agrawal2013}.
+
+\section{Previous Modelling Efforts}
+%To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
+The idea is to capture some of the physical elements in the waveform described by an effective PDE, the solution of which gives the amplitude of the wave packet.

### 2019-02-11 Thesis/Model/Model.tex
Edited model chapter, this is done for now

@@
 \chapter{A New Model}
-Rather than using transfer functions with a linear PDE, we instead return to the generalized nonlinear Schr\"odinger equation~\cite{agrawal2013, ferreira, shtyrina, yarutkina, burgoyne2007, peng} 
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align}
-to represent the waveform.
-In this expression, $\beta_3$ is the third order dispersion coefficient, $\gamma$ is the coefficient of nonlinearity or self-phase modulation, $g(A)$ is the gain, and $\alpha$ is the loss of the fibre.
-Using this expression as a starting point, the laser cavity is assumed to be composed of five independent processes---gain, nonlinearity, loss, dispersion, and modulation.
-Within each component of the laser cavity the other four processes are assumed to be negligible, that is, each process is dominant only within one part of the laser, just as with the discrete model, but embracing any nonlinearities.
-
 \section{Components}
@@
 \subsection{Gain}
-Considering the gain term as dominant as is expected with the Er-doped gain fibre, equation~\eqref{eq:nlse} reduces to
-\begin{align*}
-\pdiff{A}{z} &= \frac{1}{2} g(A),
-\end{align*}
-where $g(A)$ takes the form \cite{bohun, burgoyne2014, shtyrina, silfvast, yarutkina, peng}
+Within the Er-doped gain fibre, the gain term is dominant, and equation~\eqref{eq:nlse} reduces to
 \begin{align}
 \label{eq:gainde}
+\pdiff{A}{z} &= \frac{1}{2} g(A),
+\end{align}
+where $g(A)$ takes the form \cite{bohun, burgoyne2014, peng, shtyrina, silfvast, yarutkina}
+\begin{align}
+\label{eq:energy}
 	g(A) &= \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse and $\Es$ is the energy at which the gain begins to saturate.
-%We shall first transform \eqref{eq:gainde} into an equation in terms of the energy. 
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate.
 Multiplying~\eqref{eq:gainde} by $\bar{A}$, the complex conjugate of $A$, yields
 \begin{align*}
-	2\bar{A} \pdiff{A}{z} = \frac{g_0 |A|^2}{1 + E / \Es},
+	\bar{A} \pdiff{A}{z} = \frac{1}{2}\frac{g_0 |A|^2}{1 + E / \Es},
 \end{align*}
@@
 To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assuming the energy increases from $E$ to $E_{\textrm{out}}$, then
-\[
-	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es}
-\]
+\begin{align*}
+	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es},
+\end{align*}
 and by exponentiating, rearranging, and applying $W$, the Lambert $W$ function\footnote{see Appendix \ref{chap:lambertw}},
@@
 \end{align}
-This expression can be manipulated to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
+This expression can be manipulated in a similar manner to the gain to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
 Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives $\varphi(T,z) = \gamma |A|^2 z$.
@@
 \subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the chirped fibre Bragg grating (CFBG).
-In comparison, the dispersion due to the fibre is negligible\footnote{A $10$ cm chirped grating can provide as much dispersion as $300$ km of fibre~\cite{agrawal2002}.}.
-The dispersive terms of \eqref{eq:nlse} give
+Within the laser cavity, the dispersion is dominated by the CFBG. In comparison, the dispersion due to the fibre is negligible. The dispersive terms of \eqref{eq:nlse} give
 \begin{align}
-\label{eq:disp}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T}
+\label{eq:dispde}
+	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T},
 \end{align}
-and since dispersion acts in the frequency domain, it is convenient to take the Fourier transform of~\eqref{eq:disp}, giving
+and since dispersion acts in the frequency domain it is convenient to take the Fourier transform of~\eqref{eq:dispde} \cite{gradshteyn}, giving
 \begin{align*}
@@
 For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity in the basic model and because of the nature of the grating, the third order effect will be neglected so we set $\beta_3=0$ for the subsequent analysis~\cite{agrawal2013, ferreira}.
+However, for simplicity and because of the nature of the grating, the third order effects will be neglected \cite{agrawal2013, ferreira}---we set $\beta_3=0$ for the subsequent analysis.
 
@@
 \noalign{\global\arrayrulewidth=1.5pt}\hline
-Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, yarutkina, shtyrina} \\
-Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{burgoyne2014, agrawal2013, yarutkina, litchinitser, peng} \\
+Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, yarutkina} \\
+Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
 Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, yarutkina} \\
-Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{burgoyne2014, agrawal2013, shenping, agrawal2002} \\
+Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
 Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
 Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
-Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, shtyrina, yarutkina, peng} \\
-Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{burgoyne2014, burgoyneemail, bohun} \\
+Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, yarutkina} \\
+Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyne2014, burgoyneemail} \\
 Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
@@
 The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is proportional to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
+Specifically, the time shall be scaled by the characteristic modulation time which is related to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
 \begin{align*}
@@
 \begin{align}
+\label{eq:gain}
 G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, \\
+\label{eq:fibre}
 F(A) &= A \textrm{e}^{i b |A|^2}, \\
-M(A) &= \textrm{e}^{-T^2 / 2} A, \\
+\label{eq:loss}
+L(A) &= h A, \\
+\label{eq:disp}
 D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, \\
-L(A) &= h A,
+\label{eq:mod}
+M(A) &= \textrm{e}^{-T^2 / 2} A,
 \end{align}
 \end{subequations}
-with four dimensionless parameter groups (see Table~\ref{tab:values})
+with the four dimensionless parameters (see Table~\ref{tab:values})
 \begin{align*}
@@
 \section{Combining the Effects}
-In this model the pulse is iteratively passed through each process, the order of which is now important.
+In this model the pulse is iteratively passed through each process, the order of which must now be considered.
 We are most interested in the output of the laser cavity, and so we shall start with the loss component.
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the average model is a Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function ***, and since a Gaussian is a fixed point of the Fourier transform \cite{integrals} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the average model is a Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function ***, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\
@@
 where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
-After passing though the optical coupler the pulse will simply decay, $A_1 = h A_0$.
-The pulse then enters the CFBG, where it will maintain its Gaussian shape, however, it will spread \cite{agrawal2013}.
+After passing though the optical coupler the pulse will simply decay to $A_1 = h A_0$.
+The pulse then enters the CFBG, where it will maintain its Gaussian shape, however, it will spread \cite{agrawal2013, ferreira, silfvast}.
 This can be written as
@@
 \end{align*}
-where $\widetilde{\sigma}^2$ denotes the resulting variance, $\widetilde{C}$ denotes the resulting chirp, and $\zeta$ is the reduction of the amplitude caused by dispersion.
+where $\widetilde{\sigma}^2$ denotes the resulting variance, $\widetilde{C}$ denotes the resulting chirp, and $\zeta$ is the reduction of the amplitude caused by the spread.
 Next, the pulse is modulated:
@@
 \end{align*}
-with $E$ the energy of the pulse as it enters the gain fibre.
+with $E$ the energy of the pulse as it enters the gain fibre. \\
 
@@
 Each of these processes has a relatively straight forward effect, with the exception of dispersion.
-After dispersion, the out-going variance $\widetilde{\sigma}^2$ can be found by computing the effect of dispersion given by ***.
+After dispersion, the out-going variance, $\widetilde{\sigma}^2$, can be found by computing the effect of dispersion given by \eqref{eq:disp}.
 This yields the relations
@@
 \end{subequations}
-for the variance, chirp, and phase shift after the dispersive element, the full details can be found in Appendix \ref{chap:disp}.
+for the variance, chirp, phase shift, and spread, respectively, after the dispersive element, the full details can be found in Appendix \ref{chap:disp}.
 Now, the out-going variance and chirp can be eliminated from this system of equations using \eqref{eq:varcond} and \eqref{eq:chirpcond}:
@@
 \end{align*}
-Notice that the left hand side of this expression is strictly positive ($\sigma$ is strictly less than $1$ at equilibrium ***), therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
+As we shall see, $\sigma$ is strictly less than $1$ at equilibrium, and so, notice that the left hand side of this expression is strictly positive.
+Therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
 After squaring each side of this expression we obtain
@@
 \label{eq:equilvar}
-\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4}(1 + s^4) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
+\sigma^2 &= \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} - s^4 - s^2 \sqrt{4 + s^4}.
 \end{align}
+
+Limit?***
 
@@
 \end{align*}
-Then, by taking the exponential of each side, and multiplying by the original expression, we obtain
+Then, by taking the exponential of each side, and multiplying by this expression, we obtain\footnote{By \eqref{eq:lambertw}.}
 \begin{align*}
 \frac{1}{h^2 \zeta^2} E \exp \left(\frac{1}{h^2 \zeta^2} E \right) &= W \left( a E \textrm{e}^E \right) \exp \left( W \left( a E \textrm{e}^E \right) \right) \\
-&= a E \textrm{e}^E,
+&= a E \textrm{e}^E.
 \end{align*}
-by \eqref{eq:lambertw}. Now, this can be written as 
+Now, this can be written as 
 \begin{align*}
@@
 \end{align*}
-***the pulse will converge if the argument of the log is greater than 1***
+This expression allows us to determine a restriction on the parameters for a solution to exist---in order for this energy to be positive, $a h^2 \zeta^2 > 1$.
 The energy of the pulses as it enters the optical coupler can now be found, recall from \eqref{eq:gainde} that the energy is defined as
@@
 \end{align}
-Since we have previously found the equilibrium shape, we can now find the amplitude of the pulse as well. Again, from \eqref{eq:gainde}, it must be that $E_* = P \sigma \sqrt{\pi}$, or,
+
+We can now find the amplitude of the pulse as well as we have previously found the equilibrium shape. Again, from \eqref{eq:gainde}, it must be that $E_* = P \sigma \sqrt{\pi}$, or,
 \begin{align}

### 2019-02-14 Thesis/Intro/Introduction.tex
Added to introduction

@@
 
-\subsection{Gain and Pump}
-
-\subsection{Optical Coupler}
+\subsection{Optical Coupler and Laser Output}
+The optical coulper is a device that splits its input into two outputs---one continuing through the laser cavity, while the other exits the cavity to become the output of the laser.
+There are multiple devices that can accomplish this, however, the simplest is a partially reflecting mirror \cite{alazzawi}.
+These mirrors are characterized by their reflection coefficient, $R$.
+In the schematic shown in Figure \ref{fig:cavity}, the part of the signal that is reflected exits the cavity, whereas, the part of the signal transmitted remains within the cavity.
+\\
 
@@
 A fibre Bragg grating (FBG) is an optical fibre where the refractive index varies periodically along its length \cite{ferreira}.
-To achieve this, typically silica fibres are doped with Germanium, which when exposed to intense ultraviolet (UV) light alter the refractive index of the core \cite{starodoumov}.
-The photosensitivity of the optical fibres can be increased by more than an order of magnitude by the Germanium doping \cite{ferreira}.
+To achieve this, typically silica fibres are doped with Germanium, which when exposed to intense ultraviolet (UV) light alters the refractive index of the core \cite{becker, starodoumov}.
+The photosensitivity of the optical fibres can be increased by more than an order of magnitude by the Germanium doping \cite{becker, ferreira}.
 \\
@@
 \input{./Figures/PhaseMask}
-\caption{\textbf{Phase-Mask:} The phase-mask focuses the ultraviolet light onto the centre of the core causing periodic constructive and destructive interference.}
+\caption{\textbf{Phase-Mask:} The phase-mask refracts the UV light onto the core.}
 \label{fig:phasemask}
@@
 \input{./Figures/Hologram}
-\caption{\textbf{Holographic Side Exposure:} Two incident ultraviolet waves cause periodic constructive and destructive interference at the centre of the core.}
+\caption{\textbf{Holographic Side Exposure:} Two incident beams intersect at the core.}
 \label{fig:holographic}
 \end{subfigure}
-\caption{Depictions of the two methods for manufacturing FBGs.}
+\caption{Depictions of the two methods for manufacturing FBGs. The UV light is focused on the core causing periodic constructive and destructive interference.}
 \label{fig:fbgmake}
@@
 
-FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
+FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
 Both methods cause the periodic nature of the refractive index through interference.
-In the phase-mask method (Figure \ref{fig:phasemask}) a single beam of UV light passes through the phase-mask which acts as a series of lenses focusing the light at the core---this causes a sinusoidal interference pattern.
+In the phase-mask method (Figure \ref{fig:phasemask}) a single beam of UV light passes through the phase-mask which acts as a series of lenses, focusing the light at the core---this causes a sinusoidal interference pattern.
 Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of UV light are instead used to create the interference pattern.
@@
 The purpose of FBGs is that they act as reflective filters \cite{agrawal2002, alazzawi, ferreira, starodoumov}.
-Due to the periodicity of the refractive index, light with the corresponding wavelength will be reflected, with all others passing through.
-This wavelength is defined by the Bragg condition \cite{agrawal2002, alazzawi, ferreira, silfvast, starodoumov}:
+Due to the periodicity of the refractive index, light with the corresponding wavelength will be reflected with all others passing through.
+This wavelength is defined by the Bragg condition \cite{agrawal2002, alazzawi, becker, ferreira, silfvast, starodoumov}:
 \begin{align}
@@
 This reflects wavelengths close to $\lambda_B$, known as the stop-band.
-In this way, FBGs as be used as filters.
 \\
@@
 Figure \ref{fig:chirp} shows examples of chirped and unchirped Gaussian pulses---the most common type of chirp is linear chirp, where the frequency varies linearly across the pulse.
+Because of this, the oscillations are characterized by $\exp \left( i C x^2 \right)$, where $C x$ is the linear variation of the wave number, and $C$ is the chirp parameter.
 By using a chirped phase-mask a chirped fibre Bragg grating (CFBG) can be created.
@@
 This causes most wavelengths to be reflected by a CFBG, but with each wavelength penetrating to a different depth.
-A consequence of this is that a time delay is caused between wavelengths---this is depicted in Figure \ref{fig:cfbg} with the upper portion showing  the refractive index as a function of the depth.
+A consequence of this is that a time delay is created between wavelengths---this is depicted in Figure \ref{fig:cfbg} with the upper portion showing  the refractive index as a function of the depth.
 In this orientation, the red (dashed) wave is unable to penetrate as far as the blue (solid) wave since each wave is reflected where it matches the frequency of the refractive index.
@@
 This is a large problem in fibre optic communications, the signal can spread and potentially becomes uninterpretable after large distances.
-However, chromatic dispersion can be counteracted using a CFBG \cite{agrawal2002, alazzawi, starodoumov} (in the opposite orientation of Figure \ref{fig:cfbg}).
-By forcing the longer wavelengths to travel farther the dispersion can be reversed, restoring the original signal\footnote{A $10$ cm CFBG can compensate the dispersion of $300$ km of fibre~\cite{agrawal2002}.}.
-However, in our case, we wish to accelerate the dispersion, simulating hundreds of metres of fibre, so the CGBG is used in the orientation shown in Figure \ref{fig:cfbg}.
+However, chromatic dispersion can be counteracted using a CFBG \cite{agrawal2002, alazzawi, becker, starodoumov} (in the opposite orientation of Figure \ref{fig:cfbg}).
+By forcing the longer wavelengths to travel farther the dispersion can be reversed, restoring the original signal.
+In one experiment \cite{dong}, a signal was successfully transmitted over $109$ km at $40$ Gb/s by compensating the dispersion with two  $40$ cm CFBGs.
+Over this distance, the pulse would have spread to about $55$ times its original width, and could only have been transmitted $4$ km at that bit rate.
+At reduced bit rates however, a $10$ cm CFBG can compensate the dispersion of $300$ km of fibre \cite{agrawal2002}.
+However, in our case, we wish to accelerate the dispersion, simulating hundreds of metres of fibre, so the CFBG is used in the orientation shown in Figure \ref{fig:cfbg}.
 \\
@@
 \end{wrapfigure}
-%\begin{figure}[htbp]
-%\centering
-%\input{./Figures/Circulator}
-%\caption[Optical Circulator]{Symbol for a four port optical circulator.}
-%\label{fig:circulator}
-%\end{figure}
-An optical circulator is an optical device that routes signals from port to port in a circular fashion \cite{agrawal2002, alazzawi}, the symbol for a four port optical circulator is shown in Figure \ref{fig:circulator}.
+An optical circulator is a device that routes signals from port to port in a circular fashion \cite{agrawal2002, alazzawi, becker}, the symbol for a four port optical circulator is shown in Figure \ref{fig:circulator}.
 A signal entering from port 1 will be outputted from port 2; a signal entering from port 2 will exit from port 3; and so forth.
@@
 For example, a signal may enter through port 1, exit through port 2, be reflected by an FBG, re-enter port 2, and finally exit through port 3.
+\\
 
-\section{Generalized Nonlinear Sch\"odinger Equation}
+\subsection{Optical Amplifier and Pump Laser}
+Optical amplifiers are of particular importance in fibre optic communications, they are used to restore the strength of a signal after it hass been attenuated over large distances, or when a signal is divided into multiple paths \cite{alazzawi, starodoumov}.
+They are also more efficient, and introduce less noise than an electrical repeater.
+In this context, the optical amplifier provides the energy of the laser \cite{alazzawi}.
+Most commonly, optical amplifiers are created  doping a length of fibre (called the gain fibre) with a rare-earth element which receives power from a pump laser \cite{agrawal2002, alazzawi, starodoumov}.
+The most common dopant is Erbium, however, Ytterbium and Neodymium are also used---Holmium, Samarium, Thulium, and Tellurium are infrequently used as well \cite{agrawal2002}.
+The amplification is achieved with stimulated emission---a similar process to spontaneous emission.
+\\
+
+Spontaneous emission is the process in which an electron of an atom that is in an excited state emits a photon as it transitions to a lower energy state.
+The energy of the photon is equal to the energy difference between the two levels.
+On the other hand, in stimulated emission an incident photon triggers this emission \cite{alazzawi}.
+The rare-earth metal ions are excited by the pump laser, and when they interact with a photon of the tuneable laser, a new photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}.
+\\
+
+Erbium-doped fibre amplifiers (EDFAs) are used most widely since Erbium has a band gap that corresponds to $1.54$--$1.57$ $\mu$m, which is the preferred band for fibre optics since this has the least power loss \cite{agrawal2002, alazzawi, starodoumov}.
+The pump laser typically operates at $980$ nm or $1.48$ $\mu$m because these are able to transfer the most power (up to $100$ mW) into the fibre while introducing minimal noise \cite{agrawal2002, alazzawi, becker, starodoumov}.
+The pump power can be applied either forwards (with the laser), backwards (against the laser), or both \cite{alazzawi}, with each configuration having similar performance \cite{agrawal2002}.
+However, backwards pumping has slightly better performance at high powers when the gain begins to saturate\footnote{This concept will be discussed in Section \ref{chap:gain}.} \cite{agrawal2002}.
+Additionally, with the configuration shown in Figure \ref{fig:cavity}, the optical circulators can be used to isolate the pump circuit from the rest of the laser cavity.
+\\
+
+\section{Generalized Nonlinear Schr\"odinger Equation}
 The standard equation for studying nonlinear optics is the generalized nonlinear Schr\"odinger equation (GNLSE) \cite{agrawal2013, burgoyne2007, ferreira, peng, shtyrina, yarutkina},
@@
 \end{align}
-Here, $A$ is the complex pulse amplitude, $\beta_2$ and $\beta_3$ are the second-order dispersion or group delay dispersion and third-order dispersion, respectively.
+Here, $A$ is the complex pulse amplitude, $\beta_2$ and $\beta_3$ are the second-order (or group delay) and third-order dispersions, respectively.
 $\gamma$ is the coefficient of nonlinearity, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption.
@@
 This equation can be derived from the nonlinear wave equation, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
-Within the derivation comoving coordinates are used so that the reference frame propagates with the group velocity.
+Within the derivation comoving coordinates are used so that the reference frame propagates with the pulse at the group velocity.
 This is achieved with the substitution
@@
 For this reason, it is sometimes referred to as the cubic nonlinear Schr\"odinger equation.
-For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this makes the addition of a quintic term to incorporate nonlinearities associated with such large powers.
+For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this has the addition of a quintic term to incorporate nonlinearities associated with such large powers.
 Furthermore, the $\beta$ terms come from a Taylor expansion of the wavenumber, that is,
@@
 \end{align*}
-where $\phi$ is the phase shift, and $v_g$ is the group velocity.
+where $\phi$ is the phase shift.
 Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth \cite{agrawal2013}.

### 2019-02-14 Thesis/Appendices/Lambert.tex
Edited appendices
Minor edits

@@
 \label{chap:lambertw}
-The Lambert $W$ function is defined to be the inverse of the function $f(x) = x \textrm{e}^x$ and its graph is shown in Figure \ref{fig:lambertw}.
+The Lambert $W$ function is defined to be the inverse of the function $f(x) = x \textrm{e}^x$; its graph is shown in Figure \ref{fig:lambertw}.
 In other words, if $z = x \textrm{e}^x$ then $x = W(z)$.
@@
 M.
-Wright \cite{lambertw}.
+Wright \cite{corless}.
+\\
 
@@
 However, in this work the $W$ function will only take positive real values and so this distinction is not needed.
+\\
 
@@
 
-The Lambert $W$ function has applications in various areas of math and physics \cite{lambertw} including:
+The Lambert $W$ function has applications in various areas of math and physics \cite{corless} including:
 \begin{itemize}

### 2019-02-14 Thesis/Figures/Cavity.tex
Added/updated figures
Minor edits

@@
+% !TeX root = ../Thesis.tex
+
 \begin{tikzpicture}
@@
 \draw [rounded corners=4mm] (0,0) rectangle ++(9,4);
-\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4);
+\draw [rounded corners=4mm] (0,0) rectangle ++(-1.5,4);
 
@@
 \draw (0.5,2.25) circle (0.5cm);
-\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er Doped \\ Fibre};
+\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-Doped \\ Fibre};
 \draw (0.5,1.75) circle (0.5cm);
@@
 \filldraw[fill=white, draw=black] (3.5,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
-\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};
+\filldraw[fill=white, draw=black] (-2.1,1.5) rectangle ++(1.2,1) node [midway] {Pump};
 
 % Coupler and output
-\draw[-{Latex[length=2.5mm]}] (4.5,4) -- (4.5,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
+\draw[-stealth] (4.5,4) -- (4.5,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
 \draw[densely dashdotted] (4,3.5) -- (5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};
 
-% Circulator
+% Circulators
 \filldraw[fill=white, draw=black] (9,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
-\draw (9,2.5) arc (0:-90:0.5cm);
-\draw (9,1.5) arc (0:90:0.5cm);
+\draw[->,>=stealth] (9,2.325) arc (90:360:0.325cm);
+
+\filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
+\draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);
+
+\filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
+\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);
 
@@
 % Arrows
-\draw[-{Latex[length=2.5mm]}] (2.16,0) -- (2.15,0);
-\draw[-{Latex[length=2.5mm]}] (2.39,4) -- (2.4,4);
-\draw[-{Latex[length=2.5mm]}] (6.76,0) -- (6.75,0);
-\draw[-{Latex[length=2.5mm]}] (7.09,4) -- (7.1,4);
-\draw[-{Latex[length=2.5mm]}] (-0.649,0) -- (-0.65,0);
-\draw[-{Latex[length=2.5mm]}] (-0.351,4) -- (-0.35,4);
-\draw[-{Latex[length=2.5mm]}] (8.807,2.11) -- (8.8,2.1);
-\draw[-{Latex[length=2.5mm]}] (8.96,1.712) -- (8.97,1.7);
+%\draw[-stealth] (2.16,0) -- (2.15,0);
+%\draw[-stealth] (2.39,4) -- (2.4,4);
+%\draw[-stealth] (6.76,0) -- (6.75,0);
+%\draw[-stealth] (7.09,4) -- (7.1,4);
+%\draw[-stealth] (-0.649,0) -- (-0.65,0);
+%\draw[-stealth] (-0.351,4) -- (-0.35,4);
 \end{tikzpicture}

### 2019-03-01 Thesis/Figures/CFBG.tex
Minor edits
Changed arrow style

@@
 % Index of refraction
-\draw [->] (4,5) -- (12.5,5)
+\draw [->, >=stealth] (4,5) -- (12.5,5)
 node [pos=0.47,anchor=north,yshift=-0.25cm] {$z$};
-\draw [->] (4,5) -- (4,8)
+\draw [->, >=stealth] (4,5) -- (4,8)
 node [pos=0.5,anchor=east,xshift=-0.2cm] {$n(z)$};

### 2019-03-01 Thesis/Figures/Emission.tex
Added figure for spontaneous / stimulated emission

% !TeX root = ../Thesis.tex

\begin{tikzpicture}
% Energy levels
\draw [dashed] (0,0) -- (12,0) node [pos = -0.05] {$E_1$};
\draw [dashed] (0,4) -- (12,4) node [pos = -0.05] {$E_2$};

% Transition arrows
\draw[->, >=stealth] (2,0) -- (2,3.8);
\draw[<-, >=stealth] (6,0.2) -- (6,4);
\draw[<-, >=stealth] (10,0.2) -- (10,4);

% Circles
% Bottom
\filldraw[fill=white, draw=black, dashed] (2,0) circle (0.2);
\filldraw[fill=blue, draw=black] (6,0) circle (0.2);
\filldraw[fill=blue, draw=black] (10,0) circle (0.2);
% Top
\filldraw[fill=blue, draw=black] (2,4) circle (0.2);
\filldraw[fill=white, draw=black, dashed] (6,4) circle (0.2);
\filldraw[fill=white, draw=black, dashed] (10,4) circle (0.2);

% Photons
\draw [domain=0.5:2, samples=250, red, thick, ->, >=stealth] plot (\x, {-0.5*sin(4*pi*deg(\x-2))});
\draw [domain=6:7.5, samples=250, red, thick, ->, >=stealth] plot (\x, {4-0.5*sin(4*pi*deg(\x-6))});
\draw [domain=8.5:10, samples=250, red, thick, ->, >=stealth] plot (\x, {4-0.5*sin(4*pi*deg(\x-10))});
\draw [domain=10:11.5, samples=250, red, thick, ->, >=stealth] plot (\x, {4-sin(4*pi*deg(\x-10))});

% Labels
\node at (2, -1){Pumping};
\node [align=center] at (6, -1){Spontaneous \\ Emission};
\node [align=center] at (10, -1){Stimulated \\ Emission};
\end{tikzpicture}

### 2019-03-01 Thesis/Intro/Introduction.tex
Updated introduction

@@
 \section{Tuneable Lasers}
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 \centering
@@
 
-FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
+FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002,alazzawi,becker,starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
 Both methods cause the periodic nature of the refractive index through interference.
@@
 
+\begin{figure}[tbp]
+\centering
+\input{./Figures/Emission}
+\caption{In pumping, incident photons are absorbed by electrons which are then excited into a higher energy state.
+In spontaneous emission, an electron in an excited state emits a photon and returns to the lower energy state.
+Finally, in stimulated emission, an incident photon interacts with an electron in an excited state, the electron donates its energy to the photon and returns to the lower energy state.}
+\label{fig:emission}
+\end{figure}
+
 Spontaneous emission is the process in which an electron of an atom that is in an excited state emits a photon as it transitions to a lower energy state.
@@
 The rare-earth metal ions are excited by the pump laser, and when they interact with a photon of the tuneable laser, a new photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}.
+These processes are highlighted in Figure \ref{fig:emission}.
 \\

### 2019-05-16 Thesis/Appendices/Asymptotics.tex
Added appendix for asymptotic expansion

% !TeX root = ../Thesis.tex

\chapter{Asymptotic Expansions of the Variance}
\label{chap:asymp}
We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$, as well as when $s \rightarrow \infty$. For ease of notation, \eqref{eq:var} is rewritten as
\begin{align*}
\frac{1}{4} x^4 = \eps \left( -x^3 + 5x^2 - 8x + 4 \right),
\end{align*}
where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
\begin{align*}
x = x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \dots
\end{align*}
with $0 < \alpha < \beta$. Then,
\begin{align*}
\bigO1 : \frac{1}{4} x_0^4 = 0,
\end{align*}
and so, $x_0 = 0$. Knowing this, up to the next order we have
\begin{align*}
\frac{1}{4} x_1^4 \eps^{4\alpha} = \eps \left( -x_1^3 \eps^{3\alpha} + 5x_1^2 \eps^{2\alpha} - 8x_1 \eps^\alpha + 4 \right)
\end{align*}
in order to have dominant balance it must be that the left hand side balances with the final term of the right hand side, that is, $4\alpha = 1$, or $\alpha = \frac{1}{4}$. Therefore,
\begin{align*}
\bigO\eps : \frac{1}{4} x_1^4 &= 4, \\
(x_1 - 2)(x_1 + 2)(x_1^2 + 4) &= 0,
\end{align*}
and so, $x_1 = \pm 2, \, \pm 2 i$. However, we wish $x$ to be positive and real---recall that $x = \sigma^2$---thus, we take $x_1 = 2$. Now, the next lowest order of the left hand side must be $\eps^{3\alpha + \beta} = \eps^{3/4 + \beta}$. As with the previous iteration, this must balance with the lowest order term of the $8x$. Hence, $\frac{3}{4} + \beta = 1 + \alpha = \frac{5}{4}$, thus, $\beta = \frac{1}{2}$. Now,
\begin{align*}
\bigO{\eps^{5/4}}: \frac{1}{4} 4 x_1^3 x_2 &= -8x_1, \\
x_2 &= -2,
\end{align*}
where the additional $4$ comes from the binomial expansion. Finally, up to second(?***) order
\begin{align*}
x &\approx 2 \eps^{1/4} - 2 \eps^{1/2}, \\
\sigma^2 &\approx 2 \left( s - s^2 \right),
\end{align*}
this is shown in Figure \ref{fig:lims0}.
\begin{figure}[tbp]
\input{./Figures/Lim_s_0}
\caption{Asymptotic expansion of the variance as $s \rightarrow 0$.}
\label{fig:lims0}
\end{figure}

We shall now consider the other limit, when $s \rightarrow \infty$. Using a similar substitution we instead write \eqref{eq:var} as
\begin{align*}
\frac{1}{4} \eps x^4 = -x^3 + 5x^2 - 8x + 4,
\end{align*}
where $x = \sigma^2$, and $\eps = s^{-4}$ instead so that we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
\begin{align*}
x = \eps^{-\xi} \left( x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \dots \right).
\end{align*}
The reason for this is because the equation is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root. As with before, we obtain dominant balance when the quartic term balances with the cubic term:
\begin{align*}
1 - 4 \xi &= -3 \xi, \\
\xi &= 1.
\end{align*}
Then,
\begin{align*}
\bigO{\eps^{-3}}: \frac{1}{4} x_0^4 &= -x_0^3, \\
x_0^3 (x_0 + 4) &= 0,
\end{align*}
we shall choose $x_0 = 0$---since $x \geq 0$. Unlike up until this point, we obtain dominant balance when the right hand side dominates the left hand side, this is achieved when $\alpha = 1$. Now,
\begin{align*}
\bigO1 : 0 &= -x_1^3 + 5x_1^2 - 8x_1 + 4, \\
&= -(x_1 - 1)(x_1 - 2)^2,
\end{align*}
so either $x_1 = 1$ or $x_1 = 2$, we shall see in the next step that we can eliminate one of these. The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$:
\begin{align*}
\bigO\eps : \frac{1}{4} x_1^4 &= -3x_1^2 x_2 + 5\cdot2 x_1 x_2 - 8x_2, \\
&= -x_2 (3x_1 - 4)(x_1 - 2),
\end{align*}
where again, the coefficients come from the binomial expansions;
from this it is clear that
\begin{align*}
x_2 &= \frac{-x_1^4}{4(3x_1 - 4)(x_1 - 2)},
\end{align*}
and that $x_1 \ne 2$. Thus, $x_1 = 1$, $x_2 = -\frac{1}{4}$, and
\begin{align*}
x = 1 - \frac{1}{4} \eps + x_2 \eps^{\gamma - 1} + \dots.
\end{align*}
Expanding one final term we find $\gamma = 3$, and
\begin{align*}
\bigO{\eps^2}: \frac{1}{4} 4x_2 x_1^3 &= -(3x_3 x_1^2 + 3x_2^2 x_1) + 5(2x_3 x_1 + x_2^2) - 8(x_3).
\end{align*}
Knowing the values of $x_1$, and $x_2$ this is simply an arithmetical calculation yielding $x_3 = \frac{3}{8}$. Finally,
\begin{align*}
x &\approx 1 - \frac{1}{4}\eps + \frac{3}{8}\eps^2, \\
\sigma^2 &\approx 1 - \frac{1}{4s^4} + \frac{3}{8s^8},
\end{align*}
this approximation is shown in Figure \ref{fig:limsinfty}.
\begin{figure}[tbp]
\input{./Figures/Lim_s_Infty}
\caption{Asymptotic expansion of the variance for $s \rightarrow \infty$.}
\label{fig:limsinfty}
\end{figure}

### 2019-05-16 Thesis/Appendices/Hermite.tex
Added appendix for density of gaussians

% !TeX root = ../Thesis.tex

\chapter{Span of Gaussians in $L^2$}
\label{chap:gauss}
In order to show that Gaussians span $L^2$, we shall start our analysis with the span of the Hermite polynomials in $L^2$. Typically the Hermite polynomials are recursively defined as \cite{conway, courant, teuwen}
\begin{align*}
H_n(x) := (-1)^n \textrm{e}^{x^2} \diff[n]{}{x} \textrm{e}^{-x^2},
\end{align*}
with the inner product\footnote{The complex conjugate of $g$ is omitted since the functions dealt with are real.}
\begin{align*}
\left< f, g \right> = \int_\mathbb{R} f g \textrm{e}^{-x^2} \df x,
\end{align*}
where $\textrm{e}^{-x^2}$ is the weighting function. This is so that 
\begin{align*}
\left< H_m(x), H_n(x) \right> = \sqrt{\pi} 2^n n! \delta_{mn}
\end{align*}
and, therefore, the Hermite polynomials form an orthogonal set \cite{courant, hochstrasser, kreyszig, szego, teuwen}. Consider instead, the Gaussian--Hermite polynomials
\begin{align*}
\Her{n}{x} &:= \textrm{e}^{-x^2/2} H_n(x),
\end{align*}
with the inner product
\begin{align*}
\left< f, g \right> = \int_\mathbb{R} f g \, \df x,
\end{align*}
notice that the weighting function has been absorbed into the Hermite polynomials. We shall now show that the set of Gaussian--Hermite polynomials spans $L^2$. \\

\begin{theorem}
\label{thm:hermite}
The set of Gaussian--Hermite polynomials, $\mathcal{G} = \{ \Her{n}{x} : n \in \mathbb{N} \}$, spans $L^2$.
\end{theorem}
\begin{proof}
The Gaussian--Hermite polynomials are an orthogonalization of the set $\Xi = \{x^n \textrm{e}^{-x^2/2} : n \in \mathbb{N}\}$, and therefore, have the same span \cite{kreyszig, szego}. Thus, it is sufficient to show that $\Xi$ spans $L^2$.
Suppose there exists an $f \in L^2$ such that $\left< f, \Her{n}{x} \right> = 0$ for all $n$, or equivalently, that $\left< f, x^n \textrm{e}^{-x^2/2} \right> = 0$ for all $n$ so that it is not in the span of $\mathcal{G}$. \\

Let us now consider the function \cite{courant, szego, teuwen}
\begin{align*}
F(z) = \frac{1}{\sqrt{2\pi}}\int_\mathbb{R} f \textrm{e}^{zx} \textrm{e}^{-x^2/2} \, \df x,
\end{align*}
noting that $f \textrm{e}^{zx} \textrm{e}^{-x^2/2} \in L^2$ by the Cauchy--Schwarz inequality \cite{griffel, kolmogorov}, so $F$ converges, and that $F$ is holomorphic. The first exponential can be expanded into its Maclaurin series, then with Fubini's theorem we obtain
\begin{align*}
F(z) = \frac{1}{\sqrt{2\pi}} \sum_{n = 0}^{\infty} \frac{z^n}{n!} \int_\mathbb{R} f x^n \textrm{e}^{-x^2/2} \, \df x.
\end{align*}
Recall, that by assumption
\begin{align*}
\int_\mathbb{R} f x^n \textrm{e}^{-x^2/2} \, \df x &= \left< f, x^n \textrm{e}^{-x^2/2} \right>, \\
&=0,
\end{align*}
for all $n$ and so $F(z) \equiv 0$. We now notice that
\begin{align*}
0 &= F(z), \\
&= F(i \omega), \\
&= \FT{f \textrm{e}^{-x^2/2}},
\end{align*}
and now it is clear that $f \textrm{e}^{-x^2/2} = 0$ almost everywhere, therefore, $f = 0$ almost everywhere. \\
\end{proof}

Alternatively, without much difficulty it can be shown that the Gaussian--Hermite polynomials satisfy
\begin{align}
\label{eq:paracyl}
\diff[2]{\Her{n}{x}}{x} - \left( x^2 - 2n - 1 \right) \Her{n}{x} = 0,
\end{align}
this has the form of the parabolic cylinder functions \cite{miller}, and indeed the Gaussian--Hermite polynomials can be expressed in terms of parabolic cylinder functions \cite{hochstrasser, miller}. Moreover, \ref{eq:paracyl} can also be written in Sturm--Liouville form as
\begin{align*}
\diff{}{x} \left( 1 \cdot \diff{\Her{n}{x}}{x} \right) + (1 - x^2) \Her{n}{x} = -2n \Her{n}{x}.
\end{align*}
By the spectral theorem \cite{griffel, higson, kreyszig}, this suggests that the Gaussian--Hermite polynomials form an orthogonal set with the weighting function $w(x) = 1$, and are complete in $L^2$. Using this result, we can now show that Gaussian functions also span $L^2$ with the following theorem. \\

\begin{figure}[tbp]
\begin{subfigure}{0.5\textwidth}
\input{./Figures/GS1}
\caption{$N = 20$, $h = 0.1$}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
\input{./Figures/GS2}
\caption{$N = 10$, $h = 0.1$}
\end{subfigure}
\caption{Two examples of Gaussian series.}
\label{fig:gs}
\end{figure}

\begin{theorem}
\label{thm:gaussian}
Gaussians of a single variance span $L^2$.
\end{theorem}
\begin{proof}
Theorem \ref{thm:hermite} showed that any square integrable function can be expressed as
\begin{align*}
f = \sum_{n = 0}^\infty a_n \Her{n}{x}.
\end{align*}
Using a similar idea to \cite{calcaterra2, calcaterra}, we shall now expand the Gaussian--Hermite polynomials into their definition
\begin{align*}
f = \sum_{n = 0}^\infty a_n (-1)^n \textrm{e}^{x^2/2} \diff[n]{}{x} \textrm{e}^{-x^2}.
\end{align*}
Finally, we can rewrite the derivatives using central differences \cite{zwillinger} so that
\begin{align}
f = \sum_{n = 0}^\infty a_n (-1)^n \textrm{e}^{x^2/2} \left[ \lim_{h \rightarrow 0} \frac{1}{h^n} \sum_{i = 0}^n (-1)^i \binom{n}{i} \exp\left( -\left( x + h\left( \frac{n}{2} - i \right) \right)^2 \right) \right].
\label{eq:gs}
\end{align}
\end{proof}

\begin{figure}[tbp]
\input{./Figures/GaussMod}
\caption{$N = 20$, $h = 0.1$}
\label{fig:gaussmod}
\end{figure}

Two examples of Gaussian series from \eqref{eq:gs} are shown in Figure \ref{fig:gs}. These examples are taken from \cite{calcaterra2, calcaterra}, however, we achieve similar or better approximations with either fewer terms, or with an $h$ value an order of magnitude larger. There are two reasons for this, first, we use central difference as opposed to backwards difference yielding a convergence of $\bigO{h^2}$ instead of $\bigO{h}$. Furthermore, because \cite{calcaterra2, calcaterra} used backwards differences, the means of the Gaussians are all non-negative, whereas with central differences, our Gaussians' means are both positive and negative---this leads to smaller coefficients, and better numerical stability. Moreover, Figure \ref{fig:gaussmod} shows the Gaussian series for the modulation function in \cite{bohun, burgoyneemail}.

### 2019-05-16 Thesis/Previous_Models/Previous.tex
Added chapter on previous modelling attempts

% !TeX root = ../Thesis.tex

\chapter{Previous Modelling Efforts}
In this chapter we shall explore the previous modelling efforts by first reviewing the classic equations used in nonlinear optics. We will then build upon this to the master equation of mode-locking. The solutions to this will briefly be studied before diving into `discretized' functional models. \\

\section{Generalized Nonlinear Schr\"odinger Equation}
The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE) \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}
\begin{align*}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A.
\end{align*}
Here, $A$ is the complex pulse amplitude, $\beta_2$ is the second-order---or group delay---dispersion, and $\gamma$ is the coefficient of nonlinearity. In practice, this equation lacks a few key terms. Thus, it is often generalized by adding amplification, loss, and higher order terms. This gives the generalized nonlinear Schr\"odinger equation (GNLSE) \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
\begin{align}
\label{eq:nlse}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
\end{align}
where $\beta_3$ is the third order effect of dispersion, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption. \\

This equation can be derived from the nonlinear wave equation, the derivation is presented in detail in \cite{agrawal2013, ferreira}. Within the derivation comoving coordinates are used so that the reference frame propagates with the pulse at the group velocity. This is achieved with the substitution
\begin{align*}
T = t - \frac{z}{v_g}.
\end{align*}

The GNLSE takes the same form as the Schr\"odinger equation with the inclusion of the cubic nonlinear term, hence its name. For this reason, it is sometimes referred to as the cubic nonlinear Schr\"odinger equation. For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this has the addition of a quintic term to incorporate nonlinearities associated with such large powers. Furthermore, the $\beta$ terms come from a Taylor expansion of the wavenumber \cite{kartner}, that is,
\begin{align*}
k(\omega) &= k_0 + \pdiff{k}{\omega}(\omega - \omega_0) + \frac{1}{2} \pdiff[2]{k}{\omega}(\omega - \omega_0)^2 + \frac{1}{6} \pdiff[3]{k}{\omega}(\omega - \omega_0)^3 + \dots, \\
&= \phi + \frac{1}{v_g}(\omega - \omega_0) + \frac{1}{2}\beta_2 (\omega - \omega_0)^2 + \frac{1}{6}\beta_3 (\omega - \omega_0)^3 + \dots,
\end{align*}
where $\phi$ is the phase shift. Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth \cite{agrawal2013}.

\section{The Master Equation of Mode-Locking}
The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers we wish to add a modulation term to ensure mode-locking, this yields the master equation of mode-locking, \cite{hausbook, haus1975, haus1986, haus1992, haus2000, kartner, tamura, usechak}
\begin{align*}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T).
\end{align*}
The most common form of modulation is the sinusoid $M(T) = \frac{1}{2}\frac{M_s}{\omega_M} \left( 1 - \cos \left( \omega_M T \right) \right)$ \cite{hausbook, haus1975, haus1996, kartner}, and since $T$ is generally small, by it's definition, we expand via it's Taylor series so that $M(T) = \frac{1}{2}M_s T^2$. This brings us to the most common form of the master equation of mode-locking (neglecting the third order dispersion),
\begin{align}
\label{eq:meml}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - \frac{1}{2}M_s T^2.
\end{align}
Commonly, in an attempt to simplify the equation the gain assumed to be constant. As a whole no analytic solution is know for \eqref{eq:meml}, however, after additional simplifications there are three flavours of solutions. \\

In the least complicated case, the modulation and nonlinearity are omitted resulting in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}. Now, with the inclusion of the nonlinearity a similar solution is found, however, it is now it the form of a chirped hyperbolic secant \cite{haus1991, usechak}. Both of these are unsurprising since this reduces to the soliton solution of the NLSE \cite{ferreira}. Lastly, by including the modulation term, and excluding the nonlinearity, \eqref{eq:meml} can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura, usechak}. However, in practice only the Gaussian is stable---the higher modes quickly decay within the laser \cite{hausbook, haus1975, haus1996, haus2000}. For a more comprehensive and exhaustive history see \cite{haus2000}. \\

\section{Discrete Functional Model}
While solution to the master equation yields reasonable results, it is not necessarily representative of what happens within the laser cavity. The issue with \eqref{eq:meml} is that it assumes each process effects the pulse continuously within the cavity. As highlighted by Figure \ref{fig:cavity}, this is a poor assumption. Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG, the pulse is only amplified within the Erbium-doped fibre, etc. Thus, perhaps a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity. Each of the blocks can then be composed together functionally to give the effect of one circuit around the cavity. This yields an algebraic equation instead of a differential one. \\

Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator. This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{siegman}, which they then greatly added to the following year \cite{kuizenga1970a}. Kuizenga and Seigman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}. The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried to model passive mode-locking---mode-locking without the use of a modulator. In the absence of a modulator the nonlinearity becomes crucial to shaping the pulse. I don't know how to start this sentence*** when it was resurrected by Burgoyne \cite{burgoyne2014} in 2014 for tuneable lasers. \\

Despite these attempts, several short-comings exist. The clearest is that none of these models have contained each block--either the nonlinearity or the modulation have been omitted. In the context of tuneable lasers each component plays an important role. Another key drawback is that the functional operations of some of the components are somewhat phenomenological. While these functions are chosen based on the observed output, they are not necessarily correct. Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation (SPM) of the pulse becomes too strong distorting and damaging the wave until it ultimately becomes unstable and unsustainable. This notion will be explained in greater detail in Chapter \ref{chap:nl}. \\

### 2019-05-16 Thesis/Figures/PhaseMask.tex
Added/updated figures
Updated figures

--- 2019-02-11 Thesis/Figures/Hologram.tex
@@
 \begin{tikzpicture}
-
 \draw[pattern=north east lines, pattern color=blue] (-4,0.5) rectangle (4,1); % Top Insulation
@@
 \draw[pattern=mydots, pattern color=OliveGreen] (-4,-0.5) rectangle (4,0.5); % Core
+\draw[fill=black] (-2,1.5) rectangle (2,1.75); % Phase Mask top
+
+\foreach \i in {0,...,7}
+  \draw[magenta, thick] (-1.75 + \i/2,5) -- (-1.75 + \i/2,1.5);
 
 \foreach \i in {0,...,3}{
+  % Phase mask teeth
+  \draw[fill=black] (-2 + \i,1.25) rectangle (-1.75 + \i,1.5); 
+  \draw[fill=black] (-1.25 + \i,1.25) rectangle (-1 + \i,1.5);
   % Rays
-  \draw[->, >=stealth, magenta, thick] (-2.25 + \i,4.5) -- (-1.25 + \i,-1.5);
-  \draw[->, >=stealth, magenta, thick] (-0.75 + \i,4.5) -- (-1.75 + \i,-1.5);
+  \draw[->, >=stealth, magenta, thick] (-1.75 + \i,1.5) -- (-1.25 + \i,-1.5);
+  \draw[->, >=stealth, magenta, thick] (-1.25 + \i,1.5) -- (-1.75 + \i,-1.5);
 }
 % Labels
-\draw[->, >=stealth, thick] (3,-1.5) -- (2,0) node[pos=-0.2] {Ge Doped Core};
+\draw[->, >=stealth, thick] (3,-1.5) -- (2,0) node[pos=-0.2] {Ge-Doped Core};
 \draw[->, >=stealth, thick] (-3,-1.5) -- (-2,-0.75) node[pos=-0.3] {Cladding};
-\draw[->, >=stealth, thick] (-3,2.5) -- (-1.82,2) node[pos=-0.4] {UV Light};
+\draw[->, >=stealth, thick] (-3,2.5) -- (-1.75,2) node[pos=-0.4] {UV Light};
+\draw[->, >=stealth, thick] (3,2.5) -- (2,1.5) node[pos=-0.2] {Phase-Mask};
 \end{tikzpicture}

### 2019-05-16 Thesis/Appendices/Dispersion.tex
Minor corrections

@@
 
-The effect of dispersion can be computed analytically for several input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{gradshteyn}
+The effect of dispersion can be computed analytically for several input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{debnath, gradshteyn}
 \begin{align*}
@@
 
-The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, ferreira, silfvast}
+The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, anderson, ferreira, silfvast}
 \begin{align*}

### 2019-05-16 Thesis/Model/Model.tex
Minor corrections

@@
 \chapter{A New Model}
+\label{chap:linear}
+In this chapter we shall derive our new model and solve it analytically in the linear case.
+To accomplish this we shall use the ideas of the previous functional models \cite{cutler, siegman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
+To alleviate some of the pitfalls mentioned in the previous chapter, we shall include all five processes involved in the modification of the pulse within the laser cavity (gain, nonlinearity, loss, dispersion, and modulation).
+In addition to this, the functional operations associated with each component will be derived from \eqref{eq:nlse}, with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.
+\\
+
+We shall start our analysis with the derivation of the functional operators for the five components. \\
+
 \section{Components}
-
 \subsection{Gain}
+\label{chap:gain}
 Within the Er-doped gain fibre, the gain term is dominant, and equation~\eqref{eq:nlse} reduces to
@@
 \end{align}
-where $g(A)$ takes the form \cite{bohun, burgoyne2014, peng, shtyrina, silfvast, yarutkina}
+where $g(A)$ takes the form \cite{bohun, burgoyne2014, hausbook, haus1975, haus1991, haus1992, haus2000, peng, shtyrina, silfvast, usechak, yarutkina}
 \begin{align}
@@
 \begin{align*}
-W\left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) \\
+W \left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) \\
 &= \frac{E_{\textrm{out}}}{\Es},
@@
 \begin{align*}
-F(A) &= A e^{i \gamma |A|^2 L_f}.
+F(A) &= A \textrm{e}^{i \gamma |A|^2 L_f},
 \end{align*}
+this is also frequently called the Kerr nonlinearity or Kerr effect after John Kerr who discovered it in 1875.
+As we shall see in Section \ref{chap:energy}, this is what is responsible for self-phase modulation and ultimately the degradation of the pulse \cite{desurvire, dunlop, martinez1984, tamura}.
 
@@
 Two sources of loss exist within the laser circuit: the loss due to the output coupler and the optical loss due to absorption and scattering.
+The first case is simply a scalar multiplication depending on the reflectivity of the output coupler.
+The loss due to absorption and scattering can be derived from \eqref{eq:nlse},
+\begin{align*}
+\pdiff{A}{z} = - \alpha A.
+\end{align*}
 Combining these two effects give a loss that takes the form
 \begin{align*}
-L(A) &= (1 - R) e^{- \alpha L}A,
+L(A) &= (1 - R) \textrm{e}^{- \alpha L}A,
 \end{align*}
@@
 \end{align}
-and since dispersion acts in the frequency domain it is convenient to take the Fourier transform of~\eqref{eq:dispde} \cite{gradshteyn}, giving
+and since dispersion acts in the frequency domain it is convenient to take the Fourier transform of~\eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
 \begin{align*}
@@
 \subsection{Modulation}
-In the average model, the amount of modulation is characterized by the parameter $\epsilon$ through the term $\frac{\epsilon}{2}T^2 A$.
+In the average model, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{M_s}{2}T^2 A$.
 In this new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
@@
 \end{align*}
-where $T_M$ is a characteristic width of the modulation.
+where $T_M$ is a characteristic width of the modulation. \\
+
+Despite assuming a Gaussian modulation the following solution can be generalized to any modulation function in $L^2$ since Gaussians in fact span $L^2$ as shown in Appendix \ref{chap:gauss}. \\
 
@@
 \noalign{\global\arrayrulewidth=1.5pt}\hline
-Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, yarutkina} \\
-Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
-Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, yarutkina} \\
+Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, usechak, yarutkina} \\
+Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
+Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, usechak, yarutkina} \\
 Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
@@
 Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
-Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, yarutkina} \\
+Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
 Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
@@
 \begin{subequations}
+\label{eq:effects}
 \begin{align}
@@
 \section{Combining the Effects}
+\label{sec:effects}
 In this model the pulse is iteratively passed through each process, the order of which must now be considered.
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the average model is a Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function ***, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the average model is a Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\
@@
 Therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
+Moreover, Martinez, Fork, and Gordon \cite{martinez1984} found two solutions analytically, but showed that one was unstable---consistent with experiments.
 After squaring each side of this expression we obtain
@@
 which once fully simplified, yields the biquartic equation
-\begin{align*}
+\begin{align}
+\label{eq:var}
 \left( \sigma^2 \right)^4 + 4 s^4 \left( \sigma^2 \right)^3 - 20 s^4 \left( \sigma^2 \right)^2 + 32 s^4 \left( \sigma^2 \right) - 16 s^4 = 0.
-\end{align*}
+\end{align}
 Since this is a quartic in $\sigma^2$ this can be solved analytically; the (positive, real) solution is
@@
 \end{align}
-
-Limit?***
+The asymptotic expansions of the variance in the case of $s \rightarrow 0$, and $s \rightarrow \infty$ are derived in Appendix \ref{chap:asymp}. \\
 
@@
 \end{align}
+
+-sample solution?

### 2019-05-16 Thesis/Nonlinear/Nonlinear.tex
Drafted nonlinear chapter

--- 2019-01-21 Thesis/Nonlinear/Nonlinear.tex
@@
 \chapter{Solution of the Nonlinear Model}
+\label{chap:nl}
+We shall now consider the nonlinear case---when $b > 0$. In this case it becomes much too difficult to obtain an analytic result. Recall from \eqref{eq:fibre} that the nonlinearity takes the form
+\begin{align*}
+F(A) &= A \textrm{e}^{i b |A|^2}.
+\end{align*}
+This is a highly nonlinear operator, and attempting to take Fourier transform of a pulse that's under gone this transformation quickly becomes futile.
+Instead we must resort to a numerical solution.
+\\
 
-\begin{figure}[htbp]
+\section{Code}
+Finding the solution numerically will be done in a similar manner as with the analytic linear solution.
+Using Python a function is written for each component of the laser cavity given by \eqref{eq:effects}, an initial pulse is iteratively passed from function to function in the hopes that a `fixed point' is found.
+The full Python code can be found in Appendix \ref{chap:code}.
+\\
+
+\subsection{Validation}
+Before delving into the nonlinear behaviour of the model, we wish to validate that the code is working as expected---and as a sanity test for the linear solution---by comparing the results of the simulations with $b=0$ to the results of the linear model in Chapter \ref{chap:linear}.
+In the case of the numerical solution our initial conditions become somewhat important.
+In all of the following analysis the initial waveform is $\Gamma \sech \left( 2T \right) \textrm{e}^{i \pi / 4}$ normalized so that the initial energy is $E_0 = 0.1$; additionally, $a = 8000$, and $h = 0.04$.
+\\
+\begin{figure}[tbp]
 \centering
 \input{./Figures/Variance}
-\caption{Simulation and analytic equilibrium standard deviation as a function of $s$.}
-\label{fig:}
+\caption{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.}
+\label{fig:var}
 \end{figure}
 
-\begin{figure}[htbp]
+In the first experiment the pulse is allowed to equilibrate for 40 loops of the circuit, we then compare the variance, chirp, and phase shift of the two methods.
+The results of this are shown in Figure \ref{fig:var}.
+For the most part, we see exceptional agreement between the analytic solution and numerical solution for the variance, and phase shift.
+However, for $s > 2.4$ the chirp from the simulations seems to erratically vary from the analytic solution.
+The reason for this is quite a simple one.
+\\
+\begin{figure}[tbp]
 \centering
 \input{./Figures/LinearPlot}
-\caption{Equilibrium energy and peak power of the pulse as a function of $s$.}
-\label{fig:}
+\caption{Equilibrium energy, and peak power of the pulse as a function of $s$. The thin black line is to highlight that the energy is \emph{not} linearly related to $s$.}
+\label{fig:valenergy}
 \end{figure}
 
-\begin{figure}[htbp]
+To investigate this behaviour, we instead turn our attention to the energy, and amplitude of the pulse at equilibrium as shown in Figure \ref{fig:valenergy}.
+As with Figure \ref{fig:var}, there is very good agreement between the two solutions.
+It is also now clear that at approximately $s = 2.5$ there is too much dispersion---the pulse is no longer sustainable.
+This is of course a consequence of the condition \eqref{eq:energycond}.
+Since the pulse effectively vanishes after this point, the chirp calculation becomes numerically unstable leading to the wild oscillations.
+\\
+
+With the numerical solution yielding the expected results, we are now ready to dive into the rich structure the nonlinearity adds.
+
+\section{Nonlinear Model}
+\begin{figure}[tbp]
 \centering
+\begin{subfigure}{0.5\textwidth}
+\centering
+\input{./Figures/Stable_Shape}
+\caption{Envelope}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+\centering
+\input{./Figures/Stable_FT}
+\caption{Fourier transform}
+\end{subfigure} \\
+\begin{subfigure}{0.5\textwidth}
+\centering
+\input{./Figures/Stable_Chirp}
+\caption{Chirp}
+\end{subfigure}
+\caption{Simulation with $s = 0.15$, and $b = 2.1$ after 15 circuits.}
+\label{fig:nlstable}
+\end{figure}
+With the inclusion of the nonlinearity we generally find a similar solution to the linear case.
+An example of this is shown in Figure \ref{fig:nlstable}.
+The envelope of the pulse is unsurprisingly Gaussian-esque, however, it is \emph{not} precisely Gaussian and more closely resembles a generalized Gaussian\footnote{A generalized Gaussian has the form $\exp \left(-t^\alpha \right)$, with $\alpha > 2$.}.
+The fact that the pulse envelope is not Gaussian is further emphasized while examining the Fourier transform of the pulse.
+If the pulse were a Gaussian, we would expect the Fourier transform to also be a Gaussian \cite{debnath, gradshteyn}.
+Instead, the magnitude of the Fourier transform has a unique Batman-like shape.
+This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---this will be a key observation in the coming subsections.
+Finally, we shall examine the derivative of the phase---essentially the chirp.
+Recall in Chapter \ref{chap:linear} the chirp was defined as coefficient of $-\frac{1}{2}iT^2$ in the exponential, by taking the negative of the derivative we would expect a linear function with a slope equal to the chirp.
+In the nonlinear case, this is what we find for moderate values of $T$.
+On the other hand, for $|T| > 1$ the relation begins to level off.
+This is in agreement with experimental results \cite{chen, rothenberg, tomlinson}.
+\\
+
+We shall now take a look at perhaps the most important feature of the pulse---the energy. \\
+
+\subsection{Energy}
+\label{chap:energy}
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}{\textwidth}
+\input{./Figures/StabilityZoom}
+\caption{Centralized for more typical $s$, and $b$ values.}
+\label{fig:energyzoom}
+\end{subfigure} \\
+\begin{subfigure}{\textwidth}
 \input{./Figures/Stability}
-\caption{}
-\label{fig:}
+\caption{Energy of the pulse within the $s$-$b$ plane.}
+\label{fig:energybig}
+\end{subfigure}
+\caption{Energy of the pulse at equilibrium. The energy is constant along the black lines.}
+\label{fig:energy}
 \end{figure}
 
-\begin{figure}[htbp]
+The energy of the pulse is directly related to the output power of the laser, and since this is not as controllable as in a regular laser, it is of great interest.
+The energy of the pulse at equilibrium\footnote{The pulse is passed through each component of the laser 40 times before the energy is computed.} is shown in Figure \ref{fig:energy}.
+In Figure \ref{fig:energyzoom} we generally find that the energy is a smooth surface that slowly decays as $s$, and $b$ increase.
+In the upper left hand region of the plot this is clearly not the case.
+The contours show that the energy is very noisy and discontinuous.
+Perhaps more surprising, as shown in Figure \ref{fig:energybig}, is that this boundary appears to become periodic as $b$ increases around $s = 0.3$.
+\\
+
+% I couldn't get this to work without having blank space on like 4 pages
+
+%\begin{wrapfigure}{O}{0.5\textwidth}
+%%\vspace{-10mm}
+%\centering
+%\input{./Figures/EffNL}
+%\caption{Approximate effective nonlinearity.}
+%\label{fig:effnl}
+%\end{wrapfigure}
+\begin{figure}[tbp]
 \centering
-\input{./Figures/StabilityZoom}
-\caption{}
-\label{fig:}
+\input{./Figures/EffNL}
+\caption{Approximate effective nonlinearity.}
+\label{fig:effnl}
+\end{figure}
+This periodic strip can be explained from the functional nature of the nonlinearity. Recall once again that from \eqref{eq:fibre} that the nonlinearity takes the form
+\begin{align*}
+F(A) &= A \textrm{e}^{i b |A|^2}.
+\end{align*}
+The strength of the nonlinearity is thus controlled by $b |A|^2$, where $|A|^2$ is the power of the pulse.
+Although not the greatest, we can approximate the power of the pulse by the energy so that $b |A|^2 \sim b E$, this gives an estimate for what shall be referred to as the effective nonlinearity.
+Figure \ref{fig:effnl} shows the effective nonlinearity at equilibrium.
+Notice that as $b$ increases along the strip $0.2 < s < 0.4$, the contours become steeper and steeper.
+In addition, the contours are at multiples of $\pi$, and exit the boundary at approximately the same places.
+Thus, the reason for this periodicity is that the strength of the nonlinearity is proportional to the modulus of the effective nonlinearity---the effective nonlinearity passes through the same points repeatedly.
+\\
+
+\begin{figure}[p]
+\centering
+\begin{subfigure}{\textwidth}
+\centering
+\input{./Figures/Unstable_Shape}%
+\input{./Figures/Unstable_Bad_Shape}
+\caption{Envelope}
+\end{subfigure} \\
+\begin{subfigure}{\textwidth}
+\centering
+\input{./Figures/Unstable_FT}%
+\input{./Figures/Unstable_Bad_FT}
+\caption{Fourier transform}
+\end{subfigure} \\
+\begin{subfigure}{\textwidth}
+\centering
+\input{./Figures/Unstable_Chirp}%
+\input{./Figures/Unstable_Bad_Chirp}
+\caption{Chirp}
+\end{subfigure}
+\caption{$s = 0.15$, $b = 2.15$, \textbf{Left:} 11 loops, \textbf{Right:} 16 loops}
+\label{fig:break}
 \end{figure}
 
-\begin{figure}[htbp]
-\centering
-\input{./Figures/StabilitySwitch}
-\caption{}
-\label{fig:}
+\subsubsection{Self-Phase Modulation and Wave Breaking}
+
+The noise in the energy exhibited for moderate to large values of $b$, and small values of $s$ is a phenomenon called \emph{wave breaking} \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}.
+Wave breaking is not limited to just optics, wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
+Wave breaking occurs because the pulse begins to interfere with itself in a way called self-phase modulation \cite{agrawal2002, agrawal2013, becker}.
+Self-phase modulation occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
+This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson}.
+These high frequencies compound with each trip around the cavity becoming parasitic very quickly---Figure \ref{fig:break} highlights this.
+Notice that the difference between this figure and Figure \ref{fig:nlstable} is a difference in $b$ of $0.05$---this difference could be as small as adding a few centimetres more of fibre between the gain and output coupler.
+The left figures show the pulse after 11 trips around the cavity, in the Fourier transform it is clear that the contributions from higher frequencies has increased---we obtain similar results as in \cite{anderson, rothenberg}.
+Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is in agreement with \cite{anderson, rothenberg}.
+The parasitic nature of the high frequency contributions is evident by examining the right figures.
+After 5 additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
+Moreover, the Fourier transform has no clear defined shape and has essentially become noise, and the chirp has grown to be highly oscillatory and unstable.
+Once the pulse has reached a state such as this, there is no turning back---the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
+\\
+
+\subsection{Convergence}
+\begin{figure}[tbp]
+\input{./Figures/Step1}
+\caption{Error of the pulse (given by \eqref{eq:error}) between iterations $99$ and $100$.}
+\label{fig:error}
 \end{figure}
 
-\begin{figure}[htbp]
-\centering
-\input{./Figures/StabilitySwitchZoom}
-\caption{}
-\label{fig:}
+\begin{figure}[p]
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step2}
+\caption{$\Delta = 2$}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step3}
+\caption{$\Delta = 3$}
+\end{subfigure} \\
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step5}
+\caption{$\Delta = 5$}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step7}
+\caption{$\Delta = 7$}
+\end{subfigure} \\
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step11}
+\caption{$\Delta = 11$}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step13}
+\caption{$\Delta = 13$}
+\end{subfigure} \\
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step16}
+\caption{$\Delta = 16$}
+\end{subfigure}
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/Step60}
+\caption{$\Delta = 60$}
+\end{subfigure} \\
+\caption{Error for various values of $\Delta$, the colour bar and axis labels have been omitted for clarity, the scales and ranges are the same as in Figure \ref{fig:error}.}
+\label{fig:deltaerror}
 \end{figure}
 
-In the linear model, the pulse converges to a Gaussian as long as $a h^2 \zeta > 1$ so that the equilibrium energy from \eqref{eq:equilenergy} is positive.
-However, this is not necessarily the case with the inclusion of the nonlinearity.
-The fibre adds a phase shift proportional to the power of the pulse, this in turn can inject higher frequency oscillations due to the dispersion which then reinforces the oscillations.
-These oscillations are then intensified with each trip around the cavity until the envelope of the pulse becomes mangled.
+To obtain a better understanding of how the pulse either converges to equilibrium, or diverges to wave breaking, we shall examine the difference between the envelopes of consecutive iterations.
+More precisely, we compute the error by
+\begin{align}
+\textrm{E} = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
+\label{eq:error}
+\end{align}
+where $\| \cdot \|_2$ denotes the $L^2$ norm, which is computed numerically using trapezoid rule.
+Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested about the phase shift between iterations.
+A plot of the error can be found in Figure \ref{fig:error}, with $i = 100$.
 \\
 
-Figure \ref{fig:pulse} shows the envelope, Fourier transform, and chirp for a stable wave as well as a broken wave.
-In the case of the stable wave the envelope and the Fourier transform are Gaussian-esque, and the chirp is a very smooth function in close agreement with \cite{chen}.
-However, in the case of the broken wave the envelope and Fourier transform are oscillatory.
-Furthermore, the chirp is highly erratic.
+Unsurprisingly, the error is largest in the region where the wave breaks.
+As mentioned in the previous subsection, the pulse does not reach a stable state.
+As a consequence the envelope varies violently, which leads to this large error.
+On the other hand, the region where the energy appeared to be stable does not have a non-zero error---there are a few reasons for this.
+First, because of the numerical calculation, for all intents and purposes an error less than $10^{-10}$ can be considered $0$.
+Understanding the other sources of these small errors requires a deeper examination.
 \\
 
-The breaking of the wave is not as predictable as one may expect---the structure of the boundary is quite rich.
-Note that in Figure \ref{fig:pulse} the wave breaks for the smaller of the two $b$ values.
-This structure is highlighted in Figure \ref{fig:DMmap} where the error is calculated by
-\begin{align*}
-\frac{\|A(\text{iteration } 40) - A(\text{iteration } 39) \|_2}{\|A(\text{iteration } 39) \|_2}.
-\end{align*}
-Additionally, Figure \ref{fig:energy} shows the energy of the pulse within the parameter space. \\
-
-One interesting feature is that in the region $0.25 < s < 0.55$ the wave does not break regardless of $b$.
-This is because $b|A|^2$ is approximately constant for a particular $s$ value, and so the phase shift added by the nonlinearity is constant, thus the wave is stable.
+The second cause of these errors is because some equilibrium states have a periodicity greater than $1$, we redefine \eqref{eq:error} to be instead
+\begin{align}
+\textrm{E}_\Delta = \frac{\| |A_i| - |A_{i-\Delta}| \|_2}{\| A_{i-\Delta} \|_2},
+\label{eq:deltaerror}
+\end{align}
+to pick up equilibrium states with period $\Delta$, again with $i = 100$.
+Figure \ref{fig:deltaerror} shows the error for an assortment of $\Delta$ values.
+There are several key observations to make, first, for $\Delta = 2$ the kidney-shaped blob in the lower right corner has vanished, thus, this entire region has a periodicity of $2$.
+Second, for $\Delta = 3$ in the upper right corner a negative triangular-shaped structure emerges.
+Lastly, $\Delta \in \left\{ 5, 7, 11, 13 \right\}$ may not seem to extract any higher order periods, however, there are in fact very small striations in the lower left.
+Up until now the $\Delta$ values have been prime since they are the building blocks for composite numbers.
+However, there are two composite $\Delta$ values of interest---the first being $16$.
+Since $16 = 2^4$ it will pick up any periodic behaviour with orders of $2, 4, 8, 16$, which are frequently found in bifurcations.
+Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible---it is an abundant number.
+This extracts orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
 \\
 
-Since some of the individual mappings are nonlinear they do not commute---changing the order of the components should lead to different results.
-The nonlinearity should still follow the gain component since that is where it is most dominant.
-Furthermore, the loss is a linear mapping and so it will commute with both dispersion and modulation.
-Therefore, the only other unique case to consider is if dispersion follows modulation.
+\begin{figure}[tbp]
+\input{./Figures/Min}
+\caption{Composite error, \eqref{eq:errorcomp}, of Figure \ref{fig:deltaerror}.}
+\label{fig:errorcomp}
+\end{figure}
+
+We now have the data to make a more meaningful estimate of the error between iterations. To compute this composite error we take the minimum of the error from each of these calculations:
+\begin{align}
+\textrm{E}_c = \min_\Delta \left\{ \textrm{E}_\Delta \right\}.
+\label{eq:errorcomp}
+\end{align}
+The intriguing structure of the composite error is shown in Figure \ref{fig:errorcomp}.
+Compared with the error from Figure \ref{fig:error} the lower right region is much more well behaved, that is, the error is a few orders of magnitude lower.
+A peculiar trait of the band between the unstable and stable regions is that within this area the pulse is in a quasi-stable state---the pulse is stable and has reach a sort of equilibrium, however, the envelope of the pulse has minute variations with no clear period.
+Additionally, there appears to be no periodicity of the envelope within the wave breaking region, further supporting the claim that the pulse here is completely unstable.
 \\
 
-Figure \ref{fig:switch} shows the effect of switching these two components.
-Overall, the large scale structure is unchanged with the exception of $0.3 < s < 0.55$ and $20 < b$.
-In this region the waveform appears to have reached a period 2 equilibrium, that is, $\mathcal{L}(\mathcal{L}(A)) = A$.
+\begin{figure}[p]
+\centering
+\begin{subfigure}{\textwidth}
+\input{./Figures/StabilitySwitchZoom}
+\caption{Centralized for more typical $s$, and $b$ values.}
+\label{fig:switchzoom}
+\end{subfigure} \\
+\begin{subfigure}{\textwidth}
+\input{./Figures/StabilitySwitch}
+\caption{Energy of the pulse within the $s$-$b$ plane.}
+\label{fig:switchbig}
+\end{subfigure}
+\caption{Energy of the pulse at equilibrium, with the modulation and dispersion blocks switched.}
+\label{fig:switch}
+\end{figure}
+
+\subsection{Permutation of Components}
+The last item we wish to consider is the order in which the components are placed.
+In Section \ref{sec:effects} a brief description for the choice of the order was given.
+We start with the loss component since this coincides with the output; the fibre nonlinearity follows the gain since this is where it has the largest impact; and the loss follows the nonlinearity in an attempt to mitigate its effect.
+Therefore, the loss is first, and the gain followed by the nonlinearity are last---leaving dispersion and modulation in the middle.
+We chose to put the dispersion block ahead of the modulator.
+However, there was no real reason behind this---modulation before dispersion is equally as valid---and in this subsection we explore the effect of modulating the pulse before it passes through the CFBG.
+\\
+
+The result of this switch is shown in Figure \ref{fig:switch}.
+As a whole, unsurprisingly, we find the same behaviour and structure, however, there are some intriguing differences.
+Perhaps the most interesting is the small island of instability in Figure \ref{fig:switchzoom} at around $s = 0.075$, $b = 1.1$ which was not present in the other ordering.
+Within this island the wave is unstable and breaks, but, curiously there is a small gap between this island and the main unstable region.
+We find more distinctions when considering the larger area in Figure \ref{fig:switchbig}.
+Again, the structure and periodic nature of the boundary is similar to before, however, this boundary has shifted rightwards to a larger $s$ value.
+Additionally, within the unstable region the density of the contour lines is much greater---suggesting it is in some sense more chaotic and random than with the components in their original permutation.
+The final main difference between the two orderings, is that in this case, the energy contours are no longer monotonic functions of $s$.
+Instead we find a parabolic shape on the top contour, and two lobes on the second contour.

### 2019-05-16 Thesis/Intro/Introduction.tex
Almost done with introduction

--- 2019-02-14 Thesis/Intro/Introduction.tex
@@
 \chapter{Introduction}
+\begin{figure}[tbp]
+\centering
+\input{./Figures/Emission}
+\caption[Comparison of pumping, spontaneous emission, and stimulated emission.]{In pumping, incident photons are absorbed by electrons which are then excited into a higher energy state (the electrons may also be excited by an electric field).
+In spontaneous emission, an electron in an excited state emits a photon and returns to the lower energy state.
+Finally, in stimulated emission, an incident photon interacts with an electron in an excited state, the electron donates its energy to the photon and returns to the lower energy state.}
+\label{fig:emission}
+\end{figure}
 
-%Classical lasers, such as a laser pointer or a Helium-Neon gas laser, are limited to a single wavelength since the light is generated by stimulated emission.
-Tuneable lasers on the other hand, have the ability to operate within a range of wavelengths \cite{bohun, burgoyne2010, yamashita}.
-As a result, tuneable lasers have applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}.
-This article is concerned with dispersion-tuned actively mode-locked (DTAML) lasers.
-The laser cavity consists of four elements: the dispersive element, the modulator, the gain fibre, and the optical coupler.
-The gain fibre consists of either an Erbium or Ytterbium doped fibre, and dispersion is generated by the highly dispersive chirped fibre Bragg grating (CFBG).
+The word laser was originally an acronym for \emph{Light Amplification by Stimulated Emission of Radiation}.
+The cavity of a standard laser---such as a HeNe laser---is composed of four main components; a highly reflecting mirror, a partially reflecting mirror, something to supply the pumping energy, and the gain medium.
+The two mirrors are at opposite ends of the cavity and serve to contain most of the light to the cavity while allowing a small amount to exit, this is the output of the laser.
+The pump energy is generally supplied by either an external light source, or electric field.
+The gain medium is what amplifies the laser light and consists of gases, such as Helium and Neon, or as a crystal, such as Neodymium-doped Yttrium Aluminium garnet (Nd:YAG).
+\\
+
+More precisely, the atoms in the gain medium are pumped with energy raising the electrons to an excited state.
+When a photon in the laser cavity interacts with such an electron it becomes amplified by stimulated emission, these two process are shown in Figure \ref{fig:emission}.
+The amplified light perpetually bounces between the two mirrors becoming more amplified with each interaction with an excited electron, a fraction of this light is able to pass through the partially reflecting mirror to become the output of the laser.
+\\
+
+This is how laser light is generated, but, laser light has two fundamental characteristics that regular light does not.
+The first is that the light is highly monochromatic---the light contains (ideally) a single frequency.
+This is in contrast with an incandescent light bulb, for example, which emits light at all wavelengths with relative intensities given by Planck's law of black-body radiation.
+The other key feature is coherence, in which all the peaks and troughs of the light overlap giving very strong constructive interference---this is why laser light can be so intense.
+Something like a light emitting diode (LED) is not laser light because, while monochromatic, the light is not coherent.
+The monochromatic nature is a result of how the light is generated, the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with LEDs).
+Note that this correspondence means that  the frequency the laser operates at is fixed, and cannot be changed.
+Coherence is achieved in the laser cavity---the cavity is carefully designed so the light resonates with the length of the cavity.
+This causes all the peaks and troughs to align, and interfere constructively.
 \\
@@
 \section{Tuneable Lasers}
-\begin{figure}[htbp]
+\begin{figure}[tbp]
 \centering
 \input{./Figures/Cavity}
-\caption[Laser Cavity]{Laser cavity schematic.}
+\caption{Typical cavity of a tuneable laser.}
 \label{fig:cavity}
 \end{figure}
+
+A tuneable laser on the other hand, has the ability to vary its wavelength by about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
+Tuneable lasers in fact lase at all of these different frequencies simultaneously.
+This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}.
+However, having the capacity to tune the wavelength comes with a cost, tuneable lasers vary considerably from standard lasers in both construction and operation, but, the central ideas are the same.
+A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}.
+Instead of being perpetually reflected back and forth, the light travels in a circular fashion around the cavity, this is known as a ring laser.
+The gain medium is still excited by an external power source, and the output passes through a partially reflecting mirror to become the output.
+However, a tuneable laser also contains a few additional components, all of which will be described in the following subsections.
 
@@
 \subsection{Modulator}
+The optical pulse in the cavity can be modulated with one of two methods---amplitude modulation, or phase modulation.
+Mathematically these can be considered equivalent since they are Fourier transforms of each other, but in practice these are accomplished by different apparatuses.
+For us, we shall assume the pulses are amplitude modulated.
+Generally, the pulse can be amplitude modulated using one of two techniques.
+The first is with an acousto-optic modulator which utilizes the acousto-optic effect where the index of refraction of the fibre is varied by a sound wave \cite{hausbook, karim}.
+The second---and more common---method uses the electro-optic effect and is called an electro-optic modulator.
+These work the same way, the fibre inside the modulator responds to an applied electric field, modifying the index of refraction \cite{agrawal2002, goldstein, hausbook, karim}.
+The shape of the electrical (sound) pulse can be controlled in such a way to provide the desired effect of modulation.
+\\
+
+Moreover, a Mach--Zehnder interferometer can be used in tandem with an acousto- or electro-optic modulator to modulate an optical pulse.
+The incident pulse is separated with a Y-waveguide, one of the two branches is then modulated, finally the two branches are recombined with another Y-waveguide \cite{alazzawi, hausbook, karim}.
+In the absence of a modulator on one of the branches the two pulses recombine into the original pulse.
+However, with modulation the two pulses are no longer identical, and so when the recombine, they interfere.
+This interference can be used to further modulate the pulse \cite{agrawal2002, agrawal2013, hausbook, karim}.
+\\
 
@@
 \end{subfigure}
-\caption{Depictions of the two methods for manufacturing FBGs. The UV light is focused on the core causing periodic constructive and destructive interference.}
+\caption[Manufacture methods of fibre Bragg gratings.]{Depictions of the two most common methods for manufacturing FBGs.
+The UV light is focused on the core causing periodic constructive and destructive interference.
+The UV light alters the refractive index of the core, causing a sinusoidal variation along the length.}
 \label{fig:fbgmake}
@@
 \end{subfigure}
-\caption{In a unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.}
+\caption[Comparison of a chirped and unchirped Gaussian pulse.]{In a unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.}
 \label{fig:chirp}
@@
 \input{./Figures/Circulator}
-\caption[Optical Circulator]{Symbol for a four port optical circulator.}
+\caption{Symbol for a four port optical circulator.}
 \label{fig:circulator}
@@
 
-\section{Generalized Nonlinear Schr\"odinger Equation}
-The standard equation for studying nonlinear optics is the generalized nonlinear Schr\"odinger equation (GNLSE) \cite{agrawal2013, burgoyne2007, ferreira, peng, shtyrina, yarutkina},
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A.
-\end{align}
-Here, $A$ is the complex pulse amplitude, $\beta_2$ and $\beta_3$ are the second-order (or group delay) and third-order dispersions, respectively.
-$\gamma$ is the coefficient of nonlinearity, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption.
+\subsection{Mode-Locking}
+\begin{figure}[tbp]
+\centering
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/ML1}
+\caption{$n = 4$}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+\input{./Figures/ML2}
+\caption{$n = 12$}
+\end{subfigure}
+\caption{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi i x \right)$.}
+\label{fig:ml}
+\end{figure}
+One of the fundamental features of a laser is coherence.
+However, in the context of tuneable lasers it is perhaps less clear what is meant by coherence since the light is no longer monochromatic.
+Instead we have a particular peak of all the frequencies aligned, this is called mode-locking---all of the different modes are locked together at a peak.
+This of course creates a very intense and short pulse of light, at this particular peak all of the frequencies constructively interfere as with a standard laser, however, deviations from the peak lead to destructive interference.
+Two examples of this are shown in Figure \ref{fig:ml}, and as expected, including more modes narrows and intensifies the pulse.
 \\
 
-This equation can be derived from the nonlinear wave equation, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
-Within the derivation comoving coordinates are used so that the reference frame propagates with the pulse at the group velocity.
-This is achieved with the substitution
-\begin{align*}
-T = t - \frac{z}{v_g}.
-\end{align*}
-
-The GNLSE takes the same form as the Schr\"odinger equation with the inclusion of the cubic nonlinear term, hence its name.
-For this reason, it is sometimes referred to as the cubic nonlinear Schr\"odinger equation.
-For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this has the addition of a quintic term to incorporate nonlinearities associated with such large powers.
-Furthermore, the $\beta$ terms come from a Taylor expansion of the wavenumber, that is,
-\begin{align*}
-k(\omega) &= k_0 + \pdiff{k}{\omega}(\omega - \omega_0) + \frac{1}{2} \pdiff[2]{k}{\omega}(\omega - \omega_0)^2 + \frac{1}{6} \pdiff[3]{k}{\omega}(\omega - \omega_0)^3 + \dots, \\
-&= \phi + \frac{1}{v_g}(\omega - \omega_0) + \frac{1}{2}\beta_2 (\omega - \omega_0)^2 + \frac{1}{6}\beta_3 (\omega - \omega_0)^3 + \dots,
-\end{align*}
-where $\phi$ is the phase shift.
-Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth \cite{agrawal2013}.
-
-\section{Previous Modelling Efforts}
-%To start off the discussion of the current modelling efforts for a tuneable laser, we begin with a review of the efforts to describe an `average' model.
-The idea is to capture some of the physical elements in the waveform described by an effective PDE, the solution of which gives the amplitude of the wave packet.
+how it's done

### 2019-05-16 Thesis/Thesis.tex
Updated CFBG figure
Updated thesis
Made some edits
Added some tikz libraries
Almost done with introduction

@@
 
+\usepackage{wrapfig}
+\usepackage{lipsum}
+\usepackage{amsthm}
+
+% Load tikz and libraries
 \usepackage{tikz}
-\usetikzlibrary{patterns,snakes}
-
+\usetikzlibrary{patterns,decorations.pathreplacing}
+\usetikzlibrary{arrows.meta}
 \usetikzlibrary{external}
@@
 
+% New dots
+\pgfdeclarepatternformonly{mydots}{\pgfqpoint{-1pt}{-1pt}}{\pgfqpoint{5pt}{5pt}}{\pgfqpoint{6pt}{6pt}}%
+{
+    \pgfpathcircle{\pgfqpoint{0pt}{0pt}}{.5pt}
+    \pgfpathcircle{\pgfqpoint{3pt}{3pt}}{.5pt}
+    \pgfusepath{fill}
+}
+
 % Code Stuff
 \include{Listing}
+
+\let\originalleft\left
+\let\originalright\right
+\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
+\renewcommand{\right}{\aftergroup\egroup\originalright}
 
@@
 \newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
+\newcommand{\Her}[2]{\widetilde{H}_{#1} \left( #2 \right)}
+\newcommand{\eps}{\varepsilon}
+\newcommand{\rect}[1]{\textrm{rect}\left( #1 \right)}
 
@@
 
-\title{A Nonlinear Model for Dispersion-Tuned Actively Mode-Locked Lasers}
+\newtheorem{theorem}{Theorem}[chapter]
+
+\title{A New Method of Modelling Tuneable Lasers with Functional Composition}
 \author{Brady Metherall}
@@
 \program{Modelling and Computational Science}
+
+%\let\originalcite\cite
+%\renewcommand{\cite}[1]{\mbox{\originalcite{#1}}}
 
@@
 A new nonlinear model is proposed for tuneable lasers.
-Using the generalized non-linear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
+Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
 These transformations are then composed to give the overall effect of one trip around the cavity.
@@
 
+{\hypersetup{linkcolor=black}
 \maketableofcontents
+}
 
@@
 
-%Red light faster than blue
-
 \include{./Intro/Introduction}
+\include{./Previous_Models/Previous}
 \include{./Model/Model}
-\include{./Linear/Linear}
 \include{./Nonlinear/Nonlinear}
+\include{./Conclusion/Conclusion}
 
@@
 
+\include{./Appendices/Lambert}
+\include{./Appendices/Dispersion}
+\include{./Appendices/Asymptotics}
+\include{./Appendices/Hermite}
+
 \chapter{Code}
+\label{chap:code}
+\lstinputlisting[language=Python]{../Lasers.py}
 
-\lstinputlisting[language=Python, lastline=60]{../Lasers.py}
+% Cite collections so they show up in the references
+\nocite{abramowitz, gowers, hernandez}
 

### 2019-05-22 Thesis/Appendices/Asymptotics.tex
Moved some appendices into the body.

@@
 % !TeX root = ../Thesis.tex
-
-\chapter{Asymptotic Expansions of the Variance}
-\label{chap:asymp}
+%\chapter{Asymptotic Expansions of the Variance}
+%\label{chap:asymp}
 We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$, as well as when $s \rightarrow \infty$. For ease of notation, \eqref{eq:var} is rewritten as
@@
 \input{./Figures/Lim_s_Infty}
-\caption{Asymptotic expansion of the variance for $s \rightarrow \infty$.}
+\caption{Asymptotic expansion of the variance as $s \rightarrow \infty$.}
 \label{fig:limsinfty}

### 2019-05-22 Thesis/Appendices/Dispersion.tex
Moved some appendices into the body.

@@
 % !TeX root = ../Thesis.tex
-
-\chapter{Spread Due to Dispersion}
-\label{chap:disp}
-
-The effect of dispersion can be computed analytically for several input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{debnath, gradshteyn}
+%\chapter{Spread Due to Dispersion}
+%\label{chap:disp}
+The effect of dispersion can be computed analytically for input pulses using \eqref{eq:disp}. In the case of a Gaussian pulse, we make use of the transforms \cite{debnath, gradshteyn}
 \begin{align*}
@@
 \end{align*}
-and then by writing in polar / rectangular coordinates:
+and then by writing in polar coordinates:
 \begin{multline*}
@@
 From this expression it is clear that at equilibrium
-\begin{align*}
+\begin{subequations}
+\begin{align}
+\label{eq:varout}
 \widetilde{\sigma}^2 \sigma^2 &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4s^4, \\
+\label{eq:chirpout}
 \widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2}, \\
+\label{eq:phase}
 \phi &= \frac{1}{2} \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right), \\
 \zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}.
-\end{align*}
+\end{align}
+\end{subequations}
 

### 2019-05-22 Thesis/Intro/Introduction.tex
Made some edits.

@@
 The word laser was originally an acronym for \emph{Light Amplification by Stimulated Emission of Radiation}.
-The cavity of a standard laser---such as a HeNe laser---is composed of four main components; a highly reflecting mirror, a partially reflecting mirror, something to supply the pumping energy, and the gain medium.
+The cavity of a standard laser---such as a HeNe laser---is composed of four main components: a highly reflective mirror, a partially reflecting mirror, something to supply the pumping energy, and the gain medium.
 The two mirrors are at opposite ends of the cavity and serve to contain most of the light to the cavity while allowing a small amount to exit, this is the output of the laser.
-The pump energy is generally supplied by either an external light source, or electric field.
-The gain medium is what amplifies the laser light and consists of gases, such as Helium and Neon, or as a crystal, such as Neodymium-doped Yttrium Aluminium garnet (Nd:YAG).
+The pump energy is generally supplied by either an external light source, or an electric field.
+The gain medium is what amplifies the laser light and consists of gases, such as Helium and Neon, or a crystal, such as Neodymium-doped Yttrium Aluminium garnet (Nd:YAG).
 \\
@@
 More precisely, the atoms in the gain medium are pumped with energy raising the electrons to an excited state.
-When a photon in the laser cavity interacts with such an electron it becomes amplified by stimulated emission, these two process are shown in Figure \ref{fig:emission}.
+For stimulated emission an incident photon triggers the emission of a photon from this excited electron \cite{alazzawi}.
+This new photon absorbs the electron's energy as it returns to its ground state, amplifying the light.
+Furthermore, the photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}.
+These processes are highlighted in Figure \ref{fig:emission}.
 The amplified light perpetually bounces between the two mirrors becoming more amplified with each interaction with an excited electron, a fraction of this light is able to pass through the partially reflecting mirror to become the output of the laser.
@@
 The other key feature is coherence, in which all the peaks and troughs of the light overlap giving very strong constructive interference---this is why laser light can be so intense.
-Something like a light emitting diode (LED) is not laser light because, while monochromatic, the light is not coherent.
+Something like a light emitting diode (LED) does not produce laser light because, while monochromatic, the light is not coherent.
 The monochromatic nature is a result of how the light is generated, the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with LEDs).
@@
 \input{./Figures/Cavity}
-\caption{Typical cavity of a tuneable laser.}
+\caption[Typical cavity of a tuneable laser.]{Typical cavity of a tuneable laser. The pulses travel clockwise around the loop.}
 \label{fig:cavity}
@@
 
-A tuneable laser on the other hand, has the ability to vary its wavelength by about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
+A tuneable laser on the other hand, has the ability to vary its wavelength by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
 Tuneable lasers in fact lase at all of these different frequencies simultaneously.
-This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}.
+This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
 However, having the capacity to tune the wavelength comes with a cost, tuneable lasers vary considerably from standard lasers in both construction and operation, but, the central ideas are the same.
 A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}.
-Instead of being perpetually reflected back and forth, the light travels in a circular fashion around the cavity, this is known as a ring laser.
+Instead of being perpetually reflected back and forth, the light travels in a circular fashion around the cavity, this is a so called ring laser.
 The gain medium is still excited by an external power source, and the output passes through a partially reflecting mirror to become the output.
-However, a tuneable laser also contains a few additional components, all of which will be described in the following subsections.
+However, a tuneable laser also contains a few additional components, each of which will be described in the following subsections.
 
@@
 Moreover, a Mach--Zehnder interferometer can be used in tandem with an acousto- or electro-optic modulator to modulate an optical pulse.
-The incident pulse is separated with a Y-waveguide, one of the two branches is then modulated, finally the two branches are recombined with another Y-waveguide \cite{alazzawi, hausbook, karim}.
+The incident pulse is separated with a Y-waveguide, one of the two branches is then modulated, and finally the two branches are recombined with another Y-waveguide \cite{alazzawi, hausbook, karim}.
 In the absence of a modulator on one of the branches the two pulses recombine into the original pulse.
@@
 \input{./Figures/CFBG}
-\caption[CFBG]{CFBG}
+\caption[Chirped fibre Bragg grating.]{Chirped fibre Bragg grating.
+Light is reflected when the wavelength coincides with the Bragg wavelength.
+This causes light with different wavelengths to penetrate to different depths.
+In turn, dispersion is either heightened or compensated---depending on the orientation.}
 \label{fig:cfbg}
@@
 
-The speed of light in an optical fibre is slightly dependent on the wavelength---this causes light with a longer wavelength to travel faster, and is known as chromatic dispersion.
+Furthermore, the speed of light in an optical fibre is slightly dependent on the wavelength---this causes light with a longer wavelength to travel faster, and is known as chromatic dispersion.
 This is a large problem in fibre optic communications, the signal can spread and potentially becomes uninterpretable after large distances.
@@
 \subsection{Optical Amplifier and Pump Laser}
-Optical amplifiers are of particular importance in fibre optic communications, they are used to restore the strength of a signal after it hass been attenuated over large distances, or when a signal is divided into multiple paths \cite{alazzawi, starodoumov}.
+Optical amplifiers are of particular importance in fibre optic communications, they are used to restore the strength of a signal after it has been attenuated over large distances, or when a signal is divided into multiple paths \cite{alazzawi, starodoumov}.
 They are also more efficient, and introduce less noise than an electrical repeater.
 In this context, the optical amplifier provides the energy of the laser \cite{alazzawi}.
-Most commonly, optical amplifiers are created  doping a length of fibre (called the gain fibre) with a rare-earth element which receives power from a pump laser \cite{agrawal2002, alazzawi, starodoumov}.
+Most commonly, optical amplifiers are created by doping a length of fibre (called the gain fibre) with a rare-earth element which receives power from a pump laser \cite{agrawal2002, alazzawi, starodoumov}.
 The most common dopant is Erbium, however, Ytterbium and Neodymium are also used---Holmium, Samarium, Thulium, and Tellurium are infrequently used as well \cite{agrawal2002}.
-The amplification is achieved with stimulated emission---a similar process to spontaneous emission.
-\\
-
-Spontaneous emission is the process in which an electron of an atom that is in an excited state emits a photon as it transitions to a lower energy state.
-The energy of the photon is equal to the energy difference between the two levels.
-On the other hand, in stimulated emission an incident photon triggers this emission \cite{alazzawi}.
-The rare-earth metal ions are excited by the pump laser, and when they interact with a photon of the tuneable laser, a new photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}.
-These processes are highlighted in Figure \ref{fig:emission}.
 \\
@@
 \end{subfigure}
-\caption{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi i x \right)$.}
+\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi i x \right)$.}
 \label{fig:ml}
@@
 However, in the context of tuneable lasers it is perhaps less clear what is meant by coherence since the light is no longer monochromatic.
-Instead we have a particular peak of all the frequencies aligned, this is called mode-locking---all of the different modes are locked together at a peak.
-This of course creates a very intense and short pulse of light, at this particular peak all of the frequencies constructively interfere as with a standard laser, however, deviations from the peak lead to destructive interference.
+Instead, we have a particular peak of all the frequencies aligned, that is, the phase shift between modes is zero.
+This process is called mode-locking---all of the different modes are locked together at a peak \cite{agrawal2013, hausbook, silfvast}.
+This of course creates a very intense and short pulse of light---as short as $5$ fs \cite{silfvast}.
+At this particular peak all of the frequencies constructively interfere as with a standard laser, however, deviations from the peak lead to destructive interference.
 Two examples of this are shown in Figure \ref{fig:ml}, and as expected, including more modes narrows and intensifies the pulse.
 \\
-
-how it's done

### 2019-05-22 Thesis/Model/Model.tex
Made some edits.

@@
 In this chapter we shall derive our new model and solve it analytically in the linear case.
-To accomplish this we shall use the ideas of the previous functional models \cite{cutler, siegman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
+To accomplish this we shall use the ideas of the previous functional models \cite{cutler, seigman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
 To alleviate some of the pitfalls mentioned in the previous chapter, we shall include all five processes involved in the modification of the pulse within the laser cavity (gain, nonlinearity, loss, dispersion, and modulation).
@@
 
-We shall start our analysis with the derivation of the functional operators for the five components. \\
+\section{Components}
+We shall begin our analysis with the derivation of the functional operators for the five components. \\
 
-\section{Components}
 \subsection{Gain}
@@
 \end{align}
-where $g(A)$ takes the form \cite{bohun, burgoyne2014, hausbook, haus1975, haus1991, haus1992, haus2000, peng, shtyrina, silfvast, usechak, yarutkina}
+where $g(A)$ takes the form \cite{bohun, burgoyne2014, hausbook, haus1975, haus1991, haus1992, haus2000, kartner, peng, shtyrina, silfvast, usechak, yarutkina}
 \begin{align}
@@
 \end{align}
-For $E \ll \Es$ the energy grows exponentially, whereas for $E \gg \Es$ the gain has saturated and so the growth is linear.
+For $E \ll \Es$ the energy will grow exponentially, whereas for $E \gg \Es$ the gain has saturated and so the growth is linear.
 To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assuming the energy increases from $E$ to $E_{\textrm{out}}$, then
@@
 \end{align*}
-this is also frequently called the Kerr nonlinearity or Kerr effect after John Kerr who discovered it in 1875.
+this is also frequently called the Kerr nonlinearity or Kerr effect after John Kerr who discovered the effect in 1875.
 As we shall see in Section \ref{chap:energy}, this is what is responsible for self-phase modulation and ultimately the degradation of the pulse \cite{desurvire, dunlop, martinez1984, tamura}.
@@
 \subsection{Modulation}
-In the average model, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{M_s}{2}T^2 A$.
+In the master equation of mode-locking, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{M_s}{2}T^2 A$.
 In this new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the average model is a Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, seigman, kuizenga1970a, martinez1984, martinez1985}, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\
@@
 \end{align}
+\label{eq:linsys}
 \end{subequations}
 
+\subsection{Dispersion}
+Each of these processes has a relatively straight forward effect, with the exception of dispersion.
+\input{./Appendices/Dispersion}
+
 \subsection{Equilibrium Shape}
-Each of these processes has a relatively straight forward effect, with the exception of dispersion.
-After dispersion, the out-going variance, $\widetilde{\sigma}^2$, can be found by computing the effect of dispersion given by \eqref{eq:disp}.
-This yields the relations
-\begin{subequations}
-\begin{align}
-\label{eq:varout}
-\widetilde{\sigma}^2 \sigma^2 &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4s^4, \\
-\label{eq:chirpout}
-\widetilde{C} &= C + (1+C^2) \frac{2 s^2}{\sigma^2}, \\
-\label{eq:phase}
-\phi &= \frac{1}{2} \arctan \left( \frac{2s^2}{\sigma^2 + 2C s^2} \right), \\
-\zeta &= \left( \frac{\sigma}{\widetilde{\sigma}} \right)^{1/2}
-\end{align}
-\end{subequations}
-for the variance, chirp, phase shift, and spread, respectively, after the dispersive element, the full details can be found in Appendix \ref{chap:disp}.
-Now, the out-going variance and chirp can be eliminated from this system of equations using \eqref{eq:varcond} and \eqref{eq:chirpcond}:
+Now that the effect of dispersion is know analytically, the system \eqref{eq:linsys} can be solved.
+The out-going variance and chirp can be eliminated from this system of equations using \eqref{eq:varcond} and \eqref{eq:chirpcond}:
 \begin{align*}
@@
 \end{align}
-The asymptotic expansions of the variance in the case of $s \rightarrow 0$, and $s \rightarrow \infty$ are derived in Appendix \ref{chap:asymp}. \\
+
+\subsection{Asymptotic Expansion of the Variance}
+While \eqref{eq:equilvar} is useful, so too is the asymptotic behaviour.
+\input{./Appendices/Asymptotics}
 

### 2019-05-22 Thesis/Nonlinear/Nonlinear.tex
Made some edits.

@@
 \input{./Figures/LinearPlot}
-\caption{Equilibrium energy, and peak power of the pulse as a function of $s$. The thin black line is to highlight that the energy is \emph{not} linearly related to $s$.}
+\caption[Equilibrium energy, and peak power of the pulse as a function of $s$.]{Equilibrium energy, and peak power of the pulse as a function of $s$.
+The thin black line is to highlight that the energy is \emph{not} linearly related to $s$.}
 \label{fig:valenergy}
@@
 \end{subfigure}
-\caption{Simulation with $s = 0.15$, and $b = 2.1$ after 15 circuits.}
+\caption[Envelope, Fourier transform, and chirp of the pulse---stable case.]{Simulation with $s = 0.15$, and $b = 2.1$ after 15 circuits.}
 \label{fig:nlstable}
@@
 \input{./Figures/StabilityZoom}
-\caption{Centralized for more typical $s$, and $b$ values.}
+\caption{Centralized for typical $s$, and $b$ values.}
 \label{fig:energyzoom}
@@
 \end{subfigure}
-\caption{Energy of the pulse at equilibrium. The energy is constant along the black lines.}
+\caption[Energy of the pulse at equilibrium.]{Energy of the pulse at equilibrium. The energy is constant along the black lines.}
 \label{fig:energy}
@@
 \end{subfigure}
-\caption{$s = 0.15$, $b = 2.15$, \textbf{Left:} 11 loops, \textbf{Right:} 16 loops}
+\caption[Envelope, Fourier transform, and chirp of the pulse---unstable case.]{$s = 0.15$, $b = 2.15$, \textbf{Left:} 11 loops, \textbf{Right:} 16 loops}
 \label{fig:break}
@@
 After 5 additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
-Moreover, the Fourier transform has no clear defined shape and has essentially become noise, and the chirp has grown to be highly oscillatory and unstable.
+Moreover, the Fourier transform has no clear structure and has essentially become noise, and the chirp has grown to be highly oscillatory and unstable.
 Once the pulse has reached a state such as this, there is no turning back---the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
@@
 \input{./Figures/Step1}
-\caption{Error of the pulse (given by \eqref{eq:error}) between iterations $99$ and $100$.}
+\caption[Error of the pulse.]{Error of the pulse (given by \eqref{eq:error}) between iterations $99$ and $100$.}
 \label{fig:error}
@@
 \end{subfigure} \\
-\caption{Error for various values of $\Delta$, the colour bar and axis labels have been omitted for clarity, the scales and ranges are the same as in Figure \ref{fig:error}.}
+\caption[Error for various values of $\Delta$.]{Error for various values of $\Delta$, the colour bar and axis labels have been omitted for clarity, the scales and ranges are the same as in Figure \ref{fig:error}.}
 \label{fig:deltaerror}
@@
 Lastly, $\Delta \in \left\{ 5, 7, 11, 13 \right\}$ may not seem to extract any higher order periods, however, there are in fact very small striations in the lower left.
-Up until now the $\Delta$ values have been prime since they are the building blocks for composite numbers.
+So far, the $\Delta$ values have been prime since they are the building blocks for composite numbers.
 However, there are two composite $\Delta$ values of interest---the first being $16$.
@@
 \input{./Figures/Min}
-\caption{Composite error, \eqref{eq:errorcomp}, of Figure \ref{fig:deltaerror}.}
+\caption[Composite error.]{Composite error, \eqref{eq:errorcomp}, of Figure \ref{fig:deltaerror}.}
 \label{fig:errorcomp}
@@
 \input{./Figures/StabilitySwitchZoom}
-\caption{Centralized for more typical $s$, and $b$ values.}
+\caption{Centralized for typical $s$, and $b$ values.}
 \label{fig:switchzoom}

### 2019-05-22 Thesis/Previous_Models/Previous.tex
Made some edits.

@@
 In this chapter we shall explore the previous modelling efforts by first reviewing the classic equations used in nonlinear optics.
-We will then build upon this to the master equation of mode-locking.
-The solutions to this will briefly be studied before diving into `discretized' functional models.
+We will then build upon this to the master equation of mode-locking, where the solutions to this will briefly be studied before diving into `discretized' functional models.
 \\
@@
 \end{align*}
-Here, $A$ is the complex pulse amplitude, $\beta_2$ is the second-order---or group delay---dispersion, and $\gamma$ is the coefficient of nonlinearity.
+Here $A$ is the complex pulse amplitude, $\beta_2$ is the second-order---or group delay---dispersion, and $\gamma$ is the coefficient of nonlinearity or Kerr coefficient.
 In practice, this equation lacks a few key terms.
@@
 \end{align}
-where $\beta_3$ is the third order effect of dispersion, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption. \\
+where $\beta_3$ is the third order coefficient of dispersion, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption. \\
 
@@
 In the least complicated case, the modulation and nonlinearity are omitted resulting in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}.
-Now, with the inclusion of the nonlinearity a similar solution is found, however, it is now it the form of a chirped hyperbolic secant \cite{haus1991, usechak}.
+With the inclusion of the nonlinearity a similar solution is found, however, it is now it the form of a chirped hyperbolic secant \cite{haus1991, usechak}.
 Both of these are unsurprising since this reduces to the soliton solution of the NLSE \cite{ferreira}.
@@
 \section{Discrete Functional Model}
-While solution to the master equation yields reasonable results, it is not necessarily representative of what happens within the laser cavity.
+While solutions to the master equation yield reasonable results, it is not necessarily representative of what happens within the laser cavity.
 The issue with \eqref{eq:meml} is that it assumes each process effects the pulse continuously within the cavity.
-As highlighted by Figure \ref{fig:cavity}, this is a poor assumption.
+As highlighted by Figure \ref{fig:cavity}, this is a rather poor assumption.
 Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG, the pulse is only amplified within the Erbium-doped fibre, etc.
@@
 Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator.
-This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{siegman}, which they then greatly added to the following year \cite{kuizenga1970a}.
+This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{seigman}, which they then greatly added to the following year \cite{kuizenga1970a}.
 Kuizenga and Seigman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}.
@@
 Despite these attempts, several short-comings exist.
-The clearest is that none of these models have contained each block--either the nonlinearity or the modulation have been omitted.
-In the context of tuneable lasers each component plays an important role.
+The clearest is that none of these models have contained every block--either the nonlinearity or the modulation have been omitted.
+In the framework of tuneable lasers each component plays an important role.
 Another key drawback is that the functional operations of some of the components are somewhat phenomenological.

### 2019-05-22 Thesis/Thesis.tex
Added acknowledgements.

@@
 A new nonlinear model is proposed for tuneable lasers.
-Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component in the cavity.
+Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component within the laser cavity.
 These transformations are then composed to give the overall effect of one trip around the cavity.
 The linear version of this model is solved analytically, and the nonlinear version numerically.
-A consequence of this model being nonlinear is that it is able to exhibit wave breaking which prior models could not.
+A consequence of the nonlinear nature of this model is that it is able to exhibit wave breaking which prior models could not.
 We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
@@
 \makeacknowledgements{
-Thank some people that you like here.
+First and most importantly, I would like to thank my supervisor and mentor, Dr.
+Sean Bohun, for his assistance, guidance, and inspiration over the past two years.
+I would also like to thank my fellow modelling and computational science students for helping make the last two years enjoyable.
+\\
+
+Lastly, I would like to thank my mom and dad, and grandparents for their endless support and encouragement over the past two years.
 }
@@
 \include{./Appendices/Lambert}
-\include{./Appendices/Dispersion}
-\include{./Appendices/Asymptotics}
+%\include{./Appendices/Dispersion}
+%\include{./Appendices/Asymptotics}
 \include{./Appendices/Hermite}

### 2019-05-28 Thesis/Appendices/Asymptotics.tex
Finished corrections

@@
 %\label{chap:asymp}
-We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$, as well as when $s \rightarrow \infty$. For ease of notation, \eqref{eq:var} is rewritten as
+We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$ (a very short CFBG), as well as when $s \rightarrow \infty$ (a very long CFBG).
+For ease of notation, \eqref{eq:var} is rewritten as
+\begin{align}
+\label{eq:asymp}
+\frac{1}{4} x^4 = \eps \left( -x^3 + 5x^2 - 8x + 4 \right),
+\end{align}
+where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
+\begin{align}
+\label{eq:series}
+x = x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \cdots
+\end{align}
+with $0 < \alpha < \beta$. Then, expanding \eqref{eq:asymp} using \eqref{eq:series} and collecting terms, at $\bigO{1}$,
 \begin{align*}
-\frac{1}{4} x^4 = \eps \left( -x^3 + 5x^2 - 8x + 4 \right),
+\frac{1}{4} x_0^4 = 0,
 \end{align*}
-where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
+and so, $x_0 = 0$. Knowing this, we consider how to balance
 \begin{align*}
-x = x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \dots
+\frac{1}{4} x_1^4 \eps^{4\alpha} = \eps \left( -x_1^3 \eps^{3\alpha} + 5x_1^2 \eps^{2\alpha} - 8x_1 \eps^\alpha + 4 \right).
 \end{align*}
-with $0 < \alpha < \beta$. Then,
+In order to have dominant balance it must be that the left hand side balances with the final term of the right hand side, that is, $4\alpha = 1$, or $\alpha = \frac{1}{4}$.
+Therefore, at $\bigO{\eps}$ $x_1^4 = 16$, or
 \begin{align*}
-\bigO1 : \frac{1}{4} x_0^4 = 0,
-\end{align*}
-and so, $x_0 = 0$. Knowing this, up to the next order we have
-\begin{align*}
-\frac{1}{4} x_1^4 \eps^{4\alpha} = \eps \left( -x_1^3 \eps^{3\alpha} + 5x_1^2 \eps^{2\alpha} - 8x_1 \eps^\alpha + 4 \right)
-\end{align*}
-in order to have dominant balance it must be that the left hand side balances with the final term of the right hand side, that is, $4\alpha = 1$, or $\alpha = \frac{1}{4}$. Therefore,
-\begin{align*}
-\bigO\eps : \frac{1}{4} x_1^4 &= 4, \\
 (x_1 - 2)(x_1 + 2)(x_1^2 + 4) &= 0,
@@
 Hence, $\frac{3}{4} + \beta = 1 + \alpha = \frac{5}{4}$, thus, $\beta = \frac{1}{2}$.
-Now,
+Now, at $\bigO{\eps^{5/4}}$,
 \begin{align*}
-\bigO{\eps^{5/4}}: \frac{1}{4} 4 x_1^3 x_2 &= -8x_1, \\
-x_2 &= -2,
+\frac{1}{4} 4 x_1^3 x_2 &= -8x_1,
 \end{align*}
-where the additional $4$ comes from the binomial expansion. Finally, up to second(?***) order
-\begin{align*}
-x &\approx 2 \eps^{1/4} - 2 \eps^{1/2}, \\
-\sigma^2 &\approx 2 \left( s - s^2 \right),
-\end{align*}
-this is shown in Figure \ref{fig:lims0}.
+and with the choice of $x_1$, $x_2 = 2$. Combining these results gives $x = 2 \eps^{1/4} - 2 \eps^{1/2} + \bigO{\eps^{3/4}}$, or $\sigma^2 = 2 s \left( 1 - s \right) + \bigO{s^3}$,
+this is shown in Figure \ref{fig:lims0}. \\
 \begin{figure}[tbp]
@@
 We shall now consider the other limit, when $s \rightarrow \infty$. Using a similar substitution we instead write \eqref{eq:var} as
+\begin{align}
+\label{eq:asymp2}
+\frac{1}{4} \eps x^4 = -x^3 + 5x^2 - 8x + 4,
+\end{align}
+where $x = \sigma^2$, and $\eps = s^{-4}$ instead so that we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
+\begin{align}
+\label{eq:series2}
+x = \eps^{-\xi} \left( x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \cdots \right).
+\end{align}
+The reason for this is because the equation is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root.
+As with before, we obtain dominant balance when the quartic term balances with the cubic term which occurs when $1 - 4 \xi = -3 \xi$, or $\xi = 1$.
+Then to $\bigO{\eps^{-3}}$, expression \eqref{eq:asymp2} gives
 \begin{align*}
-\frac{1}{4} \eps x^4 = -x^3 + 5x^2 - 8x + 4,
-\end{align*}
-where $x = \sigma^2$, and $\eps = s^{-4}$ instead so that we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
-\begin{align*}
-x = \eps^{-\xi} \left( x_0 + x_1 \eps^\alpha + x_2 \eps^\beta + \dots \right).
-\end{align*}
-The reason for this is because the equation is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root.
-As with before, we obtain dominant balance when the quartic term balances with the cubic term:
-\begin{align*}
-1 - 4 \xi &= -3 \xi, \\
-\xi &= 1.
-\end{align*}
-Then,
-\begin{align*}
-\bigO{\eps^{-3}}: \frac{1}{4} x_0^4 &= -x_0^3, \\
 x_0^3 (x_0 + 4) &= 0,
 \end{align*}
-we shall choose $x_0 = 0$---since $x \geq 0$. Unlike up until this point, we obtain dominant balance when the right hand side dominates the left hand side, this is achieved when $\alpha = 1$. Now,
+we shall choose $x_0 = 0$---since $x \geq 0$. Continuing, we obtain a dominant balance when $\alpha = 1$. So the next condition occurs at $\bigO{1}$ where
 \begin{align*}
-\bigO1 : 0 &= -x_1^3 + 5x_1^2 - 8x_1 + 4, \\
-&= -(x_1 - 1)(x_1 - 2)^2,
+0 = -x_1^3 + 5x_1^2 - 8x_1 + 4 = -(x_1 - 1)(x_1 - 2)^2,
 \end{align*}
 so either $x_1 = 1$ or $x_1 = 2$, we shall see in the next step that we can eliminate one of these.
-The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$:
+The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$.
+Now at $\bigO{\eps}$,
 \begin{align*}
-\bigO\eps : \frac{1}{4} x_1^4 &= -3x_1^2 x_2 + 5\cdot2 x_1 x_2 - 8x_2, \\
-&= -x_2 (3x_1 - 4)(x_1 - 2),
+\frac{1}{4} x_1^4 = -3x_1^2 x_2 + 5\cdot2 x_1 x_2 - 8x_2 = -x_2 (3x_1 - 4)(x_1 - 2),
 \end{align*}
-where again, the coefficients come from the binomial expansions;
-from this it is clear that
+where again, the coefficients come from the binomial expansions. From this it is clear that $x_2$ is unique provided $x_1 \ne 2$ and
 \begin{align*}
-x_2 &= \frac{-x_1^4}{4(3x_1 - 4)(x_1 - 2)},
+x_2 &= \frac{-x_1^4}{4(3x_1 - 4)(x_1 - 2)}.
 \end{align*}
-and that $x_1 \ne 2$. Thus, $x_1 = 1$, $x_2 = -\frac{1}{4}$, and
+Thus, $x_1 = 1$, $x_2 = -\frac{1}{4}$, and
 \begin{align*}
-x = 1 - \frac{1}{4} \eps + x_2 \eps^{\gamma - 1} + \dots.
+x = 1 - \frac{1}{4} \eps + x_2 \eps^{\gamma - 1} + \cdots.
 \end{align*}
-Expanding one final term we find $\gamma = 3$, and
+Expanding one final term we find $\gamma = 3$, and to $\bigO{\eps^2}$,
 \begin{align*}
-\bigO{\eps^2}: \frac{1}{4} 4x_2 x_1^3 &= -(3x_3 x_1^2 + 3x_2^2 x_1) + 5(2x_3 x_1 + x_2^2) - 8(x_3).
+\frac{1}{4} 4x_2 x_1^3 &= -(3x_3 x_1^2 + 3x_2^2 x_1) + 5(2x_3 x_1 + x_2^2) - 8x_3.
 \end{align*}
@@
 \begin{align*}
-x &\approx 1 - \frac{1}{4}\eps + \frac{3}{8}\eps^2, \\
-\sigma^2 &\approx 1 - \frac{1}{4s^4} + \frac{3}{8s^8},
+x &= 1 - \frac{1}{4}\eps + \frac{3}{8}\eps^2 + \bigO{\eps^3},
 \end{align*}
-this approximation is shown in Figure \ref{fig:limsinfty}.
+or,
+\begin{align*}
+\sigma^2 &= 1 - \frac{1}{4s^4} + \frac{3}{8s^8} + \bigO{s^{-12}}
+\end{align*}
+this approximation is shown in Figure \ref{fig:limsinfty}. \\
 \begin{figure}[tbp]
@@
 \end{figure}
+
+In conclusion, the asymptotic expansions of the observables are
+\begin{align*}
+\sigma^2 &=
+\begin{cases*}
+2s(1 - s) + \bigO{s^3} & $s \rightarrow 0$ \\
+1 - \frac{1}{4s^4} + \frac{3}{8s^8} + \bigO{s^{-12}} & $s \rightarrow \infty$
+\end{cases*}
+& \phi &=
+\begin{cases*}
+\frac{1}{2}s - \frac{1}{24}s^3 + \bigO{s^5} & $s \rightarrow 0$ \\
+\frac{\pi}{4} - \frac{1}{2s^2} + \frac{5}{12s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
+\end{cases*} \\
+C &=
+\begin{cases*}
+1 - s + \frac{1}{2}s^2 + \bigO{s^3} & $s \rightarrow 0$ \\
+\frac{1}{2s^2} - \frac{3}{8s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
+\end{cases*}
+& \zeta &=
+\begin{cases*}
+1 - \frac{1}{2}s + \frac{1}{8}s^2 + \bigO{s^3} & $s \rightarrow 0$ \\
+\frac{1}{4^{1/4}s} - \frac{3 \cdot 4^{3/4}}{32 s^5} + \bigO{s^{-9}} & $s \rightarrow \infty$.
+\end{cases*}
+\end{align*}
+The general form of these is as expected.
+When $s \rightarrow 0$, we effectively remove the CFBG from the cavity.
+This causes the pulse to be perpetually modulated, and so, the pulse approaches a $\delta$ function, and therefore, $\sigma^2 \rightarrow 0$.
+Moreover, since $\zeta$ is the ratio of the amplitude of the pulse before and after dispersion, $\zeta \rightarrow 1$.
+Similarly, $\phi \rightarrow 0$ since nothing in the circuit has the capacity to provide a phase shift.
+In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, while conserving its energy.
+Because of this, the variance approaches unity because the shape is entirely determined by the modulation function.
+Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimal.

### 2019-05-28 Thesis/Appendices/Hermite.tex
Moved some appendices into the body.
Finished corrections

@@
 % !TeX root = ../Thesis.tex
-
-\chapter{Span of Gaussians in $L^2$}
-\label{chap:gauss}
+%\chapter{Span of Gaussians in $L^2$}
+%\label{chap:gauss}
+\section{Span of Gaussians in $L^2$}
 In order to show that Gaussians span $L^2$, we shall start our analysis with the span of the Hermite polynomials in $L^2$.
@@
 \begin{align*}
-\left< f, g \right> = \int_\mathbb{R} f g \textrm{e}^{-x^2} \df x,
+\left< f, g \right> = \int_\mathbb{R} f(x) g(x) \textrm{e}^{-x^2} \df x,
 \end{align*}
@@
 \begin{align*}
-\left< H_m(x), H_n(x) \right> = \sqrt{\pi} 2^n n! \delta_{mn}
+\left< H_m, H_n \right> = \sqrt{\pi} 2^n n! \delta_{mn}
 \end{align*}
@@
 \begin{align*}
-\left< f, g \right> = \int_\mathbb{R} f g \, \df x,
+\left< f, g \right> = \int_\mathbb{R} f(x) g(x) \, \df x,
 \end{align*}
@@
 \label{thm:hermite}
-The set of Gaussian--Hermite polynomials, $\mathcal{G} = \{ \Her{n}{x} : n \in \mathbb{N} \}$, spans $L^2$.
+The set of Gaussian--Hermite polynomials, $\mathcal{G}(\mathbb{R}) = \{ \Her{n}{x} : x \in \mathbb{R}, n \in \mathbb{N} \}$, spans $L^2(\mathbb{R})$.
 \end{theorem}
 \begin{proof}
-The Gaussian--Hermite polynomials are an orthogonalization of the set $\Xi = \{x^n \textrm{e}^{-x^2/2} : n \in \mathbb{N}\}$, and therefore, have the same span \cite{kreyszig, szego}.
+The Gaussian--Hermite polynomials are an orthogonalization of the set $\Xi = \{x^n \textrm{e}^{-x^2/2} : x \in \mathbb{R}, n \in \mathbb{N}\}$, and therefore, have the same span \cite{kreyszig, szego}.
 Thus, it is sufficient to show that $\Xi$ spans $L^2$.
-Suppose there exists an $f \in L^2$ such that $\left< f, \Her{n}{x} \right> = 0$ for all $n$, or equivalently, that $\left< f, x^n \textrm{e}^{-x^2/2} \right> = 0$ for all $n$ so that it is not in the span of $\mathcal{G}$.
+Suppose there exists an $f \in L^2$ such that $\left< f, \widetilde{H}_n \right> = 0$ for all $n$, or equivalently, that $\left< f, g_n \right> = 0$ for $g_n(x) = x^n \textrm{e}^{-x^2/2}$ for all $n$ so that it is not in the span of $\mathcal{G}(\mathbb{R})$.
 \\
@@
 \begin{align*}
-F(z) = \frac{1}{\sqrt{2\pi}}\int_\mathbb{R} f \textrm{e}^{zx} \textrm{e}^{-x^2/2} \, \df x,
+F(z) = \frac{1}{\sqrt{2\pi}}\int_\mathbb{R} f(x) \textrm{e}^{zx} \textrm{e}^{-x^2/2} \, \df x,
 \end{align*}
-noting that $f \textrm{e}^{zx} \textrm{e}^{-x^2/2} \in L^2$ by the Cauchy--Schwarz inequality \cite{griffel, kolmogorov}, so $F$ converges, and that $F$ is holomorphic.
+noting that $f(x) \textrm{e}^{zx} \textrm{e}^{-x^2/2} \in L^2(\mathbb{R})$ by the Cauchy--Schwarz inequality \cite{griffel, kolmogorov}, so $F$ converges, and that $F$ is holomorphic.
 The first exponential can be expanded into its Maclaurin series, then with Fubini's theorem we obtain
 \begin{align*}
-F(z) = \frac{1}{\sqrt{2\pi}} \sum_{n = 0}^{\infty} \frac{z^n}{n!} \int_\mathbb{R} f x^n \textrm{e}^{-x^2/2} \, \df x.
+F(z) = \frac{1}{\sqrt{2\pi}} \sum_{n = 0}^{\infty} \frac{z^n}{n!} \int_\mathbb{R} f(x) x^n \textrm{e}^{-x^2/2} \, \df x.
 \end{align*}
@@
 \begin{align*}
-\int_\mathbb{R} f x^n \textrm{e}^{-x^2/2} \, \df x &= \left< f, x^n \textrm{e}^{-x^2/2} \right>, \\
-&=0,
+\int_\mathbb{R} f(x) x^n \textrm{e}^{-x^2/2} \, \df x &= \left< f, g_n \right> = 0,
 \end{align*}
@@
 \begin{align*}
-0 &= F(z), \\
-&= F(i \omega), \\
-&= \FT{f \textrm{e}^{-x^2/2}},
+0 &= F(z) = F(i \omega) = \FT{f \textrm{e}^{-x^2/2}},
 \end{align*}
-and now it is clear that $f \textrm{e}^{-x^2/2} = 0$ almost everywhere, therefore, $f = 0$ almost everywhere. \\
+and now it is clear that $f(x) \textrm{e}^{-x^2/2} = 0$ almost everywhere, therefore, $f(x) = 0$ almost everywhere. \\
 \end{proof}
@@
 \label{eq:paracyl}
-\diff[2]{\Her{n}{x}}{x} - \left( x^2 - 2n - 1 \right) \Her{n}{x} = 0,
+\diff[2]{\Her{n}{x}}{x} - \left( x^2 - 2n - 1 \right) \Her{n}{x} = 0.
 \end{align}
-this has the form of the parabolic cylinder functions \cite{miller}, and indeed the Gaussian--Hermite polynomials can be expressed in terms of parabolic cylinder functions \cite{hochstrasser, miller}.
+This has the form of the parabolic cylinder functions \cite{miller}, and indeed the Gaussian--Hermite polynomials can be expressed in terms of parabolic cylinder functions \cite{hochstrasser, miller}.
 Moreover, \ref{eq:paracyl} can also be written in Sturm--Liouville form as
@@
 \end{align*}
-By the spectral theorem \cite{griffel, higson, kreyszig}, this suggests that the Gaussian--Hermite polynomials form an orthogonal set with the weighting function $w(x) = 1$, and are complete in $L^2$.
-Using this result, we can now show that Gaussian functions also span $L^2$ with the following theorem.
+By the spectral theorem \cite{griffel, higson, kreyszig}, this suggests that the Gaussian--Hermite polynomials form an orthogonal set with the weighting function $w(x) = 1$, and are complete in $L^2(\mathbb{R})$.
+Using this result, we can now show that Gaussian functions also span $L^2(\mathbb{R})$ with the following theorem.
 \\
@@
 \label{thm:gaussian}
-Gaussians of a single variance span $L^2$.
+Gaussians of a single variance span $L^2(\mathbb{R})$.
 \end{theorem}
@@
 \begin{align*}
-f = \sum_{n = 0}^\infty a_n \Her{n}{x}.
+f(x) = \sum_{n = 0}^\infty a_n \Her{n}{x}.
 \end{align*}
-Using a similar idea to \cite{calcaterra2, calcaterra}, we shall now expand the Gaussian--Hermite polynomials into their definition
+Using a similar idea to \cite{calcaterra2, calcaterra}, we shall now expand the Gaussian--Hermite polynomials using their definition
 \begin{align*}
-f = \sum_{n = 0}^\infty a_n (-1)^n \textrm{e}^{x^2/2} \diff[n]{}{x} \textrm{e}^{-x^2}.
+f(x) = \sum_{n = 0}^\infty a_n (-1)^n \textrm{e}^{x^2/2} \diff[n]{}{x} \textrm{e}^{-x^2}.
 \end{align*}
@@
 \begin{align}
-f = \sum_{n = 0}^\infty a_n (-1)^n \textrm{e}^{x^2/2} \left[ \lim_{h \rightarrow 0} \frac{1}{h^n} \sum_{i = 0}^n (-1)^i \binom{n}{i} \exp\left( -\left( x + h\left( \frac{n}{2} - i \right) \right)^2 \right) \right].
+f(x) = \sum_{n = 0}^\infty a_n (-1)^n \textrm{e}^{x^2/2} \left[ \lim_{h \rightarrow 0} \frac{1}{h^n} \sum_{i = 0}^n (-1)^i \binom{n}{i} \exp\left( -\left( x + h\left( \frac{n}{2} - i \right) \right)^2 \right) \right].
 \label{eq:gs}
@@
 \input{./Figures/GaussMod}
-\caption{$N = 20$, $h = 0.1$}
+\caption[Gaussian series for a particular modulation function.]{$N = 20$, $h = 0.1$}
 \label{fig:gaussmod}

### 2019-05-28 Thesis/Intro/Introduction.tex
Finished corrections

@@
 \subsection{Optical Coupler and Laser Output}
-The optical coulper is a device that splits its input into two outputs---one continuing through the laser cavity, while the other exits the cavity to become the output of the laser.
+The optical coupler is a device that splits its input into two outputs---one continuing through the laser cavity, while the other exits the cavity to become the output of the laser.
 There are multiple devices that can accomplish this, however, the simplest is a partially reflecting mirror \cite{alazzawi}.
@@
 
-FBGs are manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
+FBGs can be manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
 Both methods cause the periodic nature of the refractive index through interference.
@@
 where $\lambda_B$ is the Bragg wavelength, $\Lambda$ is the period of the grating, and $\bar{n}$ is the average index of refraction.
-This reflects wavelengths close to $\lambda_B$, known as the stop-band.
+Ideally, only light with a wavelength of $\lambda_B$ would be reflected, however, there is a very narrow neighbourhood around $\lambda_B$ in which wavelengths are partially reflected too, the characteristic width of this region is known as the stop-band.
 \\
@@
 Figure \ref{fig:chirp} shows examples of chirped and unchirped Gaussian pulses---the most common type of chirp is linear chirp, where the frequency varies linearly across the pulse.
-Because of this, the oscillations are characterized by $\exp \left( i C x^2 \right)$, where $C x$ is the linear variation of the wave number, and $C$ is the chirp parameter.
+Because of this, for a spatially varying frequency the oscillations are characterized by $\exp \left( i k(x) x \right) = \exp \left( i C x^2 \right)$, where $k(x) = Cx$ is the linear variation of the wave number, and $C$ is the chirp parameter.
 By using a chirped phase-mask a chirped fibre Bragg grating (CFBG) can be created.
@@
 This causes most wavelengths to be reflected by a CFBG, but with each wavelength penetrating to a different depth.
+Note that a monotonic chirping ensures that all the wavelengths are simultaneously supported.
 A consequence of this is that a time delay is created between wavelengths---this is depicted in Figure \ref{fig:cfbg} with the upper portion showing  the refractive index as a function of the depth.
@@
 \end{subfigure}
-\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi i x \right)$.}
+\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi x \right)$.}
 \label{fig:ml}
@@
 At this particular peak all of the frequencies constructively interfere as with a standard laser, however, deviations from the peak lead to destructive interference.
-Two examples of this are shown in Figure \ref{fig:ml}, and as expected, including more modes narrows and intensifies the pulse.
+Two examples of this are shown in Figure \ref{fig:ml}, and as expected, including more modes simultaneously narrows and intensifies the pulse.
 \\

### 2019-05-28 Thesis/Model/Model.tex
Finished corrections

@@
 To alleviate some of the pitfalls mentioned in the previous chapter, we shall include all five processes involved in the modification of the pulse within the laser cavity (gain, nonlinearity, loss, dispersion, and modulation).
-In addition to this, the functional operations associated with each component will be derived from \eqref{eq:nlse}, with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.
-\\
+In addition to this, the functional operations associated with each component will be derived from \eqref{eq:nlse},
+\begin{align*}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
+\end{align*}
+with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator. \\
 
@@
 \end{align*}
-and by exponentiating, rearranging, and applying $W$, the Lambert $W$ function\footnote{see Appendix \ref{chap:lambertw}},
+and by exponentiating, rearranging, and applying $W$, the Lambert $W$ function\footnote{See Appendix \ref{chap:lambertw}.},
 \begin{align*}
-W \left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) \\
-&= \frac{E_{\textrm{out}}}{\Es},
+W \left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es},
 \end{align*}
@@
 \begin{align*}
-G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A \\
-&= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
+G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
 \end{align*}
@@
 However, for simplicity and because of the nature of the grating, the third order effects will be neglected \cite{agrawal2013, ferreira}---we set $\beta_3=0$ for the subsequent analysis.
+\\
 
@@
 
-Despite assuming a Gaussian modulation the following solution can be generalized to any modulation function in $L^2$ since Gaussians in fact span $L^2$ as shown in Appendix \ref{chap:gauss}. \\
+Despite assuming a Gaussian modulation the following solution can be generalized to any modulation function in $L^2$ since Gaussians in fact span $L^2$ as will be shown shortly. \\
+
+\input{./Appendices/Hermite}
 
 \section{Non-Dimensionalization}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lclc}
-Parameter & Symbol & Value & Sources \\
-\noalign{\global\arrayrulewidth=1.5pt}\hline
-Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, usechak, yarutkina} \\
-Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
-Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, usechak, yarutkina} \\
-Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
-Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
-Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
-Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, yarutkina} \\
-Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyne2014, burgoyneemail} \\
-Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
-Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
-Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
-\hline
-\end{tabular}
-\caption{Orders of magnitude of various parameters.}
-\label{tab:values}
-\end{center}
-\end{table}
 
@@
 The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is related to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent:
+Specifically, the time shall be scaled by the characteristic modulation time which is related to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent with the energy:
 \begin{align*}
@@
 \end{align*}
-which control the behaviour of the laser.
+which characterize the behaviour of the laser.
+
+\begin{table}[tbp]
+\centering
+\begin{tabular}{lcll}
+Parameter & Symbol & Value & Sources \\
+\noalign{\global\arrayrulewidth=1.5pt}\hline
+Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, usechak, yarutkina} \\
+Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
+Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, usechak, yarutkina} \\
+Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
+Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
+Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
+Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, yarutkina} \\
+Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyne2014, burgoyneemail} \\
+Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
+Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
+Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
+\hline
+\end{tabular}
+\caption{Orders of magnitude of various parameters.}
+\label{tab:values}
+\end{table}
 
@@
 Finally, the pulse travels through the gain fibre to be amplified, and then we consider the effect of the nonlinearity since this is the region where the power is maximized.
+Note that in general the functional operators of the components do not commute, and therefore the order is indeed important---in contrast to the previous models.
+This is especially the case of dispersion due to the Fourier transform.
 The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, seigman, kuizenga1970a, martinez1984, martinez1985}, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, seigman, kuizenga1970a, martinez1984, martinez1985} (Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\
@@
 
-\subsection{Dispersion}
+\subsection{Spread Due to Dispersion}
 Each of these processes has a relatively straight forward effect, with the exception of dispersion.
@@
 \begin{align*}
-\widetilde{\sigma}^2 &= \frac{\sigma^2}{1 - \sigma^2}, \\
-\widetilde{C} &= C \frac{1}{1 - \sigma^2}.
+\widetilde{\sigma}^2 &= \frac{\sigma^2}{1 - \sigma^2}, & \widetilde{C} &= C \frac{1}{1 - \sigma^2}.
 \end{align*}
@@
 \begin{align}
-\nonumber
-C &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} \pm \sqrt{\frac{\sigma^8}{16s^4(1 - \sigma^2)^2} - 1}, \\
 \label{eq:equilchirp}
-&= \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}}{4s^2(1 - \sigma^2)}.
+C &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} \pm \sqrt{\frac{\sigma^8}{16s^4(1 - \sigma^2)^2} - 1} = \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}}{4s^2(1 - \sigma^2)}.
 \end{align}
@@
 \end{align}
+A sample solution for the linear model is shown in Figure \ref{fig:linear}.
+To reiterate, the envelope at equilibrium is Gaussian, and therefore so too is the Fourier transform.
+Also, the pulse is linearly chirped.
+\\
+
+\begin{figure}[tbp]
+\centering
+\begin{subfigure}{0.5\textwidth}
+\centering
+\input{./Figures/Linear_Shape}
+\caption{Envelope}
+\end{subfigure}%
+\begin{subfigure}{0.5\textwidth}
+\centering
+\input{./Figures/Linear_FT}
+\caption{Fourier transform}
+\end{subfigure} \\
+\begin{subfigure}{0.5\textwidth}
+\centering
+\input{./Figures/Linear_Chirp}
+\caption{Chirp}
+\end{subfigure}
+\caption[Envelope, Fourier transform, and chirp of the pulse---linear case.]{Equilibrium state for the parameters $s = 0.15$, $b = 0$, $a = 8000$, and $h = 0.04$.}
+\label{fig:linear}
+\end{figure}
 
@@
 \begin{align*}
-\frac{1}{h^2 \zeta^2} E \exp \left(\frac{1}{h^2 \zeta^2} E \right) &= W \left( a E \textrm{e}^E \right) \exp \left( W \left( a E \textrm{e}^E \right) \right) \\
-&= a E \textrm{e}^E.
+\frac{1}{h^2 \zeta^2} E \exp \left(\frac{1}{h^2 \zeta^2} E \right) &= W \left( a E \textrm{e}^E \right) \exp \left( W \left( a E \textrm{e}^E \right) \right) = a E \textrm{e}^E.
 \end{align*}
@@
 \begin{align}
-\nonumber E_* &= \int_{-\infty}^\infty |G(A)|^2 \, \df T, \\
-\nonumber &= \frac{W(a E \textrm{e}^E)}{E} \int_{-\infty}^\infty |A|^2 \, \df T, \\
-&= W(a E \textrm{e}^E).
+E_* &= \int_{-\infty}^\infty |G(A)|^2 \, \df T = \frac{W(a E \textrm{e}^E)}{E} \int_{-\infty}^\infty |A|^2 \, \df T = W(a E \textrm{e}^E).
 \end{align}
 
-We can now find the amplitude of the pulse as well as we have previously found the equilibrium shape. Again, from \eqref{eq:gainde}, it must be that $E_* = P \sigma \sqrt{\pi}$, or,
+We can now find the amplitude of the pulse as well as we have previously found the equilibrium shape. Again, from \eqref{eq:gainde}, it must be that $E_* = \sqrt{\pi} P \sigma$, or,
 \begin{align}
-P = \frac{W(a E \textrm{e}^E)}{\sigma \sqrt{\pi}}.
+P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma}.
 \end{align}
-
--sample solution?
+The asymptotic expansions when $s \rightarrow 0$ of the energy, and peak power are
+\begin{align*}
+E_* &= \Lambda - \Theta \frac{\Lambda}{1 + \Lambda} s + \bigO{s^2}, & P &= \frac{\Lambda}{\sqrt{2 \pi s}} + \left( \frac{\Lambda}{2} -  \Theta \frac{\Lambda}{1 + \Lambda} \right) \sqrt{\frac{s}{2 \pi}} +  \bigO{s^{3/2}},
+\end{align*}
+respectively, where
+\begin{align*}
+\Lambda &= W\left( \frac{a h^2 \ln(a h^2)}{1 - h^2} \exp \left( \frac{h^2 \ln(a h^2)}{1 - h^2} \right) \right),
+\end{align*}
+and
+\begin{align*}
+\Theta &= \frac{\left( h^2 \ln(a h^2) + 1 - h^2 \right) \left( \ln(a h^2) + 1 - h^2 \right)}{\left( 1 - h^2 \right)^2 \ln(a h^2)}.
+\end{align*}

### 2019-05-28 Thesis/Nonlinear/Nonlinear.tex
Finished corrections

@@
 \input{./Figures/Variance}
-\caption{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.}
+\caption{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.
+The analytic expressions are given by \eqref{eq:equilvar}, \eqref{eq:equilchirp}, \eqref{eq:phase}, respectively.}
 \label{fig:var}
@@
 This is in agreement with experimental results \cite{chen, rothenberg, tomlinson}.
+While the nonlinear model yields similar results as the linear model (Figure \ref{fig:linear}), very interesting variations arise from the nonlinearity.
 \\
@@
 
+\begin{figure}[tbp]
+\input{./Figures/Cartoon}
+\caption{Stability of the pulse in the $s$-$b$ plane.}
+\label{fig:cartoon}
+\end{figure}
+
 The energy of the pulse is directly related to the output power of the laser, and since this is not as controllable as in a regular laser, it is of great interest.
@@
 Perhaps more surprising, as shown in Figure \ref{fig:energybig}, is that this boundary appears to become periodic as $b$ increases around $s = 0.3$.
+These features are further highlighted in Figure \ref{fig:cartoon} by disregarding the energy and only examining whether the pulse is stable or not.
 \\

### 2019-05-28 Thesis/Previous_Models/Previous.tex
Finished corrections

@@
 In this chapter we shall explore the previous modelling efforts by first reviewing the classic equations used in nonlinear optics.
-We will then build upon this to the master equation of mode-locking, where the solutions to this will briefly be studied before diving into `discretized' functional models.
+We will then build upon this to obtain the master equation of mode-locking, where the solutions to this will briefly be reviewed before considering `discretized' functional models.
 \\
@@
 \end{align*}
-Here $A$ is the complex pulse amplitude, $\beta_2$ is the second-order---or group delay---dispersion, and $\gamma$ is the coefficient of nonlinearity or Kerr coefficient.
+Here $A(z, T)$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second-order---or group delay---dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient.
+This equation can be derived from the nonlinear wave equation for electric fields, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
+Within the derivation comoving coordinates are used so that the reference frame propagates with the pulse at the group velocity.
+This is achieved with the substitution
+\begin{align}
+\label{eq:shift}
+T = t - \frac{z}{v_g}.
+\end{align}
+In this way, $z$ defines the distance travelled by the pulse, and $T$ the time difference from the peak of the pulse.
+Moreover, $T = 0$ is the peak of the pulse regardless of the actual time elapsed, because of this, generally $T$ is not very large.
+In standard coordinates the nonlinear Schr\"odinger equation has an additional term
+\begin{align*}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{t} + i \gamma |A|^2 A - \frac{1}{v_g} \pdiff{A}{t}.
+\end{align*}
+However, under the transformation \eqref{eq:shift}, we have that $\pdiff{}{t} \mapsto \pdiff{}{T}$, and $\pdiff{}{z} \mapsto \pdiff{}{z} - \frac{1}{v_g} \pdiff{}{T}$ by chain rule, thus, cancelling out this final term.
+\\
+
 In practice, this equation lacks a few key terms.
@@
 \end{align}
-where $\beta_3$ is the third order coefficient of dispersion, $g(A)$ is an amplifying term due to the gain, and $\alpha$ is the loss due to scattering and absorption. \\
-
-This equation can be derived from the nonlinear wave equation, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
-Within the derivation comoving coordinates are used so that the reference frame propagates with the pulse at the group velocity.
-This is achieved with the substitution
-\begin{align*}
-T = t - \frac{z}{v_g}.
-\end{align*}
+where $\beta_3 \in \mathbb{R}$ is the third order coefficient of dispersion, $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}$ is the loss due to scattering and absorption. \\
 
@@
 \begin{align*}
-k(\omega) &= k_0 + \pdiff{k}{\omega}(\omega - \omega_0) + \frac{1}{2} \pdiff[2]{k}{\omega}(\omega - \omega_0)^2 + \frac{1}{6} \pdiff[3]{k}{\omega}(\omega - \omega_0)^3 + \dots, \\
-&= \phi + \frac{1}{v_g}(\omega - \omega_0) + \frac{1}{2}\beta_2 (\omega - \omega_0)^2 + \frac{1}{6}\beta_3 (\omega - \omega_0)^3 + \dots,
+k(\omega) &= k_0 + \left.
+\pdiff{k}{\omega}\right|_{\omega_0}(\omega - \omega_0) + \frac{1}{2} \left.
+\pdiff[2]{k}{\omega}\right|_{\omega_0}(\omega - \omega_0)^2 + \frac{1}{6} \left.
+\pdiff[3]{k}{\omega}\right|_{\omega_0}(\omega - \omega_0)^3 + \cdots \\
+&= k_0 + \frac{1}{v_g}(\omega - \omega_0) + \frac{1}{2}\beta_2 (\omega - \omega_0)^2 + \frac{1}{6}\beta_3 (\omega - \omega_0)^3 + \cdots,
 \end{align*}
-where $\phi$ is the phase shift.
-Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth \cite{agrawal2013}.
+where $k_0$ is the phase shift.
+Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth~\cite{agrawal2013}.
 
 \section{The Master Equation of Mode-Locking}
+\label{chap:meml}
 The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers we wish to add a modulation term to ensure mode-locking, this yields the master equation of mode-locking, \cite{hausbook, haus1975, haus1986, haus1992, haus2000, kartner, tamura, usechak}
-\begin{align*}
+\begin{align}
 \pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T).
-\end{align*}
-The most common form of modulation is the sinusoid $M(T) = \frac{1}{2}\frac{M_s}{\omega_M} \left( 1 - \cos \left( \omega_M T \right) \right)$ \cite{hausbook, haus1975, haus1996, kartner}, and since $T$ is generally small, by it's definition, we expand via it's Taylor series so that $M(T) = \frac{1}{2}M_s T^2$.
+\end{align}
+The most common form of modulation is the sinusoid $M(T) = \frac{1}{2}\frac{M_s}{\omega_M^2} \left( 1 - \cos \left( \omega_M T \right) \right)$ \cite{hausbook, haus1975, haus1996, kartner}, and since $T$ is generally small, by \eqref{eq:shift}, we expand via it's Taylor series so that $M(T) = \frac{1}{2}M_s T^2 + \bigO{T^4}$.
 This brings us to the most common form of the master equation of mode-locking (neglecting the third order dispersion),
@@
 \end{align}
-Commonly, in an attempt to simplify the equation the gain assumed to be constant.
+Commonly, in an attempt to simplify, the equation the gain assumed to be constant with $g(A) = 2g_0 \in \mathbb{R}$.
 As a whole no analytic solution is know for \eqref{eq:meml}, however, after additional simplifications there are three flavours of solutions.
@@
 
-In the least complicated case, the modulation and nonlinearity are omitted resulting in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}.
-With the inclusion of the nonlinearity a similar solution is found, however, it is now it the form of a chirped hyperbolic secant \cite{haus1991, usechak}.
+In the least complicated case, the modulation and nonlinearity are omitted giving
+\begin{align*}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A.
+\end{align*}
+This results in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}. On the other hand, including the nonlinearity yields
+\begin{align*}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \left( g_0 - \alpha \right) A,
+\end{align*}
+where a similar solution is found, however, it is instead of the form of a chirped hyperbolic secant \cite{haus1991, usechak}.
 Both of these are unsurprising since this reduces to the soliton solution of the NLSE \cite{ferreira}.
-Lastly, by including the modulation term, and excluding the nonlinearity, \eqref{eq:meml} can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura, usechak}.
+Finally, by including the modulation term, and excluding the nonlinearity we have
+\begin{align*}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A - \frac{1}{2}M_s T^2.
+\end{align*}
+This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura, usechak}.
 However, in practice only the Gaussian is stable---the higher modes quickly decay within the laser \cite{hausbook, haus1975, haus1996, haus2000}.
@@
 In the absence of a modulator the nonlinearity becomes crucial to shaping the pulse.
-I don't know how to start this sentence*** when it was resurrected by Burgoyne \cite{burgoyne2014} in 2014 for tuneable lasers.
+This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
+In each of these models the effect of each block is described by a Gaussian transfer function.
+These transfer functions are then multiplied together to give the overall effect.
 \\
@@
 The clearest is that none of these models have contained every block--either the nonlinearity or the modulation have been omitted.
-In the framework of tuneable lasers each component plays an important role.
+In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function without the inclusion of all of the components.
 Another key drawback is that the functional operations of some of the components are somewhat phenomenological.
-While these functions are chosen based on the observed output, they are not necessarily correct.
-Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation (SPM) of the pulse becomes too strong distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
+While these functions are chosen based on the observed output, they are not necessarily consistent with their underlying physics.
+Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation (SPM) of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
 This notion will be explained in greater detail in Chapter \ref{chap:nl}.

### 2019-05-29 Thesis/Appendices/Asymptotics.tex
Finished second draft

@@
 \end{align}
-where $x = \sigma^2$, and $\eps = s^{-4}$ instead so that we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
+where $x = \sigma^2$, and $\eps = s^{-4}$ instead so we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
 \begin{align}
@@
 Moreover, since $\zeta$ is the ratio of the amplitude of the pulse before and after dispersion, $\zeta \rightarrow 1$.
-Similarly, $\phi \rightarrow 0$ since nothing in the circuit has the capacity to provide a phase shift.
-In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, while conserving its energy.
+Similarly, $\phi \rightarrow 0$ since nothing in the circuit has the capacity to induce a phase shift.
+In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, but still conserving its energy.
 Because of this, the variance approaches unity because the shape is entirely determined by the modulation function.
-Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimal.
+Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimally small.

### 2019-05-29 Thesis/Appendices/Hermite.tex
Finished second draft

@@
 %\label{chap:gauss}
-\section{Span of Gaussians in $L^2$}
-In order to show that Gaussians span $L^2$, we shall start our analysis with the span of the Hermite polynomials in $L^2$.
+\section{Span of Gaussians in $L^2(\mathbb{R})$}
+In order to show that Gaussians span $L^2(\mathbb{R})$, we shall start our analysis with the span of the Hermite polynomials in $L^2(\mathbb{R})$.
 Typically the Hermite polynomials are recursively defined as \cite{conway, courant, teuwen}
@@
 \begin{align*}
-\left< H_m, H_n \right> = \sqrt{\pi} 2^n n! \delta_{mn}
+\left< H_m, H_n \right> = \sqrt{\pi} 2^n n! \delta_{mn},
 \end{align*}
-and, therefore, the Hermite polynomials form an orthogonal set \cite{courant, hochstrasser, kreyszig, szego, teuwen}. Consider instead, the Gaussian--Hermite polynomials
+and therefore, the Hermite polynomials form an orthogonal set \cite{courant, hochstrasser, kreyszig, szego, teuwen}. Consider instead, the Gaussian--Hermite polynomials
 \begin{align*}
@@
 \end{align*}
-notice that the weighting function has been absorbed into the Hermite polynomials. We shall now show that the set of Gaussian--Hermite polynomials spans $L^2$. \\
+notice that the weighting function has been absorbed into the Hermite polynomials. We shall now show that the set of Gaussian--Hermite polynomials spans $L^2(\mathbb{R})$. \\
 
@@
 The Gaussian--Hermite polynomials are an orthogonalization of the set $\Xi = \{x^n \textrm{e}^{-x^2/2} : x \in \mathbb{R}, n \in \mathbb{N}\}$, and therefore, have the same span \cite{kreyszig, szego}.
-Thus, it is sufficient to show that $\Xi$ spans $L^2$.
-Suppose there exists an $f \in L^2$ such that $\left< f, \widetilde{H}_n \right> = 0$ for all $n$, or equivalently, that $\left< f, g_n \right> = 0$ for $g_n(x) = x^n \textrm{e}^{-x^2/2}$ for all $n$ so that it is not in the span of $\mathcal{G}(\mathbb{R})$.
+Thus, it is sufficient to show that $\Xi$ spans $L^2(\mathbb{R})$.
+Suppose there exists an $f \in L^2(\mathbb{R})$ such that $\left< f, \widetilde{H}_n \right> = 0$ for all $n$, or equivalently, that $\left< f, g_n \right> = 0$ for $g_n(x) = x^n \textrm{e}^{-x^2/2}$ for all $n$ so that it is not in the span of $\mathcal{G}(\mathbb{R})$.
 \\
@@
 This has the form of the parabolic cylinder functions \cite{miller}, and indeed the Gaussian--Hermite polynomials can be expressed in terms of parabolic cylinder functions \cite{hochstrasser, miller}.
-Moreover, \ref{eq:paracyl} can also be written in Sturm--Liouville form as
+Moreover, \eqref{eq:paracyl} can also be written in Sturm--Liouville form as
 \begin{align*}
@@
 \input{./Figures/GaussMod}
-\caption[Gaussian series for a particular modulation function.]{$N = 20$, $h = 0.1$}
+\caption[Gaussian series for a particular modulation function.]{Gaussian series with $N = 20$, $h = 0.1$.}
 \label{fig:gaussmod}

### 2019-05-29 Thesis/Intro/Introduction.tex
Finished second draft

@@
 The cavity of a standard laser---such as a HeNe laser---is composed of four main components: a highly reflective mirror, a partially reflecting mirror, something to supply the pumping energy, and the gain medium.
-The two mirrors are at opposite ends of the cavity and serve to contain most of the light to the cavity while allowing a small amount to exit, this is the output of the laser.
+The two mirrors are at opposite ends of the cavity and serve to contain most of the light to the cavity while allowing a small amount to exit---this is the output of the laser.
 The pump energy is generally supplied by either an external light source, or an electric field.
@@
 Something like a light emitting diode (LED) does not produce laser light because, while monochromatic, the light is not coherent.
-The monochromatic nature is a result of how the light is generated, the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with LEDs).
-Note that this correspondence means that  the frequency the laser operates at is fixed, and cannot be changed.
+The monochromatic nature is a result of how the light is generated; the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with LEDs).
+Note that this correspondence means the frequency the laser operates at is fixed, and cannot be changed.
 Coherence is achieved in the laser cavity---the cavity is carefully designed so the light resonates with the length of the cavity.
@@
 \input{./Figures/Cavity}
-\caption[Typical cavity of a tuneable laser.]{Typical cavity of a tuneable laser. The pulses travel clockwise around the loop.}
+\caption[Typical cavity of a tuneable laser.]{Typical cavity of a tuneable laser. The pulses travel clockwise around each loop.}
 \label{fig:cavity}
@@
 
-A tuneable laser on the other hand, has the ability to vary its wavelength by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
+A tuneable laser, on the other hand, has the ability to vary its wavelength by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
 Tuneable lasers in fact lase at all of these different frequencies simultaneously.
 This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
-However, having the capacity to tune the wavelength comes with a cost, tuneable lasers vary considerably from standard lasers in both construction and operation, but, the central ideas are the same.
+However, having the capacity to tune the wavelength comes with a cost; tuneable lasers vary considerably from standard lasers in both construction and operation, but, the central ideas are the same.
 A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}.
-Instead of being perpetually reflected back and forth, the light travels in a circular fashion around the cavity, this is a so called ring laser.
-The gain medium is still excited by an external power source, and the output passes through a partially reflecting mirror to become the output.
+Instead of being perpetually reflected back and forth, the light travels in a circular fashion around the cavity---this is a so called ring laser.
+The gain medium is still excited by an external power source, and the output passes through a partially reflecting mirror.
 However, a tuneable laser also contains a few additional components, each of which will be described in the following subsections.
@@
 \subsection{Optical Coupler and Laser Output}
-The optical coupler is a device that splits its input into two outputs---one continuing through the laser cavity, while the other exits the cavity to become the output of the laser.
+The optical coupler is a device that splits its input into two outputs---one continues through the laser cavity, while the other exits the cavity to become the output of the laser.
 There are multiple devices that can accomplish this, however, the simplest is a partially reflecting mirror \cite{alazzawi}.
 These mirrors are characterized by their reflection coefficient, $R$.
-In the schematic shown in Figure \ref{fig:cavity}, the part of the signal that is reflected exits the cavity, whereas, the part of the signal transmitted remains within the cavity.
+In the schematic shown in Figure \ref{fig:cavity}, the part of the signal that is reflected exits the cavity, whereas the part of the signal transmitted remains within the cavity.
 \\
@@
 A fibre Bragg grating (FBG) is an optical fibre where the refractive index varies periodically along its length \cite{ferreira}.
-To achieve this, typically silica fibres are doped with Germanium, which when exposed to intense ultraviolet (UV) light alters the refractive index of the core \cite{becker, starodoumov}.
+To achieve this, typically silica fibres are doped with Germanium which when exposed to intense ultraviolet (UV) light alters the refractive index of the core \cite{becker, starodoumov}.
 The photosensitivity of the optical fibres can be increased by more than an order of magnitude by the Germanium doping \cite{becker, ferreira}.
@@
 Both methods cause the periodic nature of the refractive index through interference.
-In the phase-mask method (Figure \ref{fig:phasemask}) a single beam of UV light passes through the phase-mask which acts as a series of lenses, focusing the light at the core---this causes a sinusoidal interference pattern.
+In the phase-mask method (Figure \ref{fig:phasemask}), a single beam of UV light passes through the phase-mask which acts as a series of lenses, focusing the light onto the core---this causes a sinusoidal interference pattern.
 Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of UV light are instead used to create the interference pattern.
@@
 \end{subfigure}
-\caption[Comparison of a chirped and unchirped Gaussian pulse.]{In a unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.}
+\caption[Comparison of a chirped and unchirped Gaussian pulse.]{In an unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.}
 \label{fig:chirp}
@@
 Figure \ref{fig:chirp} shows examples of chirped and unchirped Gaussian pulses---the most common type of chirp is linear chirp, where the frequency varies linearly across the pulse.
-Because of this, for a spatially varying frequency the oscillations are characterized by $\exp \left( i k(x) x \right) = \exp \left( i C x^2 \right)$, where $k(x) = Cx$ is the linear variation of the wave number, and $C$ is the chirp parameter.
+Because of this, for a spatially varying frequency, the oscillations are characterized by $\exp \left( i k(x) x \right) = \exp \left( i C x^2 \right)$, where $k(x) = Cx$ is the linear variation of the wave number, and $C$ is the chirp parameter.
 By using a chirped phase-mask a chirped fibre Bragg grating (CFBG) can be created.
@@
 Furthermore, the speed of light in an optical fibre is slightly dependent on the wavelength---this causes light with a longer wavelength to travel faster, and is known as chromatic dispersion.
-This is a large problem in fibre optic communications, the signal can spread and potentially becomes uninterpretable after large distances.
+This is a large problem in fibre optic communications, the signal can spread and potentially becomes uninterpretable after vast distances.
 However, chromatic dispersion can be counteracted using a CFBG \cite{agrawal2002, alazzawi, becker, starodoumov} (in the opposite orientation of Figure \ref{fig:cfbg}).
@@
 Erbium-doped fibre amplifiers (EDFAs) are used most widely since Erbium has a band gap that corresponds to $1.54$--$1.57$ $\mu$m, which is the preferred band for fibre optics since this has the least power loss \cite{agrawal2002, alazzawi, starodoumov}.
-The pump laser typically operates at $980$ nm or $1.48$ $\mu$m because these are able to transfer the most power (up to $100$ mW) into the fibre while introducing minimal noise \cite{agrawal2002, alazzawi, becker, starodoumov}.
+The pump laser typically operates at $980$ nm or $1.48$ $\mu$m because these wavelengths are able to transfer the most power (up to $100$ mW) into the fibre while introducing minimal noise \cite{agrawal2002, alazzawi, becker, starodoumov}.
 The pump power can be applied either forwards (with the laser), backwards (against the laser), or both \cite{alazzawi}, with each configuration having similar performance \cite{agrawal2002}.
@@
 
-\subsection{Mode-Locking}
+\section{Mode-Locking}
 \begin{figure}[tbp]
@@
 \end{subfigure}
-\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi x \right)$.}
+\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi i x \right)$.}
 \label{fig:ml}

### 2019-05-29 Thesis/Model/Model.tex
Finished second draft

@@
 \subsection{Fibre Nonlinearity}
-The nonlinearity of the fibre arises from the parameter $\gamma$; in regions where this affect is dominant expression~\eqref{eq:nlse} becomes
+The nonlinearity of the fibre arises from the parameter $\gamma$; in regions where this effect is dominant expression~\eqref{eq:nlse} becomes
 \begin{align}
@@
 \end{align}
-This expression can be manipulated in a similar manner to the gain to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting that $A(T,z) = A_0(T) e^{i \varphi(T,z)}$.
+This expression can be manipulated in a similar manner to the gain to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting that $A(z,T) = A_0(T) e^{i \varphi(T,z)}$.
 Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives $\varphi(T,z) = \gamma |A|^2 z$.
@@
 \subsection{Modulation}
-In the master equation of mode-locking, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{M_s}{2}T^2 A$.
+In the master equation of mode-locking, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{1}{2} M_s T^2 A$.
 In this new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
@@
 
-Despite assuming a Gaussian modulation the following solution can be generalized to any modulation function in $L^2$ since Gaussians in fact span $L^2$ as will be shown shortly. \\
+Despite assuming a Gaussian modulation the following solution can be generalized to any modulation function in $L^2(\mathbb{R})$ since Gaussians in fact span $L^2(\mathbb{R})$ as will be shown shortly.
+\\
 
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, seigman, kuizenga1970a, martinez1984, martinez1985} (Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, seigman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\
@@
 where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
-After passing though the optical coupler the pulse will simply decay to $A_1 = h A_0$.
+After passing through the optical coupler the pulse will simply decay to $A_1 = h A_0$.
 The pulse then enters the CFBG, where it will maintain its Gaussian shape, however, it will spread \cite{agrawal2013, ferreira, silfvast}.
@@
 \end{align*}
-Finally, the pulse travels though the gain fibre where it is amplified to
+Finally, the pulse travels through the gain fibre where it is amplified to
 \begin{align*}
@@
 \end{align*}
-Combining this first expression with \eqref{eq:varout} and expanding, we have that
+Combining this first expression with \eqref{eq:varout} and expanding, we have
 \begin{align*}
@@
 A sample solution for the linear model is shown in Figure \ref{fig:linear}.
-To reiterate, the envelope at equilibrium is Gaussian, and therefore so too is the Fourier transform.
+To reiterate, the envelope at equilibrium is Gaussian, and therefore, so too is the Fourier transform.
 Also, the pulse is linearly chirped.
@@
 
-We can now find the amplitude of the pulse as well as we have previously found the equilibrium shape. Again, from \eqref{eq:gainde}, it must be that $E_* = \sqrt{\pi} P \sigma$, or,
+We can now find the amplitude of the pulse as well, as we have previously found the equilibrium shape. Again, from \eqref{eq:gainde}, it must be that $E_* = \sqrt{\pi} P \sigma$, or,
 \begin{align}

### 2019-05-29 Thesis/Nonlinear/Nonlinear.tex
Finished second draft

@@
 \end{align*}
-This is a highly nonlinear operator, and attempting to take Fourier transform of a pulse that's under gone this transformation quickly becomes futile.
+This is a highly nonlinear operator, and attempting to take the Fourier transform of a pulse that has under gone this transformation quickly becomes futile.
 Instead we must resort to a numerical solution.
@@
 Before delving into the nonlinear behaviour of the model, we wish to validate that the code is working as expected---and as a sanity test for the linear solution---by comparing the results of the simulations with $b=0$ to the results of the linear model in Chapter \ref{chap:linear}.
-In the case of the numerical solution our initial conditions become somewhat important.
+In the case of the numerical solution, our initial conditions become somewhat important.
 In all of the following analysis the initial waveform is $\Gamma \sech \left( 2T \right) \textrm{e}^{i \pi / 4}$ normalized so that the initial energy is $E_0 = 0.1$; additionally, $a = 8000$, and $h = 0.04$.
@@
 \input{./Figures/Variance}
-\caption{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.
+\caption[Equilibrium variance, chirp, and phase shift of the pulse as a function of $s$.]{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.
 The analytic expressions are given by \eqref{eq:equilvar}, \eqref{eq:equilchirp}, \eqref{eq:phase}, respectively.}
@@
 \caption[Equilibrium energy, and peak power of the pulse as a function of $s$.]{Equilibrium energy, and peak power of the pulse as a function of $s$.
-The thin black line is to highlight that the energy is \emph{not} linearly related to $s$.}
+The thin black line is to highlight that the energy is \emph{not} linearly dependent on $s$.}
 \label{fig:valenergy}
@@
 Notice that as $b$ increases along the strip $0.2 < s < 0.4$, the contours become steeper and steeper.
-In addition, the contours are at multiples of $\pi$, and exit the boundary at approximately the same places.
+In addition, the contours have been plotted at multiples of $\pi$, and exit the boundary at approximately the same places.
 Thus, the reason for this periodicity is that the strength of the nonlinearity is proportional to the modulus of the effective nonlinearity---the effective nonlinearity passes through the same points repeatedly.
@@
 The noise in the energy exhibited for moderate to large values of $b$, and small values of $s$ is a phenomenon called \emph{wave breaking} \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}.
-Wave breaking is not limited to just optics, wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
+Wave breaking is not limited to just optics; wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
 Wave breaking occurs because the pulse begins to interfere with itself in a way called self-phase modulation \cite{agrawal2002, agrawal2013, becker}.
 Self-phase modulation occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
-This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson}.
+This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson}, as we saw in Figure \ref{fig:nlstable}.
 These high frequencies compound with each trip around the cavity becoming parasitic very quickly---Figure \ref{fig:break} highlights this.
-Notice that the difference between this figure and Figure \ref{fig:nlstable} is a difference in $b$ of $0.05$---this difference could be as small as adding a few centimetres more of fibre between the gain and output coupler.
-The left figures show the pulse after 11 trips around the cavity, in the Fourier transform it is clear that the contributions from higher frequencies has increased---we obtain similar results as in \cite{anderson, rothenberg}.
-Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is in agreement with \cite{anderson, rothenberg}.
+Notice that the difference between this and Figure \ref{fig:nlstable} is a difference in $b$ of $0.05$---this difference could be as small as adding a few centimetres more of fibre between the gain and output coupler.
+The left figures show the pulse after 11 trips around the cavity; in the Fourier transform it is clear that the contributions from higher frequencies has increased---we obtain similar results as in \cite{anderson, rothenberg}.
+Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is again in agreement with \cite{anderson, rothenberg}.
 The parasitic nature of the high frequency contributions is evident by examining the right figures.
-After 5 additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
+After five additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
 Moreover, the Fourier transform has no clear structure and has essentially become noise, and the chirp has grown to be highly oscillatory and unstable.
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2$ norm, which is computed numerically using trapezoid rule.
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule.
 Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested about the phase shift between iterations.
@@
 Unsurprisingly, the error is largest in the region where the wave breaks.
-As mentioned in the previous subsection, the pulse does not reach a stable state.
+As mentioned in the previous subsection, the pulse does not reach a stable state in this region.
 As a consequence the envelope varies violently, which leads to this large error.
@@
 Compared with the error from Figure \ref{fig:error} the lower right region is much more well behaved, that is, the error is a few orders of magnitude lower.
-A peculiar trait of the band between the unstable and stable regions is that within this area the pulse is in a quasi-stable state---the pulse is stable and has reach a sort of equilibrium, however, the envelope of the pulse has minute variations with no clear period.
+A peculiar trait of the band between the unstable and stable regions is that within this area the pulse is in a quasi-stable state---the pulse is stable and has reached a sort of equilibrium, however, the envelope of the pulse has minute variations with no clear period.
 Additionally, there appears to be no periodicity of the envelope within the wave breaking region, further supporting the claim that the pulse here is completely unstable.
@@
 \end{subfigure}
-\caption{Energy of the pulse at equilibrium, with the modulation and dispersion blocks switched.}
+\caption{Energy of the pulse at equilibrium with the modulation and dispersion blocks switched.}
 \label{fig:switch}
@@
 Additionally, within the unstable region the density of the contour lines is much greater---suggesting it is in some sense more chaotic and random than with the components in their original permutation.
-The final main difference between the two orderings, is that in this case, the energy contours are no longer monotonic functions of $s$.
+The final main difference between the two orderings, is that in this case the energy contours are no longer monotonic functions of $s$.
 Instead we find a parabolic shape on the top contour, and two lobes on the second contour.

### 2019-05-29 Thesis/Previous_Models/Previous.tex
Finished second draft

@@
 \end{align*}
-Here $A(z, T)$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second-order---or group delay---dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient.
+Here $A = A(z, T)$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order---or group delay---dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient.
 This equation can be derived from the nonlinear wave equation for electric fields, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
@@
 Moreover, $T = 0$ is the peak of the pulse regardless of the actual time elapsed, because of this, generally $T$ is not very large.
-In standard coordinates the nonlinear Schr\"odinger equation has an additional term
+In standard coordinates the nonlinear Schr\"odinger equation has an additional term:
 \begin{align*}
@@
 \end{align}
-Commonly, in an attempt to simplify, the equation the gain assumed to be constant with $g(A) = 2g_0 \in \mathbb{R}$.
-As a whole no analytic solution is know for \eqref{eq:meml}, however, after additional simplifications there are three flavours of solutions.
+Commonly, in an attempt to simplify the equation the gain is assumed to be constant with $g(A) = 2g_0 \in \mathbb{R}$.
+As a whole no analytic solution is known for \eqref{eq:meml}, however, after additional simplifications there are three flavours of solutions.
 \\
 
-In the least complicated case, the modulation and nonlinearity are omitted giving
+In the least complicated case, the modulation and nonlinearity are both omitted giving
 \begin{align*}
@@
 
-\section{Discrete Functional Model}
+\section{Discrete Functional Models}
 While solutions to the master equation yield reasonable results, it is not necessarily representative of what happens within the laser cavity.
@@
 Despite these attempts, several short-comings exist.
-The clearest is that none of these models have contained every block--either the nonlinearity or the modulation have been omitted.
+The clearest is that none of these models have contained every block---either the nonlinearity or the modulation have been omitted.
 In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function without the inclusion of all of the components.

### 2019-05-31 Thesis/Conclusion/Conclusion.tex
Added conclusion

% !TeX root = ../Thesis.tex

\chapter{Conclusion}
By expanding upon the ideas originally proposed by Cutler \cite{cutler}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman}, we developed a nonlinear functional model for tuneable lasers. By omitting the nonlinearity, we obtain similar linearly chirped Gaussian solutions. However, a consequence of showing Gaussians span $L^2(\mathbb{R})$ is that this model has been solved regardless of the choice of the modulation function. \\

In contrast, with the inclusion of the nonlinearity we were able to demonstrate wave breaking, and found a peculiar boundary of stability. This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}, but, mathematical models have been unable to thus far. The nonlinearity induces self phase modulation which injects higher frequency modes to the pulse. This causes the Fourier transform to become a bimodal distribution instead of Gaussian. As the nonlinearity increases so too does the separation between these two modes. If this effect becomes too strong, the wave becomes incoherent and deformed, and ultimately unsustainable---the wave has broken. \\

The shape of this boundary between a stable pulse, and an unstable broken pulse is quite intriguing, and surprisingly sharp. At a critical $s$ value, about 0.3 in our simulations, the boundary becomes periodic---this arises from the nature of the nonlinearity. In a sense the nonlinearity is periodic in $b$, and thus, the stability of the solution is as well. \\

### 2019-05-31 Thesis/Appendices/Asymptotics.tex
Finished final draft

@@
 \end{cases*}
-& \phi &=
-\begin{cases*}
-\frac{1}{2}s - \frac{1}{24}s^3 + \bigO{s^5} & $s \rightarrow 0$ \\
-\frac{\pi}{4} - \frac{1}{2s^2} + \frac{5}{12s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
-\end{cases*} \\
-C &=
+& C &=
 \begin{cases*}
@@
 \frac{1}{2s^2} - \frac{3}{8s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
+\end{cases*} \\
+\frac{C}{\sigma^2} &=
+\begin{cases*}
+\frac{1}{2s} - \frac{1}{8}s + \bigO{s^3} & $s \rightarrow 0$ \\
+\frac{1}{2s^2} - \frac{1}{4s^6} + \bigO{s^{-10}} & $s \rightarrow \infty$
 \end{cases*}
@@
 Moreover, since $\zeta$ is the ratio of the amplitude of the pulse before and after dispersion, $\zeta \rightarrow 1$.
-Similarly, $\phi \rightarrow 0$ since nothing in the circuit has the capacity to induce a phase shift.
-In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, but still conserving its energy.
+In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, while conserving its energy.
 Because of this, the variance approaches unity because the shape is entirely determined by the modulation function.
 Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimally small.
+Finally, because of the expansive nature, the chirp approaches zero because any chirp will be inflated away.
+\\

### 2019-05-31 Thesis/Model/Model.tex
Finished final draft

@@
 In this chapter we shall derive our new model and solve it analytically in the linear case.
-To accomplish this we shall use the ideas of the previous functional models \cite{cutler, seigman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
+To accomplish this we shall use the ideas of the previous functional models \cite{cutler, siegman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
 To alleviate some of the pitfalls mentioned in the previous chapter, we shall include all five processes involved in the modification of the pulse within the laser cavity (gain, nonlinearity, loss, dispersion, and modulation).
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, seigman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\

### 2019-05-31 Thesis/Previous_Models/Previous.tex
Finished final draft

@@
 \label{eq:shift}
-T = t - \frac{z}{v_g}.
+T = t - \frac{z}{v_g},
 \end{align}
+reminiscent of moving to a fixed frame in a free boundary problem \cite{ockendon}.
 In this way, $z$ defines the distance travelled by the pulse, and $T$ the time difference from the peak of the pulse.
@@
 Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator.
-This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{seigman}, which they then greatly added to the following year \cite{kuizenga1970a}.
-Kuizenga and Seigman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}.
+This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{siegman}, which they then greatly added to the following year \cite{kuizenga1970a}.
+Kuizenga and Siegman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}.
 The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried to model passive mode-locking---mode-locking without the use of a modulator.

### 2019-07-12 Thesis/Appendices/Asymptotics.tex
Finished corrections

@@
 %\label{chap:asymp}
-We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$ (a very short CFBG), as well as when $s \rightarrow \infty$ (a very long CFBG).
+We shall investigate the nature of the solution to \eqref{eq:var} both when $s \rightarrow 0$ (a very short \gls{cfbg}), as well as when $s \rightarrow \infty$ (a very long \gls{cfbg}).
 For ease of notation, \eqref{eq:var} is rewritten as
@@
 \label{eq:asymp}
-\frac{1}{4} x^4 = \eps \left( -x^3 + 5x^2 - 8x + 4 \right),
+\frac{1}{4} x^4 = - \eps (x - 1)(x - 2)^2,
 \end{align}
-where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
+where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Figure \ref{fig:asympt} shows \eqref{eq:asymp}. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
 \begin{align}
@@
 and so, $x_1 = \pm 2, \, \pm 2 i$.
-However, we wish $x$ to be positive and real---recall that $x = \sigma^2$---thus, we take $x_1 = 2$.
+However, we require $x$ to be positive and real---recall that $x = \sigma^2$---thus, we take $x_1 = 2$.
 Now, the next lowest order of the left hand side must be $\eps^{3\alpha + \beta} = \eps^{3/4 + \beta}$.
@@
 and with the choice of $x_1$, $x_2 = 2$. Combining these results gives $x = 2 \eps^{1/4} - 2 \eps^{1/2} + \bigO{\eps^{3/4}}$, or $\sigma^2 = 2 s \left( 1 - s \right) + \bigO{s^3}$,
-this is shown in Figure \ref{fig:lims0}. \\
+this is shown in Figure \ref{fig:lims0}. The choice $\eps = s^4$ was for convenience, but in retrospect, $\eps = s$ yields a cleaner, but identical, solution. \\
 \begin{figure}[tbp]
 \input{./Figures/Lim_s_0}
-\caption{Asymptotic expansion of the variance as $s \rightarrow 0$.}
+\caption[Asymptotic expansion of the variance as the dispersion parameter approaches 0.]{Asymptotic expansion of the variance as the dispersion parameter, $s$, approaches $0$.}
 \label{fig:lims0}
@@
 
-We shall now consider the other limit, when $s \rightarrow \infty$. Using a similar substitution we instead write \eqref{eq:var} as
+We shall now consider the other limit, when the dispersion parameter, $s$, approaches $\infty$. Using a similar substitution we instead write \eqref{eq:var} as
 \begin{align}
@@
 \end{align}
-where $x = \sigma^2$, and $\eps = s^{-4}$ instead so we still have $\eps \rightarrow 0$. Furthermore, we must make a correction to the series expansion:
+where $x = \sigma^2$, and $\eps = s^{-4}$ instead so we still have $\eps \rightarrow 0$, this is also shown in Figure~\ref{fig:asympt}. Furthermore, we must make a correction to the series expansion:
 \begin{align}
@@
 \begin{align*}
-x_0^3 (x_0 + 4) &= 0,
+x_0^3 (x_0 + 4) &= 0.
 \end{align*}
-we shall choose $x_0 = 0$---since $x \geq 0$. Continuing, we obtain a dominant balance when $\alpha = 1$. So the next condition occurs at $\bigO{1}$ where
+The non-trivial solution $x_0 = -4$ gives rise to a boundary layer structure.
+However, this is unphysical because $x \geq 0$, leaving $x_0^3 = 0$, so this singular perturbation does not generate the boundary layer expected.
+Therefore, \eqref{eq:series2} reduces to a regular perturbation problem, and $\alpha$ must equal 1.
+The next condition occurs at $\bigO{1}$ where
 \begin{align*}
@@
 \end{align*}
-so either $x_1 = 1$ or $x_1 = 2$, we shall see in the next step that we can eliminate one of these.
-The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$.
+so either $x_1 = 1$ or $x_1 = 2$.
+The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$ provided\footnote{In the case of $x_1 = 2$ we find $\beta = \frac{3}{2}$ which leads to complex roots.} $x_1 \ne 2$.
 Now at $\bigO{\eps}$,
@@
 \end{align*}
-where again, the coefficients come from the binomial expansions. From this it is clear that $x_2$ is unique provided $x_1 \ne 2$ and
+where again, the coefficients come from the binomial expansions. From this it is clear that
 \begin{align*}
@@
 \input{./Figures/Lim_s_Infty}
-\caption{Asymptotic expansion of the variance as $s \rightarrow \infty$.}
+\caption[Asymptotic expansion of the variance as the dispersion parameter approaches $\infty$.]{Asymptotic expansion of the variance as the dispersion parameter, $s$, approaches $\infty$.}
 \label{fig:limsinfty}
@@
 In conclusion, the asymptotic expansions of the observables are
-\begin{align*}
+\begin{equation}
+\begin{aligned}
 \sigma^2 &=
@@
 \end{cases*}
-\end{align*}
+\label{eq:asympt}
+\end{aligned}
+\end{equation}
 The general form of these is as expected.
-When $s \rightarrow 0$, we effectively remove the CFBG from the cavity.
-This causes the pulse to be perpetually modulated, and so, the pulse approaches a $\delta$ function, and therefore, $\sigma^2 \rightarrow 0$.
+When $s \rightarrow 0$, we effectively remove the \gls{cfbg} from the cavity.
+This causes the pulse to be perpetually modulated, and so, the pulse's shape approaches a $\delta$ function, and therefore, $\sigma^2 \rightarrow 0$.
 Moreover, since $\zeta$ is the ratio of the amplitude of the pulse before and after dispersion, $\zeta \rightarrow 1$.
-In the opposite extreme, $s \rightarrow \infty$, we have an incredibly long / powerful CFBG---this causes the pulse to broaden greatly, while conserving its energy.
+In the opposite extreme, $s \rightarrow \infty$, the length / strength of the \gls{cfbg} approaches infinity---this causes the pulse to broaden greatly, while conserving its energy.
 Because of this, the variance approaches unity because the shape is entirely determined by the modulation function.
 Additionally, $\zeta \rightarrow 0$ because the pulse becomes infinitely wide, and thus, the amplitude becomes infinitesimally small.
-Finally, because of the expansive nature, the chirp approaches zero because any chirp will be inflated away.
+Due to the expansive nature, the chirp approaches zero because any chirp will be expanded away.
 \\

### 2019-07-12 Thesis/Appendices/Dispersion.tex
Finished second draft
Finished corrections

@@
 \begin{align*}
-D(A_1) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right),
+D(A_1) &= \left( \frac{1 + \frac{2C s^2}{\sigma^2} + \frac{2s^2}{\sigma^2}i}{\left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2} \right)^{1/2} \exp \left( -T^2 \frac{(1 + i C)(2\sigma^2 + 4 C s^2 + 4 i s^2)}{(2\sigma^2 + 4C s^2)^2 + 16s^4} \right).
 \end{align*}
-and then by writing in polar coordinates:
-\begin{multline*}
-D(A_1) = \left( \left( 1 + \frac{2C s^2}{\sigma^2} \right)^2 + \left( \frac{2s^2}{\sigma^2} \right)^2 \right)^{-1/4} \exp \left( \frac{1}{2} i \arctan \left( \frac{\frac{2s^2}{\sigma^2}}{1 + \frac{2C s^2}{\sigma^2}} \right) \right) \\
-\times \exp \left( -T^2 \frac{\sigma^2 \left[ 1 + i \left( C + (1 + C^2) \frac{2s^2}{\sigma^2} \right) \right]}{2 \left[ (\sigma^2 + 2C s^2)^2 + 4s^4 \right]} \right).
-\end{multline*}
-Finally, this can be simplified further to
+Finally, this can be simplified further to\footnote{For $a, b \in \mathbb{R}$ $\displaystyle (a + bi)^{1/2} = (a^2 + b^2)^{1/4} \exp \left( \frac{1}{2}i \arctan \left( \frac{b}{a} \right) \right)$.}
 \begin{multline*}
@@
 
-The expressions for the chirp and variance can be verified with the well known relations \cite{agrawal2013, anderson, ferreira, silfvast}
+The expressions for the chirp and variance can be verified by comparing to the dimensional equivalents from the literature \cite{agrawal2013, anderson, ferreira, silfvast}. One finds
 \begin{align*}
 \left( \frac{T_1}{T_0} \right)^2 &= \left( 1 + \frac{C \beta_2 z}{T_0^2} \right)^2 + \left( \frac{ \beta_2 z}{T_0^2} \right)^2,&
-\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2}.
+\widetilde{C} &= C + (1+C^2) \frac{\beta_2 z}{T_0^2},
 \end{align*}
-Where, within our non-dimensionalization, $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, $z = L_D$, and $\beta_2 z T_0^{-2} = 2s^2\sigma^{-2}$.
+with the conversions $T_0 = \sigma T_M$, $T_1 = \widetilde{\sigma} T_M$, and $\beta_2 L_D T_0^{-2} = 2s^2\sigma^{-2}$.
 In addition to this, the expression for $\zeta$ can be validated using conservation of energy.
-Within the CFBG energy is conserved, therefore,
+Within the \gls{cfbg} energy is conserved, therefore,
 \begin{align*}
@@
 \end{align*}
-Which, after substituting the expressions from Section \ref{sec:linear}, reduces to
+After substituting the expressions, reduces to
 \begin{align*}

### 2019-07-12 Thesis/Appendices/Hermite.tex
Finished corrections

@@
 % !TeX root = ../Thesis.tex
-%\chapter{Span of Gaussians in $L^2$}
-%\label{chap:gauss}
-\section{Span of Gaussians in $L^2(\mathbb{R})$}
+
+\chapter{Span of Gaussians in $L^2(\mathbb{R})$}
+\label{chap:gauss}
 In order to show that Gaussians span $L^2(\mathbb{R})$, we shall start our analysis with the span of the Hermite polynomials in $L^2(\mathbb{R})$.
@@
 \begin{align*}
-\left< H_m, H_n \right> = \sqrt{\pi} 2^n n! \delta_{mn},
+\left< H_m, H_n \right> = \sqrt{\pi} 2^n n! \delta_{m,n},
 \end{align*}
-and therefore, the Hermite polynomials form an orthogonal set \cite{courant, hochstrasser, kreyszig, szego, teuwen}. Consider instead, the Gaussian--Hermite polynomials
+where $\delta_{m,n}$ is the Kronecker $\delta$ function.
+Therefore, the Hermite polynomials form an orthogonal set \cite{courant, hochstrasser, kreyszig, szego, teuwen}.
+Consider instead, the Gaussian--Hermite polynomials from \eqref{eq:gaussherm}:
 \begin{align*}
@@
 \end{align*}
-and now it is clear that $f(x) \textrm{e}^{-x^2/2} = 0$ almost everywhere, therefore, $f(x) = 0$ almost everywhere. \\
+and now it is clear that $f(x) \textrm{e}^{-x^2/2} = 0$ almost everywhere, therefore, $f(x) = 0$ almost everywhere.
 \end{proof}
@@
 \begin{align*}
-\diff{}{x} \left( 1 \cdot \diff{\Her{n}{x}}{x} \right) + (1 - x^2) \Her{n}{x} = -2n \Her{n}{x}.
+\diff{}{x} \left( p(x) \cdot \diff{\Her{n}{x}}{x} \right) + (1 - x^2) \Her{n}{x} &= -2n \Her{n}{x}, & p(x) &= 1.
 \end{align*}
@@
 \end{align*}
-Using a similar idea to \cite{calcaterra2, calcaterra}, we shall now expand the Gaussian--Hermite polynomials using their definition
+Recall that $\Her{n}{x}$ has a polynomial as well as a Gaussian component.
+Without loss of generality we assumed the Gaussian has variance $\frac{1}{2}$ for convenience.
+We can effectively remove the polynomial dependence by using a similar idea to \cite{calcaterra2, calcaterra}.
+We shall expand the Gaussian--Hermite polynomials using their definition
 \begin{align*}

### 2019-07-12 Thesis/Conclusion/Conclusion.tex
Finished corrections

@@
 By omitting the nonlinearity, we obtain similar linearly chirped Gaussian solutions.
-However, a consequence of showing Gaussians span $L^2(\mathbb{R})$ is that this model has been solved regardless of the choice of the modulation function.
+However, a consequence of showing that Gaussians span $L^2(\mathbb{R})$ is that the linear model has been solved regardless of the choice of the modulation function.
 \\
@@
 In contrast, with the inclusion of the nonlinearity we were able to demonstrate wave breaking, and found a peculiar boundary of stability.
-This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}, but, mathematical models have been unable to thus far.
-The nonlinearity induces self phase modulation which injects higher frequency modes to the pulse.
-This causes the Fourier transform to become a bimodal distribution instead of Gaussian.
-As the nonlinearity increases so too does the separation between these two modes.
+This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}, but, previous mathematical models have been unable to capture it thus far.
+The nonlinearity induces \gls{spm} which injects higher frequency modes to the pulse.
+This causes the Fourier transform to become bimodal instead of Gaussian.
+As the nonlinearity increases, so too does the separation between these two modes.
 If this effect becomes too strong, the wave becomes incoherent and deformed, and ultimately unsustainable---the wave has broken.
@@
 The shape of this boundary between a stable pulse, and an unstable broken pulse is quite intriguing, and surprisingly sharp.
-At a critical $s$ value, about 0.3 in our simulations, the boundary becomes periodic---this arises from the nature of the nonlinearity.
+At a critical $s$ value, about 0.3 in our simulations, the boundary becomes periodic in the parameter space---this arises from the nature of the nonlinearity.
 In a sense the nonlinearity is periodic in $b$, and thus, the stability of the solution is as well.
 \\
+
+One of the issues experimentalists have is designing their tuneable lasers.
+They are uncertain how their laser will behave---and if the laser will lase at all---until they actually construct it.
+This model serves to provide better design principles, and how to troubleshoot should they encounter wave breaking.
+For example, from our results it is clear that to fix a broken wave $b$ must be decreased, or $s$ increased.
+This could be achieved by reducing the length of the optical fibre between the gain fibre and the output coupler, or by increasing $\beta_2 L_D$ by adding a second \gls{cfbg} in series\footnote{See \eqref{eq:ndparam}.}.
+Additionally, one could decrease  the modulation time, $T_M$, to move through the parameter space along a ray outward from the origin.
+Although this would increase $b$, it also increases $s$ enough to move out of the unstable region.
+\\
+
+\section{Future Work}
+There are a few avenues to explore as a continuation of this project.
+The first is to compare to experimental data to validate the findings.
+However, due to the ultrashort duration of the pulses it becomes difficult to accurately measure the envelope and spectrum---autocorrelation methods must be used.
+This makes it troublesome to make the distinction between a Gaussian envelope or the generalized Gaussian envelope we've found.
+\\
+
+An analytic development of interest is to find the asymptotic expansion for small values of the nonlinearity parameter---that is, $b \rightarrow 0$.
+This is likely to provide insight to how the nonlinearity  impacts the linearized solution to better understand the manifestation of wave breaking.
+Furthermore, to probe the underlying structure shown in Figure \ref{fig:error} a bifurcation diagram could be constructed or analytic continuation could be used to observe the sensitivity to the parameters.
+\\

### 2019-07-12 Thesis/Figures/Hologram.tex
Updated figures
Finished corrections

@@
 % Labels
-\draw[->, >=stealth, thick] (3,-1.5) -- (2,0) node[pos=-0.2] {Ge Doped Core};
+\draw[->, >=stealth, thick] (3,-1.5) -- (2,0) node[pos=-0.2] {Ge-Doped Core};
 \draw[->, >=stealth, thick] (-3,-1.5) -- (-2,-0.75) node[pos=-0.3] {Cladding};
-\draw[->, >=stealth, thick] (-3,2.5) -- (-1.82,2) node[pos=-0.4] {UV Light};
+\draw[->, >=stealth, thick] (-3,2.5) -- (-1.82,2) node[pos=-0.4] {\gls{uv} Light};
 \end{tikzpicture}

### 2019-07-12 Thesis/Intro/Introduction.tex
Finished corrections

@@
 \chapter{Introduction}
+
+\begin{figure}[tbp]
+\centering
+\input{./Figures/Laser}
+\caption{Depiction of a standard laser.
+A majority of the light is continually reflected by the two mirrors with a small portion escaping to become the output.
+The light is amplified by the gain medium with each pass.}
+\label{fig:laser}
+\end{figure}
+
+The word laser was originally an acronym for \emph{Light Amplification by Stimulated Emission of Radiation}.
+The cavity of a standard laser---such as a HeNe laser---is composed of four main components: a highly reflective mirror, a partially reflecting mirror, something to supply the energy, and the amplifying, or gain, medium.
+The two mirrors are at opposite ends of the cavity and serve to contain most of the light in the cavity while allowing a small amount to exit---this is the output of the laser, this is shown in Figure \ref{fig:laser}.
+The energy is generally supplied by either an external light source, or an electric field.
+The amplifying medium typically consists of gases, such as Helium and Neon, or a crystal, such as \gls{ndyag} for a single frequency laser.
+\\
+
 \begin{figure}[tbp]
@@
 \input{./Figures/Emission}
-\caption[Comparison of pumping, spontaneous emission, and stimulated emission.]{In pumping, incident photons are absorbed by electrons which are then excited into a higher energy state (the electrons may also be excited by an electric field).
+\caption[Comparison of pumping, spontaneous emission, and stimulated emission.]{In pumping, incident photons are absorbed by electrons which are then excited into a much higher energy state (the electrons may also be excited by an electric field).
+The electrons quickly emits a low energy photon and transitions to an energy state that is still much more energetic than the original.
 In spontaneous emission, an electron in an excited state emits a photon and returns to the lower energy state.
@@
 
-The word laser was originally an acronym for \emph{Light Amplification by Stimulated Emission of Radiation}.
-The cavity of a standard laser---such as a HeNe laser---is composed of four main components: a highly reflective mirror, a partially reflecting mirror, something to supply the pumping energy, and the gain medium.
-The two mirrors are at opposite ends of the cavity and serve to contain most of the light to the cavity while allowing a small amount to exit---this is the output of the laser.
-The pump energy is generally supplied by either an external light source, or an electric field.
-The gain medium is what amplifies the laser light and consists of gases, such as Helium and Neon, or a crystal, such as Neodymium-doped Yttrium Aluminium garnet (Nd:YAG).
+The atoms in the gain medium are pumped with energy raising the electrons to an excited state.
+For stimulated emission an incident photon triggers the emission of a photon which causes the electron to transition back to the ground state \cite{alazzawi}.
+This new photon is emitted with the combined energy of the previous photon as well as the electron's energy, thus, amplifying the light.
+Furthermore, the photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}.
+These processes are highlighted in Figure \ref{fig:emission}.
+The light perpetually bounces between the two mirrors becoming more amplified with each interaction with an excited electron and a fraction of this light is able to pass through the partially reflecting mirror to become the output of the laser.
 \\
 
-More precisely, the atoms in the gain medium are pumped with energy raising the electrons to an excited state.
-For stimulated emission an incident photon triggers the emission of a photon from this excited electron \cite{alazzawi}.
-This new photon absorbs the electron's energy as it returns to its ground state, amplifying the light.
-Furthermore, the photon is released with the same direction and phase as the incident one, maintaining coherence \cite{alazzawi}.
-These processes are highlighted in Figure \ref{fig:emission}.
-The amplified light perpetually bounces between the two mirrors becoming more amplified with each interaction with an excited electron, a fraction of this light is able to pass through the partially reflecting mirror to become the output of the laser.
-\\
-
-This is how laser light is generated, but, laser light has two fundamental characteristics that regular light does not.
+Laser light has two fundamental characteristics that regular light does not.
 The first is that the light is highly monochromatic---the light contains (ideally) a single frequency.
@@
 The other key feature is coherence, in which all the peaks and troughs of the light overlap giving very strong constructive interference---this is why laser light can be so intense.
-Something like a light emitting diode (LED) does not produce laser light because, while monochromatic, the light is not coherent.
-The monochromatic nature is a result of how the light is generated; the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with LEDs).
-Note that this correspondence means the frequency the laser operates at is fixed, and cannot be changed.
+A system such as a \gls{led} does not produce laser light because, while monochromatic, the light is not coherent.
+The monochromatic nature is a result of how the light is generated; the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with \gls{led}s).
+Note that this means the frequency the laser operates at is fixed, and cannot be changed.
 Coherence is achieved in the laser cavity---the cavity is carefully designed so the light resonates with the length of the cavity.
 This causes all the peaks and troughs to align, and interfere constructively.
+\\
+
+Another class of lasers are optical fibre lasers.
+Optical fibre lasers operate by the same principles, however, instead of the light being perpetually reflected back and forth, the light travels in a circular fashion through an optical fibre---this is a so called ring laser.
+Additionally, instead of the gain medium consisting of a gas or crystal, it is a length of fibre doped with a rare-earth metal.
 \\
@@
 \input{./Figures/Cavity}
-\caption[Typical cavity of a tuneable laser.]{Typical cavity of a tuneable laser. The pulses travel clockwise around each loop.}
+\caption[Typical cavity of a tuneable laser.]{Typical cavity of a fibre based tuneable laser. The pulses travel clockwise around each loop.}
 \label{fig:cavity}
@@
 
-A tuneable laser, on the other hand, has the ability to vary its wavelength by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
-Tuneable lasers in fact lase at all of these different frequencies simultaneously.
+A tuneable laser has the ability to vary its wavelength, and hence frequency, by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
+Tuneable lasers can lase at all of these different frequencies simultaneously.
 This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
-However, having the capacity to tune the wavelength comes with a cost; tuneable lasers vary considerably from standard lasers in both construction and operation, but, the central ideas are the same.
 A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}.
-Instead of being perpetually reflected back and forth, the light travels in a circular fashion around the cavity---this is a so called ring laser.
 The gain medium is still excited by an external power source, and the output passes through a partially reflecting mirror.
@@
 
-\subsection{Modulator}
-The optical pulse in the cavity can be modulated with one of two methods---amplitude modulation, or phase modulation.
-Mathematically these can be considered equivalent since they are Fourier transforms of each other, but in practice these are accomplished by different apparatuses.
-For us, we shall assume the pulses are amplitude modulated.
-Generally, the pulse can be amplitude modulated using one of two techniques.
-The first is with an acousto-optic modulator which utilizes the acousto-optic effect where the index of refraction of the fibre is varied by a sound wave \cite{hausbook, karim}.
-The second---and more common---method uses the electro-optic effect and is called an electro-optic modulator.
-These work the same way, the fibre inside the modulator responds to an applied electric field, modifying the index of refraction \cite{agrawal2002, goldstein, hausbook, karim}.
-The shape of the electrical (sound) pulse can be controlled in such a way to provide the desired effect of modulation.
-\\
-
-Moreover, a Mach--Zehnder interferometer can be used in tandem with an acousto- or electro-optic modulator to modulate an optical pulse.
-The incident pulse is separated with a Y-waveguide, one of the two branches is then modulated, and finally the two branches are recombined with another Y-waveguide \cite{alazzawi, hausbook, karim}.
-In the absence of a modulator on one of the branches the two pulses recombine into the original pulse.
-However, with modulation the two pulses are no longer identical, and so when the recombine, they interfere.
-This interference can be used to further modulate the pulse \cite{agrawal2002, agrawal2013, hausbook, karim}.
-\\
-
-\subsection{Fibre Bragg Grating}
-A fibre Bragg grating (FBG) is an optical fibre where the refractive index varies periodically along its length \cite{ferreira}.
-To achieve this, typically silica fibres are doped with Germanium which when exposed to intense ultraviolet (UV) light alters the refractive index of the core \cite{becker, starodoumov}.
+\subsection{\glslink{fbg}{Fibre Bragg Grating}}
+\label{sec:fbg}
+A \gls{fbg} is an optical fibre where the refractive index varies periodically along its length \cite{ferreira}.
+To achieve this periodicity, typically silica fibres are doped with Germanium which when exposed to intense \gls{uv} light permanently alters the refractive index of the core \cite{becker, starodoumov}.
 The photosensitivity of the optical fibres can be increased by more than an order of magnitude by the Germanium doping \cite{becker, ferreira}.
@@
 \input{./Figures/PhaseMask}
-\caption{\textbf{Phase-Mask:} The phase-mask refracts the UV light onto the core.}
+\caption{\textbf{Phase-Mask:} The phase-mask refracts the \gls{uv} light onto the core.}
 \label{fig:phasemask}
@@
 \end{subfigure}
-\caption[Manufacture methods of fibre Bragg gratings.]{Depictions of the two most common methods for manufacturing FBGs.
-The UV light is focused on the core causing periodic constructive and destructive interference.
-The UV light alters the refractive index of the core, causing a sinusoidal variation along the length.}
+\caption[Manufacture methods of fibre Bragg gratings.]{Depictions of the two most common methods for manufacturing \gls{fbg}s.
+The \gls{uv} light is focused on the core causing periodic constructive and destructive interference.
+The \gls{uv} light alters the refractive index of the core, causing a sinusoidal variation along the length.}
 \label{fig:fbgmake}
@@
 
-FBGs can be manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
+\gls{fbg}s can be manufactured using one of two methods---the phase-mask method \cite{agrawal2002, alazzawi, becker, starodoumov}, or the holographic side exposure method \cite{agrawal2002, alazzawi, becker, ferreira, starodoumov}---these are shown in Figure \ref{fig:fbgmake}.
 Both methods cause the periodic nature of the refractive index through interference.
-In the phase-mask method (Figure \ref{fig:phasemask}), a single beam of UV light passes through the phase-mask which acts as a series of lenses, focusing the light onto the core---this causes a sinusoidal interference pattern.
-Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of UV light are instead used to create the interference pattern.
+In the phase-mask method (Figure \ref{fig:phasemask}), a single beam of \gls{uv} light passes through the phase-mask which acts as a series of lenses, focusing the light onto the core---this causes a sinusoidal interference pattern.
+Similarly, in the holographic side exposure method (Figure \ref{fig:holographic}), two beams of \gls{uv} light are instead used to create the interference pattern.
 \\
 
-The purpose of FBGs is that they act as reflective filters \cite{agrawal2002, alazzawi, ferreira, starodoumov}.
+The purpose of \gls{fbg}s is that they act as reflective filters \cite{agrawal2002, alazzawi, ferreira, starodoumov}.
 Due to the periodicity of the refractive index, light with the corresponding wavelength will be reflected with all others passing through.
@@
 where $\lambda_B$ is the Bragg wavelength, $\Lambda$ is the period of the grating, and $\bar{n}$ is the average index of refraction.
-Ideally, only light with a wavelength of $\lambda_B$ would be reflected, however, there is a very narrow neighbourhood around $\lambda_B$ in which wavelengths are partially reflected too, the characteristic width of this region is known as the stop-band.
+Ideally, only light with a wavelength of $\lambda_B$ would be reflected, however, there is a very narrow neighbourhood around $\lambda_B$ in which wavelengths are partially reflected too; the characteristic width of this region is known as the stop-band.
 \\
 
-\subsubsection{Chirped Fibre Bragg Grating}
+\subsubsection{\glslink{cfbg}{Chirped Fibre Bragg Grating}}
 \begin{figure}[tbp]
@@
 \input{./Figures/Unchirped}
-\caption{Unchirped Gaussian pulse.}
+\caption{Unchirped Gaussian pulse. $\omega(x) = 3 \pi x$.}
 \label{fig:unchirped}
@@
 \input{./Figures/Chirped}
-\caption{Linearly chirped Gaussian pulse.}
+\caption{Linearly chirped Gaussian pulse. $\omega(x) = 2 (x - \pi)^2$.}
 \label{fig:chirped}
 \end{subfigure}
-\caption[Comparison of a chirped and unchirped Gaussian pulse.]{In an unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.}
+\caption[Comparison of a chirped and unchirped Gaussian pulse.]{In an unchirped pulse the frequency is constant, however, in a chirped pulse the frequency varies along the envelope.
+The waveforms are given by $\exp \left( -x^2/2 \right) \sin \omega (x)$.}
 \label{fig:chirp}
@@
 Figure \ref{fig:chirp} shows examples of chirped and unchirped Gaussian pulses---the most common type of chirp is linear chirp, where the frequency varies linearly across the pulse.
-Because of this, for a spatially varying frequency, the oscillations are characterized by $\exp \left( i k(x) x \right) = \exp \left( i C x^2 \right)$, where $k(x) = Cx$ is the linear variation of the wave number, and $C$ is the chirp parameter.
-By using a chirped phase-mask a chirped fibre Bragg grating (CFBG) can be created.
-Since the period of the refractive index varies across the CFBG, so does when the Bragg condition, \eqref{eq:bragg}, is satisfied.
-This causes most wavelengths to be reflected by a CFBG, but with each wavelength penetrating to a different depth.
-Note that a monotonic chirping ensures that all the wavelengths are simultaneously supported.
+In this case, for a spatially varying frequency, the oscillations are characterized by $\exp \left( i k(x) x \right) = \exp \left( i C x^2 \right)$, where $k(x) = Cx$ is the linear variation of the wave number, and $C$ is the chirp parameter.
+By using a chirped phase-mask, a \gls{cfbg} can be created.
+The spacial variation of the refractive index effectively creates a spacial dependence on the Bragg condition, \eqref{eq:bragg}.
+This causes most wavelengths to be reflected by a \gls{cfbg}, but with each wavelength satisfying the Bragg condition at a different spacial location\footnote{Note that a monotonic chirping ensures that the spacial dependence of the Bragg condition is continuous with respect to the wavelength.}.
 A consequence of this is that a time delay is created between wavelengths---this is depicted in Figure \ref{fig:cfbg} with the upper portion showing  the refractive index as a function of the depth.
 In this orientation, the red (dashed) wave is unable to penetrate as far as the blue (solid) wave since each wave is reflected where it matches the frequency of the refractive index.
+Each \gls{cfbg} has a bandwidth within which all frequencies are reflected at some point along the depth, alternatively, frequencies outside the bandwidth would be transmitted and lost.
 \\
@@
 \input{./Figures/CFBG}
-\caption[Chirped fibre Bragg grating.]{Chirped fibre Bragg grating.
+\caption[Chirped fibre Bragg grating.]{\Acrlong{cfbg}.
+The upper portion shows how the index of refraction varies along the depth.
 Light is reflected when the wavelength coincides with the Bragg wavelength.
@@
 Furthermore, the speed of light in an optical fibre is slightly dependent on the wavelength---this causes light with a longer wavelength to travel faster, and is known as chromatic dispersion.
-This is a large problem in fibre optic communications, the signal can spread and potentially becomes uninterpretable after vast distances.
-However, chromatic dispersion can be counteracted using a CFBG \cite{agrawal2002, alazzawi, becker, starodoumov} (in the opposite orientation of Figure \ref{fig:cfbg}).
+This is a large problem in fibre optic communications, the signal can spread and potentially becomes unrecoverable after vast distances.
+However, chromatic dispersion can be counteracted using a \gls{cfbg} \cite{agrawal2002, alazzawi, becker, starodoumov} (in the opposite orientation of Figure \ref{fig:cfbg}).
 By forcing the longer wavelengths to travel farther the dispersion can be reversed, restoring the original signal.
-In one experiment \cite{dong}, a signal was successfully transmitted over $109$ km at $40$ Gb/s by compensating the dispersion with two  $40$ cm CFBGs.
+In one experiment \cite{dong}, a signal was successfully transmitted over $109$ km at $40$ Gb/s by compensating the dispersion with two  $40$ cm \gls{cfbg}s.
 Over this distance, the pulse would have spread to about $55$ times its original width, and could only have been transmitted $4$ km at that bit rate.
-At reduced bit rates however, a $10$ cm CFBG can compensate the dispersion of $300$ km of fibre \cite{agrawal2002}.
-However, in our case, we wish to accelerate the dispersion, simulating hundreds of metres of fibre, so the CFBG is used in the orientation shown in Figure \ref{fig:cfbg}.
+At reduced bit rates however, a $10$ cm \gls{cfbg} can compensate the dispersion of $300$ km of fibre \cite{agrawal2002}.
+However, in our case, we wish to control the dispersion, simulating hundreds of metres of fibre, so the \gls{cfbg} is used in the orientation shown in Figure~\ref{fig:cfbg}.
+\\
+
+\subsection{Modulator}
+The modulator serves the purpose of reshaping the pulse.
+Without it, the pulse will repeatedly widen due to the \gls{cfbg}, but the modulator ensures the pulse is band limited by altering the envelope.
+The optical pulse in the cavity can be modulated with one of two methods---amplitude modulation, or phase modulation.
+Mathematically these can be considered equivalent since they are Fourier transforms of each other, but in practice these are accomplished by different apparatuses.
+We shall assume the pulses are amplitude modulated to minimize the analysis required in the Fourier domain.
+Generally, the pulse can be amplitude modulated using one of two techniques.
+The first is with an acousto-optic modulator which utilizes the acousto-optic effect where the index of refraction of the optical fibre is varied by a sound wave \cite{hausbook, karim}.
+The second---and more common---method uses the electro-optic effect, where the index of refraction of the optical fibre is varied by a sound wave, and is called an electro-optic modulator.
+This modulator works the same was as an acousto-optic modulator, the optical fibre inside the modulator responds to an applied electric field, modifying the index of refraction \cite{agrawal2002, goldstein, hausbook, karim}.
+The shape of the electrical (sound) pulse can be controlled in such a way to provide the desired effect of modulation.
+\\
+
+A Mach--Zehnder interferometer can be used in tandem with an acousto- or electro-optic modulator to modulate an optical pulse.
+The incident pulse is separated with a Y-waveguide, one of the two branches is then modulated, and finally the two branches are recombined with another Y-waveguide \cite{alazzawi, hausbook, karim}.
+In the absence of a modulator on one of the branches the two pulses recombine into the original pulse.
+However, with modulation the two pulses are no longer identical, and so when the recombine, they interfere.
+This interference can be used to further modulate the pulse \cite{agrawal2002, agrawal2013, hausbook, karim}.
 \\
@@
 An optical circulator is a device that routes signals from port to port in a circular fashion \cite{agrawal2002, alazzawi, becker}, the symbol for a four port optical circulator is shown in Figure \ref{fig:circulator}.
-A signal entering from port 1 will be outputted from port 2; a signal entering from port 2 will exit from port 3; and so forth.
+While a four port optical circulator is most common, within Figure \ref{fig:cavity} only three port optical circulators are required.
+A signal entering from port 1 will be outputted to port 2; a signal entering from port 2 will exit from port 3; and so forth.
 Typically, optical circulators have three or four ports, with the first port being input only, and the final port being output only \cite{alazzawi}.
 Optical circulators are most commonly used with devices that reflect signals instead of transmit them.
-For example, a signal may enter through port 1, exit through port 2, be reflected by an FBG, re-enter port 2, and finally exit through port 3.
+For example, a signal may enter through port 1, exit through port 2, be reflected by an \gls{fbg}, re-enter port 2, and finally exit through port 3.
 \\
@@
 Most commonly, optical amplifiers are created by doping a length of fibre (called the gain fibre) with a rare-earth element which receives power from a pump laser \cite{agrawal2002, alazzawi, starodoumov}.
-The most common dopant is Erbium, however, Ytterbium and Neodymium are also used---Holmium, Samarium, Thulium, and Tellurium are infrequently used as well \cite{agrawal2002}.
+The most common dopant is Erbium, however, Ytterbium and Neodymium are also used.
+Holmium, Samarium, Thulium, and Tellurium are infrequently used as well \cite{agrawal2002}.
 \\
 
-Erbium-doped fibre amplifiers (EDFAs) are used most widely since Erbium has a band gap that corresponds to $1.54$--$1.57$ $\mu$m, which is the preferred band for fibre optics since this has the least power loss \cite{agrawal2002, alazzawi, starodoumov}.
-The pump laser typically operates at $980$ nm or $1.48$ $\mu$m because these wavelengths are able to transfer the most power (up to $100$ mW) into the fibre while introducing minimal noise \cite{agrawal2002, alazzawi, becker, starodoumov}.
+\gls{edfa} are used most widely since the Erbium-doped fibre has a band gap that corresponds to $1.54$--$1.57$ $\mu$m, which is the preferred band for fibre optics since this has the least power loss \cite{agrawal2002, alazzawi, starodoumov}.
+The pump laser typically operates at $980$ nm or $1480$ nm because these wavelengths are able to transfer the most power (up to $100$ mW) into the fibre while introducing minimal noise \cite{agrawal2002, alazzawi, becker, starodoumov}.
 The pump power can be applied either forwards (with the laser), backwards (against the laser), or both \cite{alazzawi}, with each configuration having similar performance \cite{agrawal2002}.
@@
 \input{./Figures/ML1}
-\caption{$n = 4$}
+\caption{$n = 4$, $\text{\acrshort{fwhm}} \approx 0.1255$}
 \end{subfigure}%
@@
 \input{./Figures/ML2}
-\caption{$n = 12$}
+\caption{$n = 12$, $\text{\acrshort{fwhm}} \approx 0.04711$}
 \end{subfigure}
-\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{i = 1}^n \cos \left( 2 \pi i x \right)$.}
+\caption[Two examples of mode-locking.]{Two examples of mode-locking given by $\displaystyle \sum_{k = 1}^n \cos \left( 2 \pi k x \right)$.}
 \label{fig:ml}

### 2019-07-12 Thesis/Model/Model.tex
Finished corrections

@@
 To alleviate some of the pitfalls mentioned in the previous chapter, we shall include all five processes involved in the modification of the pulse within the laser cavity (gain, nonlinearity, loss, dispersion, and modulation).
-In addition to this, the functional operations associated with each component will be derived from \eqref{eq:nlse},
-\begin{align*}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align*}
-with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator. \\
+In addition to this, the functional operations associated with each component will be derived from \eqref{eq:nlse}, with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.
+\\
 
 \section{Components}
+\label{sec:comp}
 We shall begin our analysis with the derivation of the functional operators for the five components. \\
@@
 \label{eq:gainde}
-\pdiff{A}{z} &= \frac{1}{2} g(A),
+\pdiff{A}{z} &= \frac{1}{2} g(A) A,
 \end{align}
@@
 \label{eq:energy}
-	g(A) &= \frac{g_0}{1 + E / \Es} A,& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
+	g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
 \end{align}
@@
 \end{align*}
-adding this to its complex conjugate and integrating over $T$ gives
-%\begin{align*}
-%	\diff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
-%\end{align*}
-%After integrating this becomes
+adding this to its complex conjugate gives
 \begin{align}
-\label{diffez}
+\pdiff{|A|^2}{z} &= \frac{g_0 |A|^2}{1 + E / \Es}.
+\label{eq:diffea}
+\end{align}
+After integrating this becomes
+\begin{align}
 \diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
+\label{eq:diffez}
 \end{align}
 For $E \ll \Es$ the energy will grow exponentially, whereas for $E \gg \Es$ the gain has saturated and so the growth is linear.
-To obtain a closed form solution, \eqref{diffez} is integrated over a gain fibre of length $z$ and assuming the energy increases from $E$ to $E_{\textrm{out}}$, then
+To obtain a closed form solution, \eqref{eq:diffez} is integrated over a gain fibre of length $L_g$, the length of the gain fibre, and assuming the energy increases from $E$ to $E_{\textrm{out}}$, then
 \begin{align*}
-	g_0 z = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es},
+	g_0 L_g = \log\frac{E_{\textrm{out}}}{E} + \frac{E_{\textrm{out}}-E}{\Es},
 \end{align*}
@@
 \begin{align*}
-W \left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es},
+W \left(\frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g}\right) &= W\left(\frac{E_{\textrm{out}}}{\Es} \textrm{e}^{E_{\textrm{out}}/\Es}\right) = \frac{E_{\textrm{out}}}{\Es},
 \end{align*}
@@
 \begin{align*}
-E_{\textrm{out}}(z) = \Es W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 z} \right)
+E_{\textrm{out}} = \Es W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right).
 \end{align*}
-with the desired property that $E_{\textrm{out}}(0)=E$. Furthermore, since $E \sim |A|^2$, the gain in terms of the amplitude is given by
+Notice from \eqref{eq:diffea} and \eqref{eq:diffez} that
 \begin{align*}
-G(A;E) &= \left(\frac{E_{\textrm{out}}(L_g)}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
+\frac{1}{|A|^2}\pdiff{|A|^2}{z} &= \frac{1}{E}\diff{E}{z}
 \end{align*}
-where $L_g$ is the length of the gain fibre.
+and so, $E \sim |A|^2$, therefore the gain in terms of the amplitude is given by
+\begin{align*}
+G(A;E) &= \left(\frac{E_{\textrm{out}}}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A
+\end{align*}
+after passing through the gain fibre once.
 
@@
 \end{align}
-This expression can be manipulated in a similar manner to the gain to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting that $A(z,T) = A_0(T) e^{i \varphi(T,z)}$.
+This expression can be manipulated in a similar manner to the gain to show $\frac{\partial}{\partial z} |A|^2 = 0$, suggesting the \acrshort{wkb} ansatz $A(z,T) = A_0(T) e^{i \varphi(T,z)}$.
 Substituting this representation into~\eqref{eq:fibrediff} and setting $\varphi(T,0)=0$ gives $\varphi(T,z) = \gamma |A|^2 z$.
-For a fibre of length $L_f$ the effect of the nonlinearity is thus
+For a fibre of length $L_f$ the effect of the nonlinearity is given by the map $A \mapsto F(A)$, where
 \begin{align*}
-F(A) &= A \textrm{e}^{i \gamma |A|^2 L_f},
+F(A) &= A \textrm{e}^{i \gamma |A|^2 L_f}.
 \end{align*}
-this is also frequently called the Kerr nonlinearity or Kerr effect after John Kerr who discovered the effect in 1875.
-As we shall see in Section \ref{chap:energy}, this is what is responsible for self-phase modulation and ultimately the degradation of the pulse \cite{desurvire, dunlop, martinez1984, tamura}.
+This is also frequently called the Kerr nonlinearity or Kerr effect after John Kerr who discovered the effect in 1875.
+As we shall see in Section \ref{chap:energy}, this is what is responsible for \acrlong{spm} and ultimately the degradation of the pulse \cite{desurvire, dunlop, martinez1984, tamura1996}.
 
@@
 \end{align*}
-Combining these two effects give a loss that takes the form
+Combining these two effects gives a loss that takes the form
 \begin{align*}
-L(A) &= (1 - R) \textrm{e}^{- \alpha L}A,
+L(A) &= (1 - R) \textrm{e}^{- \alpha L_T}A,
 \end{align*}
-where $R$ is the reflectivity of the output coupler, and $L$ is the total length of the laser circuit.
+where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit.
 
 \subsection{Dispersion}
-Within the laser cavity, the dispersion is dominated by the CFBG. In comparison, the dispersion due to the fibre is negligible. The dispersive terms of \eqref{eq:nlse} give
+Within the laser cavity, the dispersion is dominated by the \gls{cfbg}. In comparison, the dispersion due to the fibre is negligible. The dispersive terms of \eqref{eq:nlse} give
 \begin{align}
 \label{eq:dispde}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T} + \frac{\beta_3}{6} \pdiff[3]{A}{T},
+	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T},
 \end{align}
-and since dispersion acts in the frequency domain it is convenient to take the Fourier transform of~\eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
+and since dispersion acts in the frequency domain it is convenient to take the Fourier transform\footnote{We use $\displaystyle \FT{f} = (2 \pi)^{1/2} \int_\mathbb{R} f(x) \textrm{e}^{i \omega x} \df x$ as the definition of the Fourier transform.} of \eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
 \begin{align*}
-	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\left(\beta_2 - \frac{\beta_3}{3} \omega\right) \FT{A}.
+	\pdiff{}{z}\FT{A} &= i\frac{\omega^2}{2}\beta_2 \FT{A}.
 \end{align*}
-The effect of dispersion is then
+The effect of dispersion is then by the map
 \begin{align*}
-D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D(\beta_2 - \beta_3 \omega/3)/2} \FT{A}}.
+D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}},
 \end{align*}
-For a highly dispersive media the third order effects may need to be considered~\cite{agrawal2013, litchinitser}.
-However, for simplicity and because of the nature of the grating, the third order effects will be neglected \cite{agrawal2013, ferreira}---we set $\beta_3=0$ for the subsequent analysis.
-\\
+where $L_D$ is the length of the dispersive medium. \\
 
 \subsection{Modulation}
-In the master equation of mode-locking, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{1}{2} M_s T^2 A$.
-In this new model, the modulation is considered to be applied externally through its action on the spectrum and for simplicity the representation is taken as the Gaussian
+In \eqref{eq:meml}, the amount of modulation is characterized by the parameter $M_s$ through the term $\frac{1}{2} M_s T^2 A$.
+In this new model, the modulation is considered to be applied externally through its action on the spectrum.
+For simplicity the representation is taken as the Gaussian
 \begin{align*}
@@
 
-Despite assuming a Gaussian modulation the following solution can be generalized to any modulation function in $L^2(\mathbb{R})$ since Gaussians in fact span $L^2(\mathbb{R})$ as will be shown shortly.
+Despite assuming a Gaussian modulation, the solution presented in Section \ref{sec:linear} can be generalized to any modulation function in $L^2(\mathbb{R})$ since Gaussians in fact span $L^2(\mathbb{R})$ as shown in Appendix \ref{chap:gauss}.
 \\
 
-\input{./Appendices/Hermite}
+%\input{./Appendices/Hermite}
 
@@
 The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Specifically, the time shall be scaled by the characteristic modulation time which is related to the pulse duration, the energy by the saturation energy, and the amplitude will be scaled so that it is consistent with the energy:
-\begin{align*}
+Nominal values for tuneable lasers are shown in Table~\ref{tab:values}.
+Knowing experimental durations and energies, the table suggests the convenient scalings:
+\begin{align}
 	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
-\end{align*}
-The new process maps, after dropping the tildes, become
+\end{align}
+Revisiting each process map shows each process has a characteristic non-dimensional parameter. The new mappings, after dropping the tildes, are
 \begin{subequations}
@@
 \end{subequations}
-with the four dimensionless parameters (see Table~\ref{tab:values})
-\begin{align*}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2, \\
-	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04,
-\end{align*}
-which characterize the behaviour of the laser.
+with the four dimensionless parameters, as defined by the values in Table \ref{tab:values},
+\begin{equation}
+\begin{aligned}
+	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04\\
+	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& \qquad s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,
+\label{eq:ndparam}
+\end{aligned}
+\end{equation}
+which characterize the behaviour of the laser. Notice that the modulation is characterized by $T_M$, and each other process has it's own independent non-dimensional parameter.
 
@@
 \noalign{\global\arrayrulewidth=1.5pt}\hline
-Absorption of Fibre & $\alpha$ & $0.01$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, usechak, yarutkina} \\
+Absorption of Fibre\footnotemark & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, usechak, tomlinson, yarutkina} \\
 Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
-Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, usechak, yarutkina} \\
+Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot, usechak, yarutkina} \\
 Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
-Length of Cavity & $L$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng} \\
+Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng, tamura1996} \\
 Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
-Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, yarutkina} \\
+Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, tamura1993, yarutkina} \\
 Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyne2014, burgoyneemail} \\
-Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng} \\
+Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, peng, li, tamura1993, tamura1996, yamashita} \\
 Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
@@
 \end{tabular}
-\caption{Orders of magnitude of various parameters.}
+\caption{Range of variation of various parameters.}
 \label{tab:values}
@@
 
-\section{Combining the Effects}
+\footnotetext{Fibre loss is typically reported as $\sim0.5$ dB/km.}
+
+\section{Combining the Effects of Each Block of the Model}
 \label{sec:effects}
@@
 We are most interested in the output of the laser cavity, and so we shall start with the loss component.
-Next the pulse is passed though the CFBG, as well as the modulator.
+Next the pulse is passed though the \gls{cfbg}, as well as the modulator.
 Finally, the pulse travels through the gain fibre to be amplified, and then we consider the effect of the nonlinearity since this is the region where the power is maximized.
-Note that in general the functional operators of the components do not commute, and therefore the order is indeed important---in contrast to the previous models.
-This is especially the case of dispersion due to the Fourier transform.
+Note that in general the functional operators of the components do not commute, and therefore the order of the components is indeed important---in contrast to the previous models.
+This is especially the case of dispersion as realized through the Fourier transform.
 The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
 Functionally this can be denoted as
-\begin{align*}
+\begin{align}
 	\mathcal{L}(A) = F(G(M(D(L(A))))),
-\end{align*}
+\end{align}
 where $\mathcal{L}$ is one loop of the laser.
-A solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
+A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity, that is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
+The phase shift is allowable because it is immeasurable in the laboratory---only the envelope, chirp, and variance can be measured.
 
@@
 \label{sec:linear}
-In the case of $b = 0$---which shall be referred to as the linear model---a solution can be found analytically.
+In reality the nonlinearity parameter, $b$, is of order unity by \eqref{eq:ndparam}, but we shall start our investigation with the simpler case of $b = 0$---which shall be referred to as the linear model.
+In this case, a solution can be found analytically.
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn}, dispersion will not alter the envelope.
 \\
 
-Consider the initial pulse
-\begin{align*}
+\begin{figure}[tbp]
+\centering
+\input{./Figures/Sample_Gauss}
+\caption{Sample realization of \eqref{eq:A0}.}
+\label{fig:samplegauss}
+\end{figure}
+
+To compute $\mathcal{L}(A)$, consider the initial pulse
+\begin{align}
 	A_0 = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \textrm{e}^{i \phi_0},
-\end{align*}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
-After passing through the optical coupler the pulse will simply decay to $A_1 = h A_0$.
-The pulse then enters the CFBG, where it will maintain its Gaussian shape, however, it will spread \cite{agrawal2013, ferreira, silfvast}.
+\label{eq:A0}
+\end{align}
+where $P$ is the peak power, $C$ is the chirp\footnote{As discussed in Section \ref{sec:fbg}.}, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
+An example of such a pulse is shown in Figure \ref{fig:samplegauss}.
+This form is chosen because it matches the envelope and linear chirping found by experiment.
+After passing through the optical coupler the pulse will simply decay to $A_1 = L(A_0) = h A_0$.
+The pulse then enters the \gls{cfbg}, where it will maintain its Gaussian shape, however, it will spread \cite{agrawal2013, ferreira, silfvast}.
 This can be written as
-\begin{align*}
-A_2 = \sqrt{P} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right) \textrm{e}^{i(\phi_0 + \phi)},
-\end{align*}
-where $\widetilde{\sigma}^2$ denotes the resulting variance, $\widetilde{C}$ denotes the resulting chirp, and $\zeta$ is the reduction of the amplitude caused by the spread.
+\begin{align}
+A_2 = D(A_1) = \sqrt{P} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} \right) \textrm{e}^{i(\phi_0 + \phi)},
+\end{align}
+where $\widetilde{\sigma}^2$ denotes the resulting variance, $\widetilde{C}$ denotes the resulting chirp, $\zeta$ is the reduction of the amplitude caused by the spread, and $\phi$ is the inherited phase shift from dispersion.
+At this point $\widetilde{\sigma}^2$, $\widetilde{C}$, $\zeta$, and $\phi$ remain undetermined, and are used as placeholders for convenience.
 Next, the pulse is modulated:
-\begin{align*}
-A_3 = \sqrt{P} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right) \textrm{e}^{i(\phi_0 + \phi)}.
-\end{align*}
+\begin{align}
+A_3 = M(A_2) = \sqrt{P} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right) \textrm{e}^{i(\phi_0 + \phi)}.
+\end{align}
 Finally, the pulse travels through the gain fibre where it is amplified to
-\begin{align*}
-A_4 = \sqrt{P} \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right) \textrm{e}^{i(\phi_0 + \phi)},
-\end{align*}
+\begin{align}
+A_4 = G(A_3) = \mathcal{L}(A_0) = \sqrt{P} \left( \frac{W(a E \textrm{e}^E)}{E} \right)^{1/2} h \zeta \exp \left( -(1 + i \widetilde{C}) \frac{T^2}{2 \widetilde{\sigma}^2} - \frac{T^2}{2} \right) \textrm{e}^{i(\phi_0 + \phi)},
+\label{eq:A4}
+\end{align}
 with $E$ the energy of the pulse as it enters the gain fibre. \\
 
-In equilibrium it must be that $A_0 = A_4 \textrm{e}^{-i \phi}$. More explicitly, this gives three conditions:
+In equilibrium it must be that $A_0 = A_4 \textrm{e}^{-i \phi} = \mathcal{L}(A_0) \textrm{e}^{- i \phi}$ so that after a single loop of the cavity the variance, chirp, and envelope remain unchanged.
+More explicitly, this gives three conditions:
 \begin{subequations}
@@
 
-\subsection{Spread Due to Dispersion}
+\subsection{Spread of the Pulse Due to Dispersion}
 Each of these processes has a relatively straight forward effect, with the exception of dispersion.
@@
 
-\subsection{Equilibrium Shape}
+\subsection{Equilibrium Shape of the Pulse}
 Now that the effect of dispersion is know analytically, the system \eqref{eq:linsys} can be solved.
@@
 \end{align*}
-Combining this first expression with \eqref{eq:varout} and expanding, we have
+Combining this first expression with \eqref{eq:varout} and expanding the square, we have
 \begin{align*}
@@
 or written as a polynomial in $\sigma$,
-\begin{align*}
+\begin{align}
 0 = \sigma^6 + 4 C s^2 \sigma^4 + \left( 4s^4 (C^2 + 1) - 4 C s^2 \right) \sigma^2 - 4s^4 (C^2 + 1).
-\end{align*}
+\label{eq:midvar}
+\end{align}
 The chirp can now be eliminated using \eqref{eq:chirpout}, the $1+C^2$ can be reduced in order by noticing that
 \begin{align*}
-C \frac{1}{1 - \sigma^2} &= C + (1 + C^2) \frac{2s^2}{\sigma^2}, \\
 1 + C^2 &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} C.
 \end{align*}
-Furthermore, the chirp can be completely eliminated since
+Solving for $C$ gives
 \begin{align}
 \label{eq:equilchirp}
-C &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} \pm \sqrt{\frac{\sigma^8}{16s^4(1 - \sigma^2)^2} - 1} = \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}}{4s^2(1 - \sigma^2)}.
+C &= \frac{\sigma^4}{2s^2(1 - \sigma^2)} \pm \sqrt{\frac{\sigma^8}{16s^4(1 - \sigma^2)^2} - 1} = \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}}{4s^2(1 - \sigma^2)},
 \end{align}
-After simplifying algebraically, we arrive at
-\begin{align*}
-0 &= \sigma^6 \pm \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}(2 - \sigma^2), \\
+and after simplifying \eqref{eq:midvar} algebraically, we arrive at
+\begin{align}
 \frac{\sigma^6}{2 - \sigma^2} &= \mp \sqrt{\sigma^8 - 16s^4(1 - \sigma^2)^2}.
-\end{align*}
+\label{eq:varroot}
+\end{align}
 As we shall see, $\sigma$ is strictly less than $1$ at equilibrium, and so, notice that the left hand side of this expression is strictly positive.
 Therefore, only the negative root of \eqref{eq:equilchirp} will yield a solution.
-Moreover, Martinez, Fork, and Gordon \cite{martinez1984} found two solutions analytically, but showed that one was unstable---consistent with experiments.
-After squaring each side of this expression we obtain
-\begin{align*}
-\sigma^{12} = \sigma^8 (2 - \sigma^2)^2 - 16s^4 (1 - \sigma^2)^2 (2 - \sigma^2)^2,
-\end{align*}
-which once fully simplified, yields the biquartic equation
+Moreover, Martinez, Fork, and Gordon \cite{martinez1984} found two solutions to their discrete model (Section \ref{sec:discrete}) analytically, but showed that one was unstable---consistent with experiments.
+After squaring each side of \eqref{eq:varroot} we obtain the biquartic equation
 \begin{align}
@@
 \end{subfigure}
-\caption[Envelope, Fourier transform, and chirp of the pulse---linear case.]{Equilibrium state for the parameters $s = 0.15$, $b = 0$, $a = 8000$, and $h = 0.04$.}
+\caption[Envelope, Fourier transform, and chirp of the pulse---linear case.]{Equilibrium state of the pulse for the parameters $s = 0.15$ (dispersion), $b = 0$ (nonlinearity), $a = 8000$ (gain), and $h = 0.04$ (loss) as defined by \eqref{eq:equilchirp} and \eqref{eq:equilvar}.}
 \label{fig:linear}
@@
 \subsection{Asymptotic Expansion of the Variance}
+\begin{figure}[tbp]
+\centering
+\input{./Figures/Asympt}
+\caption{Plot of \eqref{eq:asymp} and \eqref{eq:asymp2} to highlight the structure.}
+\label{fig:asympt}
+\end{figure}
 While \eqref{eq:equilvar} is useful, so too is the asymptotic behaviour.
+The asymptotic expansion provides additional information about the structure that the full analytic expression cannot.
+Moveover, the expansion provides more detail about the limits, as well has the rate of convergence.
+Lastly, the expansion allows for simplified expressions within their domains that are much less unwieldy than those found in the previous subsections.
+\\
+
 \input{./Appendices/Asymptotics}
@@
 \subsection{Equilibrium Energy}
-From~\eqref{eq:energycond} the equilibrium energy can be found, as well as the equilibrium peak power. This relation can be simplified by squaring both sides and rearranging to give
+Up until this point the $\sqrt{P}$ factor has remained undetermined, however, it can be found once the equilibrium energy is known.
+From~\eqref{eq:energycond} the equilibrium energy can be found, as well as the equilibrium peak power.
+This relation can be simplified by squaring both sides and rearranging to give
 \begin{align*}
-\frac{1}{h^2 \zeta^2} E = W \left( a E \textrm{e}^E \right).
+\frac{1}{h^2 \zeta^2} E = W \left( a E \textrm{e}^E \right),
 \end{align*}
-Then, by taking the exponential of each side, and multiplying by this expression, we obtain\footnote{By \eqref{eq:lambertw}.}
+where, once again, $W$ is the Lambert $W$ function. Then, by taking the exponential of each side, and multiplying by this expression, we obtain\footnote{By \eqref{eq:lambertw}.}
 \begin{align*}
@@
 \begin{align*}
-E = \frac{h^2 \zeta^2}{1 - h^2 \zeta^2} \log \left( a h^2 \zeta^2 \right).
+E = \frac{h^2 \zeta^2}{1 - h^2 \zeta^2} \log \left( a h^2 \zeta^2 \right). \\
 \end{align*}
-This expression allows us to determine a restriction on the parameters for a solution to exist---in order for this energy to be positive, $a h^2 \zeta^2 > 1$.
+
+This expression allows us to determine a restriction on the parameters for a solution of the form \eqref{eq:A0} to exist---in order for this energy to be positive, $a h^2 \zeta^2 > 1$.
 The energy of the pulses as it enters the optical coupler can now be found, recall from \eqref{eq:gainde} that the energy is defined as
@@
 E_* &= \int_{-\infty}^\infty |G(A)|^2 \, \df T = \frac{W(a E \textrm{e}^E)}{E} \int_{-\infty}^\infty |A|^2 \, \df T = W(a E \textrm{e}^E).
+\label{eq:equilenergy}
 \end{align}
 
-We can now find the amplitude of the pulse as well, as we have previously found the equilibrium shape. Again, from \eqref{eq:gainde}, it must be that $E_* = \sqrt{\pi} P \sigma$, or,
+We can now find the amplitude of the pulse as well now that the energy is know---as we have previously found the equilibrium shape.
+Again, from \eqref{eq:gainde}, it must be that $E_* = \sqrt{\pi} P \sigma$, or,
 \begin{align}
 P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma}.
+\label{eq:equilpower}
 \end{align}
-The asymptotic expansions when $s \rightarrow 0$ of the energy, and peak power are
-\begin{align*}
+The asymptotic expansions when $s \rightarrow 0$ of the energy, and peak power are---for completeness---
+\begin{align}
 E_* &= \Lambda - \Theta \frac{\Lambda}{1 + \Lambda} s + \bigO{s^2}, & P &= \frac{\Lambda}{\sqrt{2 \pi s}} + \left( \frac{\Lambda}{2} -  \Theta \frac{\Lambda}{1 + \Lambda} \right) \sqrt{\frac{s}{2 \pi}} +  \bigO{s^{3/2}},
-\end{align*}
+\label{eq:epasymp}
+\end{align}
 respectively, where
@@
 \end{align*}
+
+\section{Chapter Summary}
+In this chapter we first derived the effect each of the five components---gain, nonlinearity, loss, dispersion, and modulation---has on the incoming pulse from \eqref{eq:nlse}.
+Furthermore, to highlight the structure of these effects the system was non-dimensionalized.
+This yielded the functional maps \eqref{eq:effects} for the components, with corresponding non-dimensional parameters \eqref{eq:ndparam}.
+With each of the operators defined, we proceeded to compose each process, in the order most representative of a tuneable laser, to give the effect of one complete circuit around the laser cavity.
+\\
+
+We then sought a solution to the linearized model---having omitted the nonlinearity component.
+In this case, we were able to find a closed form analytic solution for the equilibrium state.
+To do this, we assumed the solution took the form of a linearly chirped Gaussian, \eqref{eq:A0}, which was then passed through each process map yielding \eqref{eq:A4} in the end.
+The fixed point of the linearized model was found by equating \eqref{eq:A0} and \eqref{eq:A4}, but, allowing a phase shift to have occured.
+The equilibrium variance, chirp, energy, and peak power were found to be \eqref{eq:equilvar}, \eqref{eq:equilchirp}, \eqref{eq:equilenergy}, and \eqref{eq:equilpower}, respectively.
+To gain a better understanding of the limiting behaviour, the asymptotic expansions were investigated.
+This yielded \eqref{eq:asympt} for the asymptotic expansions of the variance and chirp, and \eqref{eq:epasymp} for the energy and peak power.
+\\
+
+With the linear model fully solved, we shall now turn our attention to the rich structure added by the full nonlinear model. \\

### 2019-07-12 Thesis/Nonlinear/Nonlinear.tex
Finished corrections

@@
 \label{chap:nl}
-We shall now consider the nonlinear case---when $b > 0$. In this case it becomes much too difficult to obtain an analytic result. Recall from \eqref{eq:fibre} that the nonlinearity takes the form
+We shall now consider the nonlinear case---when $b > 0$. In this case it becomes impossible to obtain an analytic result. Recall from \eqref{eq:fibre} that the nonlinearity takes the form
 \begin{align*}
@@
 \end{align*}
-This is a highly nonlinear operator, and attempting to take the Fourier transform of a pulse that has under gone this transformation quickly becomes futile.
+This is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone the transformation due to the nonlinearity is futile.
 Instead we must resort to a numerical solution.
@@
 Finding the solution numerically will be done in a similar manner as with the analytic linear solution.
-Using Python a function is written for each component of the laser cavity given by \eqref{eq:effects}, an initial pulse is iteratively passed from function to function in the hopes that a `fixed point' is found.
-The full Python code can be found in Appendix \ref{chap:code}.
+Using Python, a function is written for each component of the laser cavity given by \eqref{eq:effects}; an initial pulse is iteratively passed from function to function in the hopes that a fixed point is found.
+The full Python code can be found in Appendix~\ref{chap:code}.
 \\
@@
 \subsection{Validation}
-Before delving into the nonlinear behaviour of the model, we wish to validate that the code is working as expected---and as a sanity test for the linear solution---by comparing the results of the simulations with $b=0$ to the results of the linear model in Chapter \ref{chap:linear}.
-In the case of the numerical solution, our initial conditions become somewhat important.
-In all of the following analysis the initial waveform is $\Gamma \sech \left( 2T \right) \textrm{e}^{i \pi / 4}$ normalized so that the initial energy is $E_0 = 0.1$; additionally, $a = 8000$, and $h = 0.04$.
-\\
 \begin{figure}[tbp]
@@
 \input{./Figures/Variance}
-\caption[Equilibrium variance, chirp, and phase shift of the pulse as a function of $s$.]{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of $s$.
+\caption[Equilibrium variance, chirp, and phase shift of the pulse as a function of the dispersion parameter.]{Simulation and analytic equilibrium variance, chirp, and phase shift as a function of the dispersion parameter, $s$.
 The analytic expressions are given by \eqref{eq:equilvar}, \eqref{eq:equilchirp}, \eqref{eq:phase}, respectively.}
@@
 \end{figure}
+Before delving into the nonlinear behaviour of the model, we wish to validate that the code is working as expected by comparing the results of the simulations with $b=0$ to the results of the linear model in Chapter \ref{chap:linear}.
+In the case of the numerical solution, our initial conditions become somewhat important for two reasons.
+First, if the energy is too high initially the nonlinear effects are too strong leading to \acrlong{spm}.
+Secondly, the initial waveform needs to be well behaved enough so that the Fourier transform is band limited.
+In all of the following analysis the initial waveform is $\Gamma \sech \left( 2T \right) \textrm{e}^{i \pi / 4}$ normalized so that the initial energy is $E_0 = 0.1$; additionally, $a = 8000$, and $h = 0.04$.
+\\
 
-In the first experiment the pulse is allowed to equilibrate for 40 loops of the circuit, we then compare the variance, chirp, and phase shift of the two methods.
-The results of this are shown in Figure \ref{fig:var}.
-For the most part, we see exceptional agreement between the analytic solution and numerical solution for the variance, and phase shift.
-However, for $s > 2.4$ the chirp from the simulations seems to erratically vary from the analytic solution.
-The reason for this is quite a simple one.
-\\
 \begin{figure}[tbp]
@@
 \input{./Figures/LinearPlot}
-\caption[Equilibrium energy, and peak power of the pulse as a function of $s$.]{Equilibrium energy, and peak power of the pulse as a function of $s$.
-The thin black line is to highlight that the energy is \emph{not} linearly dependent on $s$.}
+\caption[Equilibrium energy, and peak power of the pulse as a function of the dispersion parameter.]{Equilibrium energy, and peak power of the pulse as a function of the dispersion parameter, $s$.
+The thin black line is the line of best fit to highlight that the energy is \emph{not} linearly dependent on $s$.}
 \label{fig:valenergy}
@@
 
-To investigate this behaviour, we instead turn our attention to the energy, and amplitude of the pulse at equilibrium as shown in Figure \ref{fig:valenergy}.
+In the first experiment the pulse is allowed to equilibrate for 40 loops of the circuit\footnote{The choice of 40 will be justified in the following section.}, we then compare the variance, chirp, and phase shift of the analytic and numerical solution.
+The results of this are shown in Figure \ref{fig:var}.
+For the most part, we see exceptional agreement between the analytic solution and numerical solution for the variance, and phase shift.
+However, as $s \rightarrow 2.5$ the chirp from the simulations begins to deviate from the analytic solution.
+The reason for this is quite a simple one.
+We shall turn our attention to the energy, and amplitude of the pulse at equilibrium as shown in Figure \ref{fig:valenergy}.
 As with Figure \ref{fig:var}, there is very good agreement between the two solutions.
@@
 This is of course a consequence of the condition \eqref{eq:energycond}.
-Since the pulse effectively vanishes after this point, the chirp calculation becomes numerically unstable leading to the wild oscillations.
+Since the pulse effectively vanishes after this point, the chirp calculation becomes numerically unstable leading to the disagreement.
 \\
 
-With the numerical solution yielding the expected results, we are now ready to dive into the rich structure the nonlinearity adds.
+With the numerical solution yielding the expected results we are now ready to explore the rich structure, which the nonlinearity adds.
 
@@
 If the pulse were a Gaussian, we would expect the Fourier transform to also be a Gaussian \cite{debnath, gradshteyn}.
-Instead, the magnitude of the Fourier transform has a unique Batman-like shape.
-This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---this will be a key observation in the coming subsections.
+Instead, the magnitude of the Fourier transform has a unique weakly bi-modal shape.
+This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---a key observation in the coming subsections.
 Finally, we shall examine the derivative of the phase---essentially the chirp.
-Recall in Chapter \ref{chap:linear} the chirp was defined as coefficient of $-\frac{1}{2}iT^2$ in the exponential, by taking the negative of the derivative we would expect a linear function with a slope equal to the chirp.
-In the nonlinear case, this is what we find for moderate values of $T$.
-On the other hand, for $|T| > 1$ the relation begins to level off.
-This is in agreement with experimental results \cite{chen, rothenberg, tomlinson}.
-While the nonlinear model yields similar results as the linear model (Figure \ref{fig:linear}), very interesting variations arise from the nonlinearity.
+Recall in Chapter \ref{chap:linear} the chirp was defined as coefficient of $-\frac{1}{2}iT^2$ in the exponential, and by taking the negative of the derivative we would expect a linear function with a slope equal to the chirp.
+In the nonlinear case, we recover this linear response for moderate values of $T$.
+However, for $|T| > 1$ the chirp begins to saturate.
+This is consistent with experimental results \cite{chen, rothenberg, tomlinson}.
 \\
-
-We shall now take a look at perhaps the most important feature of the pulse---the energy. \\
 
@@
 
+\begin{figure}[tbp]
+\centering
+\input{./Figures/ROC}
+\caption{Rate of convergence as a function of number of iterations for various $s$ values, and $b = 0.5$. The error is given by \eqref{eq:error}.}
+\label{fig:roc}
+\end{figure}
+
 \begin{figure}[p]
 \centering
-\begin{subfigure}{\textwidth}
-\input{./Figures/StabilityZoom}
-\caption{Centralized for typical $s$, and $b$ values.}
-\label{fig:energyzoom}
-\end{subfigure} \\
 \begin{subfigure}{\textwidth}
@@
 \label{fig:energybig}
+\end{subfigure} \\
+\begin{subfigure}{\textwidth}
+\input{./Figures/StabilityZoom}
+\caption{Regime corresponding to typical $s$, and $b$ values for tuneable lasers.}
+\label{fig:energyzoom}
 \end{subfigure}
-\caption[Energy of the pulse at equilibrium.]{Energy of the pulse at equilibrium. The energy is constant along the black lines.}
+\caption[Energy of the pulse.]{Energy of the pulse after 100 cycles. The energy is constant along the black lines.}
 \label{fig:energy}
@@
 The energy of the pulse is directly related to the output power of the laser, and since this is not as controllable as in a regular laser, it is of great interest.
-The energy of the pulse at equilibrium\footnote{The pulse is passed through each component of the laser 40 times before the energy is computed.} is shown in Figure \ref{fig:energy}.
+In this nonlinear case we allow the initial pulse to pass through each component 100 times instead of 40 in the linearized case.
+This choice can be justified by Figure \ref{fig:roc}.
+The pulse reaches a state in which the error no longer decreases within typically 10--20 iterations.
+In the linearized case we chose to iterate 40 times since this is about double the number of iterations expected.
+Furthermore, in the nonlinear case we extend this number further to 100 in case the nonlinearity increases the number of iterations to converge.
+The energy of the pulse after 100 iterations is shown in Figure \ref{fig:energy}.
 In Figure \ref{fig:energyzoom} we generally find that the energy is a smooth surface that slowly decays as $s$, and $b$ increase.
 In the upper left hand region of the plot this is clearly not the case.
-The contours show that the energy is very noisy and discontinuous.
-Perhaps more surprising, as shown in Figure \ref{fig:energybig}, is that this boundary appears to become periodic as $b$ increases around $s = 0.3$.
-These features are further highlighted in Figure \ref{fig:cartoon} by disregarding the energy and only examining whether the pulse is stable or not.
+The contours show that the energy is very noisy with very large derivatives.
+Perhaps more surprising, as shown in Figure \ref{fig:energybig}, is that this boundary between periodic and aperiodic behaviour appears to become periodic (in the parameter space) as $b$ increases around $s = 0.3$.
+These features are further highlighted in Figure \ref{fig:cartoon} by disregarding the energy and only examining whether the pulse is invariant after additional iterations.
 \\
@@
 %\end{wrapfigure}
-\begin{figure}[tbp]
-\centering
-\input{./Figures/EffNL}
-\caption{Approximate effective nonlinearity.}
-\label{fig:effnl}
-\end{figure}
-This periodic strip can be explained from the functional nature of the nonlinearity. Recall once again that from \eqref{eq:fibre} that the nonlinearity takes the form
-\begin{align*}
-F(A) &= A \textrm{e}^{i b |A|^2}.
-\end{align*}
-The strength of the nonlinearity is thus controlled by $b |A|^2$, where $|A|^2$ is the power of the pulse.
+%\begin{figure}[tbp]
+%\centering
+%\input{./Figures/EffNL}
+%\caption{Approximate effective nonlinearity.}
+%\label{fig:effnl}
+%\end{figure}
+%This periodic strip can be explained from the functional nature of the nonlinearity. Recall once again that from \eqref{eq:fibre} the nonlinearity takes the form
+%\begin{align*}
+%F(A) &= A \textrm{e}^{i b |A|^2}.
+%\end{align*}
+%This of course is periodic in $b$, however, the period of boundary of stability does not share a period of $2\pi$ because
+
+%The strength of the nonlinearity is thus controlled by $b |A|^2$, where $|A|^2$ is the power of the pulse.
 Although not the greatest, we can approximate the power of the pulse by the energy so that $b |A|^2 \sim b E$, this gives an estimate for what shall be referred to as the effective nonlinearity.
-Figure \ref{fig:effnl} shows the effective nonlinearity at equilibrium.
+Figure \ref{fig:effnl} shows the effective nonlinearity.
 Notice that as $b$ increases along the strip $0.2 < s < 0.4$, the contours become steeper and steeper.
@@
 
-\subsubsection{Self-Phase Modulation and Wave Breaking}
+\subsubsection{\glslink{spm}{Self-Phase Modulation} and Wave Breaking}
+\glsreset{spm}
 
@@
 Wave breaking is not limited to just optics; wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
-Wave breaking occurs because the pulse begins to interfere with itself in a way called self-phase modulation \cite{agrawal2002, agrawal2013, becker}.
-Self-phase modulation occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
+Wave breaking occurs because the pulse begins to interfere with itself in a way called \gls{spm} \cite{agrawal2002, agrawal2013, becker}.
+\gls{spm} occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
 This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson}, as we saw in Figure \ref{fig:nlstable}.
 These high frequencies compound with each trip around the cavity becoming parasitic very quickly---Figure \ref{fig:break} highlights this.
-Notice that the difference between this and Figure \ref{fig:nlstable} is a difference in $b$ of $0.05$---this difference could be as small as adding a few centimetres more of fibre between the gain and output coupler.
-The left figures show the pulse after 11 trips around the cavity; in the Fourier transform it is clear that the contributions from higher frequencies has increased---we obtain similar results as in \cite{anderson, rothenberg}.
-Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is again in agreement with \cite{anderson, rothenberg}.
+Notice that the difference between Figure \ref{fig:nlstable} and Figure \ref{fig:break} is a difference in $b$ of $0.05$---just enough to cross the boundary---this difference could be attributed to adding a few centimetres more of fibre between the gain and output coupler.
+The left figures show the pulse after 11 trips around the cavity; in the Fourier transform it is clear that the contributions from higher frequencies has increased.
+We obtain comparable results as in the experiments \cite{anderson, rothenberg}.
+Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is again in agreement with the experiments \cite{anderson, rothenberg}.
 The parasitic nature of the high frequency contributions is evident by examining the right figures.
 After five additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
-Moreover, the Fourier transform has no clear structure and has essentially become noise, and the chirp has grown to be highly oscillatory and unstable.
-Once the pulse has reached a state such as this, there is no turning back---the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
+Moreover, the Fourier transform has no clear structure and has essentially become noise.
+The chirp has grown to be highly oscillatory and unstable.
+Once the pulse has reached a state such as this---the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
 \\
@@
 \input{./Figures/Step1}
-\caption[Error of the pulse.]{Error of the pulse (given by \eqref{eq:error}) between iterations $99$ and $100$.}
+\caption[Error of the pulse envelope.]{Error of the pulse (given by \eqref{eq:error}) between iterations $99$ and $100$.}
 \label{fig:error}
@@
 \end{subfigure} \\
-\caption[Error for various values of $\Delta$.]{Error for various values of $\Delta$, the colour bar and axis labels have been omitted for clarity, the scales and ranges are the same as in Figure \ref{fig:error}.}
+\caption[Error for various step sizes.]{Error for various values of $\Delta$, the colour bar and axis labels have been omitted for clarity, the scales and ranges are the same as in Figure \ref{fig:error}.}
 \label{fig:deltaerror}
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule.
-Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested about the phase shift between iterations.
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{12}$).
+Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested in the phase shift between iterations.
 A plot of the error can be found in Figure \ref{fig:error}, with $i = 100$.
+The standard method would be to iterate until a fixed tolerance is reached, however, there are some reasons that make a fixed number of iterations preferable---as long as a sufficient number is chosen.
+The main reason is that this allows us to observe a richer structure than simply whether or not the tolerance had been reached by some maximum number of iterations.
+Additionally, incorrectly choosing the critical tolerance could easily lead to erroneous categorizations at points.
+As we saw in Figure \ref{fig:roc} some values of the parameters lead to a steady, periodic state, but with an error of $\bigO{10^{-6}}$, and so, had we set the tolerance to $10^{-8}$ these points would have been labeled as unsteady.
 \\
@@
 As mentioned in the previous subsection, the pulse does not reach a stable state in this region.
-As a consequence the envelope varies violently, which leads to this large error.
-On the other hand, the region where the energy appeared to be stable does not have a non-zero error---there are a few reasons for this.
-First, because of the numerical calculation, for all intents and purposes an error less than $10^{-10}$ can be considered $0$.
-Understanding the other sources of these small errors requires a deeper examination.
-\\
-
-The second cause of these errors is because some equilibrium states have a periodicity greater than $1$, we redefine \eqref{eq:error} to be instead
+As a consequence the envelope varies drastically, which leads to this large error.
+Conversely, the region where the energy appeared to be stable still has a non-zero error.
+The cause of this discrepancy is because some equilibrium states have a periodicity greater than $1$, thus, we redefine \eqref{eq:error} to be instead
 \begin{align}
@@
 Lastly, $\Delta \in \left\{ 5, 7, 11, 13 \right\}$ may not seem to extract any higher order periods, however, there are in fact very small striations in the lower left.
-So far, the $\Delta$ values have been prime since they are the building blocks for composite numbers.
-However, there are two composite $\Delta$ values of interest---the first being $16$.
-Since $16 = 2^4$ it will pick up any periodic behaviour with orders of $2, 4, 8, 16$, which are frequently found in bifurcations.
-Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible---it is an abundant number.
-This extracts orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
+We typically chose $\Delta$ values to be prime since they are the building blocks for composite numbers.
+However, there are two composite $\Delta$ values of interest.
+The first is $16$, since $16 = 2^4$ and it will pick up any periodic behaviour with orders of $2, 4, 8, 16$.
+Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible extracting orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
 \\
@@
 Compared with the error from Figure \ref{fig:error} the lower right region is much more well behaved, that is, the error is a few orders of magnitude lower.
-A peculiar trait of the band between the unstable and stable regions is that within this area the pulse is in a quasi-stable state---the pulse is stable and has reached a sort of equilibrium, however, the envelope of the pulse has minute variations with no clear period.
+A peculiar trait of the band between the unstable and stable regions is that within this area the pulse is in a quasi-stable state---the pulse is stable and has reached a sort of equilibrium, however, the envelope of the pulse has small variations with no clear period.
 Additionally, there appears to be no periodicity of the envelope within the wave breaking region, further supporting the claim that the pulse here is completely unstable.
@@
 \begin{subfigure}{\textwidth}
-\input{./Figures/StabilitySwitchZoom}
-\caption{Centralized for typical $s$, and $b$ values.}
-\label{fig:switchzoom}
-\end{subfigure} \\
-\begin{subfigure}{\textwidth}
 \input{./Figures/StabilitySwitch}
@@
 \label{fig:switchbig}
+\end{subfigure} \\
+\begin{subfigure}{\textwidth}
+\input{./Figures/StabilitySwitchZoom}
+\caption{Regime corresponding to typical $s$, and $b$ values for tuneable lasers.}
+\label{fig:switchzoom}
 \end{subfigure}
-\caption{Energy of the pulse at equilibrium with the modulation and dispersion blocks switched.}
+\caption{Energy of the pulse after 100 cycles with the modulation and dispersion blocks switched.}
 \label{fig:switch}
@@
 We chose to put the dispersion block ahead of the modulator.
-However, there was no real reason behind this---modulation before dispersion is equally as valid---and in this subsection we explore the effect of modulating the pulse before it passes through the CFBG.
+However, there was no real reason behind this---modulation before dispersion is equally as valid---and in this subsection we explore the effect of modulating the pulse before it passes through the \gls{cfbg}.
 \\
@@
 Instead we find a parabolic shape on the top contour, and two lobes on the second contour.
+\\
+
+\section{Chapter Summary}
+In this chapter we investigated how the nonlinear solution deviates from the linear solution by including the effects of the nonlinearity.
+We did this numerically; First we had to validate the code by comparing to the analytic result from Chapter \ref{chap:linear}.
+Once the code yielded the expected results for the linearized version, we incorporated on the nonlinearity.
+\\
+
+We began our investigation with the quantity of most interest---the energy.
+The energy of the pulse at equilibrium was shown in Figure \ref{fig:energy}.
+Generally, the results were as expected with the exception of the left-hand region.
+In this region, while smooth, the derivatives of the energy were very large leading to a very rough and noisy surface.
+It's this region where \gls{spm} takes over and ultimately leads to the pulse becoming unstable and breaking.
+When considering the nonlinearity the pulse begins to interfere with itself which causes this instability.
+\\
+
+To better understand the stability of the pulse, we turned our attention to computing the error between consecutive iterations by \eqref{eq:error}.
+This showed that the relative error within the wave breaking region is of order unity.
+Whereas, in the stable region the error took on values between $10^{-4}$ and $10^{-16}$.
+This is because the pulse reached a steady state with a periodicity greater than 1, this was highlighted by computing the composite error, \eqref{eq:deltaerror}, shown in Figure \ref{fig:errorcomp}.
+\\
+
+Finally, because the components of our model do not necessarily commute with each other and the order is important, we considered the effect of swapping the dispersion and modulation components.
+Overall, the structure of the solutions were very similar, as we saw in Figure \ref{fig:switch}.
+There were two main differences---the first was that the boundary between stable and unstable has shifted to a larger value of the dispersion parameter, $s$.
+The second difference was that the energy, in general, was higher as in Figure \ref{fig:energy}.
+\\

### 2019-07-12 Thesis/Previous_Models/Previous.tex
Finished corrections

@@
 In this chapter we shall explore the previous modelling efforts by first reviewing the classic equations used in nonlinear optics.
-We will then build upon this to obtain the master equation of mode-locking, where the solutions to this will briefly be reviewed before considering `discretized' functional models.
+We will then build upon this to obtain the master equation of mode-locking, the solutions to this will briefly be reviewed before considering discretized functional models.
 \\
 
-\section{Generalized Nonlinear Schr\"odinger Equation}
-The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE) \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}
-\begin{align*}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A.
-\end{align*}
-Here $A = A(z, T)$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order---or group delay---dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient.
-This equation can be derived from the nonlinear wave equation for electric fields, the derivation is presented in detail in \cite{agrawal2013, ferreira}.
-Within the derivation comoving coordinates are used so that the reference frame propagates with the pulse at the group velocity.
-This is achieved with the substitution
+\section{Nonlinear Optics}
+The standard equation for studying nonlinear optics---which can be derived from the nonlinear wave equation for electric fields\footnote{The derivation is presented in detail in \cite{agrawal2013, ferreira}.}---is
+\begin{align}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{t} + i \gamma |A|^2 A - \frac{1}{v_g} \pdiff{A}{t}.
+\label{eq:NLoptics}
+\end{align}
+Here $A = A(z, t) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order---or group delay---dispersion, $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity or Kerr coefficient, and $v_g \in \mathbb{R}^+$ is the group velocity.
+However, it is customary to transform \eqref{eq:NLoptics} into a comoving reference frame, this is achieved with the substitution
 \begin{align}
@@
 reminiscent of moving to a fixed frame in a free boundary problem \cite{ockendon}.
-In this way, $z$ defines the distance travelled by the pulse, and $T$ the time difference from the peak of the pulse.
-Moreover, $T = 0$ is the peak of the pulse regardless of the actual time elapsed, because of this, generally $T$ is not very large.
-In standard coordinates the nonlinear Schr\"odinger equation has an additional term:
-\begin{align*}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{t} + i \gamma |A|^2 A - \frac{1}{v_g} \pdiff{A}{t}.
-\end{align*}
-However, under the transformation \eqref{eq:shift}, we have that $\pdiff{}{t} \mapsto \pdiff{}{T}$, and $\pdiff{}{z} \mapsto \pdiff{}{z} - \frac{1}{v_g} \pdiff{}{T}$ by chain rule, thus, cancelling out this final term.
+Now, $\pdiff{}{t} \mapsto \pdiff{}{T}$, and $\pdiff{}{z} \mapsto \pdiff{}{z} - \frac{1}{v_g} \pdiff{}{T}$ by chain rule.
+Under this transformation, $z$ still defines the distance travelled by the pulse, but, $T$ now designates the time difference from the peak of the pulse for a given $z$.
+Moreover, $T < 0$ is the leading edge of the pulse, and $T > 0$ is the trailing edge regardless of the actual time elapsed, and because of this, generally $T$ is not very large.
+Furthermore, the substitution \eqref{eq:shift} cancels the final term of \eqref{eq:NLoptics}, yielding
+\begin{align}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A.
+\label{eq:smallnlse}
+\end{align}
+Despite being physically unrelated to quantum mechanics \eqref{eq:smallnlse} is called the \gls{nlse} because of it's functional similarity \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}.
 \\
 
-In practice, this equation lacks a few key terms.
-Thus, it is often generalized by adding amplification, loss, and higher order terms.
-This gives the generalized nonlinear Schr\"odinger equation (GNLSE) \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
-\begin{align}
-\label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
-\end{align}
-where $\beta_3 \in \mathbb{R}$ is the third order coefficient of dispersion, $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}$ is the loss due to scattering and absorption. \\
-
-The GNLSE takes the same form as the Schr\"odinger equation with the inclusion of the cubic nonlinear term, hence its name.
-For this reason, it is sometimes referred to as the cubic nonlinear Schr\"odinger equation.
-For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this has the addition of a quintic term to incorporate nonlinearities associated with such large powers.
-Furthermore, the $\beta$ terms come from a Taylor expansion of the wavenumber \cite{kartner}, that is,
+The $\beta_2$ term comes from a Taylor expansion of the wavenumber \cite{kartner}, that is,
 \begin{align*}
@@
 \end{align*}
-where $k_0$ is the phase shift.
-Typically, the third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth~\cite{agrawal2013}.
+where $\omega_0$ is the central frequency of operation, $k_0 = k(\omega_0)$, and $\beta_3$ is the third order dispersive effects.
+Typically, these third order effects must only be considered for ultrashort pulses---pulse widths less than $\sim5 \text{ ps}$---because of their large bandwidth~\cite{agrawal2013}, or a highly dispersive media \cite{agrawal2013, litchinitser}.
+However, for simplicity and because of the nature of the grating, the third order effects can be neglected \cite{agrawal2013, ferreira}.
+\\
+
+In practice, \eqref{eq:smallnlse} lacks a few key terms.
+Thus, it is often generalized by adding amplification, loss, and occasionally higher order terms.
+This gives the \gls{gnlse} \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
+\begin{align}
+\label{eq:nlse}
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
+\end{align}
+where $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}$ is the loss due to scattering and absorption. \\
+
+%The \gls{gnlse} takes the same form as the Schr\"odinger equation with the inclusion of the cubic nonlinear term.
+For this reason, it is sometimes referred to as the cubic nonlinear Schr\"odinger equation.
+%For intensities approaching $1 \text{ GW/cm}^2$, the $\gamma$ parameter must be replaced by $\gamma_0 (1 - b_s |A|^2)$, where $b_s$ is a saturation parameter \cite{agrawal2013}, this has the addition of a quintic term to incorporate nonlinearities associated with such large powers.
 
@@
 \label{chap:meml}
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers we wish to add a modulation term to ensure mode-locking, this yields the master equation of mode-locking, \cite{hausbook, haus1975, haus1986, haus1992, haus2000, kartner, tamura, usechak}
+The \gls{gnlse} has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers we wish to add a modulation term to ensure mode-locking, this yields the master equation of mode-locking, \cite{hausbook, haus1975, haus1986, haus1992, haus2000, kartner, tamura1996, usechak}
 \begin{align}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \frac{\beta_3}{6}\pdiff[3]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T).
+\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T).
 \end{align}
-The most common form of modulation is the sinusoid $M(T) = \frac{1}{2}\frac{M_s}{\omega_M^2} \left( 1 - \cos \left( \omega_M T \right) \right)$ \cite{hausbook, haus1975, haus1996, kartner}, and since $T$ is generally small, by \eqref{eq:shift}, we expand via it's Taylor series so that $M(T) = \frac{1}{2}M_s T^2 + \bigO{T^4}$.
-This brings us to the most common form of the master equation of mode-locking (neglecting the third order dispersion),
+The most common form of modulation is the sinusoid $M(T) = \frac{1}{2}\frac{M_s}{\omega_M^2} \left( 1 - \cos \left( \omega_M T \right) \right)$ \cite{hausbook, haus1975, haus1996, kartner}, where $M_s$ is the strength of modulation and $\omega_M$ is the frequency of modulation.
+Moreover, since $T$ is generally small, we expand via Taylor series so that $M(T) = \frac{1}{2}M_s T^2 + \bigO{T^4}$.
+This brings us to the most common form of the master equation of mode-locking,
 \begin{align}
@@
 \end{align}
-Commonly, in an attempt to simplify the equation the gain is assumed to be constant with $g(A) = 2g_0 \in \mathbb{R}$.
-As a whole no analytic solution is known for \eqref{eq:meml}, however, after additional simplifications there are three flavours of solutions.
+Commonly, in an attempt to simplify the equation, the gain is assumed to be constant with $g(A) = 2g_0 \in \mathbb{R}$.
+No analytic solution is known for \eqref{eq:meml}, however, after additional simplifications there are three types of solutions.
 \\
@@
 In the least complicated case, the modulation and nonlinearity are both omitted giving
-\begin{align*}
+\begin{align}
 \pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A.
-\end{align*}
+\label{eq:disc1}
+\end{align}
 This results in a solution in the form of a hyperbolic secant \cite{haus1975, haus1986, haus1992}. On the other hand, including the nonlinearity yields
-\begin{align*}
+\begin{align}
 \pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \left( g_0 - \alpha \right) A,
-\end{align*}
+\label{eq:disc2}
+\end{align}
 where a similar solution is found, however, it is instead of the form of a chirped hyperbolic secant \cite{haus1991, usechak}.
-Both of these are unsurprising since this reduces to the soliton solution of the NLSE \cite{ferreira}.
+The nature of the solutions to \eqref{eq:disc1} and \eqref{eq:disc2} is as expected.
+These equations are slight generalizations of \eqref{eq:smallnlse} which has a soliton solution of a hyperbolic secant \cite{ferreira}.
 Finally, by including the modulation term, and excluding the nonlinearity we have
-\begin{align*}
+\begin{align}
 \pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + \left( g_0 - \alpha \right) A - \frac{1}{2}M_s T^2.
-\end{align*}
-This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura, usechak}.
+\end{align}
+This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura1996, usechak} defined recursively as
+\begin{align}
+\Her{n}{x} &:= (-1)^n \textrm{e}^{x^2 / 2} \diff[n]{}{x} \textrm{e}^{-x^2},
+\label{eq:gaussherm}
+\end{align}
 However, in practice only the Gaussian is stable---the higher modes quickly decay within the laser \cite{hausbook, haus1975, haus1996, haus2000}.
-For a more comprehensive and exhaustive history see \cite{haus2000}.
+For a more comprehensive history see \cite{haus2000}.
 \\
@@
 \section{Discrete Functional Models}
-While solutions to the master equation yield reasonable results, it is not necessarily representative of what happens within the laser cavity.
-The issue with \eqref{eq:meml} is that it assumes each process effects the pulse continuously within the cavity.
+\label{sec:discrete}
+While the derivation of \eqref{eq:meml} is correct mathematically, it is not representative of what happens within the laser cavity.
+The issue with \eqref{eq:meml} is that it has been assumed each process affects the pulse continuously within the cavity.
 As highlighted by Figure \ref{fig:cavity}, this is a rather poor assumption.
-Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG, the pulse is only amplified within the Erbium-doped fibre, etc.
+Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the \gls{cfbg}, the pulse is only amplified within the Erbium-doped fibre, etc.
 Thus, perhaps a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
-Each of the blocks can then be composed together functionally to give the effect of one circuit around the cavity.
+Each of the blocks can then be composed together to give an iterative map for the effect of one circuit around the cavity.
 This yields an algebraic equation instead of a differential one.
@@
 Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator.
-This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{siegman}, which they then greatly added to the following year \cite{kuizenga1970a}.
+This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, siegman}.
 Kuizenga and Siegman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}.
-The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried to model passive mode-locking---mode-locking without the use of a modulator.
+The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passive mode-locking---mode-locking without the use of a modulator.
 In the absence of a modulator the nonlinearity becomes crucial to shaping the pulse.
 This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
-In each of these models the effect of each block is described by a Gaussian transfer function.
+In these models the effect of each block is described by a transfer function, for example
+\begin{align*}
+A_{\text{out}}(T) &= A_{\text{in}}(T) \exp \left( - \frac{\epsilon T^2}{2} \right) \textrm{e}^{i \phi_M - \alpha_M / 2}, \\
+\widehat{A_{\text{out}}}(\Omega) &= \widehat{A_{\text{in}}}(\Omega) \exp \left( \frac{i \beta_2 \Omega^2}{2} \right) \textrm{e}^{i \phi_D - \alpha_D / 2}
+\end{align*}
+for modulation and dispersion, respectively.
 These transfer functions are then multiplied together to give the overall effect.
+This is in contrast to the iterative map developed in Sections \ref{sec:comp}--\ref{sec:effects}.
 \\
 
-Despite these attempts, several short-comings exist.
+Despite the development of block style models, several short-comings exist.
 The clearest is that none of these models have contained every block---either the nonlinearity or the modulation have been omitted.
 In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function without the inclusion of all of the components.
-Another key drawback is that the functional operations of some of the components are somewhat phenomenological.
+Another key drawback is that the functional operations of some of the components used in other models are somewhat phenomenological.
 While these functions are chosen based on the observed output, they are not necessarily consistent with their underlying physics.
-Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation (SPM) of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
-This notion will be explained in greater detail in Chapter \ref{chap:nl}.
+Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the \acrlong{spm} of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
+This notion will be explored in greater detail in Chapter \ref{chap:nl}.
 \\

### 2019-07-12 Thesis/Thesis.tex
Finished corrections

@@
 \usepackage{amsthm}
+\usepackage{mathtools}
+\usepackage[acronym, nomain, automake]{glossaries}
 
@@
 \usetikzlibrary{arrows.meta}
+\usetikzlibrary{shapes.arrows, fadings}
 \usetikzlibrary{external}
 \tikzexternalize[prefix=Figures/]
+
+% Gradient
+\tikzfading[name=fade left, right color=transparent!0, left color=transparent!75]
 
@@
 
+%List of Acronyms
+\makeglossaries
+\newacronym{cfbg}{CFBG}{chirped fibre Bragg grating}
+\newacronym{fbg}{FBG}{fibre Bragg grating}
+\newacronym{gnlse}{GNLSE}{generalized nonlinear Schr\"odinger equation}
+\newacronym{nlse}{NLSE}{nonlinear Schr\"odinger equation}
+\newacronym{led}{LED}{light emitting diode}
+\newacronym{uv}{UV}{ultraviolet}
+\newacronym{edfa}{EDFA}{Erbium-doped fibre amplifiers}
+\newacronym{spm}{SPM}{self-phase modulation}
+\newacronym{ndyag}{Nd:YAG}{Neodymium-doped Yttrium Aluminium garnet}
+\newacronym{fwhm}{FWHM}{full width at half maximum}
+\newacronym{wkb}{WKB}{Wentzel--Kramers--Brillouin}
+
 \title{A New Method of Modelling Tuneable Lasers with Functional Composition}
@@
 A new nonlinear model is proposed for tuneable lasers.
-Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each component within the laser cavity.
+Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity.
 These transformations are then composed to give the overall effect of one trip around the cavity.
-The linear version of this model is solved analytically, and the nonlinear version numerically.
+We first examine the linearized version of the model which is solved analytically.
+Then the full nonlinear model is solved numerically.
 A consequence of the nonlinear nature of this model is that it is able to exhibit wave breaking which prior models could not.
@@
 }
+
+%Put list of acronyms here, and add entry for TOC
+\printglossary[type=acronym, title={List of Acronyms}]
+\addcontentsline{toc}{chapter}{\numberline{}List of Acronyms}
 

### 2019-07-12 Thesis/Appendices/Asymptotics.tex
Finished final read through.

@@
 \end{align}
-where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Figure \ref{fig:asympt} shows \eqref{eq:asymp}. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
+where $x = \sigma^2$, $\eps = s^4$, and $\eps \rightarrow 0$. Figure \ref{fig:asympt} shows \eqref{eq:asymp} graphically. Additionally, suppose $x$ can be expanded as a power series in $\eps$:
 \begin{align}
@@
 \end{align}
-The reason for this is because the equation is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root.
+The reason for this is because \eqref{eq:asymp2} is now singular---when $\eps=0$ the equation transforms from a quartic to a cubic, losing a root.
 As with before, we obtain dominant balance when the quartic term balances with the cubic term which occurs when $1 - 4 \xi = -3 \xi$, or $\xi = 1$.
@@
 so either $x_1 = 1$ or $x_1 = 2$.
-The next term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$ provided\footnote{In the case of $x_1 = 2$ we find $\beta = \frac{3}{2}$ which leads to complex roots.} $x_1 \ne 2$.
+The following term obtains dominant balance when the left hand side balances with the linear term of the right hand side, that is, when $\beta = 2$ provided\footnote{In the case of $x_1 = 2$ we find $\beta = \frac{3}{2}$ which leads to complex roots.} $x_1 \ne 2$.
 Now at $\bigO{\eps}$,
@@
 \end{align*}
-where again, the coefficients come from the binomial expansions. From this it is clear that
+where the coefficients come from the binomial expansions. From this it is clear that
 \begin{align*}
@@
 \end{align*}
-Knowing the values of $x_1$, and $x_2$ this is simply an arithmetical calculation yielding $x_3 = \frac{3}{8}$. Finally,
+Knowing the values of $x_1$ and $x_2$ this is simply an arithmetical calculation yielding $x_3 = \frac{3}{8}$. Finally,
 \begin{align*}

### 2019-07-12 Thesis/Appendices/Hermite.tex
Finished final read through.

@@
 \end{align*}
-Finally, we can rewrite the derivatives using central differences \cite{zwillinger} so that
+Finally, we can rewrite the derivatives using central differences \cite{zwillinger} so that our function can be expressed as
 \begin{align}
@@
 Furthermore, because \cite{calcaterra2, calcaterra} used backwards differences, the means of the Gaussians are all non-negative, whereas with central differences, our Gaussians' means are both positive and negative---this leads to smaller coefficients, and better numerical stability.
-Moreover, Figure \ref{fig:gaussmod} shows the Gaussian series for the modulation function in \cite{bohun, burgoyneemail}.
+Moreover, Figure \ref{fig:gaussmod} shows the Gaussian series for the modulation function
+\begin{align*}
+M(T) = \frac{1}{2} \left( 1 - \cos \left( \pi \textrm{e}^{-x^2} \right) \right),
+\end{align*}
+used in \cite{bohun, burgoyneemail}.

### 2019-07-12 Thesis/Conclusion/Conclusion.tex
Finished final read through.

@@
 For example, from our results it is clear that to fix a broken wave $b$ must be decreased, or $s$ increased.
-This could be achieved by reducing the length of the optical fibre between the gain fibre and the output coupler, or by increasing $\beta_2 L_D$ by adding a second \gls{cfbg} in series\footnote{See \eqref{eq:ndparam}.}.
+This could be achieved by reducing the length of the optical fibre between the gain fibre and the output coupler, or by increasing $\beta_2 L_D$ by adding a second \gls{cfbg} in series, respectively\footnote{See \eqref{eq:ndparam}.}.
 Additionally, one could decrease  the modulation time, $T_M$, to move through the parameter space along a ray outward from the origin.
-Although this would increase $b$, it also increases $s$ enough to move out of the unstable region.
+Although this would increase $b$, it also could increase $s$ enough to move out of the unstable region.
 \\

### 2019-07-12 Thesis/Intro/Introduction.tex
Finished final read through.

@@
 The energy is generally supplied by either an external light source, or an electric field.
-The amplifying medium typically consists of gases, such as Helium and Neon, or a crystal, such as \gls{ndyag} for a single frequency laser.
+The amplifying medium for a single frequency laser typically consists of gases, such as Helium and Neon, or a crystal, such as \gls{ndyag}.
 \\
@@
 \caption[Comparison of pumping, spontaneous emission, and stimulated emission.]{In pumping, incident photons are absorbed by electrons which are then excited into a much higher energy state (the electrons may also be excited by an electric field).
-The electrons quickly emits a low energy photon and transitions to an energy state that is still much more energetic than the original.
+The electrons quickly emit a low energy photon and transition down to an energy state that is still much more energetic than the original.
 In spontaneous emission, an electron in an excited state emits a photon and returns to the lower energy state.
@@
 The monochromatic nature is a result of how the light is generated; the frequency of the light emitted directly corresponds to the energy difference between the excited and ground states of the gain medium (as with \gls{led}s).
-Note that this means the frequency the laser operates at is fixed, and cannot be changed.
+Note that this means the operating frequency of the laser is fixed, and cannot be changed.
 Coherence is achieved in the laser cavity---the cavity is carefully designed so the light resonates with the length of the cavity.
@@
 Another class of lasers are optical fibre lasers.
-Optical fibre lasers operate by the same principles, however, instead of the light being perpetually reflected back and forth, the light travels in a circular fashion through an optical fibre---this is a so called ring laser.
+Optical fibre lasers operate by the same principles, however, instead of the light being perpetually reflected back and forth, the light travels in a circular fashion along an optical fibre---this is a so called ring laser.
 Additionally, instead of the gain medium consisting of a gas or crystal, it is a length of fibre doped with a rare-earth metal.
@@
 The first is with an acousto-optic modulator which utilizes the acousto-optic effect where the index of refraction of the optical fibre is varied by a sound wave \cite{hausbook, karim}.
-The second---and more common---method uses the electro-optic effect, where the index of refraction of the optical fibre is varied by a sound wave, and is called an electro-optic modulator.
+The second---and more common---method uses the electro-optic effect, where the index of refraction of the optical fibre is varied by an electric field, and is called an electro-optic modulator.
 This modulator works the same was as an acousto-optic modulator, the optical fibre inside the modulator responds to an applied electric field, modifying the index of refraction \cite{agrawal2002, goldstein, hausbook, karim}.
@@
 \end{figure}
-One of the fundamental features of a laser is coherence.
+Recall, one of the fundamental features of a laser is coherence.
 However, in the context of tuneable lasers it is perhaps less clear what is meant by coherence since the light is no longer monochromatic.

### 2019-07-12 Thesis/Model/Model.tex
Finished final read through.

@@
 \begin{align*}
-\pdiff{A}{z} = - \alpha A.
+\pdiff{A}{z} = - \alpha A,
 \end{align*}
-Combining these two effects gives a loss that takes the form
+and gives $\textrm{e}^{-\alpha L_T}A$, which by multiplying by the amount of the signal lost to the output coupler gives
 \begin{align*}
@@
 \end{align*}
-where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit.
+where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit as the effect of the losses\footnote{Depending on the experimental setup the loss may take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$.}.
 
@@
 \end{align*}
-The effect of dispersion is then by the map
+The effect of dispersion is then given by the map
 \begin{align*}
@@
 \begin{aligned}
-	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04\\
+	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04, \\
 	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& \qquad s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,
@@
 \end{equation}
-which characterize the behaviour of the laser. Notice that the modulation is characterized by $T_M$, and each other process has it's own independent non-dimensional parameter.
+which characterize the behaviour of the laser. Notice that the modulation is characterized by $T_M$, and each other process has its own independent non-dimensional parameter.
 
@@
 It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn}, dispersion will not alter the envelope.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
 \\
@@
 Moveover, the expansion provides more detail about the limits, as well has the rate of convergence.
-Lastly, the expansion allows for simplified expressions within their domains that are much less unwieldy than those found in the previous subsections.
+Lastly, the expansion allows for simplified expressions within their domains that are much less unwieldy than those found in the previous subsection.
 \\
@@
 
-We can now find the amplitude of the pulse as well now that the energy is know---as we have previously found the equilibrium shape.
+We can now find the amplitude of the pulse as well now that the energy is known---as we have previously found the equilibrium shape.
 Again, from \eqref{eq:gainde}, it must be that $E_* = \sqrt{\pi} P \sigma$, or,
@@
 This yielded the functional maps \eqref{eq:effects} for the components, with corresponding non-dimensional parameters \eqref{eq:ndparam}.
-With each of the operators defined, we proceeded to compose each process, in the order most representative of a tuneable laser, to give the effect of one complete circuit around the laser cavity.
+With all of the operators defined, we proceeded to compose each process, in the order most representative of a tuneable laser, to give the effect of one complete circuit around the laser cavity.
 \\

### 2019-07-12 Thesis/Nonlinear/Nonlinear.tex
Finished final read through.

@@
 In the case of the numerical solution, our initial conditions become somewhat important for two reasons.
-First, if the energy is too high initially the nonlinear effects are too strong leading to \acrlong{spm}.
+First, if the energy is too high initially the nonlinear effects will be too strong leading to \acrlong{spm}.
 Secondly, the initial waveform needs to be well behaved enough so that the Fourier transform is band limited.
@@
 
-In the first experiment the pulse is allowed to equilibrate for 40 loops of the circuit\footnote{The choice of 40 will be justified in the following section.}, we then compare the variance, chirp, and phase shift of the analytic and numerical solution.
+In the first experiment the pulse is allowed to equilibrate for 40 loops of the circuit\footnote{The choice of 40 will be justified in the following section.}, we then compare the variance, chirp, and phase shift of the analytic and numerical solutions.
 The results of this are shown in Figure \ref{fig:var}.
@@
 
-With the numerical solution yielding the expected results we are now ready to explore the rich structure, which the nonlinearity adds.
+With the numerical solution yielding the expected results we are now ready to explore the rich structure that the nonlinearity adds.
 
@@
 However, for $|T| > 1$ the chirp begins to saturate.
-This is consistent with experimental results \cite{chen, rothenberg, tomlinson}.
+This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
 \\
@@
 \input{./Figures/ROC}
-\caption{Rate of convergence as a function of number of iterations for various $s$ values, and $b = 0.5$. The error is given by \eqref{eq:error}.}
+\caption{Rate of convergence as a function of number of iterations for various $s$ values, with $b = 0.5$. The error is given by \eqref{eq:error}.}
 \label{fig:roc}
@@
 In the linearized case we chose to iterate 40 times since this is about double the number of iterations expected.
-Furthermore, in the nonlinear case we extend this number further to 100 in case the nonlinearity increases the number of iterations to converge.
+Furthermore, in the nonlinear case we extend this number further to 100 in case the nonlinearity increases the number of iterations required to converge.
 The energy of the pulse after 100 iterations is shown in Figure \ref{fig:energy}.
-In Figure \ref{fig:energyzoom} we generally find that the energy is a smooth surface that slowly decays as $s$, and $b$ increase.
+In Figure \ref{fig:energyzoom} we generally find that the energy is a smooth surface that slowly decays as $s$ and $b$ increase.
 In the upper left hand region of the plot this is clearly not the case.
@@
 The chirp has grown to be highly oscillatory and unstable.
-Once the pulse has reached a state such as this---the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
+Once the pulse has reached a state such as this, the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
 \\
@@
 However, there are two composite $\Delta$ values of interest.
-The first is $16$, since $16 = 2^4$ and it will pick up any periodic behaviour with orders of $2, 4, 8, 16$.
-Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible extracting orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
+The first is $16$, since $16 = 2^4$, as it will pick up any periodic behaviour with orders of $2, 4, 8, 16$.
+Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible we can extract orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
 \\
@@
 In this chapter we investigated how the nonlinear solution deviates from the linear solution by including the effects of the nonlinearity.
-We did this numerically; First we had to validate the code by comparing to the analytic result from Chapter \ref{chap:linear}.
-Once the code yielded the expected results for the linearized version, we incorporated on the nonlinearity.
+We did this numerically; first we had to validate the code by comparing to the analytic result from Chapter \ref{chap:linear}.
+Once the code yielded the expected results for the linearized version, we incorporated the nonlinearity.
 \\
@@
 Whereas, in the stable region the error took on values between $10^{-4}$ and $10^{-16}$.
-This is because the pulse reached a steady state with a periodicity greater than 1, this was highlighted by computing the composite error, \eqref{eq:deltaerror}, shown in Figure \ref{fig:errorcomp}.
+This is because the pulse reached a steady state with a periodicity greater than 1, which was highlighted by computing the composite error, \eqref{eq:deltaerror}, shown in Figure \ref{fig:errorcomp}.
 \\

### 2019-07-12 Thesis/Previous_Models/Previous.tex
Finished final read through.

@@
 \end{align}
-Despite being physically unrelated to quantum mechanics \eqref{eq:smallnlse} is called the \gls{nlse} because of it's functional similarity \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}.
+Despite being physically unrelated to quantum mechanics \eqref{eq:smallnlse} is called the \gls{nlse} because of its functional similarity \cite{agrawal2013, anderson, burgoyne2007, desurvire, ferreira, finot, rothenberg}.
 \\
@@
 \end{align}
-This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura1996, usechak} defined recursively as
+This can be solved using separation of variables and one finds the solutions are the Gaussian--Hermite polynomials \cite{burgoyne2014, hausbook, haus1975, haus1996, haus2000, kartner, tamura1996, usechak}, defined recursively as
 \begin{align}
@@
 This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
-In these models the effect of each block is described by a transfer function, for example
+In these models the effect of each block is described by a transfer function, for example:
 \begin{align*}
 A_{\text{out}}(T) &= A_{\text{in}}(T) \exp \left( - \frac{\epsilon T^2}{2} \right) \textrm{e}^{i \phi_M - \alpha_M / 2}, \\
-\widehat{A_{\text{out}}}(\Omega) &= \widehat{A_{\text{in}}}(\Omega) \exp \left( \frac{i \beta_2 \Omega^2}{2} \right) \textrm{e}^{i \phi_D - \alpha_D / 2}
+\widehat{A_{\text{out}}}(\Omega) &= \widehat{A_{\text{in}}}(\Omega) \exp \left( \frac{i \beta_2 \Omega^2}{2} \right) \textrm{e}^{i \phi_D - \alpha_D / 2},
 \end{align*}

### 2019-07-12 Lasers.py

@@ -17,6 +17,7 @@ Function definitions and initialization
 import numpy as np
 import scipy.special.lambertw as W
 import matplotlib.pyplot as plt
+import time
 from scipy.optimize import curve_fit
 
 def func(x, a, b):
@@ -43,7 +44,7 @@ def Disp(A, T, s = 0.1):
 	F = F * (np.abs(F) > 10**-4) # Numerical stability
 	dw = np.pi / T[-1]
 	w = np.fft.fftfreq(len(A)) * len(A) * dw
-	return np.fft.ifft(F * np.exp(1j * w**2 * s**2)))
+	return np.fft.ifft(F * np.exp(1j * w**2 * s**2))
 
 # 1 round trip
 def Loop(A, T, dx, s, b, switch = False):
@@ -58,7 +59,7 @@ def Loop(A, T, dx, s, b, switch = False):
 	A = Fibre(A, b)
 	return A
 
-N = 250 # Number of loops of the circuit
+N = 25 # Number of loops of the circuit
 p = 2**12 # Number of points in the discretization
 width = 64 # Size of window
 E0 = 0.1 # Initial energy
@@ -72,7 +73,7 @@ E = np.zeros(N)
 data = np.zeros((2 * N, p))
 A = A0
 
-part = 4 # Select which part of the code to run
+part = 6 # Select which part of the code to run
 
 if part == 2:
 	###############
@@ -86,6 +87,8 @@ if part == 2:
 	ax = fig.add_subplot(111)
 	line1, = ax.plot(T, np.real(A), 'r-', label = 'Real')
 	line2, = ax.plot(T, np.imag(A), 'b-', label = 'Imaginary')
+
+	dw = np.pi / T[-1]
 	line3, = ax.plot(T, np.abs(A), 'g-', label = 'Magnitude')
 
 	fig.canvas.draw()
@@ -93,7 +96,7 @@ if part == 2:
 
 	plt.legend()
 	plt.xlim(-2, 2)
-	plt.ylim(-1, 1)
+	plt.ylim(-4, 4)
 
 	# N round trips of the laser
 	for i in range(N):
@@ -106,13 +109,18 @@ if part == 2:
 		#time.sleep(2)
 		print i
 
-		A = Loop(A, T, dx, 0.41, 2)
+		A = Loop(A, T, dx, 0.15, 0.5)
[…]

### 2019-07-13 Thesis/Model/Model.tex
Fixed typo

@@
 \end{align}
-and since dispersion acts in the frequency domain it is convenient to take the Fourier transform\footnote{We use $\displaystyle \FT{f} = (2 \pi)^{1/2} \int_\mathbb{R} f(x) \textrm{e}^{i \omega x} \df x$ as the definition of the Fourier transform.} of \eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
+and since dispersion acts in the frequency domain it is convenient to take the Fourier transform\footnote{We use $\displaystyle \FT{f} = (2 \pi)^{-1/2} \int_\mathbb{R} f(x) \textrm{e}^{i \omega x} \df x$ as the definition of the Fourier transform.} of \eqref{eq:dispde} \cite{debnath, gradshteyn}, giving
 \begin{align*}

### 2019-08-29 Thesis/Model/Model.tex
Updated for binding

@@
 In this chapter we shall derive our new model and solve it analytically in the linear case.
-To accomplish this we shall use the ideas of the previous functional models \cite{cutler, siegman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
+To accomplish this we shall use the ideas presented in the previous chapter of the prior functional models \cite{cutler, siegman, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, burgoyne2014}.
 To alleviate some of the pitfalls mentioned in the previous chapter, we shall include all five processes involved in the modification of the pulse within the laser cavity (gain, nonlinearity, loss, dispersion, and modulation).
 In addition to this, the functional operations associated with each component will be derived from \eqref{eq:nlse}, with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.
-\\
 
@@
 \label{sec:comp}
-We shall begin our analysis with the derivation of the functional operators for the five components. \\
+We shall begin our analysis with the derivation of the functional operators for the five components.
 
@@
 Despite assuming a Gaussian modulation, the solution presented in Section \ref{sec:linear} can be generalized to any modulation function in $L^2(\mathbb{R})$ since Gaussians in fact span $L^2(\mathbb{R})$ as shown in Appendix \ref{chap:gauss}.
-\\
 
@@
 \label{sec:linear}
-In reality the nonlinearity parameter, $b$, is of order unity by \eqref{eq:ndparam}, but we shall start our investigation with the simpler case of $b = 0$---which shall be referred to as the linear model.
-In this case, a solution can be found analytically.
-It is expected the solution will take the form of a Gaussian.
-There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
-\\
-
 \begin{figure}[tbp]
@@
 \end{figure}
+In reality the nonlinearity parameter, $b$, is of order unity by \eqref{eq:ndparam}, but we shall start our investigation with the simpler case of $b = 0$---which shall be referred to as the linear model.
+In this case, a solution can be found analytically.
+It is expected the solution will take the form of a Gaussian.
+There are a few reasons for this; the solution to the previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} (see Section \ref{chap:meml}), the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+\\
 
@@
 \end{subequations}
-
+\vspace{-5mm}
 \subsection{Spread of the Pulse Due to Dispersion}
@@
 \subsection{Asymptotic Expansion of the Variance}
-\begin{figure}[tbp]
-\centering
-\input{./Figures/Asympt}
-\caption{Plot of \eqref{eq:asymp} and \eqref{eq:asymp2} to highlight the structure.}
-\label{fig:asympt}
-\end{figure}
 While \eqref{eq:equilvar} is useful, so too is the asymptotic behaviour.
@@
 
-With the linear model fully solved, we shall now turn our attention to the rich structure added by the full nonlinear model. \\
+With the linear model fully solved, we shall now turn our attention to the rich structure added by the full nonlinear model.

### 2019-08-29 Thesis/Nonlinear/Nonlinear.tex
Updated for binding

@@
 This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
-\\
 
@@
 These features are further highlighted in Figure \ref{fig:cartoon} by disregarding the energy and only examining whether the pulse is invariant after additional iterations.
-\\
 
@@
 \glsreset{spm}
-
 The noise in the energy exhibited for moderate to large values of $b$, and small values of $s$ is a phenomenon called \emph{wave breaking} \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}.
@@
 Notice that the difference between Figure \ref{fig:nlstable} and Figure \ref{fig:break} is a difference in $b$ of $0.05$---just enough to cross the boundary---this difference could be attributed to adding a few centimetres more of fibre between the gain and output coupler.
+\\
+
 The left figures show the pulse after 11 trips around the cavity; in the Fourier transform it is clear that the contributions from higher frequencies has increased.
@@
 Once the pulse has reached a state such as this, the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
-\\
 
@@
 Additionally, there appears to be no periodicity of the envelope within the wave breaking region, further supporting the claim that the pulse here is completely unstable.
-\\
 

### 2019-11-04 Papers/AMMCS_Proceedings/Cavity.tex
Added AMMCS paper

--- 2019-02-14 Thesis/Figures/Cavity.tex
@@
-% !TeX root = ../Thesis.tex
+% !TeX root = ./Tuneable_Lasers.tex
 
@@
 % Two laser loops
-\draw [rounded corners=4mm] (0,0) rectangle ++(9,4);
+\draw [rounded corners=4mm] (0,0) rectangle ++(6,4);
 \draw [rounded corners=4mm] (0,0) rectangle ++(-1.5,4);
@@
 % Modulator and pump
-\filldraw[fill=white, draw=black] (3.5,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
+\filldraw[fill=white, draw=black] (2,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
 \filldraw[fill=white, draw=black] (-2.1,1.5) rectangle ++(1.2,1) node [midway] {Pump};
@@
 % Coupler and output
-\draw[-stealth] (4.5,4) -- (4.5,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
-\draw[densely dashdotted] (4,3.5) -- (5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};
+\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
+\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};
 
 % Circulators
-\filldraw[fill=white, draw=black] (9,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
-\draw[->,>=stealth] (9,2.325) arc (90:360:0.325cm);
+\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
+\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);
 
@@
 
+% Arrows
+\draw [->,>=stealth,domain=20:70] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+\draw [->,>=stealth,domain=110:160] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+\draw [->,>=stealth,domain=110:160] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
+\draw [->,>=stealth,domain=200:250] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
+\draw [->,>=stealth,domain=200:250] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+\draw [->,>=stealth,domain=290:340] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+
 % Grating
-\draw (8.5,2) -- (6.5,2) node [pos=0.5,anchor=south,yshift=0.25cm,xshift=-0.15cm] {CFBG};
+\draw (5.5,2) -- (3.5,2) node [pos=0.5,anchor=south,yshift=0.25cm,xshift=-0.15cm] {CFBG};
 \foreach \i in {0,...,13}
-  \draw (6.5 + \i*\i/100,1.75) -- (6.5 + \i*\i/100,2.25);
+  \draw (3.5 + \i*\i/100,1.75) -- (3.5 + \i*\i/100,2.25);
 

### 2019-11-04 Papers/AMMCS_Proceedings/Tuneable_Lasers.tex
Added AMMCS paper

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{amsmath}
\usepackage{amsfonts}

\usepackage{tikz}
\usetikzlibrary{patterns,decorations.pathreplacing}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{shapes.arrows, fadings}

\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}

\providecommand{\df}{\textrm{d}}
\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
\newcommand{\Es}{E_{\textrm{sat}}}
\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
\newcommand{\Her}[2]{\widetilde{H}_{#1} \left( #2 \right)}
%\newcommand{\eps}{\varepsilon}
%\newcommand{\rect}[1]{\textrm{rect}\left( #1 \right)}

\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
%\DeclareMathOperator{\sgn}{sgn}
%\DeclareMathOperator{\sech}{sech}

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

\bibliographystyle{spmpsci}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title*{A New Method of Modelling Tuneable Lasers with Functional Composition}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{B. Metherall \and C. S. Bohun}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{B. Metherall \at University of Oxford,  Oxford, UK, \email{brady.metherall@maths.ox.ac.uk}
\and C. S. Bohun \at Ontario Tech University, 2000 Simcoe St N, Oshawa, ON, \email{sean.bohun@uoit.ca}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{
A new nonlinear model is proposed for tuneable lasers. Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity. These transformations are then composed to give the overall effect of one trip around the cavity. We examine the full nonlinear model which is solved numerically. A consequence of the nonlinear nature of this model is that it is able to exhibit wave breaking which prior models could not. We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
}

\abstract{
A new nonlinear model is proposed for tuneable lasers. Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity. These transformations are then composed to give the overall effect of one trip around the cavity.
}

\section{Introduction}
\label{sec:intro}
A tuneable laser has the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}. Tuneable lasers simultaneously lase at all frequencies within this bandwidth. This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}. A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}. In contrast to a standard laser, a tuneable laser contains two additional components, namely, a chirped fibre Bragg grating (CFBG), and a modulator.

\begin{figure}[tbp]
\centering
\input{Cavity}
\caption{Typical cavity of a fibre based tuneable laser. The laser pulses travel clockwise around each loop.}
\label{fig:cavity}
\end{figure}
A CFBG is a length of optical fibre where the refractive index oscillates along its length \cite{ferreira}, and therefore, can act as a reflective filter \cite{agrawal2002, alazzawi, ferreira, starodoumov}. Due to the oscillatory nature, light with the corresponding wavelength will be reflected when the Bragg condition is satisfied \cite{agrawal2002, alazzawi, becker, ferreira, silfvast, starodoumov}. The spacial variation of the refractive index effectively creates a spacial dependence on the Bragg condition, causing most wavelengths to be reflected by a CFBG, but with each wavelength satisfying the Bragg condition at a different spacial location\footnote{Note that a monotonic chirping ensures that the spacial dependence of the Bragg condition is continuous with respect to the frequency.}. A consequence of this is that a time delay is created between wavelengths---this causes the pulse to disperse and broaden.

The modulator serves the purpose of reshaping the pulse. Without it, the pulse will repeatedly widen due to the CFBG---the modulator ensures the pulse is band limited by altering the envelope.

\section{Modelling Efforts}
\label{sec:modelling}
The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE)\footnote{The NLSE can be derived from the nonlinear wave equation for electric fields; this derivation is presented in detail in \cite{agrawal2013, ferreira}.},
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A.
\label{eq:smallnlse}
\end{align}
Here $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity. In practice, \eqref{eq:smallnlse} lacks a few key terms, thus, it is often generalized by adding amplification, loss, and occasionally higher order terms. This gives the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
\begin{align}
\label{eq:nlse}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
\end{align}
where $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}$ is the loss due to scattering and absorption.

The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers we typically also add a modulation term. This yields the master equation of mode-locking \cite{haus1975, hausbook, haus1986, haus1992, haus2000, kartner, tamura1996, usechak},
\begin{align}
\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T),
\label{eq:meml}
\end{align}
where $M(T)$ is the modulation function. The solutions of three simplifications of \eqref{eq:meml} have been investigated:
\begin{itemize}
\item Omitting both modulation and nonlinearity \cite{haus1975, haus1986, haus1992}.
\item Omitting only modulation \cite{haus1991, usechak}.
\item Omitting only nonlinearity  \cite{burgoyne2014, haus1975, hausbook, haus1996, haus2000, kartner, tamura1996, usechak}.
\end{itemize}
For a more comprehensive history see \cite{haus2000}.

\subsection{Discrete Models}
While the derivation of \eqref{eq:meml} is correct mathematically, it is not representative of what happens within the laser cavity. The issue with \eqref{eq:meml} is that it has been assumed each process affects the pulse continuously within the cavity. As highlighted by Figure \ref{fig:cavity}, this is a rather poor assumption. Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc. Thus, perhaps a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity. Each of the blocks can then be functionally composed together to give an iterative map for the effect of one circuit around the cavity. This transforms the differential equation into an algebraic equation.

Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator. This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, siegman}. Kuizenga and Siegman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}. The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passively mode-locked lasers. This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers. In these models the effect of each block is described by a transfer function.

Despite the development of these block style models, several short-comings exist. The clearest is that none of these models have contained every block---either the nonlinearity or the modulation have been omitted. In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function correctly without the inclusion of all of the components. Another key drawback is that the functional operations of some of the components used in their models are phenomenological. While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics. Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.

\section{A New Model}
\label{sec:newmodel}
Using the ideas presented in the previous section of the prior functional models \cite{burgoyne2014, cutler, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, siegman} we shall derive a new model from \eqref{eq:nlse}---with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.

\subsection{Components}
We shall determine the effect each component has on the pulse by solving \eqref{eq:nlse} while only considering the dominant term within each section of the cavity.

\subsubsection{Gain}
Within the Er-doped gain fibre, the gain term is dominant, and equation \eqref{eq:nlse} reduces to
\begin{align}
\label{eq:gainde}
\pdiff{A}{z} &= \frac{1}{2} g(A) A,
\end{align}
where $g(A)$ takes the form \cite{bohun, burgoyne2014, haus1975, hausbook, haus1992, haus2000, haus1991, kartner, peng, shtyrina, silfvast, usechak, yarutkina}
\begin{align}
\label{eq:energy}
	g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
\end{align}
where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate. Without much difficulty this differential equation can be solved, and the effect on an incident pulse is
\begin{align}
G(A;E) &= \left(\frac{E_{\textrm{out}}}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
\end{align}
where $L_g$ is the length of the gain fibre.

\subsubsection{Nonlinearity}
The nonlinearity of the fibre arises from the parameter $\gamma$; in regions where this effect is dominant expression~\eqref{eq:nlse} becomes
\begin{align}
\label{eq:fibrediff}
	\pdiff{A}{z} - i \gamma |A|^2 A = 0.
\end{align}
Using a similar method as with the gain, the effect of the nonlinearity can be shown to be
\begin{align}
F(A) &= A \textrm{e}^{i \gamma |A|^2 L_f},
\end{align}
where $L_f$ is the length of fibre.

\subsubsection{Loss}
Expression \eqref{eq:nlse} leads to exponential decay due to the scattering and absorption of the fibre. However, a majority of the signal is removed from the cavity by the optical coupler. Combining these two effects yields
\begin{align}
L(A) &= (1 - R) \textrm{e}^{- \alpha L_T}A,
\end{align}
where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit as the effect of the losses\footnote{Depending on the layout of the laser cavity the loss may take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$ instead.}.

\subsubsection{Dispersion}
Considering only the dispersive terms of \eqref{eq:nlse}, one obtains
\begin{align}
\label{eq:dispde}
	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T}.
\end{align}
The effect of dispersion is then given by the map
\begin{align}
D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}},
\end{align}
where $L_D$ is the length of the dispersive medium, and $\mathcal{F}$ denotes the Fourier transform.

\subsubsection{Modulation}
In this model, the modulation is considered to be applied externally in which ever way the operator sees fit. For simplicity the representation is taken as the Gaussian
\begin{align}
M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
\end{align}
where $T_M$ is the characteristic width of the modulation.

\subsection{Non-Dimensionalization}
The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude. Nominal values for tuneable lasers are shown in Table \ref{tab:values}. Knowing experimental durations and energies, the table suggests the convenient scalings:
\begin{align}
	T &= T_M \widetilde{T},& E &= \Es \widetilde{E},& A &= \left( \frac{\Es}{T_M} \right)^{1/2} \widetilde{A}.
\end{align}
Revisiting each process map shows each process has a characteristic non-dimensional parameter. The new mappings---after dropping the tildes---are
\begin{equation}
\begin{aligned}
G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \textrm{e}^{i b |A|^2}, & L(A) &= h A, \\
D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, & M(A) &= \textrm{e}^{-T^2 / 2} A,
\label{eq:effects}
\end{aligned}
\end{equation}
with the four dimensionless parameters, as defined by the values in Table \ref{tab:values},
\begin{equation}
\begin{aligned}
	a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04, \\
	b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& \qquad s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,
\label{eq:ndparam}
\end{aligned}
\end{equation}
which characterize the behaviour of the laser. Notice that the modulation is only characterized by $T_M$, and each other process has its own independent non-dimensional parameter.

\begin{table}[tbp]
\caption{Range of variation of various parameters.}
\label{tab:values}
\centering
\begin{tabular}{lcll}
\hline\noalign{\smallskip}
Parameter & Symbol & Value & Sources \\
\hline\noalign{\smallskip}
Absorption of Fibre$^a$& $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, tomlinson, usechak, yarutkina} \\
Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot, usechak, yarutkina} \\
Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng, tamura1996} \\
Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, tamura1993, yarutkina} \\
Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyneemail, burgoyne2014} \\
Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li, peng,  tamura1993, tamura1996, yamashita} \\
Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular} \\
$^a$  Fibre loss is typically reported as $\sim0.5$ dB/km.
\end{table}

\subsection{Combining the Effects of Each Block of the Model}
\label{sec:effects}
In this model the pulse is iteratively passed through each process, the order of which must now be considered. We are most interested in the output of the laser cavity, and so we shall start with the loss component. Next the pulse is passed though the CFBG, as well as the modulator. Finally, the pulse travels through the gain fibre to be amplified, and then we consider the effect of the nonlinearity since this is the region where the power is maximal. Note that in general the functional operators of the components do not commute, and therefore the order of the components is indeed important---in contrast to the previous models. This is especially the case of dispersion as realized through the Fourier transform. Functionally this can be denoted as
\begin{align}
\mathcal{L}(A) = F(G(M(D(L(A))))),
\end{align}
where $\mathcal{L}$ denotes one loop of the laser. The pulse after one complete circuit of the laser cavity is then passed back in to restart the process. A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase. That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.

\section{Conclusion}
Within this paper we developed a new nonlinear model for tuneable lasers. In order to better represent the underlying physics within the laser cavity the nonlinear Schr\"{o}dinger equation was reduced to simpler differential equations for each component of the laser. This led to a functional map that defines the effect of each component on a particular input pulse. These processes were then composed together to give an iterative mapping of the whole laser cavity. In a future publication we shall show the results obtained by this iterative mapping as well as discuss the dynamics exhibited by this model---including wave-breaking---to predict the conditions under which the pulse is stable and sustainable.

\bibliography{Ref}

\end{document}

### 2019-11-12 Papers/Journal/Tuneable_Lasers.tex
Started writing journal article

--- 2019-11-04 Papers/AMMCS_Proceedings/Tuneable_Lasers.tex
@@
-%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% sample root file for your "contribution" to a contributed volume
-%
-% Use this file as a template for your own input.
-%
-%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass[10pt,twocolumn,a4paper]{article}
 
-% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[graybox]{svmult}
+\usepackage{amsfonts}
+\usepackage{amsmath}
+\usepackage{geometry}
+\usepackage{xcolor,graphicx}
+%\usepackage[subfolder,cleanup]{gnuplottex}
+%\usepackage{amsthm}
+%\usepackage{enumitem}
+%\usepackage{wrapfig}
+%\usepackage{subcaption}
+%\usepackage{hyperref}
+\usepackage{tikz}
 
-% choose options for [] as required from the list
-% in the Reference Guide
-
-\usepackage{mathptmx}       % selects Times Roman as basic font
-\usepackage{helvet}         % selects Helvetica as sans-serif font
-\usepackage{courier}        % selects Courier as typewriter font
-\usepackage{type1cm}        % activate if the above 3 fonts are
-                            % not available on your system
-%
-\usepackage{makeidx}         % allows index generation
-\usepackage{graphicx}        % standard LaTeX graphics tool
-                             % when including figure files
-\usepackage{multicol}        % used for the two-column index
-\usepackage[bottom]{footmisc}% places footnotes at page bottom
-
-\usepackage{amsmath}
-\usepackage{amsfonts}
-
-\usepackage{tikz}
 \usetikzlibrary{patterns,decorations.pathreplacing}
@@
 \providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
-%\DeclareMathOperator{\sgn}{sgn}
-%\DeclareMathOperator{\sech}{sech}
 
-% see the list of further useful packages
-% in the Reference Guide
+\newgeometry{margin=1.25cm}
 
-\makeindex             % used for the subject index
-                       % please use the style svind.ist with
-                       % your makeindex program
+\bibliographystyle{ieeetr}
 
-\bibliographystyle{spmpsci}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\title{A New Method of Modelling Tuneable Lasers with Functional Composition}
+\author{B. Metherall \and C. S. Bohun}
 
@@
 
-\title*{A New Method of Modelling Tuneable Lasers with Functional Composition}
-% Use \titlerunning{Short Title} for an abbreviated version of
-% your contribution title if the original one is too long
-\author{B. Metherall \and C. S. Bohun}
-% Use \authorrunning{Short Title} for an abbreviated version of
-% your contribution title if the original one is too long
-\institute{B. Metherall \at University of Oxford,  Oxford, UK, \email{brady.metherall@maths.ox.ac.uk}
-\and C. S. Bohun \at Ontario Tech University, 2000 Simcoe St N, Oshawa, ON, \email{sean.bohun@uoit.ca}}
-%
-% Use the package "url.sty" to avoid
-% problems with special characters
-% used in your e-mail or web address
-%
+\twocolumn[
+\begin{@twocolumnfalse}
 \maketitle
-
-\abstract*{
+\begin{abstract}
 A new nonlinear model is proposed for tuneable lasers.
@@
 These transformations are then composed to give the overall effect of one trip around the cavity.
-We examine the full nonlinear model which is solved numerically.
-A consequence of the nonlinear nature of this model is that it is able to exhibit wave breaking which prior models could not.
-We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
-}
-
-\abstract{
-A new nonlinear model is proposed for tuneable lasers.
-Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity.
-These transformations are then composed to give the overall effect of one trip around the cavity.
-}
+\end{abstract}
+\end{@twocolumnfalse}
+]
 
@@
 \begin{align}
-G(A;E) &= \left(\frac{E_{\textrm{out}}}{E}\right)^{1/2}A = \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
+G(A;E) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
 \end{align}
@@
 \begin{aligned}
-G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \textrm{e}^{i b |A|^2}, & L(A) &= h A, \\
-D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, & M(A) &= \textrm{e}^{-T^2 / 2} A,
+G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \textrm{e}^{i b |A|^2} \\
+D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, & L(A) &= h A, \\
+M(A) &= \textrm{e}^{-T^2 / 2} A,
 \label{eq:effects}
@@
 
-\begin{table}[tbp]
-\caption{Range of variation of various parameters.}
-\label{tab:values}
+\begin{table*}[tbp]
 \centering
@@
 \hline\noalign{\smallskip}
-Absorption of Fibre$^a$& $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, tomlinson, usechak, yarutkina} \\
+Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, tomlinson, usechak, yarutkina} \\
 Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
@@
 Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular} \\
-$^a$  Fibre loss is typically reported as $\sim0.5$ dB/km.
-\end{table}
+\noalign{\smallskip}\hline
+\end{tabular}
+\caption{Range of variation of various parameters.}
+\label{tab:values}
+\end{table*}
 
@@
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
+\\
+
+\section{}
+In the case $b = 0$ a solution can be found analytically.
+We would expect the solution will have the form of a Gaussian.
+There are a few reasons for this; the solution to previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985}, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+
+To compute $\mathcal{L}(A)$, consider the pulse
+\begin{align}
+A = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \textrm{e}^{i \phi_0},
+\label{eq:A0}
+\end{align}
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
+This form is chosen because it resembles the envelope and linear chirping found by experiment ***cite.
+Having neglected the effect of the nonlinearity $\mathcal{L}(A)$ can be found analytically from the process mappings \eqref{eq:effects}.
+By assuming the pulse in \eqref{eq:A0} is in equilibrium, we find that the variance must satisfy
+\begin{align}
+\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0.
+\label{eq:var}
+\end{align}
+As this expression is a quartic in $\sigma^2$ it too has an analytic solution, namely,
+\begin{equation}
+\begin{split}
+\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} & \\
+- s^4 - s^2 & \sqrt{4 + s^4}.
+\label{eq:equilvar}
+\end{split}
+\end{equation}
+However, by asymptotically expanding \eqref{eq:var} we find the useful relations
+\begin{align}
+\sigma^2 &\sim
+\begin{cases}
+2s(1 - s) + \bigO{s^3} & s \rightarrow 0 \\
+1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty
+\end{cases}.
+\end{align}
+Additionally, from the variance we can determine the behaviour of the chirp to be
+\begin{align}
+C &\sim
+\begin{cases}
+1 - s + \frac{1}{2}s^2 + \bigO{s^3} & s \rightarrow 0 \\
+\frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}} & s \rightarrow \infty
+\end{cases}.
+\end{align}
+
+\begin{align}
+E = \frac{h^2 \zeta^2}{1 - h^2 \zeta^2} \log \left( a h^2 \zeta^2 \right). \\
+\end{align}
+
+\begin{align}
+P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma}.
+\label{eq:equilpower}
+\end{align}
+
+\section{}
+We shall now consider the nonlinear case---when $b > 0$. In this case it becomes impossible to obtain an analytic result. Recall from \eqref{eq:fibre} that the nonlinearity takes the form
+\begin{align*}
+F(A) &= A \textrm{e}^{i b |A|^2}.
+\end{align*}
+This is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone the transformation due to the nonlinearity is futile.
+Instead we must resort to a numerical solution.
+
+With the inclusion of the nonlinearity we generally find a similar solution to the linear case.
+An example of this is shown in Figure \ref{fig:nlstable}.
+The envelope of the pulse is unsurprisingly Gaussian-esque, however, it is \emph{not} precisely Gaussian and more closely resembles a generalized Gaussian\footnote{A generalized Gaussian has the form $\exp \left(-t^\alpha \right)$, with $\alpha > 2$.}.
+The fact that the pulse envelope is not Gaussian is further emphasized while examining the Fourier transform of the pulse.
+If the pulse were a Gaussian, we would expect the Fourier transform to also be a Gaussian \cite{debnath, gradshteyn}.
+Instead, the magnitude of the Fourier transform has a unique weakly bi-modal shape.
+This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---a key observation in the coming subsections.
+Finally, we shall examine the derivative of the phase---essentially the chirp.
+Recall in Chapter \ref{chap:linear} the chirp was defined as coefficient of $-\frac{1}{2}iT^2$ in the exponential, and by taking the negative of the derivative we would expect a linear function with a slope equal to the chirp.
+In the nonlinear case, we recover this linear response for moderate values of $T$.
+However, for $|T| > 1$ the chirp begins to saturate.
+This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
+
+The noise in the energy exhibited for moderate to large values of $b$, and small values of $s$ is a phenomenon called \emph{wave breaking} \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}.
+Wave breaking is not limited to just optics; wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
+Wave breaking occurs because the pulse begins to interfere with itself in a way called SPM \cite{agrawal2002, agrawal2013, becker}.
+SPM occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
+This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson}, as we saw in Figure \ref{fig:nlstable}.
+These high frequencies compound with each trip around the cavity becoming parasitic very quickly---Figure \ref{fig:break} highlights this.
+Notice that the difference between Figure \ref{fig:nlstable} and Figure \ref{fig:break} is a difference in $b$ of $0.05$---just enough to cross the boundary---this difference could be attributed to adding a few centimetres more of fibre between the gain and output coupler.
+\\
+
+The left figures show the pulse after 11 trips around the cavity; in the Fourier transform it is clear that the contributions from higher frequencies has increased.
+We obtain comparable results as in the experiments \cite{anderson, rothenberg}.
+Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is again in agreement with the experiments \cite{anderson, rothenberg}.
+The parasitic nature of the high frequency contributions is evident by examining the right figures.
+After five additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
+Moreover, the Fourier transform has no clear structure and has essentially become noise.
+The chirp has grown to be highly oscillatory and unstable.
+Once the pulse has reached a state such as this, the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
+
+To obtain a better understanding of how the pulse either converges to equilibrium, or diverges to wave breaking, we shall examine the difference between the envelopes of consecutive iterations.
+More precisely, we compute the error by
+\begin{align}
+\textrm{E} = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
+\label{eq:error}
+\end{align}
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{12}$).
+Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested in the phase shift between iterations.
+A plot of the error can be found in Figure \ref{fig:error}, with $i = 100$.
+The standard method would be to iterate until a fixed tolerance is reached, however, there are some reasons that make a fixed number of iterations preferable---as long as a sufficient number is chosen.
+The main reason is that this allows us to observe a richer structure than simply whether or not the tolerance had been reached by some maximum number of iterations.
+Additionally, incorrectly choosing the critical tolerance could easily lead to erroneous categorizations at points.
+As we saw in Figure \ref{fig:roc} some values of the parameters lead to a steady, periodic state, but with an error of $\bigO{10^{-6}}$, and so, had we set the tolerance to $10^{-8}$ these points would have been labeled as unsteady.
+\\
+
+Unsurprisingly, the error is largest in the region where the wave breaks.
+As mentioned in the previous subsection, the pulse does not reach a stable state in this region.
+As a consequence the envelope varies drastically, which leads to this large error.
+Conversely, the region where the energy appeared to be stable still has a non-zero error.
+The cause of this discrepancy is because some equilibrium states have a periodicity greater than $1$, thus, we redefine \eqref{eq:error} to be instead
+\begin{align}
+\textrm{E}_\Delta = \frac{\| |A_i| - |A_{i-\Delta}| \|_2}{\| A_{i-\Delta} \|_2},
+\label{eq:deltaerror}
+\end{align}
+to pick up equilibrium states with period $\Delta$, again with $i = 100$.
+Figure \ref{fig:deltaerror} shows the error for an assortment of $\Delta$ values.
+There are several key observations to make, first, for $\Delta = 2$ the kidney-shaped blob in the lower right corner has vanished, thus, this entire region has a periodicity of $2$.
+Second, for $\Delta = 3$ in the upper right corner a negative triangular-shaped structure emerges.
+Lastly, $\Delta \in \left\{ 5, 7, 11, 13 \right\}$ may not seem to extract any higher order periods, however, there are in fact very small striations in the lower left.
+We typically chose $\Delta$ values to be prime since they are the building blocks for composite numbers.
+However, there are two composite $\Delta$ values of interest.
+The first is $16$, since $16 = 2^4$, as it will pick up any periodic behaviour with orders of $2, 4, 8, 16$.
+Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible we can extract orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
+\\
+
+The last item we wish to consider is the order in which the components are placed.
+In Section \ref{sec:effects} a brief description for the choice of the order was given.
+We start with the loss component since this coincides with the output; the fibre nonlinearity follows the gain since this is where it has the largest impact; and the loss follows the nonlinearity in an attempt to mitigate its effect.
+Therefore, the loss is first, and the gain followed by the nonlinearity are last---leaving dispersion and modulation in the middle.
+We chose to put the dispersion block ahead of the modulator.
+However, there was no real reason behind this---modulation before dispersion is equally as valid---and in this subsection we explore the effect of modulating the pulse before it passes through the CFBG.
+\\
+
+The result of this switch is shown in Figure \ref{fig:switch}.
+As a whole, unsurprisingly, we find the same behaviour and structure, however, there are some intriguing differences.
+Perhaps the most interesting is the small island of instability in Figure \ref{fig:switchzoom} at around $s = 0.075$, $b = 1.1$ which was not present in the other ordering.
+Within this island the wave is unstable and breaks, but, curiously there is a small gap between this island and the main unstable region.
+We find more distinctions when considering the larger area in Figure \ref{fig:switchbig}.
+Again, the structure and periodic nature of the boundary is similar to before, however, this boundary has shifted rightwards to a larger $s$ value.
+Additionally, within the unstable region the density of the contour lines is much greater---suggesting it is in some sense more chaotic and random than with the components in their original permutation.
+The final main difference between the two orderings, is that in this case the energy contours are no longer monotonic functions of $s$.
+Instead we find a parabolic shape on the top contour, and two lobes on the second contour.
+\\
 

### 2019-11-13 Papers/Journal/Tuneable_Lasers.tex
Made 3d plot

@@
 \usepackage{xcolor,graphicx}
-%\usepackage[subfolder,cleanup]{gnuplottex}
+\usepackage[subfolder,cleanup]{gnuplottex}
 %\usepackage{amsthm}
@@
 
+\begin{figure*}
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 6in,3.7in lw 3}]
+load '/home/brady/Templates/YGB.p'
+#set format x '%.1f'
+#set format y '%.1f'
+set format z '%.1f'
+set format cb '%.1f'
+set grid
+set yl '$T$'
+set zl '$|A|$'
+set cbtics 0.2
+set ztics 0.2
+
+set yr [-2.5:2.5]
+
+set xtics ('Loss' 2, 'Disp.' 6, 'Mod.' 10, 'Gain' 14)
+
+set xtics center offset 0,-0.5
+
+set xyplane 0
+
+set view 45,325,1.25
+set pm3d
+set pm3d interpolate 5,5
+
+#set contour surface
+unset cl
+unset colorbox
+
+sp '../../Evolution.dat' u 2:1:3 w l lw 0.3 lc 8 not
+\end{gnuplot}
+\caption{}
+\label{fig:}
+\end{figure*}
+
 \section{}

### 2019-11-13 Evolution.py

@@ -1,0 +1,80 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import time
+
+N = 4
+x = np.linspace(-3,3,35)
+
+plt.ion()
+fig = plt.figure()
+ax = fig.add_subplot(111)
+line1, = ax.plot(x, np.ones(len(x)), 'r-')
+
+fig.canvas.draw()
+fig.canvas.flush_events()
+
+plt.xlim(-3, 3)
+plt.ylim(0, 1)
+
+t = 0
+
+filename = 'Evolution.dat'
+open(filename, 'w').close()
+f = open(filename, 'ab')
+
+# Loss
+for h in np.linspace(1, 0.5, N, endpoint = False):
+	y = 0.907 * h * np.exp(-x**2 / (2 * 0.81))
+
+	line1.set_ydata(y)
+	fig.canvas.draw()
+	fig.canvas.flush_events()
+
+	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
+	f.write('\n')
+	t += 1
+
+#time.sleep(1)
+
+# Dispersion
+for s in np.linspace(0.81, 2.593, N, endpoint = False):
+	y = 0.907 * 0.5 * np.sqrt(0.81 / s) * np.exp(-x**2 / (2 * s))
+
+	line1.set_ydata(y)
+	fig.canvas.draw()
+	fig.canvas.flush_events()
+
+	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
+	f.write('\n')
+	t += 1
+
+#time.sleep(1)
+
+# Modulation
+for m in np.linspace(0, 1, N, endpoint = False):
+	y = 0.907 * 0.5 * np.sqrt(0.81 / 2.593) * np.exp(-x**2 / (2 * 2.593)) * np.exp(-m * x**2 / 2)
+
+	line1.set_ydata(y)
+	fig.canvas.draw()
+	fig.canvas.flush_events()
+
+	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
+	f.write('\n')
+	t += 1
+
+#time.sleep(1)
+
+# Gain
+for a in np.linspace(1, 3.578, N+1):
+	y = a * 0.907 * 0.5 * np.sqrt(0.81 / 2.593) * np.exp(-x**2 / (2 * 2.593)) * np.exp(-x**2 / 2)
+
+	line1.set_ydata(y)
[…]

### 2019-11-13 Papers/Journal/Tuneable_Lasers.tex
Partially fixed plot

@@
 
-set xtics ('Loss' 2, 'Disp.' 6, 'Mod.' 10, 'Gain' 14)
+set xtics ('Loss' 3, 'Disp.' 9, 'Mod.' 15, 'Gain' 21)
 
@@
 set view 45,325,1.25
-set pm3d
-set pm3d interpolate 5,5
 
-#set contour surface
-unset cl
 unset colorbox
 
-sp '../../Evolution.dat' u 2:1:3 w l lw 0.3 lc 8 not
+set samples 10
+
+sp '../../EBig.dat' u ($2*0.1):1:3 w pm3d not, \
+'../../Evolution.dat' u 2:1:3 w l lw 0.3 lc 8 not
 \end{gnuplot}

### 2019-11-13 Evolution.py

@@ -2,8 +2,8 @@ import numpy as np
 import matplotlib.pyplot as plt
 import time
 
-N = 4
-x = np.linspace(-3,3,35)
+N = 6
+x = np.linspace(-3,3,350)
 
 plt.ion()
 fig = plt.figure()
@@ -31,7 +31,7 @@ for h in np.linspace(1, 0.5, N, endpoint = False):
 	fig.canvas.flush_events()
 
 	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n')
+	f.write('\n\n')
 	t += 1
 
 #time.sleep(1)
@@ -45,7 +45,7 @@ for s in np.linspace(0.81, 2.593, N, endpoint = False):
 	fig.canvas.flush_events()
 
 	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n')
+	f.write('\n\n')
 	t += 1
 
 #time.sleep(1)
@@ -59,7 +59,7 @@ for m in np.linspace(0, 1, N, endpoint = False):
 	fig.canvas.flush_events()
 
 	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n')
+	f.write('\n\n')
 	t += 1
 
 #time.sleep(1)
@@ -73,7 +73,7 @@ for a in np.linspace(1, 3.578, N+1):
 	fig.canvas.flush_events()
 
 	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n')
+	f.write('\n\n')
 	t += 1
 
 f.close()

### 2019-11-13 Papers/Journal/Tuneable_Lasers.tex
Finished figure

--- 2019-11-12 Papers/Journal/Tuneable_Lasers.tex
@@
 
+\begin{figure}
+\centering
+\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.7in lw 3}]
+load '/home/brady/Templates/YGB.p'
+#set format x '%.1f'
+#set format y '%.1f'
+set format z '%.1f'
+set grid
+set yl '$T$'
+set zl '$|A|$'
+set ztics 0.5
+
+set yr [-2.5:2.5]
+
+set xtics ('Loss' 3, 'Disp.' 9, 'Mod.' 15, 'Gain' 21)
+
+set xtics center offset 0,-0.5
+
+set xyplane 0
+
+set view 45,325,1.25
+
+unset colorbox
+
+sp 'EBig.dat' u ($2*0.1):1:3 w pm3d not, \
+'Shell1.dat' u 2:1:3 w l lw 0.2 lc 8 not, \
+'Shell2.dat' u ($2*0.1):1:3 w l lw 0.2 lc 8 not
+\end{gnuplot}
+\caption{}
+\label{fig:}
+\end{figure}
+
 \section{}

### 2019-11-13 Evolution.py

@@ -1,80 +1,0 @@
-import numpy as np
-import matplotlib.pyplot as plt
-import time
-
-N = 6
-x = np.linspace(-3,3,350)
-
-plt.ion()
-fig = plt.figure()
-ax = fig.add_subplot(111)
-line1, = ax.plot(x, np.ones(len(x)), 'r-')
-
-fig.canvas.draw()
-fig.canvas.flush_events()
-
-plt.xlim(-3, 3)
-plt.ylim(0, 1)
-
-t = 0
-
-filename = 'Evolution.dat'
-open(filename, 'w').close()
-f = open(filename, 'ab')
-
-# Loss
-for h in np.linspace(1, 0.5, N, endpoint = False):
-	y = 0.907 * h * np.exp(-x**2 / (2 * 0.81))
-
-	line1.set_ydata(y)
-	fig.canvas.draw()
-	fig.canvas.flush_events()
-
-	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n\n')
-	t += 1
-
-#time.sleep(1)
-
-# Dispersion
-for s in np.linspace(0.81, 2.593, N, endpoint = False):
-	y = 0.907 * 0.5 * np.sqrt(0.81 / s) * np.exp(-x**2 / (2 * s))
-
-	line1.set_ydata(y)
-	fig.canvas.draw()
-	fig.canvas.flush_events()
-
-	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n\n')
-	t += 1
-
-#time.sleep(1)
-
-# Modulation
-for m in np.linspace(0, 1, N, endpoint = False):
-	y = 0.907 * 0.5 * np.sqrt(0.81 / 2.593) * np.exp(-x**2 / (2 * 2.593)) * np.exp(-m * x**2 / 2)
-
-	line1.set_ydata(y)
-	fig.canvas.draw()
-	fig.canvas.flush_events()
-
-	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
-	f.write('\n\n')
-	t += 1
-
-#time.sleep(1)
-
-# Gain
-for a in np.linspace(1, 3.578, N+1):
-	y = a * 0.907 * 0.5 * np.sqrt(0.81 / 2.593) * np.exp(-x**2 / (2 * 2.593)) * np.exp(-x**2 / 2)
-
[…]

### 2019-11-13 Papers/Journal/Evolution.py

@@ -1,0 +1,103 @@
+import numpy as np
+import matplotlib.pyplot as plt
+import time
+
+N = 60
+x = np.linspace(-2.5,2.5,20)
+
+z = np.zeros(((4 * N + 1) * 20,3))
+
+plt.ion()
+fig = plt.figure()
+ax = fig.add_subplot(111)
+line1, = ax.plot(x, np.ones(len(x)), 'r-')
+
+fig.canvas.draw()
+fig.canvas.flush_events()
+
+plt.xlim(-3, 3)
+plt.ylim(0, 1)
+
+t = 0
+
+filename = 'Evolution.dat'
+open(filename, 'w').close()
+f = open(filename, 'ab')
+
+# Loss
+for h in np.linspace(1, 0.5, N, endpoint = False):
+	y = 0.907 * h * np.exp(-x**2 / (2 * 0.81))
+
+	line1.set_ydata(y)
+	fig.canvas.draw()
+	fig.canvas.flush_events()
+
+	z[20*t:20*t+20] = np.vstack((x, t * np.ones(len(x)), y)).T
+
+	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
+	f.write('\n\n')
+	t += 1
+
+#time.sleep(1)
+
+# Dispersion
+for s in np.linspace(0.81, 2.593, N, endpoint = False):
+	y = 0.907 * 0.5 * np.sqrt(0.81 / s) * np.exp(-x**2 / (2 * s))
+
+	line1.set_ydata(y)
+	fig.canvas.draw()
+	fig.canvas.flush_events()
+
+	z[20*t:20*t+20] = np.vstack((x, t * np.ones(len(x)), y)).T
+
+	np.savetxt(f, np.vstack((x, t * np.ones(len(x)), y)).T)
+	f.write('\n\n')
+	t += 1
+
+#time.sleep(1)
+
+# Modulation
+for m in np.linspace(0, 1, N, endpoint = False):
+	y = 0.907 * 0.5 * np.sqrt(0.81 / 2.593) * np.exp(-x**2 / (2 * 2.593)) * np.exp(-m * x**2 / 2)
+
+	line1.set_ydata(y)
+	fig.canvas.draw()
+	fig.canvas.flush_events()
+
+	z[20*t:20*t+20] = np.vstack((x, t * np.ones(len(x)), y)).T
+
[…]

### 2019-11-15 Papers/Journal/Tuneable_Lasers.tex
Fixed figure

@@
 \centering
-\begin{gnuplot}[terminal=epslatex, terminaloptions={color size 3in,1.7in lw 3}]
-load '/home/brady/Templates/YGB.p'
-#set format x '%.1f'
-#set format y '%.1f'
-set format z '%.1f'
-set grid
-set yl '$T$'
-set zl '$|A|$'
-set ztics 0.5
-
-set yr [-2.5:2.5]
-
-set xtics ('Loss' 3, 'Disp.' 9, 'Mod.' 15, 'Gain' 21)
-
-set xtics center offset 0,-0.5
-
-set xyplane 0
-
-set view 45,325,1.25
-
-unset colorbox
-
-sp 'EBig.dat' u ($2*0.1):1:3 w pm3d not, \
-'Shell1.dat' u 2:1:3 w l lw 0.2 lc 8 not, \
-'Shell2.dat' u ($2*0.1):1:3 w l lw 0.2 lc 8 not
-\end{gnuplot}
+\includegraphics{Evo}
 \caption{}
@@
 This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{Conv}
+\caption{}
+\label{fig:}
+\end{figure}
 

### 2019-11-16 ParamSpace.jl
Rewriting code in Julia for speed and parallelization for higher accuracy

@@ -1,0 +1,83 @@
+using FFTW
+using LambertW
+
+function fftfreq(n)
+	# Same as np.fft.fftfreq
+	w = zeros(n)
+	N = trunc(Int32, (n - 1) / 2) + 1
+	w[1:N] = 0:N-1
+	w[N+1:end] = -trunc(Int32, n / 2):-1
+	return w / n
+end
+
+# I couldn't find this anywhere surprisingly
+function trapz(y, dx)
+	s = 0.0
+	s += sum(y[2:end-1])
+	s += (y[1] + y[end]) / 2.0
+	return s * dx
+end
+
+function Energy(A, dx)
+	return trapz(abs.(A).^2, dx)
+end
+
+function Gain(A, E, a = 8000)
+	return real(sqrt(lambertw(a * E * exp(E)) / E)) .* A
+end
+
+function Loss(A, h = 0.04)
+	return h * A
+end
+
+function Mod(A, x)
+	return exp.(-x.^2 / 2) .* A	
+end
+
+function Fibre(A, b = 1.0)
+	return exp.(1im * b * abs.(A).^2) .* A
+end
+
+function Disp(A, x, s = 0.1)
+	F = fft(A)
+	dw = pi / x[end]
+	w = fftfreq(length(A)) * length(A) * dw
+	return ifft(F .* exp.(1im * w.^2 * s^2))
+end
+
+function Loop(A, x, dx, s, b)
+	A = Loss(A)
+	A = Disp(A, x, s)
+	A = Mod(A, x)
+	A = Gain(A, Energy(A, dx))
+	A = Fibre(A, b)
+	return A
+end
+
+x = -2:2^-18:2
+A = 1.0 ./ cosh.(x)
+
+
+
+
+
+#N = 60 # Number of loops of the circuit
+#p = 2**16 # Number of points in the discretization
+#width = 8 # Size of window
+#E0 = 0.1 # Initial energy
+
+# Initialization
+#T = np.linspace(-width, width, p, endpoint = False)
+#dx = T[1] - T[0]
+#A0 = 1 / np.cosh(2 * T) * np.exp(1j * np.pi / 4)
+#A0 = np.sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
+#E = np.zeros(N)
+#data = np.zeros((2 * N, p))
+#A = A0
+
+
+
+
+
+
+

### 2019-11-16 ParamSpace.jl
Code seems to be working for one realization

@@ -1,5 +1,6 @@
 using FFTW
 using LambertW
+using PyPlot
 
 function fftfreq(n)
 	# Same as np.fft.fftfreq
@@ -40,43 +41,44 @@ end
 
 function Disp(A, x, s = 0.1)
 	F = fft(A)
+	F = F .* (abs.(F) .> 10^-12)
 	dw = pi / x[end]
 	w = fftfreq(length(A)) * length(A) * dw
 	return ifft(F .* exp.(1im * w.^2 * s^2))
 end
 
-function Loop(A, x, dx, s, b)
-	A = Loss(A)
-	A = Disp(A, x, s)
-	A = Mod(A, x)
-	A = Gain(A, Energy(A, dx))
-	A = Fibre(A, b)
+function Loop(A, x, dx, s, b, N = 1)
+	for i in 1:N
+		A = Loss(A)
+		A = Disp(A, x, s)
+		A = Mod(A, x)
+		A = Gain(A, Energy(A, dx))
+		A = Fibre(A, b)
+	end
 	return A
 end
 
-x = -2:2^-18:2
-A = 1.0 ./ cosh.(x)
 
 
-
-
-
-#N = 60 # Number of loops of the circuit
-#p = 2**16 # Number of points in the discretization
-#width = 8 # Size of window
-#E0 = 0.1 # Initial energy
+N = 60 # Number of loops of the circuit
+p = 2^18 # Number of points in the discretization
+width = 8 # Size of window
+E0 = 0.1 # Initial energy
 
 # Initialization
-#T = np.linspace(-width, width, p, endpoint = False)
-#dx = T[1] - T[0]
-#A0 = 1 / np.cosh(2 * T) * np.exp(1j * np.pi / 4)
-#A0 = np.sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
-#E = np.zeros(N)
-#data = np.zeros((2 * N, p))
-#A = A0
+x = LinRange(-width, width, p)
+dx = x[2] - x[1]
+A0 = 1.0 ./ cosh.(2 * x) * exp(1im * pi / 4.0)
+A0 = sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
 
+A = A0
 
+A = Loop(A, x, dx, 0.1, 1.59, 30)
 
+plot(x, abs.(A))
+plot(x, real.(A))
+plot(x, imag.(A))
+show()
 
 
 

### 2019-11-17 ParamSpace.jl
Finished rewriting laser code (parallelized)

@@ -1,85 +1,0 @@
-using FFTW
-using LambertW
-using PyPlot
-
-function fftfreq(n)
-	# Same as np.fft.fftfreq
-	w = zeros(n)
-	N = trunc(Int32, (n - 1) / 2) + 1
-	w[1:N] = 0:N-1
-	w[N+1:end] = -trunc(Int32, n / 2):-1
-	return w / n
-end
-
-# I couldn't find this anywhere surprisingly
-function trapz(y, dx)
-	s = 0.0
-	s += sum(y[2:end-1])
-	s += (y[1] + y[end]) / 2.0
-	return s * dx
-end
-
-function Energy(A, dx)
-	return trapz(abs.(A).^2, dx)
-end
-
-function Gain(A, E, a = 8000)
-	return real(sqrt(lambertw(a * E * exp(E)) / E)) .* A
-end
-
-function Loss(A, h = 0.04)
-	return h * A
-end
-
-function Mod(A, x)
-	return exp.(-x.^2 / 2) .* A	
-end
-
-function Fibre(A, b = 1.0)
-	return exp.(1im * b * abs.(A).^2) .* A
-end
-
-function Disp(A, x, s = 0.1)
-	F = fft(A)
-	F = F .* (abs.(F) .> 10^-12)
-	dw = pi / x[end]
-	w = fftfreq(length(A)) * length(A) * dw
-	return ifft(F .* exp.(1im * w.^2 * s^2))
-end
-
-function Loop(A, x, dx, s, b, N = 1)
-	for i in 1:N
-		A = Loss(A)
-		A = Disp(A, x, s)
-		A = Mod(A, x)
-		A = Gain(A, Energy(A, dx))
-		A = Fibre(A, b)
-	end
-	return A
-end
-
-
-
-N = 60 # Number of loops of the circuit
-p = 2^18 # Number of points in the discretization
-width = 8 # Size of window
-E0 = 0.1 # Initial energy
-
-# Initialization
-x = LinRange(-width, width, p)
-dx = x[2] - x[1]
-A0 = 1.0 ./ cosh.(2 * x) * exp(1im * pi / 4.0)
-A0 = sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
-
-A = A0
-
-A = Loop(A, x, dx, 0.1, 1.59, 30)
-
-plot(x, abs.(A))
-plot(x, real.(A))
-plot(x, imag.(A))
-show()
-
-
-
-

### 2019-11-17 WaveBreaking.jl

@@ -1,0 +1,121 @@
+@everywhere using FFTW
+@everywhere using LambertW
+@everywhere using DelimitedFiles
+#using PyPlot
+using Distributed
+@everywhere using SharedArrays
+
+@everywhere function fftfreq(n::Int)
+	# Same as np.fft.fftfreq
+	w = zeros(n)
+	N = div((n - 1), 2) + 1
+	w[1:N] = 0:N-1
+	w[N+1:end] = -div(n, 2):-1
+	return w / n
+end
+
+# I couldn't find this anywhere surprisingly
+@everywhere function trapz(y, dx)::Float64
+	s = 0.0
+    s += sum(y[2:end-1])
+    s += (y[1] + y[end]) / 2.0
+	return s * dx
+end
+
+@everywhere function Energy(A, dx)
+	return trapz(abs2.(A), dx)
+end
+
+@everywhere function Gain(A, E, a = 8000)
+	return real(sqrt(lambertw(a * E * exp(E)) / E)) .* A
+end
+
+@everywhere function Loss(A, h::Float64 = 0.04)
+	return h * A
+end
+
+@everywhere function Mod(A, x)
+	return @. exp(-x^2 / 2) * A	
+end
+
+@everywhere function Fibre(A, b::Float64 = 1.0)
+	return @. exp(1im * b * abs2(A)) * A
+end
+
+@everywhere function Disp(A, x, s::Float64 = 0.1)
+	F = fft(A)
+	F = @. F * (abs(F) > 10^-12)
+	dw = pi / x[end]
+	w = fftfreq(length(A)) * length(A) * dw
+	return ifft(@. F * exp(1im * w^2 * s^2))
+end
+
+# Complete loop of the cavity
+@everywhere function Loop(A, x, dx, s::Float64, b::Float64, N::Int64 = 1)
+	for i in 1:N
+		A = Loss(A)
+		A = Disp(A, x, s)
+		A = Mod(A, x)
+		A = Gain(A, Energy(A, dx))
+		A = Fibre(A, b)
+	end
+	return A
+end
+
+# Compute solution on a grid
+function Solve(A0, n::Int64, m::Int64, numloops::Int64, fname = "Results.dat")
+    """
+    Comptues 2-norm error, Inf-norm error, Energy, Variance, and Kurtosis within the s-b plane.
+    """
+    f = open(fname, "w");
+
+    s = LinRange(0.0, 0.25, n)
[…]

### 2019-11-24 Papers/Journal/WaveBreaking.jl
Improved error

@@ -1,0 +1,126 @@
+@everywhere using FFTW
+@everywhere using LambertW
+@everywhere using DelimitedFiles
+#using PyPlot
+using Distributed
+@everywhere using SharedArrays
+
+@everywhere function fftfreq(n::Int)
+	# Same as np.fft.fftfreq
+	w = zeros(n)
+	N = div((n - 1), 2) + 1
+	w[1:N] = 0:N-1
+	w[N+1:end] = -div(n, 2):-1
+	return w / n
+end
+
+# I couldn't find this anywhere surprisingly
+@everywhere function trapz(y, dx)::Float64
+	s = 0.0
+    s += sum(y[2:end-1])
+    s += (y[1] + y[end]) / 2.0
+	return s * dx
+end
+
+@everywhere function Energy(A, dx)
+	return trapz(abs2.(A), dx)
+end
+
+@everywhere function Gain(A, E, a = 8000)
+	return real(sqrt(lambertw(a * E * exp(E)) / E)) .* A
+end
+
+@everywhere function Loss(A, h::Float64 = 0.04)
+	return h * A
+end
+
+@everywhere function Mod(A, x)
+	return @. exp(-x^2 / 2) * A	
+end
+
+@everywhere function Fibre(A, b::Float64 = 1.0)
+	return @. exp(1im * b * abs2(A)) * A
+end
+
+@everywhere function Disp(A, x, s::Float64 = 0.1, b::Float64 = 1.0)
+	F = fft(A)
+	c = b + 15 * s
+	if c >= 6 # Shenanigans
+		F = @. F * (abs(F) > 10^(1 + 0.6 * c - 15.6))
+	else
+		F = @. F * (abs(F) > 10^-11)
+	end
+	dw = pi / x[end]
+	w = fftfreq(length(A)) * length(A) * dw
+	return ifft(@. F * exp(1im * w^2 * s^2))
+end
+
+# Complete loop of the cavity
+@everywhere function Loop(A, x, dx, s::Float64, b::Float64, N::Int64 = 1)
+	for i in 1:N
+		A = Loss(A)
+		A = Disp(A, x, s, b)
+		A = Mod(A, x)
+		A = Gain(A, Energy(A, dx))
+		A = Fibre(A, b)
+	end
+	return A
+end
+
+# Compute solution on a grid
+function Solve(A0, n::Int64, m::Int64, numloops::Int64, fname = "Results.dat")
+    """
[…]

### 2019-11-24 Papers/Journal/WaveBreaking.jl
Fixed indentation

@@ -17,8 +17,8 @@ end
 # I couldn't find this anywhere surprisingly
 @everywhere function trapz(y, dx)::Float64
 	s = 0.0
-    s += sum(y[2:end-1])
-    s += (y[1] + y[end]) / 2.0
+	s += sum(y[2:end-1])
+	s += (y[1] + y[end]) / 2.0
 	return s * dx
 end
 
@@ -35,7 +35,7 @@ end
 end
 
 @everywhere function Mod(A, x)
-	return @. exp(-x^2 / 2) * A	
+	return @. exp(-x^2 / 2) * A
 end
 
 @everywhere function Fibre(A, b::Float64 = 1.0)
@@ -69,39 +69,39 @@ end
 
 # Compute solution on a grid
 function Solve(A0, n::Int64, m::Int64, numloops::Int64, fname = "Results.dat")
-    """
-    Comptues 2-norm error, Inf-norm error, Energy, Variance, and Kurtosis within the s-b plane.
-    """
-    f = open(fname, "w");
-
-    s = LinRange(0.0, 0.4, n)
-    b = LinRange(0.0, 10.0, m)
-    
-    for k in 1:m # b loop
-        println(k)
-        z = SharedArray{Float64, 2}((n, 7))
-        @sync @distributed for j in 1:n # s loop
-            A = A0
-            A = Loop(A, x, dx, s[j], b[k], numloops - 1)
-            old = abs.(A)
-            A = Loop(A, x, dx, s[j], b[k])
-            new = abs.(A)
-            
-            # Compute quantities
-            err2 = sqrt(trapz((new - old).^2, dx) / trapz(abs2.(A), dx))
-            errinf = maximum(abs.(new - old))
-            sigma = trapz(x.^2 .* new, dx) / trapz(new, dx)
-            kurt = trapz(x.^4 .* new, dx) / trapz(x.^2 .* new, dx)
-            energy = Energy(new, dx)
-            
-            # Build array of values
-            z[j,:] = [s[j] b[k] err2 errinf energy sigma kurt / sigma]
-        end
-        # Write data to file
-        writedlm(f, z)
-        println(f, "")
-    end
-    close(f)
+	"""
+	Comptues 2-norm error, Inf-norm error, Energy, Variance, and Kurtosis within the s-b plane.
[…]

### 2020-01-03 Papers/Journal/Tuneable_Lasers.tex
Created breaking plot
Added error and energy plots
Fixed indentation
Updated paper

@@
 %\usepackage{wrapfig}
-%\usepackage{subcaption}
+\usepackage{subcaption}
 %\usepackage{hyperref}
 \usepackage{tikz}
+\RequirePackage{cite}
 
@@
 
-\title{A New Method of Modelling Tuneable Lasers with Functional Composition}
+\title{}
 \author{B. Metherall \and C. S. Bohun}
@@
 		\begin{abstract}
-A new nonlinear model is proposed for tuneable lasers.
-Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity.
-These transformations are then composed to give the overall effect of one trip around the cavity.
+
 		\end{abstract}
@@
 This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
-A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}.
-In contrast to a standard laser, a tuneable laser contains two additional components, namely, a chirped fibre Bragg grating (CFBG), and a modulator.
+A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.
 
-\begin{figure}[tbp]
-\centering
-\input{Cavity}
-\caption{Typical cavity of a fibre based tuneable laser. The laser pulses travel clockwise around each loop.}
-\label{fig:cavity}
-\end{figure}
-A CFBG is a length of optical fibre where the refractive index oscillates along its length \cite{ferreira}, and therefore, can act as a reflective filter \cite{agrawal2002, alazzawi, ferreira, starodoumov}.
-Due to the oscillatory nature, light with the corresponding wavelength will be reflected when the Bragg condition is satisfied \cite{agrawal2002, alazzawi, becker, ferreira, silfvast, starodoumov}.
-The spacial variation of the refractive index effectively creates a spacial dependence on the Bragg condition, causing most wavelengths to be reflected by a CFBG, but with each wavelength satisfying the Bragg condition at a different spacial location\footnote{Note that a monotonic chirping ensures that the spacial dependence of the Bragg condition is continuous with respect to the frequency.}.
-A consequence of this is that a time delay is created between wavelengths---this causes the pulse to disperse and broaden.
+\subsection{Wave Breaking}
 
-The modulator serves the purpose of reshaping the pulse. Without it, the pulse will repeatedly widen due to the CFBG---the modulator ensures the pulse is band limited by altering the envelope.
-
-\section{Modelling Efforts}
+\subsection{Modelling Efforts}
 \label{sec:modelling}
-The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE)\footnote{The NLSE can be derived from the nonlinear wave equation for electric fields; this derivation is presented in detail in \cite{agrawal2013, ferreira}.},
+The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE),
 \begin{align}
@@
 	\begin{align}
+	\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
 	\label{eq:nlse}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A,
 \end{align}
@@
 
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers we typically also add a modulation term.
-This yields the master equation of mode-locking \cite{haus1975, hausbook, haus1986, haus1992, haus2000, kartner, tamura1996, usechak},
+The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers typically a modulation term to ensure mode-locking, this yields the master equation of mode-locking, \cite{hausbook, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak}
 \begin{align}
-\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T),
+	\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T).
 	\label{eq:meml}
 \end{align}
-where $M(T)$ is the modulation function. The solutions of three simplifications of \eqref{eq:meml} have been investigated:
-\begin{itemize}
-\item Omitting both modulation and nonlinearity \cite{haus1975, haus1986, haus1992}.
-\item Omitting only modulation \cite{haus1991, usechak}.
-\item Omitting only nonlinearity  \cite{burgoyne2014, haus1975, hausbook, haus1996, haus2000, kartner, tamura1996, usechak}.
-\end{itemize}
-For a more comprehensive history see \cite{haus2000}.
+No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic \cite{hausbook, haus1975, haus1996}.
+However, by neglecting terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak}.
+Furthermore, see Haus \cite{haus2000} for a comprehensive history of the theory of mode-locked lasers.
+
+\begin{figure}[tbp]
+	\centering
+	\input{Cavity}
+	\caption{Typical cavity of a fibre based tuneable laser. The laser pulses travel clockwise around each loop.}
+	\label{fig:cavity}
+\end{figure}
 
 \subsection{Discrete Models}
-While the derivation of \eqref{eq:meml} is correct mathematically, it is not representative of what happens within the laser cavity.
-The issue with \eqref{eq:meml} is that it has been assumed each process affects the pulse continuously within the cavity.
+\label{sec:discrete}
+Unfortunately, \eqref{eq:meml} is not completely representative of the underlying physics within our laser cavity.
+In the derivation of \eqref{eq:meml} it is assumed each process affects the pulse continuously within the cavity.
 As highlighted by Figure \ref{fig:cavity}, this is a rather poor assumption.
 Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
-Thus, perhaps a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
-Each of the blocks can then be functionally composed together to give an iterative map for the effect of one circuit around the cavity.
-This transforms the differential equation into an algebraic equation.
+Thus, a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
+Each of the blocks can then be functionally composed together to give an iterative map for the effect of one round trip of the cavity.
+This ultimately transforms the differential equation into an algebraic equation.
 
@@
 This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
-In these models the effect of each block is described by a transfer function.
+In each of these models the effect of each block is described by a transfer function.
 
@@
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
+Finally, none of these previous models have been able to exhibit wave breaking.
 
-\section{A New Model}
-\label{sec:newmodel}
-Using the ideas presented in the previous section of the prior functional models \cite{burgoyne2014, cutler, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, siegman} we shall derive a new model from \eqref{eq:nlse}---with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.
+\section{Model Derivation}
+\label{sec:model}
+Using the idea presented Section \ref{sec:discrete} we derive our model from \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
+To accomplish this, we neglect all terms but one of the right side of \eqref{eq:nlse} and solve the simplified differential equation.
+This is reasonable since the gain, loss, dispersion, modulation, and nonlinear effects are localized to one section of the laser cavity.
 
-\subsection{Components}
-We shall determine the effect each component has on the pulse by solving \eqref{eq:nlse} while only considering the dominant term within each section of the cavity.
-
-\subsubsection{Gain}
-Within the Er-doped gain fibre, the gain term is dominant, and equation \eqref{eq:nlse} reduces to
+To proceed we must choose the form of the amplification term, $g(A)$. We assume the gain has the form
 \begin{align}
-\label{eq:gainde}
-\pdiff{A}{z} &= \frac{1}{2} g(A) A,
+	g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
+	\label{eq:energy}
 \end{align}
-where $g(A)$ takes the form \cite{bohun, burgoyne2014, haus1975, hausbook, haus1992, haus2000, haus1991, kartner, peng, shtyrina, silfvast, usechak, yarutkina}
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{bohun, burgoyne2014, haus1975, hausbook, haus1992, haus2000, haus1991, kartner, peng, shtyrina, silfvast, usechak, yarutkina}.
+This leads to
 \begin{align}
-\label{eq:energy}
-	g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
+	G(A;E) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate.
-Without much difficulty this differential equation can be solved, and the effect on an incident pulse is
+for the amplification of the pulse within the Er-doped fibre. Continuing this process for the loss, dispersion, and nonlinearity yields
 \begin{align}
-G(A;E) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A,
-\end{align}
-where $L_g$ is the length of the gain fibre.
-
-\subsubsection{Nonlinearity}
-The nonlinearity of the fibre arises from the parameter $\gamma$; in regions where this effect is dominant expression~\eqref{eq:nlse} becomes
-\begin{align}
-\label{eq:fibrediff}
-	\pdiff{A}{z} - i \gamma |A|^2 A = 0.
-\end{align}
-Using a similar method as with the gain, the effect of the nonlinearity can be shown to be
-\begin{align}
+	L(A) &= (1 - R) \textrm{e}^{- \alpha L_T}A, \\
+	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}}, \\
 	F(A) &= A \textrm{e}^{i \gamma |A|^2 L_f},
 \end{align}
-where $L_f$ is the length of fibre.
-
-\subsubsection{Loss}
-Expression \eqref{eq:nlse} leads to exponential decay due to the scattering and absorption of the fibre.
-However, a majority of the signal is removed from the cavity by the optical coupler.
-Combining these two effects yields
-\begin{align}
-L(A) &= (1 - R) \textrm{e}^{- \alpha L_T}A,
-\end{align}
-where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit as the effect of the losses\footnote{Depending on the layout of the laser cavity the loss may take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$ instead.}.
-
-\subsubsection{Dispersion}
-Considering only the dispersive terms of \eqref{eq:nlse}, one obtains
-\begin{align}
-\label{eq:dispde}
-	\pdiff{A}{z} = -i \frac{\beta_2}{2} \pdiff[2]{A}{T}.
-\end{align}
-The effect of dispersion is then given by the map
-\begin{align}
-D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}},
-\end{align}
-where $L_D$ is the length of the dispersive medium, and $\mathcal{F}$ denotes the Fourier transform.
-
-\subsubsection{Modulation}
-In this model, the modulation is considered to be applied externally in which ever way the operator sees fit. For simplicity the representation is taken as the Gaussian
+where $R$ is the reflectivity of the output coupler\footnote{Depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$.}, $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre, and where $\mathcal{F}$ denotes the Fourier transform.
+Finally, we must assume a form for the modulation.
+The modulation is considered to be applied externally in which ever way the operator sees fit.
+For simplicity the representation is taken as the Gaussian
 \begin{align}
@@
 \subsection{Non-Dimensionalization}
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude.
-Nominal values for tuneable lasers are shown in Table \ref{tab:values}.
-Knowing experimental durations and energies, the table suggests the convenient scalings:
+The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude; this suggests the convenient scalings:
 \begin{align}
@@
 \end{equation}
-with the four dimensionless parameters, as defined by the values in Table \ref{tab:values},
+with the four dimensionless parameters,
 \begin{equation}
@@
 \end{equation}
-which characterize the behaviour of the laser. Notice that the modulation is only characterized by $T_M$, and each other process has its own independent non-dimensional parameter.
+which characterize the behaviour of the laser.
+Nominal values for \eqref{eq:ndparam} can be found in \cite{agrawal2002, agrawal2013, bohun, burgoyne2014, burgoyneemail, finot, li, litchinitser, peng, shtyrina, tamura1993, tamura1996, tomlinson, usechak, yamashita, yarutkina}.
+Notice that the modulation is only characterized by $T_M$, and each other process has its own associated independent non-dimensional parameter.
 
-\begin{table*}[tbp]
+% Table of parameter values
+% \begin{table*}[tbp]
+% 	\centering
+% 	\begin{tabular}{lcll}
+% 		\hline\noalign{\smallskip}
+% 		Parameter & Symbol & Value & Sources \\
+% 		\hline\noalign{\smallskip}
+% 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, tomlinson, usechak, yarutkina} \\
+% 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
+% 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot, usechak, yarutkina} \\
+% 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
+% 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng, tamura1996} \\
+% 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
+% 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, tamura1993, yarutkina} \\
+% 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyneemail, burgoyne2014} \\
+% 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li, peng,  tamura1993, tamura1996, yamashita} \\
+% 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
+% 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
+% 		\noalign{\smallskip}\hline
+% 	\end{tabular}
+% 	\caption{Range of variation of various parameters.}
+% 	\label{tab:values}
+% \end{table*}
+
+\subsection{Combining the Effects}
+\label{sec:effects}
+
+\begin{figure}[tbp]
 	\centering
-\begin{tabular}{lcll}
-\hline\noalign{\smallskip}
-Parameter & Symbol & Value & Sources \\
-\hline\noalign{\smallskip}
-Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, tomlinson, usechak, yarutkina} \\
-Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
-Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot, usechak, yarutkina} \\
-Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
-Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng, tamura1996} \\
-Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
-Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, tamura1993, yarutkina} \\
-Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyneemail, burgoyne2014} \\
-Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li, peng,  tamura1993, tamura1996, yamashita} \\
-Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
-Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
-\noalign{\smallskip}\hline
-\end{tabular}
-\caption{Range of variation of various parameters.}
-\label{tab:values}
-\end{table*}
+	\includegraphics{Evo}
+	\caption{Evolution of the envelope during one round trip of the cavity.
+The pulse decays due to the output coupler, is dispersed by the CFBG, is modulated by the modulator, and finally amplified by the gain fibre (the nonlinearity does not alter the envelope).
+Note that this is not to scale.}
+	\label{fig:cavityevo}
+\end{figure}
 
-\subsection{Combining the Effects of Each Block of the Model}
-\label{sec:effects}
-In this model the pulse is iteratively passed through each process, the order of which must now be considered.
-We are most interested in the output of the laser cavity, and so we shall start with the loss component.
-Next the pulse is passed though the CFBG, as well as the modulator.
-Finally, the pulse travels through the gain fibre to be amplified, and then we consider the effect of the nonlinearity since this is the region where the power is maximal.
-Note that in general the functional operators of the components do not commute, and therefore the order of the components is indeed important---in contrast to the previous models.
-This is especially the case of dispersion as realized through the Fourier transform.
-Functionally this can be denoted as
+Now that we have the algebraic effect of each section of the cavity, we are ready to compose each map together to give the effect of one round trip of the cavity.
+We must now consider the order of the components.
+As we are most interested in the output of the laser cavity, we shall start with the loss.
+We then pass the pulse through the CFBG followed by the modulator.
+The pulse then travels through the Er-doped fibre to be amplified, and finally we consider the effect of the nonlinearity.
+The nonlinearity must immediately follow the gain since this is the section of the cavity where the pulse has the highest energy, and by \eqref{eq:effects} the effect of the nonlinearity is proportional to the energy.
+Note that is this model, the permutation of the components is indeed important as the operators do not, in general, commute---this is in contrast to the models described in Section \ref{sec:discrete}.
+Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to mitigate the length over which the nonlinearity has an effect, and maximize the output power.
+Functionally we denote one round trip of the cavity by
 \begin{align}
-\mathcal{L}(A) = F(G(M(D(L(A))))),
+	\mathcal{L}(A) = F(G(M(D(L(A))))).
 \end{align}
-where $\mathcal{L}$ denotes one loop of the laser.
-The pulse after one complete circuit of the laser cavity is then passed back in to restart the process.
+ The pulse after one complete circuit of the laser cavity is then returned back into cavity to restart the process.
 A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase.
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
-\\
+In Figure \ref{fig:cavityevo} we can see an example of the evolution of the envelope of the pulse during one round trip of the cavity.
 
-\section{}
+\section{Results}
+
+\subsection{Linear Solution}
+
+\subsection{Nonlinear Solution and Wave Breaking}
+
+\section{Conclusion}
+
+\clearpage
+\newpage
+
+\section{Linear Solution}
 In the case $b = 0$ a solution can be found analytically.
-We would expect the solution will have the form of a Gaussian.
-There are a few reasons for this; the solution to previous models were Gaussian \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985}, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn} dispersion will not alter the envelope.
+We expect the solution will have the form of a Gaussian.
+There are a few reasons for this; the solution to the models presented in \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn}.
 
@@
 \end{align}
-As this expression is a quartic in $\sigma^2$ it too has an analytic solution, namely,
+As this expression is a quartic in $\sigma^2$ it has an analytic solution, namely,
 \begin{equation}
@@
 \end{equation}
-However, by asymptotically expanding \eqref{eq:var} we find the useful relations
+Moreover, by asymptotically expanding \eqref{eq:var} we find the useful relations
 \begin{align}
@@
 		2s(1 - s) + \bigO{s^3} & s \rightarrow 0 \\
-1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty
-\end{cases}.
+		1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty.
+	\end{cases}
 \end{align}
@@
 		1 - s + \frac{1}{2}s^2 + \bigO{s^3} & s \rightarrow 0 \\
-\frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}} & s \rightarrow \infty
-\end{cases}.
+		\frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}} & s \rightarrow \infty.
+	\end{cases}
 \end{align}
-
+The equilibrium energy and peak power can be computed from \label{eq:energy} to give
 \begin{align}
-E = \frac{h^2 \zeta^2}{1 - h^2 \zeta^2} \log \left( a h^2 \zeta^2 \right). \\
+	E = \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2}}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right),
 \end{align}
-
+and
 \begin{align}
-P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma}.
+	P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma},
 	\label{eq:equilpower}
 \end{align}
+respectively.
 
-\begin{figure}
-\centering
-\includegraphics{Evo}
-\caption{}
-\label{fig:}
-\end{figure}
+\section{Nonlinear Solution}
+We now consider the nonlinear case---when $b > 0$.
+In this case it becomes impossible to obtain an analytic result.
+Recall from \eqref{eq:effects} that the nonlinearity is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone this transformation is futile.
+Instead we resort to a numerical solution.
 
-\section{}
-We shall now consider the nonlinear case---when $b > 0$. In this case it becomes impossible to obtain an analytic result. Recall from \eqref{eq:fibre} that the nonlinearity takes the form
-\begin{align*}
-F(A) &= A \textrm{e}^{i b |A|^2}.
-\end{align*}
-This is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone the transformation due to the nonlinearity is futile.
-Instead we must resort to a numerical solution.
+With the inclusion of the nonlinearity we generally find a similar solution to the linear case. An example of this is shown in Figure \ref{fig:nlstable}.
 
-With the inclusion of the nonlinearity we generally find a similar solution to the linear case.
-An example of this is shown in Figure \ref{fig:nlstable}.
-The envelope of the pulse is unsurprisingly Gaussian-esque, however, it is \emph{not} precisely Gaussian and more closely resembles a generalized Gaussian\footnote{A generalized Gaussian has the form $\exp \left(-t^\alpha \right)$, with $\alpha > 2$.}.
-The fact that the pulse envelope is not Gaussian is further emphasized while examining the Fourier transform of the pulse.
-If the pulse were a Gaussian, we would expect the Fourier transform to also be a Gaussian \cite{debnath, gradshteyn}.
 Instead, the magnitude of the Fourier transform has a unique weakly bi-modal shape.
@@
 Finally, we shall examine the derivative of the phase---essentially the chirp.
-Recall in Chapter \ref{chap:linear} the chirp was defined as coefficient of $-\frac{1}{2}iT^2$ in the exponential, and by taking the negative of the derivative we would expect a linear function with a slope equal to the chirp.
+
  In the nonlinear case, we recover this linear response for moderate values of $T$.
@@
 
-\begin{figure}[htbp]
+\begin{figure}[tb]
+	\centering
+	\begin{subfigure}{\columnwidth}
 		\centering
 		\includegraphics{Conv}
-\caption{}
-\label{fig:}
+		\caption{Example of a pulse stabilizing from a seemingly random initial pulse shape ($s = 0.1$, $b = 1.0$, $E_0 = 0.1$, $a = 8000$, $h = 0.04$).}
+		\label{fig:convevo}
+	\end{subfigure} \\
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Break}
+		\caption{Example of a pulse destabilizing from a hyperbolic secant initial pulse ($s = 0.1$, $b = 1.6$, $E_0 = 0.1$, $a = 8000$, $h = 0.04$).}
+		\label{fig:breakevo}
+	\end{subfigure}
+	\caption{Two extremes of the evolution of a pulse.}
+	\label{fig:evolution}
 \end{figure}
@@
 
+\begin{figure}[htbp]
+	\centering
+	\includegraphics{ParamSpaceErr}
+	\caption{}
+	\label{fig:error}
+\end{figure}
+
+\begin{figure}[htbp]
+	\centering
+	\includegraphics{ParamSpaceEnergy}
+	\caption{}
+	\label{fig:}
+\end{figure}
+
 To obtain a better understanding of how the pulse either converges to equilibrium, or diverges to wave breaking, we shall examine the difference between the envelopes of consecutive iterations.
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{12}$).
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{18}$).
 Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested in the phase shift between iterations.
@@
 Additionally, incorrectly choosing the critical tolerance could easily lead to erroneous categorizations at points.
-As we saw in Figure \ref{fig:roc} some values of the parameters lead to a steady, periodic state, but with an error of $\bigO{10^{-6}}$, and so, had we set the tolerance to $10^{-8}$ these points would have been labeled as unsteady.
-\\
 
@@
 As a consequence the envelope varies drastically, which leads to this large error.
-Conversely, the region where the energy appeared to be stable still has a non-zero error.
-The cause of this discrepancy is because some equilibrium states have a periodicity greater than $1$, thus, we redefine \eqref{eq:error} to be instead
-\begin{align}
-\textrm{E}_\Delta = \frac{\| |A_i| - |A_{i-\Delta}| \|_2}{\| A_{i-\Delta} \|_2},
-\label{eq:deltaerror}
-\end{align}
-to pick up equilibrium states with period $\Delta$, again with $i = 100$.
-Figure \ref{fig:deltaerror} shows the error for an assortment of $\Delta$ values.
-There are several key observations to make, first, for $\Delta = 2$ the kidney-shaped blob in the lower right corner has vanished, thus, this entire region has a periodicity of $2$.
-Second, for $\Delta = 3$ in the upper right corner a negative triangular-shaped structure emerges.
-Lastly, $\Delta \in \left\{ 5, 7, 11, 13 \right\}$ may not seem to extract any higher order periods, however, there are in fact very small striations in the lower left.
-We typically chose $\Delta$ values to be prime since they are the building blocks for composite numbers.
-However, there are two composite $\Delta$ values of interest.
-The first is $16$, since $16 = 2^4$, as it will pick up any periodic behaviour with orders of $2, 4, 8, 16$.
-Lastly, we chose $\Delta = 60$ for a similar reason: because $60$ is highly divisible we can extract orders such as $12$ or $30$ without having to explicitly run the calculations\footnote{In the case of $\Delta = 60$ a value of $i = 150$ is used to ensure sufficient iterations to converge.}.
-\\
 
@@
 As a whole, unsurprisingly, we find the same behaviour and structure, however, there are some intriguing differences.
-Perhaps the most interesting is the small island of instability in Figure \ref{fig:switchzoom} at around $s = 0.075$, $b = 1.1$ which was not present in the other ordering.
-Within this island the wave is unstable and breaks, but, curiously there is a small gap between this island and the main unstable region.
-We find more distinctions when considering the larger area in Figure \ref{fig:switchbig}.
 Again, the structure and periodic nature of the boundary is similar to before, however, this boundary has shifted rightwards to a larger $s$ value.

### 2020-01-03 Papers/Journal/Tuneable_Lasers.tex
Added corrections from the plane

@@
 Tuneable lasers simultaneously lase at all frequencies within this bandwidth.
-This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
+This tuneability leads to applications in spectroscopy and high resolution imaging, such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
 A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.
@@
 Here $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
-In practice, \eqref{eq:smallnlse} lacks a few key terms, thus, it is often generalized by adding amplification, loss, and occasionally higher order terms.
-This gives the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
+In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification, loss, and occasionally higher order terms.
+These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
 	\begin{align}
@@
 \end{align}
-where $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}$ is the loss due to scattering and absorption.
+where $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}^+$ is the loss due to scattering and absorption.
 
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers typically a modulation term to ensure mode-locking, this yields the master equation of mode-locking, \cite{hausbook, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak}
+The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking \cite{hausbook, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak},
 \begin{align}
@@
 No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic \cite{hausbook, haus1975, haus1996}.
-However, by neglecting terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak}.
-Furthermore, see Haus \cite{haus2000} for a comprehensive history of the theory of mode-locked lasers.
+However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak}.
+Furthermore, see Haus \cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
 
@@
 \label{sec:discrete}
-Unfortunately, \eqref{eq:meml} is not completely representative of the underlying physics within our laser cavity.
+Unfortunately, the master equation, \eqref{eq:meml}, is not completely representative of the underlying physics within our laser cavity.
 In the derivation of \eqref{eq:meml} it is assumed each process affects the pulse continuously within the cavity.
-As highlighted by Figure \ref{fig:cavity}, this is a rather poor assumption.
-Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
+As highlighted by Figure \ref{fig:cavity}, this can be a poor assumption.
+Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the chirped fibre Bragg grating (CFBG) \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
 Thus, a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
@@
 Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator.
-This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, siegman}.
-Kuizenga and Siegman also had success experimentally validating their model \cite{kuizenga1970b, kuizenga1970}.
+This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman}.
 The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passively mode-locked lasers.
@@
 The clearest is that none of these models have contained every block---either the nonlinearity or the modulation have been omitted.
-In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function correctly without the inclusion of all of the components.
-Another key drawback is that the functional operations of some of the components used in their models are phenomenological.
+Each component of a tuneable plays a crucial role and the laser will not function correctly without the inclusion of all of the components.
+Another drawback is that the functional operations of some of the components used in their models are phenomenological.
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
@@
 \label{sec:model}
-Using the idea presented Section \ref{sec:discrete} we derive our model from \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
+Using the idea of a discrete model presented Section \ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
 To accomplish this, we neglect all terms but one of the right side of \eqref{eq:nlse} and solve the simplified differential equation.
-This is reasonable since the gain, loss, dispersion, modulation, and nonlinear effects are localized to one section of the laser cavity.
+This is a reasonable assumption since the gain, loss, dispersion, modulation, and nonlinear effects are localized to only one section of the laser cavity.
 
@@
 \begin{align}
-	G(A;E) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A
+	G(A) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A
 \end{align}
@@
 \end{align}
-where $R$ is the reflectivity of the output coupler\footnote{Depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$.}, $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre, and where $\mathcal{F}$ denotes the Fourier transform.
+where $R$ is the reflectivity of the output coupler\footnote{Depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$.}, $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and where $\mathcal{F}$ denotes the Fourier transform.
 Finally, we must assume a form for the modulation.
@@
 	\begin{aligned}
-		G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \textrm{e}^{i b |A|^2} \\
+		G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \textrm{e}^{i b |A|^2}, \\
 		D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, & L(A) &= h A, \\
@@
 which characterize the behaviour of the laser.
-Nominal values for \eqref{eq:ndparam} can be found in \cite{agrawal2002, agrawal2013, bohun, burgoyne2014, burgoyneemail, finot, li, litchinitser, peng, shtyrina, tamura1993, tamura1996, tomlinson, usechak, yamashita, yarutkina}.
+Nominal values for the parameters, \eqref{eq:ndparam}, can be found in \cite{agrawal2002, agrawal2013, bohun, burgoyne2014, burgoyneemail, finot, li, litchinitser, peng, shtyrina, tamura1993, tamura1996, tomlinson, usechak, yamashita, yarutkina}.
 Notice that the modulation is only characterized by $T_M$, and each other process has its own associated independent non-dimensional parameter.
@@
 	\includegraphics{Evo}
-	\caption{Evolution of the envelope during one round trip of the cavity.
-The pulse decays due to the output coupler, is dispersed by the CFBG, is modulated by the modulator, and finally amplified by the gain fibre (the nonlinearity does not alter the envelope).
-Note that this is not to scale.}
+	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
+The pulse decays due to the output coupler, dispersed by the CFBG, modulated by the modulator, and finally amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+Note that this is for visualization only, the durations are not to scale.}
 	\label{fig:cavityevo}
@@
 Now that we have the algebraic effect of each section of the cavity, we are ready to compose each map together to give the effect of one round trip of the cavity.
-We must now consider the order of the components.
+Thus, we must now consider the order of the components.
 As we are most interested in the output of the laser cavity, we shall start with the loss.
@@
 The pulse then travels through the Er-doped fibre to be amplified, and finally we consider the effect of the nonlinearity.
-The nonlinearity must immediately follow the gain since this is the section of the cavity where the pulse has the highest energy, and by \eqref{eq:effects} the effect of the nonlinearity is proportional to the energy.
-Note that is this model, the permutation of the components is indeed important as the operators do not, in general, commute---this is in contrast to the models described in Section \ref{sec:discrete}.
-Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to mitigate the length over which the nonlinearity has an effect, and maximize the output power.
+The nonlinearity must immediately follow the gain---this is the section of the cavity where the pulse is most energetic, and hence, has the largest effect.
+Note, the permutation of the other components is indeed important as the operators do not, in general, commute---this is in contrast to the models described in Section \ref{sec:discrete}.
+Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.
 Functionally we denote one round trip of the cavity by
@@
 \end{align}
- The pulse after one complete circuit of the laser cavity is then returned back into cavity to restart the process.
+ The pulse after one complete circuit of the laser cavity is then returned back into the cavity to restart the process.
 A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase.
@@
 \section{Linear Solution}
-In the case $b = 0$ a solution can be found analytically.
-We expect the solution will have the form of a Gaussian.
+By neglecting the effoct of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
+We assume the solution will have the form of a chirped Gaussian.
 There are a few reasons for this; the solution to the models presented in \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn}.
@@
 This form is chosen because it resembles the envelope and linear chirping found by experiment ***cite.
-Having neglected the effect of the nonlinearity $\mathcal{L}(A)$ can be found analytically from the process mappings \eqref{eq:effects}.
-By assuming the pulse in \eqref{eq:A0} is in equilibrium, we find that the variance must satisfy
+
+To compute $\mathcal{F}(A)$, given the initial pulse \eqref{eq:A0}, we iteratively compute the effect of each process map from \eqref{eq:effects}.
+Now, by equating $\mathcal{F}(A)$ and $A \textrm{e}^{i \phi}$ we obtain a system of equations.
+In particular,
 \begin{align}
-	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0.
-	\label{eq:var}
+	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
+	C = .
+	\label{eq:chirp}
 \end{align}
-As this expression is a quartic in $\sigma^2$ it has an analytic solution, namely,
+
+As \eqref{eq:var} is a quartic in $\sigma^2$ it has an analytic solution, namely,
 \begin{equation}
@@
 		\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} & \\
-		- s^4 - s^2 & \sqrt{4 + s^4}.
+		- s^4 - s^2 & \sqrt{4 + s^4},
 		\label{eq:equilvar}
@@
 \end{equation}
-Moreover, by asymptotically expanding \eqref{eq:var} we find the useful relations
+which can readily be used to find the chirp, $C$. By asymptotically expanding \eqref{eq:var} we find the useful relations
 \begin{align}
@@
 		2s(1 - s) + \bigO{s^3} & s \rightarrow 0 \\
-		1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty.
-	\end{cases}
-\end{align}
-Additionally, from the variance we can determine the behaviour of the chirp to be
-\begin{align}
+		1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty,
+	\end{cases} \\
 	C &\sim
@@
 \end{align}
-The equilibrium energy and peak power can be computed from \label{eq:energy} to give
+The equilibrium energy and peak power can be found by conservation of energy to give
 \begin{align}

### 2020-01-19 Papers/Journal/Tuneable_Lasers.tex
Inverted colour scheme

@@
 Tuneable lasers simultaneously lase at all frequencies within this bandwidth.
-This tuneability leads to applications in spectroscopy and high resolution imaging, such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
+This tuneability leads to applications in spectroscopy and high resolution imaging, such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultrafast processes \cite{silfvast}.
 A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.
@@
 In particular,
-\begin{align}
+\begin{gather}
 	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
-	C = .
+	C = \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
 	\label{eq:chirp}
-\end{align}
+\end{gather}
 

### 2020-02-06 Papers/Journal/Tuneable_Lasers.tex
Fixed spacing in derivatives
Added introduction on wave breaking and modulation instability

@@
 \providecommand{\df}{\textrm{d}}
-\newcommand{\diff}[3][]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
-\newcommand{\pdiff}[3][]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
+\newcommand{\diff}[3][\hspace{-0.5pt}]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
+\newcommand{\pdiff}[3][\hspace{-0.5pt}]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
 \newcommand{\Es}{E_{\textrm{sat}}}
@@
 \newcommand{\Her}[2]{\widetilde{H}_{#1} \left( #2 \right)}
+\DeclareMathOperator{\sech}{sech}
 %\newcommand{\eps}{\varepsilon}
@@
 \label{sec:intro}
-A tuneable laser has the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun, burgoyne2010, yamashita}.
+A tuneable laser has the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009}.
 Tuneable lasers simultaneously lase at all frequencies within this bandwidth.
-This tuneability leads to applications in spectroscopy and high resolution imaging, such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultrafast processes \cite{silfvast}.
+This tuneability leads to applications such as optical coherence tomography \cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy \cite{burgoyne2014}, deep tissue multi-photon microscopy \cite{chung2017, liu2017}, and diagnostics of ultrafast processes \cite{burgoyne2014, silfvast2004}.
 A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.
 
-\subsection{Wave Breaking}
+The nonlinearity causes several effects to arise within the laser cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
+The effect of most interest for this paper is optical wave breaking which causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted\footnote{In a normally dispersive optical fibre.} to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+The frequency shifts cause the pulse to become rectangular in the frequency domain with a linear chirp over most of the pulse.
+Wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the nonlinearity in which the pulse interferes with itself.
+This interference generates new frequencies which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
+Modulation instablility is another effect that will be of interest that typically arises in the anomolous dispersion regime.
+However, in the presence of multiple pulses modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation (XPM) and four-wave mixing (FWM) \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
+Modulation instability causes a wave to break into short pulses, and can cause a laser to lose mode-locking \cite{agrawal1987, coen1997, haelterman1992}.
+Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
+This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable \cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
 
-\subsection{Modelling Efforts}
+\section{Modelling Efforts}
 \label{sec:modelling}
@@
 Here $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
-In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification, loss, and occasionally higher order terms.
-These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun, finot, peng, shtyrina, yarutkina},
+In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss\footnote{Occasionally higher order terms are added as well.}.
+These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking \cite{hausbook, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak},
+\begin{figure}[tbp]
+	\centering
+	\input{Cavity}
+	\caption{Typical cavity of a fibre ring tuneable laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
+	\label{fig:cavity}
+\end{figure}
+
+The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking \cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005},
 \begin{align}
@@
 \end{align}
-No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic \cite{hausbook, haus1975, haus1996}.
-However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak}.
+No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic \cite{haus1984, haus1975, haus1996}.
+However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
 Furthermore, see Haus \cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
-
-\begin{figure}[tbp]
-	\centering
-	\input{Cavity}
-	\caption{Typical cavity of a fibre based tuneable laser. The laser pulses travel clockwise around each loop.}
-	\label{fig:cavity}
-\end{figure}
 
@@
 
-Such a method was first proposed in 1955 by Cutler \cite{cutler} while analyzing a microwave regenerative pulse generator.
-This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman}.
+Such a method was first proposed in 1955 by Cutler \cite{cutler1955} while analyzing a microwave regenerative pulse generator.
+This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
 The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passively mode-locked lasers.
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{bohun, burgoyne2014, haus1975, hausbook, haus1992, haus2000, haus1991, kartner, peng, shtyrina, silfvast, usechak, yarutkina}.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{bohun2015, burgoyne2014, haus1975, haus1984, haus1992, haus2000, haus1991, kartner2005, peng2018, shtyrina2017, silfvast2004, usechak2005, yarutkina2013}.
 This leads to
@@
 	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
+	\label{eq:modform}
 \end{align}
 where $T_M$ is the characteristic width of the modulation.
+This assumption is not particularly restrictive.
+Calcaterra and Boldt have shown that Gaussians can form a basis for $L^2(\mathbb{R})$ \cite{calcaterra2008a}.
+Therefore, we can approximate any modulation function in $L^2(\mathbb{R})$ by a sum of \eqref{eq:modform}.
 
@@
 which characterize the behaviour of the laser.
-Nominal values for the parameters, \eqref{eq:ndparam}, can be found in \cite{agrawal2002, agrawal2013, bohun, burgoyne2014, burgoyneemail, finot, li, litchinitser, peng, shtyrina, tamura1993, tamura1996, tomlinson, usechak, yamashita, yarutkina}.
+Nominal values for the parameters, \eqref{eq:ndparam}, can be found in \cite{agrawal2002, agrawal2013, bohun2015, burgoyne2014, burgoyneemail, finot2008, li1998, litchinitser1997, peng2018, shtyrina2017, tamura1993, tamura1996, tomlinson1984, usechak2005, yamashita2009, yarutkina2013}.
 Notice that the modulation is only characterized by $T_M$, and each other process has its own associated independent non-dimensional parameter.
@@
 \section{Results}
+We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section \ref{sec:nlresults} we look at the full nonlinear model.
 
 \subsection{Linear Solution}
-
-\subsection{Nonlinear Solution and Wave Breaking}
-
-\section{Conclusion}
-
-\clearpage
-\newpage
-
-\section{Linear Solution}
-By neglecting the effoct of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
-We assume the solution will have the form of a chirped Gaussian.
-There are a few reasons for this; the solution to the models presented in \cite{cutler, siegman, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn}.
+By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
+We assume the solution will take the form of a chirped Gaussian.
+There are a few reasons for this; the solution to the models presented in \cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn2007}.
+Furthermore, this form is chosen because it resembles the envelope and linear chirp expected \cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
-This form is chosen because it resembles the envelope and linear chirping found by experiment ***cite.
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase. This pulse shape is depicted in Figure \ref{fig:samplegauss}.
+
+\begin{figure}[tbp]
+	\includegraphics{Sample_Gauss}
+	\caption{Solution to the linear model given by \eqref{eq:A0}.}
+	\label{fig:samplegauss}
+\end{figure}
 
@@
 
-\section{Nonlinear Solution}
-We now consider the nonlinear case---when $b > 0$.
-In this case it becomes impossible to obtain an analytic result.
-Recall from \eqref{eq:effects} that the nonlinearity is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone this transformation is futile.
-Instead we resort to a numerical solution.
+Our linearized model indeed exhibits the same form as previous linear models.
+However, by including the effects of the nonlinearity we uncover the rich interplay between dispersion, modulation, and nonlinearity not previously found mathematically.
 
-With the inclusion of the nonlinearity we generally find a similar solution to the linear case. An example of this is shown in Figure \ref{fig:nlstable}.
+\subsection{Nonlinear Solution and Instability}
+\label{sec:nlresults}
 
-Instead, the magnitude of the Fourier transform has a unique weakly bi-modal shape.
-This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---a key observation in the coming subsections.
-Finally, we shall examine the derivative of the phase---essentially the chirp.
+In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
+The most common form is a hyperbolic secant \cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+\begin{align}
+	A_0 = \Gamma \sech \left( 2 T \right) \textrm{e}^{i \pi / 4},
+\end{align}
+where $\Gamma$ is a normalizing factor chosen so the pulse has an initial energy of $E_0 = 0.1$.
 
- In the nonlinear case, we recover this linear response for moderate values of $T$.
-However, for $|T| > 1$ the chirp begins to saturate.
-This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
+xpm \cite{agrawal2013, agrawal1987, agrawal1989}
 
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{ParamSpaceErr}
+	\caption{}
+	\label{fig:error}
+\end{figure}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{ParamSpaceEnergy}
+	\caption{}
+	\label{fig:}
+\end{figure}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{ParamSpaceEnergySwitch}
+	\caption{}
+	\label{fig:energyswitch}
+\end{figure}
+
+\section{Conclusion}
+
+\clearpage
+\newpage
+
+\section{Nonlinear Solution}
+We now consider the nonlinear case---when $b > 0$.
+In this case it becomes impossible to obtain an analytic result.
+Recall from \eqref{eq:effects} that the nonlinearity is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone this transformation is futile.
+Instead we resort to a numerical solution.
+
+With the inclusion of the nonlinearity we generally find a similar solution to the linear case. An example of this is shown in Figure \ref{fig:nlstable}.
+
+Instead, the magnitude of the Fourier transform has a unique weakly bi-modal shape.
+This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---a key observation in the coming subsections.
+Finally, we shall examine the derivative of the phase---essentially the chirp.
+
+ In the nonlinear case, we recover this linear response for moderate values of $T$.
+However, for $|T| > 1$ the chirp begins to saturate.
+This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
+
 The noise in the energy exhibited for moderate to large values of $b$, and small values of $s$ is a phenomenon called \emph{wave breaking} \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}.
@@
 Once the pulse has reached a state such as this, the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics{ParamSpaceErr}
-	\caption{}
-	\label{fig:error}
-\end{figure}
-
-\begin{figure}[htbp]
-	\centering
-	\includegraphics{ParamSpaceEnergy}
-	\caption{}
-	\label{fig:}
-\end{figure}
 

### 2020-03-20 Papers/Journal/Tuneable_Lasers.tex
Added plot to paper

@@
 \label{sec:intro}
-A tuneable laser has the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009}.
-Tuneable lasers simultaneously lase at all frequencies within this bandwidth.
+Tuneable lasers have the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009} and simultaneously lase at all frequencies within this bandwidth in short pulses.
 This tuneability leads to applications such as optical coherence tomography \cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy \cite{burgoyne2014}, deep tissue multi-photon microscopy \cite{chung2017, liu2017}, and diagnostics of ultrafast processes \cite{burgoyne2014, silfvast2004}.
-A typical tuneable ring laser cavity is shown in Figure \ref{fig:cavity}.
+Tuneable lasers are usually constructed in a ring with five components: an output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and a pump laser.
+A typical tuneable ring laser cavity is depicted in Figure \ref{fig:cavity}.
+Due to the high power and short duratino of the pulses, the Kerr nonlinearity becomes crucial to the dynamics within the cavity.
 
 The nonlinearity causes several effects to arise within the laser cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
-The effect of most interest for this paper is optical wave breaking which causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted\footnote{In a normally dispersive optical fibre.} to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
-The frequency shifts cause the pulse to become rectangular in the frequency domain with a linear chirp over most of the pulse.
-Wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the nonlinearity in which the pulse interferes with itself.
+The effect of most interest for this paper is optical wave breaking which causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted\footnote{In the anomalous dispersion regime, the effect is reversed.} to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+The shift in frequencies cause the pulse to become rectangular in the frequency domain with a linear chirp over most of the pulse.
+Wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the nonlinearity causing the pulse to interfere with itself.
 This interference generates new frequencies which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
-Modulation instablility is another effect that will be of interest that typically arises in the anomolous dispersion regime.
+Modulation instablility is another effect that will be of interest that typically arises in the anomalous dispersion regime.
 However, in the presence of multiple pulses modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation (XPM) and four-wave mixing (FWM) \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
-Modulation instability causes a wave to break into short pulses, and can cause a laser to lose mode-locking \cite{agrawal1987, coen1997, haelterman1992}.
+Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence \cite{agrawal1987, coen1997, haelterman1992}.
 Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
 This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable \cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
+
+*** Paragraph explaining method / results / layout
 
@@
 As highlighted by Figure \ref{fig:cavity}, this can be a poor assumption.
-Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the chirped fibre Bragg grating (CFBG) \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
-Thus, a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
-Each of the blocks can then be functionally composed together to give an iterative map for the effect of one round trip of the cavity.
-This ultimately transforms the differential equation into an algebraic equation.
+Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
+Thus, a better model is one where we consider a simplified version of the master equation, \eqref{eq:meml}, for each component.
+Solving these simplified differential equations yields an algebraic expression for the effect of each individual component.
+The relations can then be functionally composed to give an iterative map for the effect of one round trip of the cavity.
 
@@
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, none of these previous models have been able to exhibit wave breaking.
+Finally, none of these previous models have been able to fully exhibit the instabilities described in Section \ref{sec:intro}.
 
@@
 Using the idea of a discrete model presented Section \ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
-To accomplish this, we neglect all terms but one of the right side of \eqref{eq:nlse} and solve the simplified differential equation.
-This is a reasonable assumption since the gain, loss, dispersion, modulation, and nonlinear effects are localized to only one section of the laser cavity.
+To accomplish this we follow the method described in Section \ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
 
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{bohun2015, burgoyne2014, haus1975, haus1984, haus1992, haus2000, haus1991, kartner2005, peng2018, shtyrina2017, silfvast2004, usechak2005, yarutkina2013}.
-This leads to
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{haus1984, shtyrina2017, silfvast2004}.
+This reduces the GNLSE, \eqref{eq:nlse}, to
+\begin{align}
+	\pdiff{A}{z} &= \frac{g_0 A}{2 \left( 1 + E / \Es \right)}.
+\end{align}
+By assuming $E(0) = E$ and $E(L_g) = E_{\text{out}}$, we find the energy after amplification is
+\begin{align}
+	\label{eq:engain}
+	E_{\text{out}} &= \Es W \left( \frac{E}{\Es} \textrm{e}^{E / \Es} \textrm{e}^{g_9 L_g} \right),
+\end{align}
+where $W$ is the Lambert $W$ function \cite{corless1996}. Rewriting \eqref{eq:engain} in terms of the pulse gives
 \begin{align}
@@
 \end{align}
-for the amplification of the pulse within the Er-doped fibre. Continuing this process for the loss, dispersion, and nonlinearity yields
+for the amplification of the pulse within the Er-doped fibre. Repeating this process for the loss, dispersion, and nonlinearity yields
 \begin{align}
@@
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
-In Figure \ref{fig:cavityevo} we can see an example of the evolution of the envelope of the pulse during one round trip of the cavity.
+An example of the evolution of the envelope during one round trip of the laser cavity can be found in Figure \ref{fig:cavityevo}.
 
@@
 	A_0 = \Gamma \sech \left( 2 T \right) \textrm{e}^{i \pi / 4},
+	\label{eq:nlA0}
 \end{align}
-where $\Gamma$ is a normalizing factor chosen so the pulse has an initial energy of $E_0 = 0.1$.
+where $\Gamma$ is a normalizing factor chosen so the pulse has an initial energy of $E_0 = 0.1$, unless specified otherwise.
+We plot the evolution of a pulse through the cavity in Figure \ref{fig:evolution}.
+We find very different behaviour in these two examples despite very similar parameters.
+In Figure \ref{fig:convevo} the input pulse is very noisy, but, sheds off the left lobe and reaches an equilibrium state quickly after.
+In the opposite extreme, Figure \ref{fig:breakevo} has the smooth initial pulse given in \eqref{eq:nlA0}, however, the nonlinearity causes the pulse to pulsate or `breathe'.
+This effect compounds with each round trip, which ultimately results in the degradation of the pulse into an unusable and unrecoverable state.
+The only difference between these two realizations, besides the initial pulse shape, is the value of the nonlinearity parameter, $b$.
 
-xpm \cite{agrawal2013, agrawal1987, agrawal1989}
+stability
+
+instability
+
+energy
+
+error
+
+permutation
+
+chirp / chirp Saturation
+
+shape / kurtosis
 
@@
 		\includegraphics{Conv}
-		\caption{Example of a pulse stabilizing from a seemingly random initial pulse shape ($s = 0.1$, $b = 1.0$, $E_0 = 0.1$, $a = 8000$, $h = 0.04$).}
+		\caption{Example of a pulse stabilizing from a seemingly random initial pulse shape ($b = 1.0$).}
 		\label{fig:convevo}
@@
 		\includegraphics{Break}
-		\caption{Example of a pulse destabilizing from a hyperbolic secant initial pulse ($s = 0.1$, $b = 1.6$, $E_0 = 0.1$, $a = 8000$, $h = 0.04$).}
+		\caption{Example of a pulse destabilizing from a hyperbolic secant initial pulse ($b = 1.6$).}
 		\label{fig:breakevo}
 	\end{subfigure}
-	\caption{Two extremes of the evolution of a pulse.}
+	\caption{Two extremes of the evolution of a pulse ($s = 0.1$, $E_0 = 0.1$, $a = 8000$, $h = 0.04$).}
 	\label{fig:evolution}
+\end{figure}
+
+\newpage
+
+In the nonlinear case, we recover this linear response for moderate values of $T$.
+However, for $|T| > 1$ the chirp begins to saturate.
+This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
+
+Wave breaking is not limited to just optics; wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
+Wave breaking occurs because the pulse begins to interfere with itself in a way called SPM \cite{agrawal2002, agrawal2013, becker}.
+SPM occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
+This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson},
+
+We obtain comparable results as in the experiments \cite{anderson, rothenberg}
+
+To obtain a better understanding of how the pulse either converges to equilibrium, or diverges to wave breaking, we shall examine the difference between the envelopes of consecutive iterations.
+More precisely, we compute the error by
+\begin{align}
+	\textrm{E} = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
+	\label{eq:error}
+\end{align}
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{18}$).
+
+he standard method would be to iterate until a fixed tolerance is reached, however, there are some reasons that make a fixed number of iterations preferable---as long as a sufficient number is chosen.
+The main reason is that this allows us to observe a richer structure than simply whether or not the tolerance had been reached by some maximum number of iterations.
+Additionally, incorrectly choosing the critical tolerance could easily lead to erroneous categorizations at points.
+
+The last item we wish to consider is the order in which the components are placed.
+
+xpm \cite{agrawal2013, agrawal1987, agrawal1989}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{ChirpFT}
+	\caption{}
+	\label{fig:chirpft}
 \end{figure}
@@
 
-\clearpage
-\newpage
-
-\section{Nonlinear Solution}
-We now consider the nonlinear case---when $b > 0$.
-In this case it becomes impossible to obtain an analytic result.
-Recall from \eqref{eq:effects} that the nonlinearity is a highly nonlinear operator, and attempting to compute the Fourier transform analytically of a pulse that has undergone this transformation is futile.
-Instead we resort to a numerical solution.
-
-With the inclusion of the nonlinearity we generally find a similar solution to the linear case. An example of this is shown in Figure \ref{fig:nlstable}.
-
-Instead, the magnitude of the Fourier transform has a unique weakly bi-modal shape.
-This deviation suggests the nonlinearity implants higher frequency oscillations into the pulse---a key observation in the coming subsections.
-Finally, we shall examine the derivative of the phase---essentially the chirp.
-
- In the nonlinear case, we recover this linear response for moderate values of $T$.
-However, for $|T| > 1$ the chirp begins to saturate.
-This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
-
-The noise in the energy exhibited for moderate to large values of $b$, and small values of $s$ is a phenomenon called \emph{wave breaking} \cite{agrawal2013, anderson, finot, rothenberg, tomlinson}.
-Wave breaking is not limited to just optics; wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
-Wave breaking occurs because the pulse begins to interfere with itself in a way called SPM \cite{agrawal2002, agrawal2013, becker}.
-SPM occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
-This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson}, as we saw in Figure \ref{fig:nlstable}.
-These high frequencies compound with each trip around the cavity becoming parasitic very quickly---Figure \ref{fig:break} highlights this.
-Notice that the difference between Figure \ref{fig:nlstable} and Figure \ref{fig:break} is a difference in $b$ of $0.05$---just enough to cross the boundary---this difference could be attributed to adding a few centimetres more of fibre between the gain and output coupler.
-\\
-
-The left figures show the pulse after 11 trips around the cavity; in the Fourier transform it is clear that the contributions from higher frequencies has increased.
-We obtain comparable results as in the experiments \cite{anderson, rothenberg}.
-Additionally, the chirp starts losing its linearity causing it to start becoming unstable; the nature of this instability is again in agreement with the experiments \cite{anderson, rothenberg}.
-The parasitic nature of the high frequency contributions is evident by examining the right figures.
-After five additional trips around the cavity, the envelope of the pulse is much more rippled, and the real and imaginary parts become incoherent.
-Moreover, the Fourier transform has no clear structure and has essentially become noise.
-The chirp has grown to be highly oscillatory and unstable.
-Once the pulse has reached a state such as this, the envelope, Fourier transform, and chirp never reach a steady equilibrium state.
-
-To obtain a better understanding of how the pulse either converges to equilibrium, or diverges to wave breaking, we shall examine the difference between the envelopes of consecutive iterations.
-More precisely, we compute the error by
-\begin{align}
-	\textrm{E} = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
-	\label{eq:error}
-\end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{18}$).
-Notice as well that in the numerator we use the modulus of the pulses, again this is because we are uninterested in the phase shift between iterations.
-A plot of the error can be found in Figure \ref{fig:error}, with $i = 100$.
-The standard method would be to iterate until a fixed tolerance is reached, however, there are some reasons that make a fixed number of iterations preferable---as long as a sufficient number is chosen.
-The main reason is that this allows us to observe a richer structure than simply whether or not the tolerance had been reached by some maximum number of iterations.
-Additionally, incorrectly choosing the critical tolerance could easily lead to erroneous categorizations at points.
-
-Unsurprisingly, the error is largest in the region where the wave breaks.
-As mentioned in the previous subsection, the pulse does not reach a stable state in this region.
-As a consequence the envelope varies drastically, which leads to this large error.
-
-The last item we wish to consider is the order in which the components are placed.
-In Section \ref{sec:effects} a brief description for the choice of the order was given.
-We start with the loss component since this coincides with the output; the fibre nonlinearity follows the gain since this is where it has the largest impact; and the loss follows the nonlinearity in an attempt to mitigate its effect.
-Therefore, the loss is first, and the gain followed by the nonlinearity are last---leaving dispersion and modulation in the middle.
-We chose to put the dispersion block ahead of the modulator.
-However, there was no real reason behind this---modulation before dispersion is equally as valid---and in this subsection we explore the effect of modulating the pulse before it passes through the CFBG.
-\\
-
-The result of this switch is shown in Figure \ref{fig:switch}.
-As a whole, unsurprisingly, we find the same behaviour and structure, however, there are some intriguing differences.
-Again, the structure and periodic nature of the boundary is similar to before, however, this boundary has shifted rightwards to a larger $s$ value.
-Additionally, within the unstable region the density of the contour lines is much greater---suggesting it is in some sense more chaotic and random than with the components in their original permutation.
-The final main difference between the two orderings, is that in this case the energy contours are no longer monotonic functions of $s$.
-Instead we find a parabolic shape on the top contour, and two lobes on the second contour.
-\\
-
-\section{Conclusion}
-Within this paper we developed a new nonlinear model for tuneable lasers.
-In order to better represent the underlying physics within the laser cavity the nonlinear Schr\"{o}dinger equation was reduced to simpler differential equations for each component of the laser.
-This led to a functional map that defines the effect of each component on a particular input pulse.
-These processes were then composed together to give an iterative mapping of the whole laser cavity.
-In a future publication we shall show the results obtained by this iterative mapping as well as discuss the dynamics exhibited by this model---including wave-breaking---to predict the conditions under which the pulse is stable and sustainable.
-
 \bibliography{Ref}

### 2020-05-18 Papers/AMMCS_Proceedings/Tuneable_Lasers.tex
Fixed indentation
Added paragraph on split-step Fourier methods

@@
 
-\abstract*{
-A new nonlinear model is proposed for tuneable lasers.
-Using the generalized nonlinear Schr\"{o}dinger equation as a starting point, expressions for the transformations undergone by the pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity.
-These transformations are then composed to give the overall effect of one trip around the cavity.
-We examine the full nonlinear model which is solved numerically.
-A consequence of the nonlinear nature of this model is that it is able to exhibit wave breaking which prior models could not.
-We highlight the rich structure of the boundary of stability for a particular plane of the parameter space.
-}
-
 \abstract{
@@
 These transformations are then composed to give the overall effect of one trip around the cavity.
+This is in contrast to solving the generalized nonlinear Schr\"{o}dinger equation which treats the processes as continuous.
 }
@@
 This tuneability is quite useful and has applications in spectroscopy and high resolution imaging such as coherent anti-Stokes Raman spectroscopy and optical coherence tomography \cite{bohun, burgoyne2014, yamashita}, as well as communications and diagnostics of ultra fast processes \cite{silfvast}.
-A typical tuneable laser cavity is shown in Figure \ref{fig:cavity}.
+A typical tuneable laser cavity can be seen in Figure \ref{fig:cavity}.
 In contrast to a standard laser, a tuneable laser contains two additional components, namely, a chirped fibre Bragg grating (CFBG), and a modulator.
@@
 	\input{Cavity}
-\caption{Typical cavity of a fibre based tuneable laser. The laser pulses travel clockwise around each loop.}
+	\caption{Typical cavity of a fibre based tuneable laser. The laser pulses travel clockwise around each loop. The pulses iteratively pass through each component successively.}
 	\label{fig:cavity}
@@
 
-\section{Modelling Efforts}
+\section{Previous Modelling Efforts}
 \label{sec:modelling}
@@
 
-\subsection{Discrete Models}
-While the derivation of \eqref{eq:meml} is correct mathematically, it is not representative of what happens within the laser cavity.
-The issue with \eqref{eq:meml} is that it has been assumed each process affects the pulse continuously within the cavity.
+\subsection{Discrete Component Models}
+While the derivation of \eqref{eq:meml} is sound mathematically, it is not representative of what happens within the laser cavity.
+The issue with \eqref{eq:meml} is that it has been assumed each process affects the pulse continuously within the cavity; for example, the pulse is amplified regardless of if it is in the Erbium-doped fibre.
 As highlighted by Figure \ref{fig:cavity}, this is a rather poor assumption.
 Within the cavity each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
-Thus, perhaps a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
+Thus, a better model is one where \eqref{eq:meml} is broken down into the individual components giving the effect of each `block' of the cavity.
 Each of the blocks can then be functionally composed together to give an iterative map for the effect of one circuit around the cavity.
 This transforms the differential equation into an algebraic equation.
+%\begin{figure}[tbp]
+%	\centering
+%	\input{Block}
+%	\caption{Simplification of Figure \ref{fig:cavity}.
+Each component of the laser cavity has an associated functional operator.
+As a pulse transits around the cavity, the output of one functional operator becomes the input of the next.}
+%	\label{fig:block}
+%\end{figure}
 
@@
 This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
-In these models the effect of each block is described by a transfer function.
+In these models the effect of each component is described by a transfer function.
 
-Despite the development of these block style models, several short-comings exist.
+These discrete component models differ from the often used split-step Fourier method (see \cite{agrawal2013, taha1984}).
+The split-step Fourier method is a numerical technique used for solving nonlinear partial differential equations, such as \eqref{eq:smallnlse}.
+The method considers the linear and nonlinear terms separately and has a half integration step for both parts---in a manner similar to the leap-frog algorithm\footnote{Also known as velocity Verlet in molecular dynamics, the St\"{o}rmer method in astronomy, and further names in other areas \cite{hairer2006}.}.
+Therefore, in the case of the NLSE, the dispersion and nonlinearity are still treated as continuous processes.
+However, in discrete component models the entire effect of each component is computed at once and the output of one component becomes the input for the following component, instead of alternating between the components in small integration steps.
+In this way, discrete component models are able to account for the geometry of a laser cavity, and indeed altering the permutation of the components gives rise to different dynamics.
+
+Despite the development of discrete component models, several short-comings exist.
 The clearest is that none of these models have contained every block---either the nonlinearity or the modulation have been omitted.
-In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function correctly without the inclusion of all of the components.
+In the framework of tuneable lasers, each component plays a crucial role and the tuneable laser will not function correctly without the inclusion of all the components.
 Another key drawback is that the functional operations of some of the components used in their models are phenomenological.
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, none of these previous models have been able to exhibit a phenomena called \emph{wave-breaking} in which the self-phase modulation of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
+Finally, none of these previous models have been able to exhibit a phenomenon called \emph{modulation instability} in which the self-phase modulation of the pulse becomes too strong, distorting and damaging the wave until it ultimately becomes unstable and unsustainable.
 
@@
 \label{sec:newmodel}
-Using the ideas presented in the previous section of the prior functional models \cite{burgoyne2014, cutler, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, siegman} we shall derive a new model from \eqref{eq:nlse}---with the exception of the modulation in which we consider the exact functional form to be determined by the laser operator.
+Using the ideas presented in the previous section of the prior functional models \cite{burgoyne2014, cutler, kuizenga1970a, kuizenga1970b, kuizenga1970, martinez1984, martinez1985, siegman} we shall derive a new model from \eqref{eq:nlse}---with the exception of modulation in which we consider the exact functional form to be determined by the laser operator.
 
 \subsection{Components}
-We shall determine the effect each component has on the pulse by solving \eqref{eq:nlse} while only considering the dominant term within each section of the cavity.
+We shall determine the effect each component has on the pulse by solving \eqref{eq:nlse} while only considering the dominant term within each section of the cavity, and neglecting the others.
 
@@
 \end{align}
-where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit as the effect of the losses\footnote{Depending on the layout of the laser cavity the loss may take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$ instead.}.
+where $R$ is the reflectivity of the output coupler, and $L_T$ is the total length of the laser circuit, as the effect of the losses\footnote{Depending on the layout of the laser cavity the loss may take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$ instead.}.
 
@@
 \end{align}
-where $L_D$ is the length of the dispersive medium, and $\mathcal{F}$ denotes the Fourier transform.
+where $L_D$ is the characteristic length of the dispersive medium, and $\mathcal{F}$ denotes the Fourier transform.
 
@@
 Finally, the pulse travels through the gain fibre to be amplified, and then we consider the effect of the nonlinearity since this is the region where the power is maximal.
-Note that in general the functional operators of the components do not commute, and therefore the order of the components is indeed important---in contrast to the previous models.
+Note that in general the functional operators of the components do not commute, and therefore the order of the components is indeed important---in contrast to previous models.
 This is especially the case of dispersion as realized through the Fourier transform.
@@
 \section{Conclusion}
-Within this paper we developed a new nonlinear model for tuneable lasers.
+Within this paper we developed a nonlinear model for tuneable lasers.
 In order to better represent the underlying physics within the laser cavity the nonlinear Schr\"{o}dinger equation was reduced to simpler differential equations for each component of the laser.
@@
 These processes were then composed together to give an iterative mapping of the whole laser cavity.
-In a future publication we shall show the results obtained by this iterative mapping as well as discuss the dynamics exhibited by this model---including wave-breaking---to predict the conditions under which the pulse is stable and sustainable.
+In a future publication we shall show the results obtained by this iterative mapping as well as discuss the dynamics exhibited by this model---including modulation instability---to predict the conditions under which the pulse is stable and sustainable.
 

### 2020-11-15 Papers/Journal/Tuneable_Lasers.tex
Finished draft of nonlinear results

@@
 \usepackage{xcolor,graphicx}
-\usepackage[subfolder,cleanup]{gnuplottex}
+%\usepackage[subfolder,cleanup]{gnuplottex}
 %\usepackage{amsthm}
@@
 \usepackage{tikz}
-\RequirePackage{cite}
+\usepackage{cite}
 
@@
 A typical tuneable ring laser cavity is depicted in Figure \ref{fig:cavity}.
-Due to the high power and short duratino of the pulses, the Kerr nonlinearity becomes crucial to the dynamics within the cavity.
+Due to the high power and short duration of the pulses, the Kerr nonlinearity becomes crucial to the dynamics within the cavity.
 
 The nonlinearity causes several effects to arise within the laser cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
-The effect of most interest for this paper is optical wave breaking which causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted\footnote{In the anomalous dispersion regime, the effect is reversed.} to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+The two effects of most interest for this paper are optical wave breaking, and modulation instability.
+Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The shift in frequencies cause the pulse to become rectangular in the frequency domain with a linear chirp over most of the pulse.
-Wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the nonlinearity causing the pulse to interfere with itself.
+In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the nonlinearity causing the pulse to interfere with itself.
 This interference generates new frequencies which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
-Modulation instablility is another effect that will be of interest that typically arises in the anomalous dispersion regime.
+Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics \cite{rothenberg1989b}.
+Modulation instability is another effect that will be of interest that typically arises in the anomalous dispersion regime.
 However, in the presence of multiple pulses modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation (XPM) and four-wave mixing (FWM) \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
@@
 
-*** Paragraph explaining method / results / layout
+In Section \ref{sec:modelling}, we briefly review previous mathematical models for the evolution of laser pulses, then we derive our own model in Section \ref{sec:model}.
+We then examine the results of our model in Section \ref{sec:results}---first solving the model analytically assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+Finally, the concluding thoughts and possible directions of future work are given in Section \ref{sec:conclusion}.
 
@@
 Here $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
-In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss\footnote{Occasionally higher order terms are added as well.}.
+In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (occasionally higher order terms are added as well).
 These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
@@
 \end{align}
-where $R$ is the reflectivity of the output coupler\footnote{Depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$.}, $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and where $\mathcal{F}$ denotes the Fourier transform.
+where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and where $\mathcal{F}$ denotes the Fourier transform.
 Finally, we must assume a form for the modulation.
@@
 	\mathcal{L}(A) = F(G(M(D(L(A))))).
+	\label{eq:order}
 \end{align}
@@
 \section{Results}
+\label{sec:results}
 We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section \ref{sec:nlresults} we look at the full nonlinear model.
@@
 \begin{figure}[tbp]
+	\centering
 	\includegraphics{Sample_Gauss}
@@
 \label{sec:nlresults}
-
 In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
@@
 where $\Gamma$ is a normalizing factor chosen so the pulse has an initial energy of $E_0 = 0.1$, unless specified otherwise.
-We plot the evolution of a pulse through the cavity in Figure \ref{fig:evolution}.
-We find very different behaviour in these two examples despite very similar parameters.
-In Figure \ref{fig:convevo} the input pulse is very noisy, but, sheds off the left lobe and reaches an equilibrium state quickly after.
-In the opposite extreme, Figure \ref{fig:breakevo} has the smooth initial pulse given in \eqref{eq:nlA0}, however, the nonlinearity causes the pulse to pulsate or `breathe'.
-This effect compounds with each round trip, which ultimately results in the degradation of the pulse into an unusable and unrecoverable state.
-The only difference between these two realizations, besides the initial pulse shape, is the value of the nonlinearity parameter, $b$.
 
-stability
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{ChirpFT}
+	\caption{Chirp and Fourier transform in equilibrium state obtained by \eqref{eq:nlA0}, with values $a = 8 \times 10^3$, $h = 0.04$, $b = 1$, $s = 0.2$, and $E_0 = 0.1$.}
+	\label{fig:chirpft}
+\end{figure}
 
-instability
+In Figure \ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
+In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transform.
+Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity.
+Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with experimental results \cite{chen2008, rothenberg1989b, tomlinson1985}.
+As the nonlinearity parameter, $b$, is increased, the two lobes in the Fourier transform become more pronounced.
+However, once a critical point is reached SPM begins to play a more substantial factor, leading to modulation instability.
+This phenomenon is highlighted in Figure \ref{fig:breakevo}.
+By increasing the nonlinearity, and decreasing the dispersion we find the pulse begins to `breathe'.
+During the first two dozen round trips of the cavity, the SPM compounds and becomes too parasitic to the pulse.
+This in turn induces modulation instability, and degrades the pulse, making the pulse no longer stable or sustainable.
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable initial pulse (Figure \ref{fig:convevo}).
+The pulse is able to shed the initial left lobe because of dispersion and modulation, and the central lobe is able to grow due to the gain medium.
+This allows the pulse to come to equilibrium very quickly.
+Furthermore, since the intensity of the initial pulse is relatively small, the effect of SPM is negligible during the first few round trips which allows the laser to select preferable modes.
+These preferable modes then get amplified which stabilizes the pulse.
+From this, it is clear the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
 
-energy
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Break}
+	\caption{Example of a pulse destabilizing from the initial pulse \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.6$, $s = 0.1$, and $E_0 = 0.1$).}
+	\label{fig:breakevo}
+\end{figure}
 
-error
-
-permutation
-
-chirp / chirp Saturation
-
-shape / kurtosis
-
-\begin{figure}[tb]
-	\centering
-	\begin{subfigure}{\columnwidth}
+\begin{figure}[tbp]
 	\centering
 	\includegraphics{Conv}
-		\caption{Example of a pulse stabilizing from a seemingly random initial pulse shape ($b = 1.0$).}
+	\caption{Example of a pulse coming to equilibrium from noise ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.1$, and $E_0 = 0.1$).}
 	\label{fig:convevo}
-	\end{subfigure} \\
-	\begin{subfigure}{\columnwidth}
-		\centering
-		\includegraphics{Break}
-		\caption{Example of a pulse destabilizing from a hyperbolic secant initial pulse ($b = 1.6$).}
-		\label{fig:breakevo}
-	\end{subfigure}
-	\caption{Two extremes of the evolution of a pulse ($s = 0.1$, $E_0 = 0.1$, $a = 8000$, $h = 0.04$).}
-	\label{fig:evolution}
 \end{figure}
 
-\newpage
-
-In the nonlinear case, we recover this linear response for moderate values of $T$.
-However, for $|T| > 1$ the chirp begins to saturate.
-This is consistent with the experimental results \cite{chen, rothenberg, tomlinson}.
-
-Wave breaking is not limited to just optics; wave breaking occurs in areas such as plasmas, transmission lines, and fluid dynamics \cite{rothenberg}.
-Wave breaking occurs because the pulse begins to interfere with itself in a way called SPM \cite{agrawal2002, agrawal2013, becker}.
-SPM occurs because the index of refraction is intensity dependent \cite{agrawal2002, becker, rothenberg, silfvast}, which leads to additional chirp across the pulse \cite{agrawal2013, anderson, rothenberg, silfvast}.
-This in turn causes higher order frequencies to be injected into the pulse \cite{agrawal2013, anderson},
-
-We obtain comparable results as in the experiments \cite{anderson, rothenberg}
-
-To obtain a better understanding of how the pulse either converges to equilibrium, or diverges to wave breaking, we shall examine the difference between the envelopes of consecutive iterations.
-More precisely, we compute the error by
+We now turn our attention to characterizing the stability of a laser by exploring the parameter space.
+We focus on the $s$--$b$ plane in particular since $a$ and $h$ effect only the amplitude of the pulse and do not contribute to the interplay of dispersion and the nonlinearity.
+Additionally, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while coming to equilibrium.
+To identify the stability of a pulse we examine the relative change in the pulse's envelope between consecutive iterations.
+We compute this error by
 \begin{align}
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, which is computed numerically using the trapezoid rule ($N = 2^{18}$).
-
-he standard method would be to iterate until a fixed tolerance is reached, however, there are some reasons that make a fixed number of iterations preferable---as long as a sufficient number is chosen.
-The main reason is that this allows us to observe a richer structure than simply whether or not the tolerance had been reached by some maximum number of iterations.
-Additionally, incorrectly choosing the critical tolerance could easily lead to erroneous categorizations at points.
-
-The last item we wish to consider is the order in which the components are placed.
-
-xpm \cite{agrawal2013, agrawal1987, agrawal1989}
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{ChirpFT}
-	\caption{}
-	\label{fig:chirpft}
-\end{figure}
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 250$ in our experiments (Figure \ref{fig:error}).
+Note that we take the modulus of the pulse since we are only interested in the evolution of the envelope.
+We find a very sharp and rich boundary between two regions.
+In the upper-left region the error is $\bigO{1}$, this is where the nonlinearity is too strong, and the SPM induces modulation instability.
+In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable.
+The error is on the order of machine precision, or slightly higher due to approximating a smooth continuous function by discrete points.
 
@@
 	\includegraphics{ParamSpaceErr}
-	\caption{}
+	\caption{Relative error of a pulse's envelope between round trips 249 and 250 ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
 	\label{fig:error}
 \end{figure}
+
+Also of interest is the energy of the pulse at equilibrium. We compute the energy using \eqref{eq:energy}, or equivalently 
+\begin{align}
+	E &= \| A_i \|_2,
+	\label{eq:energy2norm}
+\end{align}
+where, again, $i = 250$ in our experiments.
+Recall from \eqref{eq:order}, this energy is the immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is instead $(1 - h^2) \| A_i \|_2$, and $h^2 \| A_i \|_2$ remains in the cavity.
+We plot \eqref{eq:energy2norm} in Figure \ref{fig:energy}.
+Unsurprisingly, we find the same sharp boundary as we saw in Figure \ref{fig:error}.
+In the unstable region (upper-left) the energy is relatively small.
+Since the pulse is not stable in this region it is not able to foster prominent modes, thus, the intensity is low across the entire pulse.
+In the stable region (lower-right) we find that the energy smoothly decays as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
+From this it is clear that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
 
@@
 	\includegraphics{ParamSpaceEnergy}
-	\caption{}
-	\label{fig:}
+	\caption{Energy of the pulse after 250 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\label{fig:energy}
 \end{figure}
+
+Finally, we briefly look at how the order of the components effects the dynamics.
+In Section \ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
+Here we consider the effect of swapping the dispersion and modulation components.
+The energy landscape (Figure \ref{fig:energyswitch}) is as we would expect.
+In the previous case of having modulation following dispersion, more energy is removed from the pulse tails.
+Whereas, having modulation first, more of this energy remains in the cavity.
+This has the effect of making the laser more powerful, which in turn increases the unstable region.
+Comparing with Figure \ref{fig:energy}, this is what we find.
+The unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
 
@@
 	\includegraphics{ParamSpaceEnergySwitch}
-	\caption{}
+	\caption{Energy of the pulse after 250 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
 	\label{fig:energyswitch}
@@
 \section{Conclusion}
+\label{sec:conclusion}
+
+\section{Acknowledgement}
+BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling (EP/L015803/1).
 

### 2020-11-15 Papers/Journal/Tuneable_Lasers.tex
Added conclusion

@@
 \label{sec:conclusion}
+Expanding upon the ideas originally proposed by Cutler \cite{cutler1955}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear functional model for tuneable ring lasers.
+We recover linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
+Moreover, the solution of the linear model can easily be extended to any modulation function using results of \cite{calcaterra2008a}.
+In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
+This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has difficult to predict with mathematical models.
+Furthermore, it is of interest to analyze the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$.
+Doing so would provide insight to how the nonlinearity impacts the linearized solution to better understand the manifestation of wave breaking and modulation instability.
 
-\section{Acknowledgement}
+\section*{Acknowledgement.}
 BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling (EP/L015803/1).
+
+\section*{Disclosures.}
+The authors declare no conflicts of interest.
 

### 2020-11-15 Papers/Journal/Tuneable_Lasers.tex
Added abstract and title

@@
 
-\title{}
+\title{Predicting stability of a tuneable ring laser with an iterative model}
 \author{B. Metherall \and C. S. Bohun}
@@
 		\begin{abstract}
-
+			We propose a nonlinear iterative map for tuneable ring lasers.
+Using the generalized nonlinear Schr\"odinger equation, expressions for the transformations undergone by the laser pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity.
+These transformations are then iteratively composed to give the overall effect of one round trip of the cavity.
+We first examine the linear version of the model which we solve analytically.
+Then the full nonlinear model is investigated numerically.
+The nonlinear model is able to exhibit wave breaking as well as modulation instability.
+We highlight the rich landscape and sharp divide for a particular plane of the parameter space.
 		\end{abstract}
@@
 
+\begin{figure}[tbp]
+	\centering
+	\input{Cavity}
+	\caption{Typical cavity of a fibre ring tuneable laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
+	\label{fig:cavity}
+\end{figure}
+
 \section{Modelling Efforts}
@@
 where $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}^+$ is the loss due to scattering and absorption.
-
-\begin{figure}[tbp]
-	\centering
-	\input{Cavity}
-	\caption{Typical cavity of a fibre ring tuneable laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
-	\label{fig:cavity}
-\end{figure}
 

### 2020-11-18 Papers/Journal/Tuneable_Lasers.tex
Added journal style

@@
-\documentclass[10pt,twocolumn,a4paper]{article}
+\documentclass[9pt,twocolumn,twoside]{osajnl}
+%% Please use 11pt if submitting to AOP
+% \documentclass[11pt,twocolumn,twoside]{osajnl}
+
+\journal{josab} % Choose journal (ao, aop, josaa, josab, ol, optica, pr)
+
+% See template introduction for guidance on setting shortarticle option
+\setboolean{shortarticle}{false}
+% true = letter / tutorial
+% false = research / review article
+% (depending on journal).
 
@@
 \usepackage{amsmath}
-\usepackage{geometry}
 \usepackage{xcolor,graphicx}
-%\usepackage[subfolder,cleanup]{gnuplottex}
-%\usepackage{amsthm}
-%\usepackage{enumitem}
-%\usepackage{wrapfig}
-\usepackage{subcaption}
-%\usepackage{hyperref}
 \usepackage{tikz}
-\usepackage{cite}
+%\usepackage{cite}
 
@@
 \DeclareMathOperator{\sech}{sech}
-%\newcommand{\eps}{\varepsilon}
-%\newcommand{\rect}[1]{\textrm{rect}\left( #1 \right)}
 
@@
 
-\newgeometry{margin=1.25cm}
+\title{Predicting stability of a tuneable ring laser with an iterative model}
 
-\bibliographystyle{ieeetr}
+\author[1]{B. Metherall}
+\author[2,*]{C. S. Bohun}
 
-\title{Predicting stability of a tuneable ring laser with an iterative model}
-\author{B. Metherall \and C. S. Bohun}
+\affil[1]{Mathematical Institute, University of Oxford, Woodstock Rd, Oxford, UK}
+\affil[2]{University of Ontario Institute of Technology, 2000 Simcoe St, Oshawa, ON, Canada}
 
-\begin{document}
+\affil[*]{Corresponding author: sean.bohun@uoit.ca}
 
-\twocolumn[
-	\begin{@twocolumnfalse}
-		\maketitle
+%% To be edited by editor
+% \dates{Compiled \today}
+
+%\ociscodes{(140.3490) Lasers, distributed feedback; (060.2420) Fibers, polarization-maintaining;(060.3735) Fiber Bragg gratings.}
+
+%% To be edited by editor
+% \doi{\url{http://dx.doi.org/10.1364/XX.XX.XXXXXX}}
+
 \begin{abstract}
@@
 \end{abstract}
-	\end{@twocolumnfalse}
-]
+
+\setboolean{displaycopyright}{true}
+
+\begin{document}
+
+\maketitle
 
@@
 % Table of parameter values
-% \begin{table*}[tbp]
-% 	\centering
-% 	\begin{tabular}{lcll}
-% 		\hline\noalign{\smallskip}
-% 		Parameter & Symbol & Value & Sources \\
-% 		\hline\noalign{\smallskip}
-% 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina, tomlinson, usechak, yarutkina} \\
-% 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser, peng, yarutkina} \\
-% 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot, usechak, yarutkina} \\
-% 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li} \\
-% 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng, tamura1996} \\
-% 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
-% 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng, shtyrina, tamura1993, yarutkina} \\
-% 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun, burgoyneemail, burgoyne2014} \\
-% 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li, peng,  tamura1993, tamura1996, yamashita} \\
-% 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak, yarutkina} \\
-% 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina} \\
-% 		\noalign{\smallskip}\hline
-% 	\end{tabular}
-% 	\caption{Range of variation of various parameters.}
-% 	\label{tab:values}
-% \end{table*}
+ \begin{table*}[tbp]
+ 	\centering
+ 	\begin{tabular}{lcll}
+ 		\hline\noalign{\smallskip}
+ 		Parameter & Symbol & Value & Sources \\
+ 		\hline\noalign{\smallskip}
+ 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005, yarutkina2013} \\
+ 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser1997, peng2018, yarutkina2013} \\
+ 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot2008, usechak2005, yarutkina2013} \\
+ 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li1998} \\
+ 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng2018, tamura1996} \\
+ 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
+ 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng2018, shtyrina2017, tamura1993,yarutkina2013} \\
+ 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun2015, burgoyneemail, burgoyne2014} \\
+ 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li1998, peng2018,  tamura1993, tamura1996, yamashita2009} \\
+ 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak2005, yarutkina2013} \\
+ 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina2013} \\
+ 		\noalign{\smallskip}\hline
+ 	\end{tabular}
+ 	\caption{Range of variation of various parameters.}
+ 	\label{tab:values}
+ \end{table*}
 

### 2020-11-18 Papers/Journal/Tuneable_Lasers.tex
Updated some formatting

@@
 
-\author[1]{B. Metherall}
-\author[2,*]{C. S. Bohun}
+\author[1]{Brady Metherall}
+\author[2,*]{C. Sean Bohun}
 
-\affil[1]{Mathematical Institute, University of Oxford, Woodstock Rd, Oxford, UK}
-\affil[2]{University of Ontario Institute of Technology, 2000 Simcoe St, Oshawa, ON, Canada}
+\affil[1]{Mathematical Institute, University of Oxford, Radcliffe Observatory Quarter, Woodstock Rd, Oxford OX2 6GG, UK}
+\affil[2]{Facutlty of Science, University of Ontario Institute of Technology, 2000 Simcoe St N, Oshawa, ON L1G 0C5, Canada}
 
-\affil[*]{Corresponding author: sean.bohun@uoit.ca}
+\affil[3]{brady.metherall@maths.ox.ac.uk}
+\affil[4]{sean.bohun@uoit.ca}
 
@@
 Tuneable lasers are usually constructed in a ring with five components: an output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and a pump laser.
-A typical tuneable ring laser cavity is depicted in Figure \ref{fig:cavity}.
+A typical tuneable ring laser cavity is depicted in Fig.
+\ref{fig:cavity}.
 Due to the high power and short duration of the pulses, the Kerr nonlinearity becomes crucial to the dynamics within the cavity.
@@
 In the derivation of \eqref{eq:meml} it is assumed each process affects the pulse continuously within the cavity.
-As highlighted by Figure \ref{fig:cavity}, this can be a poor assumption.
+As highlighted by Fig.
+\ref{fig:cavity}, this can be a poor assumption.
 Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
@@
 	\centering
+	\caption{Range of variation of various parameters.}
+ 	\label{tab:values}
  	\begin{tabular}{lcll}
@@
  	\end{tabular}
- 	\caption{Range of variation of various parameters.}
- 	\label{tab:values}
  \end{table*}
@@
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
-An example of the evolution of the envelope during one round trip of the laser cavity can be found in Figure \ref{fig:cavityevo}.
+An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.
+\ref{fig:cavityevo}.
 
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase. This pulse shape is depicted in Figure \ref{fig:samplegauss}.
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase. This pulse shape is depicted in Fig. \ref{fig:samplegauss}.
 
@@
 
-In Figure \ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
+In Fig.
+\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
 In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transform.
@@
 However, once a critical point is reached SPM begins to play a more substantial factor, leading to modulation instability.
-This phenomenon is highlighted in Figure \ref{fig:breakevo}.
+This phenomenon is highlighted in Fig.
+\ref{fig:breakevo}.
 By increasing the nonlinearity, and decreasing the dispersion we find the pulse begins to `breathe'.
@@
 This in turn induces modulation instability, and degrades the pulse, making the pulse no longer stable or sustainable.
-On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable initial pulse (Figure \ref{fig:convevo}).
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable initial pulse (Fig.
+\ref{fig:convevo}).
 The pulse is able to shed the initial left lobe because of dispersion and modulation, and the central lobe is able to grow due to the gain medium.
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 250$ in our experiments (Figure \ref{fig:error}).
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 250$ in our experiments (Fig.
+\ref{fig:error}).
 Note that we take the modulus of the pulse since we are only interested in the evolution of the envelope.
@@
 Recall from \eqref{eq:order}, this energy is the immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is instead $(1 - h^2) \| A_i \|_2$, and $h^2 \| A_i \|_2$ remains in the cavity.
-We plot \eqref{eq:energy2norm} in Figure \ref{fig:energy}.
-Unsurprisingly, we find the same sharp boundary as we saw in Figure \ref{fig:error}.
+We plot \eqref{eq:energy2norm} in Fig.
+\ref{fig:energy}.
+Unsurprisingly, we find the same sharp boundary as we saw in Fig.
+\ref{fig:error}.
 In the unstable region (upper-left) the energy is relatively small.
@@
 Here we consider the effect of swapping the dispersion and modulation components.
-The energy landscape (Figure \ref{fig:energyswitch}) is as we would expect.
+The energy landscape (Fig.
+\ref{fig:energyswitch}) is as we would expect.
 In the previous case of having modulation following dispersion, more energy is removed from the pulse tails.
@@
 This has the effect of making the laser more powerful, which in turn increases the unstable region.
-Comparing with Figure \ref{fig:energy}, this is what we find.
+Comparing with Fig.
+\ref{fig:energy}, this is what we find.
 The unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.

### 2020-11-20 Papers/Journal/Tuneable_Lasers.tex
Added edits

@@
 
-\usepackage{amsfonts}
-\usepackage{amsmath}
-\usepackage{xcolor,graphicx}
 \usepackage{tikz}
-%\usepackage{cite}
 
@@
 
+% Fixes bracket spacing
 \let\originalleft\left
@@
 
-\providecommand{\df}{\textrm{d}}
-\newcommand{\diff}[3][\hspace{-0.5pt}]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
-\newcommand{\pdiff}[3][\hspace{-0.5pt}]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
-\newcommand{\Es}{E_{\textrm{sat}}}
-\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}}
-\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}}
-\newcommand{\Her}[2]{\widetilde{H}_{#1} \left( #2 \right)}
+\providecommand{\df}{\textrm{d}} % Roman d for differentials
+\newcommand{\diff}[3][\hspace{-0.5pt}]{\frac{\df^{#1}#2}{\df{#3}^{#1}}} % Derivatives
+\newcommand{\pdiff}[3][\hspace{-0.5pt}]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}} % Partial derivatives
+\newcommand{\Es}{E_{\textrm{sat}}} % Saturation energy
+\newcommand{\FT}[1]{\mathcal{F}\left\{ #1 \right\}} % Fourier transform
+\newcommand{\FTi}[1]{\mathcal{F}^{-1}\left\{ #1 \right\}} % Inverse Fourier transform
+
+\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}} % Big O notation
+
 \DeclareMathOperator{\sech}{sech}
 
-\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
-
-\title{Predicting stability of a tuneable ring laser with an iterative model}
+\title{Predicting instabilities of a tuneable ring laser with an iterative map model}
 
@@
 \label{sec:intro}
-Tuneable lasers have the ability to vary the frequency of its output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009} and simultaneously lase at all frequencies within this bandwidth in short pulses.
-This tuneability leads to applications such as optical coherence tomography \cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy \cite{burgoyne2014}, deep tissue multi-photon microscopy \cite{chung2017, liu2017}, and diagnostics of ultrafast processes \cite{burgoyne2014, silfvast2004}.
-Tuneable lasers are usually constructed in a ring with five components: an output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and a pump laser.
-A typical tuneable ring laser cavity is depicted in Fig.
+Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009}.
+This ability to vary the frequency leads to applications such as optical coherence tomography \cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy \cite{burgoyne2014}, deep tissue multi-photon microscopy \cite{chung2017, liu2017}, and diagnostics of ultrafast processes \cite{burgoyne2014, silfvast2004}.
+Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser.
+A typical ring laser cavity is depicted in Fig.
 \ref{fig:cavity}.
-Due to the high power and short duration of the pulses, the Kerr nonlinearity becomes crucial to the dynamics within the cavity.
+Due to the high power and short duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.
 
-The nonlinearity causes several effects to arise within the laser cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
-The two effects of most interest for this paper are optical wave breaking, and modulation instability.
+Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
+The two effects of most interest for this paper are wave breaking, and modulation instability.
 Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
-The shift in frequencies cause the pulse to become rectangular in the frequency domain with a linear chirp over most of the pulse.
-In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the nonlinearity causing the pulse to interfere with itself.
-This interference generates new frequencies which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
+The shifts in frequencies cause the pulse to become more rectangular in the frequency domain with a linear chirp over most of the pulse.
+In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself.
+New frequencies are then generated which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
 Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics \cite{rothenberg1989b}.
-Modulation instability is another effect that will be of interest that typically arises in the anomalous dispersion regime.
-However, in the presence of multiple pulses modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation (XPM) and four-wave mixing (FWM) \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
+Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
+However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
 Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence \cite{agrawal1987, coen1997, haelterman1992}.
@@
 	\input{Cavity}
-	\caption{Typical cavity of a fibre ring tuneable laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
+	\caption{Typical cavity of a fibre ring laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
 	\label{fig:cavity}
@@
 \end{align}
-Here $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
+Here, $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
 In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (occasionally higher order terms are added as well).
@@
 However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
-Furthermore, see Haus \cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
+See Haus \cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
 
@@
 Unfortunately, the master equation, \eqref{eq:meml}, is not completely representative of the underlying physics within our laser cavity.
-In the derivation of \eqref{eq:meml} it is assumed each process affects the pulse continuously within the cavity.
+It is assumed in \eqref{eq:meml} that each process affects the pulse continuously within the cavity.
 As highlighted by Fig.
 \ref{fig:cavity}, this can be a poor assumption.
-Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, etc.
-Thus, a better model is one where we consider a simplified version of the master equation, \eqref{eq:meml}, for each component.
+Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
+Thus, a better model is one where we consider a simplified version of \eqref{eq:meml} for each component.
 Solving these simplified differential equations yields an algebraic expression for the effect of each individual component.
@@
 Such a method was first proposed in 1955 by Cutler \cite{cutler1955} while analyzing a microwave regenerative pulse generator.
-This method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
-The effects of the nonlinearity would not be considered until Martinez, Fork, and Gordon \cite{martinez1984, martinez1985} tried modelling passively mode-locked lasers.
+His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
+The effects of the nonlinearity would not be considered until Martinez \emph{et al.} \cite{martinez1984, martinez1985} modelled passively mode-locked lasers.
 This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
@@
 
-Despite the development of these block style models, several short-comings exist.
-The clearest is that none of these models have contained every block---either the nonlinearity or the modulation have been omitted.
-Each component of a tuneable plays a crucial role and the laser will not function correctly without the inclusion of all of the components.
+Despite the development of discrete, block style models, several short-comings exist.
+None of the previous models have contained every component within a laser cavity---either the nonlinearity or the modulation have been omitted.
+Each component of a tuneable plays a pivotal role and the laser will not function correctly without the inclusion of all of the components.
 Another drawback is that the functional operations of some of the components used in their models are phenomenological.
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, none of these previous models have been able to fully exhibit the instabilities described in Section \ref{sec:intro}.
+Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section \ref{sec:intro}.
 
@@
 where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{haus1984, shtyrina2017, silfvast2004}.
-This reduces the GNLSE, \eqref{eq:nlse}, to
+This reduces \eqref{eq:nlse} to
 \begin{align}
@@
 \end{align}
-By assuming $E(0) = E$ and $E(L_g) = E_{\text{out}}$, we find the energy after amplification is
+By assuming the incoming energy is $E$ and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we find the energy after amplification is
 \begin{align}
 	\label{eq:engain}
-	E_{\text{out}} &= \Es W \left( \frac{E}{\Es} \textrm{e}^{E / \Es} \textrm{e}^{g_9 L_g} \right),
+	E_{\text{out}} &= \Es W \left( \frac{E}{\Es} \exp( E / \Es ) \exp( g_0 L_g ) \right),
 \end{align}
-where $W$ is the Lambert $W$ function \cite{corless1996}. Rewriting \eqref{eq:engain} in terms of the pulse gives
+where $W$ is the Lambert $W$ function. Rewriting \eqref{eq:engain} in terms of the pulse gives
 \begin{align}
-	G(A) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \textrm{e}^{E/\Es} \textrm{e}^{g_0 L_g} \right) \right)^{1/2} A
+	G(A) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \exp( E / \Es ) \exp( g_0 L_g ) \right) \right)^{1/2} A
+	\label{eq:gainform}
 \end{align}
@@
 \begin{align}
-	L(A) &= (1 - R) \textrm{e}^{- \alpha L_T}A, \\
-	D(A) &= \FTi{\textrm{e}^{i \omega^2 L_D\beta_2/2} \FT{A}}, \\
-	F(A) &= A \textrm{e}^{i \gamma |A|^2 L_f},
+	L(A) &= (1 - R) \exp( - \alpha L_T )A, \\
+	D(A) &= \FTi{\exp( i \omega^2 L_D\beta_2/2 ) \FT{A}}, \\
+	F(A) &= A \exp( i \gamma |A|^2 L_f ),
 \end{align}
-where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \textrm{e}^{- \alpha L_T}A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and where $\mathcal{F}$ denotes the Fourier transform.
-Finally, we must assume a form for the modulation.
+where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and $\mathcal{F}$ denotes the Fourier transform.
+Finally, we must consider the modulation.
 The modulation is considered to be applied externally in which ever way the operator sees fit.
@@
 \begin{align}
-	M(A) &= \textrm{e}^{-T^2 / 2 T_M^2} A,
+	M(A) &= \exp( -T^2 / 2 T_M^2 ) A,
 	\label{eq:modform}
@@
 \subsection{Non-Dimensionalization}
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude; this suggests the convenient scalings:
+The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
 \begin{align}
@@
 \end{align}
-Revisiting each process map shows each process has a characteristic non-dimensional parameter. The new mappings---after dropping the tildes---are
+Revisiting the process maps, \eqref{eq:gainform}--\eqref{eq:modform}, shows each process has a characteristic non-dimensional parameter. The new mappings---after dropping the tildes---are
 \begin{equation}
 	\begin{aligned}
-		G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \textrm{e}^{i b |A|^2}, \\
-		D(A) &= \FTi{\textrm{e}^{i s^2 \omega^2} \FT{A}}, & L(A) &= h A, \\
-		M(A) &= \textrm{e}^{-T^2 / 2} A,
+		G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \\
+		D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \\
+		M(A) &= \exp( -T^2 / 2 ) A,
 		\label{eq:effects}
@@
 	\begin{aligned}
-		a &= \textrm{e}^{g_0 L_g} \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04, \\
+		a &= \exp( g_0 L_g ) \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04, \\
 		b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& \qquad s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,
@@
 	\centering
-	\includegraphics{Evo}
+	\includegraphics{Figures/Evo}
 	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
-The pulse decays due to the output coupler, dispersed by the CFBG, modulated by the modulator, and finally amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
-Note that this is for visualization only, the durations are not to scale.}
+The pulse decays due to the output coupler, disperses due to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+Note that the $x$ axis is not to scale.}
 	\label{fig:cavityevo}
@@
 
-Now that we have the algebraic effect of each section of the cavity, we are ready to compose each map together to give the effect of one round trip of the cavity.
+Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
 Thus, we must now consider the order of the components.
@@
 The pulse then travels through the Er-doped fibre to be amplified, and finally we consider the effect of the nonlinearity.
-The nonlinearity must immediately follow the gain---this is the section of the cavity where the pulse is most energetic, and hence, has the largest effect.
-Note, the permutation of the other components is indeed important as the operators do not, in general, commute---this is in contrast to the models described in Section \ref{sec:discrete}.
+The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic.
+Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section \ref{sec:discrete}.
 Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.
@@
  The pulse after one complete circuit of the laser cavity is then returned back into the cavity to restart the process.
-A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase.
+A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase due to the nature of experimental measurements.
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
@@
 By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
-We assume the solution will take the form of a chirped Gaussian.
-There are a few reasons for this; the solution to the models presented in \cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the shape of the modulation function, and since a Gaussian is a fixed point of the Fourier transform \cite{gradshteyn2007}.
-Furthermore, this form is chosen because it resembles the envelope and linear chirp expected \cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
+We proceed by assuming the solution will take the form of a chirped Gaussian.
+There are a few reasons for this; the solution to the models presented in \cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
+Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature \cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
-To compute $\mathcal{L}(A)$, consider the pulse
+First, consider the pulse
 \begin{align}
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase. This pulse shape is depicted in Fig. \ref{fig:samplegauss}.
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Sample_Gauss}
-	\caption{Solution to the linear model given by \eqref{eq:A0}.}
-	\label{fig:samplegauss}
-\end{figure}
-
-To compute $\mathcal{F}(A)$, given the initial pulse \eqref{eq:A0}, we iteratively compute the effect of each process map from \eqref{eq:effects}.
-Now, by equating $\mathcal{F}(A)$ and $A \textrm{e}^{i \phi}$ we obtain a system of equations.
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
+This initial pulse is depicted in Fig.
+\ref{fig:samplegauss}.
+To compute $\mathcal{L}(A)$, given the initial pulse \eqref{eq:A0}, we iteratively compute the effect of each map in \eqref{eq:effects}.
+Now, by equating $\mathcal{L}(A)$ and $A \textrm{e}^{i \phi}$ we obtain a system of equations.
 In particular,
@@
 \end{gather}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/Sample_Gauss}
+	\caption{Solution to the linear model given by \eqref{eq:A0}.}
+	\label{fig:samplegauss}
+\end{figure}
 
@@
 \end{equation}
-which can readily be used to find the chirp, $C$. By asymptotically expanding \eqref{eq:var} we find the useful relations
+which can readily be used to find the chirp, $C$. However, by asymptotically expanding \eqref{eq:var} we find the much simpler relations
 \begin{align}
@@
 
-Our linearized model indeed exhibits the same form as previous linear models.
-However, by including the effects of the nonlinearity we uncover the rich interplay between dispersion, modulation, and nonlinearity not previously found mathematically.
+Our linearized model indeed exhibits a solution of the same form as previous linear models.
+However, by including the effects of the nonlinearity we uncover the rich interplay between dispersion, modulation, and nonlinearity.
 
@@
 In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
-The most common form is a hyperbolic secant \cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+One of the most common form is a hyperbolic secant \cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}
@@
 \end{align}
-where $\Gamma$ is a normalizing factor chosen so the pulse has an initial energy of $E_0 = 0.1$, unless specified otherwise.
+where $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$, unless specified otherwise.
 
@@
 	\centering
-	\includegraphics{ChirpFT}
-	\caption{Chirp and Fourier transform in equilibrium state obtained by \eqref{eq:nlA0}, with values $a = 8 \times 10^3$, $h = 0.04$, $b = 1$, $s = 0.2$, and $E_0 = 0.1$.}
+	\includegraphics{Figures/ChirpFT}
+	\caption{Chirp and Fourier transform at equilibrium (500 round trips) seeded by \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.2$, and $E_0 = 0.1$).}
 	\label{fig:chirpft}
@@
 In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transform.
-Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity.
-Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with experimental results \cite{chen2008, rothenberg1989b, tomlinson1985}.
-As the nonlinearity parameter, $b$, is increased, the two lobes in the Fourier transform become more pronounced.
-However, once a critical point is reached SPM begins to play a more substantial factor, leading to modulation instability.
+Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity giving a bi-modal appearance.
+Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results \cite{chen2008, rothenberg1989b, tomlinson1985}.
+As the nonlinearity parameter, $b$, is increased, the two lobes in the Fourier transform become more pronounced and the tails decay more sharply indicating wave breaking.
+However, once a critical point is reached SPM plays a more substantial role, leading to modulation instability.
 This phenomenon is highlighted in Fig.
@@
 During the first two dozen round trips of the cavity, the SPM compounds and becomes too parasitic to the pulse.
-This in turn induces modulation instability, and degrades the pulse, making the pulse no longer stable or sustainable.
-On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable initial pulse (Fig.
+This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.
 \ref{fig:convevo}).
-The pulse is able to shed the initial left lobe because of dispersion and modulation, and the central lobe is able to grow due to the gain medium.
-This allows the pulse to come to equilibrium very quickly.
+The pulse is able to shed the initial left lobe ($T = -1 / 2$) because of dispersion and modulation, and a central lobe ($T = 0$) is formed and is able to grow due to the gain medium.
+This then allows the pulse to come to equilibrium very quickly.
 Furthermore, since the intensity of the initial pulse is relatively small, the effect of SPM is negligible during the first few round trips which allows the laser to select preferable modes.
-These preferable modes then get amplified which stabilizes the pulse.
+The preferable modes then get amplified which stabilizes the pulse.
 From this, it is clear the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
@@
 	\centering
-	\includegraphics{Break}
+	\includegraphics{Figures/Break}
 	\caption{Example of a pulse destabilizing from the initial pulse \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.6$, $s = 0.1$, and $E_0 = 0.1$).}
@@
 	\centering
-	\includegraphics{Conv}
+	\includegraphics{Figures/Conv}
 	\caption{Example of a pulse coming to equilibrium from noise ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.1$, and $E_0 = 0.1$).}
@@
 
-We now turn our attention to characterizing the stability of a laser by exploring the parameter space.
-We focus on the $s$--$b$ plane in particular since $a$ and $h$ effect only the amplitude of the pulse and do not contribute to the interplay of dispersion and the nonlinearity.
-Additionally, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while coming to equilibrium.
-To identify the stability of a pulse we examine the relative change in the pulse's envelope between consecutive iterations.
+We now turn our attention to a more quantitative analysis, and characterize the stability of a laser by exploring the parameter space.
+We focus on the $s$--$b$ plane in particular since $a$ and $h$ effect only the amplitude of the pulse, whereas the interplay of dispersion and nonlinearity give rise to the instabilities.
+Additionally, as mentioned, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while coming to equilibrium.
+To identify the stability of a pulse we examine the relative change in the pulse's envelope between consecutive round trips of the cavity.
 We compute this error by
 \begin{align}
-	\textrm{E} = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
+	\Delta = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
 	\label{eq:error}
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 250$ in our experiments (Fig.
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments (Fig.
 \ref{fig:error}).
-Note that we take the modulus of the pulse since we are only interested in the evolution of the envelope.
+We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the methods used experimentally.
 We find a very sharp and rich boundary between two regions.
-In the upper-left region the error is $\bigO{1}$, this is where the nonlinearity is too strong, and the SPM induces modulation instability.
+In the upper-left region the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
 In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable.
-The error is on the order of machine precision, or slightly higher due to approximating a smooth continuous function by discrete points.
+The increase in dispersion, coupled with modulation, allow the laser to balance the nonlinear effects.
+The error in this region is on the order of machine precision, or slightly higher due to the discretization.
 
@@
 	\centering
-	\includegraphics{ParamSpaceErr}
-	\caption{Relative error of a pulse's envelope between round trips 249 and 250 ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\includegraphics{Figures/ParamSpaceErr}
+	\caption{Relative error of a pulse's envelope between round trips 499 and 500 ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
 	\label{fig:error}
@@
 \begin{align}
-	E &= \| A_i \|_2,
+	E &= \| A_i \|_2.
 	\label{eq:energy2norm}
 \end{align}
-where, again, $i = 250$ in our experiments.
-Recall from \eqref{eq:order}, this energy is the immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is instead $(1 - h^2) \| A_i \|_2$, and $h^2 \| A_i \|_2$ remains in the cavity.
-We plot \eqref{eq:energy2norm} in Fig.
+Recall from \eqref{eq:order}, this energy is immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
+We plot the energy, \eqref{eq:energy2norm}, in the $s$--$b$ plane in Fig.
 \ref{fig:energy}.
@@
 In the unstable region (upper-left) the energy is relatively small.
-Since the pulse is not stable in this region it is not able to foster prominent modes, thus, the intensity is low across the entire pulse.
+Since the pulse is not sustainable in this region it is not able to foster prominent modes, thus, the intensity is low across the entire pulse.
 In the stable region (lower-right) we find that the energy smoothly decays as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
-From this it is clear that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
+As $s$ increases, more energy is lost due to modulation since the tails of the pulse become larger.
+Similarly, as $b$ increases, high frequencies generated by SPM are reduced by our choice of modulation function.
+From this, we find that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
 
@@
 	\centering
-	\includegraphics{ParamSpaceEnergy}
-	\caption{Energy of the pulse after 250 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\includegraphics{Figures/ParamSpaceEnergy}
+	\caption{Energy of the pulse after 500 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
 	\label{fig:energy}
@@
 
-Finally, we briefly look at how the order of the components effects the dynamics.
+Finally, we briefly investigate the effect the order of the components has on the dynamics.
 In Section \ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
-Here we consider the effect of swapping the dispersion and modulation components.
+Here, we consider the effect of swapping the dispersion and modulation components.
 The energy landscape (Fig.
@@
 Whereas, having modulation first, more of this energy remains in the cavity.
-This has the effect of making the laser more powerful, which in turn increases the unstable region.
+This has the effect of making the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
 Comparing with Fig.
-\ref{fig:energy}, this is what we find.
-The unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
+\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
 
@@
 	\centering
-	\includegraphics{ParamSpaceEnergySwitch}
-	\caption{Energy of the pulse after 250 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\includegraphics{Figures/ParamSpaceEnergySwitch}
+	\caption{Energy of the pulse after 500 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
 	\label{fig:energyswitch}
@@
 \label{sec:conclusion}
-Expanding upon the ideas originally proposed by Cutler \cite{cutler1955}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear functional model for tuneable ring lasers.
-We recover linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
+Expanding upon the ideas originally proposed by Cutler \cite{cutler1955}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear iterative map model for tuneable ring lasers.
+We recovered linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
 Moreover, the solution of the linear model can easily be extended to any modulation function using results of \cite{calcaterra2008a}.
 In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has difficult to predict with mathematical models.
-Furthermore, it is of interest to analyze the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$.
+This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models.
+
+It is of interest to analyze the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$.
 Doing so would provide insight to how the nonlinearity impacts the linearized solution to better understand the manifestation of wave breaking and modulation instability.

### 2020-11-20 Papers/Journal/Cavity.tex
Apparently this got deleted

--- 2019-11-04 Papers/AMMCS_Proceedings/Cavity.tex
@@
 % Circulators
-\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Optical \\ Circulator};
+\filldraw[fill=white, draw=black] (6,2) circle (0.5cm);
 \draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);
@@
 
-\filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
+\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical Circulator};
 \draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);

### 2020-11-21 Papers/Journal/Tuneable_Lasers.tex
Resized figures for journal

@@
 
+\usepackage{subcaption}
 \usepackage{tikz}
+
+\renewcommand{\topfraction}{.9}
 
@@
 The pulse decays due to the output coupler, disperses due to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
-Note that the $x$ axis is not to scale.}
+Note, the $z$ axis is not to scale.}
 	\label{fig:cavityevo}
@@
 	\centering
-	\includegraphics{Figures/ChirpFT}
-	\caption{Chirp and Fourier transform at equilibrium (500 round trips) seeded by \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.2$, and $E_0 = 0.1$).}
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Figures/Chirp}
+		\caption{Chirp}
+		\label{fig:}
+	\end{subfigure} \\
+	\vspace{3mm}
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Figures/FT}
+		\caption{Chirp}
+		\label{fig:}
+	\end{subfigure}
+	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.2$, and $E_0 = 0.1$).}
 	\label{fig:chirpft}

### 2020-11-22 Papers/Journal/Tuneable_Lasers.tex
Fixed typo
More edits

@@
 \usepackage{tikz}
-
-\renewcommand{\topfraction}{.9}
 
@@
 
-In Section \ref{sec:modelling}, we briefly review previous mathematical models for the evolution of laser pulses, then we derive our own model in Section \ref{sec:model}.
-We then examine the results of our model in Section \ref{sec:results}---first solving the model analytically assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
-Finally, the concluding thoughts and possible directions of future work are given in Section \ref{sec:conclusion}.
-
 \begin{figure}[tbp]
@@
 \end{figure}
+
+In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
+In Section \ref{sec:modelling}, we will briefly review previous mathematical models for ring lasers.
+Then, we will present our own iterative map model in Section \ref{sec:model}, as well as non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
+We will then examine the results of our model in Section \ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
+Finally, the concluding thoughts and possible ideas for future work are given in Section \ref{sec:conclusion}.
 
@@
 \subsection{Non-Dimensionalization}
-The structure of each process of the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
+Non-dimensionalization is a technique used in mathematical modelling to better understand the relative importance of different processes within a system.
+In essence, we scale all variables by typical values of the system based on the geometry and boundary conditions (see, for example, \cite{howison2005}).
+Doing so `factors' the dimensional units out of the problem, leaving only dimensionless equations with dimensionless parameters.
+The magnitude of the dimensionless parameters characterizes the dominant dynamics of the system---much like how fluid flow can be described with only the Reynolds number.
+The structure of each process in the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
 \begin{align}
@@
 \end{align}
-Revisiting the process maps, \eqref{eq:gainform}--\eqref{eq:modform}, shows each process has a characteristic non-dimensional parameter. The new mappings---after dropping the tildes---are
+
+Revisiting the process maps \eqref{eq:gainform}--\eqref{eq:modform} yields the new, non-dimensional, mappings---after dropping the tildes---
+\begin{align}
+	G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \nonumber \\
+	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
+	M(A) &= \exp( -T^2 / 2 ) A, \nonumber
+\end{align}
+with the four dimensionless parameters, as defined by the values in Table \ref{tab:values},
 \begin{equation}
 	\begin{aligned}
-		G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \\
-		D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \\
-		M(A) &= \exp( -T^2 / 2 ) A,
-		\label{eq:effects}
-	\end{aligned}
-\end{equation}
-with the four dimensionless parameters,
-\begin{equation}
-	\begin{aligned}
-		a &= \exp( g_0 L_g ) \sim 8 \times 10^3,& \qquad h &= (1 - R) \textrm{e}^{-\alpha L} \sim 0.04, \\
-		b &= \gamma L_f \frac{\Es}{T_M} \sim 1,& \qquad s &= \sqrt{\frac{\beta_2 L_D}{2 T_M^2}} \sim 0.2,
+		a &= \exp( g_0 L_g ) \sim 8 \times 10^3, & 
+		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, \\
+		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, & s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2.
 		\label{eq:ndparam}
@@
 \end{equation}
-which characterize the behaviour of the laser.
-Nominal values for the parameters, \eqref{eq:ndparam}, can be found in \cite{agrawal2002, agrawal2013, bohun2015, burgoyne2014, burgoyneemail, finot2008, li1998, litchinitser1997, peng2018, shtyrina2017, tamura1993, tamura1996, tomlinson1984, usechak2005, yamashita2009, yarutkina2013}.
-Notice that the modulation is only characterized by $T_M$, and each other process has its own associated independent non-dimensional parameter.
+Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the output coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
+Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:ndparam} have their own independent, non-dimensional parameter.
 
@@
 
-First, consider the pulse
-\begin{align}
-	A = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \textrm{e}^{i \phi_0},
-	\label{eq:A0}
-\end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the initial phase.
-This initial pulse is depicted in Fig.
-\ref{fig:samplegauss}.
-To compute $\mathcal{L}(A)$, given the initial pulse \eqref{eq:A0}, we iteratively compute the effect of each map in \eqref{eq:effects}.
-Now, by equating $\mathcal{L}(A)$ and $A \textrm{e}^{i \phi}$ we obtain a system of equations.
-In particular,
-\begin{gather}
-	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
-	C = \frac{\sigma^4 \pm \sqrt{\sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
-	\label{eq:chirp}
-\end{gather}
-
 \begin{figure}[tbp]
@@
 
-As \eqref{eq:var} is a quartic in $\sigma^2$ it has an analytic solution, namely,
+Consider the pulse
+\begin{align}
+	A = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \textrm{e}^{i \phi_0},
+	\label{eq:A0}
+\end{align}
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.
+\ref{fig:samplegauss}).
+By computing $\mathcal{L}(A)$ using \eqref{eq:order}, and equating to $A \textrm{e}^{i \phi}$, we obtain the conditions
+\begin{align}
+	\frac{\sigma^4}{1 - \sigma^2} &= (\sigma^2 + 2 C s^2)^2 + 4 s^4, \label{eq:sigrelation} \\
+	\frac{C}{1 - \sigma^2} &= C + 2 \frac{s^2}{\sigma^2} (1 + C^2), \label{eq:chirprelation} \\
+	1 &= \frac{W(a E \textrm{e}^E)}{E} h^2 (1 - \sigma^2)^{1/2} \label{eq:energyrelation}
+\end{align}
+for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we acquire the simpler relations
+\begin{gather}
+	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
+	C = \frac{\sigma^4 \pm \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
+	\label{eq:chirp}
+\end{gather}
+The equilibrium energy can be found from \eqref{eq:energyrelation}, using the properties of the Lambert $W$ function, giving
+\begin{align}
+	E = \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2}}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right).
+\end{align}
+
+\eqref{eq:var} has an analytic solution, as it is a quartic in $\sigma^2$. Namely,
 \begin{equation}
@@
 The equilibrium energy and peak power can be found by conservation of energy to give
-\begin{align}
-	E = \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2}}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right),
-\end{align}
+
 and

### 2020-11-22 Papers/Journal/Tuneable_Lasers.tex
Fixed energy and power section

@@
 \label{sec:intro}
-Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009}.
-This ability to vary the frequency leads to applications such as optical coherence tomography \cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy \cite{burgoyne2014}, deep tissue multi-photon microscopy \cite{chung2017, liu2017}, and diagnostics of ultrafast processes \cite{burgoyne2014, silfvast2004}.
+Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}.
+This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017, liu2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}.
 Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser.
-A typical ring laser cavity is depicted in Fig.
-\ref{fig:cavity}.
+A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
 Due to the high power and short duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.
 
-Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
+Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
 The two effects of most interest for this paper are wave breaking, and modulation instability.
-Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The shifts in frequencies cause the pulse to become more rectangular in the frequency domain with a linear chirp over most of the pulse.
 In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself.
-New frequencies are then generated which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
-Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics \cite{rothenberg1989b}.
+New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, mollenauer1980, woodward2018}.
+Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics~\cite{rothenberg1989b}.
 Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
-However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
-Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence \cite{agrawal1987, coen1997, haelterman1992}.
+However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
+Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
 Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
-This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable \cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
+This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
 
@@
 	\input{Cavity}
-	\caption{Typical cavity of a fibre ring laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
+	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
 	\label{fig:cavity}
@@
 In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
-In Section \ref{sec:modelling}, we will briefly review previous mathematical models for ring lasers.
-Then, we will present our own iterative map model in Section \ref{sec:model}, as well as non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
-We will then examine the results of our model in Section \ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+In Section~\ref{sec:modelling}, we will briefly review previous mathematical models for ring lasers.
+Then, we will present our own iterative map model in Section~\ref{sec:model}, as well as non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
+We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
 We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
-Finally, the concluding thoughts and possible ideas for future work are given in Section \ref{sec:conclusion}.
+Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.
 
@@
 In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (occasionally higher order terms are added as well).
-These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
+These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking \cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005},
+The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking~\cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005},
 \begin{align}
@@
 \end{align}
-No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic \cite{haus1984, haus1975, haus1996}.
-However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
-See Haus \cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
+No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic~\cite{haus1984, haus1975, haus1996}.
+However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found~\cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
+See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
 
@@
 It is assumed in \eqref{eq:meml} that each process affects the pulse continuously within the cavity.
-As highlighted by Fig.
-\ref{fig:cavity}, this can be a poor assumption.
-Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
+As highlighted by Fig.~\ref{fig:cavity}, this can be a poor assumption.
+Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
 Thus, a better model is one where we consider a simplified version of \eqref{eq:meml} for each component.
@@
 
-Such a method was first proposed in 1955 by Cutler \cite{cutler1955} while analyzing a microwave regenerative pulse generator.
-His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
-The effects of the nonlinearity would not be considered until Martinez \emph{et al.} \cite{martinez1984, martinez1985} modelled passively mode-locked lasers.
-This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
+Such a method was first proposed in 1955 by Cutler~\cite{cutler1955} while analyzing a microwave regenerative pulse generator.
+His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
+The effects of the nonlinearity would not be considered until Martinez \emph{et al.}~\cite{martinez1984, martinez1985} modelled passively mode-locked lasers.
+This issue has recently been readdressed by Burgoyne~\cite{burgoyne2014} in the literature for tuneable lasers.
 In each of these models the effect of each block is described by a transfer function.
@@
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section \ref{sec:intro}.
+Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section~\ref{sec:intro}.
 
@@
 \label{sec:model}
-Using the idea of a discrete model presented Section \ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
-To accomplish this we follow the method described in Section \ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
+Using the idea of a discrete model presented Section~\ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
+To accomplish this we follow the method described in Section~\ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
 
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{haus1984, shtyrina2017, silfvast2004}.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}.
 This reduces \eqref{eq:nlse} to
@@
 This assumption is not particularly restrictive.
-Calcaterra and Boldt have shown that Gaussians can form a basis for $L^2(\mathbb{R})$ \cite{calcaterra2008a}.
+Calcaterra and Boldt have shown that Gaussians can form a basis for $L^2(\mathbb{R})$~\cite{calcaterra2008a}.
 Therefore, we can approximate any modulation function in $L^2(\mathbb{R})$ by a sum of \eqref{eq:modform}.
@@
 Non-dimensionalization is a technique used in mathematical modelling to better understand the relative importance of different processes within a system.
-In essence, we scale all variables by typical values of the system based on the geometry and boundary conditions (see, for example, \cite{howison2005}).
+In essence, we scale all variables by typical values of the system based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
 Doing so `factors' the dimensional units out of the problem, leaving only dimensionless equations with dimensionless parameters.
@@
 \end{align}
-with the four dimensionless parameters, as defined by the values in Table \ref{tab:values},
+with the four dimensionless parameters, as defined by the values in Table~\ref{tab:values},
 \begin{equation}
@@
  		\hline\noalign{\smallskip}
- 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005, yarutkina2013} \\
- 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser1997, peng2018, yarutkina2013} \\
- 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot2008, usechak2005, yarutkina2013} \\
- 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li1998} \\
- 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng2018, tamura1996} \\
- 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
- 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng2018, shtyrina2017, tamura1993,yarutkina2013} \\
- 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun2015, burgoyneemail, burgoyne2014} \\
- 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li1998, peng2018,  tamura1993, tamura1996, yamashita2009} \\
- 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak2005, yarutkina2013} \\
- 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina2013} \\
+ 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  &~\cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005, yarutkina2013} \\
+ 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ &~\cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser1997, peng2018, yarutkina2013} \\
+ 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ &~\cite{agrawal2013, finot2008, usechak2005, yarutkina2013} \\
+ 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ &~\cite{agrawal2002, agrawal2013, burgoyne2014, li1998} \\
+ 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ &~\cite{burgoyneemail, peng2018, tamura1996} \\
+ 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ &~\cite{burgoyneemail} \\
+ 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ &~\cite{burgoyne2014, peng2018, shtyrina2017, tamura1993,yarutkina2013} \\
+ 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ &~\cite{bohun2015, burgoyneemail, burgoyne2014} \\
+ 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ &~\cite{burgoyneemail, li1998, peng2018,  tamura1993, tamura1996, yamashita2009} \\
+ 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ &~\cite{burgoyneemail, usechak2005, yarutkina2013} \\
+ 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ &~\cite{burgoyneemail, yarutkina2013} \\
  		\noalign{\smallskip}\hline
@@
 The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic.
-Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section \ref{sec:discrete}.
+Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section~\ref{sec:discrete}.
 Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.
@@
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
-An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.
-\ref{fig:cavityevo}.
+An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
 
@@
 \label{sec:results}
-We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section \ref{sec:nlresults} we look at the full nonlinear model.
+We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section~\ref{sec:nlresults} we look at the full nonlinear model.
 
@@
 We proceed by assuming the solution will take the form of a chirped Gaussian.
-There are a few reasons for this; the solution to the models presented in \cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
-Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature \cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
+There are a few reasons for this; the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
+Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.
-\ref{fig:samplegauss}).
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.~\ref{fig:samplegauss}).
 By computing $\mathcal{L}(A)$ using \eqref{eq:order}, and equating to $A \textrm{e}^{i \phi}$, we obtain the conditions
@@
 \end{align}
-for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we acquire the simpler relations
-\begin{gather}
-	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
-	C = \frac{\sigma^4 \pm \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
-	\label{eq:chirp}
-\end{gather}
-The equilibrium energy can be found from \eqref{eq:energyrelation}, using the properties of the Lambert $W$ function, giving
+for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find an expression in terms of $\sigma$ only, that is,
 \begin{align}
-	E = \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2}}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right).
+	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0. \label{eq:var}
 \end{align}
-
-\eqref{eq:var} has an analytic solution, as it is a quartic in $\sigma^2$. Namely,
+As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
 \begin{equation}
@@
 		\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} & \\
-		- s^4 - s^2 & \sqrt{4 + s^4},
+		- s^4 - s^2 & \sqrt{4 + s^4}.
 		\label{eq:equilvar}
@@
 \end{equation}
-which can readily be used to find the chirp, $C$. However, by asymptotically expanding \eqref{eq:var} we find the much simpler relations
+Additionally, we find the chirp to be
 \begin{align}
-	\sigma^2 &\sim
-	\begin{cases}
-		2s(1 - s) + \bigO{s^3} & s \rightarrow 0 \\
-		1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty,
-	\end{cases} \\
-	C &\sim
-	\begin{cases}
-		1 - s + \frac{1}{2}s^2 + \bigO{s^3} & s \rightarrow 0 \\
-		\frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}} & s \rightarrow \infty.
-	\end{cases}
+	C = \frac{\sigma^4 \pm \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
+	\label{eq:chirp}
 \end{align}
-The equilibrium energy and peak power can be found by conservation of energy to give
+in terms of $s$ and $\sigma^2$.
+Moreover, we can obtain the energy of the pulse entering the gain fibre from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the output coupler.
+Doing so gives
+\begin{align}
+	E &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
+	\label{eq:analenergy}
+\end{align}
+By equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, the peak power is found to be
+\begin{align}
+	P &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{\sqrt{\pi} \sigma \left( 1 - h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}.
+	\label{eq:analpower}
+\end{align}
 
-and
+The nature of \eqref{eq:var}--\eqref{eq:analpower} makes it difficult to work with.
+However, by asymptotically expanding \eqref{eq:var}--\eqref{eq:analpower} in terms of the dispersion parameter, $s$, we find the simpler relations
 \begin{align}
-	P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma},
-	\label{eq:equilpower}
+	\sigma^2 &\sim 2s(1 - s) + \bigO{s^3}, \\
+	C &\sim 1 - s + \frac{1}{2}s^2 + \bigO{s^3}, \\
+	E &\sim \frac{\log (a h^2)}{1 - h^2} - \frac{1}{1 - h^2} \left( 1 + \frac{h^2 \log(a h^2)}{1 - h^2}  \right) s + \bigO{s^2}, \\
+	P &\sim \frac{\log(ah^2)}{\sqrt{2 \pi}(1 - h^2)} s^{-1/2} + \bigO{s^{1/2}},
 \end{align}
-respectively.
+in the case $s \rightarrow 0$. And,
+\begin{align}
+	\sigma^2 &\sim 1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}}, \label{eq:siginfty}\\
+	C &\sim \frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}},
+\end{align}
+in the case $s \rightarrow \infty$.
+We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit the gain is unable to balance the energy lost due to modulation, as indicated by the logarithm in \eqref{eq:analenergy}.
+Expanding the condition $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for a first-order approximation), we find
+\begin{align}
+	s^* = \left( \frac{a h^2}{2} \right)^{1/2}
+\end{align}
+is the maximum value of $s$ to facilitate a sustainable pulse.
 
@@
 In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
-One of the most common form is a hyperbolic secant \cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+One of the most common form is a hyperbolic secant~\cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}
@@
 
-In Fig.
-\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
+In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
 In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transform.
 Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity giving a bi-modal appearance.
-Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results \cite{chen2008, rothenberg1989b, tomlinson1985}.
+Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
 As the nonlinearity parameter, $b$, is increased, the two lobes in the Fourier transform become more pronounced and the tails decay more sharply indicating wave breaking.
 However, once a critical point is reached SPM plays a more substantial role, leading to modulation instability.
-This phenomenon is highlighted in Fig.
-\ref{fig:breakevo}.
+This phenomenon is highlighted in Fig.~\ref{fig:breakevo}.
 By increasing the nonlinearity, and decreasing the dispersion we find the pulse begins to `breathe'.
@@
 This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
-On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.
-\ref{fig:convevo}).
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}).
 The pulse is able to shed the initial left lobe ($T = -1 / 2$) because of dispersion and modulation, and a central lobe ($T = 0$) is formed and is able to grow due to the gain medium.
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments (Fig.
-\ref{fig:error}).
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments (Fig.~\ref{fig:error}).
 We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the methods used experimentally.
@@
 \begin{align}
-	E &= \| A_i \|_2.
+	E &= \| A_i \|_2^2.
 	\label{eq:energy2norm}
@@
 Recall from \eqref{eq:order}, this energy is immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
-We plot the energy, \eqref{eq:energy2norm}, in the $s$--$b$ plane in Fig.
-\ref{fig:energy}.
-Unsurprisingly, we find the same sharp boundary as we saw in Fig.
-\ref{fig:error}.
+We plot the energy, \eqref{eq:energy2norm}, in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
+Unsurprisingly, we find the same sharp boundary as we saw in Fig.~\ref{fig:error}.
 In the unstable region (upper-left) the energy is relatively small.
@@
 Finally, we briefly investigate the effect the order of the components has on the dynamics.
-In Section \ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
+In Section~\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
 Here, we consider the effect of swapping the dispersion and modulation components.
-The energy landscape (Fig.
-\ref{fig:energyswitch}) is as we would expect.
+The energy landscape (Fig.~\ref{fig:energyswitch}) is as we would expect.
 In the previous case of having modulation following dispersion, more energy is removed from the pulse tails.
@@
 This has the effect of making the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
-Comparing with Fig.
-\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
+Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
 
@@
 \label{sec:conclusion}
-Expanding upon the ideas originally proposed by Cutler \cite{cutler1955}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear iterative map model for tuneable ring lasers.
+Expanding upon the ideas originally proposed by Cutler~\cite{cutler1955}, and Kuizenga and Siegman~\cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear iterative map model for tuneable ring lasers.
 We recovered linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
-Moreover, the solution of the linear model can easily be extended to any modulation function using results of \cite{calcaterra2008a}.
+Moreover, the solution of the linear model can easily be extended to any modulation function using results of~\cite{calcaterra2008a}.
 In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models.
+This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models.
 

### 2020-11-22 Papers/Journal/Tuneable_Lasers.tex
Updated references

@@
 Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}.
-This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017, liu2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}.
+This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}.
 Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser.
@@
 In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself.
-New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, mollenauer1980, woodward2018}.
+New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, woodward2018}.
 Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics~\cite{rothenberg1989b}.
 Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
-However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
+However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
 Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
@@
 	\input{Cavity}
-	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
+	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The laser pulses travel clockwise around each loop.}
 	\label{fig:cavity}
@@
 		\hline\noalign{\smallskip}
- 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  &~\cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005, yarutkina2013} \\
- 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ &~\cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser1997, peng2018, yarutkina2013} \\
- 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ &~\cite{agrawal2013, finot2008, usechak2005, yarutkina2013} \\
- 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ &~\cite{agrawal2002, agrawal2013, burgoyne2014, li1998} \\
- 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ &~\cite{burgoyneemail, peng2018, tamura1996} \\
+		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  &~\cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005} \\
+		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ &~\cite{agrawal2002, agrawal2013, burgoyne2014} \\
+		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ &~\cite{agrawal2013, finot2008, usechak2005} \\
+		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ &~\cite{agrawal2002, agrawal2013, burgoyne2014} \\
+		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ &~\cite{burgoyneemail, tamura1996} \\
 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ &~\cite{burgoyneemail} \\
- 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ &~\cite{burgoyne2014, peng2018, shtyrina2017, tamura1993,yarutkina2013} \\
+		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ &~\cite{burgoyne2014, shtyrina2017} \\
 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ &~\cite{bohun2015, burgoyneemail, burgoyne2014} \\
- 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ &~\cite{burgoyneemail, li1998, peng2018,  tamura1993, tamura1996, yamashita2009} \\
- 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ &~\cite{burgoyneemail, usechak2005, yarutkina2013} \\
- 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ &~\cite{burgoyneemail, yarutkina2013} \\
+		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ &~\cite{burgoyneemail, tamura1996, yamashita2009} \\
+		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ &~\cite{burgoyneemail, usechak2005} \\
+		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ &~\cite{burgoyneemail} \\
 		\noalign{\smallskip}\hline
@@
 In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
-One of the most common form is a hyperbolic secant~\cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+One of the most common form is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}

### 2020-11-22 Papers/Journal/Tuneable_Lasers.tex
Reworded some sentences

@@
 
-Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
+Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, shao2019, woodward2018}.
 The two effects of most interest for this paper are wave breaking, and modulation instability.
@@
 \label{sec:model}
-Using the idea of a discrete model presented Section~\ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
-To accomplish this we follow the method described in Section~\ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
+Using the idea of a discrete model presented Section~\ref{sec:modelling}\ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
+To accomplish this we follow the method described in Section~\ref{sec:modelling}\ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
 
@@
 Therefore, we can approximate any modulation function in $L^2(\mathbb{R})$ by a sum of \eqref{eq:modform}.
+
+Saturable Absorber \cite{lapre2019, meng2020}
 
@@
 The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic.
-Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section~\ref{sec:discrete}.
+Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section~\ref{sec:modelling}\ref{sec:discrete}.
 Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.
@@
 \label{sec:results}
-We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section~\ref{sec:nlresults} we look at the full nonlinear model.
+We split the results into two subsections.
+In the following subsection we investigate the low nonlinearity limit, and in Section~\ref{sec:results}\ref{sec:nlresults} we look at the full nonlinear model.
 
@@
 This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
-On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}).
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
 The pulse is able to shed the initial left lobe ($T = -1 / 2$) because of dispersion and modulation, and a central lobe ($T = 0$) is formed and is able to grow due to the gain medium.
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments (Fig.~\ref{fig:error}).
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments.
 We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the methods used experimentally.
-We find a very sharp and rich boundary between two regions.
+We plot the error in Fig.~\ref{fig:error}.
+It is clear the parameter space is split into two distinct regions, divided by an incredibly sharp and complex boundary.
 In the upper-left region the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
 In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable.
-The increase in dispersion, coupled with modulation, allow the laser to balance the nonlinear effects.
+The increase in dispersion, coupled with modulation, allows the laser to balance the nonlinear effects.
 The error in this region is on the order of machine precision, or slightly higher due to the discretization.
@@
 Finally, we briefly investigate the effect the order of the components has on the dynamics.
-In Section~\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
+In Section~\ref{sec:model}\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
 Here, we consider the effect of swapping the dispersion and modulation components.
@@
 In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models.
+This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
 

### 2020-11-24 Papers/Journal/Tuneable_Lasers.tex
Added AMMCS paper reference

--- 2020-11-22 Papers/Journal/Tuneable_Lasers.tex
@@
 \affil[3]{brady.metherall@maths.ox.ac.uk}
-\affil[4]{sean.bohun@uoit.ca}
+\affil[4]{sean.bohun@ontariotechu.ca}
 
@@
 \label{sec:intro}
-Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}.
-This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}.
+Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres \cite{bohun2015, burgoyne2010, yamashita2009}.
+This ability to vary the frequency leads to applications such as optical coherence tomography \cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy \cite{burgoyne2014}, deep tissue multi-photon microscopy \cite{chung2017, liu2017}, and diagnostics of ultrafast processes \cite{burgoyne2014, silfvast2004}.
 Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser.
-A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
+A typical ring laser cavity is depicted in Fig.
+\ref{fig:cavity}.
 Due to the high power and short duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.
 
-Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
+Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity \cite{bohun2015, coen1997, lapre2019, shao2019, woodward2018}.
 The two effects of most interest for this paper are wave breaking, and modulation instability.
-Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed \cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The shifts in frequencies cause the pulse to become more rectangular in the frequency domain with a linear chirp over most of the pulse.
 In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself.
-New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, woodward2018}.
-Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics~\cite{rothenberg1989b}.
+New frequencies are then generated which induces the rectangular profile \cite{agrawal2013, mollenauer1980, woodward2018}.
+Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics \cite{rothenberg1989b}.
 Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
-However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
-Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
+However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing \cite{agrawal1987, agrawal1989, agrawal2013, haelterman1992}.
+Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence \cite{agrawal1987, coen1997, haelterman1992}.
 Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
-This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
+This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable \cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
 
@@
 	\input{Cavity}
-	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The laser pulses travel clockwise around each loop.}
+	\caption{Typical cavity of a fibre ring laser \cite{burgoyne2014, chung2017, lapre2019, shao2019, tang2014}. The laser pulses travel clockwise around each loop.}
 	\label{fig:cavity}
@@
 In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
-In Section~\ref{sec:modelling}, we will briefly review previous mathematical models for ring lasers.
-Then, we will present our own iterative map model in Section~\ref{sec:model}, as well as non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
-We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+In Section \ref{sec:modelling}, we will briefly review previous mathematical models for ring lasers.
+Then, we will present our own iterative map model in Section \ref{sec:model}, as well as non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
+We will then examine the results of our model in Section \ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
 We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
-Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.
+Finally, the concluding thoughts and possible ideas for future work are given in Section \ref{sec:conclusion}.
 
@@
 In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (occasionally higher order terms are added as well).
-These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
+These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE) \cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking~\cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005},
+The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking \cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005},
 \begin{align}
@@
 \end{align}
-No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic~\cite{haus1984, haus1975, haus1996}.
-However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found~\cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
-See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
+No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic \cite{haus1984, haus1975, haus1996}.
+However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found \cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
+See Haus \cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
 
@@
 It is assumed in \eqref{eq:meml} that each process affects the pulse continuously within the cavity.
-As highlighted by Fig.~\ref{fig:cavity}, this can be a poor assumption.
-Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
+As highlighted by Fig.
+\ref{fig:cavity}, this can be a poor assumption.
+Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG \cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
 Thus, a better model is one where we consider a simplified version of \eqref{eq:meml} for each component.
@@
 
-Such a method was first proposed in 1955 by Cutler~\cite{cutler1955} while analyzing a microwave regenerative pulse generator.
-His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
-The effects of the nonlinearity would not be considered until Martinez \emph{et al.}~\cite{martinez1984, martinez1985} modelled passively mode-locked lasers.
-This issue has recently been readdressed by Burgoyne~\cite{burgoyne2014} in the literature for tuneable lasers.
+Such a method was first proposed in 1955 by Cutler \cite{cutler1955} while analyzing a microwave regenerative pulse generator.
+His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga \cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
+The effects of the nonlinearity would not be considered until Martinez \emph{et al.} \cite{martinez1984, martinez1985} modelled passively mode-locked lasers.
+This issue has recently been readdressed by Burgoyne \cite{burgoyne2014} in the literature for tuneable lasers.
 In each of these models the effect of each block is described by a transfer function.
@@
 While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section~\ref{sec:intro}.
+Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section \ref{sec:intro}.
 
@@
 \label{sec:model}
-Using the idea of a discrete model presented Section~\ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
-To accomplish this we follow the method described in Section~\ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
+Using the idea of a discrete model presented Section \ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
+To accomplish this we follow the method described in Section \ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
 
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate \cite{haus1984, shtyrina2017, silfvast2004}.
 This reduces \eqref{eq:nlse} to
@@
 This assumption is not particularly restrictive.
-Calcaterra and Boldt have shown that Gaussians can form a basis for $L^2(\mathbb{R})$~\cite{calcaterra2008a}.
+Calcaterra and Boldt have shown that Gaussians can form a basis for $L^2(\mathbb{R})$ \cite{calcaterra2008a}.
 Therefore, we can approximate any modulation function in $L^2(\mathbb{R})$ by a sum of \eqref{eq:modform}.
@@
 Non-dimensionalization is a technique used in mathematical modelling to better understand the relative importance of different processes within a system.
-In essence, we scale all variables by typical values of the system based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
+In essence, we scale all variables by typical values of the system based on the geometry and boundary conditions (see, for example, \cite{howison2005}).
 Doing so `factors' the dimensional units out of the problem, leaving only dimensionless equations with dimensionless parameters.
@@
 \end{align}
-with the four dimensionless parameters, as defined by the values in Table~\ref{tab:values},
+with the four dimensionless parameters, as defined by the values in Table \ref{tab:values},
 \begin{equation}
@@
  		\hline\noalign{\smallskip}
-		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  &~\cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005} \\
-		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ &~\cite{agrawal2002, agrawal2013, burgoyne2014} \\
-		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ &~\cite{agrawal2013, finot2008, usechak2005} \\
-		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ &~\cite{agrawal2002, agrawal2013, burgoyne2014} \\
-		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ &~\cite{burgoyneemail, tamura1996} \\
-		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ &~\cite{burgoyneemail} \\
-		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ &~\cite{burgoyne2014, shtyrina2017} \\
-		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ &~\cite{bohun2015, burgoyneemail, burgoyne2014} \\
-		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ &~\cite{burgoyneemail, tamura1996, yamashita2009} \\
-		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ &~\cite{burgoyneemail, usechak2005} \\
-		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ &~\cite{burgoyneemail} \\
+ 		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  & \cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005, yarutkina2013} \\
+ 		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ & \cite{agrawal2002, agrawal2013, burgoyne2014, litchinitser1997, peng2018, yarutkina2013} \\
+ 		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ & \cite{agrawal2013, finot2008, usechak2005, yarutkina2013} \\
+ 		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ & \cite{agrawal2002, agrawal2013, burgoyne2014, li1998} \\
+ 		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ & \cite{burgoyneemail, peng2018, tamura1996} \\
+ 		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ & \cite{burgoyneemail} \\
+ 		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ & \cite{burgoyne2014, peng2018, shtyrina2017, tamura1993,yarutkina2013} \\
+ 		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ & \cite{bohun2015, burgoyneemail, burgoyne2014} \\
+ 		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ & \cite{burgoyneemail, li1998, peng2018,  tamura1993, tamura1996, yamashita2009} \\
+ 		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ & \cite{burgoyneemail, usechak2005, yarutkina2013} \\
+ 		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ & \cite{burgoyneemail, yarutkina2013} \\
  		\noalign{\smallskip}\hline
@@
 The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic.
-Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section~\ref{sec:discrete}.
+Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section \ref{sec:discrete}.
 Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.
@@
 That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
-An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
+An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.
+\ref{fig:cavityevo}.
 
@@
 \label{sec:results}
-We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section~\ref{sec:nlresults} we look at the full nonlinear model.
+We split the results into two subsections. In the following subsection we investigate the low nonlinearity limit, and in Section \ref{sec:nlresults} we look at the full nonlinear model.
 
@@
 We proceed by assuming the solution will take the form of a chirped Gaussian.
-There are a few reasons for this; the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
-Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
+There are a few reasons for this; the solution to the models presented in \cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
+Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature \cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.~\ref{fig:samplegauss}).
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.
+\ref{fig:samplegauss}).
 By computing $\mathcal{L}(A)$ using \eqref{eq:order}, and equating to $A \textrm{e}^{i \phi}$, we obtain the conditions
@@
 \end{align}
-for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find an expression in terms of $\sigma$ only, that is,
+for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we acquire the simpler relations
+\begin{gather}
+	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0, \label{eq:var} \\
+	C = \frac{\sigma^4 \pm \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
+	\label{eq:chirp}
+\end{gather}
+The equilibrium energy can be found from \eqref{eq:energyrelation}, using the properties of the Lambert $W$ function, giving
 \begin{align}
-	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0. \label{eq:var}
+	E = \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2}}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right).
 \end{align}
-As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
+
+\eqref{eq:var} has an analytic solution, as it is a quartic in $\sigma^2$. Namely,
 \begin{equation}
@@
 \end{equation}
-Additionally, we find the chirp to be
+which can readily be used to find the chirp, $C$. However, by asymptotically expanding \eqref{eq:var} we find the much simpler relations
 \begin{align}
-	C = \frac{\sigma^4 \pm \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
-	\label{eq:chirp}
+	\sigma^2 &\sim
+	\begin{cases}
+		2s(1 - s) + \bigO{s^3} & s \rightarrow 0 \\
+		1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}} & s \rightarrow \infty,
+	\end{cases} \\
+	C &\sim
+	\begin{cases}
+		1 - s + \frac{1}{2}s^2 + \bigO{s^3} & s \rightarrow 0 \\
+		\frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}} & s \rightarrow \infty.
+	\end{cases}
 \end{align}
-in terms of $s$ and $\sigma^2$.
-Moreover, we can obtain the energy of the pulse entering the gain fibre from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the output coupler.
-Doing so gives
+The equilibrium energy and peak power can be found by conservation of energy to give
+
+and
 \begin{align}
-	E &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
-	\label{eq:analenergy}
+	P = \frac{W(a E \textrm{e}^E)}{\sqrt{\pi} \sigma},
+	\label{eq:equilpower}
 \end{align}
-By equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, the peak power is found to be
-\begin{align}
-	P &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{\sqrt{\pi} \sigma \left( 1 - h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}.
-	\label{eq:analpower}
-\end{align}
-
-The nature of \eqref{eq:var}--\eqref{eq:analpower} makes it difficult to work with.
-However, by asymptotically expanding \eqref{eq:var}--\eqref{eq:analpower} in terms of the dispersion parameter, $s$, we find the simpler relations
-\begin{align}
-	\sigma^2 &\sim 2s(1 - s) + \bigO{s^3}, \\
-	C &\sim 1 - s + \frac{1}{2}s^2 + \bigO{s^3}, \\
-	E &\sim \frac{\log (a h^2)}{1 - h^2} - \frac{1}{1 - h^2} \left( 1 + \frac{h^2 \log(a h^2)}{1 - h^2}  \right) s + \bigO{s^2}, \\
-	P &\sim \frac{\log(ah^2)}{\sqrt{2 \pi}(1 - h^2)} s^{-1/2} + \bigO{s^{1/2}},
-\end{align}
-in the case $s \rightarrow 0$. And,
-\begin{align}
-	\sigma^2 &\sim 1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}}, \label{eq:siginfty}\\
-	C &\sim \frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}},
-\end{align}
-in the case $s \rightarrow \infty$.
-We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit the gain is unable to balance the energy lost due to modulation, as indicated by the logarithm in \eqref{eq:analenergy}.
-Expanding the condition $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for a first-order approximation), we find
-\begin{align}
-	s^* = \left( \frac{a h^2}{2} \right)^{1/2}
-\end{align}
-is the maximum value of $s$ to facilitate a sustainable pulse.
+respectively.
 
@@
 In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
-One of the most common form is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+One of the most common form is a hyperbolic secant \cite{coen1997, finot2008, mitschke1986, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}
@@
 
-In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
+In Fig.
+\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
 In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transform.
 Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity giving a bi-modal appearance.
-Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
+Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results \cite{chen2008, rothenberg1989b, tomlinson1985}.
 As the nonlinearity parameter, $b$, is increased, the two lobes in the Fourier transform become more pronounced and the tails decay more sharply indicating wave breaking.
 However, once a critical point is reached SPM plays a more substantial role, leading to modulation instability.
-This phenomenon is highlighted in Fig.~\ref{fig:breakevo}.
+This phenomenon is highlighted in Fig.
+\ref{fig:breakevo}.
 By increasing the nonlinearity, and decreasing the dispersion we find the pulse begins to `breathe'.
@@
 This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
-On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}).
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.
+\ref{fig:convevo}).
 The pulse is able to shed the initial left lobe ($T = -1 / 2$) because of dispersion and modulation, and a central lobe ($T = 0$) is formed and is able to grow due to the gain medium.
@@
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments (Fig.~\ref{fig:error}).
+where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments (Fig.
+\ref{fig:error}).
 We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the methods used experimentally.
@@
 \begin{align}
-	E &= \| A_i \|_2^2.
+	E &= \| A_i \|_2.
 	\label{eq:energy2norm}
@@
 Recall from \eqref{eq:order}, this energy is immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
-We plot the energy, \eqref{eq:energy2norm}, in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
-Unsurprisingly, we find the same sharp boundary as we saw in Fig.~\ref{fig:error}.
+We plot the energy, \eqref{eq:energy2norm}, in the $s$--$b$ plane in Fig.
+\ref{fig:energy}.
+Unsurprisingly, we find the same sharp boundary as we saw in Fig.
+\ref{fig:error}.
 In the unstable region (upper-left) the energy is relatively small.
@@
 Finally, we briefly investigate the effect the order of the components has on the dynamics.
-In Section~\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
+In Section \ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
 Here, we consider the effect of swapping the dispersion and modulation components.
-The energy landscape (Fig.~\ref{fig:energyswitch}) is as we would expect.
+The energy landscape (Fig.
+\ref{fig:energyswitch}) is as we would expect.
 In the previous case of having modulation following dispersion, more energy is removed from the pulse tails.
@@
 This has the effect of making the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
-Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
+Comparing with Fig.
+\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
 
@@
 \label{sec:conclusion}
-Expanding upon the ideas originally proposed by Cutler~\cite{cutler1955}, and Kuizenga and Siegman~\cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear iterative map model for tuneable ring lasers.
+Expanding upon the ideas originally proposed by Cutler \cite{cutler1955}, and Kuizenga and Siegman \cite{kuizenga1970, kuizenga1970a, siegman1969}, we developed a nonlinear iterative map model for tuneable ring lasers.
 We recovered linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
-Moreover, the solution of the linear model can easily be extended to any modulation function using results of~\cite{calcaterra2008a}.
+Moreover, the solution of the linear model can easily be extended to any modulation function using results of \cite{calcaterra2008a}.
 In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models.
+This phenomenon has been demonstrated in a laboratory setting \cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models.
 
@@
 \section*{Acknowledgement.}
+
+Portions of this work were presented at The V AMMCS International Conference in 2019, ``A new method of modelling tuneable lasers with functional composition'' \cite{metherallammcs}.
 BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling (EP/L015803/1).

### 2020-11-24 Papers/Journal/Tuneable_Lasers.tex
Fixed table and some notation

@@
 \usepackage{tikz}
+\usepackage{mathtools}
 
@@
 \end{align}
-By assuming the incoming energy is $E$ and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we find the energy after amplification is
+By assuming the energy entering the gain fibre is $E_g$ and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we find the energy after amplification is
 \begin{align}
 	\label{eq:engain}
-	E_{\text{out}} &= \Es W \left( \frac{E}{\Es} \exp( E / \Es ) \exp( g_0 L_g ) \right),
+	E_{\text{out}} &= \Es W \left( \frac{E_g}{\Es} \exp( E_g / \Es ) \exp( g_0 L_g ) \right),
 \end{align}
@@
 \begin{align}
-	G(A) &= \left( \frac{\Es}{E} W \left( \frac{E}{\Es} \exp( E / \Es ) \exp( g_0 L_g ) \right) \right)^{1/2} A
+	G(A) &= \left( \frac{\Es}{E_g} W \left( \frac{E_g}{\Es} \exp( E_g / \Es ) \exp( g_0 L_g ) \right) \right)^{1/2} A
 	\label{eq:gainform}
@@
 This assumption is not particularly restrictive.
-Calcaterra and Boldt have shown that Gaussians can form a basis for $L^2(\mathbb{R})$~\cite{calcaterra2008a}.
-Therefore, we can approximate any modulation function in $L^2(\mathbb{R})$ by a sum of \eqref{eq:modform}.
+Calcaterra and Boldt~\cite{calcaterra2008a} have shown that a sum of Gaussian functions can approximate any square integrable function.
+Therefore, our solution extends to any continuous, bounded modulation function.
 
@@
 \begin{align}
-	G(A) &= \left(E^{-1} W \left( a E \textrm{e}^{E}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \nonumber \\
+	G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \nonumber \\
 	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
@@
 	\centering
-	\caption{Range of variation of various parameters.}
+	\caption{Range of parameter values (taken from~\cite{agrawal2013, burgoyne2014, burgoyneemail, tamura1996, usechak2005}).}
  	\label{tab:values}
- 	\begin{tabular}{lcll}
+ 	\begin{tabular}{clll}
 		\hline\noalign{\smallskip}
-		Parameter & Symbol & Value & Sources \\
+		Symbol & Parameter & Value & Units \\
 		\hline\noalign{\smallskip}
-		Absorption of Fibre & $\alpha$ & $10^{-4}$--$0.3\text{ m}^{-1}$  &~\cite{burgoyneemail, shtyrina2017, tomlinson1984, usechak2005} \\
-		Fibre Dispersion & $\beta_2^f$ & $-50$--$50 \text{ ps}^2/ \text{km}$ &~\cite{agrawal2002, agrawal2013, burgoyne2014} \\
-		Fibre Nonlinearity & $\gamma$ & $0.001$--$0.01 \text{ W}^{-1} \text{m}^{-1}$ &~\cite{agrawal2013, finot2008, usechak2005} \\
-		Grating Dispersion & $\beta_2^g L_D$ & $10$--$2000 \text{ ps}^2$ &~\cite{agrawal2002, agrawal2013, burgoyne2014} \\
-		Length of Cavity & $L_T$ & $10$--$100 \text{ m}$ &~\cite{burgoyneemail, tamura1996} \\
-		Length of Fibre & $L_f$ & $0.15$--$1 \text{ m}$ &~\cite{burgoyneemail} \\
-		Length of Gain Fibre & $L_g$ & $2$--$3 \text{ m}$ &~\cite{burgoyne2014, shtyrina2017} \\
-		Modulation Time & $T_M$ & $15$--$150 \text{ ps}$ &~\cite{bohun2015, burgoyneemail, burgoyne2014} \\
-		Reflectivity of Optical Coupler & $R$ & $0.1$--$0.9$ &~\cite{burgoyneemail, tamura1996, yamashita2009} \\
-		Saturation Energy & $\Es$ & $10^3$--$10^4 \text{ pJ}$ &~\cite{burgoyneemail, usechak2005} \\
-		Small Signal Gain & $g_0$ & $1$--$10 \text{ m}^{-1}$ &~\cite{burgoyneemail} \\
+		$\alpha$ & Absorption of fibre & $10^{-4}$--$0.3$ & m$^{-1}$ \\
+		$\beta_2^f$ & Fibre dispersion & $-50$--$50$ & ps$^2$/km \\
+		$\gamma$ & Fibre nonlinearity & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
+		$\beta_2^g L_D$ & Grating dispersion & $10$--$2000$ & ps$^2$ \\
+		$L_T$ & Length of cavity & $10$--$100$ & m \\
+		\vspace*{-2mm} $L_f$ & Length of fibre between & $0.15$--$1$ & m \\
+		& gain and output coupler & & \\
+		$L_g$ & Length of gain fibre & $2$--$3$ & m \\
+		$T_M$ & Modulation Time & $15$--$150$ & ps \\
+		$R$ & Reflectivity of optical coupler & $0.1$--$0.9$ & -- \\
+		$\Es$ & Saturation energy & $10^3$--$10^4$ & pJ \\
+		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
 		\noalign{\smallskip}\hline
@@
 	\frac{C}{1 - \sigma^2} &= C + 2 \frac{s^2}{\sigma^2} (1 + C^2), \label{eq:chirprelation} \\
-	1 &= \frac{W(a E \textrm{e}^E)}{E} h^2 (1 - \sigma^2)^{1/2} \label{eq:energyrelation}
+	1 &= \frac{W(a E_g \textrm{e}^{E_g})}{E_g} h^2 (1 - \sigma^2)^{1/2} \label{eq:energyrelation}
 \end{align}
@@
 in terms of $s$ and $\sigma^2$.
-Moreover, we can obtain the energy of the pulse entering the gain fibre from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the output coupler.
+Moreover, we can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the output coupler.
 Doing so gives
@@
 	C &\sim 1 - s + \frac{1}{2}s^2 + \bigO{s^3}, \\
-	E &\sim \frac{\log (a h^2)}{1 - h^2} - \frac{1}{1 - h^2} \left( 1 + \frac{h^2 \log(a h^2)}{1 - h^2}  \right) s + \bigO{s^2}, \\
+	E &\sim \frac{\log (a h^2)}{1 - h^2} - \frac{1}{1 - h^2} \left( 1 + \frac{h^2 \log(a h^2)}{1 - h^2}  \right) s + \bigO{s^2}, \label{eq:maxenergy} \\
 	P &\sim \frac{\log(ah^2)}{\sqrt{2 \pi}(1 - h^2)} s^{-1/2} + \bigO{s^{1/2}},
@@
 \begin{align}
-	\Delta = \frac{\| |A_i| - |A_{i-1}| \|_2}{\| A_{i-1} \|_2},
+	\Delta = \frac{\| |\mathcal{L}^n(A_0)| - |\mathcal{L}^{n-1}(A_0)| \|_2}{\| \mathcal{L}^{n-1}(A_0) \|_2},
 	\label{eq:error}
 \end{align}
-where $\| \cdot \|_2$ denotes the $L^2(\mathbb{R})$ norm, and $i$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $i = 500$ in our experiments.
+where
+\begin{align}
+	\| f \|_2^2 \coloneqq \int_{-\infty}^\infty |f|^2 \, \df T,
+\end{align}
+and $n$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $n = 500$ in our experiments.
 We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the methods used experimentally.
@@
 
-Also of interest is the energy of the pulse at equilibrium. We compute the energy using \eqref{eq:energy}, or equivalently 
-\begin{align}
-	E &= \| A_i \|_2^2.
-	\label{eq:energy2norm}
-\end{align}
+Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}.
 Recall from \eqref{eq:order}, this energy is immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
-We plot the energy, \eqref{eq:energy2norm}, in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
+We plot the energy in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
 Unsurprisingly, we find the same sharp boundary as we saw in Fig.~\ref{fig:error}.
@@
 From this, we find that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
+Moreover, the maximum energy, which occurs in the limit that both $s$ and $b$ go to zero, is slightly larger than 2.5.
+With our choice of parameters, \eqref{eq:maxenergy} predicts an energy of 2.55 at the origin, inline with Fig.~\ref{fig:energy}.
 
@@
 Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
+Lastly, once again, the energy at the origin is somewhat larger than 2.5, as predicted by \eqref{eq:maxenergy}.
 

### 2020-11-24 Papers/Journal/Tuneable_Lasers.tex
Added stuff about modulator, and fixed some captions

@@
 Finally, we must consider the modulation.
-The modulation is considered to be applied externally in which ever way the operator sees fit.
+Here, we assume the pulse is modulated by an electro-optic modulator.
+This gives the freedom of choosing the profile of the modulation how ever the operator sees fit.
 For simplicity the representation is taken as the Gaussian
@@
 Therefore, our solution extends to any continuous, bounded modulation function.
-
-Saturable Absorber \cite{lapre2019, meng2020}
+Additionally, it is common to use a saturable absorber in place of a modulator.
+In this case, \eqref{eq:modform} can freely be replaced by~\cite{lapre2019, meng2020}
+\begin{align}
+	S(A) &= 1 - \frac{q_0}{1 + |A|^2 / P_\text{sat}},
+\end{align}
+where $q_0$ is the modulation depth, $|A|^2$ is the instantaneous power of the pulse, and $P_\text{sat}$ is the saturation power.
 
@@
 	\includegraphics{Figures/Sample_Gauss}
-	\caption{Solution to the linear model given by \eqref{eq:A0}.}
+	\caption{Linearly chirped Gaussian pulse, \eqref{eq:A0}.}
 	\label{fig:samplegauss}
@@
 \begin{align}
-	C = \frac{\sigma^4 \pm \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
+	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
 	\label{eq:chirp}
@@
 \label{sec:nlresults}
-In this iterative scheme---as well as within the laboratory---we must specify the input pulse shape.
-One of the most common form is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+In this iterative map model---as well as within the laboratory---we must specify the input pulse.
+One of the most common forms is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}
@@
 where $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$, unless specified otherwise.
+Using \eqref{eq:nlA0} as a seed, we simulate the pulse as it travels around the cavity using $2^{18}$ points, and a time span of 16.
 
@@
 		\includegraphics{Figures/Chirp}
-		\caption{Chirp}
-		\label{fig:}
+		\caption{Chirp.}
+		\label{fig:chirp}
 	\end{subfigure} \\
@@
 		\includegraphics{Figures/FT}
-		\caption{Chirp}
-		\label{fig:}
+		\caption{Fourier transform.}
+		\label{fig:ft}
 	\end{subfigure}
-	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.2$, and $E_0 = 0.1$).}
+	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for two values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
 	\label{fig:chirpft}
@@
 
-In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}.
-In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transform.
-Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity giving a bi-modal appearance.
+In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}, and an additional $b$ value.
+In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transforms.
+Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity, giving a bi-modal appearance.
 Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
-As the nonlinearity parameter, $b$, is increased, the two lobes in the Fourier transform become more pronounced and the tails decay more sharply indicating wave breaking.
-However, once a critical point is reached SPM plays a more substantial role, leading to modulation instability.
+As the nonlinearity parameter, $b$, is increased, the chirp increases more sharply across the pulse, and saturates at a larger value.
+Also, the two lobes in the Fourier transform become more pronounced and further apart, and the pulse becomes more rectangular.
+However, after a critical point, SPM plays a more substantial role, leading to modulation instability.
 This phenomenon is highlighted in Fig.~\ref{fig:breakevo}.

### 2020-11-24 Papers/Journal/Tuneable_Lasers.tex
Merged previous models section to into and model section

@@
 
-In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
-In Section~\ref{sec:modelling}, we will briefly review previous mathematical models for ring lasers.
-Then, we will present our own iterative map model in Section~\ref{sec:model}, as well as non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
-We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
-We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
-Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.
-
-\section{Modelling Efforts}
-\label{sec:modelling}
 The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE),
@@
 Here, $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
-In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (occasionally higher order terms are added as well).
-These additions give the generalized nonlinear Schr\"{o}dinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
+In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (and occasionally higher order terms).
+These additions give the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 
-The GNLSE has many applications in nonlinear optics and fibre optic communications, however, in laser physics typically a modulation term is also added to ensure mode-locking, this yields the master equation of mode-locking~\cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005},
-\begin{align}
-	\pdiff{A}{z} &= - i \frac{\beta_2}{2}\pdiff[2]{A}{T} + i \gamma |A|^2 A + \frac{1}{2}g(A) A - \alpha A - M(T).
-	\label{eq:meml}
-\end{align}
-No analytic solution is known for \eqref{eq:meml}---even after making the assumptions that the gain is constant, and the modulation is quadratic~\cite{haus1984, haus1975, haus1996}.
-However, by neglecting certain terms of \eqref{eq:meml} analytic solutions can be found~\cite{burgoyne2014, haus1975, haus1986, haus1991, haus1992, haus1996, tamura1996, usechak2005}.
+The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers a modulation term is typically also added to ensure mode-locking, this yields the master equation of mode-locking (see \cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005}).
+Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known.
 See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
 
-\subsection{Discrete Models}
-\label{sec:discrete}
-Unfortunately, the master equation, \eqref{eq:meml}, is not completely representative of the underlying physics within our laser cavity.
-It is assumed in \eqref{eq:meml} that each process affects the pulse continuously within the cavity.
-As highlighted by Fig.~\ref{fig:cavity}, this can be a poor assumption.
+In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
+In Section~\ref{sec:model}, we will briefly review previous iterative mathematical models, then, we will present our own iterative map model.
+We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
+We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
+Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.
+
+\section{Iterative Map Model}
+\label{sec:model}
+The GNLSE well represents the dynamics in, say, a single optical fibre, it is not completely representative of the underlying physics within a laser cavity.
+It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity.
+As highlighted by Fig.~\ref{fig:cavity}, this can be a poor assumption as we have discrete components.
 Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
-Thus, a better model is one where we consider a simplified version of \eqref{eq:meml} for each component.
-Solving these simplified differential equations yields an algebraic expression for the effect of each individual component.
-The relations can then be functionally composed to give an iterative map for the effect of one round trip of the cavity.
+Thus, a better model is one where we consider separate, simplified, versions of \eqref{eq:nlse} within each component.
+These simplified equations can then be solved, giving an analytic expression for how an input pulse will be transformed after passing through each component.
+We are then able to iteratively send a pulse through each process map to give the total effect of one round trip around the cavity.
+An iterative map method has the advantage of modelling each component directly, which allows us to portray the geometry of the cavity as it is constructed.
 
@@
 
-Despite the development of discrete, block style models, several short-comings exist.
+Despite the development of discrete, iterative models, several short-comings exist.
 None of the previous models have contained every component within a laser cavity---either the nonlinearity or the modulation have been omitted.
@@
 
-\section{Model Derivation}
-\label{sec:model}
-Using the idea of a discrete model presented Section~\ref{sec:modelling}\ref{sec:discrete}, we derive our model from the GNLSE, \eqref{eq:nlse}; however, in the case of the modulation we consider the exact functional form to be determined by the laser operator.
-To accomplish this we follow the method described in Section~\ref{sec:modelling}\ref{sec:discrete}; we neglect all terms but one on the right side of \eqref{eq:nlse} and solve the simplified differential equations.
-
-To proceed we must choose the form of the amplification term, $g(A)$. We assume the gain has the form
+We continue by deriving our own iterative map model by solving a reduced GNLSE for each component---except modulation, which we consider to be applied externally by an electro-optic modulator.
+Within the gain fibre, we assume all other effects are negligible, allowing us to simplify \eqref{eq:nlse} to
+\begin{align}
+	\pdiff{A}{z} &= \frac{1}{2}g(A)A.
+	\label{eq:gainexample}
+\end{align}
+To proceed, we assume the gain has the form
 \begin{align}
@@
 where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}.
-This reduces \eqref{eq:nlse} to
+Thus, \eqref{eq:gainexample} becomes
 \begin{align}
@@
 \end{align}
-for the amplification of the pulse within the Er-doped fibre. Repeating this process for the loss, dispersion, and nonlinearity yields
+for the amplification of the pulse within the Er-doped fibre.
+
+Repeating this same procedure for the loss, dispersion, and nonlinearity yields
 \begin{align}
@@
 where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and $\mathcal{F}$ denotes the Fourier transform.
-Finally, we must consider the modulation.
+Finally, we consider the modulation.
 Here, we assume the pulse is modulated by an electro-optic modulator.
@@
 The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic.
-Note, the permutation of the components is indeed important as the operators do not, in general, commute---unlike the models described in Section~\ref{sec:modelling}\ref{sec:discrete}.
+Note, the permutation of the components is indeed important as the process maps do not, in general, commute---unlike the models described in the beginning of Section~\ref{sec:model}.
 Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.

### 2020-11-26 Papers/Journal/Tuneable_Lasers.tex
Edited section 2, and added a reference

@@
 
-\author[1]{Brady Metherall}
-\author[2,*]{C. Sean Bohun}
+\author[1,3]{Brady Metherall}
+\author[2,4]{C. Sean Bohun}
 
@@
 \label{sec:intro}
+
+% vary 100 nm ~\cite{bohun2015, burgoyne2010, yamashita2009}
+
+% optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}
+
+% optical frequency metrology, material processing, terahertz generation \cite{oktem2010}
+
 Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}.
@@
 New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, woodward2018}.
-Outside of optics, wave breaking occurs in other areas with nonlinear waves such as plasmas, heat propagation, transmission lines, and fluid dynamics~\cite{rothenberg1989b}.
 Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
 However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
-Modulation instability causes a wave to break into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
+Modulation instability causes a degrade into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
+Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
 Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
@@
 
-The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, in the context of lasers a modulation term is typically also added to ensure mode-locking, this yields the master equation of mode-locking (see \cite{haus1984, haus1975, haus1986, haus1992, haus2000, tamura1996, usechak2005}).
+The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, it is regularly generalized further to include a modulation term in the context of lasers.
+This is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
 Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known.
 See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
+The GNLSE well represents the dynamics in, say, a single optical fibre, it is not entirely representative of the underlying physics within a laser cavity.
+It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity.
+Therefore, the GNLSE, and its derivatives, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during one round trip.
+Often, this is the case due to the specialized, discrete components.
 
 In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
-In Section~\ref{sec:model}, we will briefly review previous iterative mathematical models, then, we will present our own iterative map model.
+In Section~\ref{sec:model}, we will briefly review previous iterative mathematical models, then, we will derive our own iterative map model from \eqref{eq:nlse}.
 We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
@@
 \label{sec:model}
-The GNLSE well represents the dynamics in, say, a single optical fibre, it is not completely representative of the underlying physics within a laser cavity.
-It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity.
-As highlighted by Fig.~\ref{fig:cavity}, this can be a poor assumption as we have discrete components.
-Within the cavity, each effect is localized to its corresponding component: almost all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
-Thus, a better model is one where we consider separate, simplified, versions of \eqref{eq:nlse} within each component.
-These simplified equations can then be solved, giving an analytic expression for how an input pulse will be transformed after passing through each component.
-We are then able to iteratively send a pulse through each process map to give the total effect of one round trip around the cavity.
-An iterative map method has the advantage of modelling each component directly, which allows us to portray the geometry of the cavity as it is constructed.
+To resolve some of the issues with an `average' model, it is common to use separate GNLSEs for each component and region in the laser, iteratively passing the pulse from one PDE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
+This method allows us to better encapsulate specific dynamics introduced by each component.
+The main drawback of this method is its extreme computational expense, since a nonlinear PDE must be numerically solved for every component and each of the hundreds of round trips in a given simulation.
+We can alleviate this computational expense by noticing that each effect is localized to its corresponding component in the cavity: essentially all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
+Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
+We get the benefit of the fine-grain simulation over an `average' model, allowing us to reflect the specific geometry of the cavity, without much additional computational cost.
 
-Such a method was first proposed in 1955 by Cutler~\cite{cutler1955} while analyzing a microwave regenerative pulse generator.
-His method was adapted for mode-locked lasers in 1969 by Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969}.
-The effects of the nonlinearity would not be considered until Martinez \emph{et al.}~\cite{martinez1984, martinez1985} modelled passively mode-locked lasers.
-This issue has recently been readdressed by Burgoyne~\cite{burgoyne2014} in the literature for tuneable lasers.
-In each of these models the effect of each block is described by a transfer function.
-
-Despite the development of discrete, iterative models, several short-comings exist.
-None of the previous models have contained every component within a laser cavity---either the nonlinearity or the modulation have been omitted.
-Each component of a tuneable plays a pivotal role and the laser will not function correctly without the inclusion of all of the components.
-Another drawback is that the functional operations of some of the components used in their models are phenomenological.
-While these functions are chosen based on the observed output, they are not necessarily consistent with the underlying physics.
-Finally, the previous models have been unsuccessful in exhibiting the instabilities described in Section~\ref{sec:intro}.
+Iterative map methods have been around since 1955 when Cutler~\cite{cutler1955} analyzed a microwave regenerative pulse generator.
+Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969} adapted Cutler's method for both AM and FM mode-locked lasers in 1969, and Martinez \emph{et al.}~\cite{martinez1984, martinez1985} incorporated the nonlinearity while modelling passively mode-locked lasers.
+This method was used for dispersion-tuned actively mode-locked lasers recently by Burgoyne \emph{et al.}~\cite{burgoyne2014}.
+Each of these models used a prescribed transfer function to describe the effect each component has on the pulse.
+While the transfer functions are chosen suitably to have the effect observed in the laboratory, they are phenomenologically chosen, and not necessarily obtained from the underlying physics.
+Furthermore, these methods have not included the effect of every component, lacking the imperative interplay of dispersion, modulation, and nonlinearity---disallowing their models to exhibit modulation instability.
 
@@
 Additionally, it is common to use a saturable absorber in place of a modulator.
-In this case, \eqref{eq:modform} can freely be replaced by~\cite{lapre2019, meng2020}
+In this case, \eqref{eq:modform} can freely be replaced by~\cite{lapre2019, meng2020, oktem2010, woodward2018}
 \begin{align}
@@
 
-Revisiting the process maps \eqref{eq:gainform}--\eqref{eq:modform} yields the new, non-dimensional, mappings---after dropping the tildes---
+Returning to the process maps \eqref{eq:gainform}--\eqref{eq:modform}, we find the non-dimensional mappings to be (after dropping the tildes)
 \begin{align}
@@
 \end{align}
-with the four dimensionless parameters, as defined by the values in Table~\ref{tab:values},
+with the four dimensionless parameters,
 \begin{equation}
@@
 		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, \\
-		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, & s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2.
+		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, & s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2,
 		\label{eq:ndparam}
@@
 \end{equation}
+as defined by the values in Table~\ref{tab:values}.
 Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the output coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
@@
 Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
-Thus, we must now consider the order of the components.
-As we are most interested in the output of the laser cavity, we shall start with the loss.
-We then pass the pulse through the CFBG followed by the modulator.
-The pulse then travels through the Er-doped fibre to be amplified, and finally we consider the effect of the nonlinearity.
-The nonlinearity must immediately follow the gain in this model---this is where the nonlinearity will have the largest effect since this is where the pulse is most energetic.
-Note, the permutation of the components is indeed important as the process maps do not, in general, commute---unlike the models described in the beginning of Section~\ref{sec:model}.
-Moreover, we prefer the loss to follow the gain and nonlinearity as we wish to minimize the length over which the nonlinearity has an effect, and maximize the output power.
-Functionally we denote one round trip of the cavity by
+Unlike the models models described in the beginning of this section, the permutation of our components is important as the maps \eqref{eq:effects} do not commute with each other.
+Furthermore, the order of the components will be dictated by the geometry of a particular laser, however, we the laser is constructed as in Fig.~\ref{fig:cavity},  with the following justifications.
+The effect of the nonlinearity will me maximized after the pulse passes through the gain fibre---this is the region where the pulse is most energetic.
+Thus, we take the nonlinearity component to follow the gain.
+Similarly, we would want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse.
+This leaves the dispersion and modulation components.
+For now, let us assume the CFBG precedes the modulator.
+Finally, we assume the loss component is our reference point since this corresponds to the output coupler, and thus, the point in the cavity we are able to take our measurements.
+More precisely, let
 \begin{align}
-	\mathcal{L}(A) = F(G(M(D(L(A))))).
+	\mathcal{L}(A) = F(G(M(D(L(A)))))
 	\label{eq:order}
 \end{align}
- The pulse after one complete circuit of the laser cavity is then returned back into the cavity to restart the process.
-A steady solution to this model is one in which the envelope and chirp are unchanged after traversing every component in the cavity---we are uninterested in the phase due to the nature of experimental measurements.
-That is, such that $\mathcal{L}(A) = A \textrm{e}^{i \phi}$---for some $\phi \in \mathbb{R}$.
+denote one complete round trip of the cavity.
+Since a ring laser is cyclic in nature, we use the result of one round trip as the input pulse for the next round trip---restarting the process.
+We continually repeat this procedure until the envelope and chirp of the pulse reaches equilibrium, or the pulse degrades due to modulation instability.
+Note that we are uninterested in the phase change as it is not modified by the maps in a meaningful way, and due to the nature of experimental measurements.
 An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
@@
 By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
-We proceed by assuming the solution will take the form of a chirped Gaussian.
+We proceed by assuming a fixed point will take the form of a linearly chirped Gaussian.
 There are a few reasons for this; the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
@@
 
+\begin{figure*}[tbp]
+	\centering
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Figures/Chirp}
+		\caption{Chirp.}
+		\label{fig:chirp}
+	\end{subfigure} %
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Figures/FT}
+		\caption{Fourier transform.}
+		\label{fig:ft}
+	\end{subfigure}
+	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for two values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
+	\label{fig:chirpft}
+\end{figure*}
+
 The nature of \eqref{eq:var}--\eqref{eq:analpower} makes it difficult to work with.
@@
 	\centering
-	\begin{subfigure}{\columnwidth}
+	\includegraphics{Figures/Break}
+	\caption{Example of a pulse destabilizing from the initial pulse \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.6$, $s = 0.1$, and $E_0 = 0.1$).}
+	\label{fig:breakevo}
+\end{figure}
+
+\begin{figure}[tbp]
 	\centering
-		\includegraphics{Figures/Chirp}
-		\caption{Chirp.}
-		\label{fig:chirp}
-	\end{subfigure} \\
-	\vspace{3mm}
-	\begin{subfigure}{\columnwidth}
-		\centering
-		\includegraphics{Figures/FT}
-		\caption{Fourier transform.}
-		\label{fig:ft}
-	\end{subfigure}
-	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for two values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
-	\label{fig:chirpft}
+	\includegraphics{Figures/Conv}
+	\caption{Example of a pulse coming to equilibrium from noise ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.1$, and $E_0 = 0.1$).}
+	\label{fig:convevo}
 \end{figure}
@@
 From this, it is clear the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/Break}
-	\caption{Example of a pulse destabilizing from the initial pulse \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.6$, $s = 0.1$, and $E_0 = 0.1$).}
-	\label{fig:breakevo}
-\end{figure}
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/Conv}
-	\caption{Example of a pulse coming to equilibrium from noise ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.1$, and $E_0 = 0.1$).}
-	\label{fig:convevo}
-\end{figure}
 
@@
 
+%The authors would like to thank O. Aytür for critical reading of the manuscript
+
 \section*{Disclosures.}

### 2020-11-26 Papers/Journal/Cavity.tex
Finished rewriting, proper draft finished!

@@
 \draw (0.5,2.25) circle (0.5cm);
-\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-Doped \\ Fibre};
+\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ fibre};
 \draw (0.5,1.75) circle (0.5cm);
@@
 % Coupler and output
-\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser Output};
-\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ Coupler};
+\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser output};
+\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ coupler};
 
@@
 
-\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical Circulator};
+\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical circulator};
 \draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);
@@
 % Arrows
-\draw [->,>=stealth,domain=20:70] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
-\draw [->,>=stealth,domain=110:160] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
-\draw [->,>=stealth,domain=110:160] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
-\draw [->,>=stealth,domain=200:250] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
-\draw [->,>=stealth,domain=200:250] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
-\draw [->,>=stealth,domain=290:340] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+\draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+\draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+\draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
+\draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
+\draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+\draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+
+\draw [->,>=stealth,domain=270:360,blue] plot ({2.325+0.5*cos(\x)}, {4.675+0.5*sin(\x)});
+\draw [->,>=stealth,blue] (2.125, 4.675-0.5) -- (2.325+0.6, 4.675-0.5);
 
@@
 
-% Arrows
-%\draw[-stealth] (2.16,0) -- (2.15,0);
-%\draw[-stealth] (2.39,4) -- (2.4,4);
-%\draw[-stealth] (6.76,0) -- (6.75,0);
-%\draw[-stealth] (7.09,4) -- (7.1,4);
-%\draw[-stealth] (-0.649,0) -- (-0.65,0);
-%\draw[-stealth] (-0.351,4) -- (-0.35,4);
 \end{tikzpicture}

### 2020-11-26 Papers/Journal/Tuneable_Lasers.tex
Finished rewriting, proper draft finished!

@@
 \begin{abstract}
-	We propose a nonlinear iterative map for tuneable ring lasers.
-Using the generalized nonlinear Schr\"odinger equation, expressions for the transformations undergone by the laser pulse are derived for each of the five components (gain, loss, dispersion, modulation, and nonlinearity) within the laser cavity.
-These transformations are then iteratively composed to give the overall effect of one round trip of the cavity.
-We first examine the linear version of the model which we solve analytically.
-Then the full nonlinear model is investigated numerically.
-The nonlinear model is able to exhibit wave breaking as well as modulation instability.
-We highlight the rich landscape and sharp divide for a particular plane of the parameter space.
+	Simple mathematical models have been unable to predict the conditions that lead to instabilities in a tuneable ring laser.
+Here, we propose a nonlinear iterative map model for tuneable ring lasers.
+Solving a reduced nonlinear Schr\"odinger equation for each component, we obtain an algebraic map for each component in the laser cavity, which we then iterate through to give the effect of one complete round trip.
+By neglecting the nonlinearity initially, we find and analyze the analytic fixed point solution of a linearly chirped Gaussian.
+We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as an initial pulse evolves during many round trips of the cavity.
+In this nonlinear case, we find the chirp saturates, and envelope of the pulse becomes more rectangular in shape.
+Finally, for a nominal plane in the parameter space, we uncover a rich, sharp boundary separating the stable region and the unstable region where modulation instability degrades the pulse into an unsustainable state.
 \end{abstract}
@@
 \label{sec:intro}
+Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have many applications owing to their ultrashort pulses, a short as 50 femtoseconds \cite{chung2017}, and an ability to tune their output frequency rapidly~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
+The capability to alter the operating frequency makes this kind of laser particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}.
+As well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
+Tuneable lasers are usually constructed in a ring with five main components: optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), Er-doped fibre, and pump laser.
+A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
+Due to the high power and ultrashort duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.
 
-% vary 100 nm ~\cite{bohun2015, burgoyne2010, yamashita2009}
-
-% optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}
-
-% optical frequency metrology, material processing, terahertz generation \cite{oktem2010}
-
-Tuneable lasers have the ability to vary the frequency of their output by up to about 100 nanometres~\cite{bohun2015, burgoyne2010, yamashita2009}.
-This ability to vary the frequency leads to applications such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, deep tissue multi-photon microscopy~\cite{chung2017}, and diagnostics of ultrafast processes~\cite{burgoyne2014, silfvast2004}.
-Tuneable lasers are usually constructed in a ring with five main components: output coupler, chirped fibre Bragg grating (CFBG), modulator, Er-doped fibre, and pump laser.
-A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
-Due to the high power and short duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.
-
-Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, shao2019, woodward2018}.
+Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, oktem2010, shao2019, woodward2018}.
 The two effects of most interest for this paper are wave breaking, and modulation instability.
@@
 	\input{Cavity}
-	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}. The laser pulses travel clockwise around each loop.}
+	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
+The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped fibre.
+The main laser travels clockwise around the right-hand loop (blue arrows) passing through each component, with most of the pulse exiting the cavity through the optical coupler.}
 	\label{fig:cavity}
@@
 
-The standard equation for studying nonlinear optics is the nonlinear Schr\"odinger equation (NLSE),
+The canonical equation in nonlinear optics is the nonlinear Schr\"odinger equation (NLSE),
 \begin{align}
@@
 \end{align}
-Here, $A = A(T, z) : \mathbb{R}^2 \mapsto \mathbb{C}$ is the complex pulse amplitude, $\beta_2 \in \mathbb{R}$ is the second order dispersion, and $\gamma \in \mathbb{R}$ is the coefficient of nonlinearity.
-In practice, the NLSE, \eqref{eq:smallnlse}, lacks a few key terms, thus, it is often generalized by adding amplification and loss (and occasionally higher order terms).
-These additions give the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
+Here, $A = A(T, z)$ is the complex pulse envelope, $T$ is co-moving time, $z$ is the propagation coordinate, and $\beta_2$ and $\gamma$ are the group velocity dispersion and Kerr nonlinearity, respectively.
+Typically, \eqref{eq:smallnlse} is generalized to incorporate terms more specific to laser physics.
+A gain term and loss term are added (and sometimes higher order dispersion), to give the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 \end{align}
-where $g(A)$ is an amplifying term due to the gain, and $\alpha \in \mathbb{R}^+$ is the loss due to scattering and absorption.
+where $g(A)$ is an amplifying term due to the gain fibre, and $\alpha$ is the loss due to scattering and absorption.
 
 The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, it is regularly generalized further to include a modulation term in the context of lasers.
-This is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
+The resulting equation is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
 Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known.
@@
 The main drawback of this method is its extreme computational expense, since a nonlinear PDE must be numerically solved for every component and each of the hundreds of round trips in a given simulation.
-We can alleviate this computational expense by noticing that each effect is localized to its corresponding component in the cavity: essentially all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Erbium-doped fibre, \emph{et cetera}.
+We can alleviate this computational expense by noticing that each effect is localized to its corresponding component in the cavity: essentially all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Er-doped fibre, \emph{et cetera}.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
@@
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}.
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser.
 Thus, \eqref{eq:gainexample} becomes
@@
 \end{align}
-where $R$ is the reflectivity of the output coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the output coupler, and $\mathcal{F}$ denotes the Fourier transform.
+where $R$ is the reflectivity of the optical coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the optical coupler, and $\mathcal{F}$ denotes the Fourier transform.
 Finally, we consider the modulation.
@@
 as defined by the values in Table~\ref{tab:values}.
-Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the output coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
+Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the optical coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
 Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:ndparam} have their own independent, non-dimensional parameter.
@@
 		\hline\noalign{\smallskip}
-		$\alpha$ & Absorption of fibre & $10^{-4}$--$0.3$ & m$^{-1}$ \\
-		$\beta_2^f$ & Fibre dispersion & $-50$--$50$ & ps$^2$/km \\
-		$\gamma$ & Fibre nonlinearity & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
-		$\beta_2^g L_D$ & Grating dispersion & $10$--$2000$ & ps$^2$ \\
-		$L_T$ & Length of cavity & $10$--$100$ & m \\
-		\vspace*{-2mm} $L_f$ & Length of fibre between & $0.15$--$1$ & m \\
-		& gain and output coupler & & \\
-		$L_g$ & Length of gain fibre & $2$--$3$ & m \\
-		$T_M$ & Modulation Time & $15$--$150$ & ps \\
+		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
+		$\beta_2^g L_D$ & Dispersion provided by CFBG & $10$--$2000$ & ps$^2$ \\
+		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
+		$L_f$ & Length of fibre between gain and optical coupler & $0.15$--$1$ & m \\
+		$L_g$ & Length of the Er-doped gain fibre & $2$--$3$ & m \\
+		$\alpha$ & Loss of fibre due to scattering and absorption & $10^{-4}$--$0.3$ & m$^{-1}$ \\
 		$R$ & Reflectivity of optical coupler & $0.1$--$0.9$ & -- \\
-		$\Es$ & Saturation energy & $10^3$--$10^4$ & pJ \\
+		$\Es$ & Saturation energy of Er-doped gain fibre & $10^3$--$10^4$ & pJ \\
+		$\beta_2^f$ & Second order fibre dispersion & $-50$--$50$ & ps$^2$/km \\
 		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
+		$L_T$ & Total length of fibre in the cavity & $10$--$100$ & m \\
 		\noalign{\smallskip}\hline
@@
 	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
-The pulse decays due to the output coupler, disperses due to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+The pulse decays due to the optical coupler, disperses due to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
 Note, the $z$ axis is not to scale.}
@@
 For now, let us assume the CFBG precedes the modulator.
-Finally, we assume the loss component is our reference point since this corresponds to the output coupler, and thus, the point in the cavity we are able to take our measurements.
+Finally, we assume the loss component is our reference point since this corresponds to the optical coupler, and thus, the point in the cavity we are able to take our measurements.
 More precisely, let
@@
 in terms of $s$ and $\sigma^2$.
-Moreover, we can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the output coupler.
+Moreover, we can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the optical coupler.
 Doing so gives
@@
 Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}.
-Recall from \eqref{eq:order}, this energy is immediately before passing through the output coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
+Recall from \eqref{eq:order}, this energy is immediately before passing through the optical coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
 We plot the energy in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
@@
 This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
+We've shown that a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
+Our model can easily be adapted to specific laser geometries, and to more complicated models of the components.
+For example, incorporating a frequency dependence in the gain function, or using a saturable absorber instead of a Gaussian modulator.
 
@@
 Doing so would provide insight to how the nonlinearity impacts the linearized solution to better understand the manifestation of wave breaking and modulation instability.
+Furthermore, a more detailed analysis of crossing the sharp boundary between stability and instability may provide valuable insight for mechanisms that trigger the instability.
 

### 2020-11-29 Papers/Journal/Tuneable_Lasers.tex
Moved some figures
Read through and edited draft

@@
 \affil[1]{Mathematical Institute, University of Oxford, Radcliffe Observatory Quarter, Woodstock Rd, Oxford OX2 6GG, UK}
-\affil[2]{Facutlty of Science, University of Ontario Institute of Technology, 2000 Simcoe St N, Oshawa, ON L1G 0C5, Canada}
+\affil[2]{Faculty of Science, University of Ontario Institute of Technology, 2000 Simcoe St N, Oshawa, ON L1G 0C5, Canada}
 
@@
 \begin{abstract}
-	Simple mathematical models have been unable to predict the conditions that lead to instabilities in a tuneable ring laser.
+	Simple mathematical models have been unable to predict the conditions leading to instabilities in a tuneable ring laser.
 Here, we propose a nonlinear iterative map model for tuneable ring lasers.
-Solving a reduced nonlinear Schr\"odinger equation for each component, we obtain an algebraic map for each component in the laser cavity, which we then iterate through to give the effect of one complete round trip.
-By neglecting the nonlinearity initially, we find and analyze the analytic fixed point solution of a linearly chirped Gaussian.
-We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as an initial pulse evolves during many round trips of the cavity.
-In this nonlinear case, we find the chirp saturates, and envelope of the pulse becomes more rectangular in shape.
+Solving a reduced nonlinear Schr\"odinger equation for each component in the laser cavity, we obtain an algebraic map for each component.
+Iterating these maps gives the total effect of one complete round trip.
+By neglecting the nonlinearity initially, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
+We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over many round trips of the cavity.
+In this nonlinear case, we find the chirp saturates, and the envelope of the pulse becomes more rectangular in shape.
 Finally, for a nominal plane in the parameter space, we uncover a rich, sharp boundary separating the stable region and the unstable region where modulation instability degrades the pulse into an unsustainable state.
@@
 \label{sec:intro}
-Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have many applications owing to their ultrashort pulses, a short as 50 femtoseconds \cite{chung2017}, and an ability to tune their output frequency rapidly~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
-The capability to alter the operating frequency makes this kind of laser particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}.
-As well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
+Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have a wide range of applications, owing to their ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
+The capability to alter the operating frequency makes this kind of laser particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}; as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
 Tuneable lasers are usually constructed in a ring with five main components: optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), Er-doped fibre, and pump laser.
@@
 The two effects of most interest for this paper are wave breaking, and modulation instability.
-Wave breaking causes the leading edge of a pulse to be red shifted, and the trailing edge blue shifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock is developed~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
-The shifts in frequencies cause the pulse to become more rectangular in the frequency domain with a linear chirp over most of the pulse.
-In optics, wave breaking manifests from self-phase modulation (SPM) which is a direct effect of the Kerr nonlinearity causing the pulse to interfere with itself.
-New frequencies are then generated which induces the rectangular profile~\cite{agrawal2013, woodward2018}.
+Wave breaking causes the leading edge of a pulse to be redshifted, and the trailing edge to be blueshifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edge.
+In optics, wave breaking manifests from self-phase modulation (SPM), which is a direct effect of the Kerr nonlinearity, causing the pulse to interfere with itself.
+New frequencies are then generated such that a rectangular profile is induced~\cite{agrawal2013, woodward2018}.
 Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
 However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
-Modulation instability causes a degrade into short pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
+Modulation instability causes a pulse to degrade into much shorter, less intense pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
 Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
@@
 	\input{Cavity}
-	\caption{Typical cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
+	\caption{Common cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
 The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped fibre.
@@
 
-The canonical equation in nonlinear optics is the nonlinear Schr\"odinger equation (NLSE),
+The canonical equation in nonlinear optics is the nonlinear Schr\"odinger equation,
 \begin{align}
@@
 Typically, \eqref{eq:smallnlse} is generalized to incorporate terms more specific to laser physics.
-A gain term and loss term are added (and sometimes higher order dispersion), to give the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
+A gain term and loss term are added (and sometimes higher order dispersion terms), to give the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 
-The GNLSE, \eqref{eq:nlse}, has many applications in nonlinear optics and fibre optic communications, however, it is regularly generalized further to include a modulation term in the context of lasers.
+The GNLSE, \eqref{eq:nlse}, has applications in nonlinear optics and fibre optic communications, however, it is regularly generalized even further to include a modulation term.
 The resulting equation is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
-Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known.
+Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known to the master equation.
 See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
-The GNLSE well represents the dynamics in, say, a single optical fibre, it is not entirely representative of the underlying physics within a laser cavity.
+While, the GNLSE well represents the dynamics in, say, a single optical fibre, it is not entirely representative of the underlying physics within a laser cavity such as Fig.
+\ref{fig:cavity}.
 It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity.
-Therefore, the GNLSE, and its derivatives, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during one round trip.
+Therefore, the GNLSE, and its generalizations, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during any one round trip.
 Often, this is the case due to the specialized, discrete components.
@@
 In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
-In Section~\ref{sec:model}, we will briefly review previous iterative mathematical models, then, we will derive our own iterative map model from \eqref{eq:nlse}.
+In Section~\ref{sec:model}, we will briefly review previous iterative map models, then, we will derive our own iterative map model from \eqref{eq:nlse}.
 We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
-We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically, by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
 We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
-Finally, the concluding thoughts and possible ideas for future work are given in Section~\ref{sec:conclusion}.
+Finally, the concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
 
@@
 \label{sec:model}
-To resolve some of the issues with an `average' model, it is common to use separate GNLSEs for each component and region in the laser, iteratively passing the pulse from one PDE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
+To resolve some of the issues with an `average' model, it is common to use separate GNLSEs for each component and region in the laser, iteratively passing the pulse from one GNLSE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
 This method allows us to better encapsulate specific dynamics introduced by each component.
-The main drawback of this method is its extreme computational expense, since a nonlinear PDE must be numerically solved for every component and each of the hundreds of round trips in a given simulation.
+The main drawback of this method is its extreme computational expense, since a nonlinear GNLSE must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
 We can alleviate this computational expense by noticing that each effect is localized to its corresponding component in the cavity: essentially all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Er-doped fibre, \emph{et cetera}.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
-We get the benefit of the fine-grain simulation over an `average' model, allowing us to reflect the specific geometry of the cavity, without much additional computational cost.
+This reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise simulation.
 
-Iterative map methods have been around since 1955 when Cutler~\cite{cutler1955} analyzed a microwave regenerative pulse generator.
+Iterative map methods have been used for optics since 1955 when Cutler~\cite{cutler1955} analyzed a microwave regenerative pulse generator.
 Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969} adapted Cutler's method for both AM and FM mode-locked lasers in 1969, and Martinez \emph{et al.}~\cite{martinez1984, martinez1985} incorporated the nonlinearity while modelling passively mode-locked lasers.
@@
 Each of these models used a prescribed transfer function to describe the effect each component has on the pulse.
-While the transfer functions are chosen suitably to have the effect observed in the laboratory, they are phenomenologically chosen, and not necessarily obtained from the underlying physics.
-Furthermore, these methods have not included the effect of every component, lacking the imperative interplay of dispersion, modulation, and nonlinearity---disallowing their models to exhibit modulation instability.
+While the transfer functions are chosen suitably to have the effect observed in the laboratory, the transfer functions are phenomenologically chosen, and not necessarily obtained directly from the underlying physics.
+Furthermore, these methods have not included the effect of every component, lacking the imperative interplay of dispersion, modulation, and nonlinearity---hindering their models to exhibit modulation instability.
 
 We continue by deriving our own iterative map model by solving a reduced GNLSE for each component---except modulation, which we consider to be applied externally by an electro-optic modulator.
-Within the gain fibre, we assume all other effects are negligible, allowing us to simplify \eqref{eq:nlse} to
+Within the gain fibre we assume all other effects are negligible.
+Any dispersion, for example, in the gain fibre pales in comparison to the dispersion introduced by the CFBG.
+Thus, we neglect the dispersion (as well as loss and nonlinearity by the same argument) in the gain fibre, allowing us to simplify \eqref{eq:nlse} to
 \begin{align}
@@
 \begin{align}
-	g(A) &= \frac{g_0}{1 + E / \Es},& E &= \int_{-\infty}^\infty |A|^2 \, \df T,
+	g(A) &= \frac{g_0}{1 + E / \Es},
+\end{align}
+where $g_0$ is a small signal gain, $E$ is the energy of the pulse, defined as
+\begin{align}
+	E &= \int_{-\infty}^\infty |A|^2 \, \df T,
 	\label{eq:energy}
 \end{align}
-where $g_0$ is a small signal gain, $E$ is the energy of the pulse, and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser.
-Thus, \eqref{eq:gainexample} becomes
+and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser. Thus, \eqref{eq:gainexample} becomes
 \begin{align}
@@
 	L(A) &= (1 - R) \exp( - \alpha L_T )A, \\
-	D(A) &= \FTi{\exp( i \omega^2 L_D\beta_2/2 ) \FT{A}}, \\
+	D(A) &= \FTi{\exp( i \omega^2 \beta_2 L_D/2 ) \FT{A}}, \\
 	F(A) &= A \exp( i \gamma |A|^2 L_f ),
 \end{align}
-where $R$ is the reflectivity of the optical coupler (depending on the layout of the laser cavity the loss may instead take the form $L(A) = R \exp( - \alpha L_T )A$), $L_T$ is the total length of the laser circuit, $L_D$ is the length of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the optical coupler, and $\mathcal{F}$ denotes the Fourier transform.
+where $R$ is the reflectivity of the optical coupler, $L_T$ is the total length of the laser circuit, $L_D$ is the `length' of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the optical coupler, and $\mathcal{F}$ denotes the Fourier transform.
 Finally, we consider the modulation.
 Here, we assume the pulse is modulated by an electro-optic modulator.
-This gives the freedom of choosing the profile of the modulation how ever the operator sees fit.
-For simplicity the representation is taken as the Gaussian
+This gives the freedom of choosing the profile of the modulation, how ever the operator sees fit.
+For simplicity, the form is taken as the Gaussian
 \begin{align}
@@
 where $T_M$ is the characteristic width of the modulation.
-This assumption is not particularly restrictive.
+This assumption is not restrictive.
 Calcaterra and Boldt~\cite{calcaterra2008a} have shown that a sum of Gaussian functions can approximate any square integrable function.
@@
 Additionally, it is common to use a saturable absorber in place of a modulator.
-In this case, \eqref{eq:modform} can freely be replaced by~\cite{lapre2019, meng2020, oktem2010, woodward2018}
+In this case, we can exchange \eqref{eq:modform} for~\cite{lapre2019, meng2020, oktem2010, woodward2018}
 \begin{align}
-	S(A) &= 1 - \frac{q_0}{1 + |A|^2 / P_\text{sat}},
+	S(A) &= \left( 1 - \frac{q_0}{1 + |A|^2 / P_\text{sat}} \right) A,
 \end{align}
@@
 Non-dimensionalization is a technique used in mathematical modelling to better understand the relative importance of different processes within a system.
-In essence, we scale all variables by typical values of the system based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
+In essence, we scale all variables by typical values, based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
 Doing so `factors' the dimensional units out of the problem, leaving only dimensionless equations with dimensionless parameters.
-The magnitude of the dimensionless parameters characterizes the dominant dynamics of the system---much like how fluid flow can be described with only the Reynolds number.
-The structure of each process in the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
+The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how fluid flow can be described by the Reynolds number.
+Each process in the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
 \begin{align}
@@
 \begin{align}
-	G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A, & F(A) &= A \exp( i b |A|^2), \nonumber \\
+	G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A, & F(A) &= \exp( i b |A|^2) A, \nonumber \\
 	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
@@
 as defined by the values in Table~\ref{tab:values}.
-Here, $a$ is a measure of the strength of the gain fibre, $h$ is the loss due to absorption and the optical coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
-Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:ndparam} have their own independent, non-dimensional parameter.
+Here, $a$ is a measure of the strength of the gain fibre, $h$ is the total loss due to absorption and the optical coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
+Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:effects} have their own independent, non-dimensional parameter.
 
@@
  	\begin{tabular}{clll}
-		\hline\noalign{\smallskip}
-		Symbol & Parameter & Value & Units \\
+		\hline
+		Parameter & Description & Value & Units \\
 		\hline\noalign{\smallskip}
 		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
-		$\beta_2^g L_D$ & Dispersion provided by CFBG & $10$--$2000$ & ps$^2$ \\
+		$\beta_2 L_D$ & Dispersion provided by CFBG & $10$--$2000$ & ps$^2$ \\
 		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
@@
 		$\Es$ & Saturation energy of Er-doped gain fibre & $10^3$--$10^4$ & pJ \\
-		$\beta_2^f$ & Second order fibre dispersion & $-50$--$50$ & ps$^2$/km \\
 		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
@@
 Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
-Unlike the models models described in the beginning of this section, the permutation of our components is important as the maps \eqref{eq:effects} do not commute with each other.
-Furthermore, the order of the components will be dictated by the geometry of a particular laser, however, we the laser is constructed as in Fig.~\ref{fig:cavity},  with the following justifications.
-The effect of the nonlinearity will me maximized after the pulse passes through the gain fibre---this is the region where the pulse is most energetic.
+Unlike the models described in the beginning of this section, the permutation of our components is important as the maps \eqref{eq:effects} do not necessarily commute with each other.
+The geometry of a particular laser will dictate the order of the process maps.
+We assume the laser is constructed as in Fig.~\ref{fig:cavity}, and provide the following justifications.
+The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---this is the region where the pulse is most energetic.
 Thus, we take the nonlinearity component to follow the gain.
@@
 For now, let us assume the CFBG precedes the modulator.
-Finally, we assume the loss component is our reference point since this corresponds to the optical coupler, and thus, the point in the cavity we are able to take our measurements.
+Finally, we assume the loss component is our starting point since this corresponds to the optical coupler, and thus, allows us to more easily compare to experiments.
 More precisely, let
@@
 Since a ring laser is cyclic in nature, we use the result of one round trip as the input pulse for the next round trip---restarting the process.
-We continually repeat this procedure until the envelope and chirp of the pulse reaches equilibrium, or the pulse degrades due to modulation instability.
-Note that we are uninterested in the phase change as it is not modified by the maps in a meaningful way, and due to the nature of experimental measurements.
+We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse succumbs to modulation instability.
+We are uninterested in the phase change, as it is not modified by \eqref{eq:effects} in a meaningful way, and since the phase cannot easily be measured experimentally.
 An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
@@
 We split the results into two subsections.
-In the following subsection we investigate the low nonlinearity limit, and in Section~\ref{sec:results}\ref{sec:nlresults} we look at the full nonlinear model.
+In the following subsection we investigate the small nonlinearity limit, and in Section~\ref{sec:results}\ref{sec:nlresults} we explore the full nonlinear model.
 
@@
 By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
-We proceed by assuming a fixed point will take the form of a linearly chirped Gaussian.
-There are a few reasons for this; the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be highly correlated to the modulation function, and since a Gaussian is a fixed point of the Fourier transform.
+We proceed by assuming a fixed point solution will take the form of a linearly chirped Gaussian.
+The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be correlated to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
 Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
@@
 \end{figure}
-
-Consider the pulse
-\begin{align}
-	A = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \textrm{e}^{i \phi_0},
-	\label{eq:A0}
-\end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.~\ref{fig:samplegauss}).
-By computing $\mathcal{L}(A)$ using \eqref{eq:order}, and equating to $A \textrm{e}^{i \phi}$, we obtain the conditions
-\begin{align}
-	\frac{\sigma^4}{1 - \sigma^2} &= (\sigma^2 + 2 C s^2)^2 + 4 s^4, \label{eq:sigrelation} \\
-	\frac{C}{1 - \sigma^2} &= C + 2 \frac{s^2}{\sigma^2} (1 + C^2), \label{eq:chirprelation} \\
-	1 &= \frac{W(a E_g \textrm{e}^{E_g})}{E_g} h^2 (1 - \sigma^2)^{1/2} \label{eq:energyrelation}
-\end{align}
-for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find an expression in terms of $\sigma$ only, that is,
-\begin{align}
-	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0. \label{eq:var}
-\end{align}
-As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
-\begin{equation}
-	\begin{split}
-		\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} & \\
-		- s^4 - s^2 & \sqrt{4 + s^4}.
-		\label{eq:equilvar}
-	\end{split}
-\end{equation}
-Additionally, we find the chirp to be
-\begin{align}
-	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
-	\label{eq:chirp}
-\end{align}
-in terms of $s$ and $\sigma^2$.
-Moreover, we can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the optical coupler.
-Doing so gives
-\begin{align}
-	E &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
-	\label{eq:analenergy}
-\end{align}
-By equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, the peak power is found to be
-\begin{align}
-	P &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{\sqrt{\pi} \sigma \left( 1 - h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}.
-	\label{eq:analpower}
-\end{align}
 
@@
 	\end{subfigure}
-	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for two values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
+	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
 	\label{fig:chirpft}
@@
 
-The nature of \eqref{eq:var}--\eqref{eq:analpower} makes it difficult to work with.
+Consider the pulse
+\begin{align}
+	A = \sqrt{P} \exp \left( -(1 + iC) \frac{T^2}{2 \sigma^2} \right) \exp(i \phi_0),
+	\label{eq:A0}
+\end{align}
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.~\ref{fig:samplegauss}).
+By computing \eqref{eq:A0} after one round trip, and solving $\mathcal{L}(A) = A \textrm{e}^{i \phi}$, a tedious manipulation yields the conditions
+\begin{align}
+	\frac{\sigma^4}{1 - \sigma^2} &= (\sigma^2 + 2 C s^2)^2 + 4 s^4, \label{eq:sigrelation} \\
+	\frac{C}{1 - \sigma^2} &= C + 2 \frac{s^2}{\sigma^2} (1 + C^2), \label{eq:chirprelation} \\
+	1 &= \frac{W(a E_g \textrm{e}^{E_g})}{E_g} h^2 (1 - \sigma^2)^{1/2} \label{eq:energyrelation}
+\end{align}
+for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find the expression
+\begin{align}
+	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0,
+	\label{eq:var}
+\end{align}
+which is in terms of $\sigma^2$ only. As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
+\begin{equation}
+	\begin{split}
+		\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} & \\
+		- s^4 - s^2 & \sqrt{4 + s^4}.
+		\label{eq:equilvar}
+	\end{split}
+\end{equation}
+Additionally, the chirp is
+\begin{align}
+	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
+	\label{eq:chirp}
+\end{align}
+in terms of $s$ and $\sigma^2$.
+Moreover, we can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the optical coupler.
+Doing so gives
+\begin{align}
+	E &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
+	\label{eq:analenergy}
+\end{align}
+By equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
+\begin{align}
+	P &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{\sqrt{\pi} \sigma \left( 1 - h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}.
+	\label{eq:analpower}
+\end{align}
+
+The nature of \eqref{eq:var}--\eqref{eq:analpower} makes the expressions difficult to work with.
 However, by asymptotically expanding \eqref{eq:var}--\eqref{eq:analpower} in terms of the dispersion parameter, $s$, we find the simpler relations
@@
 \begin{align}
-	\sigma^2 &\sim 1 - \frac{1}{4}s^{-4} + \frac{3}{8}s^{-8} + \bigO{s^{-12}}, \label{eq:siginfty}\\
-	C &\sim \frac{1}{2}s^{-2} - \frac{3}{8}s^{-6} + \bigO{s^{-10}},
+	\sigma^2 &\sim 1 - \frac{1}{4}s^{-4} + \bigO{s^{-8}}, \label{eq:siginfty}\\
+	C &\sim \frac{1}{2}s^{-2} + \bigO{s^{-6}},
 \end{align}
 in the case $s \rightarrow \infty$.
-We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit the gain is unable to balance the energy lost due to modulation, as indicated by the logarithm in \eqref{eq:analenergy}.
-Expanding the condition $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for a first-order approximation), we find
+We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit too much energy is lost due to dispersion and modulation.
+The gain is not powerful enough to balance the energy lost.
+The argument of the logarithm in \eqref{eq:analenergy} gives us a condition for the pulse to be sustainable.
+Expanding the requirement $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for simple approximation), we find
 \begin{align}
@@
 Our linearized model indeed exhibits a solution of the same form as previous linear models.
-However, by including the effects of the nonlinearity we uncover the rich interplay between dispersion, modulation, and nonlinearity.
+However, by including the effect of the nonlinearity, we uncover the rich interplay between dispersion, modulation, and nonlinearity.
 
@@
 \label{sec:nlresults}
-In this iterative map model---as well as within the laboratory---we must specify the input pulse.
-One of the most common forms is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+The nonlinear solution requires a numerical simulation, and so we must specify the input pulse---as in the laboratory.
+One of the common forms is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}
-	A_0 = \Gamma \sech \left( 2 T \right) \textrm{e}^{i \pi / 4},
+	A_0 = \Gamma \sech \left( 2 T \right) \textrm{e}^{i \pi / 4}.
 	\label{eq:nlA0}
 \end{align}
-where $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$, unless specified otherwise.
+Here, $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$, unless specified otherwise.
 Using \eqref{eq:nlA0} as a seed, we simulate the pulse as it travels around the cavity using $2^{18}$ points, and a time span of 16.
+
+In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} after it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}, and two additional $b$ values.
+In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transforms.
+Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity, giving a bi-modal distribution.
+Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
+As the nonlinearity parameter, $b$, is increased, the chirp increases more sharply across the pulse, and saturates at a larger value.
+Also, the two peaks in the Fourier transform become more pronounced and further apart, and the Fourier transform of the pulse becomes more rectangular.
+However, after a critical point, SPM plays a more substantial role, leading to modulation instability.
+This phenomenon is highlighted in Fig.~\ref{fig:breakevo}.
+By decreasing the dispersion from to Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
+During the first two dozen round trips of the cavity, the SPM compounds and becomes detrimental to the pulse.
+This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
+On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
+The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) is formed and is able to grow due to the gain medium.
+This then allows the pulse to come to equilibrium very quickly.
+Furthermore, since the intensity of the initial pulse is relatively small, the effect of SPM is negligible during the first few round trips, allowing the laser to select preferable modes.
+The preferable modes then get amplified, stabilizing the pulse.
+It is clear the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
 
@@
 
-In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} once it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}, and an additional $b$ value.
-In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transforms.
-Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity, giving a bi-modal appearance.
-Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
-As the nonlinearity parameter, $b$, is increased, the chirp increases more sharply across the pulse, and saturates at a larger value.
-Also, the two lobes in the Fourier transform become more pronounced and further apart, and the pulse becomes more rectangular.
-However, after a critical point, SPM plays a more substantial role, leading to modulation instability.
-This phenomenon is highlighted in Fig.~\ref{fig:breakevo}.
-By increasing the nonlinearity, and decreasing the dispersion we find the pulse begins to `breathe'.
-During the first two dozen round trips of the cavity, the SPM compounds and becomes too parasitic to the pulse.
-This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
-On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
-The pulse is able to shed the initial left lobe ($T = -1 / 2$) because of dispersion and modulation, and a central lobe ($T = 0$) is formed and is able to grow due to the gain medium.
-This then allows the pulse to come to equilibrium very quickly.
-Furthermore, since the intensity of the initial pulse is relatively small, the effect of SPM is negligible during the first few round trips which allows the laser to select preferable modes.
-The preferable modes then get amplified which stabilizes the pulse.
-From this, it is clear the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
-
 We now turn our attention to a more quantitative analysis, and characterize the stability of a laser by exploring the parameter space.
-We focus on the $s$--$b$ plane in particular since $a$ and $h$ effect only the amplitude of the pulse, whereas the interplay of dispersion and nonlinearity give rise to the instabilities.
-Additionally, as mentioned, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while coming to equilibrium.
-To identify the stability of a pulse we examine the relative change in the pulse's envelope between consecutive round trips of the cavity.
-We compute this error by
+We focus on the $s$--$b$ plane in particular, since $a$ and $h$ effect only the amplitude of the pulse, whereas the interplay of dispersion and nonlinearity gives rise to the instabilities.
+Additionally, as mentioned, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while initially coming to equilibrium.
+To identify the stability of a pulse, we examine the relative change in the pulse's envelope between consecutive round trips of the cavity.
+We compute this error as
 \begin{align}
@@
 \end{align}
-and $n$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or degrades due to modulation instability---we use $n = 500$ in our experiments.
-We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the methods used experimentally.
+and $n$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates due to modulation instability---we use $n = 500$ in our experiments.
+We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the auto-correlation methods used for experimental measurements.
 We plot the error in Fig.~\ref{fig:error}.
-It is clear the parameter space is split into two distinct regions, divided by an incredibly sharp and complex boundary.
-In the upper-left region the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
+The parameter space is split into two distinct regions, divided by an incredibly sharp and complicated boundary.
+In the upper-left region, the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
 In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable.
 The increase in dispersion, coupled with modulation, allows the laser to balance the nonlinear effects.
-The error in this region is on the order of machine precision, or slightly higher due to the discretization.
+The error in this region is on the order of machine precision.
 
@@
 Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}.
-Recall from \eqref{eq:order}, this energy is immediately before passing through the optical coupler, and so the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
+Given our ordering of the components, \eqref{eq:order}, the energy of the pulse is immediately before it passes through the optical coupler.
+The energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
 We plot the energy in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
@@
 In the stable region (lower-right) we find that the energy smoothly decays as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
-As $s$ increases, more energy is lost due to modulation since the tails of the pulse become larger.
-Similarly, as $b$ increases, high frequencies generated by SPM are reduced by our choice of modulation function.
-From this, we find that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
-Moreover, the maximum energy, which occurs in the limit that both $s$ and $b$ go to zero, is slightly larger than 2.5.
-With our choice of parameters, \eqref{eq:maxenergy} predicts an energy of 2.55 at the origin, inline with Fig.~\ref{fig:energy}.
+As $s$ increases, more energy is lost due to modulation since dispersion increases the length of the tails of the pulse.
+Similarly, as $b$ increases, the additional frequencies generated by SPM are suppressed by our choice of modulation function.
+We find that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
+Moreover, the maximum energy, which occurs in the limit that both $s$ and $b$ go to zero, is 2.5487.
+With our choice of parameters, \eqref{eq:maxenergy} predicts an equilibrium energy of 2.5535 at the origin, confirming the usefulness of the approximation.
 
@@
 Here, we consider the effect of swapping the dispersion and modulation components.
-The energy landscape (Fig.~\ref{fig:energyswitch}) is as we would expect.
-In the previous case of having modulation following dispersion, more energy is removed from the pulse tails.
+The energy landscape (Fig.~\ref{fig:energyswitch}) is largely the same as in Fig.~\ref{fig:energy}.
+In the previous case, with modulation following dispersion, more energy is removed from the pulse tails.
 Whereas, having modulation first, more of this energy remains in the cavity.
 This has the effect of making the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
-Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially farther away from the origin.
-Lastly, once again, the energy at the origin is somewhat larger than 2.5, as predicted by \eqref{eq:maxenergy}.
+Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially away from the origin.
+Once again, the energy at the origin is 2.5487, as we are effectively removing the CFBG in the limit $s \rightarrow 0$.
 
@@
 We recovered linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
-Moreover, the solution of the linear model can easily be extended to any modulation function using results of~\cite{calcaterra2008a}.
-In contrast, with the inclusion of the nonlinearity we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
+Moreover, the solution to the linear model can be extended to any modulation function using results of~\cite{calcaterra2008a}.
+In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
 This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
@@
 
-It is of interest to analyze the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$.
-Doing so would provide insight to how the nonlinearity impacts the linearized solution to better understand the manifestation of wave breaking and modulation instability.
-Furthermore, a more detailed analysis of crossing the sharp boundary between stability and instability may provide valuable insight for mechanisms that trigger the instability.
+Analyzing the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$, is of interest.
+Doing so would provide insight to how the nonlinearity impacts the linear solution to better understand the manifestation of wave breaking and modulation instability.
+Furthermore, a more detailed analysis of crossing the boundary between stability and instability may provide valuable insight for mechanisms that trigger the instability.
 
@@
 BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling (EP/L015803/1).
-
-%The authors would like to thank O. Aytür for critical reading of the manuscript
+The authors would like to thank C.
+Breward for critical reading of the manuscript.
 

### 2020-11-29 Papers/Journal/Tuneable_Lasers.tex
Fixed passive voice

@@
 The two effects of most interest for this paper are wave breaking, and modulation instability.
-Wave breaking causes the leading edge of a pulse to be redshifted, and the trailing edge to be blueshifted (in the anomalous dispersion regime, the effect is reversed) to the point that a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+Wave breaking causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point that a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edge.
@@
 \ref{fig:cavity}.
-It is assumed in \eqref{eq:nlse} that each process affects the pulse continuously within the cavity.
+An assumption of \eqref{eq:nlse} is that each process affects the pulse continuously within the cavity.
 Therefore, the GNLSE, and its generalizations, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during any one round trip.
@@
 Siegman and Kuizenga~\cite{kuizenga1970a, kuizenga1970b, kuizenga1970, siegman1969} adapted Cutler's method for both AM and FM mode-locked lasers in 1969, and Martinez \emph{et al.}~\cite{martinez1984, martinez1985} incorporated the nonlinearity while modelling passively mode-locked lasers.
-This method was used for dispersion-tuned actively mode-locked lasers recently by Burgoyne \emph{et al.}~\cite{burgoyne2014}.
+A linear iterative method was used for dispersion-tuned actively mode-locked lasers recently by Burgoyne \emph{et al.}~\cite{burgoyne2014}.
 Each of these models used a prescribed transfer function to describe the effect each component has on the pulse.
@@
 Doing so `factors' the dimensional units out of the problem, leaving only dimensionless equations with dimensionless parameters.
-The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how fluid flow can be described by the Reynolds number.
+The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how the Reynolds number can describe fluid flow.
 Each process in the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
@@
 The geometry of a particular laser will dictate the order of the process maps.
-We assume the laser is constructed as in Fig.~\ref{fig:cavity}, and provide the following justifications.
+We assume the construction of the laser is as in Fig.~\ref{fig:cavity}, and provide the following justifications.
 The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---this is the region where the pulse is most energetic.
 Thus, we take the nonlinearity component to follow the gain.
-Similarly, we would want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse.
+Similarly, we want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse.
 This leaves the dispersion and modulation components.
@@
 We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse succumbs to modulation instability.
-We are uninterested in the phase change, as it is not modified by \eqref{eq:effects} in a meaningful way, and since the phase cannot easily be measured experimentally.
+The phase change is uninteresting to us, as it is not modified by \eqref{eq:effects} in a meaningful way, and since the phase cannot easily be measured experimentally.
 An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
@@
 We proceed by assuming a fixed point solution will take the form of a linearly chirped Gaussian.
-The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will be correlated to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
-Furthermore, this form is chosen because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
+The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will correlate to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
+Furthermore, we choose this form because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
@@
 \end{align}
-which is in terms of $\sigma^2$ only. As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
+which contains $\sigma^2$ terms only. As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
 \begin{equation}
@@
 in the case $s \rightarrow \infty$.
-We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit too much energy is lost due to dispersion and modulation.
+We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit the pulse loses too much energy due to dispersion and modulation.
 The gain is not powerful enough to balance the energy lost.
@@
 In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transforms.
-Notice that compared to the linear case, higher frequency modes are introduced due to the nonlinearity, giving a bi-modal distribution.
+Notice that compared to the linear case, the nonlinearity introduces higher frequency modes, giving a bi-modal distribution.
 Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
-As the nonlinearity parameter, $b$, is increased, the chirp increases more sharply across the pulse, and saturates at a larger value.
+As the nonlinearity parameter, $b$, increases, the chirp increases more sharply across the pulse, and saturates at a larger value.
 Also, the two peaks in the Fourier transform become more pronounced and further apart, and the Fourier transform of the pulse becomes more rectangular.
 However, after a critical point, SPM plays a more substantial role, leading to modulation instability.
-This phenomenon is highlighted in Fig.~\ref{fig:breakevo}.
+Fig.~\ref{fig:breakevo} highlights this phenomenon.
 By decreasing the dispersion from to Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
@@
 On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
-The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) is formed and is able to grow due to the gain medium.
+The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) forms and is able to grow due to the gain medium.
 This then allows the pulse to come to equilibrium very quickly.
@@
 \end{align}
-and $n$ is chosen to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates due to modulation instability---we use $n = 500$ in our experiments.
+and we choose $n$ to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates due to modulation instability---we use $n = 500$ in our experiments.
 We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the auto-correlation methods used for experimental measurements.
 We plot the error in Fig.~\ref{fig:error}.
-The parameter space is split into two distinct regions, divided by an incredibly sharp and complicated boundary.
+Two distinct regions split the parameter space, divided by an incredibly sharp and complicated boundary.
 In the upper-left region, the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
@@
 As $s$ increases, more energy is lost due to modulation since dispersion increases the length of the tails of the pulse.
-Similarly, as $b$ increases, the additional frequencies generated by SPM are suppressed by our choice of modulation function.
+Our choice of modulation function suppresses the additional frequencies generated by SPM, as $b$ increases.
 We find that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
@@
 We recovered linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
-Moreover, the solution to the linear model can be extended to any modulation function using results of~\cite{calcaterra2008a}.
+Moreover, the solution to the linear model extends to any modulation function using results of~\cite{calcaterra2008a}.
 In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
 This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
-We've shown that a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
-Our model can easily be adapted to specific laser geometries, and to more complicated models of the components.
+We have shown that a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
+Our model easily adapts to specific laser geometries, and to more complicated models of the components.
 For example, incorporating a frequency dependence in the gain function, or using a saturable absorber instead of a Gaussian modulator.
@@
 Analyzing the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$, is of interest.
-Doing so would provide insight to how the nonlinearity impacts the linear solution to better understand the manifestation of wave breaking and modulation instability.
+Doing so will provide insight to how the nonlinearity impacts the linear solution to better understand the manifestation of wave breaking and modulation instability.
 Furthermore, a more detailed analysis of crossing the boundary between stability and instability may provide valuable insight for mechanisms that trigger the instability.

### 2020-11-29 Papers/Journal/Tuneable_Lasers.tex
Fixed weasel words

@@
 By neglecting the nonlinearity initially, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
-We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over many round trips of the cavity.
+We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over hundreds of round trips of the cavity.
 In this nonlinear case, we find the chirp saturates, and the envelope of the pulse becomes more rectangular in shape.
@@
 The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) forms and is able to grow due to the gain medium.
-This then allows the pulse to come to equilibrium very quickly.
-Furthermore, since the intensity of the initial pulse is relatively small, the effect of SPM is negligible during the first few round trips, allowing the laser to select preferable modes.
+This then allows the pulse to come to equilibrium quickly.
+Furthermore, since the intensity of the initial pulse is small compared to the saturation energy, the effect of SPM is negligible during the first few round trips, allowing the laser to select preferable modes.
 The preferable modes then get amplified, stabilizing the pulse.
@@
 Unsurprisingly, we find the same sharp boundary as we saw in Fig.~\ref{fig:error}.
-In the unstable region (upper-left) the energy is relatively small.
+In the unstable region (upper-left) the energy is small.
 Since the pulse is not sustainable in this region it is not able to foster prominent modes, thus, the intensity is low across the entire pulse.
@@
 Here, we consider the effect of swapping the dispersion and modulation components.
-The energy landscape (Fig.~\ref{fig:energyswitch}) is largely the same as in Fig.~\ref{fig:energy}.
+The overall structure of the energy landscape (Fig.~\ref{fig:energyswitch}) is the same as in Fig.~\ref{fig:energy}.
 In the previous case, with modulation following dispersion, more energy is removed from the pulse tails.

### 2020-11-29 Papers/Journal/Tuneable_Lasers.tex
Fixed some commas and long sentences

@@
 \label{sec:intro}
-Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have a wide range of applications, owing to their ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
+Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have a wide range of applications.
+This kind of laser can have ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
 The capability to alter the operating frequency makes this kind of laser particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}; as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
@@
 A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
-Due to the high power and ultrashort duration of the pulses, the Kerr nonlinearity plays a crucial role in the dynamics within the cavity.
+The Kerr nonlinearity plays a crucial role in the dynamics within the cavity due to the high power and ultrashort duration of the pulses.
 
@@
 In essence, we scale all variables by typical values, based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
-Doing so `factors' the dimensional units out of the problem, leaving only dimensionless equations with dimensionless parameters.
+Doing so `factors' the dimensional units out of the problem---leaving only dimensionless equations with dimensionless parameters.
 The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how the Reynolds number can describe fluid flow.
@@
 The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will correlate to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
-Furthermore, we choose this form because it resembles the envelope and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
+Furthermore, we choose this form because it resembles the envelope, and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
@@
 However, after a critical point, SPM plays a more substantial role, leading to modulation instability.
-Fig.~\ref{fig:breakevo} highlights this phenomenon.
+
+Fig.~\ref{fig:breakevo} highlights the phenomenon of modulation instability.
 By decreasing the dispersion from to Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
-During the first two dozen round trips of the cavity, the SPM compounds and becomes detrimental to the pulse.
+During the first two dozen round trips of the cavity the SPM compounds and becomes detrimental to the pulse.
 This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
 On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
-The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) forms and is able to grow due to the gain medium.
+The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) forms, which is able to grow due to the gain medium.
 This then allows the pulse to come to equilibrium quickly.
@@
 Additionally, as mentioned, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while initially coming to equilibrium.
-To identify the stability of a pulse, we examine the relative change in the pulse's envelope between consecutive round trips of the cavity.
+We examine the relative change in the pulse's envelope between consecutive round trips of the cavity to identify the stability of a pulse.
 We compute this error as
@@
 We plot the error in Fig.~\ref{fig:error}.
-Two distinct regions split the parameter space, divided by an incredibly sharp and complicated boundary.
+Two distinct regions split the parameter space, divided by an incredibly sharp, and complicated boundary.
 In the upper-left region, the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.

### 2020-11-29 Papers/Journal/Tuneable_Lasers.tex
Fixed things like it, this, that, etc

@@
 Solving a reduced nonlinear Schr\"odinger equation for each component in the laser cavity, we obtain an algebraic map for each component.
-Iterating these maps gives the total effect of one complete round trip.
+Iterating the maps gives the total effect of one complete round trip.
 By neglecting the nonlinearity initially, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
 We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over hundreds of round trips of the cavity.
-In this nonlinear case, we find the chirp saturates, and the envelope of the pulse becomes more rectangular in shape.
+In the nonlinear case, we find the chirp saturates, and the envelope of the pulse becomes more rectangular in shape.
 Finally, for a nominal plane in the parameter space, we uncover a rich, sharp boundary separating the stable region and the unstable region where modulation instability degrades the pulse into an unsustainable state.
@@
 Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have a wide range of applications.
-This kind of laser can have ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
-The capability to alter the operating frequency makes this kind of laser particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}; as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
+These lasers can have ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
+The capability to alter the operating frequency makes tuneable lasers particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}; as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
 Tuneable lasers are usually constructed in a ring with five main components: optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), Er-doped fibre, and pump laser.
@@
 The two effects of most interest for this paper are wave breaking, and modulation instability.
-Wave breaking causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point that a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+Wave breaking causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edge.
@@
 Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
-This gives rise to the need of understanding the rich landscape of the parameter space, and determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
+Understanding the rich landscape of the parameter space, is important for determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
 
@@
 \end{align}
-where $g(A)$ is an amplifying term due to the gain fibre, and $\alpha$ is the loss due to scattering and absorption.
+where $g(A)$ is an amplifying term owing to the gain fibre, and $\alpha$ is the loss due to scattering and absorption.
 
-The GNLSE, \eqref{eq:nlse}, has applications in nonlinear optics and fibre optic communications, however, it is regularly generalized even further to include a modulation term.
+The GNLSE, \eqref{eq:nlse}, has applications in nonlinear optics and fibre optic communications, however, \eqref{eq:nlse} is regularly generalized even further to include a modulation term.
 The resulting equation is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
-Due to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known to the master equation.
+Owing to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known to the master equation.
 See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
-While, the GNLSE well represents the dynamics in, say, a single optical fibre, it is not entirely representative of the underlying physics within a laser cavity such as Fig.
+While, the GNLSE well represents the dynamics in, say, a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
 \ref{fig:cavity}.
-An assumption of \eqref{eq:nlse} is that each process affects the pulse continuously within the cavity.
-Therefore, the GNLSE, and its generalizations, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during any one round trip.
-Often, this is the case due to the specialized, discrete components.
+An assumption of \eqref{eq:nlse} is each process affects the pulse continuously within the cavity.
+Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during any one round trip.
+Often, this assumption does not hold because of the specialized, discrete components.
 
-In this paper, we will build an iterative map model for the evolution of a laser pulse as it travels though the cavity.
+In this paper, we will build an iterative map model for the evolution of a laser pulse as the pulse travels though the cavity.
 In Section~\ref{sec:model}, we will briefly review previous iterative map models, then, we will derive our own iterative map model from \eqref{eq:nlse}.
@@
 \label{sec:model}
-To resolve some of the issues with an `average' model, it is common to use separate GNLSEs for each component and region in the laser, iteratively passing the pulse from one GNLSE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
+To resolve some of the issues with an `average' model, using separate GNLSEs for each component and region in the laser is common.
+Iteratively passing the pulse from one GNLSE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
 This method allows us to better encapsulate specific dynamics introduced by each component.
-The main drawback of this method is its extreme computational expense, since a nonlinear GNLSE must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
-We can alleviate this computational expense by noticing that each effect is localized to its corresponding component in the cavity: essentially all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only amplified within the Er-doped fibre, \emph{et cetera}.
+The main drawback of this method is the extreme computational expense, since a nonlinear GNLSE must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
+We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is amplified only within the Er-doped fibre, \emph{et cetera}.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
-This reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise simulation.
+Using analytic solutions instead of numerically solving a GNLSE reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise simulation.
 
@@
 \end{align}
-and $\Es$ is the energy at which the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser. Thus, \eqref{eq:gainexample} becomes
+and $\Es$ is the energy that the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser. Thus, \eqref{eq:gainexample} becomes
 \begin{align}
@@
 
-Repeating this same procedure for the loss, dispersion, and nonlinearity yields
+Repeating the same procedure for the loss, dispersion, and nonlinearity yields
 \begin{align}
@@
 Here, we assume the pulse is modulated by an electro-optic modulator.
-This gives the freedom of choosing the profile of the modulation, how ever the operator sees fit.
 For simplicity, the form is taken as the Gaussian
@@
 This assumption is not restrictive.
-Calcaterra and Boldt~\cite{calcaterra2008a} have shown that a sum of Gaussian functions can approximate any square integrable function.
+Calcaterra and Boldt~\cite{calcaterra2008a} have shown a sum of Gaussian functions can approximate any square integrable function.
 Therefore, our solution extends to any continuous, bounded modulation function.
-Additionally, it is common to use a saturable absorber in place of a modulator.
+Additionally, using a saturable absorber in place of a modulator is common in practice.
 In this case, we can exchange \eqref{eq:modform} for~\cite{lapre2019, meng2020, oktem2010, woodward2018}
@@
 as defined by the values in Table~\ref{tab:values}.
-Here, $a$ is a measure of the strength of the gain fibre, $h$ is the total loss due to absorption and the optical coupler, $b$ is the ratio of the frequency shift due to the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
-Furthermore, notice that in this non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:effects} have their own independent, non-dimensional parameter.
+Here, $a$ is a measure of the strength of the gain fibre, $h$ is the total loss due to absorption and the optical coupler, $b$ is the ratio of the frequency shift because of the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
+Furthermore, in non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:effects} have their own independent, non-dimensional parameter.
 
@@
 	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
-The pulse decays due to the optical coupler, disperses due to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+The pulse decays because of the optical coupler, disperses owing to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
 Note, the $z$ axis is not to scale.}
@@
 We assume the construction of the laser is as in Fig.~\ref{fig:cavity}, and provide the following justifications.
-The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---this is the region where the pulse is most energetic.
+The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---after the gain is where the pulse is most energetic.
 Thus, we take the nonlinearity component to follow the gain.
 Similarly, we want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse.
-This leaves the dispersion and modulation components.
+All that remains is the dispersion and modulation components.
 For now, let us assume the CFBG precedes the modulator.
-Finally, we assume the loss component is our starting point since this corresponds to the optical coupler, and thus, allows us to more easily compare to experiments.
+Finally, we assume the loss component is our starting point since the loss corresponds to the optical coupler, and thus, allows us to more easily compare our results with experiments.
 More precisely, let
@@
 We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse succumbs to modulation instability.
-The phase change is uninteresting to us, as it is not modified by \eqref{eq:effects} in a meaningful way, and since the phase cannot easily be measured experimentally.
+The phase change is uninteresting to us, as \eqref{eq:effects} does not modify the phase in a meaningful way, and since the phase cannot easily be measured experimentally.
 An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
@@
 \subsection{Linear Solution}
-By neglecting the effect of the nonlinearity, that is, $b = 0$, a solution can be found analytically.
+By neglecting the effect of the nonlinearity, that is, taking $b = 0$, a solution can be found analytically.
 We proceed by assuming a fixed point solution will take the form of a linearly chirped Gaussian.
 The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will correlate to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
-Furthermore, we choose this form because it resembles the envelope, and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
+Furthermore, we choose a linearly chirped Gaussian because it resembles the envelope, and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
 
@@
 \end{align}
-which contains $\sigma^2$ terms only. As \eqref{eq:var} is a quartic in $\sigma^2$, it has an analytic solution, namely,
+which contains only $\sigma^2$ terms. As \eqref{eq:var} has an analytic solution, as is a quartic in $\sigma^2$, namely,
 \begin{equation}
@@
 in the case $s \rightarrow \infty$.
-We have no asymptotic expansion of the energy or peak power as $s \rightarrow \infty$ since in this limit the pulse loses too much energy due to dispersion and modulation.
+We have no asymptotic expansion of the energy or peak power in the limit $s \rightarrow \infty$ since the pulse loses too much energy because of dispersion and modulation.
 The gain is not powerful enough to balance the energy lost.
@@
 Here, $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$, unless specified otherwise.
-Using \eqref{eq:nlA0} as a seed, we simulate the pulse as it travels around the cavity using $2^{18}$ points, and a time span of 16.
+Using \eqref{eq:nlA0} as a seed, we simulate the pulse travelling around the cavity using $2^{18}$ points, and a time span of 16.
 
-In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} after it has reached equilibrium for the nominal parameter values given in \eqref{eq:ndparam}, and two additional $b$ values.
-In this nonlinear case, we find that the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transforms.
-Notice that compared to the linear case, the nonlinearity introduces higher frequency modes, giving a bi-modal distribution.
+In Fig.~\ref{fig:chirpft} we show the chirp and Fourier transform of the pulse \eqref{eq:nlA0} after reaching equilibrium for the nominal parameter values given in \eqref{eq:ndparam}, and two additional $b$ values.
+In the nonlinear case, we find the equilibrium pulse is no longer Gaussian---as evidenced by the Fourier transforms.
+Notice, in comparison to the linear case, the nonlinearity introduces higher frequency modes, giving a bi-modal distribution.
 Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
@@
 During the first two dozen round trips of the cavity the SPM compounds and becomes detrimental to the pulse.
-This in turn induces modulation instability, and degrades the pulse, until the pulse is no longer stable or sustainable.
+In turn, modulation instability is induced, and degrades the pulse, until the pulse is no longer stable or sustainable.
 On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
-The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) forms, which is able to grow due to the gain medium.
-This then allows the pulse to come to equilibrium quickly.
-Furthermore, since the intensity of the initial pulse is small compared to the saturation energy, the effect of SPM is negligible during the first few round trips, allowing the laser to select preferable modes.
+The pulse is able to shed the initial left lobe ($T \approx -1 / 2$) because of dispersion and modulation, and a central lobe ($T \approx 0$) forms, which is able to grow because of the gain medium.
+The central lobe then allows the pulse to come to equilibrium quickly.
+Furthermore, since the intensity of the initial pulse is small relative to the saturation energy, the effect of SPM is negligible during the first few round trips, allowing the laser to select preferable modes.
 The preferable modes then get amplified, stabilizing the pulse.
-It is clear the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
+Evidently, the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
 
@@
 We examine the relative change in the pulse's envelope between consecutive round trips of the cavity to identify the stability of a pulse.
-We compute this error as
+We compute the error as
 \begin{align}
@@
 \end{align}
-and we choose $n$ to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates due to modulation instability---we use $n = 500$ in our experiments.
-We take the modulus of the pulse since we are only interested in the evolution of the envelope because of the auto-correlation methods used for experimental measurements.
+and we choose $n$ to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates because of modulation instability---we use $n = 500$ in our experiments.
+We take the modulus of the pulse since we are interested in the evolution of only the envelope because of the auto-correlation methods used for experimental measurements.
 We plot the error in Fig.~\ref{fig:error}.
@@
 The increase in dispersion, coupled with modulation, allows the laser to balance the nonlinear effects.
-The error in this region is on the order of machine precision.
+The error in this region is on the order of machine precision, suggesting the pulse has come to equilibrium.
 
@@
 Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}.
-Given our ordering of the components, \eqref{eq:order}, the energy of the pulse is immediately before it passes through the optical coupler.
+Given our ordering of the components, \eqref{eq:order}, the energy of the pulse is immediately before passing through the optical coupler.
 The energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
@@
 In the unstable region (upper-left) the energy is small.
-Since the pulse is not sustainable in this region it is not able to foster prominent modes, thus, the intensity is low across the entire pulse.
-In the stable region (lower-right) we find that the energy smoothly decays as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
-As $s$ increases, more energy is lost due to modulation since dispersion increases the length of the tails of the pulse.
+The pulse is not able to foster prominent modes in this region and is unsustainable, thus, the intensity is low across the entire pulse.
+In the stable region (lower-right) we find the energy smoothly decays as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
+As $s$ increases, more energy is lost because of modulation since dispersion increases the length of the tails of the pulse.
 Our choice of modulation function suppresses the additional frequencies generated by SPM, as $b$ increases.
-We find that a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
-Moreover, the maximum energy, which occurs in the limit that both $s$ and $b$ go to zero, is 2.5487.
+We find a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
+Moreover, the maximum energy, which occurs in the limit where both $s$ and $b$ go to zero, is 2.5487.
 With our choice of parameters, \eqref{eq:maxenergy} predicts an equilibrium energy of 2.5535 at the origin, confirming the usefulness of the approximation.
@@
 In the previous case, with modulation following dispersion, more energy is removed from the pulse tails.
-Whereas, having modulation first, more of this energy remains in the cavity.
-This has the effect of making the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
+Whereas, having modulation first, more energy remains in the cavity.
+The additional energy makes the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
 Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially away from the origin.
@@
 In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-This phenomenon has been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
-We have shown that a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
+These instabilities have been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
+We have shown a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
 Our model easily adapts to specific laser geometries, and to more complicated models of the components.

### 2020-11-29 Papers/Journal/Tuneable_Lasers.tex
Fixed figure justification

@@
 
-\subsection{Combining the Effects}
+\subsection{Combining the Component Maps}
 \label{sec:effects}
@@
 We now turn our attention to a more quantitative analysis, and characterize the stability of a laser by exploring the parameter space.
-We focus on the $s$--$b$ plane in particular, since $a$ and $h$ effect only the amplitude of the pulse, whereas the interplay of dispersion and nonlinearity gives rise to the instabilities.
-Additionally, as mentioned, a conservative initial energy will effect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while initially coming to equilibrium.
+We focus on the $s$--$b$ plane in particular, since $a$ and $h$ affect only the amplitude of the pulse, whereas the interplay of dispersion and nonlinearity gives rise to the instabilities.
+Additionally, as mentioned, a conservative initial energy will affect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while initially coming to equilibrium.
 We examine the relative change in the pulse's envelope between consecutive round trips of the cavity to identify the stability of a pulse.
@@
 
-Finally, we briefly investigate the effect the order of the components has on the dynamics.
+Finally, we briefly investigate the affect the order of the components has on the dynamics.
 In Section~\ref{sec:model}\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.

### 2020-12-03 Papers/Journal/Tuneable_Lasers.tex
My edits are done

@@
 Solving a reduced nonlinear Schr\"odinger equation for each component in the laser cavity, we obtain an algebraic map for each component.
-Iterating the maps gives the total effect of one complete round trip.
+Iterating through the maps gives the total effect of one round trip.
 By neglecting the nonlinearity initially, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
 We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over hundreds of round trips of the cavity.
-In the nonlinear case, we find the chirp saturates, and the envelope of the pulse becomes more rectangular in shape.
+In the nonlinear case, we find the chirp saturates, and the Fourier transform of the pulse becomes more rectangular in shape.
 Finally, for a nominal plane in the parameter space, we uncover a rich, sharp boundary separating the stable region and the unstable region where modulation instability degrades the pulse into an unsustainable state.
@@
 Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
-Within a ring laser cavity wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
-Understanding the rich landscape of the parameter space, is important for determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
+Within a ring laser cavity, wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
+Understanding the rich landscape of the parameter space is important for determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
 
@@
 The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped fibre.
-The main laser travels clockwise around the right-hand loop (blue arrows) passing through each component, with most of the pulse exiting the cavity through the optical coupler.}
+The main laser travels clockwise around the right-hand loop (blue arrows), with most of the pulse exiting the cavity through the optical coupler.}
 	\label{fig:cavity}
@@
 Typically, \eqref{eq:smallnlse} is generalized to incorporate terms more specific to laser physics.
-A gain term and loss term are added (and sometimes higher order dispersion terms), to give the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
+A gain term and a loss term are added (and sometimes higher order dispersion terms), to yield the generalized nonlinear Schr\"odinger equation (GNLSE)~\cite{agrawal2013, bohun2015, finot2008, peng2018, shtyrina2017, yarutkina2013},
 	\begin{align}
@@
 The resulting equation is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
-Owing to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known to the master equation.
+Owing to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known to the master equation or to \eqref{eq:nlse}.
 See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
-While, the GNLSE well represents the dynamics in, say, a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
+While the GNLSE well represents the dynamics in, say, a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
 \ref{fig:cavity}.
@@
 
-In this paper, we will build an iterative map model for the evolution of a laser pulse as the pulse travels though the cavity.
+In this paper, we will build an iterative map model for the evolution of a laser pulse as the pulse travels through the cavity.
 In Section~\ref{sec:model}, we will briefly review previous iterative map models, then, we will derive our own iterative map model from \eqref{eq:nlse}.
@@
 Iteratively passing the pulse from one GNLSE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
-This method allows us to better encapsulate specific dynamics introduced by each component.
-The main drawback of this method is the extreme computational expense, since a nonlinear GNLSE must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
+This method allows for better encapsulation of specific dynamics introduced by each component.
+The main drawback of this method is the extreme computational expense since a nonlinear equation must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
 We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is amplified only within the Er-doped fibre, \emph{et cetera}.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
-Using analytic solutions instead of numerically solving a GNLSE reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise simulation.
+Using analytic maps instead of numerically solving a GNLSE reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise simulation.
 
@@
 While the transfer functions are chosen suitably to have the effect observed in the laboratory, the transfer functions are phenomenologically chosen, and not necessarily obtained directly from the underlying physics.
-Furthermore, these methods have not included the effect of every component, lacking the imperative interplay of dispersion, modulation, and nonlinearity---hindering their models to exhibit modulation instability.
+Furthermore, these methods have not included the effect of every component, lacking the imperative interactions of dispersion, modulation, and nonlinearity---hindering their models to exhibit modulation instability.
 
 We continue by deriving our own iterative map model by solving a reduced GNLSE for each component---except modulation, which we consider to be applied externally by an electro-optic modulator.
-Within the gain fibre we assume all other effects are negligible.
+Within the gain fibre, we assume all other effects are negligible.
 Any dispersion, for example, in the gain fibre pales in comparison to the dispersion introduced by the CFBG.
@@
 \end{align}
-for the amplification of the pulse within the Er-doped fibre.
+for the amplification of the pulse after the Er-doped fibre.
 
@@
 \end{align}
-where $R$ is the reflectivity of the optical coupler, $L_T$ is the total length of the laser circuit, $L_D$ is the `length' of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the optical coupler, and $\mathcal{F}$ denotes the Fourier transform.
-Finally, we consider the modulation.
-Here, we assume the pulse is modulated by an electro-optic modulator.
-For simplicity, the form is taken as the Gaussian
+where $R$ is the reflectivity of the optical coupler, $L_T$ is the total length of fibre in the cavity, $L_D$ is the `length' of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the optical coupler, and $\mathcal{F}$ denotes the Fourier transform.
+
+Finally, we consider the modulation. Here, we assume the pulse is modulated by an electro-optic modulator. For simplicity, the form is taken as the Gaussian
 \begin{align}
@@
 Doing so `factors' the dimensional units out of the problem---leaving only dimensionless equations with dimensionless parameters.
-The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how the Reynolds number can describe fluid flow.
+The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how the Reynolds number describes fluid flow.
 Each process in the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
@@
 as defined by the values in Table~\ref{tab:values}.
-Here, $a$ is a measure of the strength of the gain fibre, $h$ is the total loss due to absorption and the optical coupler, $b$ is the ratio of the frequency shift because of the Kerr nonlinearity to the width of the pulse, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
+Here, $a$ is a measure of the strength of the gain fibre, $h$ is the total loss due to absorption and the optical coupler, $b$ is the frequency shift because of the Kerr nonlinearity, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
 Furthermore, in non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:effects} have their own independent, non-dimensional parameter.
@@
 		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
-		$\beta_2 L_D$ & Dispersion provided by CFBG & $10$--$2000$ & ps$^2$ \\
+		$\beta_2 L_D$ & Dispersion provided by the CFBG & $10$--$2000$ & ps$^2$ \\
 		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
@@
 	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
-The pulse decays because of the optical coupler, disperses owing to the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
 Note, the $z$ axis is not to scale.}
@@
 Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
-Unlike the models described in the beginning of this section, the permutation of our components is important as the maps \eqref{eq:effects} do not necessarily commute with each other.
+Unlike the models described in the beginning of this section, the permutation of our components is important as the maps in \eqref{eq:effects} do not necessarily commute with each other.
+
 The geometry of a particular laser will dictate the order of the process maps.
-We assume the construction of the laser is as in Fig.~\ref{fig:cavity}, and provide the following justifications.
+However, we assume the construction of the laser is as in Fig.~\ref{fig:cavity}, and provide the following justifications.
 The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---after the gain is where the pulse is most energetic.
@@
 	\includegraphics{Figures/Sample_Gauss}
-	\caption{Linearly chirped Gaussian pulse, \eqref{eq:A0}.}
+	\caption{Linearly chirped Gaussian pulse, \eqref{eq:A0} $(\phi_0 = 0)$.}
 	\label{fig:samplegauss}
@@
 	\end{subfigure}
-	\caption{Chirp and Fourier transform at equilibrium (500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
+	\caption{Chirp and Fourier transform at equilibrium (after 500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
 	\label{fig:chirpft}
@@
 \end{align}
-for \eqref{eq:A0} to be in equilibrium. Manipulating \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find the expression
+for \eqref{eq:A0} to be in equilibrium. Using \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find the expression
 \begin{align}
@@
 \end{align}
-which contains only $\sigma^2$ terms. As \eqref{eq:var} has an analytic solution, as is a quartic in $\sigma^2$, namely,
+which contains only $\sigma^2$ terms. \eqref{eq:var} has an analytic solution, as is a quartic in $\sigma^2$, namely,
 \begin{equation}
@@
 in terms of $s$ and $\sigma^2$.
-Moreover, we can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the optical coupler.
+We can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the optical coupler.
 Doing so gives
@@
 
-The nature of \eqref{eq:var}--\eqref{eq:analpower} makes the expressions difficult to work with.
-However, by asymptotically expanding \eqref{eq:var}--\eqref{eq:analpower} in terms of the dispersion parameter, $s$, we find the simpler relations
+The nature of \eqref{eq:equilvar}--\eqref{eq:analpower} make the expressions difficult to work with.
+However, by asymptotically expanding \eqref{eq:equilvar}--\eqref{eq:analpower} in terms of the dispersion parameter, $s$, we find the simpler relations
 \begin{align}
@@
 The argument of the logarithm in \eqref{eq:analenergy} gives us a condition for the pulse to be sustainable.
-Expanding the requirement $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for simple approximation), we find
+Expanding the requirement $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for a simple approximation), we find
 \begin{align}
@@
 
-Our linearized model indeed exhibits a solution of the same form as previous linear models.
+Our linear model indeed exhibits a solution of the same form as previous linear models.
 However, by including the effect of the nonlinearity, we uncover the rich interplay between dispersion, modulation, and nonlinearity.
@@
 \end{align}
-Here, $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$, unless specified otherwise.
+Here, $\Gamma$ is a normalizing factor chosen so the pulse has the initial energy $E_0$, which we take as $E_0 = 0.1$.
 Using \eqref{eq:nlA0} as a seed, we simulate the pulse travelling around the cavity using $2^{18}$ points, and a time span of 16.
@@
 Notice, in comparison to the linear case, the nonlinearity introduces higher frequency modes, giving a bi-modal distribution.
-Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| > 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
+Moreover, we find the pulse is linearly chirped near the peak, but, in the tails, $|T| \gtrsim 1$, the chirp begins to saturate---consistent with the experimental results~\cite{chen2008, rothenberg1989b, tomlinson1985}.
 As the nonlinearity parameter, $b$, increases, the chirp increases more sharply across the pulse, and saturates at a larger value.
@@
 Fig.~\ref{fig:breakevo} highlights the phenomenon of modulation instability.
-By decreasing the dispersion from to Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
+By decreasing the dispersion from Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
 During the first two dozen round trips of the cavity the SPM compounds and becomes detrimental to the pulse.
@@
 The preferable modes then get amplified, stabilizing the pulse.
-Evidently, the initial shape of the pulse is much less important than the initial energy of the pulse, $E_0$, or the strength of the nonlinearity, $b$.
+Evidently, the initial shape of the pulse is much less important than the initial energy of the pulse, or the strength of the nonlinearity.
 
@@
 We now turn our attention to a more quantitative analysis, and characterize the stability of a laser by exploring the parameter space.
-We focus on the $s$--$b$ plane in particular, since $a$ and $h$ affect only the amplitude of the pulse, whereas the interplay of dispersion and nonlinearity gives rise to the instabilities.
+We focus on the $s$--$b$ plane in particular, since $a$ and $h$ affect only the amplitude of the pulse, whereas the interactions of dispersion and nonlinearity give rise to the instabilities.
 Additionally, as mentioned, a conservative initial energy will affect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while initially coming to equilibrium.
-We examine the relative change in the pulse's envelope between consecutive round trips of the cavity to identify the stability of a pulse.
+We examine the relative change in the pulse's envelope between consecutive round trips of the cavity to identify stability.
 We compute the error as
@@
 The increase in dispersion, coupled with modulation, allows the laser to balance the nonlinear effects.
-The error in this region is on the order of machine precision, suggesting the pulse has come to equilibrium.
+The error in this region is on the order of machine precision, suggesting the pulse has indeed reached to equilibrium.
 
@@
 Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}.
-Given our ordering of the components, \eqref{eq:order}, the energy of the pulse is immediately before passing through the optical coupler.
-The energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
+Given our ordering of the components, we compute the energy of the pulse immediately before passing through the optical coupler.
+Thus, the energy of each pulse emitted by the laser is $(1 - h^2) E$, and $h^2 E$ remains in the cavity.
 We plot the energy in the $s$--$b$ plane in Fig.~\ref{fig:energy}.
@@
 As $s$ increases, more energy is lost because of modulation since dispersion increases the length of the tails of the pulse.
-Our choice of modulation function suppresses the additional frequencies generated by SPM, as $b$ increases.
+As $b$ increases, our choice of modulation function helps suppress the additional frequencies generated by SPM, ensuring the pulse remains band-limited.
 We find a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
@@
 In Section~\ref{sec:model}\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
-Here, we consider the effect of swapping the dispersion and modulation components.
+Now, we consider the effect of swapping the dispersion and modulation components.
 The overall structure of the energy landscape (Fig.~\ref{fig:energyswitch}) is the same as in Fig.~\ref{fig:energy}.
@@
 The additional energy makes the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
-Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward, and the energy is larger in the stable region---especially away from the origin.
+Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward and upward, and the energy is larger in the stable region---especially away from the origin.
 Once again, the energy at the origin is 2.5487, as we are effectively removing the CFBG in the limit $s \rightarrow 0$.
@@
 In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-These instabilities have been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, has proven difficult to predict with simple mathematical models~\cite{meng2020}.
+These instabilities have been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, have proven difficult to predict with simple mathematical models~\cite{meng2020}.
 We have shown a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
-Our model easily adapts to specific laser geometries, and to more complicated models of the components.
+Our model easily adapts to specific laser geometries, and to more complicated models of individual components.
 For example, incorporating a frequency dependence in the gain function, or using a saturable absorber instead of a Gaussian modulator.

### 2021-02-09 Papers/Journal/Tuneable_Lasers.tex
Started Chris' edits

@@
 Iterating through the maps gives the total effect of one round trip.
-By neglecting the nonlinearity initially, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
+By neglecting the nonlinearity, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
 We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over hundreds of round trips of the cavity.
@@
 These lasers can have ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
-The capability to alter the operating frequency makes tuneable lasers particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}; as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
-Tuneable lasers are usually constructed in a ring with five main components: optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), Er-doped fibre, and pump laser.
+The capability to alter the operating frequency makes tuneable lasers particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}, as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
+Tuneable lasers are usually constructed in a ring with five main components: an optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), Er-doped fibre, and pump laser.
 A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
@@
 Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, oktem2010, shao2019, woodward2018}.
-The two effects of most interest for this paper are wave breaking, and modulation instability.
+The two effects of most interest for us are wave breaking, and modulation instability.
 Wave breaking causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edge.
-In optics, wave breaking manifests from self-phase modulation (SPM), which is a direct effect of the Kerr nonlinearity, causing the pulse to interfere with itself.
+In optics, wave breaking arises from self-phase modulation (SPM), which is a direct effect of the Kerr nonlinearity, causing the pulse to interfere with itself.
 New frequencies are then generated such that a rectangular profile is induced~\cite{agrawal2013, woodward2018}.
@@
 However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
-Modulation instability causes a pulse to degrade into much shorter, less intense pulses, and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
+Modulation instability causes a pulse to degrade into multiple much shorter, less intense, pulses and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
 Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
@@
 
-The GNLSE, \eqref{eq:nlse}, has applications in nonlinear optics and fibre optic communications, however, \eqref{eq:nlse} is regularly generalized even further to include a modulation term.
-The resulting equation is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes the Ginzburg--Landau equation.
+The GNLSE, \eqref{eq:nlse}, has been applied in nonlinear optics and fibre optic communications.
+However, \eqref{eq:nlse} is regularly generalized even further to include a modulation term.
+The resulting equation is referred to as the master equation of mode-locking (see \cite{haus1975, haus1984, haus2000, tamura1996, usechak2005}), or sometimes as the Ginzburg--Landau equation.
 Owing to the nonlinear term in \eqref{eq:nlse} and the often non-trivial form of $g(A)$, as well as the possible addition of a modulation term, no analytic solution is known to the master equation or to \eqref{eq:nlse}.
-See Haus~\cite{haus2000} for a comprehensive description and history of the theory of mode-locked lasers.
+A comprehensive description of the theory and history of mode-locking lasers is presented in Haus~\cite{haus2000}.
 While the GNLSE well represents the dynamics in, say, a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
 \ref{fig:cavity}.
-An assumption of \eqref{eq:nlse} is each process affects the pulse continuously within the cavity.
+The derivation of \eqref{eq:nlse} assumes that each process affects the pulse continuously within the cavity.
 Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during any one round trip.
@@
 We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
-Finally, the concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
+Finally, our concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
 
@@
 
-We continue by deriving our own iterative map model by solving a reduced GNLSE for each component---except modulation, which we consider to be applied externally by an electro-optic modulator.
+We derive our own iterative map model for the evolution of a pulse through a laser cavity by solving a reduced GNLSE for each component in the cavity---except modulation, which we consider to be applied externally by an electro-optic modulator.
 Within the gain fibre, we assume all other effects are negligible.
@@
 	g(A) &= \frac{g_0}{1 + E / \Es},
+	\label{eq:gainform}
 \end{align}
@@
 \end{align}
-and $\Es$ is the energy that the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser. Thus, \eqref{eq:gainexample} becomes
+and $\Es$ is the energy that the gain begins to saturate~\cite{haus1984, shtyrina2017, silfvast2004}, which depends on the power of the pump laser.
+With the choice of $g(A)$ given in \eqref{eq:gainform}, \eqref{eq:gainexample} becomes
 \begin{align}
@@
 	\label{eq:engain}
-	E_{\text{out}} &= \Es W \left( \frac{E_g}{\Es} \exp( E_g / \Es ) \exp( g_0 L_g ) \right),
+	E_{\text{out}} &= \Es W \left( \frac{E_g}{\Es} \exp \left( \frac{E_g}{\Es} \right) \exp( g_0 L_g ) \right),
 \end{align}
-where $W$ is the Lambert $W$ function. Rewriting \eqref{eq:engain} in terms of the pulse gives
+where $W$ is the Lambert $W$ function. Moreover, as the gain will amplify the pulse without changing the envelope, the pulse after travelling through the gain fibre can be expressed as
 \begin{align}
-	G(A) &= \left( \frac{\Es}{E_g} W \left( \frac{E_g}{\Es} \exp( E_g / \Es ) \exp( g_0 L_g ) \right) \right)^{1/2} A
+	G(A) &= \mathcal{G} A.
+\end{align}
+Then,
+\begin{align}
+	\mathcal{G}^2 E_g &= E_\text{out}
+	\label{eq:ampfact}
+\end{align}
+by \eqref{eq:energy}, \eqref{eq:engain} and \eqref{eq:ampfact}, therefore,
+\begin{align}
+	G(A) &= \left( \frac{\Es}{E_g} W \left( \frac{E_g}{\Es} \exp \left( \frac{E_g}{\Es} \right) \exp( g_0 L_g ) \right) \right)^{1/2} A
 	\label{eq:gainform}
@@
 
-Returning to the process maps \eqref{eq:gainform}--\eqref{eq:modform}, we find the non-dimensional mappings to be (after dropping the tildes)
+We find the non-dimensional mappings (after dropping the tildes) are
 \begin{align}
@@
 	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
-	M(A) &= \exp( -T^2 / 2 ) A, \nonumber
+	M(A) &= \exp( -T^2 / 2 ) A.\, \nonumber
 \end{align}
-with the four dimensionless parameters,
+where we have introduced four dimensionless parameters, namely
 \begin{equation}
@@
 		a &= \exp( g_0 L_g ) \sim 8 \times 10^3, & 
+		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, \\
+		s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2, &
 		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, \\		
-		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, & s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2,
 		\label{eq:ndparam}
@@
 \end{equation}
-as defined by the values in Table~\ref{tab:values}.
-Here, $a$ is a measure of the strength of the gain fibre, $h$ is the total loss due to absorption and the optical coupler, $b$ is the frequency shift because of the Kerr nonlinearity, and $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse.
-Furthermore, in non-dimensional form, the modulation has no associated parameter, and each of the other processes in \eqref{eq:effects} have their own independent, non-dimensional parameter.
+and we have estimated their sizes using values in Table~\ref{tab:values}.
+The dimensionless parameter $a$ is a measure of the strength of the gain fibre, $b$ is the frequency shift because of the Kerr nonlinearity, $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse, and $h$ is the total loss due to absorption and the optical coupler.
+We note that each expression in \eqref{eq:effects} depends on one dimensionless parameter, except the modulation which is parameter free.
 
@@
 Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
-Unlike the models described in the beginning of this section, the permutation of our components is important as the maps in \eqref{eq:effects} do not necessarily commute with each other.
+Unlike the models described in the beginning of this section, the order of our components is important since the maps in \eqref{eq:effects} do not necessarily commute with each other.
 
 The geometry of a particular laser will dictate the order of the process maps.
-However, we assume the construction of the laser is as in Fig.~\ref{fig:cavity}, and provide the following justifications.
+However, we assume the construction of the laser is as shown in Fig.~\ref{fig:cavity}.
 The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---after the gain is where the pulse is most energetic.
@@
 	\includegraphics{Figures/Sample_Gauss}
-	\caption{Linearly chirped Gaussian pulse, \eqref{eq:A0} $(\phi_0 = 0)$.}
+	\caption{Graph of the linearly chirped Gaussian pulse given by \eqref{eq:A0} with $\phi_0 = 0$.}
 	\label{fig:samplegauss}
@@
 \end{align}
-for \eqref{eq:A0} to be in equilibrium. Using \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we are able to eliminate the chirp, and find the expression
+for \eqref{eq:A0} to be in equilibrium. Using \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we eliminate the chirp, $C$, and find an expression relating $\sigma^2$ and $s$, namely
 \begin{align}
-	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0,
+	\sigma^8 + 4 s^4 \sigma^6 - 20 s^4 \sigma^4 + 32 s^4 \sigma^2 - 16 s^4 = 0.
 	\label{eq:var}
 \end{align}
-which contains only $\sigma^2$ terms. \eqref{eq:var} has an analytic solution, as is a quartic in $\sigma^2$, namely,
+\eqref{eq:var} has the analytic solution
 \begin{equation}
@@
 \end{equation}
-Additionally, the chirp is
+Substituting \eqref{eq:equilvar} into \eqref{eq:chirprelation}, we find the chirp is
 \begin{align}
-	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)},
+	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
 	\label{eq:chirp}
 \end{align}
-in terms of $s$ and $\sigma^2$.
-We can obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}, and thus, the equilibrium energy at the optical coupler.
-Doing so gives
+We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation} and, thus, the equilibrium energy at the optical coupler, is
 \begin{align}
@@
 \end{align}
-By equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
+Equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
 \begin{align}
@@
 
-The nature of \eqref{eq:equilvar}--\eqref{eq:analpower} make the expressions difficult to work with.
-However, by asymptotically expanding \eqref{eq:equilvar}--\eqref{eq:analpower} in terms of the dispersion parameter, $s$, we find the simpler relations
+The form of \eqref{eq:equilvar}--\eqref{eq:analpower} make the expressions difficult to work with.
+However, recall that $s$ is small, thus, we asymptotically expand \eqref{eq:equilvar}--\eqref{eq:analpower} assuming $s \ll 1$, and
 \begin{align}
@@
 \end{align}
-in the case $s \rightarrow 0$. And,
+in the limit $s \rightarrow 0$. And,
 \begin{align}

### 2021-02-21 Papers/Journal/Tuneable_Lasers.tex
Finished Chris edits

@@
 The capability to alter the operating frequency makes tuneable lasers particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}, as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
-Tuneable lasers are usually constructed in a ring with five main components: an optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), Er-doped fibre, and pump laser.
+Tuneable lasers are usually constructed in a ring with five main components: an optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), gain fibre (usually doped with Er), and pump laser.
 A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
@@
 	\caption{Common cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
-The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped fibre.
+The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped gain fibre.
 The main laser travels clockwise around the right-hand loop (blue arrows), with most of the pulse exiting the cavity through the optical coupler.}
@@
 
-The GNLSE, \eqref{eq:nlse}, has been applied in nonlinear optics and fibre optic communications.
+The GNLSE, \eqref{eq:nlse}, has been applied in nonlinear optics~\cite{agrawal2013} and fibre optic communications~\cite{agrawal2002}.
 However, \eqref{eq:nlse} is regularly generalized even further to include a modulation term.
@@
 The derivation of \eqref{eq:nlse} assumes that each process affects the pulse continuously within the cavity.
-Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---this assumption breaks down if the pulse undergoes large changes during any one round trip.
+Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---the assumption of continuously effecting the pulse breaks down if the pulse undergoes large changes during any one round trip.
 Often, this assumption does not hold because of the specialized, discrete components.
 
-In this paper, we will build an iterative map model for the evolution of a laser pulse as the pulse travels through the cavity.
-In Section~\ref{sec:model}, we will briefly review previous iterative map models, then, we will derive our own iterative map model from \eqref{eq:nlse}.
-We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
-We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
-We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
-Finally, our concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
-
-\section{Iterative Map Model}
-\label{sec:model}
-To resolve some of the issues with an `average' model, using separate GNLSEs for each component and region in the laser is common.
-Iteratively passing the pulse from one GNLSE to the next \cite{lapre2019, meng2020, oktem2010, woodward2018}.
-This method allows for better encapsulation of specific dynamics introduced by each component.
+To resolve some of the issues with an `average' model, each component and region in the laser is modelled with a separate GNLSE.
+The solution of one GNLSE is used as the initial condition for the GNLSE for the next component~\cite{lapre2019, meng2020, oktem2010, woodward2018}.
+An iterative map model allows for better encapsulation of specific dynamics introduced by each component.
 The main drawback of this method is the extreme computational expense since a nonlinear equation must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
-We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is amplified only within the Er-doped fibre, \emph{et cetera}.
+We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: a majority of the loss is due to the optical coupler, virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only modulated by the modulator, and, the pulse is amplified only within the Er-doped gain fibre.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
@@
 
+In this paper, we will build an iterative map model for the evolution of a laser pulse as the pulse travels through the cavity.
+In Section~\ref{sec:model}, we will derive our own iterative map model from \eqref{eq:nlse}.
+We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
+We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
+Finally, our concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
+
+\section{Iterative Map Model}
+\label{sec:model}
 We derive our own iterative map model for the evolution of a pulse through a laser cavity by solving a reduced GNLSE for each component in the cavity---except modulation, which we consider to be applied externally by an electro-optic modulator.
-Within the gain fibre, we assume all other effects are negligible.
-Any dispersion, for example, in the gain fibre pales in comparison to the dispersion introduced by the CFBG.
-Thus, we neglect the dispersion (as well as loss and nonlinearity by the same argument) in the gain fibre, allowing us to simplify \eqref{eq:nlse} to
+Starting with the gain component, we reduce \eqref{eq:nlse} to
 \begin{align}
-	\pdiff{A}{z} &= \frac{1}{2}g(A)A.
+	\pdiff{A}{z} &= \frac{1}{2}g(A)A,
 	\label{eq:gainexample}
 \end{align}
+by assuming all other effects are negligible.
+Once again, our assumption is justified by the localization of each effect to its corresponding component, allowing us to simplify \eqref{eq:nlse} to \eqref{eq:gainexample} in the gain fibre.
 To proceed, we assume the gain has the form
@@
 	\pdiff{A}{z} &= \frac{g_0 A}{2 \left( 1 + E / \Es \right)}.
+	\label{eq:pdiffgain}
 \end{align}
-By assuming the energy entering the gain fibre is $E_g$ and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we find the energy after amplification is
+Multiplying \eqref{eq:pdiffgain} by the complex conjugate of $A$, we have
+\begin{align}
+	\overline{A} \pdiff{A}{z} &= \frac{g_0}{2 \left( 1 + E / \Es \right)} |A|^2.
+	\label{eq:pdiffgain2}
+\end{align}
+By adding \eqref{eq:pdiffgain2} and the complex conjugate of \eqref{eq:pdiffgain2}, and then integrating over the pulse, we have
+\begin{align}
+	\diff{E}{z} &= \frac{g_0 E}{1 + E / \Es}.
+	\label{eq:energyde}
+\end{align}
+By assuming the energy entering the gain fibre is $E_g$ and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we integrate \eqref{eq:energyde} to find the energy after amplification is
 \begin{align}
@@
 \end{align}
-where $W$ is the Lambert $W$ function. Moreover, as the gain will amplify the pulse without changing the envelope, the pulse after travelling through the gain fibre can be expressed as
+where $W$ is the Lambert $W$ function. Moreover, as the gain will amplify the pulse without changing the shape of the envelope, the pulse after travelling through the gain fibre can be expressed as
 \begin{align}
 	G(A) &= \mathcal{G} A.
+	\label{eq:ampfact}
 \end{align}
@@
 	\mathcal{G}^2 E_g &= E_\text{out}
-	\label{eq:ampfact}
 \end{align}
@@
 \begin{align}
-	G(A) &= \left( \frac{\Es}{E_g} W \left( \frac{E_g}{\Es} \exp \left( \frac{E_g}{\Es} \right) \exp( g_0 L_g ) \right) \right)^{1/2} A
-	\label{eq:gainform}
+	G(A) &= \left( \frac{E_\text{out}}{E_g} \right)^{1/2} A, \\
+	&=	\left( \frac{\Es}{E_g} W \left( \frac{E_g}{\Es} \exp \left( \frac{E_g}{\Es} \right) \exp( g_0 L_g ) \right) \right)^{1/2} A \label{eq:dimgain}
 \end{align}
-for the amplification of the pulse after the Er-doped fibre.
+for the amplification of the pulse after the Er-doped gain fibre.
 
-Repeating the same procedure for the loss, dispersion, and nonlinearity yields
+Repeating the same procedure for the nonlinearity, loss, and dispersion components yields
 \begin{align}
-	L(A) &= (1 - R) \exp( - \alpha L_T )A, \\
-	D(A) &= \FTi{\exp( i \omega^2 \beta_2 L_D/2 ) \FT{A}}, \\
-	F(A) &= A \exp( i \gamma |A|^2 L_f ),
+	\pdiff{A}{z} &= i \gamma |A|^2 A, \label{eq:nlde} \\
+	\pdiff{A}{z} &= - \alpha A,  \label{eq:lossde} \\
+	\pdiff{A}{z} &= - i \frac{\beta_2}{2} \pdiff[2]{A}{T} \label{eq:dispde}
 \end{align}
-where $R$ is the reflectivity of the optical coupler, $L_T$ is the total length of fibre in the cavity, $L_D$ is the `length' of the dispersive medium, $L_f$ is the length of fibre between the amplifier and the optical coupler, and $\mathcal{F}$ denotes the Fourier transform.
+as the reduced versions of \eqref{eq:nlse}, respectively. Solving \eqref{eq:nlde} over a length of fibre $L_f$, we find the effect of the fibre nonlinearity is
+\begin{align}
+	F(A) &= A \exp \left( i \gamma |A|^2 L_f \right). \label{eq:dimnl}
+\end{align}
+Similarly, the effect of the loss is
+\begin{align}
+	L(A) &= (1 - R) \exp( - \alpha L_T )A, \label{eq:dimloss}
+\end{align}
+where $L_T$ is the total length of fibre in the cavity, $R$ is the reflectivity of the optical coupler, and the $(1 - R)$ term  is the loss to the output of the laser.
+The effect of dispersion is obtained by solving \eqref{eq:dispde} over the `length' of the dispersive medium, $L_D$,
+\begin{align}
+	D(A) &= \FTi{\exp( i \omega^2 \beta_2 L_D / 2 ) \FT{A}}, \label{eq:dimdisp}
+\end{align}
+where, $\mathcal{F}$ denotes the Fourier transform.
 
@@
 
+\subsection{Combining the Component Maps}
+\label{sec:effects}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/Evo}
+	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
+The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+Note, the $z$ axis is not to scale.}
+	\label{fig:cavityevo}
+\end{figure}
+
+Now that we have the algebraic effect of each component of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
+Unlike the models described in Section \ref{sec:intro}, the order of our components is important since the maps in \eqref{eq:dimgain}, and \eqref{eq:dimnl}--\eqref{eq:modform} do not necessarily commute with each other.
+
+The geometry of a particular laser will dictate the order of the process maps.
+However, we assume the construction of the laser is as shown in Fig.~\ref{fig:cavity}.
+The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---the pulse is most energetic after being amplified by the gain.
+Thus, we take the nonlinearity component to follow the gain.
+Similarly, we want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse.
+All that remains is the dispersion and modulation components.
+For now, let us assume the CFBG precedes the modulator.
+Finally, we assume the loss component is our starting point since the loss corresponds to the optical coupler, and thus, allows us to more easily compare our results with experiments.
+More precisely, let
+\begin{align}
+	\mathcal{L}(A) = F(G(M(D(L(A)))))
+	\label{eq:order}
+\end{align}
+denote one complete round trip of the cavity.
+Since a ring laser is cyclic in nature, we use the result of one round trip as the input pulse for the next round trip---restarting the process.
+We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse succumbs to modulation instability.
+The phase change is uninteresting to us, as the phase cannot easily be measured experimentally.
+An illustration of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
+
 \subsection{Non-Dimensionalization}
@@
 The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how the Reynolds number describes fluid flow.
-Each process in the laser can be better understood by re-scaling the time, energy, and amplitude by the convenient scalings:
+Each process in the laser can be better understood by re-scaling the time, energies, and amplitude by the convenient scalings:
 \begin{align}
@@
 We find the non-dimensional mappings (after dropping the tildes) are
-\begin{align}
-	G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A, & F(A) &= \exp( i b |A|^2) A, \nonumber \\
-	D(A) &= \FTi{\exp( i s^2 \omega^2 ) \FT{A}}, & L(A) &= h A, \label{eq:effects} \\
-	M(A) &= \exp( -T^2 / 2 ) A.\, \nonumber
-\end{align}
+\begin{equation}
+	\begin{aligned}
+		G(A) &= \left(E_g^{-1} W \left( a E_g \textrm{e}^{E_g}\right) \right)^{1/2} A,\\
+		F(A) &= \exp \left( i b |A|^2 \right) A, \\
+		L(A) &= h A, \\
+		D(A) &= \FTi{\exp \left( i s^2 \omega^2 \right) \FT{A}}, \\
+		M(A) &= \exp \left( -T^2 / 2 \right) A.
+	\end{aligned}
+	\label{eq:effects}
+\end{equation}
 where we have introduced four dimensionless parameters, namely
 \begin{equation}
+	\hspace*{-1mm}
 	\begin{aligned}
@@
 		b &= \gamma L_f \frac{\Es}{T_M} \sim 1, \\
-		s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2, &
-		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, \\		
+		h &= (1 - R) \exp( - \alpha L_T) \sim 0.04, &
+		s &= \left( \frac{\beta_2 L_D}{2 T_M^2} \right)^{1/2} \sim 0.2,	
+	\end{aligned}
 	\label{eq:ndparam}
-	\end{aligned}
 \end{equation}
@@
 
-\subsection{Combining the Component Maps}
-\label{sec:effects}
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/Evo}
-	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
-The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
-Note, the $z$ axis is not to scale.}
-	\label{fig:cavityevo}
-\end{figure}
-
-Now that we have the algebraic effect of each section of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
-Unlike the models described in the beginning of this section, the order of our components is important since the maps in \eqref{eq:effects} do not necessarily commute with each other.
-
-The geometry of a particular laser will dictate the order of the process maps.
-However, we assume the construction of the laser is as shown in Fig.~\ref{fig:cavity}.
-The effect of the nonlinearity will be maximal after the pulse passes through the gain fibre---after the gain is where the pulse is most energetic.
-Thus, we take the nonlinearity component to follow the gain.
-Similarly, we want the loss component to directly follow the nonlinearity in an attempt to minimize the effect the nonlinearity has on the pulse.
-All that remains is the dispersion and modulation components.
-For now, let us assume the CFBG precedes the modulator.
-Finally, we assume the loss component is our starting point since the loss corresponds to the optical coupler, and thus, allows us to more easily compare our results with experiments.
-More precisely, let
-\begin{align}
-	\mathcal{L}(A) = F(G(M(D(L(A)))))
-	\label{eq:order}
-\end{align}
-denote one complete round trip of the cavity.
-Since a ring laser is cyclic in nature, we use the result of one round trip as the input pulse for the next round trip---restarting the process.
-We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse succumbs to modulation instability.
-The phase change is uninteresting to us, as \eqref{eq:effects} does not modify the phase in a meaningful way, and since the phase cannot easily be measured experimentally.
-An example of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
-
 \section{Results}
 \label{sec:results}
-We split the results into two subsections.
-In the following subsection we investigate the small nonlinearity limit, and in Section~\ref{sec:results}\ref{sec:nlresults} we explore the full nonlinear model.
+We split the results into two subsections. First, we investigate the small nonlinearity limit ($b \ll 1$), and then we explore the full nonlinear model.
 
 \subsection{Linear Solution}
-By neglecting the effect of the nonlinearity, that is, taking $b = 0$, a solution can be found analytically.
-We proceed by assuming a fixed point solution will take the form of a linearly chirped Gaussian.
+We neglect the effect of the nonlinearity, that is, we take $b \ll 1$.
+We proceed by assuming a fixed point solution will take the form of a linearly chirped Gaussian, and our aim is to find the variance, chirp, and energy of the pulse.
 The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will correlate to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
@@
 
-Consider the pulse
+We consider the pulse given by
 \begin{align}
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase (Fig.~\ref{fig:samplegauss}).
-By computing \eqref{eq:A0} after one round trip, and solving $\mathcal{L}(A) = A \textrm{e}^{i \phi}$, a tedious manipulation yields the conditions
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase; the pulse is shown in Fig.~\ref{fig:samplegauss}.
+By computing \eqref{eq:A0} after one round trip, and solving $\mathcal{L}(A) = A \textrm{e}^{i \phi}$, tedious manipulations yield the conditions
 \begin{align}
@@
 \end{align}
-\eqref{eq:var} has the analytic solution
+\eqref{eq:var} has the positive, real, analytic solution
 \begin{equation}
@@
 \end{align}
-We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation} and, thus, the equilibrium energy at the optical coupler, is
+We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}:
 \begin{align}
-	E &= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
+	E_g &= \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{h^2 \left( 1 - \sigma^2 \right)^{1/2} - 1}
+\end{align}
+and, thus, the equilibrium energy at the optical coupler, is
+\begin{align}
+	E &= W \left( a E_g \textrm{e}^{E_g} \right) \\
+	&= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
 	\label{eq:analenergy}
 \end{align}
+The argument of the logarithm in \eqref{eq:analenergy} gives us the condition
+\begin{align}
+	a h^2 (1 - \sigma^2)^{1/2} > 1
+	\label{eq:energycond}
+\end{align}
+for the pulse to be sustainable.
+
 Equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
@@
 \end{align}
-in the limit $s \rightarrow 0$. And,
-\begin{align}
-	\sigma^2 &\sim 1 - \frac{1}{4}s^{-4} + \bigO{s^{-8}}, \label{eq:siginfty}\\
-	C &\sim \frac{1}{2}s^{-2} + \bigO{s^{-6}},
-\end{align}
-in the case $s \rightarrow \infty$.
-We have no asymptotic expansion of the energy or peak power in the limit $s \rightarrow \infty$ since the pulse loses too much energy because of dispersion and modulation.
-The gain is not powerful enough to balance the energy lost.
-The argument of the logarithm in \eqref{eq:analenergy} gives us a condition for the pulse to be sustainable.
-Expanding the requirement $a h^2 (1 - \sigma^2)^{1/2} > 1$, from \eqref{eq:analenergy}, using \eqref{eq:siginfty} (for a simple approximation), we find
-\begin{align}
-	s^* = \left( \frac{a h^2}{2} \right)^{1/2}
-\end{align}
-is the maximum value of $s$ to facilitate a sustainable pulse.
+in the limit $s \rightarrow 0$. The expansions in the limit $s \rightarrow \infty$ are given in Appendix \ref{sec:largedisp}.
 
@@
 
+\appendix
+\section{Large Dispersion Limit}
+\label{sec:largedisp}
+In the large dispersion limit, we have $s \rightarrow \infty$, and
+\begin{align}
+	\sigma^2 &\sim 1 - \frac{1}{4}s^{-4} + \bigO{s^{-8}}, \label{eq:siginfty} \\
+	C &\sim \frac{1}{2}s^{-2} + \bigO{s^{-6}}.
+\end{align}
+We have no asymptotic expansion of the energy or peak power in the limit $s \rightarrow \infty$ since the pulse loses too much energy because of dispersion and modulation.
+The gain is not powerful enough to balance the energy lost.
+Expanding the requirement in \eqref{eq:energycond} using \eqref{eq:siginfty}, we find
+\begin{align}
+	s^* = \left( \frac{a h^2}{2} \right)^{1/2}
+	\label{eq:maxs}
+\end{align}
+is the maximum value of $s$ to facilitate a sustainable pulse.
+
 \section*{Acknowledgement.}
-
 Portions of this work were presented at The V AMMCS International Conference in 2019, ``A new method of modelling tuneable lasers with functional composition'' \cite{metherallammcs}.

### 2021-02-21 Papers/Journal/Tuneable_Lasers.tex
Final read through

@@
 By neglecting the nonlinearity, we find a linearly chirped Gaussian to be the analytic fixed point solution, which we analyze asymptotically.
-We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity, as the pulse evolves over hundreds of round trips of the cavity.
+We then numerically solve the full nonlinear model, allowing us to probe the underlying interplay of dispersion, modulation, and nonlinearity as the pulse evolves over hundreds of round trips of the cavity.
 In the nonlinear case, we find the chirp saturates, and the Fourier transform of the pulse becomes more rectangular in shape.
@@
 The capability to alter the operating frequency makes tuneable lasers particularly useful for imaging applications, such as optical coherence tomography~\cite{bohun2015, burgoyne2014, yamashita2009}, coherent anti-Stokes Raman spectroscopy~\cite{burgoyne2014}, and deep tissue multi-photon microscopy~\cite{chung2017}, as well as sensing and measuring of other ultrafast processes~\cite{burgoyne2014, silfvast2004, oktem2010}.
-Tuneable lasers are usually constructed in a ring with five main components: an optical coupler, chirped fibre Bragg grating (CFBG), modulator (or saturable absorber), gain fibre (usually doped with Er), and pump laser.
+Tuneable lasers are usually constructed in a ring with five main components: an optical coupler, a chirped fibre Bragg grating (CFBG), a modulator (or saturable absorber), a gain fibre (usually doped with Er), and a pump laser.
 A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
@@
 However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
-Modulation instability causes a pulse to degrade into multiple much shorter, less intense, pulses and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
+Modulation instability causes a pulse to degrade into multiple, much shorter, less intense pulses and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
 Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
-Within a ring laser cavity, wave breaking and modulation instability can become parasitic leading to an unstable and unsustainable pulse.
+Within a ring laser cavity, wave breaking and modulation instability can become parasitic, leading to an unstable and unsustainable pulse.
 Understanding the rich landscape of the parameter space is important for determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
@@
 	\input{Cavity}
-	\caption{Common cavity of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
+	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
 The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped gain fibre.
@@
 The derivation of \eqref{eq:nlse} assumes that each process affects the pulse continuously within the cavity.
-Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---the assumption of continuously effecting the pulse breaks down if the pulse undergoes large changes during any one round trip.
+Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---the assumption of continuously effecting the pulse breaks down if the pulse undergoes large changes during any one round trip of the cavity.
 Often, this assumption does not hold because of the specialized, discrete components.
@@
 An iterative map model allows for better encapsulation of specific dynamics introduced by each component.
-The main drawback of this method is the extreme computational expense since a nonlinear equation must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
-We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: a majority of the loss is due to the optical coupler, virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only modulated by the modulator, and, the pulse is amplified only within the Er-doped gain fibre.
+The main drawback of this method is the extreme computational expense since a nonlinear partial differential equation must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
+We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: a majority of the loss is due to the optical coupler, virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only modulated by the modulator, and the pulse is amplified only within the Er-doped gain fibre.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
@@
 \end{align}
-By adding \eqref{eq:pdiffgain2} and the complex conjugate of \eqref{eq:pdiffgain2}, and then integrating over the pulse, we have
+By adding \eqref{eq:pdiffgain2} and the complex conjugate of \eqref{eq:pdiffgain2}, and then integrating over $T$, we have
 \begin{align}
@@
 \end{align}
-where $T_M$ is the characteristic width of the modulation.
+where $T_M$ is the characteristic width of modulation.
 This assumption is not restrictive.
@@
 Therefore, our solution extends to any continuous, bounded modulation function.
-Additionally, using a saturable absorber in place of a modulator is common in practice.
+Additionally, using a saturable absorber in place of an electro-optic modulator is common in practice.
 In this case, we can exchange \eqref{eq:modform} for~\cite{lapre2019, meng2020, oktem2010, woodward2018}
@@
 \end{align}
-where $q_0$ is the modulation depth, $|A|^2$ is the instantaneous power of the pulse, and $P_\text{sat}$ is the saturation power.
+where $q_0$ is the modulation depth, and $P_\text{sat}$ is the saturation power.
 
@@
 	\includegraphics{Figures/Evo}
-	\caption{Evolution of the envelope during one round trip of the cavity at equilibrium.
+	\caption{Evolution of the envelope during one round trip of the cavity.
 The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
@@
 Doing so `factors' the dimensional units out of the problem---leaving only dimensionless equations with dimensionless parameters.
-The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---like how the Reynolds number describes fluid flow.
+The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---comparable to how the Reynolds number describes fluid flow.
 Each process in the laser can be better understood by re-scaling the time, energies, and amplitude by the convenient scalings:
@@
 \begin{align}
-	\frac{\sigma^4}{1 - \sigma^2} &= (\sigma^2 + 2 C s^2)^2 + 4 s^4, \label{eq:sigrelation} \\
-	\frac{C}{1 - \sigma^2} &= C + 2 \frac{s^2}{\sigma^2} (1 + C^2), \label{eq:chirprelation} \\
-	1 &= \frac{W(a E_g \textrm{e}^{E_g})}{E_g} h^2 (1 - \sigma^2)^{1/2} \label{eq:energyrelation}
+	\frac{\sigma^4}{1 - \sigma^2} &= \left( \sigma^2 + 2 C s^2 \right)^2 + 4 s^4, \label{eq:sigrelation} \\
+	\frac{C}{1 - \sigma^2} &= C + 2 \frac{s^2}{\sigma^2} \left( 1 + C^2 \right), \label{eq:chirprelation} \\
+	1 &= \frac{W(a E_g \textrm{e}^{E_g})}{E_g} h^2 \left( 1 - \sigma^2 \right)^{1/2} \label{eq:energyrelation}
 \end{align}
@@
 \end{equation}
-Substituting \eqref{eq:equilvar} into \eqref{eq:chirprelation}, we find the chirp is
+We find the chirp is
 \begin{align}
-	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}.
+	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}
 	\label{eq:chirp}
 \end{align}
-We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}:
+by \eqref{eq:chirprelation}. We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}:
 \begin{align}
-	E_g &= \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{h^2 \left( 1 - \sigma^2 \right)^{1/2} - 1}
+	E_g &= \frac{h^2 \left( 1 - \sigma^2 \right)^{1/2} \log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{h^2 \left( 1 - \sigma^2 \right)^{1/2} - 1},
 \end{align}
-and, thus, the equilibrium energy at the optical coupler, is
+and thus, the equilibrium energy at the optical coupler, is
 \begin{align}
-	E &= W \left( a E_g \textrm{e}^{E_g} \right) \\
+	E &= W \left( a E_g \textrm{e}^{E_g} \right), \\
 	&= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
@@
 
-Equating the energy of the pulse in \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
+Equating the energy of the pulse given by \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
 \begin{align}
@@
 
-The form of \eqref{eq:equilvar}--\eqref{eq:analpower} make the expressions difficult to work with.
+The forms of \eqref{eq:equilvar}--\eqref{eq:analpower} make the expressions difficult to work with.
 However, recall that $s$ is small, thus, we asymptotically expand \eqref{eq:equilvar}--\eqref{eq:analpower} assuming $s \ll 1$, and
@@
 Fig.~\ref{fig:breakevo} highlights the phenomenon of modulation instability.
-By decreasing the dispersion from Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
+By decreasing the dispersion compared to Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
 During the first two dozen round trips of the cavity the SPM compounds and becomes detrimental to the pulse.
@@
 Our model easily adapts to specific laser geometries, and to more complicated models of individual components.
-For example, incorporating a frequency dependence in the gain function, or using a saturable absorber instead of a Gaussian modulator.
+For example, incorporating a frequency dependence in the gain function, or model a saturable absorber instead of a Gaussian electro-optic modulator.
 

### 2021-02-21 Papers/Journal/Tuneable_Lasers.tex
Fixed formatting

@@
 \usepackage{mathtools}
+\usepackage{dblfloatfix}
 
@@
 A typical ring laser cavity is depicted in Fig.~\ref{fig:cavity}.
-The Kerr nonlinearity plays a crucial role in the dynamics within the cavity due to the high power and ultrashort duration of the pulses.
+The Kerr nonlinearity plays a crucial role in the dynamics within the cavity due to the high power and ultrashort duration of the~pulses.
+
+\begin{figure}[tbp]
+	\centering
+	\input{Cavity}
+	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
+The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped gain fibre.
+The main laser travels clockwise around the right-hand loop (blue arrows), with most of the pulse exiting the cavity through the optical coupler.}
+	\label{fig:cavity}
+\end{figure}
 
@@
 Understanding the rich landscape of the parameter space is important for determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
-
-\begin{figure}[tbp]
-	\centering
-	\input{Cavity}
-	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
-The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped gain fibre.
-The main laser travels clockwise around the right-hand loop (blue arrows), with most of the pulse exiting the cavity through the optical coupler.}
-	\label{fig:cavity}
-\end{figure}
 
@@
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
-Using analytic maps instead of numerically solving a GNLSE reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise simulation.
+Using analytic maps instead of numerically solving a GNLSE reduces the computational cost, while maintaining the benefit of reflecting the specific geometry of a component-wise~simulation.
 
@@
 While the transfer functions are chosen suitably to have the effect observed in the laboratory, the transfer functions are phenomenologically chosen, and not necessarily obtained directly from the underlying physics.
-Furthermore, these methods have not included the effect of every component, lacking the imperative interactions of dispersion, modulation, and nonlinearity---hindering their models to exhibit modulation instability.
+Furthermore, these methods have not included the effect of every component, lacking the interactions of dispersion, modulation, and nonlinearity---hindering their models ability to exhibit modulation instability.
 
@@
 \label{sec:effects}
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/Evo}
-	\caption{Evolution of the envelope during one round trip of the cavity.
-The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
-Note, the $z$ axis is not to scale.}
-	\label{fig:cavityevo}
-\end{figure}
-
 Now that we have the algebraic effect of each component of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
@@
 An illustration of the evolution of the envelope during one round trip of the laser cavity can be found in Fig.~\ref{fig:cavityevo}.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/Evo}
+	\caption{Evolution of the envelope during one round trip of the cavity.
+The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+Note, the $z$ axis is not to scale.}
+	\label{fig:cavityevo}
+\end{figure}
+
+% Table of parameter values
+\begin{table*}[!b]
+	\centering
+	\caption{Range of parameter values (taken from~\cite{agrawal2013, burgoyne2014, burgoyneemail, tamura1996, usechak2005}).}
+ 	\label{tab:values}
+ 	\begin{tabular}{clll}
+		\hline
+		Parameter & Description & Value & Units \\
+		\hline\noalign{\smallskip}
+		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
+		$\beta_2 L_D$ & Dispersion provided by the CFBG & $10$--$2000$ & ps$^2$ \\
+		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
+		$L_f$ & Length of fibre between gain and optical coupler & $0.15$--$1$ & m \\
+		$L_g$ & Length of the Er-doped gain fibre & $2$--$3$ & m \\
+		$\alpha$ & Loss of fibre due to scattering and absorption & $10^{-4}$--$0.3$ & m$^{-1}$ \\
+		$R$ & Reflectivity of optical coupler & $0.1$--$0.9$ & -- \\
+		$\Es$ & Saturation energy of Er-doped gain fibre & $10^3$--$10^4$ & pJ \\
+		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
+		$L_T$ & Total length of fibre in the cavity & $10$--$100$ & m \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+\end{table*}
 
@@
 We note that each expression in \eqref{eq:effects} depends on one dimensionless parameter, except the modulation which is parameter free.
-
-% Table of parameter values
-\begin{table*}[tbp]
-	\centering
-	\caption{Range of parameter values (taken from~\cite{agrawal2013, burgoyne2014, burgoyneemail, tamura1996, usechak2005}).}
- 	\label{tab:values}
- 	\begin{tabular}{clll}
-		\hline
-		Parameter & Description & Value & Units \\
-		\hline\noalign{\smallskip}
-		$T_M$ & Characteristic modulation time & $15$--$150$ & ps \\
-		$\beta_2 L_D$ & Dispersion provided by the CFBG & $10$--$2000$ & ps$^2$ \\
-		$\gamma$ & Kerr nonlinearity coefficient & $0.001$--$0.01$ & W$^{-1}$ m$^{-1}$ \\
-		$L_f$ & Length of fibre between gain and optical coupler & $0.15$--$1$ & m \\
-		$L_g$ & Length of the Er-doped gain fibre & $2$--$3$ & m \\
-		$\alpha$ & Loss of fibre due to scattering and absorption & $10^{-4}$--$0.3$ & m$^{-1}$ \\
-		$R$ & Reflectivity of optical coupler & $0.1$--$0.9$ & -- \\
-		$\Es$ & Saturation energy of Er-doped gain fibre & $10^3$--$10^4$ & pJ \\
-		$g_0$ & Small signal gain &  $1$--$10$ & m$^{-1}$ \\
-		$L_T$ & Total length of fibre in the cavity & $10$--$100$ & m \\
-		\noalign{\smallskip}\hline
-	\end{tabular}
-\end{table*}
 
@@
 \end{align}
-for \eqref{eq:A0} to be in equilibrium. Using \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we eliminate the chirp, $C$, and find an expression relating $\sigma^2$ and $s$, namely
+for \eqref{eq:A0} to be in equilibrium. Using \eqref{eq:sigrelation} and \eqref{eq:chirprelation} we eliminate the chirp, $C$, and find an expression relating $\sigma^2$ and $s$,~namely
 \begin{align}

### 2021-02-28 Papers/Journal/Tuneable_Lasers.tex
Added Sean's edits

@@
 \label{sec:intro}
-Dispersion-tuned actively mode-locked lasers are an active area of optics research since they have a wide range of applications.
+
+The sophistication of current active research for dispersion-tuned actively mode-locked lasers lies in stark contrast to current modelling efforts.
 These lasers can have ultrashort pulses, as short as 50 femtoseconds \cite{chung2017}, and the ability to tune their output frequency rapidly over a range of over 100 nm~\cite{bohun2015, burgoyne2010, chung2017, yamashita2009}.
@@
 
-Several effects arise within the cavity due to the interplay of dispersion, modulation, and the nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, oktem2010, shao2019, woodward2018}.
+Several effects arise within the cavity due to the interplay of dispersion, modulation, and nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, oktem2010, shao2019, woodward2018}.
 The two effects of most interest for us are wave breaking, and modulation instability.
@@
 \end{align}
-Here, $A = A(T, z)$ is the complex pulse envelope, $T$ is co-moving time, $z$ is the propagation coordinate, and $\beta_2$ and $\gamma$ are the group velocity dispersion and Kerr nonlinearity, respectively.
+Here, $A = A(T, z)$ is the complex pulse envelope, $T$ is the co-moving time, and $z$ is the propagation coordinate.
+The respective parameters, $\beta_2$, and $\gamma$, are the group velocity dispersion and the Kerr nonlinearity.
 Typically, \eqref{eq:smallnlse} is generalized to incorporate terms more specific to laser physics.
@@
 A comprehensive description of the theory and history of mode-locking lasers is presented in Haus~\cite{haus2000}.
-While the GNLSE well represents the dynamics in, say, a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
+While the GNLSE well represents the dynamics in a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
 \ref{fig:cavity}.
 The derivation of \eqref{eq:nlse} assumes that each process affects the pulse continuously within the cavity.
-Therefore, the GNLSE, and generalizations, can be thought of as an `average' model for lasers---the assumption of continuously effecting the pulse breaks down if the pulse undergoes large changes during any one round trip of the cavity.
+The assumption that a single GNLSE applies to the whole laser cavity breaks down if the pulse undergoes large changes during any one round trip.
 Often, this assumption does not hold because of the specialized, discrete components.
@@
 The main drawback of this method is the extreme computational expense since a nonlinear partial differential equation must be numerically solved for every segment for each of the hundreds of round trips in a given simulation.
-We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity: a majority of the loss is due to the optical coupler, virtually all of the dispersion happens within the CFBG~\cite{agrawal2002}, the pulse is only modulated by the modulator, and the pulse is amplified only within the Er-doped gain fibre.
+We can alleviate this computational expense by noticing each effect is localized to a corresponding component in the cavity.
+A majority of the loss is due to the optical coupler, and virtually all the dispersion happens within the CFBG~\cite{agrawal2002}.
+The pulse is only modulated by the modulator, and the pulse is amplified only within the Er-doped gain fibre.
 Therefore, we can drastically simplify each of the GNLSEs into a form we can solve analytically.
@@
 
-In this paper, we will build an iterative map model for the evolution of a laser pulse as the pulse travels through the cavity.
-In Section~\ref{sec:model}, we will derive our own iterative map model from \eqref{eq:nlse}.
-We will then non-dimensionalize the model and introduce four dimensionless parameters that govern the dynamics of the system.
-We will then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
-We will identify a sharp boundary in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
+In this paper, we build an iterative map model for the evolution of a laser pulse as the pulse travels through the cavity.
+In Section~\ref{sec:model}, we derive our own iterative map from \eqref{eq:nlse}, we non-dimensionalize the model and discover four non-dimensional parameters that govern the dynamics of the system.
+We then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
+A sharp boundary is identified in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
 Finally, our concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
@@
 \label{sec:model}
-We derive our own iterative map model for the evolution of a pulse through a laser cavity by solving a reduced GNLSE for each component in the cavity---except modulation, which we consider to be applied externally by an electro-optic modulator.
+We derive our own iterative map model for the evolution of a pulse through a laser cavity by solving a reduced GNLSE for each component in the cavity---except the modulator, which we consider to be applied externally by an electro-optic modulator.
 Starting with the gain component, we reduce \eqref{eq:nlse} to
@@
 \end{align}
-By assuming the energy entering the gain fibre is $E_g$ and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we integrate \eqref{eq:energyde} to find the energy after amplification is
+By assuming the energy entering the gain fibre is $E_g$, and the energy after travelling through the gain fibre of length $L_g$ is $E_{\text{out}}$, we integrate \eqref{eq:energyde} to find the energy after amplification is
 \begin{align}
@@
 \end{align}
-Then,
+By \eqref{eq:energy}, \eqref{eq:engain} and \eqref{eq:ampfact},
 \begin{align}
-	\mathcal{G}^2 E_g &= E_\text{out}
+	\mathcal{G}^2 E_g &= E_\text{out},
 \end{align}
-by \eqref{eq:energy}, \eqref{eq:engain} and \eqref{eq:ampfact}, therefore,
+therefore,
 \begin{align}
-	G(A) &= \left( \frac{E_\text{out}}{E_g} \right)^{1/2} A, \\
+	G(A) &= \left( \frac{E_\text{out}}{E_g} \right)^{1/2} A \\
 	&=	\left( \frac{\Es}{E_g} W \left( \frac{E_g}{\Es} \exp \left( \frac{E_g}{\Es} \right) \exp( g_0 L_g ) \right) \right)^{1/2} A \label{eq:dimgain}
@@
 \end{align}
-where, $\mathcal{F}$ denotes the Fourier transform.
+where, $\mathcal{F}$ and $\mathcal{F}^{-1}$ denote the Fourier transform and its inverse.
 
-Finally, we consider the modulation. Here, we assume the pulse is modulated by an electro-optic modulator. For simplicity, the form is taken as the Gaussian
+Finally, we consider the modulation. We assume the pulse is modulated by an electro-optic modulator. For simplicity, the form is taken as the Gaussian
 \begin{align}
@@
 This assumption is not restrictive.
-Calcaterra and Boldt~\cite{calcaterra2008a} have shown a sum of Gaussian functions can approximate any square integrable function.
-Therefore, our solution extends to any continuous, bounded modulation function.
+The results apply to any square integrable modulation function through a result of Calcaterra and Boldt~\cite{calcaterra2008a} who prove that linear combinations of translations of a single Gaussian, $\textrm{e}^{-x^2}$, are dense in $L^2(\mathbb{R})$.
+Any continuous modulation function with compact support would fall into this class.
 Additionally, using a saturable absorber in place of an electro-optic modulator is common in practice.
@@
 \label{sec:effects}
-Now that we have the algebraic effect of each component of the cavity, we are ready to take the composition of the maps to give the effect of one round trip of the cavity.
+Now that we have the algebraic effect of each component of the cavity, we are ready to take the composition of the maps to give the effect of one round trip.
 Unlike the models described in Section \ref{sec:intro}, the order of our components is important since the maps in \eqref{eq:dimgain}, and \eqref{eq:dimnl}--\eqref{eq:modform} do not necessarily commute with each other.
@@
 Non-dimensionalization is a technique used in mathematical modelling to better understand the relative importance of different processes within a system.
-In essence, we scale all variables by typical values, based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
+In essence, we scale all variables by typical values based on the geometry and boundary conditions (see, for example,~\cite{howison2005}).
 Doing so `factors' the dimensional units out of the problem---leaving only dimensionless equations with dimensionless parameters.
 The relative magnitudes of the dimensionless parameters characterize the dominant dynamics---comparable to how the Reynolds number describes fluid flow.
-Each process in the laser can be better understood by re-scaling the time, energies, and amplitude by the convenient scalings:
+Each process in the laser can be better understood by scaling the time, energy, and amplitude by the convenient factors:
 \begin{align}
@@
 and we have estimated their sizes using values in Table~\ref{tab:values}.
-The dimensionless parameter $a$ is a measure of the strength of the gain fibre, $b$ is the frequency shift because of the Kerr nonlinearity, $s$ is the ratio of the effectiveness of the CFBG to the width of the pulse, and $h$ is the total loss due to absorption and the optical coupler.
-We note that each expression in \eqref{eq:effects} depends on one dimensionless parameter, except the modulation which is parameter free.
+
+Each expression in \eqref{eq:effects} contains a single parameter that characterizes the device.
+The parameter governing the modulation, the time $T_M$, does not appear in $M(A)$, but is used to define the relative strength of the other devices.
+The gain is characterized by $a$, a measure of the energy added by the gain fibre; the Kerr nonlinearity by $b$, prescribing the frequency shift; the total loss by $h$, includes absorption and the optical coupler; and the dispersion by $s$, specifying the effectiveness of the CFBG to the width of the pulse.
 
@@
 We neglect the effect of the nonlinearity, that is, we take $b \ll 1$.
-We proceed by assuming a fixed point solution will take the form of a linearly chirped Gaussian, and our aim is to find the variance, chirp, and energy of the pulse.
+Proceeding by assuming a fixed point solution in the representation of a linearly chirped Gaussian, our aim is to find the variance, chirp, and energy of the pulse.
 The reasons for this assumption are that the solution to the models presented in~\cite{cutler1955, siegman1969, kuizenga1970a, martinez1984, martinez1985} were Gaussian, the equilibrium shape will correlate to the modulation function, and a Gaussian is a fixed point of the Fourier transform.
@@
 
-We consider the pulse given by
+We consider the pulse, shown in Figure \ref{fig:samplegauss}, given by
 \begin{align}
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase; the pulse is shown in Fig.~\ref{fig:samplegauss}.
+where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase.
 By computing \eqref{eq:A0} after one round trip, and solving $\mathcal{L}(A) = A \textrm{e}^{i \phi}$, tedious manipulations yield the conditions
@@
 \end{equation}
-We find the chirp is
+We find the chirp
 \begin{align}
-	C = \frac{\sigma^4 - \left( \sigma^8 - 16 s^4 \left( 1 - \sigma^2 \right)^2 \right)^{1/2}}{4 s^2 \left( 1 - \sigma^2 \right)}
+	C = \frac{\sigma^4}{2 s^2 (2 - \sigma^2)}
 	\label{eq:chirp}
 \end{align}
-by \eqref{eq:chirprelation}. We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}:
+by combining \eqref{eq:sigrelation} and \eqref{eq:chirprelation}. We obtain the energy of the pulse entering the gain fibre, $E_g$, from \eqref{eq:energyrelation}:
 \begin{align}
@@
 \begin{align}
-	E &= W \left( a E_g \textrm{e}^{E_g} \right), \\
+	E &= W \left( a E_g \textrm{e}^{E_g} \right) \\
 	&= \frac{\log \left( a h^2 \left( 1 - \sigma^2 \right)^{1/2} \right)}{1 - h^2 \left( 1 - \sigma^2 \right)^{1/2}}.
@@
 
-Our linear model indeed exhibits a solution of the same form as previous linear models.
+Our linear model exhibits a solution of the same form as previous linear models.
 However, by including the effect of the nonlinearity, we uncover the rich interplay between dispersion, modulation, and nonlinearity.
@@
 \label{sec:nlresults}
-The nonlinear solution requires a numerical simulation, and so we must specify the input pulse---as in the laboratory.
-One of the common forms is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
+The nonlinear solution is solved with a numerical simulation.
+For the input pulse, one of the common forms is a hyperbolic secant~\cite{coen1997, finot2008, rothenberg1989b, tomlinson1984}, which we assume has the exact form
 \begin{align}
@@
 We focus on the $s$--$b$ plane in particular, since $a$ and $h$ affect only the amplitude of the pulse, whereas the interactions of dispersion and nonlinearity give rise to the instabilities.
-Additionally, as mentioned, a conservative initial energy will affect the dynamics much less than a more intense pulse since the nonlinearity will be negligible while initially coming to equilibrium.
 We examine the relative change in the pulse's envelope between consecutive round trips of the cavity to identify stability.
@@
 In the upper-left region, the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
-In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable.
+In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable to within machine precision.
 The increase in dispersion, coupled with modulation, allows the laser to balance the nonlinear effects.
-The error in this region is on the order of machine precision, suggesting the pulse has indeed reached to equilibrium.
 
@@
 In the unstable region (upper-left) the energy is small.
-The pulse is not able to foster prominent modes in this region and is unsustainable, thus, the intensity is low across the entire pulse.
-In the stable region (lower-right) we find the energy smoothly decays as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
-As $s$ increases, more energy is lost because of modulation since dispersion increases the length of the tails of the pulse.
+The pulse is not able to foster prominent modes in this region, and is unsustainable, thus, the intensity is low across the entire pulse.
+In the stable region (lower-right) we find the energy decays smoothly as both $b$ and $s$ increase, with the contours being hyperbolic-esque.
+As $s$ increases, the tails of the pulse increase in length due to the dispersion, and more energy is lost due to modulation.
 As $b$ increases, our choice of modulation function helps suppress the additional frequencies generated by SPM, ensuring the pulse remains band-limited.
@@
 Finally, we briefly investigate the affect the order of the components has on the dynamics.
-In Section~\ref{sec:model}\ref{sec:effects} we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
-Now, we consider the effect of swapping the dispersion and modulation components.
+In Section~\ref{sec:model}\ref{sec:effects}, we justified the order of the gain, nonlinearity, and loss, but, just assumed dispersion preceded modulation.
+Now we consider the effect of swapping the dispersion and modulation components.
 The overall structure of the energy landscape (Fig.~\ref{fig:energyswitch}) is the same as in Fig.~\ref{fig:energy}.
@@
 The additional energy makes the laser more powerful than in the previous case, which in turn increases the size of the unstable region.
-Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther rightward and upward, and the energy is larger in the stable region---especially away from the origin.
+Comparing with Fig.~\ref{fig:energy}, the unstable upper-left region spreads farther to the right and upward, and the energy is larger in the stable region, especially away from the origin.
 Once again, the energy at the origin is 2.5487, as we are effectively removing the CFBG in the limit $s \rightarrow 0$.
@@
 We recovered linearly chirped Gaussian solutions in the case of a Gaussian modulation function when omitting the nonlinearity.
-Moreover, the solution to the linear model extends to any modulation function using results of~\cite{calcaterra2008a}.
+Moreover, the solution of the linear model extends to any continuous function with compact support when using the results of~\cite{calcaterra2008a}.
 In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.

### 2021-03-02 Papers/Journal/Tuneable_Lasers.tex
Fixed layout of figures
Ready for submission

@@
 Modulation instability causes a pulse to degrade into multiple, much shorter, less intense pulses and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
-Outside of optics, wave breaking and modulation instability occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
+Outside of optics, wave breaking and modulation instability can occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
 Within a ring laser cavity, wave breaking and modulation instability can become parasitic, leading to an unstable and unsustainable pulse.
@@
 While the transfer functions are chosen suitably to have the effect observed in the laboratory, the transfer functions are phenomenologically chosen, and not necessarily obtained directly from the underlying physics.
-Furthermore, these methods have not included the effect of every component, lacking the interactions of dispersion, modulation, and nonlinearity---hindering their models ability to exhibit modulation instability.
+Furthermore, these methods have not included the effect of every component, lacking the interactions of dispersion, modulation, and nonlinearity---hindering their models' ability to exhibit modulation instability.
 
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/ParamSpaceEnergy}
+	\caption{Energy of the pulse after 500 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\label{fig:energy}
+\end{figure}
+
 Also of interest is the energy of the pulse at equilibrium, which we compute numerically by \eqref{eq:energy}.
@@
 	\centering
-	\includegraphics{Figures/ParamSpaceEnergy}
-	\caption{Energy of the pulse after 500 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
-	\label{fig:energy}
+	\includegraphics{Figures/ParamSpaceEnergySwitch}
+	\caption{Energy of the pulse after 500 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\label{fig:energyswitch}
 \end{figure}
@@
 Once again, the energy at the origin is 2.5487, as we are effectively removing the CFBG in the limit $s \rightarrow 0$.
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/ParamSpaceEnergySwitch}
-	\caption{Energy of the pulse after 500 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
-	\label{fig:energyswitch}
-\end{figure}
 

### 2021-05-29 Papers/Journal/Cavity.tex
Finished Chris edits
Updated Figure 1

@@
 % Two laser loops
-\draw [rounded corners=4mm] (0,0) rectangle ++(6,4);
-\draw [rounded corners=4mm] (0,0) rectangle ++(-1.5,4);
+\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4); % Pump
+\draw [fill=white, white] (0, -0.1) rectangle ++(-1.1,2); % Hide pump
+\draw [rounded corners=4mm] (0,0) rectangle ++(6,4); % Main
+
+% Isolator
+\filldraw[fill=white, draw=black] (1,-0.25) rectangle ++(1,0.5) node [midway, anchor=north, yshift=-6] {Isolator};
+\draw[-triangle 90] (1.9,0) -- (1.1,0);
+\draw[very thick] (1.9,0) -- (1.2,0);
 
@@
 \draw (0.5,2.25) circle (0.5cm);
-\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ fibre};
+\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ gain fibre};
 \draw (0.5,1.75) circle (0.5cm);
@@
 % Modulator and pump
-\filldraw[fill=white, draw=black] (2,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
-\filldraw[fill=white, draw=black] (-2.1,1.5) rectangle ++(1.2,1) node [midway] {Pump};
+\filldraw[fill=white, draw=black] (3,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
+\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};
 
@@
 % Circulators
-\filldraw[fill=white, draw=black] (6,2) circle (0.5cm);
+\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,align=center,xshift=0.5cm] {OC};
 \draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);
 
-\filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
-\draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);
+% \filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
+% \draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);
 
-\filldraw[fill=white, draw=black] (0,4) circle (0.5cm) node [anchor=south,align=center,yshift=0.5cm] {Optical circulator};
-\draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);
+% \filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
+% \draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);
+
+% WDMs
+\filldraw[fill=white, draw=black] (-0.15,3.8) rectangle ++(0.3,-0.6) node [midway, anchor=west, xshift=3] {WDM};
+% \filldraw[fill=white, draw=black] (-0.15,0.2) rectangle ++(0.3,0.6) node [midway, anchor=west, xshift=2] {WDM};
 
 % Arrows
-\draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
-\draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+% \draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+% \draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
 \draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
 \draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
-\draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
-\draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+% \draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+% \draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
 

### 2021-05-29 Papers/Journal/Tuneable_Lasers.tex
Updated Figure 1

--- 2021-02-28 Papers/Journal/Tuneable_Lasers.tex
@@
 \usetikzlibrary{shapes.arrows, fadings}
+\usetikzlibrary{arrows}
+\usetikzlibrary{decorations.markings}
 
@@
 	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.
-The pump laser travels clockwise around the left-hand loop (red arrows) energizing the Er-doped gain fibre.
-The main laser travels clockwise around the right-hand loop (blue arrows), with most of the pulse exiting the cavity through the optical coupler.}
+The laser travels clockwise around the loop, with most of the pulse exiting the cavity through the optical coupler.
+CFBG, chirped fibre Bragg grating; OC, optical circulator; WDM, wavelength division multiplexer}
 	\label{fig:cavity}

### 2021-05-29 Papers/Journal/WaveBreaking.jl
Small modification

@@ -1,8 +1,7 @@
+using Distributed
 @everywhere using FFTW
 @everywhere using LambertW
 @everywhere using DelimitedFiles
-#using PyPlot
-using Distributed
 @everywhere using SharedArrays
 
 @everywhere function fftfreq(n::Int)
@@ -131,8 +130,8 @@ dx = x[2] - x[1]
 A0 = exp.(-(x .- 0.5).^2 ./ (2 * 0.05^2))
 A0 = sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
 
-Loop(A0, x, dx, 0.1, 1.0, 2); # Compile
+# Loop(A0, x, dx, 0.1, 1.0, 2); # Compile
 
-Solve(A0, 2, 2, 2) # Compile
+# Solve(A0, 2, 2, 2) # Compile
 
-@time Solve(A0, n, m, numloops, "ResultsDelta.dat")
+# @time Solve(A0, n, m, numloops, "ResultsDelta.dat")

### 2021-05-29 Papers/Journal/Tuneable_Lasers.tex
Updated sigma definition

--- 2021-03-02 Papers/Journal/Tuneable_Lasers.tex
@@
 \end{align}
-where $P$ is the peak power, $C$ is the chirp, $\sigma^2$ is the variance, and $\phi_0$ is the phase.
+where $P$ is the peak power, $C$ is the chirp, $\sigma$ is the half-width of the pulse (at $1 / \textrm{e}$ intensity), and $\phi_0$ is the phase.
 By computing \eqref{eq:A0} after one round trip, and solving $\mathcal{L}(A) = A \textrm{e}^{i \phi}$, tedious manipulations yield the conditions

### 2021-05-31 Papers/Journal/WaveBreaking.jl
commit message

@@ -115,8 +115,21 @@ function Solve(A0, n::Int64, m::Int64, numloops::Int64, fname = "Results.dat")
 	close(f)
 end
 
+function energy_plot(A, x, dx, s, b, N)
+	res = zeros(N)
+
+	for i in 1:N
+		A = Loop(A, x, dx, s, b)
+		res[i] = Energy(A, dx)
+	end
+
+	display(plot(x, abs.(A)))
+
+	return 1:N, res	
+end
+
 # Parameters
-p = 2^16 # Number of points in the discretization
+p = 2^12 # Number of points in the discretization
 width = 8 # Size of window
 E0 = 0.1 # Initial energy
 n = 151 # Number in s
@@ -126,8 +139,8 @@ numloops = 25
 # Initialization
 x = LinRange(-width, width, p)
 dx = x[2] - x[1]
-#A0 = 1.0 ./ cosh.(2 * x) * exp(1im * pi / 4.0)
-A0 = exp.(-(x .- 0.5).^2 ./ (2 * 0.05^2))
+A0 = 1.0 ./ cosh.(2 * x) * exp(1im * pi / 4.0)
+#A0 = exp.(-(x .- 0.5).^2 ./ (2 * 0.05^2))
 A0 = sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
 
 # Loop(A0, x, dx, 0.1, 1.0, 2); # Compile

### 2021-05-31 Papers/Journal/Tuneable_Lasers.tex
Extended paragraph to talk about the energy variation

@@
 		\label{fig:chirp}
-	\end{subfigure} %
+	\end{subfigure} \hfill
 	\begin{subfigure}{\columnwidth}
@@
 With our choice of parameters, \eqref{eq:maxenergy} predicts an equilibrium energy of 2.5535 at the origin, confirming the usefulness of the approximation.
+Moreover, we show in Fig.
+\ref{fig:energytime} the energy variation of four pulses during the 500 round trips.
+In particular, we plot two pulses in the stable region (purple and blue) and two pulses in the unstable region (green and red).
+Each of the pulses, again, has an initial energy of $E_0 = 0.1$, and after about a dozen round trips the energy is approximately 1.25 in the case of the $s = 0.35$, $b = 6.0$, and approximately 2 in the other three cases.
+The two examples in the stable region quickly reach equilibrium, and their energy remains constant for the remaining round trips.
+However, for the examples in the unstable region the pulses lose a considerable amount of their energy and the pulse begins to degrade.
+The energy of the pulses varies by up to 25\% between consecutive round trips.
+A pulse in the unstable region undergoes large transformations with each round trip leading to the error we saw in Fig.
+\ref{fig:error}, as well as the energy variation in Fig.
+\ref{fig:energytime}.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/EnergyTime}
+	\caption{Energy of four pulses during the first 500 round trips ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\label{fig:energytime}
+\end{figure}
 

### 2021-05-31 Papers/Journal/WaveBreaking.jl
Added some lines to generate the energy variation data

@@ -116,16 +116,18 @@ function Solve(A0, n::Int64, m::Int64, numloops::Int64, fname = "Results.dat")
 end
 
 function energy_plot(A, x, dx, s, b, N)
-	res = zeros(N)
+	res = zeros(N+1)
 
-	for i in 1:N
+	res[1] = Energy(A, dx)
+
+	for i in 2:N+1
 		A = Loop(A, x, dx, s, b)
 		res[i] = Energy(A, dx)
 	end
 
-	display(plot(x, abs.(A)))
+	# display(plot(x, abs.(A)))
 
-	return 1:N, res	
+	return 0:N, res	
 end
 
 # Parameters
@@ -148,3 +150,10 @@ A0 = sqrt(E0 / Energy(A0, dx)) * A0 # Normalize
 # Solve(A0, 2, 2, 2) # Compile
 
 # @time Solve(A0, n, m, numloops, "ResultsDelta.dat")
+
+_, y1 = energy_plot(A0, x, dx, 0.2, 1.0, 500)
+_, y2 = energy_plot(A0, x, dx, 0.1, 2.0, 500)
+_, y3 = energy_plot(A0, x, dx, 0.15, 4.0, 500)
+_, y4 = energy_plot(A0, x, dx, 0.35, 6.0, 500)
+
+writedlm("EnergyTime.dat", [0:500 y1 y2 y3 y4])

### 2021-06-02 Papers/Journal/Tuneable_Lasers.tex
Updated conclusion and fixed back matter formatting

@@
 % (depending on journal).
+
+% 2020-12-22: Backmatter sections should use smaller font
+% size, including run-in headings \bmsection.
+\newenvironment{backmatter}{%
+  \small%
+  \newcommand{\bmsection}[1]{\par\medskip\noindent{\bfseries ##1.\enspace}}%
+}{}
 
@@
 Moreover, the solution of the linear model extends to any continuous function with compact support when using the results of~\cite{calcaterra2008a}.
-In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability.
-These instabilities have been demonstrated in a laboratory setting~\cite{agrawal2013, anderson1992, finot2008, rothenberg1989b, tomlinson1985}, but, have proven difficult to predict with simple mathematical models~\cite{meng2020}.
+In contrast, with the inclusion of the nonlinearity, we found an unstable region in the $s$--$b$ plane, with a sharp boundary separating the stable and unstable regions.
+Predicting the conditions under which a tuneable ring laser is unstable has proven difficult with simple mathematical models~\cite{meng2020}.
 We have shown a simple iterative map model is able to reproduce complicated instabilities arising naturally from the interplay between dispersion, modulation, and nonlinear effects.
@@
 
-\section*{Acknowledgement.}
+\begin{backmatter}
+	\bmsection{Funding}
+
+	\bmsection{Acknowledgement}
 	Portions of this work were presented at The V AMMCS International Conference in 2019, ``A new method of modelling tuneable lasers with functional composition'' \cite{metherallammcs}.
@@
 
-\section*{Disclosures.}
+	\bmsection{Disclosures}
 	The authors declare no conflicts of interest.
+
+	\bmsection{Data Availability}
+	Data underlying the results presented in this paper are not publicly available at this time but may be obtained from the authors upon reasonable request.
+\end{backmatter}
 

### 2021-06-02 Papers/Journal/Tuneable_Lasers.tex
Removed instances of modulation instability

@@
 In the nonlinear case, we find the chirp saturates, and the Fourier transform of the pulse becomes more rectangular in shape.
-Finally, for a nominal plane in the parameter space, we uncover a rich, sharp boundary separating the stable region and the unstable region where modulation instability degrades the pulse into an unsustainable state.
+Finally, for a nominal plane in the parameter space, we uncover a rich, sharp boundary separating the stable region, and the unstable region where instabilities degrade the pulse into an unsustainable state.
 \end{abstract}
@@
 The laser travels clockwise around the loop, with most of the pulse exiting the cavity through the optical coupler.
-CFBG, chirped fibre Bragg grating; OC, optical circulator; WDM, wavelength division multiplexer}
+CFBG, chirped fibre Bragg grating; OC, optical circulator; WDM, wavelength division multiplexer.}
 	\label{fig:cavity}
@@
 Several effects arise within the cavity due to the interplay of dispersion, modulation, and nonlinearity~\cite{bohun2015, coen1997, lapre2019, meng2020, oktem2010, shao2019, woodward2018}.
-The two effects of most interest for us are wave breaking, and modulation instability.
-Wave breaking causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
+One effect, wave breaking, causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
 The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edge.
@@
 New frequencies are then generated such that a rectangular profile is induced~\cite{agrawal2013, woodward2018}.
-Modulation instability---which typically arises in the anomalous dispersion regime---is the other effect that will be of interest.
-However, in the presence of multiple frequencies, modulation instability can emerge in the normal dispersion regime as well through cross-phase modulation and four-wave mixing~\cite{agrawal1987, agrawal2013, haelterman1992}.
-Modulation instability causes a pulse to degrade into multiple, much shorter, less intense pulses and can cause a laser to lose coherence~\cite{agrawal1987, coen1997, haelterman1992}.
-Outside of optics, wave breaking and modulation instability can occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
-Within a ring laser cavity, wave breaking and modulation instability can become parasitic, leading to an unstable and unsustainable pulse.
+Outside of optics, wave breaking can also occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
+Within a ring laser cavity, combination of dispersion, modulation, and nonlinearity can also lead to instabilities that degrade the pulse.
+Wave breaking and instabilities can become parasitic, leading to an unstable and unsustainable pulse.
 Understanding the rich landscape of the parameter space is important for determining design principles to guarantee the ring laser is stable and sustainable~\cite{bohun2015, burgoyneemail, finot2008, lapre2019, woodward2018}.
@@
 While the transfer functions are chosen suitably to have the effect observed in the laboratory, the transfer functions are phenomenologically chosen, and not necessarily obtained directly from the underlying physics.
-Furthermore, these methods have not included the effect of every component, lacking the interactions of dispersion, modulation, and nonlinearity---hindering their models' ability to exhibit modulation instability.
+Furthermore, these methods have not included the effect of every component, lacking the interactions of dispersion, modulation, and nonlinearity---hindering their models' ability to exhibit instabilities.
 
@@
 We then examine the results of our model in Section~\ref{sec:results}---first solving the model analytically by assuming the absence of the nonlinearity, then numerically solving the full nonlinear model.
-A sharp boundary is identified in the parameter space separating the region of stability, and the region where modulation instability degrades the pulse.
+A sharp boundary is identified in the parameter space separating the stable region from the unstable region.
 Finally, our concluding thoughts and ideas for possible future work are given in Section~\ref{sec:conclusion}.
@@
 Since a ring laser is cyclic in nature, we use the result of one round trip as the input pulse for the next round trip---restarting the process.
-We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse succumbs to modulation instability.
+We continually repeat this procedure until the envelope and chirp of the pulse reach equilibrium, or the pulse becomes unstable.
 The phase change is uninteresting to us, as the phase cannot easily be measured experimentally.
@@
 Also, the two peaks in the Fourier transform become more pronounced and further apart, and the Fourier transform of the pulse becomes more rectangular.
-However, after a critical point, SPM plays a more substantial role, leading to modulation instability.
+However, after a critical point, SPM plays a more substantial role, leading to instability.
 
-Fig.~\ref{fig:breakevo} highlights the phenomenon of modulation instability.
+Fig.~\ref{fig:breakevo} highlights the instability.
 By decreasing the dispersion compared to Fig.~\ref{fig:chirpft}, we find the pulse begins to `breathe'.
 During the first two dozen round trips of the cavity the SPM compounds and becomes detrimental to the pulse.
-In turn, modulation instability is induced, and degrades the pulse, until the pulse is no longer stable or sustainable.
+In turn, the pulse starts to become unstable and further degrades, until the pulse is no longer stable or sustainable.
 On the other hand, having a more moderate value of $b$, the pulse is able to equilibrate even with a less favourable, random, initial pulse (Fig.~\ref{fig:convevo}), as in~\cite{meng2020}.
@@
 \end{align}
-and we choose $n$ to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates because of modulation instability---we use $n = 500$ in our experiments.
+and we choose $n$ to be sufficiently large to guarantee the pulse reaches equilibrium or deteriorates because of the instability---we use $n = 500$ in our experiments.
 We take the modulus of the pulse since we are interested in the evolution of only the envelope because of the auto-correlation methods used for experimental measurements.
@@
 Two distinct regions split the parameter space, divided by an incredibly sharp, and complicated boundary.
-In the upper-left region, the error is $\bigO{1}$; here, the nonlinearity is too strong, and the SPM induces modulation instability.
+In the upper-left region, the error is $\bigO{1}$; here, the nonlinearity is too strong, and the instability is induced by SPM.
 In the lower-right region we find the opposite behaviour---the pulse reaches an equilibrium state and is stable to within machine precision.
@@
 As $b$ increases, our choice of modulation function helps suppress the additional frequencies generated by SPM, ensuring the pulse remains band-limited.
-We find a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise modulation instability will destroy the pulse.
+We find a more energetic laser requires weaker dispersion, however, the nonlinearity must be correspondingly low, otherwise the pulse will succumb to the instability.
 Moreover, the maximum energy, which occurs in the limit where both $s$ and $b$ go to zero, is 2.5487.
@@
 Analyzing the nonlinear model analytically using an asymptotic expansion for small values of the nonlinearity parameter, $b$, is of interest.
-Doing so will provide insight to how the nonlinearity impacts the linear solution to better understand the manifestation of wave breaking and modulation instability.
+Doing so will provide insight to how the nonlinearity impacts the linear solution to better understand the manifestation of wave breaking and the instability.
 Furthermore, a more detailed analysis of crossing the boundary between stability and instability may provide valuable insight for mechanisms that trigger the instability.

### 2021-06-05 Papers/Journal/Tuneable_Lasers.tex
Finished edits

@@
 \DeclareMathOperator{\sech}{sech}
+
+\renewcommand{\topfraction}{.75}
+\renewcommand{\floatpagefraction}{.8}
 
@@
 
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/Evo}
-	\caption{Evolution of the envelope during one round trip of the cavity.
-The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
-Note, the $z$ axis is not to scale.}
-	\label{fig:cavityevo}
-\end{figure}
-
 % Table of parameter values
-\begin{table*}[!b]
+\begin{table*}[tbp]
 	\centering
@@
 \end{table*}
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/Evo}
+	\caption{Evolution of the envelope during one round trip of the cavity.
+The pulse decays because of the optical coupler, disperses because of the CFBG, is modulated by the modulator, and finally, is amplified by the gain fibre (the envelope is unaltered by the nonlinearity).
+Note, the $z$ axis is not to scale.}
+	\label{fig:cavityevo}
+\end{figure}
 
@@
 
+To further justify the decoupling of the GNSLE into an iterative map, \eqref{eq:nlse} can be written in a dimensionless form where the characteristic time, length, and amplitude are taken to be $T_M$, $L$, and $P_0^{1/2}$, respectively.
+Letting
+\begin{align}
+	T &= T_M \widetilde{T}, & z &= L \widetilde{z}, & A &= P_0^{1/2} \widetilde{A},
+\end{align}
+\eqref{eq:nlse} becomes
+\begin{align}
+	\pdiff{\widetilde{A}}{\widetilde{z}} = \frac{-i \, \textrm{sgn}(\beta_2) L}{L_\textrm{disp}} \pdiff[2]{\widetilde{A}}{\widetilde{T}} + i \frac{L}{L_\textrm{NL}} |\widetilde{A}|^2 \widetilde{A} + \frac{1}{2}g_0 L \, \widetilde{g}(\widetilde{A}) \widetilde{A} - \alpha L \widetilde{A},
+	\label{eq:ndgnlse}
+\end{align}
+where
+\begin{equation}
+	\begin{gathered}
+		\widetilde{g}(\widetilde{A}) = \left( 1 + \frac{P_0 T_M}{\Es} \int_{-\infty}^\infty |\widetilde{A}|^2 \, \df \widetilde{T} \right)^{-1}, \\
+		L_\textrm{disp} = \frac{T_M^2}{|\beta_2|}, \hspace{2cm} L_\textrm{NL} = \frac{1}{\gamma P_0}.
+	\end{gathered}
+\end{equation}
+The dispersion length $L_\textrm{disp}$, and the nonlinear length $L_\textrm{NL}$, are identified in~\cite{agrawal2013} as length scales over which either the dispersive, or nonlinear, effects dominate the evolution of a pulse.
+
+For the gain, the characteristic quantity is $g_0 L$, and within the gain fibre $g_0 L = \bigO{10^1}$.
+Outside this domain, $g_0 L = \bigO{10^{-3}}$, reflecting the small amount of gain in these other regions.
+A similar argument can be made for the attenuation factor $-\alpha L$ by considering the output coupler to be analogous to additional length of fibre.
+The dispersion-dominant regime is characterized by the condition~\cite{agrawal2013}
+\begin{align}
+	\frac{L_\textrm{disp}}{L_\textrm{NL}} = \frac{\gamma P_0 T_M^2}{|\beta_2|} \ll 1.
+\end{align}
+This condition is attained in regions with relatively low pulse power, and a large value of $|\beta_2|$.
+The nonlinearity-dominant regime corresponds to $L_\textrm{disp} / L_\textrm{NL} \gg 1$, with a much larger pulse power, and small value of $|\beta_2|$.
+For a single-mode silicon fibre $|\beta_2| \sim 20$ ps$^2$/km, illustrating that the effective dispersion, $|\beta_2| L$, varies by a factor of $10^4$ from inside to outside the dispersive~region.
+
+We show in Table \ref{tab:NDparams} an order of magnitude estimate of the size of each of the non-dimensional parameters in \eqref{eq:ndgnlse}.
+Within each of the four regions we find that one parameter (highlighted) dominates the three others, further justifying the proposed decoupling process.
+
+% Table of relative dynamics
+\begin{table}[tbp]
+	\centering
+	\caption{Relative size of loss, dispersion, gain, and nonlinearity in each section of the cavity.}
+ 	\label{tab:NDparams}
+ 	\begin{tabular}{ccccc}
+		\hline
+		Parameter \hspace*{-1mm} & Loss & Dispersion & Gain & Fibre \\
+		\hline\noalign{\smallskip}
+		$\alpha L$ & \color{color2}$\bigO{10^{-1}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ \\
+		$L / L_\text{disp}$ & $\bigO{10^{-3}}$ & \color{color2}$\bigO{10^{-1}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ \\
+		$g_0 L$ & $\bigO{10^{-4}}$ & $\bigO{10^{-4}}$ & \color{color2}$\bigO{10^{1}}$ & $\bigO{10^{-4}}$ \\
+		$L / L_\text{NL}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ & $\bigO{10^{-3}}$ & \color{color2}$\bigO{10^{0}}$ \\
+		\noalign{\smallskip}\hline
+	\end{tabular}
+\end{table}
+
 \section{Results}
@@
 Furthermore, we choose a linearly chirped Gaussian because it resembles the envelope, and linear chirp expected from the literature~\cite{burgoyne2014, haus1975, haus1996, haus2000, usechak2005}.
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/Sample_Gauss}
-	\caption{Graph of the linearly chirped Gaussian pulse given by \eqref{eq:A0} with $\phi_0 = 0$.}
-	\label{fig:samplegauss}
-\end{figure}
-
-\begin{figure*}[tbp]
-	\centering
-	\begin{subfigure}{\columnwidth}
-		\centering
-		\includegraphics{Figures/Chirp}
-		\caption{Chirp.}
-		\label{fig:chirp}
-	\end{subfigure} \hfill
-	\begin{subfigure}{\columnwidth}
-		\centering
-		\includegraphics{Figures/FT}
-		\caption{Fourier transform.}
-		\label{fig:ft}
-	\end{subfigure}
-	\caption{Chirp and Fourier transform at equilibrium (after 500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
-	\label{fig:chirpft}
-\end{figure*}
 
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/Sample_Gauss}
+	\caption{Graph of the linearly chirped Gaussian pulse given by \eqref{eq:A0} with $\phi_0 = 0$.}
+	\label{fig:samplegauss}
+\end{figure}
+
+\begin{figure*}[tbp]
+	\centering
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Figures/Chirp}
+		\caption{Chirp.}
+		\label{fig:chirp}
+	\end{subfigure} \hfill
+	\begin{subfigure}{\columnwidth}
+		\centering
+		\includegraphics{Figures/FT}
+		\caption{Fourier transform.}
+		\label{fig:ft}
+	\end{subfigure}
+	\caption{Chirp and Fourier transform at equilibrium (after 500 round trips) initiated by \eqref{eq:nlA0} for three values of $b$, the nonlinearity parameter ($a = 8 \times 10^3$, $h = 0.04$, $s = 0.2$, and $E_0 = 0.1$).}
+	\label{fig:chirpft}
+\end{figure*}
+
 Equating the energy of the pulse given by \eqref{eq:A0} and \eqref{eq:analenergy}, we find the peak power to be
@@
 
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/Break}
+	\caption{Example of a pulse destabilizing from the initial pulse \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.6$, $s = 0.1$, and $E_0 = 0.1$).}
+	\label{fig:breakevo}
+\end{figure}
+
 Fig.~\ref{fig:breakevo} highlights the instability.
@@
 	\centering
-	\includegraphics{Figures/Break}
-	\caption{Example of a pulse destabilizing from the initial pulse \eqref{eq:nlA0} ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.6$, $s = 0.1$, and $E_0 = 0.1$).}
-	\label{fig:breakevo}
+	\includegraphics{Figures/Conv}
+	\caption{Example of a pulse coming to equilibrium from noise ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.1$, and $E_0 = 0.1$).}
+	\label{fig:convevo}
 \end{figure}
@@
 	\centering
-	\includegraphics{Figures/Conv}
-	\caption{Example of a pulse coming to equilibrium from noise ($a = 8 \times 10^3$, $h = 0.04$, $b = 1.0$, $s = 0.1$, and $E_0 = 0.1$).}
-	\label{fig:convevo}
+	\includegraphics{Figures/ParamSpaceErr}
+	\caption{Relative error of a pulse's envelope between round trips 499 and 500 ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\label{fig:error}
 \end{figure}
@@
 The increase in dispersion, coupled with modulation, allows the laser to balance the nonlinear effects.
-
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/ParamSpaceErr}
-	\caption{Relative error of a pulse's envelope between round trips 499 and 500 ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
-	\label{fig:error}
-\end{figure}
 
@@
 
-\begin{figure}[tbp]
-	\centering
-	\includegraphics{Figures/ParamSpaceEnergySwitch}
-	\caption{Energy of the pulse after 500 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
-	\label{fig:energyswitch}
-\end{figure}
-
 Finally, we briefly investigate the affect the order of the components has on the dynamics.
@@
 For example, incorporating a frequency dependence in the gain function, or model a saturable absorber instead of a Gaussian electro-optic modulator.
+
+\begin{figure}[tbp]
+	\centering
+	\includegraphics{Figures/ParamSpaceEnergySwitch}
+	\caption{Energy of the pulse after 500 round trips with dispersion and modulation swapped ($a = 8 \times 10^3$, $h = 0.04$, and $E_0 = 0.1$).}
+	\label{fig:energyswitch}
+\end{figure}
 

### 2021-06-06 Papers/Journal/Tuneable_Lasers.tex
Moved table
Added a few minor changes

@@
 Outside of optics, wave breaking can also occur in other areas with nonlinear waves and dispersive media such as plasma physics, heat propagation, transmission lines, and fluid dynamics~\cite{coen1997, rothenberg1989b}.
-Within a ring laser cavity, combination of dispersion, modulation, and nonlinearity can also lead to instabilities that degrade the pulse.
+Within a ring laser cavity, the combination of dispersion, modulation, and nonlinearity can also lead to instabilities that degrade the pulse.
 Wave breaking and instabilities can become parasitic, leading to an unstable and unsustainable pulse.
@@
 % Table of parameter values
-\begin{table*}[tbp]
+\begin{table*}[!b]
 	\centering
@@
 The nonlinearity-dominant regime corresponds to $L_\textrm{disp} / L_\textrm{NL} \gg 1$, with a much larger pulse power, and small value of $|\beta_2|$.
-For a single-mode silicon fibre $|\beta_2| \sim 20$ ps$^2$/km, illustrating that the effective dispersion, $|\beta_2| L$, varies by a factor of $10^4$ from inside to outside the dispersive~region.
+For a single-mode silicon fibre $|\beta_2| \sim 20$ ps$^2$/km~\cite{agrawal2013}, illustrating that the effective dispersion, $|\beta_2| L$, varies by a factor of $10^4$ from inside to outside the dispersive~region.
 
@@
 
-We consider the pulse, shown in Figure \ref{fig:samplegauss}, given by
+We consider the pulse, shown in Fig. \ref{fig:samplegauss}, given by
 \begin{align}

### 2021-06-14 Papers/Journal/Tuneable_Lasers.tex
Made final grammar changes

@@
 One effect, wave breaking, causes the leading edge of a pulse to redshift, and the trailing edge to blueshift (the effect reverses in the anomalous dispersion regime) to the point a shock develops~\cite{anderson1992, rothenberg1989a, rothenberg1989b, tomlinson1984, tomlinson1985}.
-The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edge.
+The frequency shift causes the pulse to become more rectangular in the frequency domain, with a linear chirp over most of the pulse, saturating at the leading and trailing edges.
 In optics, wave breaking arises from self-phase modulation (SPM), which is a direct effect of the Kerr nonlinearity, causing the pulse to interfere with itself.
@@
 A comprehensive description of the theory and history of mode-locking lasers is presented in Haus~\cite{haus2000}.
-While the GNLSE well represents the dynamics in a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.
-\ref{fig:cavity}.
+While the GNLSE well represents the dynamics in a single optical fibre, \eqref{eq:nlse} is not entirely representative of the underlying physics within a laser cavity such as Fig.~\ref{fig:cavity}.
 The derivation of \eqref{eq:nlse} assumes that each process affects the pulse continuously within the cavity.
@@
 Once again, our assumption is justified by the localization of each effect to its corresponding component, allowing us to simplify \eqref{eq:nlse} to \eqref{eq:gainexample} in the gain fibre.
-To proceed, we assume the gain has the form
+To proceed, we assume the gain has the~form
 \begin{align}
@@
 \end{align}
-where $W$ is the Lambert $W$ function. Moreover, as the gain will amplify the pulse without changing the shape of the envelope, the pulse after travelling through the gain fibre can be expressed as
+where $W$ is the Lambert $W$ function. Moreover, as the gain will amplify the pulse without changing the shape of the envelope, the pulse after travelling through the gain fibre can be expressed~as
 \begin{align}
@@
 \end{align}
-as the reduced versions of \eqref{eq:nlse}, respectively. Solving \eqref{eq:nlde} over a length of fibre $L_f$, we find the effect of the fibre nonlinearity is
+as the reduced versions of \eqref{eq:nlse}, respectively. Solving \eqref{eq:nlde} over a length of fibre $L_f$, we find the effect of the fibre nonlinearity~is
 \begin{align}
@@
 \end{align}
-where $L_T$ is the total length of fibre in the cavity, $R$ is the reflectivity of the optical coupler, and the $(1 - R)$ term  is the loss to the output of the laser.
+where $L_T$ is the total length of fibre in the cavity, $R$ is the reflectivity of the optical coupler, and the $(1 - R)$ term is the percent not lost to the output of the laser.
 The effect of dispersion is obtained by solving \eqref{eq:dispde} over the `length' of the dispersive medium, $L_D$,
@@
 This assumption is not restrictive.
-The results apply to any square integrable modulation function through a result of Calcaterra and Boldt~\cite{calcaterra2008a} who prove that linear combinations of translations of a single Gaussian, $\textrm{e}^{-x^2}$, are dense in $L^2(\mathbb{R})$.
+The results apply to any square integrable modulation function through a result of Calcaterra and Boldt~\cite{calcaterra2008a} who prove that linear combinations of translations of a single Gaussian, $\exp \left( -x^2 \right)$, are dense in $L^2(\mathbb{R})$.
 Any continuous modulation function with compact support would fall into this class.
@@
 
-To further justify the decoupling of the GNSLE into an iterative map, \eqref{eq:nlse} can be written in a dimensionless form where the characteristic time, length, and amplitude are taken to be $T_M$, $L$, and $P_0^{1/2}$, respectively.
+To further justify the decoupling of the GNLSE into an iterative map, \eqref{eq:nlse} can be written in a dimensionless form where the characteristic time, length, and amplitude are taken to be $T_M$, $L$, and $P_0^{1/2}$, respectively.
 Letting
@@
 
-We consider the pulse, shown in Fig. \ref{fig:samplegauss}, given by
+We consider the pulse, shown in Fig.~\ref{fig:samplegauss}, given by
 \begin{align}
@@
 The forms of \eqref{eq:equilvar}--\eqref{eq:analpower} make the expressions difficult to work with.
-However, recall that $s$ is small, thus, we asymptotically expand \eqref{eq:equilvar}--\eqref{eq:analpower} assuming $s \ll 1$, and
+However, recall that $s$ is small, thus, we asymptotically expand \eqref{eq:equilvar}--\eqref{eq:analpower} assuming $s \ll 1$, and find
 \begin{align}
@@
 With our choice of parameters, \eqref{eq:maxenergy} predicts an equilibrium energy of 2.5535 at the origin, confirming the usefulness of the approximation.
-Moreover, we show in Fig.
-\ref{fig:energytime} the energy variation of four pulses during the 500 round trips.
+Moreover, we show in Fig.~\ref{fig:energytime} the energy variation of four pulses during the 500 round trips.
 In particular, we plot two pulses in the stable region (purple and blue) and two pulses in the unstable region (green and red).
@@
 The energy of the pulses varies by up to 25\% between consecutive round trips.
-A pulse in the unstable region undergoes large transformations with each round trip leading to the error we saw in Fig.
-\ref{fig:error}, as well as the energy variation in Fig.
-\ref{fig:energytime}.
+A pulse in the unstable region undergoes large transformations with each round trip leading to the error we saw in Fig.~\ref{fig:error}, as well as the energy variation in Fig.~\ref{fig:energytime}.
 

### 2021-06-14 Papers/Journal/Reviewers_Letter.tex
Added letter for editor

\documentclass[12pt,twoside,letterpaper]{article}

\usepackage{fancyhdr}
\usepackage{graphicx,epsfig,color,pstricks}
\usepackage{amsmath}
\usepackage{latexsym,amssymb}
% \usepackage{gensymb}
\usepackage{units}
\usepackage{hyperref}

\usepackage{caption}
\usepackage{mwe}

% sget page layout parameters (two sides)
\newlength{\defaultheadheight}
\setlength{\defaultheadheight}{\headheight}
\newlength{\defaultheadsep}
\setlength{\defaultheadsep}{\headsep}

% set page layout parameters (two sides)
\textwidth 7.0in
\textheight 9.75in
\hoffset -0.25in 
\voffset -0.75in
\topmargin 0in
\headheight \defaultheadheight
\headsep 0.16in
\footskip=0in
\oddsidemargin 0in 
\evensidemargin 0in %22pt default
%\evensidemargin 0.34in %22pt default
\raggedbottom

\DeclareMathOperator{\prob}{Prob}
\DeclareMathOperator{\pv}{PV}
\DeclareMathOperator{\sech}{sech}

%differentiation
\makeatletter
\providecommand*{\diff}%
  {\@ifnextchar^{\DIfF}{\DIfF^{}}}
\def\DIfF^#1{%
  \mathop{\mathrm{\mathstrut d}}%
    \nolimits^{#1}\gobblespace}
\def\gobblespace{%
  \futurelet\diffarg\opspace}
\def\opspace{%
  \let\DiffSpace\!%
  \ifx\diffarg(%
    \let\DiffSpace\relax
  \else
    \ifx\diffarg[%
      \let\DiffSpace\relax
  \else
    \ifx\diffarg\{%
      \let\DiffSpace\relax
    \fi\fi\fi\DiffSpace}

\providecommand*{\deriv}[3][]{%          % \deriv[]{u}{x}
  \frac{\diff^{#1}#2}{\diff #3^{#1}}}
%\providecommand*{\deriv}[3][]{\frac{\diff^{#1}}{\diff #3^{#1}}#2}
\providecommand*{\pd}[3][]{\frac{\partial^{#1}#2}{\partial #3^{#1}}}
\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}
\providecommand{\littleO}[1]{\ensuremath{\mathop{}\mathopen{}o\mathopen{}\left(#1\right)}}

% Special code to use the double bracket without loading the whole stmry package
\DeclareSymbolFont{stmry}{U}{stmry}{m}{n}
\SetSymbolFont{stmry}{bold}{U}{stmry}{b}{n}
\DeclareMathDelimiter\llbracket{\mathopen}{stmry}{"4A}{stmry}{"71}
\DeclareMathDelimiter\rrbracket{\mathclose}{stmry}{"4B}{stmry}{"79}

\begin{document}

\newcounter{mychapter}
\setcounter{mychapter}{1}
%\renewcommand{\labelenumi}{\textbf{\arabic{mychapter}.\arabic{enumi}}}

\pagenumbering{arabic}
%\setcounter{page}{1}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\headrulewidth}{0.1pt}

\fancyhead[L]{Review of \textit{Predicting instabilities of a tuneable ring laser with an\\
iterative map model} by Metherall \& Bohun}
\fancyhead[R]{Response to referee}

~\vspace{\baselineskip}

The authors would like to thank the reviewer for their kind words and suggested improvements to the proposed manuscript. We are grateful for the insight provided by this referee, and their comments have significantly strengthened the work. The initial comments reflect on a number of weaknesses in this document, and we will address these first. For clarity, we repeat these initial comment here.

\begin{quote}
    In this submission by Metherall and Bohun, they developed a nonlinear iterative map model for tunable ring lasers. This discrete (split-step) method significantly reduce the computation cost comparing with solving the full GNLSE for each fiber iteratively. However, my major concern is that to what extend is the method used in the manuscript valid. As was pointed out by the authors, the method is quite similar to that used in Ref.~[5] which had a negligible nonlinear effect and were validated experimentally.

    The model in the manuscript includes the nonlinear effect. It is well known that nonlinear effects can interact simultaneously with dispersion and gain. However, these effects are considered separately in the method used by the authors. It is not clear whether the approximations and assumptions made in the manuscript are physically reliable. I would suggest the authors validating their method by comparing with numerical results calculated from the complete propagation equation (GNLSE) sequentially for each components in the cavity at typical system parameters. Otherwise, it is hard to know if the method makes sense in fiber laser modellings. A comparison may also shed some light on how to arrange the order of the components which has been shown to be important (by comparing Figs.~8 and 9) in the discrete model.
\end{quote}

To further justify the decoupling of the GNLSE, as proposed, Eq.~(2) is written in dimensionless form. This allows the identification of both a dispersion length scale and a nonlinear length scale in correspondence with the classical analysis found in Ref.~[18]. As in  Ref.~[18], a condition is identified which characterizes the dispersion-dominant regime (low power, and large value of $|\beta_2|$) and the nonlinear-dominant regime (high power, and small value of $|\beta_2|$) of the laser pulse. The complete analysis of the relative size of the loss, dispersion, gain, and nonlinearity in each section of the cavity is summarized in a new table, Table 2. From the relative order of magnitude estimates, it is further illustrated that within each of the four regions, one parameter dominates the other three.

\vspace{\baselineskip}

Below are the remaining remarks and the changes made to the manuscript to 
address a variety of issues.

\vspace{\baselineskip}
\noindent
\textbf{Other comments:}

\begin{itemize}
    \item[{(1)}]
    I suggest the authors be a bit careful to use the terminology ``modulation instability'' in explaining the results shown in Fig.~5. Modulation instability is well defined concept in physics. I didn't see any clear sign of modulation instabilities in the current results. Modulation instabilities usually manifest itself by significant sidebands in the spectrum (for example, please see Refs.~[9--10, 18] in the manuscript, Opt.~Lett.~27, 482--484 (2002) and Opt.~Express 17, 21497--21508 (2009)). Actually, there are many mechanisms that can cause instabilities in fiber lasers (for example see, Phys.~Rev.~E 63, 056602 and Opt.~Lett.~39, 1362--1365 (2014)). If the authors have enough evidence to prove that the instabilities shown in the manuscript is indeed from the modulation instability, please clarify it in details. Otherwise, I would suggest not use this terminology to avoid misleading.

    \begin{quote}
        We agree with the referee, and all mentions of `modulation instability' have been removed from the manuscript.
    \end{quote}

    \item[{(2)}]
    Since the authors are investigating lasers in the manuscript, it may be better to show the intensity instead of the amplitude of the pulse in Figs.~2--6, as was commonly done in the community.

    \begin{quote}
        Figure 2, and Figures 4--6 have been changed to show the intensity instead of the amplitude. No change was made to Figure 3 since we actually want the waveform for that, including the real and imaginary parts. The style of Figure 2 was completely reworked to accommodate this.
    \end{quote}

    \item[{(3)}]
    In Fig.~1, the left loop for the pump is quite strange for me. Why the intracavity laser was fed back to the pump? It is also uncommon to use a circulator for coupling pump into the cavity. I would suggest replacing the two circulators with a WDM as was commonly in other literatures (which is also the case in the experiments).

    \begin{quote}
        Figure 1 has been fixed as suggested by the referee by replacing the two circulators with a WDM. 
    \end{quote}

    \item[{(4)}]
    The acronyms in Fig.~1 should be defined explicitly in the caption.

    \begin{quote}
        Done as indicated.
    \end{quote}

    \item[{(5)}]
    In the context below Eq.~(26), ``$\sigma^2$ is the variance''. It may be better to say `$\sigma$' the half width of the pulse (at 1/e intensity) as in  Ref.~[18].

    \begin{quote}
        Changed $\sigma$ as indicated by the reviewer.
    \end{quote}

    \item[{(6)}]
    In Figs.~8 and 9, the pulse energies at a single roundtrip (i.e., roundtrip 500 in the manuscript) were used. But the pulse energy usually changes significantly over roundtrips in the unstable regime. Is it also true for the results shown in the manuscript? If so, I would suggest use an average value over a certain range of roundtrips, or please show another plot for a typical pulse energy evolution over roundtrips for the unstable regime.

    \begin{quote}
        Figure 9 has been added to show the energy as a function of the number of round trips. In addition, the following text was added to Section 3B: Nonlinear Solution and Instability.

        \vspace{\baselineskip}

        ``Moreover, we show in Fig.~9 the energy variation of four pulses during the $500$ round trips. In particular, we plot two pulses in the stable region (purple and blue) and two pulses in the unstable region (green and red). Each of the pulses, again, has an initial energy of $E_0 = 0.1$, and after about a dozen round trips the energy is approximately $1.25$ in the case of the $s = 0.35$, $b = 6.0$, and approximately $2$ in the other three cases. The two examples in the stable region quickly reach equilibrium, and their energy remains constant for the remaining round trips. However, for the examples in the unstable region the pulses lose a considerable amount of their energy and the pulse begins to degrade. The energy of the pulses varies by up to 25\% between consecutive round trips. A pulse in the unstable region undergoes large transformations with each round trip leading to the error we saw in Fig.~7, as well as the energy variation in Fig.~9.''
    \end{quote}

    \item[{(7)}]
    In the conclusion paragraph, it was claimed that ``In contrast, with the inclusion of the nonlinearity, we were able to recover wave breaking and modulation instability, and found a sharp boundary of stability. These instabilities have been demonstrated in a laboratory setting [13, 15, 17, 18, 22], but, have proven difficult to predict with simple mathematical models [11]''. I don't think it appropriate to relate the dynamics in the manuscript to that in Refs.~[13, 15, 17, 18, 22]. The dissipative (gain and loss) and feedback nature of the laser in the manuscript seems to be different from the single-pass dynamics in Refs.~[13, 15, 17, 18, 22].

    \begin{quote}
        We agree with the referee and thank them for this insight. This comparison has been removed.
    \end{quote}
\end{itemize}

Finally, a number of small grammatical changes were made to the manuscript. These were
identified on the final reading.
\end{document}

### 2021-06-14 Papers/Journal/Metherall_JOSA_B.tex
TeX file including the cavity figure since you can only submit one TeX file

--- 2021-06-14 Papers/Journal/Tuneable_Lasers.tex
@@
 	\centering
-	\input{Cavity}
+	\begin{tikzpicture}
+		% Two laser loops
+		\draw [rounded corners=4mm] (0,0) rectangle ++(-1,4); % Pump
+		\draw [fill=white, white] (0, -0.1) rectangle ++(-1.1,2); % Hide pump
+		\draw [rounded corners=4mm] (0,0) rectangle ++(6,4); % Main
+
+		% Isolator
+		\filldraw[fill=white, draw=black] (1,-0.25) rectangle ++(1,0.5) node [midway, anchor=north, yshift=-6] {Isolator};
+		\draw[-triangle 90] (1.9,0) -- (1.1,0);
+		\draw[very thick] (1.9,0) -- (1.2,0);
+
+		% Gain
+		\draw (0.5,2.25) circle (0.5cm);
+		\draw (0.5,2) circle (0.5cm) node [anchor=west,xshift=0.5cm,align=center] {Er-doped \\ gain fibre};
+		\draw (0.5,1.75) circle (0.5cm);
+
+		% Modulator and pump
+		\filldraw[fill=white, draw=black] (3,-0.75) rectangle ++(2,1.5) node [midway] {Modulator};
+		\filldraw[fill=white, draw=black] (-1.6,1.5) rectangle ++(1.2,1) node [midway] {Pump};
+
+		% Coupler and output
+		\draw[-stealth] (3,4) -- (3,5.5) node [pos=0.75,anchor=west,xshift=0.25cm] {Laser output};
+		\draw[densely dashdotted] (2.5,3.5) -- (3.5,4.5) node [pos=1,anchor=north,yshift=-0.75cm,align=center] {Optical \\ coupler};
+
+		% Circulators
+		\filldraw[fill=white, draw=black] (6,2) circle (0.5cm) node [anchor=west,align=center,xshift=0.5cm] {OC};
+		\draw[->,>=stealth] (6,2.325) arc (90:360:0.325cm);
+
+		% \filldraw[fill=white, draw=black] (0,0) circle (0.5cm);
+		% \draw[->,>=stealth] (0,0.325) arc (90:360:0.325cm);
+
+		% \filldraw[fill=white, draw=black] (0,4) circle (0.5cm);
+		% \draw[->,>=stealth] (0,4.325) arc (90:360:0.325cm);
+
+		% WDMs
+		\filldraw[fill=white, draw=black] (-0.15,3.8) rectangle ++(0.3,-0.6) node [midway, anchor=west, xshift=3] {WDM};
+		% \filldraw[fill=white, draw=black] (-0.15,0.2) rectangle ++(0.3,0.6) node [midway, anchor=west, xshift=2] {WDM};
+
+		% Arrows
+		% \draw [->,>=stealth,domain=20:70,blue] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+		% \draw [->,>=stealth,domain=110:160,red] plot ({0.675*cos(\x)}, {0.675*sin(\x)});
+		\draw [->,>=stealth,domain=110:160,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
+		\draw [->,>=stealth,domain=200:250,blue] plot ({6+0.675*cos(\x)}, {2+0.675*sin(\x)});
+		% \draw [->,>=stealth,domain=200:250,red] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+		% \draw [->,>=stealth,domain=290:340,blue] plot ({0.675*cos(\x)}, {4+0.675*sin(\x)});
+
+		\draw [->,>=stealth,domain=270:360,blue] plot ({2.325+0.5*cos(\x)}, {4.675+0.5*sin(\x)});
+		\draw [->,>=stealth,blue] (2.125, 4.675-0.5) -- (2.325+0.6, 4.675-0.5);
+
+		% Grating
+		\draw (5.5,2) -- (3.5,2) node [pos=0.5,anchor=south,yshift=0.25cm,xshift=-0.15cm] {CFBG};
+		\foreach \i in {0,...,13}
+			\draw (3.5 + \i*\i/100,1.75) -- (3.5 + \i*\i/100,2.25);
+
+	\end{tikzpicture}
 	\caption{Common cavity construction of a fibre ring laser~\cite{burgoyne2014, chung2017, lapre2019, shao2019}.

### 2021-07-08 Papers/Journal/Proof_Errors.tex
Compiled corrections to the proofs

\documentclass[11pt,a4paper]{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage{graphicx}
%\usepackage[subfolder,cleanup]{gnuplottex}
%\usepackage{amsthm}
%\usepackage{enumitem}
%\usepackage{wrapfig}
%\usepackage{subcaption}
%\usepackage{hyperref}
%\usepackage{tikz}

% Nicer brackets for operators
\let\originalleft\left
\let\originalright\right
\renewcommand{\left}{\mathopen{}\mathclose\bgroup\originalleft}
\renewcommand{\right}{\aftergroup\egroup\originalright}

% Math operators
\providecommand{\bigO}[1]{\ensuremath{\mathop{}\mathopen{}\mathcal{O}\mathopen{}\left(#1\right)}}

% Macros
\newcommand{\diff}[3][\hspace{-0.5pt}]{\frac{\textrm{d}^{#1}#2}{\textrm{d}{#3}^{#1}}}
\newcommand{\pdiff}[3][\hspace{-0.5pt}]{\frac{\partial^{#1}#2}{\partial{#3}^{#1}}}
\newcommand{\df}{\, \textrm{d}}
%\newcommand{\eps}{\varepsilon}

% Row colouring in tables
%\usepackage[table]{xcolor}
%\rowcolors{2}{gray!25}{white}

% Margin size
\newgeometry{margin=2cm}

% Reference style
%\bibliographystyle{ieeetr}

\title{Predicting instabilities of a tunable ring laser with \\
an iterative map model \\ \Large Requested Revisions}
\author{Brady Metherall \and C. Sean Bohun}
\date{\today}

\begin{document}
\maketitle

Below are our responses to the queries, and additional requested revisions to the proofs.

\section{Queries}
\begin{enumerate}
	\item AU: Your submitted paper listed two e-mails. Please let us know the sole corresponding author. You also have the option of listing no corresponding author at all, in which case both of the e-mail addresses can be listed with the ``e-mail:" label.
	\begin{quote}
		List both e-mail addresses.
	\end{quote}
	\item AU: Please check the callout to Appendix 5 in this sentence, as no such section exists in this paper: ``The expansions in the limit $s \rightarrow \infty$ are given in Appendix 5."
	\begin{quote}
		The sentence should read ``The expansions in the limit $s \rightarrow \infty$ are given in Appendix A."
	\end{quote}
	\item AU: Please check the section number in this sentence, as no Section 22.1 appears in this paper: ``In Section 22.1, we justified the order of the gain, nonlinearity..."
	\begin{quote}
		The sentence should read ``In Section 2A, we justified the order of the gain, nonlinearity...".
	\end{quote}
	\item AU: The funding information for this article has been generated using the information you provided to OSA at the time of article submission. Please check it carefully. If any information needs to be corrected or added, please provide the full name of the funding organization/institution as provided in the CrossRef Open Funder Registry (https://search.crossref.org/funding).
	\begin{quote}
		The funding information is fine.
	\end{quote}
	\item AU: The Data Availability Statement for this article has been generated automatically. Please check it carefully. If any information needs to be corrected or added, please provide us with an updated statement.
	\begin{quote}
		The Data Availability Statement is fine.
	\end{quote}
	\item AU: Please update Ref.~[37].
	\begin{quote}
		The updated reference is:

		C. Calcaterra, “Linear Combinations of Gaussians with a Single Variance are Dense in $L^2$ ,” in Proceedings of the World Congress on Engineering, vol. II, 2008.

		\begin{verbatim}
			@inproceedings{calcaterra2008,
				author    = {C. Calcaterra},
				title     = {{Linear Combinations of Gaussians with a Single Variance
				are Dense in $L^2$}},
				booktitle = {Proceedings of the World Congress on Engineering},
				volume    = {II},
				year      = {2008},
			}
		\end{verbatim}
	\end{quote}
\end{enumerate}

\section{Punctuation}
\begin{itemize}
	\item Add comma on line 31 after `\ldots\ multiphoton microscopy [1]'.
	\item Add comma on line 62 after `\ldots\ Schr\"odinger equation'.
	\item Add comma on line 71 after `\ldots\ (GNLSE) [2,18,20--23]'.
	\item Add comma on line 101 after `\ldots\ for every segment'.
	\item Add comma on line 169 after `\ldots\ and therefore'.
	\item Enclose `$E_g$' in commas on line 314.
	\item Add comma on line 345 after `\ldots\ given in Eq.~(25)'.
	\item Change `$s - b$' to `$s$--$b$' on lines 380 and 465 (italicized s, en-dash, italicized b).
\end{itemize}

\section{Grammar and style}
\begin{itemize}
	\item Add `model' to line 132 to read `\ldots\ our own iterative map model from \ldots'.
	\item Change line 3 of Fig.~2 caption to read `\ldots\ the modulator, and finally, is amplified \ldots' or `\ldots\ the modulator, and finally is amplified \ldots'.
	\item Change `Ps$^2$' to `ps$^2$' in line 2 of Table 1.
	\item Add `relative' to line 256 to read `\ldots\ the CFBG relative to the width \ldots'.
	\item Change `Figure 5' to `Fig.~5' on line 359.
	\item Hyphenate `upper left' and `lower right' on lines 408 and 411 (or remove hyphenation on lines 394, 396, and 451).
	\item Capitalize `Theory' on line 588.
	\item Capitalize `Experimental' on line 591.
\end{itemize}

\section{Spacing}
\begin{itemize}
	\item Remove indents on lines 64, 158, 159, 161, 168, 179, 261, 263, 274, 311, 312, 317, 339, and 488.
	\item Remove blank lines 170, 174, 175, 306, 307, 316, 326, 327, 328, and 487.
	\item Add horizontal space between equations in equation 23, and 26.
	\item Fix short hanging singular word on lines 152, 199, 242, 246, 266, and 310.
\end{itemize}

\section{Alignment}
\begin{itemize}
	\item Align equations 12 and 13; 14, 15, and 16; 25; 38 and 39; 42, 43, and 45; 49 and 50.
	\item Vertically centre the labels for equations 24, 27, 28, and 35.
	\item Left justify `Description' column in Table 1.
	\item Move second line of equations 27, and 35 further right.
	\item Centre align the two lines of equation 28.
	\item Align Fig.~6 and Fig.~8.
\end{itemize}

\section{Miscellaneous}
\begin{itemize}
	\item Fix size of parentheses in equations 17, 19, 20, 24, 31, 32, 33, 35, 37, 38, 39, 40, 41, 42, 43, 44, 45, 49, and 50; and line 193.
	\item Change font in sub-captions of Fig.~4 to match rest of document.
	\item Change `$\partial 2$' to `$\partial^2$' in first line of equation 27.
	\item Change `$\mathcal{O}$' to upper-case / full size on lines 268 and 269.
	\item Re-highlight the diagonal entries of Table 2, or remove the reference on line 283.
	\item Move Fig.~9 to previous page under Fig.~8.
	\item Insert `BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling.' to line 499 after `\ldots\ [41].'.
\end{itemize}

%\bibliography{Ref}

\end{document}

### 2021-07-24 Papers/Journal/Proof_Errors_v2.tex
Added second iteration of proof revisions

--- 2021-07-08 Papers/Journal/Proof_Errors.tex
@@
 
+\newcommand{\Es}{E_{\textrm{sat}}} % Saturation energy
+
 % Math operators
@@
 \title{Predicting instabilities of a tunable ring laser with \\
-an iterative map model \\ \Large Requested Revisions}
+an iterative map model \\ \Large Requested Revisions v2}
 \author{Brady Metherall \and C. Sean Bohun}
@@
 \maketitle
-
-Below are our responses to the queries, and additional requested revisions to the proofs.
-
-\section{Queries}
-\begin{enumerate}
-	\item AU: Your submitted paper listed two e-mails.
-Please let us know the sole corresponding author.
-You also have the option of listing no corresponding author at all, in which case both of the e-mail addresses can be listed with the ``e-mail:" label.
-	\begin{quote}
-		List both e-mail addresses.
-	\end{quote}
-	\item AU: Please check the callout to Appendix 5 in this sentence, as no such section exists in this paper: ``The expansions in the limit $s \rightarrow \infty$ are given in Appendix 5."
-	\begin{quote}
-		The sentence should read ``The expansions in the limit $s \rightarrow \infty$ are given in Appendix A."
-	\end{quote}
-	\item AU: Please check the section number in this sentence, as no Section 22.1 appears in this paper: ``In Section 22.1, we justified the order of the gain, nonlinearity..."
-	\begin{quote}
-		The sentence should read ``In Section 2A, we justified the order of the gain, nonlinearity...".
-	\end{quote}
-	\item AU: The funding information for this article has been generated using the information you provided to OSA at the time of article submission.
-Please check it carefully.
-If any information needs to be corrected or added, please provide the full name of the funding organization/institution as provided in the CrossRef Open Funder Registry (https://search.crossref.org/funding).
-	\begin{quote}
-		The funding information is fine.
-	\end{quote}
-	\item AU: The Data Availability Statement for this article has been generated automatically.
-Please check it carefully.
-If any information needs to be corrected or added, please provide us with an updated statement.
-	\begin{quote}
-		The Data Availability Statement is fine.
-	\end{quote}
-	\item AU: Please update Ref.~[37].
-	\begin{quote}
-		The updated reference is:
-
-		C. Calcaterra, “Linear Combinations of Gaussians with a Single Variance are Dense in $L^2$ ,” in Proceedings of the World Congress on Engineering, vol. II, 2008.
-
-		\begin{verbatim}
-			@inproceedings{calcaterra2008,
-				author    = {C. Calcaterra},
-				title     = {{Linear Combinations of Gaussians with a Single Variance
-				are Dense in $L^2$}},
-				booktitle = {Proceedings of the World Congress on Engineering},
-				volume    = {II},
-				year      = {2008},
-			}
-		\end{verbatim}
-	\end{quote}
-\end{enumerate}
-
-\section{Punctuation}
 \begin{itemize}
-	\item Add comma on line 31 after `\ldots\ multiphoton microscopy [1]'.
-	\item Add comma on line 62 after `\ldots\ Schr\"odinger equation'.
-	\item Add comma on line 71 after `\ldots\ (GNLSE) [2,18,20--23]'.
-	\item Add comma on line 101 after `\ldots\ for every segment'.
-	\item Add comma on line 169 after `\ldots\ and therefore'.
-	\item Enclose `$E_g$' in commas on line 314.
-	\item Add comma on line 345 after `\ldots\ given in Eq.~(25)'.
-	\item Change `$s - b$' to `$s$--$b$' on lines 380 and 465 (italicized s, en-dash, italicized b).
+	\item Align $b=$ with $s=$ in equation 25.
+	\item The second lines of equations 27 and 35 should be further right, for example:
+	\begin{equation}
+		\begin{gathered}
+		\sigma^2 = \sqrt{2} s \left( s^6 + 3s^2 + \sqrt{4 + s^4} \left( 1 + s^4 \right) \right)^{1/2} \\
+		\hspace{15mm} - s^4 - s^2 \sqrt{4 + s^4}.
+		\end{gathered}
+	\end{equation}
+	\item The two lines of equation 28 should be centred:
+	\begin{equation}
+		\begin{gathered}
+			\widetilde{g}(\widetilde{A}) = \left( 1 + \frac{P_0 T_M}{\Es} \int_{-\infty}^\infty |\widetilde{A}|^2 \, \df \widetilde{T} \right)^{-1}, \\
+			L_\textrm{disp} = \frac{T_M^2}{|\beta_2|}, \quad L_\textrm{NL} = \frac{1}{\gamma P_0}.
+		\end{gathered}
+	\end{equation}
+	\item The font size in equations 27 and 28 seems to have been reduced, please return to the normal~size.
+	\item Align figures 7 and 9.
+	\item Most of the $\exp$, $\log$, $W$, and $\mathcal{O}$ seem to have additional space before the parenthesis, please remove the extra space.
+For example, compare the $W \left( a E_g \textrm{e}^{E_g} \right)$ terms in equations 33 and 38.
 \end{itemize}
 
-\section{Grammar and style}
+\noindent Please correct the size of the parentheses for:
 \begin{itemize}
-	\item Add `model' to line 132 to read `\ldots\ our own iterative map model from \ldots'.
-	\item Change line 3 of Fig.~2 caption to read `\ldots\ the modulator, and finally, is amplified \ldots' or `\ldots\ the modulator, and finally is amplified \ldots'.
-	\item Change `Ps$^2$' to `ps$^2$' in line 2 of Table 1.
-	\item Add `relative' to line 256 to read `\ldots\ the CFBG relative to the width \ldots'.
-	\item Change `Figure 5' to `Fig.~5' on line 359.
-	\item Hyphenate `upper left' and `lower right' on lines 408 and 411 (or remove hyphenation on lines 394, 396, and 451).
-	\item Capitalize `Theory' on line 588.
-	\item Capitalize `Experimental' on line 591.
+	\item Exponential on second line of equation 24.
+	\item Logarithm in equation 37.
+	\item $\exp \left( g_0 L_g \right)$ in equation 9, 13, 25.
+	\item $\mathcal{O}$ in paragraph above equation 29 (two instances), and in Table 2.
 \end{itemize}
-
-\section{Spacing}
-\begin{itemize}
-	\item Remove indents on lines 64, 158, 159, 161, 168, 179, 261, 263, 274, 311, 312, 317, 339, and 488.
-	\item Remove blank lines 170, 174, 175, 306, 307, 316, 326, 327, 328, and 487.
-	\item Add horizontal space between equations in equation 23, and 26.
-	\item Fix short hanging singular word on lines 152, 199, 242, 246, 266, and 310.
-\end{itemize}
-
-\section{Alignment}
-\begin{itemize}
-	\item Align equations 12 and 13; 14, 15, and 16; 25; 38 and 39; 42, 43, and 45; 49 and 50.
-	\item Vertically centre the labels for equations 24, 27, 28, and 35.
-	\item Left justify `Description' column in Table 1.
-	\item Move second line of equations 27, and 35 further right.
-	\item Centre align the two lines of equation 28.
-	\item Align Fig.~6 and Fig.~8.
-\end{itemize}
-
-\section{Miscellaneous}
-\begin{itemize}
-	\item Fix size of parentheses in equations 17, 19, 20, 24, 31, 32, 33, 35, 37, 38, 39, 40, 41, 42, 43, 44, 45, 49, and 50; and line 193.
-	\item Change font in sub-captions of Fig.~4 to match rest of document.
-	\item Change `$\partial 2$' to `$\partial^2$' in first line of equation 27.
-	\item Change `$\mathcal{O}$' to upper-case / full size on lines 268 and 269.
-	\item Re-highlight the diagonal entries of Table 2, or remove the reference on line 283.
-	\item Move Fig.~9 to previous page under Fig.~8.
-	\item Insert `BM acknowledges the support provided by the EPSRC Centre for Doctoral Training in Industrially Focused Mathematical Modelling.' to line 499 after `\ldots\ [41].'.
-\end{itemize}
-
-%\bibliography{Ref}
+I assume the additional space after the $\exp$ and such is a consequence of increasing the size of the parentheses. Please ensure the above changes do not add additional spacing.
 

### 2022-12-20 Thesis/Figures/Laser.tex
Missed this file somehow

\begin{tikzpicture}
% Light
\fill[red, path fading=fade left] (-3,-0.75/2.0) rectangle (3,0.75/2.0); % Gain
\fill[red, fill opacity=0.25] (-4,-0.75/2.0) rectangle (-3,0.75/2.0); % Left
\fill[red] (3,-0.75/2.0) rectangle (4,0.75/2.0); % Right
\fill[red] (4,-0.2) rectangle (6,0.2); % Right

\draw[fill=Goldenrod] (-4,1) rectangle (-3.8,-1); % Left
\fill[pattern=north west lines, pattern color=Goldenrod] (3.8,-0.2) rectangle (4,0.2); % Right Mid
\draw[fill=Goldenrod] (3.8,0.2) rectangle (4,1); % Right Top
\draw[fill=Goldenrod] (3.8,-0.2) rectangle (4,-1); % Right Bottom
\draw[pattern=mydots, pattern color=Purple] (-3,-0.75) rectangle (3,0.75); % Gain
\draw (-4,1) -- (4,1); % Top
\draw (-4,-1) -- (4,-1); % Bottom

% Labels
\draw[->, >=stealth, thick] (3.5,-1.5) -- (3.9,-0.75) node[pos=-0.3] {Partially Reflecting Mirror};
\draw[->, >=stealth, thick] (-3.5,-1.5) -- (-3.9,-0.75) node[pos=-0.3] {Mirror};
\draw[->, >=stealth, thick] (-1,-1.43) -- (-1,-0.5) node[pos=-0.3] {Gain Medium};
\draw[->, >=stealth, thick] (5,1.2) -- (5.5,0) node[pos=-0.3] {Laser Output};
\draw[->, >=stealth, thick] (0,1.2) -- (-3.5,0);
\draw[->, >=stealth, thick] (0,1.2) -- (3.5,0);
\draw (0,1.5) node {Laser Light};
\end{tikzpicture}
